### 2019-04-29 0_main.tex
first project setup

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref}
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

\bibliographystyle{elsarticle-num-names}

% ACM template
%
%\documentclass[acmtog,anonymous,timestamp,review]{acmart}
%
%\usepackage{booktabs} % For formal tables
%

% My TK added packages and commands

	% for for using hyperref and elsarticle-num-names together in order to get \citeauthor to work
	\makeatletter
	\providecommand{\doi}[1]{%
	  \begingroup
	    \let\bibinfo\@secondoftwo
	    \urlstyle{rm}%
	    \href{http://dx.doi.org/#1}{%
	      doi:\discretionary{}{}{}%
	      \nolinkurl{#1}%
	    }%
	  \endgroup
	}
	\makeatother

	% have multiline subfigure captions be centered
	\usepackage[labelformat=parens]{subcaption} % subfigures
	\captionsetup[subfigure]{justification=centering}
	\captionsetup{subrefformat=parens} % pure refernce subfigure with parentheses: fig.10a and (b)
	%\renewcommand\thesubfigure{(\alph{subfigure})} % refernce subfigure always with parentheses: fig.10(a) and (b)

	\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period} % use `Fig.' for figure subscript instead of `Figure'

	\usepackage[export]{adjustbox} % [right] alignment for includegraphics

	\usepackage{rotating} % turn env for rotating text in figures

	\usepackage{wrapfig} % inline figures

	% tables
	\usepackage{multirow} % multicolumn, multirow
	\usepackage{colortbl} % \cellcolor{<color>}
	\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}   %% centered
	\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}m{#1}}  %% right aligned

	\usepackage[capitalise]{cleveref} % automatically add `Fig.'  etc before a reference.

        \usepackage{ amssymb } % \therefore

	\usepackage[binary-units]{siunitx} % mm and stuff
	\sisetup{per-mode = symbol}
	\DeclareSIUnit\pixel{px}

	\usepackage{units} % \nicefrac{3}{8}

	\usepackage[inline]{enumitem} % inline enumerate*

	\usepackage[toc,page]{appendix} % appendicces

	\usepackage{pgfplots}
	\usepackage{pgfplotstable} % tikzpicture table plots
	\pgfplotsset{compat=1.15}
	\usetikzlibrary{backgrounds}

	\usepackage{algpseudocode} % algorithmic
	\usepackage{algorithm} % wrapper for pseudocode to give a caption and label
	\newcommand{\pluseq}{\mathrel{+}=} %pluseq symbol

    % \usepackage[disable]{todonotes} % notes not showed  
    % \usepackage[draft]{todonotes}   % notes showed
    \usepackage{color,soul} % caps, highlight (\hl)

%    \newcommand{\todo}[1]{\hl{#1}}

%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
%	\newcommand{\charlie}[1]{\textcolor[rgb]{0, 0.2, 0}{\todo{[Charlie: #1]}}}
%	\newcommand{\toberemoved}[1]{\textcolor[rgb]{0.9, 0, 0.2}{\st{#1}}}
%	\newcommand{\inserttext}[1]{\textcolor[rgb]{0, 0.7, 0}{\hl{#1}}}
%	\newcommand{\replacewith}[2]{\toberemoved{#1}\inserttext{#2}}

    \newcommand{\changed}[1]{#1}
    %\newcommand{\changed}[1]{\hl{#1}}

	\renewcommand\floatpagefraction{.8}

	% deal with missing images which are not directly included in the repo
	\iffalse
	\newcommand{\noimage}{%
	  \setlength{\fboxsep}{-\fboxrule}%
	  \fbox{\phantom{\rule{10pt}{10pt}}File missing\phantom{\rule{10pt}{10pt}}}% Framed box
	}
	\let\includegraphicsoriginal\includegraphics
	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage}}
	\fi
% ENd of TK's added packages and commands

% ACM template
%
% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
%
% DOI
%\acmDOI{10.475/123_4}
%
% ISBN
%\acmISBN{123-4567-24-567/08/06}
%
%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El  Paso, Texas USA}
%\acmYear{1997}
%\copyrightyear{2016}
%
%\acmPrice{15.00}

\begin{document}
\baselineskip11pt % SPM template

\begin{frontmatter} % SPM template

\title{Title}

\author{Paper ID: xxx}

\author[um,tud]{Tim Kuipers}
%\author[tud]{Jun Wu}
%\author[cuhk]{Charlie Wang{\corref{cor1}}}
%\ead{cwang@mae.cuhk.edu.hk}
%\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
%\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

\begin{abstract}
abstract
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
%\begin{CCSXML}
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

%\keywords{Space-filling Curve, Fractal, Dithering} % ACM
\begin{keyword} % SPM
keyword
\end{keyword}

\end{frontmatter}

% \temp{Table of contents just for reviewing purposes
% \tableofcontents
% }

\input{1_intro}

\input{2_related_work}

\input{4_method}

\input{10_applications}

\section*{References}
\bibliography{99_mybib}

\end{document}

### 2019-04-29 1_intro.tex
first project setup

\section{Introduction}

Compare to simple offsets with constant width

\subsection{Goal}
\begin{itemize}
\item Accurate fabrication of thin walls
\item Prevent underfilling and overfilling
\item ... for accurately matching stiffness properties
\item ... and/or translucency properties
\end{itemize}

### 2019-04-30 10_applications.tex
first mockup litho section

\section{Applications}
\subsection{3D Lithophane}
``The illuminance $E_\text{p}$ lux at a location $d$ metres from a point source of intensity $I$ candela is given by the cosine law of illumination,
$E_\text{p} = I \cos \theta / d^2$.''\cite{snow2001plant}
We relate the distances to the model: $E_\text{p} = I \cos \theta / (d_\text{rel} \cdot d_\text{max})^2 = d_\text{max}^2 I \cos \theta / d_\text{rel}^2$.
The scaling factor $d_\text{max}^2 I$ depends on the light source (intensity and location) and the 3D model.

The RGB values are scaled in order to prevent too dark requests which would correspond to too thick shell: $R' = E_\text{min} +  (1 - E_\text{min}) R$.
Likewise for G and B.

We assume a simple translucency model where twice the thickness implies squaring the fraction of transmitted light.
Suppose a thickness of $w=1$ corresponds to \SI{30}{\percent} absorbtion, so the transmittance is $\tau_1 = 0.7$.
Then a thickness of $w=2$ should correspond to a transmittance of $\tau = \tau_1^2 = 0.7^2 = .49$.
% A thickness of $w=4$ then corresponds to $\tau = (\tau_1^2)^2$.
In general $\tau = \tau_1^w$, so we derive that $w = \log_{\tau_1} \tau = \frac{\log \tau}{\log \tau_1} = c \log \tau$,
where $c$ and $\tau_1$ depend on the material.
The thickness of the shell at any location is determined by $w = c \log \frac{E_\text{p}}{E_\text{r}}$.

The requested luminance is computed from the texture image as $E_\text{r} = I_\text{r} \left( 0.212655 R^\gamma + 0.715158 G^\gamma + 0.072187 B ^\gamma \right)$, where $\gamma = 2.2$.
This formula comes from the official conversion from sRGB to CIE XYZ and taking the Y for luminance.
Zero light requires infinite thickness, so we introduce an $E_\text{min}$.
We might choose to cap all $E_\text{r}$ to lie above $E_\text{min}$, but that means we'd lose a range of brightnesses.
We instead choose to resize the range of requested brightnesses to be between min luminance and $1.0$.

$E_\text{p}$ depends on an unknown scaling factor $I$, and $E_\text{r}$ can be scaled at will.
The total ratio $\frac{E_\text{p}}{E_\text{r}}$ can therefore be scaled by some factor $b$:
$w = c \log b \frac{E_\text{p}}{E_\text{r}} = cb + c \log \frac{E_\text{p}}{E_\text{r}} = x + c \log \frac{E_\text{p}}{E_\text{r}}$
(Beware this formula can give negative values for $w$.)

We can choose $x$ so as to optimize the range of achievable brightnesses given the minimum and maximum thickness of the shell.
Finally, the offset is clamped to within the range $[0.4, 3.0]$ so that it is always manufacturable with a nozzle size of \SI{0.4}{\milli\meter} and is not too large.

For materials where $\tau_1 \to 1$ (i.e. $c \to 0$) the translucency is too high and the luminance modulation would require thicknesses which are too large.
For materials where $\tau_1 \to 0$ (i.e. $c \to -\infty)$ the translucency is too low and the luminance is modulated by a too small range in thicknesses.
The optimal $\tau_1$ depends on the size and geometry of the model as well as the texture colors.
See \url{https://www.photonics.com/Articles/Accurate_Transmission_Measurements_of_Translucent/a32297} on measurement of transmittance.
Also see \url{https://www.plasticsnet.com/doc/article-how-to-measure-translucent-materials-0001}

### 2019-04-30 2_related_work.tex
related work section

\section{Related Work}
Adjusted MAT structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
\Cref{moessen}

Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017}
\Cref{jin}

Using variable width lines to fit a precise amount of lines using the MAT. \cite{Ding2016a}
\Cref{ding}

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/related_work/moessen.jpg}
\caption{asfd}
\label{moessen}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
\caption{asfd}
\label{jin}
\end{subfigure}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
\caption{asfd}
\label{ding}
\end{figure}

### 2019-04-30 4_method.tex
initial method section
transcribed method considerations

\section{Method}
\paragraph{Overview}
\begin{itemize}
\item compute medial axis transform (MAT)
\item find verts `of high curvature' in the medial axis
\item round the distance measures at those locations to integer multiples of the middle of the range of possible bead widths
\item introduce points on the `arms' of the medial axis connected to the changed verts, around even subdivision of the distance measures
\item connect points to the outline with new fingers
\item introduce new locations on the `fingers' of the medial axis at ideas distances for fingers from non-rounded medial axis verts
\item introduce new locations on the fingers at regular intervals for medial axis verts with rounded distance measures
\item connect all locations to form the inset polygons and polylines
\end{itemize}

\subsection{Straight Skeleton or Medial Axis?}
Medial Axis!
Medial axis is stable against small perturbations in the input polygon!
Concave corners are handled irrespective of how many vertices are in a corner.

$\to$ approximate parabolas for simpler processing!

This approximation leads to even spacing,
while a derived formula seems to produce different results:

See \url{/home/t.kuipers/Documents/PhD/Variable_Width_project/pathplanning preliminaries/medial_axis_parabolas.svg}

\Cref{medial_axis_parabolas}

\hl{But the uneven spacing figure looks like its evenly spaced in the direction orthogonal to the toolpath itself!}

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
\end{subfigure}
\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline.}
\label{medial_axis_parabolas}
\end{figure}

\subsection{Angle of fingers introduced on the skeleton}
\Cref{finger_angles}
Cannot be optimized.
Always has to be orthogonal to the polygon segment.
Otherwise the algorithm isn’t stable w.r.t. extra vertices.

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
\end{subfigure}
\caption{Figner angles should always be orthogonal}
\label{finger_angles}
\end{figure}

\subsection{Single bead segments}
\Cref{single_bead_strategy}
Could be printed from polygon and return to polygon over same segment without extruding

How to deal with single beads connecting two polys?
: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly

How to deal with three-way intersection single beads?
: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
\end{subfigure}
\caption{We can do single-bead segments. Blue is travel move.}
\label{single_bead_strategy}
\end{figure}

\subsection{When to introduce fingers?}
Depends on the angle between the poly segments

When to introduce joints rather than using existing joints? When round joint distances to integer multiples of the nozzle size rather than introducing a new joint?

\paragraph{We could introduce bones implicitly.}
Instead of changing the straight skeleton and introducing bones,
we can simply introduce new vertices on the polygon and generate a new straight skeleton.

\subsection{Where to add fingers?}
\Cref{rounded_dist_measures}
Based on unrounded distance measures.
Otherwise we don’t get the switch to twice the bead width
Moreover, the algorithm wouldn’t be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.

\hl{But what does this mean?
When should I round distances to integer multiples?!}

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/rounded_dist_measures.jpg}
\caption{Distance measure rounding}
\label{rounded_dist_measures}
\end{figure}

### 2019-05-01 4_method.tex
expand thinking on method

@@
 
+\begin{figure}[H]
+\begin{subfigure}{0.9\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
+\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
+\end{subfigure}
+\begin{subfigure}{0.9\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
+\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
+\label{medial_axis_parabolas_functions}
+\end{subfigure}
+\caption{The equidistant points between a vert and a line form a parabola.
+There are different methods for generating toolpaths which are in between the medial axis and the outline.
+Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
+\label{medial_axis_parabolas}
+\end{figure}
+
 \hl{But the uneven spacing figure looks like its evenly spaced in the direction orthogonal to the toolpath itself!}
 
-\begin{figure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
-\end{subfigure}
-\caption{The equidistant points between a vert and a line form a parabola. There are different methods for generating toolpaths which are in between the medial axis and the outline.}
-\label{medial_axis_parabolas}
+Perhaps we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
+We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
+No, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.9\columnwidth]{sources/method/angular_based_spacing.pdf}
+\caption{Angular based spacing isn't feasible.
+The bottom medial axis bone has different spacing based on the two patches.
+The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
+\label{angular_based_spacing}
 \end{figure}
@@
 Always has to be orthogonal to the polygon segment.
-Otherwise the algorithm isn’t stable w.r.t. extra vertices.
+Otherwise the algorithm isn't stable w.r.t. extra vertices.
 
-\begin{figure}
+\begin{figure}[H]
 \begin{subfigure}{0.45\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
+\caption{Stability against extra vertices}
+\label{finger_angles_stability}
 \end{subfigure}
@@
 
-\begin{figure}
+\begin{figure}[H]
 \begin{subfigure}{0.45\columnwidth}
@@
 
-\subsection{Where to add fingers?}
+%\subsection{Where to add fingers?}
+%\Cref{rounded_dist_measures}
+%Based on unrounded distance measures.
+%Otherwise we don't get the switch to twice the bead width.
+%Moreover, the algorithm wouldn't be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.
+%\hl{But what does this mean?
+%When should I round distances to integer multiples?!}
+
+\subsection{Angle estimation}
+When the angle between two outline segments is small, the naive method will produce long triangular cusps.
+We can measure the angle between two outline segments which generate a MAT segment by looking at the angle where the lines going through those segments (would) meet.
+Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
+if the Euclidean distance is larger than twice the distance measure difference, the angle between the segments is less than {\SI{60}{\degree}}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
+\caption{Distance based angle estimation. By comparing the euclidean distance between two vertices with the distance measure of the MAT we can skip comparing the angles between the outline segments.}
+\label{distance_based_angles}
+\end{figure}
+
+The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
+\begin{figure}[H]
+\centering
+\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
+\end{figure}
+
+\subsection{Where to round distance measures?}
 \Cref{rounded_dist_measures}
-Based on unrounded distance measures.
-Otherwise we don’t get the switch to twice the bead width
-Moreover, the algorithm wouldn’t be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.
+Based on where the medial axis stops being of high curvature.
 
-\hl{But what does this mean?
-When should I round distances to integer multiples?!}
+We mark bones as to-be-split based on the angle between the two edges of the polygon for which this bone is the bisector.
+Parabolas are always to-be-split, since all points on the parabola are equidistant, so not rounding would introduce a gap along the parabola.
+%For parabolas we check the angle between the three points involved: the end points of the line segment and the point which together generate the parabola.
+That angle is never less than \SI{90}{\degree}.
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/rounded_dist_measures.jpg}
+\hl{Is it impossible for three marked edges to come together?}
+
+When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?
+But that isn't stable against perturbations such as \cref{finger_angles_stability}!
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
 \caption{Distance measure rounding}
@@
 \end{figure}
+
+\begin{figure}[H]
+\includegraphics[width=\columnwidth]{sources/method/rounded_vs_unrounded.pdf}
+\caption{Toolpaths employing dist rounding vs without.}
+\label{rounded_vs_unrounded}
+\end{figure}

### 2019-05-03 4_method.tex
MAT distance remapping and the cutoff point for markings

@@
 \end{subfigure}
-\caption{Figner angles should always be orthogonal}
+\caption{Figner angles should always be orthogonal to the outlines}
 \label{finger_angles}
@@
 \includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
+\caption{Overview}
+\label{single_bead_strategy_overview}
 \end{subfigure}
@@
 \includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
+\caption{Travel order}
 \end{subfigure}
@@
 \includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
+\caption{Minimal Euclidean distance for a given difference in MAT distance measure.}
+\label{distance_ratio_limit}
+\end{figure}
+
+\subsection{Determining which parts of the MAT should be transformed}
+\Cref{rounded_dist_measures}
+\paragraph{line-line-segments}
+We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
+
+\paragraph{line-point segments}
+For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
+The angle between the outline segments is twice the angle between the MAT segment and an outline segment.
+The angle between the MAT parabola and the x-axis is the inverse tangent of the derivative of this formula: $\tan^{-1} \left( \abs x / d \right)$.
+The angle is less than \SI{60}{\degree} when 
+$\tan^{-1} \left( \abs x / d \right) < \SI{30}{\degree}$ 
+i.e. when $\abs x/d < 1 / \sqrt{3}$
+i.e. when $\abs x < d / \sqrt{3}$.
+So we mark the part of the parabola as to-be-transformed for which $x \in [-d / \sqrt{3}, d / \sqrt{3}]$.
+
+\paragraph{point-point segments}
+For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
+For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + \frac12 d}$.
+The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{x}{\sqrt{x^2 + d/2}}$
+So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
+%Wolfram Alpha:
+so $\abs x < \frac{\sqrt{d}}{\sqrt{6}} \approx 0.408 d$.
+So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
+\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}
+
+\subsection{Ends of markings}
+For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
+See bottom of \cref{rounded_vs_unrounded}.
+
+It impossible for three marked edges to come together.
+(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
+
+However, \hl{what if we connect two marked segments using a small segment?}
+It seems there is some distance limit based on \cref{distance_ratio_limit}.
+
+\subsection{MAT distance remapping}
+In a narrow cusp region we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
+See \cref{single_bead_strategy_overview}.
+We use a distance of the median bead width for the transition.
+The transition needs to be robust against extra fingers in the MAT
+How do we compute the vertex location of an inset on a finger which crosses a transitional segment in the middle?
+
+By aligning the MAT distance with Euclidean space around the transition locations, we obtain a stable method for determining the vertex locations of insets.
+See \cref{distance_rounding_transition}.
+The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
+\caption{MAT distance remapping.}
+\label{distance_rounding_transition}
 \end{figure}
@@
 \subsection{Where to round distance measures?}
-\Cref{rounded_dist_measures}
-Based on where the medial axis stops being of high curvature.
-
-We mark bones as to-be-split based on the angle between the two edges of the polygon for which this bone is the bisector.
-Parabolas are always to-be-split, since all points on the parabola are equidistant, so not rounding would introduce a gap along the parabola.
-%For parabolas we check the angle between the three points involved: the end points of the line segment and the point which together generate the parabola.
-That angle is never less than \SI{90}{\degree}.
-
-\hl{Is it impossible for three marked edges to come together?}
-
 When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?

### 2019-05-03 10_applications.tex
expand on litho section and TODOs

@@
 Also see \url{https://www.plasticsnet.com/doc/article-how-to-measure-translucent-materials-0001}
+
+\hl{The ambient illuminance can be better approximated using existing algorithms.
+We can render the object lit from within and bake the illumination into a separate texture channel.
+That channel can then serve as input to our program.}
+
+Performing offsets can sometimes produce self-intersections.
+We therefore export the outer and inner shell and perform a boolean difference operation using existing tools (Blender).

### 2019-05-03 4_method.tex
restructure method and give a clear overview

@@
 \section{Method}
-\paragraph{Overview}
-\begin{itemize}
-\item compute medial axis transform (MAT)
-\item find verts `of high curvature' in the medial axis
-\item round the distance measures at those locations to integer multiples of the middle of the range of possible bead widths
-\item introduce points on the `arms' of the medial axis connected to the changed verts, around even subdivision of the distance measures
-\item connect points to the outline with new fingers
-\item introduce new locations on the `fingers' of the medial axis at ideas distances for fingers from non-rounded medial axis verts
-\item introduce new locations on the fingers at regular intervals for medial axis verts with rounded distance measures
-\item connect all locations to form the inset polygons and polylines
-\end{itemize}
+The general idea is to generate the medial axis transform and round the distance measures to integer multiples of the nominal bead width,
+so that there is never a gap region left over in the middle of the polygon.
 
-\subsection{Straight Skeleton or Medial Axis?}
-Medial Axis!
-Medial axis is stable against small perturbations in the input polygon!
-Concave corners are handled irrespective of how many vertices are in a corner.
+We round to ingteger multiples of half the nozzle width so as to allow single-bead segments.
+These could be printed from polygon and return to polygon over same segment without extruding
 
-$\to$ approximate parabolas for simpler processing!
-
-This approximation leads to even spacing,
-while a derived formula seems to produce different results:
-
-See \url{/home/t.kuipers/Documents/PhD/Variable_Width_project/pathplanning preliminaries/medial_axis_parabolas.svg}
-
-\Cref{medial_axis_parabolas}
-
-\begin{figure}[H]
-\begin{subfigure}{0.9\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
-\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
-\end{subfigure}
-\begin{subfigure}{0.9\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
-\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
-\label{medial_axis_parabolas_functions}
-\end{subfigure}
-\caption{The equidistant points between a vert and a line form a parabola.
-There are different methods for generating toolpaths which are in between the medial axis and the outline.
-Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
-\label{medial_axis_parabolas}
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/method/rounded_vs_unrounded.pdf}
+\caption{Toolpaths employing dist rounding vs without.}
+\label{rounded_vs_unrounded}
 \end{figure}
 
-\hl{But the uneven spacing figure looks like its evenly spaced in the direction orthogonal to the toolpath itself!}
-
-Perhaps we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
-We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
-No, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.9\columnwidth]{sources/method/angular_based_spacing.pdf}
-\caption{Angular based spacing isn't feasible.
-The bottom medial axis bone has different spacing based on the two patches.
-The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
-\label{angular_based_spacing}
-\end{figure}
-
-\subsection{Angle of fingers introduced on the skeleton}
-\Cref{finger_angles}
-Cannot be optimized.
-Always has to be orthogonal to the polygon segment.
-Otherwise the algorithm isn't stable w.r.t. extra vertices.
-
-\begin{figure}[H]
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
-\caption{Stability against extra vertices}
-\label{finger_angles_stability}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
-\end{subfigure}
-\caption{Figner angles should always be orthogonal to the outlines}
-\label{finger_angles}
-\end{figure}
-
-\subsection{Single bead segments}
-\Cref{single_bead_strategy}
-Could be printed from polygon and return to polygon over same segment without extruding
-
-How to deal with single beads connecting two polys?
-: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly
-
-How to deal with three-way intersection single beads?
-: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly
-
-\begin{figure}[H]
+\begin{figure}
 \begin{subfigure}{0.45\columnwidth}
@@
 
-\subsection{When to introduce fingers?}
-Depends on the angle between the poly segments
+\subsection{Overview}
+\begin{enumerate}
+\item compute medial axis transform (MAT)
+\item find places `of high curvature' in the medial axis and mark those regions
+\item transform the MAT distance measures in the marked regions to enable fitting an integer multiple beads.
+		This transformation uses trasnition regions to smoothly transition from $n$ into $n+1$ insets.
+\item introduce extra `joints' on the medial axis in order to discretize the transformed distance measure
+\item connect these new joints to the outline with new `bones' (In the standard MAT manner)
+\item (optional) transform MAT distance fields along all bones, while keeping the endpoint dist measures fixed.
+(Deviate from evenly distributed linear space in order to have outer outlines closer to the nominal bead width and only change the innermost couple of toolpaths.)
+\item define locations everywhere on the bones of the medial axis at integer MAT distances
+\item connect all locations with odd distance measure to form the inset toolpaths
+\item connect all even locations to form the extent of the toolpaths, which defines the variable width of the segments.
+\end{enumerate}
 
-When to introduce joints rather than using existing joints? When round joint distances to integer multiples of the nozzle size rather than introducing a new joint?
+\subsection{1. Compute MAT}
 
-\paragraph{We could introduce bones implicitly.}
-Instead of changing the straight skeleton and introducing bones,
-we can simply introduce new vertices on the polygon and generate a new straight skeleton.
+\begin{figure}
+% from /home/t.kuipers/Documents/PhD/Variable_Width_project/pathplanning preliminaries/straight_skeleton_vs_medial_axis.svg
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/example_straight_skeleton.pdf}
+\caption{Straight skeleton}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/example_medial_axis.pdf}
+\caption{Medial axis}
+\end{subfigure}
+\caption{Example polygon middle analysis thingies. Difference is colored.}
+\label{medial_axis_vs_straight_skeleton}
+\end{figure}
 
-%\subsection{Where to add fingers?}
-%\Cref{rounded_dist_measures}
-%Based on unrounded distance measures.
-%Otherwise we don't get the switch to twice the bead width.
-%Moreover, the algorithm wouldn't be stable: the locations where bones would get introduces would depend on where the other joints are, instead of on the distance measure.
-%\hl{But what does this mean?
-%When should I round distances to integer multiples?!}
+\paragraph{Medial axis rather than Straight Skeleton}
+See \cref{medial_axis_vs_straight_skeleton}.
+Medial axis handles concave corners differently:
+instead of generating the bisector, it will generate a parabolic arc in between the vertex and another line segment of the outline polygon.
 
-\subsection{Angle estimation}
-When the angle between two outline segments is small, the naive method will produce long triangular cusps.
+Medial axis is stable against small perturbations in the input polygon!
+Concave corners are handled irrespective of how many vertices are in a corner.
+
+$\to$ approximate parabolas for simpler processing!
+A straight skeleton can be made to coincide with the medial axis by changing concave corners into an infinitesimal circle arc;
+this does introduce a lot of extra bones, though.
+
+\subsection{2. High curvature marking}
+\label{sec:transitioning_cutoff}
+\Cref{rounded_dist_measures}
+We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
+We generalize this concept of angle to parabola sections and to MAT sections generated by two outline verts.
+
+\paragraph{line-line-segments}
+When the angle between two outline segments is small, the naive method will produce long triangular gaps.
 We can measure the angle between two outline segments which generate a MAT segment by looking at the angle where the lines going through those segments (would) meet.
@@
 \end{figure}
-
-\subsection{Determining which parts of the MAT should be transformed}
-\Cref{rounded_dist_measures}
-\paragraph{line-line-segments}
-We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
 
@@
 
-\subsection{Ends of markings}
-For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
-See bottom of \cref{rounded_vs_unrounded}.
+\subsection{3. MAT distance transformation}
 
-It impossible for three marked edges to come together.
-(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
+\begin{figure}
+\centering
+\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
+\caption{Distance measure rounding}
+\label{rounded_dist_measures}
+\end{figure}
 
-However, \hl{what if we connect two marked segments using a small segment?}
-It seems there is some distance limit based on \cref{distance_ratio_limit}.
+See \cref{rounded_dist_measures}.
 
-\subsection{MAT distance remapping}
-In a narrow cusp region we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
+In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
 See \cref{single_bead_strategy_overview}.
@@
 
-\subsection{Where to round distance measures?}
-When a vertex in the medial axis has only a part of the connected bones marked then the distance measure should be rounded?
-But that isn't stable against perturbations such as \cref{finger_angles_stability}!
+\subsubsection{Ends of markings}
+For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
+See bottom of \cref{rounded_vs_unrounded}.
+
+It impossible for three marked edges to come together.
+(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
+
+However, \hl{what if we connect two marked segments using a small segment?}
+It seems there is some distance limit based on \cref{distance_ratio_limit}.
+
+\subsection{4. Introduce joints at key MAT dists}
+At the locations where the distance measure changes.
+We discretize the distance measure field piecewise linear.
+In \cref{distance_rounding_transition} we have one piece at MAT dist $0.0$ from bar $0$ to bar $2.5$, than a piece increasing from MAT dist $0.0$ to $1.0$ from bar $2.5$ to $7.5$ etc.
+
+At the end of a marked section we round the MAT distance measure to the nearest integer and introduce a joint there and connect it to the outline using a new finger.
+At those places we round the distance measure without applying transitioning, because the end of the transition would lie beyond the marked region.
+
+\paragraph{Note}
+We could introduce bones implicitly.
+Instead of changing the straight skeleton and introducing bones,
+we can simply introduce new vertices on the polygon and generate a new straight skeleton.
+
+\textcolor{gray}{
+One could think that this means that the method for introducing joints in the original medial axis should be the same method as used for introducing joints on the newly added fingers connected to the joints introduced in the first step!
+}
+However, the method for introducing joints on the marked regions may differ from the method for introducing joints on the non-marked regions!
+
+\subsection{5. Add bones for introduced joints}
+\textcolor{gray}{
+\paragraph{Angle of fingers introduced on the skeleton}
+\Cref{finger_angles}
+Cannot be optimized.
+Always has to be orthogonal to the polygon segment.
+Otherwise the algorithm isn't stable w.r.t. extra vertices in the outline.
+}
+\begin{figure}[H]
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
+\caption{Stability against extra vertices}
+\label{finger_angles_stability}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
+\end{subfigure}
+\caption{Figner angles should always be orthogonal to the outlines}
+\label{finger_angles}
+\end{figure}
+
+\subsection{6. transform MAT distance field}
+Before generating the locations we can specify a way to space the integer values non-uniformly along a segment.
+We can choose have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.
+\hl{How do we do this exactly?}
+
+\hl{Is it possible to make this stable against small perturbations?}
+See \cref{heterogeneous_joint_generation}.
+We must first define a stable end point for where to place the upper region!
+
+\begin{figure}[H]
+\includegraphics[width=\columnwidth]{sources/method/heterogeneous_joint_generation.pdf}
+\caption{Toolpaths employing dist rounding vs without.}
+\label{heterogeneous_joint_generation}
+\end{figure}
+
+\subsection{7. Location spacing}
+\textcolor{gray}{
+One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
+We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
+However, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
+\hl{Does that mean the angle of the bones should ideally be updated?}
+}
 
@@
 \centering
-\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
-\caption{Distance measure rounding}
-\label{rounded_dist_measures}
+\includegraphics[width=.5\columnwidth]{sources/method/angular_based_spacing.pdf}
+\caption{Angular based spacing isn't feasible.
+The bottom medial axis bone has different spacing based on the two patches.
+The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
+\label{angular_based_spacing}
 \end{figure}
 
+\paragraph{Ideal parabolas}
+Subdividing bones introduced for parabolas evenly leads to even spacing along the bone,
+while a derived formula seems to produce even spacing in a different sense:
+See \cref{medial_axis_parabolas}
+
 \begin{figure}[H]
-\includegraphics[width=\columnwidth]{sources/method/rounded_vs_unrounded.pdf}
-\caption{Toolpaths employing dist rounding vs without.}
-\label{rounded_vs_unrounded}
+\begin{subfigure}{0.9\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
+\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
+\end{subfigure}
+\begin{subfigure}{0.9\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
+\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
+\label{medial_axis_parabolas_functions}
+\end{subfigure}
+\caption{The equidistant points between a vert and a line form a parabola.
+There are different methods for generating toolpaths which are in between the medial axis and the outline.
+Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
+\label{medial_axis_parabolas}
 \end{figure}
+
+\hl{But the uneven spacing figure looks like its evenly spaced in the direction orthogonal to the toolpath itself!}
+
+\subsection{8. Connect locations into toolpaths}
+\paragraph{Single bead segments}
+\Cref{single_bead_strategy}
+We round to ingteger multiples of half the nozzle width so as to allow single-bead segments.
+These could be printed from polygon and return to polygon over same segment without extruding.
+See \cref{single_bead_strategy}.
+
+How to deal with single beads connecting two polys?
+: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly
+
+How to deal with three-way intersection single beads?
+: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly
+
+\subsection{Overview}
+Below in \cref{parabola_switch_to_less_lines} you can see the different technique preliminaries thought out.
+The problem this paper is trying to solve is the large gap in M0.
+M1, M2 and M3 use vertices at specific locations and use altered distance measures for those points; these methods are not stable to adding more bones to the skeleton.
+M4 and M5 define distance measures in any location (based on \cref{distance_rounding_transition}) which makes them stable.
+M5 avoids jagged lines by only applying the MAT distance remapping up to a cutoff point discussed in \cref{sec:transitioning_cutoff}.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{sources/method/parabola_switch_to_less_lines.pdf}
+\caption{Different preliminary variants of the proposed algorithm on a parabola segment.}
+\label{parabola_switch_to_less_lines}
+\end{figure*}

### 2019-05-03 4_method.tex
make legend

@@
 \end{enumerate}
+
+For an explanation of the terms used, see \cref{legend}.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/method/legend_double_wedge_example.pdf}
+\caption{Explanation of terms.}
+\label{legend}
+\end{figure}
 
@@
 For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
-For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + \frac12 d}$.
-The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{x}{\sqrt{x^2 + d/2}}$
+For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + (\frac12 d)^2}$.
+The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{2x}{ \sqrt{4x^2 + d^2}}$
 So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
 %Wolfram Alpha:
-so $\abs x < \frac{\sqrt{d}}{\sqrt{6}} \approx 0.408 d$.
+so $\abs x < \frac{d}{2\sqrt{3}} \approx 0.289 d$.
 So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.

### 2019-05-08 4_method.tex
thought out transitions and end-of-markings

@@
 So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
-\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}
 
@@
 See \cref{single_bead_strategy_overview}.
-We use a distance of the median bead width for the transition.
-The transition needs to be robust against extra fingers in the MAT
-How do we compute the vertex location of an inset on a finger which crosses a transitional segment in the middle?
+The transition is such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
+The length of the transition along the medial axis depends on the angles involved.
+See \cref{transition_length}.
+\begin{equation}
+t = d_0 (\sin \alpha + \cos \alpha)
+\end{equation}
 
-By aligning the MAT distance with Euclidean space around the transition locations, we obtain a stable method for determining the vertex locations of insets.
+\begin{figure}[H]
+\centering
+\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
+\caption{Transition length on a line-line segment.}
+\label{transition_length}
+\end{figure}
+
+\hl{We need a formulation of the MAT distance stranform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}
+
+The transition needs to be robust against extra fingers in the MAT.
+How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
+By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
 See \cref{distance_rounding_transition}.
 The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
+\hl{Does this hold for any angled wedge? How about point-line segments or point-point segments?}
 
@@
 \subsubsection{Ends of markings}
-For vertices at the end of a sequence of marked MAT segments we need to perform rounding on the MAT distance measure, so as to avoid a gap being generated by toolapths around that vertex.
+There are multiple ways in which a sequence of bones starting from the outline polygon can be said to end.
+\begin{enumerate}
+\item The last node in the sequence is a root node
+\item The last node in the sequence is not connected to a marked segment
+\end{enumerate}
+
+The MAT distance measure of a root node of the medial axis should always be rounded;
+i.e. where the MAT distance measure is a local maximum it should be rounded.
 See bottom of \cref{rounded_vs_unrounded}.
+
+For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.
+If a transition is overlapping the end of the sequence, then either end of the transition would fall beyond the area where transitions should occur.
+How should we deal with thse?
+\begin{itemize}
+\item We need to keep the transition tick on the marked side, because we need to switch to a different number of ticks somewhere.
+Moreover, leaving out the whole transition around end-of-markings would violate the stability principle.
+\item The end-of-marking itself will retain its interpolated MAT distance as described above.
+\item The transition tick on the non-marked side of discarded.
+This means that there will also be no single bead segment leading up to the transition, which coincides with how we deal with non-marked areas.
+See \cref{single_bead_strategy}.
+\end{itemize}
+This method of dealing with end-of-markings can result in gaps slightly larger than usual.
+See \cref{change_to_marked}.
+
+\begin{figure}[H]
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/change_to_marked.pdf}
+\caption{before end of markings}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/change_to_marked_2.pdf}
+\caption{after end of markings}
+\end{subfigure}
+\caption{Transition near end of markings. The gap depends on the positioning of the middle of the transition (dotted lines) with respect to the end of the marked areas.}
+\label{change_to_marked}
+\end{figure}
 
@@
 (Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
-
-However, \hl{what if we connect two marked segments using a small segment?}
-It seems there is some distance limit based on \cref{distance_ratio_limit}.
+However, what if we connect two marked segments using a small non-marked segment?
+There is a distance limit based on \cref{distance_ratio_limit}:
+the connecting segment is always larger in Euclidean distance than the difference in MAT distance.
 
@@
 Before generating the locations we can specify a way to space the integer values non-uniformly along a segment.
-We can choose have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.
-\hl{How do we do this exactly?}
+We can choose to have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.
 
-\hl{Is it possible to make this stable against small perturbations?}
+This needs to be stable against small perturbations in the outline polygon.
 See \cref{heterogeneous_joint_generation}.
-We must first define a stable end point for where to place the upper region!
+For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
+Based on the MAT distance there we place ticks along the non-marked bones.
 
@@
 
-How to deal with single beads connecting two polys?
+We only introduce single bead segments along marked areas of the medial axis.
+We could also do it for non-marked areas, but that would result in a small single bead segment at \emph{every} corner.
+
+\hl{How to deal with single beads connecting two polys?}
 : Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly
 
-How to deal with three-way intersection single beads?
+\hl{How to deal with three-way intersection single beads?}
 : Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly

### 2019-05-08 4_method.tex
terminology considerations

@@
 \end{figure}
+
+\hl{We need consistent terminology and symbols which adhere to standards in literature.}
+The following synonym groups are used here which are not yet checked with existing literature':
+\begin{itemize}
+\item bones, medial axis segments, arms, fingers, ribs
+\item joints, ticks, medial axis vertices, locations
+\item MAT distance measure
+\end{itemize}
+
+Based on the straight skeleton naming, I would like to introduce a new consistent terminology:
+\begin{itemize}
+\item marked medial axis segment: vertebra
+\item marked medial axis: spine
+\item non-marked medial axis segment: arm
+\item any medial axis segment: bone
+\item bone introduced to the medial axis: rib
+\item medial axis vert: joint
+\item introduced medial axis vert: ligament?
+\item location of an insets along a bone: tick? locus?
+\end{itemize}
 

### 2019-05-08 4_method.tex
lil update on angle of introduced ribs

@@
 \includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
+\caption{Wrong rib angle, not orthogonal to outline}
 \end{subfigure}
-\caption{Figner angles should always be orthogonal to the outlines}
+\caption{Finger angles should always be orthogonal to the outlines}
 \label{finger_angles}
 \end{figure}
+
+\begin{wrapfigure}[5]{r}{0.2\linewidth}
+\begin{center}
+\includegraphics[width=\linewidth]{sources/method/min_angle_of_introduced_bones.pdf}
+\end{center}
+\end{wrapfigure}
+
+Because the ribs are always orthogonal to the outline segments, the angle $\alpha$ between the spine and ribs is within the range $\SI{60}{\degree} < \alpha < \SI{90}{\degree}$.
 

### 2019-05-13 4_method.tex
Enhanced ticking and better transition location

@@
 \section{Method}
-The general idea is to generate the medial axis transform and round the distance measures to integer multiples of the nominal bead width,
+The general idea is to generate the medial axis transform and round the distance measures,
+such that an exact integer beads will fit the polygon there
 so that there is never a gap region left over in the middle of the polygon.
 
-We round to ingteger multiples of half the nozzle width so as to allow single-bead segments.
-These could be printed from polygon and return to polygon over same segment without extruding
+We round to integer multiples of half the nozzle width so as to allow single-bead segments, rather than only having polygonal insets.
 
@@
 
-\subsection{Overview}
+\subsection{Method Overview}
 \begin{enumerate}
@@
 \item transform the MAT distance measures in the marked regions to enable fitting an integer multiple beads.
-		This transformation uses trasnition regions to smoothly transition from $n$ into $n+1$ insets.
+		This transformation uses transition regions to smoothly transition from $n$ into $n+1$ insets.
 \item introduce extra `joints' on the medial axis in order to discretize the transformed distance measure
@@
 
+\subsection{}
+\hl{This section needs to change and the changes will impact other sections as well.}
+We need to change the method overview.
+The transition placement needs to depend on the MAT distance transform function described below.
+
+We need a good function from a given (MAT) distance $d$ to a number of beads and their widths.
+The function needs to be able to deal with a range which is considerably shorter than $[r_-, 2r_-]$, even so short as to accomodate just $[w_*,w_*]$ only.
+The function needs to be such that we never overshoot the MAT distance, because that would affect the dimensional accuracy.
+Any distance left over which cannot be filled given the range $[r_-,r_+]$ should be placed on the inside near the MAT.
+
+\hl{we should work in terms of $w_*$ instead of $r_*$ because the beads should always have the same radius in both directions!}
+
+The function should be stable:
+\begin{itemize}
+\item between a location with MAT distance of $\frac12 nw_*$ and $\frac12 (n+1)w_*$ (for integer $n$) there is only one transition to a different number of beads
+\item the bead widths increase monotonically with the MAT distance in between transitions to a different number of beads
+\item the bead widths change gradually in between transitions to a different number of beads
+\end{itemize}
+
+The basics of the function are as such:
+\begin{itemize}
+\item we compute $m = \frac12 \lfloor 2 d / w_* \rfloor$
+\item we decide whether to use $n = m$ or $n = m+\frac12$ beads
+\item we reduce the discrepancy between $d$ and $nw_*$ by dividing as much as possible of the difference over the beads
+\end{itemize}
+
+We prefer a homogenous line width, so that tweaking the printing parameters for that line width and estimating the object properties becomes more simple.
+We can decide on a preference scheme which decides on how many bead widths to alter in a case-by-case manner:
+We could say dividing a left-over space $<r_*$ over 3 beads is better than dividing it over 2 beads without specifying an exact loss function on each possible bead size (which would require a lot of experiments to establish).
+
 \subsection{3. MAT distance transformation}
@@
 \includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
-\caption{Distance measure rounding}
+\caption{MAT distance measures at existing joints can be non-integer multiples of bead width.}
 \label{rounded_dist_measures}
@@
 See \cref{rounded_dist_measures}.
+
+In this section we describe how we transform the MAT distance values into a measure of tick quantity.
+First we divide all MAT distance measures by the preferred bead radius $r_*$ to get an initial tick quantity measure.
+In the simple case the preferred width is in the middle of the range of possible bead widths
+These initial tick quantity measures are then transformed so that they are integer values at a lot of places.
 
@@
 \begin{equation}
-t = d_0 (\sin \alpha + \cos \alpha)
+t = r_0 (\sin \alpha + \cos \alpha)
 \end{equation}
@@
 
-\hl{We need a formulation of the MAT distance stranform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}
+The position of the transition is somehwre in between whole tick values.
+The relative position in between the whole tick values relates to the relative position of the preferred line width within the range of possible widths.
+For a distance $d$ in between a location on the medial axis with a MAT distance of $nr_*$ and one with $(n+1)r_*$ the transition should be positioned around $d - d\frac{r_* - r_-}{r_+ - r_-}$ from the former location.
+See \cref{transition_location}.
+However, where should the transition be placed precisely? Should the middle of the transition be at that location, or do we again take a relative position of the transition to be at that location?
+For extremal values of $r_*$ the transition could overlap with the whole ticks if we simple place the middle of the transition at the specified location.
+We therefore place the same ratio of the transition is before the specified location.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.9\columnwidth]{sources/method/ticking.pdf}
+\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
+\caption{Mapping of different lengths to a ticking.
+Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
+\label{transition_location}
+\end{figure}
+
+\hl{We would like to have a formulation of the MAT distance stransform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}
+In terms of dMAT/dEuclidean?
 
@@
 \begin{enumerate}
-\item The last node in the sequence is a root node
+\item The last node in the sequence is a local maximum
 \item The last node in the sequence is not connected to a marked segment
@@
 
-The MAT distance measure of a root node of the medial axis should always be rounded;
-i.e. where the MAT distance measure is a local maximum it should be rounded.
+The tick quantity measure should be rounded
+where the MAT distance measure is a local maximum: when all directly connected nodes have a lower MAT distance measure.
 See bottom of \cref{rounded_vs_unrounded}.
@@
 
-\subsection{5. Add bones for introduced joints}
+\subsection{5. Add ribs for introduced joints}
 \textcolor{gray}{

### 2019-05-13 6_validation.tex
add experimentation sections

\section{Validation}
Render toolpaths and calculate percentage of covered volume.

Visualize thickness of beads as color.

### 2019-05-13 4_method.tex
better related work and related literature terminology

@@
 
+\subsection{Terminology}
 For an explanation of the terms used, see \cref{legend}.
@@
 \end{itemize}
+
+\subsubsection{In related literature}
+
+``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.
+Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.''
+\cite{lee1982medial}
+
+\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
+\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, thethe feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
+
+\cite{kao1998optimal}
+\begin{figure}[H]
+\centering
+\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
+\caption{MAT explanation by Kao et al.}
+\end{figure}
 

### 2019-05-19 2_related_work.tex
better related work and related literature terminology
lil comments

@@
 \Cref{moessen}
+Problem: small grey areas which are too small for the second wall lines.
 
@@
 
-Using variable width lines to fit a precise amount of lines using the MAT. \cite{Ding2016a}
+Using variable width lines to fit a precise amount of lines using the MAT.
+\cite{Ding2016a} apply the method from \cite{kao1998optimal}.
 \Cref{ding}
@@
 \begin{figure}
+\centering
 \includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
-\caption{asfd}
+\includegraphics[width=.7\columnwidth]{sources/related_work/kao.jpg}
+\caption{Path planning strategies proposed by Kao (bottom) and employed in FDM by Ding et al (top).}
 \label{ding}

### 2019-05-19 4_method.tex
big refactor of method

@@
 \includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
-\caption{Travel order}
+\caption{Travel order}s
 \end{subfigure}
@@
 \item find places `of high curvature' in the medial axis and mark those regions
-\item transform the MAT distance measures in the marked regions to enable fitting an integer multiple beads.
+\item transform the $R$ distance measures in the marked regions to enable fitting an integer multiple beads.
 		This transformation uses transition regions to smoothly transition from $n$ into $n+1$ insets.
@@
 \item connect these new joints to the outline with new `bones' (In the standard MAT manner)
-\item (optional) transform MAT distance fields along all bones, while keeping the endpoint dist measures fixed.
+\item (optional) transform $R$ fields along all bones, while keeping the endpoint bead measures fixed.
 (Deviate from evenly distributed linear space in order to have outer outlines closer to the nominal bead width and only change the innermost couple of toolpaths.)
@@
 \end{enumerate}
+
+\hl{Idea: generate only outer 3 walls, except in marked regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.}
+\Cref{wedge_and_infill}
+
+\hl{Filter beading number in order to prevent regions with a lot of back and forth transitions.}
 
@@
 
+The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
+A novel way of conceptualizing the medial axis is as an efficient data structure to store a distance field.
+The medial axis is the set of all points where the derivative of the distance field is discontinuous.
+
+By introducing extra bones to the MAT, we can approximate insets from the medial axis by connecting points on the segments of the MAT using linear segments.
+
+We introduce the Grounded Medial Axis Transform.
+We dscretize the segments of the MAT where $R$ changes non-linearly (point-line parabolas and point-point bisectors) into short segments
+and connect the introduced vertices to the two closest locations on the outline.
+This allows us to directly generate accurate insets from the GMAT.
+
+Note that by altering the outline by an infinitesimal change the straight skeleton of the polygon can be made to coincide with the GMAT.
+
+We call any graph a GMAT if it contains the MAT and its segments are within the outline and the nodes have an accurate distance measure $R$ and the distance $R$ changes approximately linearly between two connected nodes.
+The GMAT allows for extra segments.
+
+We can generate an inset with rounded corners at distance $d$ by interpolating the $R$ at GMAT nodes and connecting the interpolated points.
+Similarly one could compute an unmitered inset by connecting interpolated points along the straight skeleton.
+
 \paragraph{Medial axis rather than Straight Skeleton}
@@
 
-Medial axis is stable against small perturbations in the input polygon!
+\st{Medial axis is stable against small perturbations in the input polygon!}
 Concave corners are handled irrespective of how many vertices are in a corner.
+\hl{(The medial axis is not stable in that whole new bones can be introduced just by adding a small bump in the outline.)}
 
@@
 
-\subsection{2. High curvature marking}
-\label{sec:transitioning_cutoff}
+\subsection{2. Significance measure}\label{sec:significance_measure}
 \Cref{rounded_dist_measures}
 We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
-We generalize this concept of angle to parabola sections and to MAT sections generated by two outline verts.
+Equivalently we can look at the angle $\alpha$ between a skeletal point and the two closest points on the outline.
+(Same definition as \cite{attali1996modeling}.)
+A computationally efficient way to compute the same can be obtained by looking at the ratio between $R$ and Euclidean distance.
 
-\paragraph{line-line-segments}
+\paragraph{line-line bones}
 When the angle between two outline segments is small, the naive method will produce long triangular gaps.
-We can measure the angle between two outline segments which generate a MAT segment by looking at the angle where the lines going through those segments (would) meet.
 Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
-if the Euclidean distance is larger than twice the distance measure difference, the angle between the segments is less than {\SI{60}{\degree}}.
+if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.
 
@@
 
-\paragraph{line-point segments}
+\paragraph{line-point bones}
+\hl{reformulate in terms of $\alpha$}
 For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
@@
 
-\paragraph{point-point segments}
-For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
-For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + (\frac12 d)^2}$.
-The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{2x}{ \sqrt{4x^2 + d^2}}$
-So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
-%Wolfram Alpha:
-so $\abs x < \frac{d}{2\sqrt{3}} \approx 0.289 d$.
-So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
+\paragraph{point-point bones}
+For a segment gerenated by points $(0,0)$ and $(0,d)$, the angle $\alpha > \SI{120}{\degree}$ when $\abs(x) < \frac12 d \tan \SI{30}{\degree} $,
+so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.
 
-\subsection{}
+\begin{figure}[H]
+\centering
+\includegraphics[width=.3\columnwidth]{sources/method/end_of_markings_point_point.pdf}
+\caption{End-of-markings for the segment(s) generated by two outline verts.}
+\label{end_of_markings_point_point}
+\end{figure}
+
+\subsection{Beading strategy}
 \hl{This section needs to change and the changes will impact other sections as well.}
@@
 
-We need a good function from a given (MAT) distance $d$ to a number of beads and their widths.
-The function needs to be able to deal with a range which is considerably shorter than $[r_-, 2r_-]$, even so short as to accomodate just $[w_*,w_*]$ only.
-The function needs to be such that we never overshoot the MAT distance, because that would affect the dimensional accuracy.
-Any distance left over which cannot be filled given the range $[r_-,r_+]$ should be placed on the inside near the MAT.
+We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
+These widths depend on the following parameters:
+\begin{description}
+\item[$\wmin$] the minimum possible bead width
+\item[$\wmax$] the maximum possible bead width
+\item[$\wout$] the preferred bead width of the outer inset
+\item[$\win$] the preferred bead width of the other insets
+\end{description}
 
-\hl{we should work in terms of $w_*$ instead of $r_*$ because the beads should always have the same radius in both directions!}
+The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
+The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
+Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
 
-The function should be stable:
+We define $W(d)$ as a sequence of bead widths.
+The length of that sequence is $b(d)$.
+For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
+The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
+
+The function $b$ should adhere to several criteria:
 \begin{itemize}
-\item between a location with MAT distance of $\frac12 nw_*$ and $\frac12 (n+1)w_*$ (for integer $n$) there is only one transition to a different number of beads
-\item the bead widths increase monotonically with the MAT distance in between transitions to a different number of beads
-\item the bead widths change gradually in between transitions to a different number of beads
+\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
+\item $b$ is monotonic
+%the item below follows from the two above
+% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
+\item $ 0 \leq b(d) \leq d / w_\text{min} $
+\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
 \end{itemize}
 
-The basics of the function are as such:
+For our method we also require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
+
+For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
 \begin{itemize}
-\item we compute $m = \frac12 \lfloor 2 d / w_* \rfloor$
-\item we decide whether to use $n = m$ or $n = m+\frac12$ beads
-\item we reduce the discrepancy between $d$ and $nw_*$ by dividing as much as possible of the difference over the beads
+\item Minimize unfilled area
+\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
+\item Have the rest of the $W_n$ the same width
+\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
+\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis
 \end{itemize}
 
-We prefer a homogenous line width, so that tweaking the printing parameters for that line width and estimating the object properties becomes more simple.
-We can decide on a preference scheme which decides on how many bead widths to alter in a case-by-case manner:
-We could say dividing a left-over space $<r_*$ over 3 beads is better than dividing it over 2 beads without specifying an exact loss function on each possible bead size (which would require a lot of experiments to establish).
+\iffalse
+\begin{align}
+W(d)_1 = 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   \wout & \text{if } d \geq \wout + \wmin \\
+   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
+  \end{cases}
+\end{align}
+\fi
 
-\subsection{3. MAT distance transformation}
+%\subsubsection{Optimal beading strategy}
+%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
+
+\begin{align}
+L(w_1) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
+   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
+  \end{cases}
+  \\
+L(w_n) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
+   (\win - w) / (\win - \wmin)       & \text{otherwise}
+  \end{cases}
+\\
+L(W(d)) &= \sum_{n=1}^{n=\lceil f(d) \rceil} L( W(d)_n )
+\end{align}
+
+Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
+An example is given in \cref{transition_location}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
+\includegraphics[width=.25\textwidth]{sources/method/transition_location_precise.pdf}
+\caption{Mapping of different lengths to a ticking.
+Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
+\label{transition_location}
+\end{figure*}
+
+\subsection{Transitioning}
 
@@
 
-In this section we describe how we transform the MAT distance values into a measure of tick quantity.
-First we divide all MAT distance measures by the preferred bead radius $r_*$ to get an initial tick quantity measure.
-In the simple case the preferred width is in the middle of the range of possible bead widths
-These initial tick quantity measures are then transformed so that they are integer values at a lot of places.
+In order to apply the beading strategy to the MAT, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
+The transition will be placed so as to overlap the locations of $b^{-1}(n)$.
+We assign each node $v$ of the medial axis a value $b^*$ which is initially based on $b(R(v))$, but it is modified in order to account for transitioning zones.
+On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
+For all locations on the MAT in between we linearly interpolate the $b^*$ values, so that we can later interpolate the bead widths $W$ linearly as well.
 
@@
 See \cref{single_bead_strategy_overview}.
-The transition is such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
+The transition will be such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
 The length of the transition along the medial axis depends on the angles involved.
@@
 We therefore place the same ratio of the transition is before the specified location.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.9\columnwidth]{sources/method/ticking.pdf}
-\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
-\caption{Mapping of different lengths to a ticking.
-Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
-\label{transition_location}
-\end{figure}
 
@@
 
+Where to put the middle of the toolpath, based on the middle of the line, the line width and the processing order?
+
+Idea: generate only outer 3 walls, except in marked regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.
+Don't generate transitions when $R > 5\win$ or something?
+Only do this in skin regions?
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
+\caption{Use single and double wall lines in regions where the infill would be too thin.}
+\label{wedge_and_infill}
+\end{figure}
+
 \subsection{Overview}
@@
 M4 and M5 define distance measures in any location (based on \cref{distance_rounding_transition}) which makes them stable.
-M5 avoids jagged lines by only applying the MAT distance remapping up to a cutoff point discussed in \cref{sec:transitioning_cutoff}.
+M5 avoids jagged lines by only applying the MAT distance remapping up to a cutoff point discussed in \cref{sec:significance_measure}.
 

### 2019-05-20 10_applications.tex
description of 2D lithophanes

@@
 \section{Applications}
+
+\subsection{2D Lithophane}
+A user sets the minimum thickness  $n$ and maximum thickness $m$.
+Based on the material parameter transmittance $t$ as percentage of light after 1mm (more) thickness,
+we calculate the thickness $h$ at each location based on the luminance $I$ there:
+\begin{align}
+p &= \frac{1}{\log_2 t}
+\\
+b &= 2^{(m-n)/p}
+\\
+h &= n + p \log_2 ( b + (1-b) I )
+\end{align}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.75\columnwidth]{sources/litho/luminance_to_thickness.pdf}
+\caption{Mapping luminance to height for 2D lithophanes.}
+\label{luminance_to_thickness}
+\end{figure}
+
 \subsection{3D Lithophane}

### 2019-05-22 4_method.tex
lil
rewrite gMAT section

@@
 
+\old{
 \subsection{Method Overview}
@@
 \end{enumerate}
+}
 
@@
 \item medial axis vert: joint
-\item introduced medial axis vert: ligament?
 \item location of an insets along a bone: tick? locus?
@@
 
-The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
-A novel way of conceptualizing the medial axis is as an efficient data structure to store a distance field.
-The medial axis is the set of all points where the derivative of the distance field is discontinuous.
-
-By introducing extra bones to the MAT, we can approximate insets from the medial axis by connecting points on the segments of the MAT using linear segments.
-
-We introduce the Grounded Medial Axis Transform.
-We dscretize the segments of the MAT where $R$ changes non-linearly (point-line parabolas and point-point bisectors) into short segments
-and connect the introduced vertices to the two closest locations on the outline.
-This allows us to directly generate accurate insets from the GMAT.
-
-Note that by altering the outline by an infinitesimal change the straight skeleton of the polygon can be made to coincide with the GMAT.
-
-We call any graph a GMAT if it contains the MAT and its segments are within the outline and the nodes have an accurate distance measure $R$ and the distance $R$ changes approximately linearly between two connected nodes.
-The GMAT allows for extra segments.
-
-We can generate an inset with rounded corners at distance $d$ by interpolating the $R$ at GMAT nodes and connecting the interpolated points.
-Similarly one could compute an unmitered inset by connecting interpolated points along the straight skeleton.
-
-\paragraph{Medial axis rather than Straight Skeleton}
+\subsubsection{Medial axis rather than Straight Skeleton}
 See \cref{medial_axis_vs_straight_skeleton}.
@@
 this does introduce a lot of extra bones, though.
+
+The bones of the medial axis which are not directly connected to the outline segment the area in as much sub-areas as the part has polygons.
+
+\begin{figure}
+\begin{subfigure}{0.3\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
+\caption{MAT}
+\end{subfigure}
+\begin{subfigure}{0.3\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
+\caption{gMAT}
+\end{subfigure}
+\begin{subfigure}{0.3\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
+\caption{Quads in gMAT}
+\end{subfigure}
+\caption{Grounded medial axis transform.
+Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple.
+The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
+\label{gmat}
+\end{figure}
+
+\subsubsection{grounded Medial Axis Transform}
+See \cref{gmat}.
+The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
+A novel way of conceptualizing the medial axis is as a data structure which encodes the distance field.
+The medial axis is the set of all points where the derivative of the distance field is discontinuous.
+
+The medial axis transform (MAT) is the combination of the medial axis with at each node the distance values $R$.
+
+We propose a modified MAT: the grounded medial axis transform: gMAT.
+The distance field defined by the gMAT approximates the distance field of the MAT using \uwave{piece-wise linear quads}.
+The gMAT is the set of all points where the derivative of the distance field is not constant.
+
+Each node in the gMAT is connected to the outline via a \emph{single} bone.
+This condition is violated on a MAT where there are concave outline verts.
+The gMAT segments the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
+For concave verts the outline segments is missing and the quad becomes a triangle;
+likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
+
+For a normal MAT it is already the case that
+for a bone segment $v_0 v_1$ generated by two outline segments $p_0 p_1$ and $p_2 p_3$,
+the distance on locations along $v_0 v_1$ can be interpolated linearly between $R(v_0)$ and $R(v_1)$.
+The distance field between $v_0 v_1$ and $p_0 p_1$ can be constructed linearly as well.
+
+For a MAT the same does not hold for parabolic bones or bones generated by two concave outline verts.
+We therefore discretize these segments and connect the introduced nodes to the oulines using new ribs.
+The resulting quads encode the original distance field in a piece-wise fashion using linear gradients.
+
+The MAT is a subset of the Voronoi diagram inside the part, which in turn is a subset of the gMAT.
+See \cref{voronoi_MAT}.
+
+\begin{figure}
+\centering
+\includegraphics[width=.8\columnwidth]{sources/method/voronoi_MAT.png}
+\caption{From \citeauthor{lee1982medial} \cite{lee1982medial}}
+\label{voronoi_MAT}
+\end{figure}
 

### 2019-05-22 4_method.tex
explain end-of-markings better

@@
 
-\subsection{1. Compute MAT}
+\subsection{Compute MAT}
 
@@
 
-\subsection{2. Significance measure}\label{sec:significance_measure}
+\subsection{Significance measure}\label{sec:significance_measure}
 \Cref{rounded_dist_measures}
 We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
-Equivalently we can look at the angle $\alpha$ between a skeletal point and the two closest points on the outline.
+Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
 (Same definition as \cite{attali1996modeling}.)
-A computationally efficient way to compute the same can be obtained by looking at the ratio between $R$ and Euclidean distance.
 
@@
 When the angle between two outline segments is small, the naive method will produce long triangular gaps.
+A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
 Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
@@
 
-\paragraph{line-point bones}
-\hl{reformulate in terms of $\alpha$}
+\paragraph{line-point segments}
 For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
-The angle between the outline segments is twice the angle between the MAT segment and an outline segment.
-The angle between the MAT parabola and the x-axis is the inverse tangent of the derivative of this formula: $\tan^{-1} \left( \abs x / d \right)$.
-The angle is less than \SI{60}{\degree} when 
-$\tan^{-1} \left( \abs x / d \right) < \SI{30}{\degree}$ 
-i.e. when $\abs x/d < 1 / \sqrt{3}$
-i.e. when $\abs x < d / \sqrt{3}$.
-So we mark the part of the parabola as to-be-transformed for which $x \in [-d / \sqrt{3}, d / \sqrt{3}]$.
+If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
+i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
+i.e. when $\abs x/d < 1 / \sqrt{3}$,
+i.e. when $\abs x < d \sqrt{3} / 3$.
+So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
+\caption{End-of-markings for a parabolic spine segment.}
+\label{end_of_markings_point_point}
+\end{figure}
 

### 2019-05-22 4_method.tex
more math

@@
 \subsection{Beading strategy}
-\hl{This section needs to change and the changes will impact other sections as well.}
-We need to change the method overview.
-The transition placement needs to depend on the MAT distance transform function described below.
+The next step is to determine how we will fill a given distance between the outline and a significant/marked MAT segment with a whole number of beads.
+We want to fit an exact whole number of beads in order to prevent a gap being generated.
 
@@
 \item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
-\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis
+\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
+\hl{Perhaps we should disallow this because that would require a different transition length}
 \end{itemize}
@@
 \\
-L(W(d)) &= \sum_{n=1}^{n=\lceil f(d) \rceil} L( W(d)_n )
+L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
 \end{align}
 
+(Singular beads are counted only half.)
 Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
@@
 \includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
-\includegraphics[width=.25\textwidth]{sources/method/transition_location_precise.pdf}
 \caption{Mapping of different lengths to a ticking.
@@
 \end{figure*}
+
+We introduce a function which produces the $d$ at which all widths are prefered: 
+\begin{align}
+p(n) =
+  \begin{cases} 
+   \frac12 \wout & \text{if } n = \frac12 \\
+    \wout + (n - 1) \win       & \text{otherwise}
+  \end{cases}
+\end{align}
+We call a distance $d$ `prefered' when $d = p(b(d))$
+
+\subsubsection{MAT distance transform}
+In order to apply the beading strategy to the MAT
+we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
+
+\hl{How should we define $B^*$? Currently it is always the rounded measure, but it needs to be unrounded in non-marked areas and it needs to support fractional numbers around transitions!}
+
+The bead quantity measure $B^*$ measure should be rounded
+where the MAT distance measure $R$ is a local maximum: when all directly connected nodes have a lower MAT distance measure.
+See bottom of \cref{rounded_vs_unrounded}.
 

### 2019-05-22 4_method.tex
enhance transitioning

@@
 
-In order to apply the beading strategy to the MAT, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
+In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
 The transition will be placed so as to overlap the locations of $b^{-1}(n)$.
-We assign each node $v$ of the medial axis a value $b^*$ which is initially based on $b(R(v))$, but it is modified in order to account for transitioning zones.
+
 On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
@@
 
-In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n-1$ beads; this transition requires a distance.
+In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n+\nicefrac12$ beads; this transition requires a distance.
 See \cref{single_bead_strategy_overview}.
@@
 
-The position of the transition is somehwre in between whole tick values.
-The relative position in between the whole tick values relates to the relative position of the preferred line width within the range of possible widths.
-For a distance $d$ in between a location on the medial axis with a MAT distance of $nr_*$ and one with $(n+1)r_*$ the transition should be positioned around $d - d\frac{r_* - r_-}{r_+ - r_-}$ from the former location.
-See \cref{transition_location}.
-However, where should the transition be placed precisely? Should the middle of the transition be at that location, or do we again take a relative position of the transition to be at that location?
-For extremal values of $r_*$ the transition could overlap with the whole ticks if we simple place the middle of the transition at the specified location.
-We therefore place the same ratio of the transition is before the specified location.
+The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
+However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
+For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
+$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$
 
-\hl{We would like to have a formulation of the MAT distance stransform which defines the MAT distance for any position even if it's not possible to define where the middle of the transition would end up.}
-In terms of dMAT/dEuclidean?
+\begin{figure}[H]
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
+\caption{Transition placement.
+The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length.
+\hl{outdated functions and variables!}}
+\label{transition_length}
+\end{figure}
+
+\hl{How to deal with non-marked regions shorter than the transition length?}
 
@@
 The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
-\hl{Does this hold for any angled wedge? How about point-line segments or point-point segments?}
+\hl{What does it look like for point-line segments or point-point segments?}
 
@@
 \subsubsection{Ends of markings}
-There are multiple ways in which a sequence of bones starting from the outline polygon can be said to end.
-\begin{enumerate}
-\item The last node in the sequence is a local maximum
-\item The last node in the sequence is not connected to a marked segment
-\end{enumerate}
-
-The tick quantity measure should be rounded
-where the MAT distance measure is a local maximum: when all directly connected nodes have a lower MAT distance measure.
-See bottom of \cref{rounded_vs_unrounded}.
-
 For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.

### 2019-05-22 4_method.tex
refactor old sections

@@
 
-\subsection{4. Introduce joints at key MAT dists}
-At the locations where the distance measure changes.
+\subsection{Add ribs for introduced joints}
+
+\subsubsection{Introduce joints at transition ends}
+At the locations $v$ of prefered width, i.e. when $R(v) = p(b(R(v)))$.
 We discretize the distance measure field piecewise linear.
@@
 
-\textcolor{gray}{
+\old{
 One could think that this means that the method for introducing joints in the original medial axis should be the same method as used for introducing joints on the newly added fingers connected to the joints introduced in the first step!
@@
 
-\subsection{5. Add ribs for introduced joints}
-\textcolor{gray}{
+\subsubsection{Connect introduced joints to outline}
+\old{
 \paragraph{Angle of fingers introduced on the skeleton}
@@
 
-\subsection{6. transform MAT distance field}
-Before generating the locations we can specify a way to space the integer values non-uniformly along a segment.
-We can choose to have bead widths closer to the nominal bead width near lower MAT dists and do the uniform layout only in the upper region of the segment.
+\subsection{Location spacing}
+\hl{Change terminology: location $\to$ junction?}
+
+Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be.
+For marked regions / significant regions we have already inroduced joints around the transitions which serve as those locations.
+For non-marked regions / unsignificant regions we can simply apply the beading strategy in order to find the toolpath verts.
 
@@
 
-\subsection{7. Location spacing}
-\textcolor{gray}{
+\subsection{Alternative spacing}
+Applying a beading strategy to the skeleton might not be trivial.
+The trivial approach explained above introduces slight deviations from the beading strategy at intermediate locations in a quad.
+When the widths are always the same this doesn't happen, but with widths changing throughout a quad this can pose a slight problem.
+
+In the end this problem comes down to the fact that the medial axis is the location of quench sites when performing homogeneous insets.
+Changing the bones for the chosen beading strategy is impossible, because the new skeleton would then induce a new beading strategy.
+While this process could converge, it would spend too much computation time for only a small benefit.
+
+In the following we assume an even spacing, i.e. $\win = \wout$.
+
 One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
@@
 \hl{Does that mean the angle of the bones should ideally be updated?}
-}
 
@@
 
-\subsection{8. Connect locations into toolpaths}
+\subsection{Toolpath extraction}
+\paragraph{Processing order}
+\hl{How do we process the graph?}
+\begin{itemize}
+\item walk along polygons and for each vert walk down the graph up to the desired depth
+\item process nodes in depth first order
+\item process nodes in $R$ sorted order
+\end{itemize}
+
+We would require either a mapping from locations or bones to toolpath segments, which we can use to efficiently connect paths together.
+
+Or we process all segments in order of the polygon, but then we need to track which polygons have been processed.
+
+If we don't process both sides of the gMAT at the same time then we should record certain calculations such as the transition locations and maye also the parabola sample points.
+
+\hl{Is there or should there be a specific ordering on the bones connected to a joint?}
+A joint can have multiple parents.
+We could order the bones cyclically, irrespective of whether they are going `up' or `down'.
+
 \paragraph{Single bead segments}

### 2019-05-22 4_method.tex
show new instability issue

@@
 For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
-Based on the MAT distance there we place ticks along the non-marked bones.
+Based on the MAT distance $R$ there we place ticks along the non-marked bones following the beading strategy.
 
-\begin{figure}[H]
+\begin{figure}
 \includegraphics[width=\columnwidth]{sources/method/heterogeneous_joint_generation.pdf}
@@
 
-In the following we assume an even spacing, i.e. $\win = \wout$.
+(In this subsection we assume an even spacing beading strategy, i.e. $\win = \wout$.)
 
+A related problem is that that applying the beading strategy to highly skewed quads would not be stable to the addition of extra bones.
+See \cref{quad_instability}.
+\hl{We should introduce bones in such a case!}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/quad_instability.pdf}
+\caption{The addition of the extra bone (orange) causes a significant change from the dark red path to the green path.}
+\label{quad_instability}
+\end{figure}
+
+See \cref{angular_based_spacing}.
 One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
@@
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{subfigure}{0.9\columnwidth}

### 2019-05-22 4_method.tex
move beading strategy to before MAT section

@@
 \end{itemize}
+
+\subsection{Beading strategy}
+First we determine how we should fill a 	polygon with constant width with a number of beads.
+We want to fit an exact whole number of beads in order to prevent a gap being generated.
+We consider only half of the polygon, because our beading strategy should be symmetrical.
+
+We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
+These widths depend on the following parameters:
+\begin{description}
+\item[$\wmin$] the minimum possible bead width
+\item[$\wmax$] the maximum possible bead width
+\item[$\wout$] the preferred bead width of the outer inset
+\item[$\win$] the preferred bead width of the other insets
+\end{description}
+
+The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
+The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
+Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
+
+We define $W(d)$ as a sequence of bead widths.
+The length of that sequence is $b(d)$.
+For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
+The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
+
+The function $b$ should adhere to several criteria:
+\begin{itemize}
+\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
+\item $b$ is monotonic
+%the item below follows from the two above
+% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
+\item $ 0 \leq b(d) \leq d / w_\text{min} $
+\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\end{itemize}
+
+For our method we also require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
+
+For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
+\begin{itemize}
+\item Minimize unfilled area
+\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
+\item Have the rest of the $W_n$ the same width
+\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
+\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
+\hl{Perhaps we should disallow this because that would require a different transition length}
+\end{itemize}
+
+\iffalse
+\begin{align}
+W(d)_1 = 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   \wout & \text{if } d \geq \wout + \wmin \\
+   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
+  \end{cases}
+\end{align}
+\fi
+
+%\subsubsection{Optimal beading strategy}
+%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
+
+\begin{align}
+L(w_1) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
+   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
+  \end{cases}
+  \\
+L(w_n) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
+   (\win - w) / (\win - \wmin)       & \text{otherwise}
+  \end{cases}
+\\
+L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
+\end{align}
+
+(Singular beads are counted only half.)
+Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
+An example is given in \cref{transition_location}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
+\caption{Mapping of different lengths to a ticking.
+Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
+\label{transition_location}
+\end{figure*}
+
+We introduce a function which produces the $d$ at which all widths are prefered: 
+\begin{align}
+p(n) =
+  \begin{cases} 
+   \frac12 \wout & \text{if } n = \frac12 \\
+    \wout + (n - 1) \win       & \text{otherwise}
+  \end{cases}
+\end{align}
+We call a distance $d$ `prefered' when $d = p(b(d))$
+
+\subsection{Medial Axis}
+In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
+There are several possible skeletonal structures we could consider.
 
@@
 \end{figure}
-
-\subsection{Beading strategy}
-The next step is to determine how we will fill a given distance between the outline and a significant/marked MAT segment with a whole number of beads.
-We want to fit an exact whole number of beads in order to prevent a gap being generated.
-
-We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
-These widths depend on the following parameters:
-\begin{description}
-\item[$\wmin$] the minimum possible bead width
-\item[$\wmax$] the maximum possible bead width
-\item[$\wout$] the preferred bead width of the outer inset
-\item[$\win$] the preferred bead width of the other insets
-\end{description}
-
-The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
-The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
-Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
-
-We define $W(d)$ as a sequence of bead widths.
-The length of that sequence is $b(d)$.
-For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
-The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
-
-The function $b$ should adhere to several criteria:
-\begin{itemize}
-\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
-\item $b$ is monotonic
-%the item below follows from the two above
-% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
-\item $ 0 \leq b(d) \leq d / w_\text{min} $
-\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\end{itemize}
-
-For our method we also require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
-
-For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
-\begin{itemize}
-\item Minimize unfilled area
-\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
-\item Have the rest of the $W_n$ the same width
-\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
-\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
-\hl{Perhaps we should disallow this because that would require a different transition length}
-\end{itemize}
-
-\iffalse
-\begin{align}
-W(d)_1 = 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   \wout & \text{if } d \geq \wout + \wmin \\
-   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
-  \end{cases}
-\end{align}
-\fi
-
-%\subsubsection{Optimal beading strategy}
-%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
-
-\begin{align}
-L(w_1) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
-   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
-  \end{cases}
-  \\
-L(w_n) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
-   (\win - w) / (\win - \wmin)       & \text{otherwise}
-  \end{cases}
-\\
-L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
-\end{align}
-
-(Singular beads are counted only half.)
-Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
-An example is given in \cref{transition_location}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
-\caption{Mapping of different lengths to a ticking.
-Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
-\label{transition_location}
-\end{figure*}
-
-We introduce a function which produces the $d$ at which all widths are prefered: 
-\begin{align}
-p(n) =
-  \begin{cases} 
-   \frac12 \wout & \text{if } n = \frac12 \\
-    \wout + (n - 1) \win       & \text{otherwise}
-  \end{cases}
-\end{align}
-We call a distance $d$ `prefered' when $d = p(b(d))$
 

### 2019-05-22 4_method.tex
redo method overview

@@
 
-\old{
 \subsection{Method Overview}
 \begin{enumerate}
-\item compute medial axis transform (MAT)
-\item find places `of high curvature' in the medial axis and mark those regions
-\item transform the $R$ distance measures in the marked regions to enable fitting an integer multiple beads.
-		This transformation uses transition regions to smoothly transition from $n$ into $n+1$ insets.
-\item introduce extra `joints' on the medial axis in order to discretize the transformed distance measure
-\item connect these new joints to the outline with new `bones' (In the standard MAT manner)
-\item (optional) transform $R$ fields along all bones, while keeping the endpoint bead measures fixed.
-(Deviate from evenly distributed linear space in order to have outer outlines closer to the nominal bead width and only change the innermost couple of toolpaths.)
-\item define locations everywhere on the bones of the medial axis at integer MAT distances
-\item connect all locations with odd distance measure to form the inset toolpaths
-\item connect all even locations to form the extent of the toolpaths, which defines the variable width of the segments.
+\item Determine the beading strategy: the optimal number of beads and their widths in order to cover a given distance with those beads.
+\item Compute the medial axis transform (MAT)
+\item Discretize the MAT and add extra segments such that the gMAT divides a polygon in quads
+\item Mark significant high curvature portions of the gMAT
+\item Introduce bones on marked regions where we transition to a different number of beads
+\item Add ticks on non-marked regions according to the beading strategy.
+\item Connect ticks and transition nodes into toolpaths.
 \end{enumerate}
-}
 
@@
 \end{figure}
-
-\subsection{Compute MAT}
 
@@
 
-\subsection{Add ribs for introduced joints}
-
 \subsubsection{Introduce joints at transition ends}
@@
 
-\subsection{Location spacing}
+\subsection{Tick placement}
 \hl{Change terminology: location $\to$ junction?}
@@
 
-\subsection{Alternative spacing}
+\subsection{Spacing problems}
 Applying a beading strategy to the skeleton might not be trivial.

### 2019-07-08 4_method.tex
extended gMAT figure ewith voronoi
fix figure which was initialized wrongly
MAT intro

@@
 
-\subsection{Medial Axis}
+\subsection{Skeletonization}
 In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
@@
 
-\subsubsection{In related literature}
+\subsubsection{Background}
+The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
+See \cref{MAT_explanation}.
 
@@
 
+The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
+The MAT can unambiguously recreate the exact input shape. \todo{[citation needed]}
+
 \cite{Moesen2011} provides a thorough overview of all MAT algorithms.
-\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, thethe feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
+\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
 
-\cite{kao1998optimal}
-\begin{figure}[H]
+The medial axis of a polygonal shape is a subset of the voronoi diagram generated on the line segments of the shape. \todo{[citation needed]}
+
+\begin{figure}
 \centering
-\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
-\caption{MAT explanation by Kao et al.}
+\includegraphics[width=.9\columnwidth]{sources/intro/medial_axis_Kao.png}
+\caption{MAT explanation by \citeauthor{kao1998optimal}}
+\label{MAT_explanation}
 \end{figure}
@@
 \begin{figure}
-\begin{subfigure}{0.3\columnwidth}
+\begin{subfigure}{0.24\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
+\begin{subfigure}{0.24\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
+\caption{Voronoi}
+\end{subfigure}
+\begin{subfigure}{0.24\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
+\begin{subfigure}{0.24\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
-\caption{Quads in gMAT}
+\caption{Quads}
 \end{subfigure}

### 2019-07-08 4_method.tex
rename sections;  section -> subsection etc.

@@
 
-\subsection{Significance measure}\label{sec:significance_measure}
+\subsection{Beading}
+We assign a beading to each significant node (and each local optimum).
+
+\subsubsection{Significance measure}\label{sec:significance_measure}
 \Cref{rounded_dist_measures}
@@
 (Same definition as \cite{attali1996modeling}.)
+
+Contrary to common techniques we will \emph{keep} the insignificant regions of the skeleton.
 
@@
 
-\subsubsection{MAT distance transform}
+\paragraph{MAT distance transform}
 In order to apply the beading strategy to the MAT
@@
 
-\subsection{Transitioning}
+\subsubsection{Transitioning}
 
@@
 
-\subsection{Tick placement}
+\subsection{Toolpath extraction}
+
+\subsubsection{Tick placement}
 \hl{Change terminology: location $\to$ junction?}
@@
 
-\subsection{Spacing problems}
+\subsubsection{Spacing problems}
 Applying a beading strategy to the skeleton might not be trivial.
@@
 
-\subsection{Toolpath extraction}
-\paragraph{Processing order}
+\subsubsection{Processing order}
 \hl{How do we process the graph?}

### 2019-07-08 4_method.tex
remove straight skeleton section

@@
 \end{figure}
-
-\subsubsection{Medial axis rather than Straight Skeleton}
-See \cref{medial_axis_vs_straight_skeleton}.
-Medial axis handles concave corners differently:
-instead of generating the bisector, it will generate a parabolic arc in between the vertex and another line segment of the outline polygon.
-
-\st{Medial axis is stable against small perturbations in the input polygon!}
-Concave corners are handled irrespective of how many vertices are in a corner.
-\hl{(The medial axis is not stable in that whole new bones can be introduced just by adding a small bump in the outline.)}
-
-$\to$ approximate parabolas for simpler processing!
-A straight skeleton can be made to coincide with the medial axis by changing concave corners into an infinitesimal circle arc;
-this does introduce a lot of extra bones, though.
-
-The bones of the medial axis which are not directly connected to the outline segment the area in as much sub-areas as the part has polygons.
 

### 2019-07-08 4_method.tex
rewrite grounded medial axis > voronoi quadrangualtion

@@
 
-The medial axis of a polygonal shape is a subset of the voronoi diagram generated on the line segments of the shape. \todo{[citation needed]}
-
 \begin{figure}
@@
 
-\subsubsection{grounded Medial Axis Transform}
-See \cref{gmat}.
-The medial axis is commonly defined either as the set of points with more than one closest point on the boundary or as the set of quench sites of a fire started at the outline polygon growing inward.
-A novel way of conceptualizing the medial axis is as a data structure which encodes the distance field.
-The medial axis is the set of all points where the derivative of the distance field is discontinuous.
+\subsubsection{Voronoi Quadrangulation}
+The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}
+First we throw away all locations in the Voronoi diagram which fall outside the boundary shape.
+We can then obtain the medial axis by further reducing the Voronoi bones connected to a concave corner in the boundary shape.
 
-The medial axis transform (MAT) is the combination of the medial axis with at each node the distance values $R$.
+However, instead of removing bones from the Voronoi diagram we will introduce more bones such that the skeleton discretizes the boundary shape into quads within which the $R$ can be interpolated linearly.
+We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
+The VQ greatly simplifies the processing required downstream in our framework.
 
-We propose a modified MAT: the grounded medial axis transform: gMAT.
-The distance field defined by the gMAT approximates the distance field of the MAT using \uwave{piece-wise linear quads}.
-The gMAT is the set of all points where the derivative of the distance field is not constant.
+In order to generate the VQ, we start by generating a normal Voronoi Diagram and remove all segments which lie outside of the boundary shape.
+We then introduce bones such that each node in the VQ is directly connected to the outline via a single bone:
+each node in the VQ is connected to the closest points on the boundary (its \emph{support}).
+As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
+For concave verts the quad is missing the outline segments and so it regresses into a triangle;
+likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
+\todo{TODO: make pics}
 
-Each node in the gMAT is connected to the outline via a \emph{single} bone.
-This condition is violated on a MAT where there are concave outline verts.
-The gMAT segments the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
-For concave verts the outline segments is missing and the quad becomes a triangle;
-likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
+We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
+That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
+Furthermore, we can linearly interpolate the distance field of a quad $p_0v_0v_1p_1$ (where $p_0$ and $p_1$ lie on the outline shape):
+For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.
 
-For a normal MAT it is already the case that
-for a bone segment $v_0 v_1$ generated by two outline segments $p_0 p_1$ and $p_2 p_3$,
-the distance on locations along $v_0 v_1$ can be interpolated linearly between $R(v_0)$ and $R(v_1)$.
-The distance field between $v_0 v_1$ and $p_0 p_1$ can be constructed linearly as well.
-
-For a MAT the same does not hold for parabolic bones or bones generated by two concave outline verts.
-We therefore discretize these segments and connect the introduced nodes to the oulines using new ribs.
-The resulting quads encode the original distance field in a piece-wise fashion using linear gradients.
-
-The MAT is a subset of the Voronoi diagram inside the part, which in turn is a subset of the gMAT.
-See \cref{voronoi_MAT}.
+i
 

### 2019-07-08 4_method.tex
rewrite single bead segments section > printing order section

@@
 
-\paragraph{Single bead segments}
-\Cref{single_bead_strategy}
-We round to ingteger multiples of half the nozzle width so as to allow single-bead segments.
-These could be printed from polygon and return to polygon over same segment without extruding.
+\paragraph{Printing order}
+The order in which beads are printed has influence on the quality and dimensional accuracy of a print.
+If the inner beads are printed first then small inaccuracies in the deposition process propagate outward and the final outline of the print layer will be less accurate.
+However, if the second bead is printed before the outer bead then the outer bead has more material to adhere to, which lessens the overhang constraints.
+We therefore choose to print the inner beads first starting from the second bead and at the very end print the outermost bead.
+
+When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.
+These polylines generally form closed polygons, but at significant regions of the VQ the toolpaths consist of single bead polyline toolpaths.
 See \cref{single_bead_strategy}.
+These single bead polylines can connect to polygonal toolpaths and they can also meet each other at 3-way junctions.
+We determine the printing order for all segments of a given bead index by minimizing the travel distance using a greedy path order optimizer.
+\todo{[implementation needed!]}
 
-We only introduce single bead segments along marked areas of the medial axis.
-We could also do it for non-marked areas, but that would result in a small single bead segment at \emph{every} corner.
+In general the toolpath location should be centered on the middle of the bead.
+However, when the bead width is smaller than the nozzle size we might want to offset the toolpath toward a previously printed bead.
+That way the previously printed bead occludes part of the hole in the nozzle such that the unoccluded hole is as wide as the required bead width.
+The printing order and the toolpath positioning of the beading strategy are therefore interrelated.
 
-\hl{How to deal with single beads connecting two polys?}
-: Print 1st poly $\to$ print single bead $\to$ print 2nd poly $\to$ travel over single bead $\to$ print 1st poly
+Around 3-way junctions we need to prevent overextrusion.
+We need to reduce the extrusion amount after the first time we pass an intersection: commonly known as \emph{ghosting}.
+See \cref{ghosting}.
+In order to realize the reduction we remove a section from the extrusion bead up to a distance equal to the feature radius from the junction.
 
-\hl{How to deal with three-way intersection single beads?}
-: Cut up in 1 single bead connecting two polys and 1 normal single bead only connected to one poly
-
-Where to put the middle of the toolpath, based on the middle of the line, the line width and the processing order?
-
-Idea: generate only outer 3 walls, except in marked regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.
-Don't generate transitions when $R > 5\win$ or something?
-Only do this in skin regions?
+\begin{figure}
+\centering
+\includegraphics[width=.99\columnwidth]{sources/method/ghosting.pdf}
+\caption{Ghosting prevents over-extrusion at junctions.}
+\label{ghosting}
+\end{figure}
 

### 2019-07-08 pathplanning_preliminaries/cheetah/convert_for_repetierHost.py
save original image source files

@@ -1,0 +1,35 @@
+#!/usr/bin/python
+
+import sys
+from parse import *
+from math import *
+
+#print('Number of arguments:', len(sys.argv), 'arguments.')
+#print('Argument List:', str(sys.argv))
+
+filename = sys.argv[1]
+outfile = sys.argv[2]
+
+last_x = 0
+last_y = 0
+with open(filename, 'r') as f:
+  with open(outfile, 'w') as out:
+    for (line_nr, line) in enumerate(f):
+      if line.startswith("M82"):
+        out.write("M83 ; relative extrusion mode")
+        continue
+      result = parse("G5 X{} Y{} S{} E{}", line)
+      if result != None:
+        (_x, _y, s, e) = result
+        x = float(_x)
+        y = float(_y)
+        dist = sqrt((x - last_x)**2 + (y - last_y)**2)
+        w = float(s) *0+1* float(e)
+        ee = w * dist
+        print(w, dist, ee)
+        #print(str(line_nr) + " : " + x + " ; " + y + " ; " + s + " ; " + e)
+        out.write("G1 X" + _x + " Y" + _y + " E" + str(w) + "\n")
+        last_x = x
+        last_y = y
+      else:
+        out.write(line)

### 2019-07-08 pathplanning_preliminaries/cheetah/scale_G5_coords.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python
+
+import sys
+from parse import *
+
+#print('Number of arguments:', len(sys.argv), 'arguments.')
+#print('Argument List:', str(sys.argv))
+
+filename = sys.argv[1]
+scale = float(sys.argv[2])
+
+outfile = sys.argv[3]
+
+
+with open(filename, 'r') as f:
+  with open(outfile, 'w') as out:
+    for line in f:
+      result = parse("G5 X{} Y{} {}", line)
+      if result != None:
+        (x, y, rest) = result
+        out.write("G5 X" + str(float(x) * scale) + " Y" + str(float(y) * scale) + " " + rest + "\n")
+      else:
+        out.write(line)

### 2019-07-08 pathplanning_preliminaries/shapes/wedge/wedge_4_80_verification.py

@@ -1,0 +1,82 @@
+'overlap compensated'
+data = [[3500.02, 525.62, 500  ],
+ [13749.69, 0, 500      ],
+ [13749.69, 0, 0        ],
+ [3500.02, -525.62, 500 ],
+ [2500.02, 1576.87, 500 ],
+ [34037.46, 0, 500      ],
+ [34037.46, 0, 0        ],
+ [24049.96, -499.38, 500],
+ [2500.02, -1576.87, 500],
+ [1500.01, 2628.12, 500 ],
+ [54062.43, 0, 500      ],
+ [54062.43, 0, 0        ],
+ [44074.91, 499.38, 500 ],
+ [1500.01, -2628.12, 500],
+ [500.00, 3679.37, 500  ],
+ [74087.39, 0, 500      ],
+ [74087.39, 0, 0        ],
+ [64099.88, 499.38, 500 ],
+ [500.00, -3679.37, 500 ]]
+d=np.array(data)
+
+
+
+'my algorithm'
+>>> data = [[3500.02, 525.62, 500   ],
+...  [23860.08, 360.72, 363  ],
+...  [24025.0, 0.0, 363      ],
+...  [23860.08, -360.72, 363 ],
+...  [3500.02, -525.62, 500  ],
+...  [2500.02, 1576.87, 500  ],
+...  [24581.51, 1082.15, 367 ],
+...  [25022.63, 472.02, 473  ],
+...  [43846.44, 322.12, 325  ],
+...  [44049.95, 0, 325       ],
+...  [43846.44, -322.12, 325 ],
+...  [25022.63, -472.02, 473 ],
+...  [24581.51, -1082.15, 367],
+...  [2500.02, -1576.87, 500 ],
+...  [1500.01, 2628.12, 500  ],
+...  [25302.95, 1803.59, 372 ],
+...  [25967.57, 1416.96, 484 ],
+...  [44490.54, 966.22, 330  ],
+...  [45046.10, 470.53, 475  ],
+...  [63793.94, 244.65, 247  ],
+...  [64074.91, 0, 247       ],
+...  [63793.94, -244.65, 247 ],
+...  [45046.10, -470.53, 475 ],
+...  [44490.54, -966.22, 330 ],
+...  [25967.57, -1416.96, 484],
+...  [25302.95, -1803.59, 372],
+...  [1500.01, -2628.12, 500 ],
+...  [500.0, 3679.37, 500    ],
[…]

### 2019-07-08 4_method.tex
remove comparison of different versions of technique

@@
 \end{figure}
-
-\subsection{Overview}
-Below in \cref{parabola_switch_to_less_lines} you can see the different technique preliminaries thought out.
-The problem this paper is trying to solve is the large gap in M0.
-M1, M2 and M3 use vertices at specific locations and use altered distance measures for those points; these methods are not stable to adding more bones to the skeleton.
-M4 and M5 define distance measures in any location (based on \cref{distance_rounding_transition}) which makes them stable.
-M5 avoids jagged lines by only applying the MAT distance remapping up to a cutoff point discussed in \cref{sec:significance_measure}.
-
-\begin{figure*}
-\includegraphics[width=\textwidth]{sources/method/parabola_switch_to_less_lines.pdf}
-\caption{Different preliminary variants of the proposed algorithm on a parabola segment.}
-\label{parabola_switch_to_less_lines}
-\end{figure*}

### 2019-07-08 10_applications.tex
lil todos
remove lithophane text adn figures

--- 2019-04-30 10_applications.tex
@@
 \section{Applications}
-\subsection{3D Lithophane}
-``The illuminance $E_\text{p}$ lux at a location $d$ metres from a point source of intensity $I$ candela is given by the cosine law of illumination,
-$E_\text{p} = I \cos \theta / d^2$.''\cite{snow2001plant}
-We relate the distances to the model: $E_\text{p} = I \cos \theta / (d_\text{rel} \cdot d_\text{max})^2 = d_\text{max}^2 I \cos \theta / d_\text{rel}^2$.
-The scaling factor $d_\text{max}^2 I$ depends on the light source (intensity and location) and the 3D model.
 
-The RGB values are scaled in order to prevent too dark requests which would correspond to too thick shell: $R' = E_\text{min} +  (1 - E_\text{min}) R$.
-Likewise for G and B.
+\subsection{Variable thickness microstructures}
+show the effect of the planned toolpath on the performance of varying thickness microstructures
 
-We assume a simple translucency model where twice the thickness implies squaring the fraction of transmitted light.
-Suppose a thickness of $w=1$ corresponds to \SI{30}{\percent} absorbtion, so the transmittance is $\tau_1 = 0.7$.
-Then a thickness of $w=2$ should correspond to a transmittance of $\tau = \tau_1^2 = 0.7^2 = .49$.
-% A thickness of $w=4$ then corresponds to $\tau = (\tau_1^2)^2$.
-In general $\tau = \tau_1^w$, so we derive that $w = \log_{\tau_1} \tau = \frac{\log \tau}{\log \tau_1} = c \log \tau$,
-where $c$ and $\tau_1$ depend on the material.
-The thickness of the shell at any location is determined by $w = c \log \frac{E_\text{p}}{E_\text{r}}$.
-
-The requested luminance is computed from the texture image as $E_\text{r} = I_\text{r} \left( 0.212655 R^\gamma + 0.715158 G^\gamma + 0.072187 B ^\gamma \right)$, where $\gamma = 2.2$.
-This formula comes from the official conversion from sRGB to CIE XYZ and taking the Y for luminance.
-Zero light requires infinite thickness, so we introduce an $E_\text{min}$.
-We might choose to cap all $E_\text{r}$ to lie above $E_\text{min}$, but that means we'd lose a range of brightnesses.
-We instead choose to resize the range of requested brightnesses to be between min luminance and $1.0$.
-
-$E_\text{p}$ depends on an unknown scaling factor $I$, and $E_\text{r}$ can be scaled at will.
-The total ratio $\frac{E_\text{p}}{E_\text{r}}$ can therefore be scaled by some factor $b$:
-$w = c \log b \frac{E_\text{p}}{E_\text{r}} = cb + c \log \frac{E_\text{p}}{E_\text{r}} = x + c \log \frac{E_\text{p}}{E_\text{r}}$
-(Beware this formula can give negative values for $w$.)
-
-We can choose $x$ so as to optimize the range of achievable brightnesses given the minimum and maximum thickness of the shell.
-Finally, the offset is clamped to within the range $[0.4, 3.0]$ so that it is always manufacturable with a nozzle size of \SI{0.4}{\milli\meter} and is not too large.
-
-For materials where $\tau_1 \to 1$ (i.e. $c \to 0$) the translucency is too high and the luminance modulation would require thicknesses which are too large.
-For materials where $\tau_1 \to 0$ (i.e. $c \to -\infty)$ the translucency is too low and the luminance is modulated by a too small range in thicknesses.
-The optimal $\tau_1$ depends on the size and geometry of the model as well as the texture colors.
-See \url{https://www.photonics.com/Articles/Accurate_Transmission_Measurements_of_Translucent/a32297} on measurement of transmittance.
-Also see \url{https://www.plasticsnet.com/doc/article-how-to-measure-translucent-materials-0001}
+Implement varying width for infill patterns in Cura?

### 2019-07-08 4_method.tex
remove section on shortcomings and ideas which are 'out there'

@@
 
-\subsubsection{Spacing problems}
-Applying a beading strategy to the skeleton might not be trivial.
-The trivial approach explained above introduces slight deviations from the beading strategy at intermediate locations in a quad.
-When the widths are always the same this doesn't happen, but with widths changing throughout a quad this can pose a slight problem.
-
-In the end this problem comes down to the fact that the medial axis is the location of quench sites when performing homogeneous insets.
-Changing the bones for the chosen beading strategy is impossible, because the new skeleton would then induce a new beading strategy.
-While this process could converge, it would spend too much computation time for only a small benefit.
-
-(In this subsection we assume an even spacing beading strategy, i.e. $\win = \wout$.)
-
-A related problem is that that applying the beading strategy to highly skewed quads would not be stable to the addition of extra bones.
-See \cref{quad_instability}.
-\hl{We should introduce bones in such a case!}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/quad_instability.pdf}
-\caption{The addition of the extra bone (orange) causes a significant change from the dark red path to the green path.}
-\label{quad_instability}
-\end{figure}
-
-See \cref{angular_based_spacing}.
-One could think we should not space the joints evenly along the bones, but make the spacing depend on the angles involved.
-We could check the intersection point of the lines of two polygon segments and radially project lines with the same angular spacing.
-However, the angular spacing for two patches connected to a single bone would be different, so the paths wouldn't connect!
-\hl{Does that mean the angle of the bones should ideally be updated?}
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/angular_based_spacing.pdf}
-\caption{Angular based spacing isn't feasible.
-The bottom medial axis bone has different spacing based on the two patches.
-The radially evenly spaced lines are drawn in cyan for the interaction between the bottom outline segment with the top segment and in purple for the interaction between the second bottom segment with  the top segment.}
-\label{angular_based_spacing}
-\end{figure}
-
-\paragraph{Ideal parabolas}
-Subdividing bones introduced for parabolas evenly leads to even spacing along the bone,
-while a derived formula seems to produce even spacing in a different sense:
-See \cref{medial_axis_parabolas}
-
-\begin{figure}
-\begin{subfigure}{0.9\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_even_spacing.jpg}
-\caption{Parabola transformed to straight skeleton and offsets using even spacing along bones.}
-\end{subfigure}
-\begin{subfigure}{0.9\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/medial_axis_uneven_spacing.pdf}
-\caption{Parabola function plots from analytical solutions where the distance to the point is a whole fraction of the distance to the line.}
-\label{medial_axis_parabolas_functions}
-\end{subfigure}
-\caption{The equidistant points between a vert and a line form a parabola.
-There are different methods for generating toolpaths which are in between the medial axis and the outline.
-Note that the uneven spacing does \emph{not} coincide with an even angular spacingat the border between the patches: see the left side of \subref{medial_axis_parabolas_functions}.}
-\label{medial_axis_parabolas}
-\end{figure}
-
-\hl{But the uneven spacing figure looks like its evenly spaced in the direction orthogonal to the toolpath itself!}
-
 \subsubsection{Processing order}

### 2019-07-08 10_applications.tex
lil redo of validation and of applications

@@
 
-\subsection{Variable thickness microstructures}
+\subsection{Thin parts}
+\begin{itemize}
+\item Casings (e.g. for electronics)
+\item Prototypes for blowmold parts or sheet metal parts etc.
+\item Miniature models, architectural models
+\item Microstructures
+\item Lithophanes
+\end{itemize}
+
 show the effect of the planned toolpath on the performance of varying thickness microstructures
 
-Implement varying width for infill patterns in Cura?
+\subsection{Widening}
+Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.

### 2019-07-08 6_validation.tex
outline of other sections
lil redo of validation and of applications

@@
 \section{Validation}
+
+\subsection{Strategies}
+We can emulate a variety of toolpath generation strategies by applying various beading strategies to our framework.
+
+\paragraph{Naive Strategy}
+
+\paragraph{Constant bead count}
+Emulates \cite{Ding2016a}
+
+\paragraph{Deviation at middle}
+Emulates \cite{Jin2017}
+
+\paragraph{Only outer bead}
+Emulates \cite{Moesen2011}
+
+\paragraph{Distributed strategy}
+Distribute the overfill or underfill which would happen using a naive strategy over all beads.
+This maximizes robustness and minimizes narrow beads qhich are difficult to print.
+
+\paragraph{Combined strategy}
+\Cref{wedge_and_infill} shows a combined toolpath strategy.
+
+\begin{figure}
+\centering
+\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
+\caption{Use single and double wall lines in regions where the infill would be too thin.}
+\label{wedge_and_infill}
+\end{figure}
+
+\subsection{Filling accuracy}
 Render toolpaths and calculate percentage of covered volume.
@@
 Visualize thickness of beads as color.
+
+Show results for different settings.
+
+Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.
+
+Take same examples as Moessen: grids of triangular holes and circular holes.
+Also use examples of Jin and Kao.
+
+Use example layers of a typical object with thin walls: electronics casing.

### 2019-07-08 4_method.tex
lil redo of validation and of applications
remove section 'Connect introduced joints to outline'
The angle of introduced bones is never explicitly dealt with.
It follows directly from the condition that we connect each node to its supporting outline locations.

@@
 
-\subsubsection{Connect introduced joints to outline}
-\old{
-\paragraph{Angle of fingers introduced on the skeleton}
-\Cref{finger_angles}
-Cannot be optimized.
-Always has to be orthogonal to the polygon segment.
-Otherwise the algorithm isn't stable w.r.t. extra vertices in the outline.
-}
-\begin{figure}[H]
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/finger_angles.jpg}
-\caption{Stability against extra vertices}
-\label{finger_angles_stability}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/finger_angles_2.jpg}
-\caption{Wrong rib angle, not orthogonal to outline}
-\end{subfigure}
-\caption{Finger angles should always be orthogonal to the outlines}
-\label{finger_angles}
-\end{figure}
-
-\begin{wrapfigure}[5]{r}{0.2\linewidth}
-\begin{center}
-\includegraphics[width=\linewidth]{sources/method/min_angle_of_introduced_bones.pdf}
-\end{center}
-\end{wrapfigure}
-
-Because the ribs are always orthogonal to the outline segments, the angle $\alpha$ between the spine and ribs is within the range $\SI{60}{\degree} < \alpha < \SI{90}{\degree}$.
-
 \subsection{Toolpath extraction}
@@
 \end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
-\caption{Use single and double wall lines in regions where the infill would be too thin.}
-\label{wedge_and_infill}
-\end{figure}

### 2019-07-08 4_method.tex
describe tick placement algorithms

@@
 
-\subsubsection{Processing order}
-\hl{How do we process the graph?}
-\begin{itemize}
-\item walk along polygons and for each vert walk down the graph up to the desired depth
-\item process nodes in depth first order
-\item process nodes in $R$ sorted order
-\end{itemize}
+\subsubsection{Toolpath extraction algorithm}
+After the beading strategy has been applied we have a beading associated with each significant node as well as each node with locally optimal $R$.
+In order to determine the tick locations of quads which don't contain any such node, we propagate the beading information down.
+We therefore sort all quads on their highest $R$-value and process the high $R$ quads first.
+The beading information is then passed down along the bones of the quad to lower $R$ nodes if those nodes don't already have a beading associated.
 
-We would require either a mapping from locations or bones to toolpath segments, which we can use to efficiently connect paths together.
+See \cref{alg_beading_propagation}.
 
-Or we process all segments in order of the polygon, but then we need to track which polygons have been processed.
+\begin{algorithm}
+\caption{Beading propagation}
+\label{alg_beading_propagation}
+\begin{algorithmic}
+\State quads.sortOn(getHighestR())
+\ForAll{$q \in$ quads}
+	\State $v_\text{max} = q$.getHighestR()
+	\State beading = retrieveBeading($v_\text{max}$)
+	\If {$\neg$ retrieveBeading($v_\text{max}$.next())}
+		\State storeBeading($v_\text{max}$.next(), beading)
+	\EndIf
+	\If {$\neg$ retrieveBeading($v_\text{max}$.prev())}
+		\State storeBeading($v_\text{max}$.prev(), beading)
+	\EndIf
+\EndFor
+\end{algorithmic}
+\end{algorithm}
 
-If we don't process both sides of the gMAT at the same time then we should record certain calculations such as the transition locations and maye also the parabola sample points.
+We can then process all bones in arbitrary order and generate the ticks along those bones.
+See \cref{alg_tick_generation}.
 
-\hl{Is there or should there be a specific ordering on the bones connected to a joint?}
-A joint can have multiple parents.
-We could order the bones cyclically, irrespective of whether they are going `up' or `down'.
+\begin{algorithm}
+\caption{Tick generation}
+\label{alg_tick_generation}
+\lstset{language=C++}
+\begin{lstlisting}[frame=single]
+Point a = edge->to->p;
+Point b = edge->from->p;
+Point ab = b - a;
+
+int start_R = edge->to->data.distance_to_boundary; // higher R
+int end_R = edge->from->data.distance_to_boundary; // lower R
+assert(end_R <= start_R);
+
+int junction_idx;
+// compute starting junction_idx for this segment
+for (junction_idx = (beading->toolpath_locations.size() - 1) / 2; junction_idx >= 0 && junction_idx < beading->toolpath_locations.size(); junction_idx--)
+{
+  int bead_R = beading->toolpath_locations[junction_idx];
+  if (bead_R <= start_R)
+    break; // junction coinciding with start node is used in this function call
+}
+
+for (; junction_idx >= 0 && junction_idx < coord_t(beading->toolpath_locations.size()); junction_idx--)
+{
+  int bead_R = beading->toolpath_locations[junction_idx];
+  assert(bead_R > 0);
+  if (bead_R < end_R)
+    break; // junction coinciding with a node is handled by the next segment
+
+  Point junction(a + ab * (bead_R - start_R) / (end_R - start_R));
+  ticks.emplace_back(junction, beading->bead_widths[junction_idx], junction_idx);
+}
+\end{lstlisting}
+\end{algorithm}
+
+We then generate bead segments for each quad by connecting together the ticks of the same index.
+If the amount of ticks on both sides of the quad is not the same then this quad is in a transition and we leave one tick unconnected.
 

### 2019-07-08 6_validation.tex
planning of example shapes

@@
 \subsection{Filling accuracy}
-Render toolpaths and calculate percentage of covered volume.
+Render toolpaths and calculate amount of overfilling and amount of underfilling.
 
-Visualize thickness of beads as color.
+\old{Visualize thickness of beads as color.}
 
@@
 
-Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.
+\old{Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.}
 
-Take same examples as Moessen: grids of triangular holes and circular holes.
-Also use examples of Jin and Kao.
-
-Use example layers of a typical object with thin walls: electronics casing.
+Example shapes:
+\begin{itemize}
+\item same as Moessen: grids of triangular holes
+\item same as Moessen: circular holes.
+\item same as Jin 
+\item same as Kao
+\item wedge
+\item layer of a typical model: phone case
+\item some of the above shapes, but with some fuzzy randomized outline
+\end{itemize}

### 2019-07-08 12_conclusions_future_work.tex
add conclusion and future work

\section{Conclusion and future work}
conclusion: reiterate abstract

\subsection{Future work}
Use Voronoi Quadrangulation to generate quad dominant meshings for FEM.

Generate thicker bead widths near sharp corners in order to mimic limitations in the extrusion process.

### 2019-07-09 4_method.tex
make figure positions floating

@@
 if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.
+See \cref{distance_based_angles}.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 
-The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
-\begin{figure}[H]
+The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices: \cref{distance_ratio_limit}.
+
+\begin{figure}
 \centering
@@
 So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.
+See \cref{end_of_markings_point_point}.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.
+See \cref{end_of_markings_point_point}.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 $ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$
+See \cref{transition_placement}.
 
-\begin{figure}[H]
+\begin{figure}
 \centering
@@
 \hl{outdated functions and variables!}}
-\label{transition_length}
+\label{transition_placement}
 \end{figure}
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{subfigure}{0.45\columnwidth}

### 2019-07-10 2_related_work.tex
lil
lil todos
rename sections;  section -> subsection etc.
more related work

@@
 \section{Related Work}
-Adjusted MAT structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
+
+\subsection{Toolpath strategies}
+
+\todo{Find reference on patchwise Zig-Zag toolpathing strategy.}
+
+Combining concentric toolpaths into continuous extrusion spirals. \cite{Held2009}
+
+Defining a continuous extrusion Zig-Zag toolpath. \cite{Jin2017}
+
+\subsection{Space filling toolpaths}
+\todo{find other literature which tries to minimize underfilling and overfilling which is not based on a skeletonization.}
+
+\subsection{Medial axis based toolpaths}
+Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
 \Cref{moessen}
@@
 \includegraphics[width=\columnwidth]{sources/related_work/moessen.jpg}
-\caption{asfd}
+\caption{\citeauthor{Moesen2011}}
 \label{moessen}
@@
 \includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
-\caption{asfd}
+\caption{\citeauthor{Jin2017}}
 \label{jin}
@@
 \end{figure}
+
+\subsection{Variable extrusion width}
+
+Changing extrusion rate and temperature to match a given velocity. \cite{Ertay2018}
+
+Changing velocity in order to change extrusion rate.
+Shortly discussed in \cite{Kuipers2018}.
+\todo{find another reference}

### 2019-07-10 8_discussion.tex
add discussion section

\section{Discussion}

\subsection{Theoretical analysis}
In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
\todo{[figure showing wedges, naive toolpaths and gaps]}
Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
The final skeleton is still an exact and full feature descriptor.
In that sense our framework provides an exact solution space.

Note also that our method is robust against small perturbations in the input shape.
Although the skeleton might acquire extra bones, the significant portions of the skeleton remain similar and the output toolpaths change infinitesimally.

Our framework is also local.
The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
This means the toolpathing is stable against large perturbations of the input shape in far away regions
and it also allows for some parallelism during the computation of the toolpaths.

\subsection{Comparison of different beading strategies}
\todo{Discussion of finding of Validation section}

### 2019-07-10 4_method.tex
rewrite method overview

@@
 \subsection{Method Overview}
+The global idea is that we locally decide on the number of beads everywhere in the input shape, then apply a beading strategy to determine the widths of the beads and then generate the toolpath locations and widths from this.
+We decide on a bead count at locations which lie in the middle of the shape in some sense to be defined.
+The beading strategy then gives us the beading widths and locations in between those center locations and the outline.
+These beadings are then used to generate the toolpath junctions, which are connected together to form the extrusion toolpaths with varying width.
+
 \begin{enumerate}
-\item Determine the beading strategy: the optimal number of beads and their widths in order to cover a given distance with those beads.
-\item Compute the medial axis transform (MAT)
-\item Discretize the MAT and add extra segments such that the gMAT divides a polygon in quads
-\item Mark significant high curvature portions of the gMAT
-\item Introduce bones on marked regions where we transition to a different number of beads
-\item Add ticks on non-marked regions according to the beading strategy.
-\item Connect ticks and transition nodes into toolpaths.
+\item Compute a skeletonization of the outline shape based on the Voronoi diagram.
+\item Use a significance measure to mark portions of the skeleton which lie in the center.
+\item Determine the bead count values in the marked regions and handle transitions in bead count values.
+\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
 \end{enumerate}

### 2019-07-10 4_method.tex
redefine beading strategy mathematically
The old definition was for the specific beading strategy I was working on, rather than for beading strategies in general.

@@
 
+We define a beading strategy as the following set:
+$$
+\left\{ b(d), p(n), W(n, d), L(n, d), t, \alpha_{\text{max}} \right\}
+$$
+where
+$b(d)$ gives the optimal bead count to cover a total distance of $d$,
+$p(n)$ gives the optimal total distance of a given bead count $n$,
+$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
+$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
+$t$ is the length of transitions within which we switch to a different number of beads
+and
+$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.
+
+We call a distance $d$ `prefered' when $d = p(b(d))$
+For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
+
+The following restrictions hold:
+\begin{itemize}
+\item $tb(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0$
+\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
+\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
+\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
+\item $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
+%\item $b \left( p(n) \right) = n$ % follows from the above!
+\item $b(d)$ is monotonic: $ b(d) \leq b(d + \epsilon)$
+\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\end{itemize}
+
+The angle requirement ansures that there is never a 3-way junction of significant bones.
+
+By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading, which is defined as the following set:
+$$
+\left\{ d, w_i, l_i  \right\}
+$$
+where
+$d = 2 R(v)$ is the total distance associated with $v$,
+$w_i$ is the bead width of the bead with index $i$
+end
+$l_i$ is the distance of the toolpath location of bead $i$ from the outline.
+
+\subsubsection{Proposed optimal beading strategy}
+\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
+
+\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}
+
 We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
@@
 \item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
-\item $b$ is monotonic
+%\item $b$ is monotonic
 %the item below follows from the two above
@@
 \item $ 0 \leq b(d) \leq d / w_\text{min} $
-\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+%\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
 \end{itemize}
-
-For our method we also require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
 
@@
 \end{align}
-We call a distance $d$ `prefered' when $d = p(b(d))$
 

### 2019-07-10 4_method.tex
lil

@@
 \subsubsection{Background}
+One of the most commonly used skeletonizations of a shape is the medial axis.
 The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
@@
 The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
-The MAT can unambiguously recreate the exact input shape. \todo{[citation needed]}
+The MAT can unambiguously recreate the input shape exactly. \todo{[citation needed]}
 

### 2019-07-10 4_method.tex
rewrite significance measure section

@@
 \subsection{Beading}
-We assign a beading to each significant node (and each local optimum).
+We assign a bead count to each node in the skeleton which is connected to a bone which is in `the center' of the shape
+and also to each node with locally optimal feature radius $R$.
+Around regions where the bead count changes we introduce transition regions.
 
@@
 \Cref{rounded_dist_measures}
-We mark bones as to-be-transformed based on the angle between the two edges of the polygon for which this bone is the bisector.
-Equivalently we can look at the \emph{bisector angle} $\alpha$ between a skeletal point and the two closest points on the outline.
-(Same definition as \cite{attali1996modeling}.)
+Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
+This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
+The bisector angle $\alpha$ is the angle $\widehat{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
+See \cref{naive_overfill_underfill}.
+The bisector angle is therefore an exact measure of the amount of overfill and underfill.
+Contrary to related literature we will \emph{keep} the insignificant regions of the skeleton.
+Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.
 
-Contrary to common techniques we will \emph{keep} the insignificant regions of the skeleton.
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
+\caption{
+Overfill and underfill areas in a naive beading using a constant bead witdh $w$ of a wedge area with vertex angle $\beta$.
+The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
+The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
+}
+\label{naive_overfill_underfill}
+\end{figure}
 
-\paragraph{line-line bones}
-When the angle between two outline segments is small, the naive method will produce long triangular gaps.
-A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
-Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
-if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.
+A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
+if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \sin(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
 See \cref{distance_based_angles}.
+This ratio can be immediately applied to simple skeleton segments to determine whether they are significant.
+For skeletal segments generated by a polygon vertex and another vertex or line segment, we could exactly determine at which location $\frac{\partial R}{\partial x} > \sin(\alpha_\text{max} / 2)$.
+However, because we have discretized such segments, we can approximate the location by applying our ratio based significance measure on the piecewise linear approximating segments directly.
 
@@
 
-\paragraph{line-point segments}
-For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
-If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
-i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
-i.e. when $\abs x/d < 1 / \sqrt{3}$,
-i.e. when $\abs x < d \sqrt{3} / 3$.
-So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.
-See \cref{end_of_markings_point_point}.
+Any node in the skeleton can have at most two significant bones connected to it, because we have limited $\alpha_\text{max} > 120\degree$,
+while the corners of a triangle can only add up to \SI{180}{\degree}.
+\todo{TODO: make figure which clearly shows this!}
+This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.
 
-\begin{figure}
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
-\caption{End-of-markings for a parabolic spine segment.}
-\label{end_of_markings_point_point}
-\end{figure}
+\paragraph{Bead counts}
+In order to apply the beading strategy to the VQ
+we assign each significant node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
 
-\paragraph{point-point bones}
-For a segment gerenated by points $(0,0)$ and $(0,d)$, the angle $\alpha > \SI{120}{\degree}$ when $\abs(x) < \frac12 d \tan \SI{30}{\degree} $,
-so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.
-See \cref{end_of_markings_point_point}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.3\columnwidth]{sources/method/end_of_markings_point_point.pdf}
-\caption{End-of-markings for the segment(s) generated by two outline verts.}
-\label{end_of_markings_point_point}
-\end{figure}
-
-\paragraph{MAT distance transform}
-In order to apply the beading strategy to the MAT
-we assign each node $v$ of the medial axis a bead quantity $B^*$ which is initially based on $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
-
-\hl{How should we define $B^*$? Currently it is always the rounded measure, but it needs to be unrounded in non-marked areas and it needs to support fractional numbers around transitions!}
-
-The bead quantity measure $B^*$ measure should be rounded
-where the MAT distance measure $R$ is a local maximum: when all directly connected nodes have a lower MAT distance measure.
-See bottom of \cref{rounded_vs_unrounded}.
+We also assign a bead count $v.B^*=b(R(v))$ to all nodes $v$ which are local maxima, i.e. the $v$ for which $\forall v_\text{n} \in v.\text{neighborhood} : R(v) > R(v_\text{n})$. 
+This prevents the single overfill or underfill region in non-significant regions.
+See \cref{rounded_vs_unrounded}.
 

### 2019-07-10 4_method.tex
lil fixes
reformulated mathematical requirements on strategy

@@
 \begin{itemize}
-\item $tb(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0$
+\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
 \item $120\degree < \alpha_{\text{max}} \leq 180\degree$
@@
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
+\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
 %\item $b \left( p(n) \right) = n$ % follows from the above!
-\item $b(d)$ is monotonic: $ b(d) \leq b(d + \epsilon)$
-\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
+\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\item $t$ is viable: $\forall i \in \mathbb{N} : t < \left( p(i + 1) - p(i) \right) /{2 \cos \alpha_\text{max}}$
 \end{itemize}
 
-The angle requirement ansures that there is never a 3-way junction of significant bones.
+The angle requirement ensures that there is never a 3-way junction of significant bones.
 
@@
 \subsubsection{Proposed optimal beading strategy}
+@Readers: you can skip reading this section for now.
 \todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
-
 \todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}
@@
 For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.
-
-i
 

### 2019-07-10 4_method.tex
remove old figures

@@
 \begin{figure}
-% from /home/t.kuipers/Documents/PhD/Variable_Width_project/pathplanning preliminaries/straight_skeleton_vs_medial_axis.svg
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/example_straight_skeleton.pdf}
-\caption{Straight skeleton}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/example_medial_axis.pdf}
-\caption{Medial axis}
-\end{subfigure}
-\caption{Example polygon middle analysis thingies. Difference is colored.}
-\label{medial_axis_vs_straight_skeleton}
-\end{figure}
-
-\begin{figure}
-\begin{subfigure}{0.24\columnwidth}
+\begin{subfigure}{0.3\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.24\columnwidth}
+\begin{subfigure}{0.3\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
-\caption{Voronoi}
+\caption{Limited VD}
 \end{subfigure}
-\begin{subfigure}{0.24\columnwidth}
+\begin{subfigure}{0.3\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
-\caption{gMAT}
+\caption{VQ}
 \end{subfigure}
-\begin{subfigure}{0.24\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/gMAT_example_labeling.pdf}
-\caption{Quads}
-\end{subfigure}
-\caption{Grounded medial axis transform.
-Dark red are linear segments,  bright red are parabolic segments with high curvature, parabola segments with low curvature are purple.
-The labelings of areas show that the gMAT divides the area into quads and triangles and that the medial axis divides the area into sub-areas for each outline polygon.}
-\label{gmat}
+\caption{
+Relation between the medial axis, the limited Voronoi Diagram and the Voronoi quadrangulation: MAT $\subset$ Limited VD $\subset$ VQ.
+Significant parts of the skeleton are visualized in shades of red, insignificant regions in grey and blue.
+}
+\label{skeletonization_comparison}
 \end{figure}
@@
 We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
+See \cref{skeletonization_comparison}.
 The VQ greatly simplifies the processing required downstream in our framework.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.8\columnwidth]{sources/method/voronoi_MAT.png}
-\caption{From \citeauthor{lee1982medial} \cite{lee1982medial}}
-\label{voronoi_MAT}
-\end{figure}
-
 \subsection{Beading}
@@
 \subsubsection{Significance measure}\label{sec:significance_measure}
-\Cref{rounded_dist_measures}
 Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
@@
 \subsubsection{Transitioning}
-
-\begin{figure}
-\centering
-\includegraphics[width=.6\columnwidth]{sources/method/rounded_dist_measures.jpg}
-\caption{MAT distance measures at existing joints can be non-integer multiples of bead width.}
-\label{rounded_dist_measures}
-\end{figure}
-
-See \cref{rounded_dist_measures}.
-
 In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.

### 2019-07-10 4_method.tex
move optimal beading strategy to validation section

@@
 $l_i$ is the distance of the toolpath location of bead $i$ from the outline.
-
-\subsubsection{Proposed optimal beading strategy}
-@Readers: you can skip reading this section for now.
-\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
-\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}
-
-We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
-These widths depend on the following parameters:
-\begin{description}
-\item[$\wmin$] the minimum possible bead width
-\item[$\wmax$] the maximum possible bead width
-\item[$\wout$] the preferred bead width of the outer inset
-\item[$\win$] the preferred bead width of the other insets
-\end{description}
-
-The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
-The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
-Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
-
-We define $W(d)$ as a sequence of bead widths.
-The length of that sequence is $b(d)$.
-For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
-The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
-
-The function $b$ should adhere to several criteria:
-\begin{itemize}
-\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
-%\item $b$ is monotonic
-%the item below follows from the two above
-% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
-\item $ 0 \leq b(d) \leq d / w_\text{min} $
-%\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\end{itemize}
-
-For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
-\begin{itemize}
-\item Minimize unfilled area
-\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
-\item Have the rest of the $W_n$ the same width
-\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
-\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
-\hl{Perhaps we should disallow this because that would require a different transition length}
-\end{itemize}
-
-\iffalse
-\begin{align}
-W(d)_1 = 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   \wout & \text{if } d \geq \wout + \wmin \\
-   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
-  \end{cases}
-\end{align}
-\fi
-
-%\subsubsection{Optimal beading strategy}
-%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
-
-\begin{align}
-L(w_1) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
-   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
-  \end{cases}
-  \\
-L(w_n) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
-   (\win - w) / (\win - \wmin)       & \text{otherwise}
-  \end{cases}
-\\
-L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
-\end{align}
-
-(Singular beads are counted only half.)
-Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
-An example is given in \cref{transition_location}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
-\caption{Mapping of different lengths to a ticking.
-Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
-\label{transition_location}
-\end{figure*}
-
-We introduce a function which produces the $d$ at which all widths are prefered: 
-\begin{align}
-p(n) =
-  \begin{cases} 
-   \frac12 \wout & \text{if } n = \frac12 \\
-    \wout + (n - 1) \win       & \text{otherwise}
-  \end{cases}
-\end{align}
 

### 2019-07-10 6_validation.tex
move experimentation into validation
move optimal beading strategy to validation section

@@
 
-\subsection{Filling accuracy}
+\subsubsection{Proposed optimal beading strategy}
+@Readers: you can skip reading this section for now.
+\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
+\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}
+
+We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
+These widths depend on the following parameters:
+\begin{description}
+\item[$\wmin$] the minimum possible bead width
+\item[$\wmax$] the maximum possible bead width
+\item[$\wout$] the preferred bead width of the outer inset
+\item[$\win$] the preferred bead width of the other insets
+\end{description}
+
+The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
+The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
+Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
+
+We define $W(d)$ as a sequence of bead widths.
+The length of that sequence is $b(d)$.
+For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
+The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
+
+The function $b$ should adhere to several criteria:
+\begin{itemize}
+\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
+%\item $b$ is monotonic
+%the item below follows from the two above
+% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
+\item $ 0 \leq b(d) \leq d / w_\text{min} $
+%\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\end{itemize}
+
+For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
+\begin{itemize}
+\item Minimize unfilled area
+\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
+\item Have the rest of the $W_n$ the same width
+\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
+\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
+\hl{Perhaps we should disallow this because that would require a different transition length}
+\end{itemize}
+
+\iffalse
+\begin{align}
+W(d)_1 = 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   \wout & \text{if } d \geq \wout + \wmin \\
+   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
+  \end{cases}
+\end{align}
+\fi
+
+%\subsubsection{Optimal beading strategy}
+%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
+
+\begin{align}
+L(w_1) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
+   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
+  \end{cases}
+  \\
+L(w_n) &= 
+  \begin{cases} 
+%  \infty & \text{if } w < w_\text{min} \\
+   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
+   (\win - w) / (\win - \wmin)       & \text{otherwise}
+  \end{cases}
+\\
+L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
+\end{align}
+
+(Singular beads are counted only half.)
+Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
+An example is given in \cref{transition_location}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
+\caption{Mapping of different lengths to a ticking.
+Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
+\label{transition_location}
+\end{figure*}
+
+The prefered width $p$ is given as follows:
+\begin{align}
+p(n) =
+  \begin{cases} 
+   \frac12 \wout & \text{if } n = \frac12 \\
+    \wout + (n - 1) \win       & \text{otherwise}
+  \end{cases}
+\end{align}
+
+\subsection{Computational analysis}
+\paragraph{Accuracy}
 Render toolpaths and calculate amount of overfilling and amount of underfilling.
@@
 \end{itemize}
+
+\subsection{Experimentation}
+Print objects and show qualities:
+\begin{itemize}
+\item visual consistency of flat top skin surface
+\item visual gradual transparency changes
+\item graphs of tensile tests on thin walled object
+\end{itemize}
+
+Print on mississipi?
+
+What material should I print with for the tensile tests?

### 2019-07-11 4_method.tex
discretization figure

@@
 As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
-For concave verts the quad is missing the outline segments and so it regresses into a triangle;
-likewise for convex sections it may happen that the inner bone is missing from the quad so that it forms a triangle.
-\todo{TODO: make pics}
+However some of these quads are triangles, as can be seen in \cref{discretization}.
 
 We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
+See \cref{discretization}.
 That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
@@
 For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.
+
+\begin{figure}
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/parabola_dip.pdf}
+\caption{
+Construction of a VQ:
+the MAT in red,
+the bones added by VD in purple,
+the bones added by VQ in orange,
+the bones added by discretization in dashed lines.
+The 3 types of quad are highlighted.
+}
+\label{discretization}
+\end{figure}
 

### 2019-07-11 4_method.tex
make transition length into function depending on bead lower count

@@
 \item Use a significance measure to mark portions of the skeleton which lie in the center.
-\item Determine the bead count values in the marked regions and handle transitions in bead count values.
+\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
 \item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
@@
 $$
-\left\{ b(d), p(n), W(n, d), L(n, d), t, \alpha_{\text{max}} \right\}
+\left\{ b(d), p(n), W(n, d), L(n, d), t(n), \alpha_{\text{max}} \right\}
 $$
@@
 $L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
-$t$ is the length of transitions within which we switch to a different number of beads
+$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads
 and
@@
 
-We call a distance $d$ `prefered' when $d = p(b(d))$
+We call a distance $d$ `preferred' when $d = p(b(d))$
 For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
@@
 \item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\item $t$ is viable: $\forall i \in \mathbb{N} : t < \left( p(i + 1) - p(i) \right) /{2 \cos \alpha_\text{max}}$
+\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
 \end{itemize}

### 2019-07-11 4_method.tex
rewrite transitioning main section

@@
 \subsubsection{Transitioning}
-In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
-The transition will be placed so as to overlap the locations of $b^{-1}(n)$.
+In order to prevent discontinuities in the toolpaths around locations where the bead count changes, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
+See \cref{transitions}.
+The transition will be placed anchored on each location $v$ where $R(v) = \nicefrac12 b^{-1}(n+1)$ for any lower bead count $n$.
+At the start $v_0$ and end $v_1$ of the transition we introduce a new node in the skeleton and connect it to the outline as per the VQ requirement.
+We then assign $v_0.B^* = n$ and $v_1.B^* = n + 1$.
+If there is any node $v_x$ in between $v_0$ and $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the Euclidean distance measured along the significant bone(s).
+See \cref{distance_rounding_transition}.
 
-On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
-For all locations on the MAT in between we linearly interpolate the $b^*$ values, so that we can later interpolate the bead widths $W$ linearly as well.
+\begin{figure*}
+\centering
+\begin{subfigure}{0.9\textwidth}
+\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated__no_transitions.pdf}
+\caption{Without transitioning}
+\end{subfigure}
+\begin{subfigure}{0.9\textwidth}
+\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated.pdf}
+\caption{Transitioning}
+\end{subfigure}
+\caption{
+Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
+}
+\label{transitions}
+\end{figure*}
 
-In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n+\nicefrac12$ beads; this transition requires a distance.
-See \cref{single_bead_strategy_overview}.
-The transition will be such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
-The length of the transition along the medial axis depends on the angles involved.
-See \cref{transition_length}.
-\begin{equation}
-t = r_0 (\sin \alpha + \cos \alpha)
-\end{equation}
-
-\begin{figure}
-\centering
-\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
-\caption{Transition length on a line-line segment.}
-\label{transition_length}
-\end{figure}
-
-The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
-However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
-For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
-$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$
+We determined above that $v_0$ and $v_1$ should be placed around $v$, but their exact position has yet to be specified.
+While the Euclidean distance between them is $t(n-1)$, the distance between $v_0$ and the anchor point $v$ is yet to be specified.
+We determine the distance between the anchor and the transition start $v_0$ proportial to the positioning of the transition relative to the preferred distances: $D(v_0, v) =  t(n) (b^{-1}(n+1) - p(n) ) / (p(n+1) - p(n))$.
+That way the transitions never override the preferred beading.
 See \cref{transition_placement}.
@@
 \centering
-\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
-\caption{Transition placement.
-The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length.
-\hl{outdated functions and variables!}}
+\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
+\caption{
+Transition placement.
+The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
+}
 \label{transition_placement}
 \end{figure}
-
-\hl{How to deal with non-marked regions shorter than the transition length?}
-
-The transition needs to be robust against extra fingers in the MAT.
-How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
-By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
-See \cref{distance_rounding_transition}.
-The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
-\hl{What does it look like for point-line segments or point-point segments?}
 

### 2019-07-11 4_method.tex
lil typo
rewrite transitioning section

@@
 This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.
+(Simple case) If 2 edges of the VQ meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
+However, what if we connect two marked segments using a small non-marked segment?
+There is a distance limit based on \cref{distance_ratio_limit}:
+the connecting segment is always larger in Euclidean distance than the difference in feature radius $R$.
 
@@
 
-\subsubsection{Ends of markings}
-For vertices at the end of a sequence of marked MAT segments we need to take care of transitions.
-If a transition is overlapping the end of the sequence, then either end of the transition would fall beyond the area where transitions should occur.
-How should we deal with thse?
-\begin{itemize}
-\item We need to keep the transition tick on the marked side, because we need to switch to a different number of ticks somewhere.
-Moreover, leaving out the whole transition around end-of-markings would violate the stability principle.
-\item The end-of-marking itself will retain its interpolated MAT distance as described above.
-\item The transition tick on the non-marked side of discarded.
-This means that there will also be no single bead segment leading up to the transition, which coincides with how we deal with non-marked areas.
-See \cref{single_bead_strategy}.
-\end{itemize}
-This method of dealing with end-of-markings can result in gaps slightly larger than usual.
-See \cref{change_to_marked}.
+\subsubsection{Transitioning to insignificance}
+In significant regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in insignificant regions the beading is only governed by the beading of locations with locally optimal feature radius.
+Significant bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$.
+At the end of such chain $v$ we may need to transition from the former approach to the latter.
+This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \sin(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
+See \cref{transition_to_insignificance_problem}.
+
+\todo{Applying the bead count and determining the beading with the associated widths $W$ and locations $L$ is only handled in the next section, so perhaps we should introduce the beading propagation before the section on transitioning.}
+See \cref{alg_beading_propagation}.
 
 \begin{figure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/change_to_marked.pdf}
-\caption{before end of markings}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/change_to_marked_2.pdf}
-\caption{after end of markings}
-\end{subfigure}
-\caption{Transition near end of markings. The gap depends on the positioning of the middle of the transition (dotted lines) with respect to the end of the marked areas.}
-\label{change_to_marked}
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/transition_to_insignificance_problem.pdf}
+\caption{
+Problems at significance boundary regions highlighted with red ovals.
+The beading approach from the significant region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the center bottom.
+}
+\label{transition_to_insignificance_problem}
 \end{figure}
 
-It impossible for three marked edges to come together.
-(Simple case) If 2 edges of the MAT meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
-However, what if we connect two marked segments using a small non-marked segment?
-There is a distance limit based on \cref{distance_ratio_limit}:
-the connecting segment is always larger in Euclidean distance than the difference in MAT distance.
+The transition length of these transitions to insignificance is determined by the fractional difference in bead count between the two beadings:
+if $v.B^* < n$ then $t = t(n) . (R(v) - v.L_n)$
+otherwise $t = t(n) . (1 - (R(v) - v.L_n))$,
+where $n = \argmax_i v.L_i < R(v)$.
+At a distance $t$ from $v$ along significant bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the VQ requirements.
 
-\subsubsection{Introduce joints at transition ends}
-At the locations $v$ of prefered width, i.e. when $R(v) = p(b(R(v)))$.
-We discretize the distance measure field piecewise linear.
-In \cref{distance_rounding_transition} we have one piece at MAT dist $0.0$ from bar $0$ to bar $2.5$, than a piece increasing from MAT dist $0.0$ to $1.0$ from bar $2.5$ to $7.5$ etc.
+We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local optimum or another significant region.
+(This propagation is explained in \cref{section_toolpath_extraction}.)
+We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the significant beading to the beading of the insignificant approach entirely.
+For nodes $v_x$ in between $v_0$ and $v$ we interpolate $v_x.B^*$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
 
-At the end of a marked section we round the MAT distance measure to the nearest integer and introduce a joint there and connect it to the outline using a new finger.
-At those places we round the distance measure without applying transitioning, because the end of the transition would lie beyond the marked region.
-
-\paragraph{Note}
-We could introduce bones implicitly.
-Instead of changing the straight skeleton and introducing bones,
-we can simply introduce new vertices on the polygon and generate a new straight skeleton.
-
-\old{
-One could think that this means that the method for introducing joints in the original medial axis should be the same method as used for introducing joints on the newly added fingers connected to the joints introduced in the first step!
-}
-However, the method for introducing joints on the marked regions may differ from the method for introducing joints on the non-marked regions!
+\todo{TODO: implement this! }
+\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
+\todo{Explain beading propagation before transitioning}
 
 \subsection{Toolpath extraction}
+\label{section_toolpath_extraction}
 

### 2019-07-11 4_method.tex
update outdated terminology

@@
 \section{Method}
-The general idea is to generate the medial axis transform and round the distance measures,
+The general idea is similar to generating the medial axis transform and round the distance measures,
 such that an exact integer beads will fit the polygon there
@@
 \item Use a significance measure to mark portions of the skeleton which lie in the center.
-\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
-\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
+\item Determine the bead count values in the significant regions and handle transitions to different bead count values.
+\item Generate ticks along insignificant bones of the skeleton and connect the ticks together to extract the toolpaths.
 \end{enumerate}
 
-\hl{Idea: generate only outer 3 walls, except in marked regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.}
+\hl{Idea: generate only outer 3 walls, except in significant regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.}
 \Cref{wedge_and_infill}
@@
 \begin{itemize}
-\item bones, medial axis segments, arms, fingers, ribs
-\item joints, ticks, medial axis vertices, locations
-\item MAT distance measure
+\item bones, skeleton segment
+\item joints, ticks, vertices, locations
+\item feature radius $R$, $\nicefrac12$ total distance $d$
 \end{itemize}
@@
 \begin{itemize}
-\item marked medial axis segment: vertebra
-\item marked medial axis: spine
-\item non-marked medial axis segment: arm
-\item any medial axis segment: bone
-\item bone introduced to the medial axis: rib
-\item medial axis vert: joint
-\item location of an insets along a bone: tick? locus?
+\item any skeleton segment: bone
+\item skeleton vert: joint
+\item location of an insets along a bone: tick
 \end{itemize}
@@
 \includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
-\caption{Distance based angle estimation. By comparing the euclidean distance between two vertices with the distance measure of the MAT we can skip comparing the angles between the outline segments.}
+\caption{
+Distance based angle estimation.
+By comparing the Euclidean distance between two vertices with the feature radius $R$ we can skip comparing the angles between the outline segments.
+}
 \label{distance_based_angles}
@@
 
-The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices: \cref{distance_ratio_limit}.
+The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: \cref{distance_ratio_limit}.
 
@@
 \includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
-\caption{Minimal Euclidean distance for a given difference in MAT distance measure.}
+\caption{Minimal Euclidean distance for a given difference in feature radius $R$.}
 \label{distance_ratio_limit}
@@
 (Simple case) If 2 edges of the VQ meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
-However, what if we connect two marked segments using a small non-marked segment?
+However, what if we connect two significant segments using a small insignificant segment?
 There is a distance limit based on \cref{distance_ratio_limit}:
@@
 \includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
-\caption{MAT distance remapping.}
+\caption{Feature radius remapping.}
 \label{distance_rounding_transition}
@@
 
-Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be.
-For marked regions / significant regions we have already inroduced joints around the transitions which serve as those locations.
-For non-marked regions / unsignificant regions we can simply apply the beading strategy in order to find the toolpath verts.
+Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be: the \emph{ticks}.
+For significant regions we have already inroduced joints around the transitions which serve as those locations.
+For insignificant regions we can simply apply the beading strategy in order to find the toolpath verts.
 
@@
 See \cref{heterogeneous_joint_generation}.
-For any sequence on non-marked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked medial axis segment.
-Based on the MAT distance $R$ there we place ticks along the non-marked bones following the beading strategy.
+For any sequence on insignificant bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a significant VQ segment.
+Based on the feature radius $R$ there we place ticks along the insignificant bones following the beading strategy.
 

### 2019-07-13 4_method.tex
local maxima bead rounding  (First draft version)

@@
 
+If a local maximum gets an odd bead count this would result in a single dot bead toolpath with zero length.
+This not only forms an exception we would need to account for when extracting toolpath segments,
+it also results in a toolpath which is difficult to manufacture.
+Instead we prevent odd bead counts by either increasing or decresing the bead count based on the prefered widths of those bead counts:
+if $v.B^* \% 2 = 1$ then $v.B^* := \argmin_n |p(n) - R(v)|$.
+
 \subsubsection{Transitioning}

### 2019-07-21 4_method.tex
some lil related work updates

@@
 \subsubsection{Voronoi Quadrangulation}
+\todo{The Voronoi Quadrangulation has already been described in} \cite{Ding2016a}. Section 2.4 Domain Decomposition.
+
 The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}

### 2019-07-21 4_method.tex
use \angle instead of \widehat

@@
 This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the angle $\widehat{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
+The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
 For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.

### 2019-07-21 4_method.tex
fix bisector angle and describe discretization of parabolas

@@
 A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
-if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \sin(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
+if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
 See \cref{distance_based_angles}.
-This ratio can be immediately applied to simple skeleton segments to determine whether they are significant.
-For skeletal segments generated by a polygon vertex and another vertex or line segment, we could exactly determine at which location $\frac{\partial R}{\partial x} > \sin(\alpha_\text{max} / 2)$.
-However, because we have discretized such segments, we can approximate the location by applying our ratio based significance measure on the piecewise linear approximating segments directly.
+This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
+For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
+For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
+and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
+This ensures that the discretization doesn't alter the extent and existance of significant regions.
 
@@
 At the end of such chain $v$ we may need to transition from the former approach to the latter.
-This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \sin(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
+This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
 See \cref{transition_to_insignificance_problem}.

### 2019-07-21 4_method.tex
properties of significance measure

@@
 
-\paragraph{Bead counts}
+\subsubsection{Properties of significant regions}
+A node in the graph can have at most two significant edges.
+For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
+% However, because of some filtering operations this property does not neccesarily hold for the markings.
+The extra edges added to the VD to form the VQ can never be significant because their bisector angle is \SI{0}{\degree} by definition,
+so the nodes of the VQ also have at most two significant edges.
+
+A saddle point is always marked.
+When going from one local maximum to another we must pass through a significant region.
+You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
+This menas that the feature radius function in between marked regions is monotonic.
+This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
+
+From any node in the graph which is not a saddle point there is only a single edge going upward.
+\todo{Explanation / proof needed.}
+%See VoronoiQuadrangulation::filterUnmarkedRegions
+This means that walking up the graph from a marked region to a local maximum follows a single path without branchings.
+
+The two downward edges from a branch point cannot both be significant.
+A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
+This means that all support points lie within a \SI{180}{\degree} range around the node. 
+Suppose the one edge going upward is generated by $p_1$ and $p_3$.
+Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
+so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
+%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.
+
+\subsubsection{Bead counts}
 In order to apply the beading strategy to the VQ

### 2019-07-21 4_method.tex
prove single upward edge property

@@
 
-From any node in the graph which is not a saddle point there is only a single edge going upward.
-\todo{Explanation / proof needed.}
+From any node in the graph which is not a saddle point there is at most a single edge going upward.
+Any branch point $v$ in the VD coincides with the circumcircle of its support $p_1, p_2, p_3$.
+If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
+If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
+and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
+Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
+See \cref{branch_upward_edge_property}.
 %See VoronoiQuadrangulation::filterUnmarkedRegions
-This means that walking up the graph from a marked region to a local maximum follows a single path without branchings.
+This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
+
+\begin{figure}
+\centering
+\includegraphics[width=.4\columnwidth]{sources/method/branch_upward_edge_property.pdf}
+\caption{The radial distance can only increase along one edge around a branch point in the VD.}
+\label{branch_upward_edge_property}
+\end{figure}
 

### 2019-07-25 0_main.tex
MAT distance remapping and the cutoff point for markings
restructure method and give a clear overview
add experimentation sections
big refactor of method
new underline and textcolor macros
rename sections;  section -> subsection etc.
describe tick placement algorithms
add conclusion and future work
add discussion section
rewrite method overview
rewrite transitioning section
intial abstract

@@
 
+	\newcommand{\degree}{^\circ}
+
 	\usepackage[binary-units]{siunitx} % mm and stuff
@@
 	\usepackage{units} % \nicefrac{3}{8}
+
+	\DeclareMathOperator*{\argmax}{arg\,max}
+	\DeclareMathOperator*{\argmin}{arg\,min}
+
+	\DeclareMathOperator{\abs}{abs} % absolute function
 
@@
 
+	\usepackage{listings} % for listing C++ code instead of pseudocode
+	\lstset{ 
+      breaklines=true,                 % sets automatic line breaking
+    }
+
+	\newcommand{\wmin}{w_\text{min}}
+	\newcommand{\wmax}{w_\text{max}}
+	\newcommand{\wout}{w_\text{out}}
+	\newcommand{\win}{w_\text{in}}
+
     % \usepackage[disable]{todonotes} % notes not showed  
@@
 
-%    \newcommand{\todo}[1]{\hl{#1}}
+    \newcommand{\todo}[1]{\hl{#1}}
 
-%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
-%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
-%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
-%	\newcommand{\charlie}[1]{\textcolor[rgb]{0, 0.2, 0}{\todo{[Charlie: #1]}}}
-%	\newcommand{\toberemoved}[1]{\textcolor[rgb]{0.9, 0, 0.2}{\st{#1}}}
-%	\newcommand{\inserttext}[1]{\textcolor[rgb]{0, 0.7, 0}{\hl{#1}}}
-%	\newcommand{\replacewith}[2]{\toberemoved{#1}\inserttext{#2}}
+	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
+	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
+	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
 
-    \newcommand{\changed}[1]{#1}
-    %\newcommand{\changed}[1]{\hl{#1}}
+	\newcommand{\old}[1]{\textcolor{gray}{#1}}
+
+	\setulcolor{red}
+
+	\usepackage[normalem]{ulem} % squigly underline
 
@@
 
-\title{Title}
+\title{A robust framework for variable extrusion width concentric toolpath generation}
 
-\author{Paper ID: xxx}
+%\author{Paper ID: xxx}
 
@@
 \begin{abstract}
-abstract
+3D printing techniques such as Fused Deposition Modeling (FDM) works by depositing material along paths which lie in horizontal layers.
+The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.
+Filling the outlines with extruded material densely and accurately is important for fabricating parts accurately and stiffly.
+Especially thin parts require an accurate dense filling, such as casings for electronics, blowmolding prototypes, (architectural) models and some tpyes of microstructure.
+
+A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
+In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
+Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
+However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size.
+We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
+
+Our method determines the number of extrusion beads at each location, then it generates the beads from the center of the outline shape outward and finally connects all bead together to form extrusion toolpaths.
+We determine the middle of the shape by applying a significance measure to the skeleton of the outline polygon, use the beading strategy to determine the optimal number of beads in those middle regions and derive the toolpath locations as distances from the middle parts of the skeleton from the beading strategy.
+Because the skeletal structure decomposes the outline domain into simple cells, the toolpaths can be generated by drawing straight line segments along each cell.
+
+Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
+We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
+We show that our implementation exhibits computation times in the same order of magnitude as the naive method.
 \end{abstract}
@@
 
-% \temp{Table of contents just for reviewing purposes
-% \tableofcontents
-% }
+ \temp{%Table of contents just for reviewing purposes
+ \tableofcontents
+ }
 
@@
 
+\input{6_validation}
+
+\input{8_discussion}
+
 \input{10_applications}
+
+\input{12_conclusions_future_work}
 

### 2019-07-26 4_method.tex
new VQ images

@@
 \begin{figure}
-\begin{subfigure}{0.3\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/MAT_example.pdf}
-\caption{MAT}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/Voronoi_example.pdf}
-\caption{Limited VD}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/gMAT_example.pdf}
-\caption{VQ}
-\end{subfigure}
+\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
 \caption{
-Relation between the medial axis, the limited Voronoi Diagram and the Voronoi quadrangulation: MAT $\subset$ Limited VD $\subset$ VQ.
-Significant parts of the skeleton are visualized in shades of red, insignificant regions in grey and blue.
+Skeletonization of an outline shape (black).
+Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Voronoi Quadrangulation (red, green and gray): MAT $\subset$ Limited VD $\subset$ VQ.
 }
@@
 \centering
-\includegraphics[width=.5\columnwidth]{sources/method/parabola_dip.pdf}
+%\begin{subfigure}{0.45\textwidth}
+%\includegraphics[width=\columnwidth]{sources/method/parabola_dip.pdf}
+%\caption{asf}
+%\end{subfigure}
+%\begin{subfigure}{0.45\textwidth}
+\includegraphics[width=\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
+%\caption{Transitioning}
+%\end{subfigure}
 \caption{
-Construction of a VQ:
-the MAT in red,
-the bones added by VD in purple,
-the bones added by VQ in orange,
-the bones added by discretization in dashed lines.
-The 3 types of quad are highlighted.
+Voronoi quadrangulation domain decomposition.
+Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
+Parabolic medial axis segments are discretized and likewise for segments generated by two concave outline vertices, because the feature radius (black text in microns) doesn't increase linearly along those segments.
+The blue segments are significant according to $\alpha_\text{max} = 135\degree$.
 }

### 2019-07-26 4_method.tex
new terminology figure
move beading strategy to toolpath extraction section
We don't need the toolpath locations L until that point.
remove section on rounding local maxima odd bead count because we don't do that any more
we dont do it anymore because it deviates from the core method too much and introduces all kinds of horrible edge cases

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/legend_double_wedge_example.pdf}
+\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
 \caption{Explanation of terms.}
@@
 \end{itemize}
-
-\subsection{Beading strategy}
-First we determine how we should fill a 	polygon with constant width with a number of beads.
-We want to fit an exact whole number of beads in order to prevent a gap being generated.
-We consider only half of the polygon, because our beading strategy should be symmetrical.
-
-We define a beading strategy as the following set:
-$$
-\left\{ b(d), p(n), W(n, d), L(n, d), t(n), \alpha_{\text{max}} \right\}
-$$
-where
-$b(d)$ gives the optimal bead count to cover a total distance of $d$,
-$p(n)$ gives the optimal total distance of a given bead count $n$,
-$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
-$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
-$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads
-and
-$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.
-
-We call a distance $d$ `preferred' when $d = p(b(d))$
-For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
-
-The following restrictions hold:
-\begin{itemize}
-\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
-\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
-\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
-\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
-%\item $b \left( p(n) \right) = n$ % follows from the above!
-\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
-\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
-\end{itemize}
-
-The angle requirement ensures that there is never a 3-way junction of significant bones.
-
-By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading, which is defined as the following set:
-$$
-\left\{ d, w_i, l_i  \right\}
-$$
-where
-$d = 2 R(v)$ is the total distance associated with $v$,
-$w_i$ is the bead width of the bead with index $i$
-end
-$l_i$ is the distance of the toolpath location of bead $i$ from the outline.
 
@@
 
-If a local maximum gets an odd bead count this would result in a single dot bead toolpath with zero length.
-This not only forms an exception we would need to account for when extracting toolpath segments,
-it also results in a toolpath which is difficult to manufacture.
-Instead we prevent odd bead counts by either increasing or decresing the bead count based on the prefered widths of those bead counts:
-if $v.B^* \% 2 = 1$ then $v.B^* := \argmin_n |p(n) - R(v)|$.
-
 \subsubsection{Transitioning}
@@
 \label{section_toolpath_extraction}
+
+\subsection{Beading strategy}
+First we determine how we should fill a 	polygon with constant width with a number of beads.
+We want to fit an exact whole number of beads in order to prevent a gap being generated.
+We consider only half of the polygon, because our beading strategy should be symmetrical.
+
+We define a beading strategy as the following set:
+$$
+\left\{ b(d), p(n), W(n, d), L(n, d), t(n), \alpha_{\text{max}} \right\}
+$$
+where
+$b(d)$ gives the optimal bead count to cover a total distance of $d$,
+$p(n)$ gives the optimal total distance of a given bead count $n$,
+$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
+$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
+$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads
+and
+$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.
+
+We call a distance $d$ `preferred' when $d = p(b(d))$
+For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
+
+The following restrictions hold:
+\begin{itemize}
+\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
+\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
+\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
+\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
+\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
+%\item $b \left( p(n) \right) = n$ % follows from the above!
+\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
+\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
+\end{itemize}
+
+The angle requirement ensures that there is never a 3-way junction of significant bones.
+
+By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading, which is defined as the following set:
+$$
+\left\{ d, w_i, l_i  \right\}
+$$
+where
+$d = 2 R(v)$ is the total distance associated with $v$,
+$w_i$ is the bead width of the bead with index $i$
+end
+$l_i$ is the distance of the toolpath location of bead $i$ from the outline.
 

### 2019-07-26 4_method.tex
move single_bead_strategy figure down to where its used
remove terminology and clean up method overview

@@
 
-\begin{figure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
-\caption{Overview}
-\label{single_bead_strategy_overview}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
-\caption{Travel order}s
-\end{subfigure}
-\caption{We can do single-bead segments. Blue is travel move.}
-\label{single_bead_strategy}
-\end{figure}
-
 \subsection{Method Overview}
 The global idea is that we locally decide on the number of beads everywhere in the input shape, then apply a beading strategy to determine the widths of the beads and then generate the toolpath locations and widths from this.
-We decide on a bead count at locations which lie in the middle of the shape in some sense to be defined.
+We decide on a bead count at locations which lie in centeral positions of the shape in some sense to be defined below.
 The beading strategy then gives us the beading widths and locations in between those center locations and the outline.
@@
 \item Use a significance measure to mark portions of the skeleton which lie in the center.
-\item Determine the bead count values in the significant regions and handle transitions to different bead count values.
-\item Generate ticks along insignificant bones of the skeleton and connect the ticks together to extract the toolpaths.
+\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
+\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to form the toolpaths.
 \end{enumerate}
-
-\hl{Idea: generate only outer 3 walls, except in significant regions where the distance $R < 5 \win$, so as to prevent jagged infill lines.}
-\Cref{wedge_and_infill}
-
-\hl{Filter beading number in order to prevent regions with a lot of back and forth transitions.}
-
-\subsection{Terminology}
-For an explanation of the terms used, see \cref{legend}.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
-\caption{Explanation of terms.}
-\label{legend}
-\end{figure}
-
-\hl{We need consistent terminology and symbols which adhere to standards in literature.}
-The following synonym groups are used here which are not yet checked with existing literature':
-\begin{itemize}
-\item bones, skeleton segment
-\item joints, ticks, vertices, locations
-\item feature radius $R$, $\nicefrac12$ total distance $d$
-\end{itemize}
-
-Based on the straight skeleton naming, I would like to introduce a new consistent terminology:
-\begin{itemize}
-\item any skeleton segment: bone
-\item skeleton vert: joint
-\item location of an insets along a bone: tick
-\end{itemize}
 
@@
 
+\begin{figure}
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
+\caption{Overview}
+\label{single_bead_strategy_overview}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth}
+\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
+\caption{Travel order}s
+\end{subfigure}
+\caption{We can do single-bead segments. Blue is travel move.}
+\label{single_bead_strategy}
+\end{figure}
+
 When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.

### 2019-07-26 4_method.tex
rename tick => junction
conforms with code
and a tick sounds too small for a whole bead

@@
 \item Determine the bead count values in the marked regions and handle transitions to different bead count values.
-\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to form the toolpaths.
+\item Generate junctions along non-marked bones of the skeleton and connect the junctions together to form the toolpaths.
 \end{enumerate}
@@
 
-\subsubsection{Tick placement}
-\hl{Change terminology: location $\to$ junction?}
+\subsubsection{Junction placement}
 
-Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be: the \emph{ticks}.
+Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be: the \emph{junctions}.
 For significant regions we have already inroduced joints around the transitions which serve as those locations.
@@
 For any sequence on insignificant bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a significant VQ segment.
-Based on the feature radius $R$ there we place ticks along the insignificant bones following the beading strategy.
+Based on the feature radius $R$ there we place junctions along the insignificant bones following the beading strategy.
 
@@
 After the beading strategy has been applied we have a beading associated with each significant node as well as each node with locally optimal $R$.
-In order to determine the tick locations of quads which don't contain any such node, we propagate the beading information down.
+In order to determine the junction locations of quads which don't contain any such node, we propagate the beading information down.
 We therefore sort all quads on their highest $R$-value and process the high $R$ quads first.
@@
 
-We can then process all bones in arbitrary order and generate the ticks along those bones.
-See \cref{alg_tick_generation}.
+We can then process all bones in arbitrary order and generate the junctions along those bones.
+See \cref{alg_junction_generation}.
 
 \begin{algorithm}
-\caption{Tick generation}
-\label{alg_tick_generation}
+\caption{Junction generation}
+\label{alg_junction_generation}
 \lstset{language=C++}
@@
   Point junction(a + ab * (bead_R - start_R) / (end_R - start_R));
-  ticks.emplace_back(junction, beading->bead_widths[junction_idx], junction_idx);
+  junctions.emplace_back(junction, beading->bead_widths[junction_idx], junction_idx);
 }
@@
 
-We then generate bead segments for each quad by connecting together the ticks of the same index.
-If the amount of ticks on both sides of the quad is not the same then this quad is in a transition and we leave one tick unconnected.
+We then generate bead segments for each quad by connecting together the junctions of the same index.
+If the amount of junctions on both sides of the quad is not the same then this quad is in a transition and we leave one junction unconnected.
 

### 2019-07-26 4_method.tex
reformulate: significant => marked
because we filter unmarked regions

@@
 \item Determine the bead count values in the marked regions and handle transitions to different bead count values.
-\item Generate junctions along non-marked bones of the skeleton and connect the junctions together to form the toolpaths.
+\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the toolpaths.
 \end{enumerate}
@@
 The bisector angle is therefore an exact measure of the amount of overfill and underfill.
-Contrary to related literature we will \emph{keep} the insignificant regions of the skeleton.
+Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
 Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.
@@
 and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
-This ensures that the discretization doesn't alter the extent and existance of significant regions.
+This ensures that the discretization doesn't alter the extent and existence of significant regions.
 
@@
 In order to apply the beading strategy to the VQ
-we assign each significant node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
+we assign each marked node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
 
 We also assign a bead count $v.B^*=b(R(v))$ to all nodes $v$ which are local maxima, i.e. the $v$ for which $\forall v_\text{n} \in v.\text{neighborhood} : R(v) > R(v_\text{n})$. 
-This prevents the single overfill or underfill region in non-significant regions.
+This prevents the single overfill or underfill region in unmarked regions.
 See \cref{rounded_vs_unrounded}.
@@
 We then assign $v_0.B^* = n$ and $v_1.B^* = n + 1$.
-If there is any node $v_x$ in between $v_0$ and $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the Euclidean distance measured along the significant bone(s).
+If there is any node $v_x$ in between $v_0$ and $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the Euclidean distance measured along the marked bone(s).
 See \cref{distance_rounding_transition}.
@@
 
-\subsubsection{Transitioning to insignificance}
-In significant regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in insignificant regions the beading is only governed by the beading of locations with locally optimal feature radius.
-Significant bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$.
+\subsubsection{Beading conflicts}
+In marked regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally optimal feature radius.
+Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
 At the end of such chain $v$ we may need to transition from the former approach to the latter.
-This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the significant region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
-See \cref{transition_to_insignificance_problem}.
+This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
+See \cref{beading_conflict_problem}.
 
@@
 \caption{
-Problems at significance boundary regions highlighted with red ovals.
-The beading approach from the significant region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the center bottom.
+Problems at the boundary of marked regions highlighted with red ovals.
+The beading approach from the marked region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the local maximum in the bottom center.
 }
-\label{transition_to_insignificance_problem}
+\label{beading_conflict_problem}
 \end{figure}
 
-The transition length of these transitions to insignificance is determined by the fractional difference in bead count between the two beadings:
+The transition length of these transitions to unmarked regions is determined by the fractional difference in bead count between the two beadings:
 if $v.B^* < n$ then $t = t(n) . (R(v) - v.L_n)$
@@
 where $n = \argmax_i v.L_i < R(v)$.
-At a distance $t$ from $v$ along significant bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the VQ requirements.
+At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the VQ requirements.
 
-We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local optimum or another significant region.
+We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local optimum or another marked region.
 (This propagation is explained in \cref{section_toolpath_extraction}.)
-We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the significant beading to the beading of the insignificant approach entirely.
+We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
 For nodes $v_x$ in between $v_0$ and $v$ we interpolate $v_x.B^*$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
@@
 
-The angle requirement ensures that there is never a 3-way junction of significant bones.
+The angle requirement ensures that there is never a 3-way junction of significant bones. \todo{not true anymore}
 
@@
 Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be: the \emph{junctions}.
-For significant regions we have already inroduced joints around the transitions which serve as those locations.
-For insignificant regions we can simply apply the beading strategy in order to find the toolpath verts.
+For marked regions we have already inroduced joints around the transitions which serve as those locations.
+For unmarked regions we can simply apply the beading strategy in order to find the toolpath verts.
 
@@
 See \cref{heterogeneous_joint_generation}.
-For any sequence on insignificant bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a significant VQ segment.
-Based on the feature radius $R$ there we place junctions along the insignificant bones following the beading strategy.
+For any sequence on unmarked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked VQ segment.
+Based on the feature radius $R$ there we place junctions along the unmarked bones following the beading strategy.
 
@@
 \subsubsection{Toolpath extraction algorithm}
-After the beading strategy has been applied we have a beading associated with each significant node as well as each node with locally optimal $R$.
+After the beading strategy has been applied we have a beading associated with each marked node as well as each node with locally optimal $R$.
 In order to determine the junction locations of quads which don't contain any such node, we propagate the beading information down.
@@
 When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.
-These polylines generally form closed polygons, but at significant regions of the VQ the toolpaths consist of single bead polyline toolpaths.
+These polylines generally form closed polygons, but at marked regions of the VQ the toolpaths consist of single bead polyline toolpaths.
 See \cref{single_bead_strategy}.

### 2019-07-26 4_method.tex
rewrite method overview

@@
 \section{Method}
-The general idea is similar to generating the medial axis transform and round the distance measures,
-such that an exact integer beads will fit the polygon there
-so that there is never a gap region left over in the middle of the polygon.
+When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
+Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
+Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
+We decide on a bead count at locations which lie in centeral positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the centeral regions outward.
 
-We round to integer multiples of half the nozzle width so as to allow single-bead segments, rather than only having polygonal insets.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/rounded_vs_unrounded.pdf}
-\caption{Toolpaths employing dist rounding vs without.}
-\label{rounded_vs_unrounded}
-\end{figure}
-
-\subsection{Method Overview}
-The global idea is that we locally decide on the number of beads everywhere in the input shape, then apply a beading strategy to determine the widths of the beads and then generate the toolpath locations and widths from this.
-We decide on a bead count at locations which lie in centeral positions of the shape in some sense to be defined below.
-The beading strategy then gives us the beading widths and locations in between those center locations and the outline.
-These beadings are then used to generate the toolpath junctions, which are connected together to form the extrusion toolpaths with varying width.
+What constitutes an optimal distribution is governed by a beading strategy.
+Our framework allows for different beading strategies which can optimize for different criteria.
 
 \begin{enumerate}
-\item Compute a skeletonization of the outline shape based on the Voronoi diagram.
-\item Use a significance measure to mark portions of the skeleton which lie in the center.
+\item Compute a skeleton of the outline shape based on the Voronoi diagram.
+\item Use a significance measure to mark regions of the skeleton which are central.
 \item Determine the bead count values in the marked regions and handle transitions to different bead count values.
-\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the toolpaths.
+\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the extrusion beads.
 \end{enumerate}

### 2019-07-29 12_conclusions_future_work.tex
list of concluding remarks

@@
 \section{Conclusion and future work}
-conclusion: reiterate abstract
+
+\begin{itemize}
+\item Accurate filling using few/small overfill and underfill areas
+\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
+\item Our framework is able to emulate several previously proposed methods
+\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
+\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
+\item The computation times are approximately 3 times as fast as the state of the art method for naive toolpath generation employing constant width
+\item (depending on what we do in the validation chapter) The produced parts employing our method are more stiff compared to other methods.
+\end{itemize}
 
@@
 Generate thicker bead widths near sharp corners in order to mimic limitations in the extrusion process.
+Allow for adjusting the toolpath widths to local part curvature.
+
+Allow for information sharing between the layers.

### 2019-07-29 4_method.tex
reintroduce terminology figure
accidentally removed it
rewrite skeletonization section and rename Voronoi Quadrangulation > Skeletal Trapezoidation

@@
 \begin{enumerate}
-\item Compute a skeleton of the outline shape based on the Voronoi diagram.
+\item Compute a skeleton of the outline shape.
 \item Use a significance measure to mark regions of the skeleton which are central.
@@
 
-\subsection{Skeletonization}
-In order to apply the beading strategy to an arbitrary outline polygon we look at the skeleton of the polygon.
-There are several possible skeletonal structures we could consider.
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
+\caption{Explanation of terms.}
+\label{legend}
+\end{figure}
 
-\subsubsection{Background}
+\subsection{Shape decomposition}
+The shape decomposition we employ on the outline shape of a layer is based on the medial axis.
+We then further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.
+
+\subsubsection{Medial axis transform}
 One of the most commonly used skeletonizations of a shape is the medial axis.
 The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
+We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
 See \cref{MAT_explanation}.
+The resulting skeleton consists of straight segments and parabolic segments connected to each other at \emph{branch nodes}.
 
@@
 Skeletonization of an outline shape (black).
-Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Voronoi Quadrangulation (red, green and gray): MAT $\subset$ Limited VD $\subset$ VQ.
+Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
 }
@@
 
-\subsubsection{Voronoi Quadrangulation}
-\todo{The Voronoi Quadrangulation has already been described in} \cite{Ding2016a}. Section 2.4 Domain Decomposition.
+\subsubsection{Skeletal trapezoidation}
+We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
+Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
+The resulting skeleton decomposes the outline shape into trapezoids and triangles.
+We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
+(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
+See \cref{skeletonization_comparison}.
 
-The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape. \cite{lee1982medial}
-First we throw away all locations in the Voronoi diagram which fall outside the boundary shape.
-We can then obtain the medial axis by further reducing the Voronoi bones connected to a concave corner in the boundary shape.
+The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all segments of the VD falling outside of the outline shape and throwing away the bones connected to concave vertices in the outline shape.
+\cite{lee1982medial}
+However, the concave vertices are precisely in the support of the nodes to which those bones connect.
+This means we can efficiently compute the ST from the VD by removing all segments which lie outside the outline shape and add radial bones to the nodes from there.
+See \cref{skeletonization_comparison}.
 
-However, instead of removing bones from the Voronoi diagram we will introduce more bones such that the skeleton discretizes the boundary shape into quads within which the $R$ can be interpolated linearly.
-We call the resulting skeletonization the \emph{Voronoi Quadrangulation} (VQ).
-See \cref{skeletonization_comparison}.
-The VQ greatly simplifies the processing required downstream in our framework.
-
-In order to generate the VQ, we start by generating a normal Voronoi Diagram and remove all segments which lie outside of the boundary shape.
-We then introduce bones such that each node in the VQ is directly connected to the outline via a single bone:
-each node in the VQ is connected to the closest points on the boundary (its \emph{support}).
-As such the VQ divides the polygon in quads consisting of 1 outline segment and 3 bones, one of which is not directly connected to the outline.
-However some of these quads are triangles, as can be seen in \cref{discretization}.
-
-We then also discretize parabolic bones and bones generated by two concave outline vertices into approximately equidistant segments.
+We then also discretize parabolic segments and segments generated by two concave outline vertices into approximately equidistant segments.
 See \cref{discretization}.
-That way we can approximate the feature radius $R$ in between two nodes $v_0$ and $v_1$ in the VQ by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-Furthermore, we can linearly interpolate the distance field of a quad $p_0v_0v_1p_1$ (where $p_0$ and $p_1$ lie on the outline shape):
-For a point $a \in p_0v_0$ and a point $b \in p_1v_1$ for which $R(a) = R(b)$ we have that all points in the line segment $ab$ have the same feature radius $R$.
+That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
+If we then map those feature radii into Z coordinates, we obtain a 3D model which intuitively shows how our decomposition captures the distance field of the outline shape: \cref{mat_3d}.
 
@@
 \caption{
-Voronoi quadrangulation domain decomposition.
+Skeletal trapezoidation domain decomposition.
 Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
@@
 \label{discretization}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/method/mat_3d_blender_render.png}
+\caption{
+Visualization of the distance field function as captured by the skeletal trapezoidation.
+}
+\label{mat_3d}
 \end{figure}
@@
 This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.
-(Simple case) If 2 edges of the VQ meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
+(Simple case) If 2 edges of the ST meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
 However, what if we connect two significant segments using a small insignificant segment?
@@
 % However, because of some filtering operations this property does not neccesarily hold for the markings.
-The extra edges added to the VD to form the VQ can never be significant because their bisector angle is \SI{0}{\degree} by definition,
-so the nodes of the VQ also have at most two significant edges.
+The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
+so the nodes of the ST also have at most two significant edges.
 
@@
 \subsubsection{Bead counts}
-In order to apply the beading strategy to the VQ
+In order to apply the beading strategy to the ST
 we assign each marked node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
@@
 The transition will be placed anchored on each location $v$ where $R(v) = \nicefrac12 b^{-1}(n+1)$ for any lower bead count $n$.
-At the start $v_0$ and end $v_1$ of the transition we introduce a new node in the skeleton and connect it to the outline as per the VQ requirement.
+At the start $v_0$ and end $v_1$ of the transition we introduce a new node in the skeleton and connect it to the outline as per the ST requirement.
 We then assign $v_0.B^* = n$ and $v_1.B^* = n + 1$.
@@
 \subsubsection{Beading conflicts}
-In marked regions of the VQ we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally optimal feature radius.
+In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally optimal feature radius.
 Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
@@
 where $n = \argmax_i v.L_i < R(v)$.
-At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the VQ requirements.
+At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the ST requirements.
 
@@
 See \cref{heterogeneous_joint_generation}.
-For any sequence on unmarked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked VQ segment.
+For any sequence on unmarked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked ST segment.
 Based on the feature radius $R$ there we place junctions along the unmarked bones following the beading strategy.
@@
 After the beading strategy has been applied we have a beading associated with each marked node as well as each node with locally optimal $R$.
-In order to determine the junction locations of quads which don't contain any such node, we propagate the beading information down.
-We therefore sort all quads on their highest $R$-value and process the high $R$ quads first.
-The beading information is then passed down along the bones of the quad to lower $R$ nodes if those nodes don't already have a beading associated.
+In order to determine the junction locations of trapezoids which don't contain any such node, we propagate the beading information down.
+We therefore sort all trapezoids on their highest $R$-value and process the high $R$ trapezoids first.
+The beading information is then passed down along the bones of the trapezoid to lower $R$ nodes if those nodes don't already have a beading associated.
 
@@
 \begin{algorithmic}
-\State quads.sortOn(getHighestR())
-\ForAll{$q \in$ quads}
+\State trapezoids.sortOn(getHighestR())
+\ForAll{$q \in$ trapezoids}
 	\State $v_\text{max} = q$.getHighestR()
@@
 
-We then generate bead segments for each quad by connecting together the junctions of the same index.
-If the amount of junctions on both sides of the quad is not the same then this quad is in a transition and we leave one junction unconnected.
+We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
+If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one junction unconnected.
 
@@
 When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.
-These polylines generally form closed polygons, but at marked regions of the VQ the toolpaths consist of single bead polyline toolpaths.
+These polylines generally form closed polygons, but at marked regions of the ST the toolpaths consist of single bead polyline toolpaths.
 See \cref{single_bead_strategy}.

### 2019-07-29 4_method.tex
rework MAT section

@@
 \subsection{Shape decomposition}
-The shape decomposition we employ on the outline shape of a layer is based on the medial axis.
-We then further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.
+The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
+Starting from the medial axis we further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.
 
@@
 One of the most commonly used skeletonizations of a shape is the medial axis.
-The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \todo{[citation needed]}
+The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
 We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
+The resulting skeleton consists of straight segments and parabolic segments which form a graph.
+See \cref{MAT_explanation_circles}.
+
+Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is disctoninuous,
+or it can be defined as the locations where wavefront propagating from the outline shape make sharp corners. \cite{blum1967transformation}
+This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wavefronts from the outline.
+The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
 See \cref{MAT_explanation}.
-The resulting skeleton consists of straight segments and parabolic segments connected to each other at \emph{branch nodes}.
 
-``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.
-Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.''
-\cite{lee1982medial}
+%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
+``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
+The medial axis along with the feature radius values along the skeleton combine into a complete shape descriptor, called the medial axis transform (MAT).
+Feature radius and node locations of segments will be used below to analyse the shape locally.
 
-The medial axis along with the feature radius combine into a complete feature decsriptor, called the medial axis transform (MAT).
-The MAT can unambiguously recreate the input shape exactly. \todo{[citation needed]}
-
-\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
-\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
+%\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
+%\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
 
@@
 \centering
-\includegraphics[width=.9\columnwidth]{sources/intro/medial_axis_Kao.png}
-\caption{MAT explanation by \citeauthor{kao1998optimal}}
+\begin{subfigure}{0.3\columnwidth}
+\centering
+\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
+\caption{Circles}
+\label{MAT_explanation_circles}
+\end{subfigure}
+\begin{subfigure}{0.3\columnwidth}
+\centering
+\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
+\caption{Wavefronts}
+\end{subfigure}
+\begin{subfigure}{0.3\columnwidth}
+\centering
+\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
+\caption{Cones}
+\end{subfigure}
+\caption{
+Medial axis representations.
+The medial axis can be defined in terms of the the number of support points of the inscribed circles,
+as the pinch sites in wavefronts
+or as ridges in a volume defined by the union of cones.
+}
 \label{MAT_explanation}
@@
 \begin{figure}
+\begin{subfigure}{0.3\columnwidth}
+\centering
+\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
+\caption{Simple case}
+\label{shape_decomposition_simple}
+\end{subfigure}
+\begin{subfigure}{0.65\columnwidth}
 \includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
+\caption{Complex case employing discretization}
+\label{shape_decomp_complex}
+\end{subfigure}
 \caption{
@@
 \label{skeletonization_comparison}
+\end{figure}
+
+\begin{figure} \centering
+\includegraphics[width=.75\columnwidth]{sources/method/mat_3d_blender_render.png}
+\caption{
+Visualization of the distance field function as captured by the skeletal trapezoidation.
+}
+\label{mat_3d}
 \end{figure}
@@
 (The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
-See \cref{skeletonization_comparison}.
+See \cref{shape_decomposition_simple}.
 
@@
 We then also discretize parabolic segments and segments generated by two concave outline vertices into approximately equidistant segments.
-See \cref{discretization}.
+See \cref{discretization} and \cref{shape_decomp_complex}.
 That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-If we then map those feature radii into Z coordinates, we obtain a 3D model which intuitively shows how our decomposition captures the distance field of the outline shape: \cref{mat_3d}.
+This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical represenatation of the medial axis; see \cref{mat_3d}.
 
@@
 \label{discretization}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/mat_3d_blender_render.png}
-\caption{
-Visualization of the distance field function as captured by the skeletal trapezoidation.
-}
-\label{mat_3d}
 \end{figure}

### 2019-07-29 4_method.tex
revamp distance_based_angles and distance_ratio_limit figures

@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
+\begin{figure} \centering
+\begin{subfigure}{0.45\columnwidth} \centering
+\includegraphics[height=.7\columnwidth]{sources/method/distance_based_angles.pdf}
+\caption{Significance}
+\label{distance_based_angles}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth} \centering
+\includegraphics[height=.7\columnwidth]{sources/method/distance_ratio_limit.pdf}
+\caption{Distance}
+\label{distance_ratio_limit}
+\end{subfigure}
 \caption{
-Distance based angle estimation.
-By comparing the Euclidean distance between two vertices with the feature radius $R$ we can skip comparing the angles between the outline segments.
+Properties of feature radius $R$.
+Part of outline shape in thick black,
+skeleton in red,
+inscribed circle in gray,
+radii in dashed lines.
+The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
+The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
 }
-\label{distance_based_angles}
 \end{figure}
@@
 The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: \cref{distance_ratio_limit}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
-\caption{Minimal Euclidean distance for a given difference in feature radius $R$.}
-\label{distance_ratio_limit}
-\end{figure}
 

### 2019-07-29 4_method.tex
rewrite section on properties of significance measure

@@
 \subsection{Beading}
-We assign a bead count to each node in the skeleton which is connected to a bone which is in `the center' of the shape
-and also to each node with locally optimal feature radius $R$.
-Around regions where the bead count changes we introduce transition regions.
+We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
+Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.
 
 \subsubsection{Significance measure}\label{sec:significance_measure}
-Places where the naive concentric toolpathing strategy would create large underfilling and overfilling areas are locations which intuitively look like `the center' of the shape.
+Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which intuitively look like `the center' of the shape.
 This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$. \cite{attali1996modeling}
+The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
 For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
 See \cref{naive_overfill_underfill}.
-The bisector angle is therefore an exact measure of the amount of overfill and underfill.
-Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
-Our framework will employ a different toolpathing strategy to prevent overfill and underfill areas if they would be so large that $\alpha > \alpha_\text{max}$.
+The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
+%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
+We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
+Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.
 
@@
 
-A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance.
+A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
 if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
+This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
 See \cref{distance_based_angles}.
@@
 
-The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: \cref{distance_ratio_limit}.
+\subsubsection{Properties of significant regions}
+The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: see \cref{distance_ratio_limit}.
+The distance $|v - p| = \Delta R$ exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.
 
-Any node in the skeleton can have at most two significant bones connected to it, because we have limited $\alpha_\text{max} > 120\degree$,
-while the corners of a triangle can only add up to \SI{180}{\degree}.
-\todo{TODO: make figure which clearly shows this!}
-This results in the fact that we will never have 3-way intersections of non-closed extrusion toolpaths.
-(Simple case) If 2 edges of the ST meet then 3 outline segments are involved; lines through those segments form a triangle which cannot have more than two angles less than \SI{60}{\degree}.
-However, what if we connect two significant segments using a small insignificant segment?
-There is a distance limit based on \cref{distance_ratio_limit}:
-the connecting segment is always larger in Euclidean distance than the difference in feature radius $R$.
-
-\subsubsection{Properties of significant regions}
+\iffalse
+% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
 A node in the graph can have at most two significant edges.
@@
 so the nodes of the ST also have at most two significant edges.
+\fi
 
-A saddle point is always marked.
-When going from one local maximum to another we must pass through a significant region.
+A saddle point is always marked, i.e.\
+when traversing the skeletal graph from one locally maximum $R$ to another we must pass through a significant region.
 You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
-This menas that the feature radius function in between marked regions is monotonic.
+This means that the feature radius function in between marked regions is always monotonic.
 This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
@@
 From any node in the graph which is not a saddle point there is at most a single edge going upward.
-Any branch point $v$ in the VD coincides with the circumcircle of its support $p_1, p_2, p_3$.
+Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_1, p_2, p_3$.
 If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
@@
 
+\iffalse
+% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
 The two downward edges from a branch point cannot both be significant.
@@
 %so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.
+\fi
 

### 2019-07-30 4_method.tex
lil fixes to properties of significance measure

@@
 The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: see \cref{distance_ratio_limit}.
-The distance $|v - p| = \Delta R$ exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.
+The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.
 
@@
 %See VoronoiQuadrangulation::filterUnmarkedRegions
+Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
 This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
@@
 \includegraphics[width=.4\columnwidth]{sources/method/branch_upward_edge_property.pdf}
-\caption{The radial distance can only increase along one edge around a branch point in the VD.}
+\caption{The radial distance can only increase along one edge around a branch point in the medial axis.}
 \label{branch_upward_edge_property}

### 2019-07-30 4_method.tex
make properties of significant regions into Lemmas

@@
 \subsubsection{Properties of significant regions}
-The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices: see \cref{distance_ratio_limit}.
+%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
+The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
+See \cref{distance_ratio_limit}.
 The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.
@@
 
+\begin{lemma}\label{saddle_points_are_marked}
 A saddle point is always marked, i.e.\
-when traversing the skeletal graph from one locally maximum $R$ to another we must pass through a significant region.
+when traversing the skeletal graph from one locally maximal $R$ to another we must pass through a significant region.
+\end{lemma}
+\begin{proof}
 You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
@@
 This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
+\end{proof}
 
+\begin{lemma}\label{single_upward_edge}
 From any node in the graph which is not a saddle point there is at most a single edge going upward.
+\end{lemma}
+\begin{proof}
 Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_1, p_2, p_3$.
@@
 This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
+\end{proof}
 

### 2019-07-30 4_method.tex
rewrite section on marking filtering and initial bead count

@@
 
+We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
+We also mark whole bones as being central if they are significant according to a common significance measure.
+
 \subsubsection{Significance measure}\label{sec:significance_measure}
@@
 
+\subsubsection{Marking filtering}
+Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
+We then filter out high frequency changes in the marking in order to ensure smooth output toolpaths. 
+We perform filtering on the unmarked regions, so that the properties of significant regions mentioned above remain valid.
+From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}).
+If the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.
+
 \subsubsection{Bead counts}
-In order to apply the beading strategy to the ST
-we assign each marked node $v$ of the skeleton a bead count $v.B^*$ which is initialized to $b(R(v))$, but it is modified in order to prevent discontinuities and remaining gaps.
+In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
+In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
+(The feature diameter is twice the radius.)
+We might choose different functions for $b$ depending on the beading strategy used.
 
-We also assign a bead count $v.B^*=b(R(v))$ to all nodes $v$ which are local maxima, i.e. the $v$ for which $\forall v_\text{n} \in v.\text{neighborhood} : R(v) > R(v_\text{n})$. 
-This prevents the single overfill or underfill region in unmarked regions.
-See \cref{rounded_vs_unrounded}.
+We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
+We also filter unmarked regions where the bead count remains constant.
+\todo{Explaining why would have to refer forward to section about interpolating beadings}
+From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
+If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.
+
+\todo{TODO: figure of basic bead counts left, middle with transition mids, right with transition ends.}
 
@@
 $\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.
+
+\todo{TODO: Replace `distance' with `diameter'.}
 

### 2019-07-30 4_method.tex
locally optimal > locally maximal; local optimum ? local maximum

@@
 \subsubsection{Beading conflicts}
-In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally optimal feature radius.
+In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.
 Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
 At the end of such chain $v$ we may need to transition from the former approach to the latter.
-This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local optimum at $v_n$ or some farther node.
+This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local maximum at $v_n$ or some farther node.
 See \cref{beading_conflict_problem}.
@@
 
-We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local optimum or another marked region.
+We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
 (This propagation is explained in \cref{section_toolpath_extraction}.)
@@
 \subsubsection{Toolpath extraction algorithm}
-After the beading strategy has been applied we have a beading associated with each marked node as well as each node with locally optimal $R$.
+After the beading strategy has been applied we have a beading associated with each marked node as well as each node with locally maximal $R$.
 In order to determine the junction locations of trapezoids which don't contain any such node, we propagate the beading information down.

### 2019-07-31 4_method.tex
merged and redo significance properties figures

@@
 \begin{figure} \centering
-\begin{subfigure}{0.45\columnwidth} \centering
-\includegraphics[height=.7\columnwidth]{sources/method/distance_based_angles.pdf}
+\newlength{\significancePropertiesHeight}
+\setlength{\significancePropertiesHeight}{.25\columnwidth}
+\begin{subfigure}{0.35\columnwidth} \centering
+\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
 \caption{Significance}
@@
 \end{subfigure}
-\begin{subfigure}{0.45\columnwidth} \centering
-\includegraphics[height=.7\columnwidth]{sources/method/distance_ratio_limit.pdf}
+\begin{subfigure}{0.3\columnwidth} \centering
+\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
 \caption{Distance}
 \label{distance_ratio_limit}
+\end{subfigure}
+\begin{subfigure}{0.3\columnwidth} \centering
+\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
+\caption{Upward edge}
+\label{branch_upward_edge_property}
 \end{subfigure}
@@
 radii in dashed lines.
-The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
-The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
+\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
+\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
+\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
 }
@@
 \begin{proof}
-Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_1, p_2, p_3$.
-If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
-If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
-and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
-Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
+Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
+If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
+If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
+and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
+Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
 See \cref{branch_upward_edge_property}.
@@
 \end{proof}
-
-\begin{figure}
-\centering
-\includegraphics[width=.4\columnwidth]{sources/method/branch_upward_edge_property.pdf}
-\caption{The radial distance can only increase along one edge around a branch point in the medial axis.}
-\label{branch_upward_edge_property}
-\end{figure}
 

### 2019-07-31 4_method.tex
lil better reference to lemmas

@@
 We perform filtering on the unmarked regions, so that the properties of significant regions mentioned above remain valid.
+Because of \cref{saddle_points_are_marked} we only have to consider paths between marked regions which are monotonically in/decreasing in feature radius.
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}).
@@
 \todo{Explaining why would have to refer forward to section about interpolating beadings}
-From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
-If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.
+From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
+In case $B^*_{v_0} = B^*_{v_1}$ we mark all bones and nodes $v_x$ in between, and set the bead count $B^*_{v_x} \leftarrow B^*_{v_0}$.
 

### 2019-07-31 4_method.tex
new figure on transitioning and lil rewording on bead count section

--- 2019-07-31 4_method.tex
@@
 We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
+See \cref{beading_transitioning_filtering__bead_count}.
+
 We also filter unmarked regions where the bead count remains constant.
-\todo{Explaining why would have to refer forward to section about interpolating beadings}
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
 If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.
+\todo{Explaining why would have to refer forward to section about interpolating beadings}
 
-\todo{TODO: figure of basic bead counts left, middle with transition mids, right with transition ends.}
+\begin{figure*}
+\centering
+\setlength{\figwidth}{\textwidth}
+\begin{subfigure}{0.19\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
+\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
+\end{subfigure}
+\begin{subfigure}{0.19\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
+\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
+\end{subfigure}
+\begin{subfigure}{0.19\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
+\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
+\end{subfigure}
+\begin{subfigure}{0.19\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
+\caption{Transition ends}\label{beading_transitioning_filtering__transition_ends}
+\end{subfigure}
+\begin{subfigure}{0.19\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
+\caption{Radial bones}\label{beading_transitioning_filtering__transitions_applied}
+\end{subfigure}
+\caption{
+Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
+Outline in black, medial axis edges in red, radial edges in grey.
+First we initialize the bead counts (black) in the marked regions (blue).
+We then extract the anchor locations (purple) of the transitions to a different bead count should be.
+We then filter out regions of constant bead count.
+We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
+Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
+Transitioning is robust against small pertuirbations in the outline shape.
+}
+\label{beading_transitioning_filtering}
+\end{figure*}
 

### 2019-07-31 4_method.tex
introduce half-edge datastructure

@@
 \centering
-\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
+%\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
+\includegraphics[height=1.5\columnwidth]{sources/method/half_edge_datastructure.pdf}
 \caption{Simple case}
@@
 (The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
+We repesent such a skeleton in a standard half-edge datastructure.
 See \cref{shape_decomposition_simple}.

### 2019-07-31 4_method.tex
update beading_transitioning_filtering image

@@
 \centering
-\setlength{\figwidth}{\textwidth}
-\begin{subfigure}{0.19\figwidth}
+\setlength{\figwidth}{0.15\textwidth}
+\begin{subfigure}{\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.19\figwidth}
+\begin{subfigure}{\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.19\figwidth}
+\begin{subfigure}{\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.19\figwidth}
+\begin{subfigure}{\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.19\figwidth}
+\begin{subfigure}{\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
@@
 Outline in black, medial axis edges in red, radial edges in grey.
-First we initialize the bead counts (black) in the marked regions (blue).
-We then extract the anchor locations (purple) of the transitions to a different bead count should be.
-We then filter out regions of constant bead count.
-We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
-Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
-Transitioning is robust against small pertuirbations in the outline shape.
+\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
+\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
+\subref{beading_transitioning_filtering__filtered}We then filter out regions of constant bead count.
+\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
+\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
+The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
 }

### 2019-07-31 4_method.tex
rewrite transitioning section

@@
 
-We also filter unmarked regions where the bead count remains constant.
+We also filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
-If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.
-\todo{Explaining why would have to refer forward to section about interpolating beadings}
+If the upper node has the same bead count $B^*_{v_0} = B^*_{v_1}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.
 
@@
 See \cref{transitions}.
-The transition will be placed anchored on each location $v$ where $R(v) = \nicefrac12 b^{-1}(n+1)$ for any lower bead count $n$.
-At the start $v_0$ and end $v_1$ of the transition we introduce a new node in the skeleton and connect it to the outline as per the ST requirement.
-We then assign $v_0.B^* = n$ and $v_1.B^* = n + 1$.
-If there is any node $v_x$ in between $v_0$ and $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the Euclidean distance measured along the marked bone(s).
-See \cref{distance_rounding_transition}.
+The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
+Because transitions in bead count only occurs in locations where the prefered bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.
 
-\begin{figure*}
+For each marked bone between $v_0$ and $v_1$ with $v_0.B^* \neq v_1.B*$ we introduce transitions.
+A transition from bead count $n$ to $n+1$ will be placed anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
+We can compute the location of the anchor simply as
+$$v_x = v_0 + (v_1 - v_0) (b^{-1}(n) - R(v_0)) / (R(v_1) - R(v_0))$$
+for each $n$ such that $v_0.B^*<n<v_1.B^*$.
+See \cref{beading_transitioning_filtering__transition_mids}.
+
+A transition with length $t(n)$ will be placed somewhere covering the anchor position.
+We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
+$$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
+See \cref{transition_placement}.
+For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
+That way the transitions never overlap locations with preferred bead count.
+
+In order to prevent frequent oscillations in the bead count, we filter locally maximal or minimal bead count regions.
+For each edge which contains a transition anchor we walk along the marked regions until we encounter another anchor.
+If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
+If we hit the end of a marked region and the traversed distance is less than the corresponding part $d_\pm^\text{transition}(v)$ of the transition length $t(n)$ we dissolve the bead count region in the same manner.
+See \cref{beading_transitioning_filtering__filtered}.
+
+In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $d_\pm^\text{transition}(v)$.
+If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
+See \cref{beading_transitioning_filtering__transition_ends}.
+
+Finally we perform the graph update by introducing nodes at the transition ends and introducing radial bones from these new nodes to the outline as per the trapezoidation requirement.
+See \cref{beading_transitioning_filtering__transitions_applied}.
+
+\begin{figure}
 \centering
-\begin{subfigure}{0.9\textwidth}
+\setlength{\figwidth}{\columnwidth}
+\begin{subfigure}{0.9\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated__no_transitions.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.9\textwidth}
+\begin{subfigure}{0.9\figwidth}
 \includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated.pdf}
@@
 \label{transitions}
-\end{figure*}
-
-We determined above that $v_0$ and $v_1$ should be placed around $v$, but their exact position has yet to be specified.
-While the Euclidean distance between them is $t(n-1)$, the distance between $v_0$ and the anchor point $v$ is yet to be specified.
-We determine the distance between the anchor and the transition start $v_0$ proportial to the positioning of the transition relative to the preferred distances: $D(v_0, v) =  t(n) (b^{-1}(n+1) - p(n) ) / (p(n+1) - p(n))$.
-That way the transitions never override the preferred beading.
-See \cref{transition_placement}.
+\end{figure}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
-\caption{Feature radius remapping.}
-\label{distance_rounding_transition}
-\end{figure}
-
-\subsubsection{Beading conflicts}
+\subsubsection{Beading conflicts}\label{section_beading_conflicts}
 In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.

### 2019-07-31 4_method.tex
change interpretation of b^-1 : now works on lower bead count

@@
 We call a distance $d$ `preferred' when $d = p(b(d))$
-For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.
+For our method we require the inverse $b^{-1}(n) := \argmax_d b(d) = n$.
 
@@
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
+\item $p$ is within the range of optimal: $b^{-1}(n - 1) < p(n) < b^{-1}(n)$
 %\item $b \left( p(n) \right) = n$ % follows from the above!

### 2019-07-31 4_method.tex
move beading conflicts section down to beading section
disable transition_placement figure

@@
 $$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
-See \cref{transition_placement}.
+%See \cref{transition_placement}.
 For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
@@
 
+\iffalse
 \begin{figure}
@@
 \end{figure}
-
-\subsubsection{Beading conflicts}\label{section_beading_conflicts}
-In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.
-Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
-At the end of such chain $v$ we may need to transition from the former approach to the latter.
-This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local maximum at $v_n$ or some farther node.
-See \cref{beading_conflict_problem}.
-
-\todo{Applying the bead count and determining the beading with the associated widths $W$ and locations $L$ is only handled in the next section, so perhaps we should introduce the beading propagation before the section on transitioning.}
-See \cref{alg_beading_propagation}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/transition_to_insignificance_problem.pdf}
-\caption{
-Problems at the boundary of marked regions highlighted with red ovals.
-The beading approach from the marked region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the local maximum in the bottom center.
-}
-\label{beading_conflict_problem}
-\end{figure}
-
-The transition length of these transitions to unmarked regions is determined by the fractional difference in bead count between the two beadings:
-if $v.B^* < n$ then $t = t(n) . (R(v) - v.L_n)$
-otherwise $t = t(n) . (1 - (R(v) - v.L_n))$,
-where $n = \argmax_i v.L_i < R(v)$.
-At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the ST requirements.
-
-We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
-(This propagation is explained in \cref{section_toolpath_extraction}.)
-We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
-For nodes $v_x$ in between $v_0$ and $v$ we interpolate $v_x.B^*$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
-
-\todo{TODO: implement this! }
-\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
-\todo{Explain beading propagation before transitioning}
+\fi
 
@@
 $l_i$ is the distance of the toolpath location of bead $i$ from the outline.
+
+\subsubsection{Beading conflicts}\label{section_beading_conflicts}
+In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.
+Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
+At the end of such chain $v$ we may need to transition from the former approach to the latter.
+This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local maximum at $v_n$ or some farther node.
+See \cref{beading_conflict_problem}.
+
+\todo{Applying the bead count and determining the beading with the associated widths $W$ and locations $L$ is only handled in the next section, so perhaps we should introduce the beading propagation before the section on transitioning.}
+See \cref{alg_beading_propagation}.
+
+\begin{figure}
+\centering
+\includegraphics[width=.5\columnwidth]{sources/method/transition_to_insignificance_problem.pdf}
+\caption{
+Problems at the boundary of marked regions highlighted with red ovals.
+The beading approach from the marked region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the local maximum in the bottom center.
+}
+\label{beading_conflict_problem}
+\end{figure}
+
+The transition length of these transitions to unmarked regions is determined by the fractional difference in bead count between the two beadings:
+if $v.B^* < n$ then $t = t(n) . (R(v) - v.L_n)$
+otherwise $t = t(n) . (1 - (R(v) - v.L_n))$,
+where $n = \argmax_i v.L_i < R(v)$.
+At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the ST requirements.
+
+We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
+(This propagation is explained in \cref{section_toolpath_extraction}.)
+We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
+For nodes $v_x$ in between $v_0$ and $v$ we interpolate $v_x.B^*$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
+
+\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
+\todo{Explain beading propagation before transitioning}
 

### 2019-07-31 4_method.tex
lil formula updates

@@
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
-If the upper node has the same bead count $B^*_{v_0} = B^*_{v_1}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.
+If the upper node has the same bead count $B^*_{v_1} = B^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.
 
@@
 We can compute the location of the anchor simply as
-$$v_x = v_0 + (v_1 - v_0) (b^{-1}(n) - R(v_0)) / (R(v_1) - R(v_0))$$
+$$v_x = v_0 + (v_1 - v_0) \frac{ b^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
 for each $n$ such that $v_0.B^*<n<v_1.B^*$.
@@
 We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
-$$d_-^\text{transition}(v) =  t(n) (b^{-1}(n) - p(n) ) / (p(n+1) - p(n))$$
+$$d_-^\text{transition}(v) =  t(n) \frac{ b^{-1}(n) - p(n) }{ p(n+1) - p(n) }$$
 %See \cref{transition_placement}.
@@
 That way the transitions never overlap locations with preferred bead count.
+\todo{TODO: introduce $p$ first!}
 

### 2019-07-31 4_method.tex
toolpath extraction intro

@@
 \label{section_toolpath_extraction}
+Now that we have decided on the bead counts in the central marked regions, we can apply those bead counts outward along the unmarked bones of the skeleton in order to define the locations of the toolpath junctions.
+Because there is a plethora ways to cover a distance $d$ with $n$ beads, the placement of junctions depends on the chosen beading strategy.
+The beading strategy is used to generate the radial distances at which the junctions are placed for each node: the \emph{beading}.
+That beading information is then propagated along the unmarked bones of the skeleton, so that we can generate the junctions on each unmarked bone.
+The junctions are then connected together per trapezoid in order to form the final toolpaths.
 
@@
 $l_i$ is the distance of the toolpath location of bead $i$ from the outline.
+
+\paragraph{Beading interpolation}
+Skeletal nodes which are in the middle of a transition have obtained a fractional bead count, but the functions defined in the beading strategy are only defined on natural numbers.
+The fractional part of the bead count is used to interpolate between two beadings defined on the fractional bead count rounded up and down.
 

### 2019-07-31 4_method.tex
remove the concept of prefered width p(n)
It was only used to determine the transition anchor position.
Now we determine the transition anchor position in the beading strategy
and specify in the Validation section what values we use for that, which are based on the nozzle size.

@@
 A transition with length $t(n)$ will be placed somewhere covering the anchor position.
-We determine the distance between the anchor $v$ and the lower transition end $v_0$ proportial to the positioning of the transition relative to the preferred distances: 
-$$d_-^\text{transition}(v) =  t(n) \frac{ b^{-1}(n) - p(n) }{ p(n+1) - p(n) }$$
-%See \cref{transition_placement}.
-For the other end we have $d_+^\text{transition}(v) = t(n) - d_-^\text{transition}(v)$.
-That way the transitions never overlap locations with preferred bead count.
-\todo{TODO: introduce $p$ first!}
+We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
+From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
 
@@
 If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
-If we hit the end of a marked region and the traversed distance is less than the corresponding part $d_\pm^\text{transition}(v)$ of the transition length $t(n)$ we dissolve the bead count region in the same manner.
+If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner.
 See \cref{beading_transitioning_filtering__filtered}.
 
-In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $d_\pm^\text{transition}(v)$.
+In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
 If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
@@
 $$
-\left\{ b(d), p(n), W(n, d), L(n, d), t(n), \alpha_{\text{max}} \right\}
+\left\{ b(d), W(n, d), L(n, d), t(n), t_0(n), \alpha_{\text{max}} \right\}
 $$
@@
 $b(d)$ gives the optimal bead count to cover a total distance of $d$,
-$p(n)$ gives the optimal total distance of a given bead count $n$,
 $W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
 $L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
-$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads
+$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads,
+$t_0(n)$ is the length of between the lower end and the anchor point of the transition from $n$ to $n+1$ beads
 and
@@
 
-We call a distance $d$ `preferred' when $d = p(b(d))$
 For our method we require the inverse $b^{-1}(n) := \argmax_d b(d) = n$.
@@
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $p$ is within the range of optimal: $b^{-1}(n - 1) < p(n) < b^{-1}(n)$
-%\item $b \left( p(n) \right) = n$ % follows from the above!
 \item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
 \item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
+\item $t$ is viable:  \todo{TODO: verify this.} \\ $t_1(n) + t_0(n+1) < \left( b^{-1}(n + 1) - b^{-1}(n) \right) /{2 \cos \alpha_\text{max}}$
 \end{itemize}

### 2019-07-31 6_validation.tex
printability evaluation
remove the concept of prefered width p(n)
It was only used to determine the transition anchor position.
Now we determine the transition anchor position in the beading strategy
and specify in the Validation section what values we use for that, which are based on the nozzle size.

@@
 \section{Validation}
+
+We use a transition anchor position of
+%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
+%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
+%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
+$$t_0(n) =  t(n) \left( b^{-1}(n) / 0.4  - n \right)$$
+This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the prefered bead width for a similar nozzle size.
 
@@
 
+\paragraph{Printability}
+Define some function to determine printability $0<P<1$, 
+then define a loss function $L = 1/P$.
+Evaluate average loss divided by total toolpath length.
+
 \old{Visualize thickness of beads as color.}

### 2019-07-31 4_method.tex
clearly introduce functions as belonging to the beading strategy

@@
 Our framework allows for different beading strategies which can optimize for different criteria.
+A beading strategy is defined by several several functions which govern the behavior of our framework.
 
@@
 
-We then also discretize parabolic segments and segments generated by two concave outline vertices into approximately equidistant segments.
+We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
 See \cref{discretization} and \cref{shape_decomp_complex}.
@@
 
-\subsection{Beading}
+\subsection{Bead counts}
 We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
@@
 \subsubsection{Significance measure}\label{sec:significance_measure}
-Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which intuitively look like `the center' of the shape.
+Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which arew in some sense \emph{central} to the shape.
 This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
 The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
+Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
+
 For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
@@
 This ensures that the discretization doesn't alter the extent and existence of significant regions.
+See \cref{discretization}.
 
@@
 
-\subsubsection{Bead counts}
+\subsubsection{Initial bead count}
 In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
@@
 (The feature diameter is twice the radius.)
-We might choose different functions for $b$ depending on the beading strategy used.
+The function $b$ is determined by the beading strategy.
 

### 2019-08-01 4_method.tex
rewrite beading strategy section and write beading interpolation

@@
 (The feature diameter is twice the radius.)
-The function $b$ is determined by the beading strategy.
+The function $b$ is determined by the beading strategy and is required to increase monotonically with the input feature diameter.
 
-We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
+We first assign each marked node $v$ of the skeleton an initial bead count $b^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
 See \cref{beading_transitioning_filtering__bead_count}.
@@
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
-If the upper node has the same bead count $B^*_{v_1} = B^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $B^*_v \leftarrow B^*_{v_0}$.
+If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
 
@@
 
-For each marked bone between $v_0$ and $v_1$ with $v_0.B^* \neq v_1.B*$ we introduce transitions.
+For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
 A transition from bead count $n$ to $n+1$ will be placed anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
@@
 $$v_x = v_0 + (v_1 - v_0) \frac{ b^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
-for each $n$ such that $v_0.B^*<n<v_1.B^*$.
+for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
 See \cref{beading_transitioning_filtering__transition_mids}.
@@
 In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
-If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
+If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
 See \cref{beading_transitioning_filtering__transition_ends}.
+These fractional bead counts will be used in \cref{section_beading_interpolation}.
 
@@
 
-\subsection{Beading strategy}
-First we determine how we should fill a 	polygon with constant width with a number of beads.
-We want to fit an exact whole number of beads in order to prevent a gap being generated.
-We consider only half of the polygon, because our beading strategy should be symmetrical.
-
+\begin{definition}
 We define a beading strategy as the following set:
 $$
-\left\{ b(d), W(n, d), L(n, d), t(n), t_0(n), \alpha_{\text{max}} \right\}
+\left\{ \alpha_\text{max}, b(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
 $$
 where
-$b(d)$ gives the optimal bead count to cover a total distance of $d$,
-$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
-$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
-$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads,
-$t_0(n)$ is the length of between the lower end and the anchor point of the transition from $n$ to $n+1$ beads
+$\alpha_{\text{max}}$ (the limit bisector angle),
+$b(d)$ (optimal bead count),
+$t(n)$ (transition length)
 and
-$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.
-
-\todo{TODO: Replace `distance' with `diameter'.}
-
-For our method we require the inverse $b^{-1}(n) := \argmax_d b(d) = n$.
+$t_0(n)$ (transition anchor position) have already been defined above.
+We introduce here
+$W(n, d)$, which gives the sequence of bead widths to cover a distance $d$ using $n$ beads
+and
+$L(n, d)$, which gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads.
+\end{definition}
 
@@
 \begin{itemize}
-\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
-\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
 \item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
 \item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
@@
 
-The angle requirement ensures that there is never a 3-way junction of significant bones. \todo{not true anymore}
-
-By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading, which is defined as the following set:
+\begin{definition}
+By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading $B$, which is defined as the following set:
 $$
-\left\{ d, w_i, l_i  \right\}
+\left\{ d, n, w_i, l_i  \right\}
 $$
 where
-$d = 2 R(v)$ is the total distance associated with $v$,
-$w_i$ is the bead width of the bead with index $i$
-end
-$l_i$ is the distance of the toolpath location of bead $i$ from the outline.
+$d = 2 R(v)$ is the diameter associated with $v$,
+$n$ is the bead count,
+$w_i$ is the bead width of the bead with index $0 \leq i < n$ counting from the outline inward
+and
+$l_i$ is the distance of the toolpath location of bead with index $0 \leq i < n$.
+\end{definition}
 
-\paragraph{Beading interpolation}
+\subsubsection{Beading interpolation}\label{section_beading_interpolation}
 Skeletal nodes which are in the middle of a transition have obtained a fractional bead count, but the functions defined in the beading strategy are only defined on natural numbers.
 The fractional part of the bead count is used to interpolate between two beadings defined on the fractional bead count rounded up and down.
+Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
+We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry contraints on the upper indices.
+See \cref{beading_interpolation}.
+The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the skeleton inside of transition regions.
+
+\iffalse
+In order to create an interpolated beading $B = xB^V + (1-x) B^W$, for some $0<x<1$
+we calculate:
+\begin{align*}
+n^{B} &= n^{B^W} \\
+d^B &= x d^{B^V} + (1-x) d^{B^W} \\
+w_i^{B} &= w_{n^B-i}^{B} = x w_i^{B^V} + (1-x) w_i^{B^W} \text{ for } i < \frac12 n^{B^V} \\
+%  w_{frac{n}{2}^B - frac12}  = something difficult \text{ if } n \mod 2 == 1
+w_i^{B} &= w_i^{B^W} \text{ otherwise}\\
+l_i^{B} &= 
+\begin{cases} 
+x l_i^{B^V} + (1-x) l_i^{B^W} & \text{ for } i < \frac12 (n^{B^V} - 1) \\
+d^B - x l_{i-n^{B^W}+n^{B^V}}^{B^V} + (1-x) l_i^{B^W} & \text{ for } i > n^B - 1 - \frac12 (n^{B^V} - 1) \\
+\frac12 d^B  & \text{ if $n^B$ is odd and } i = (n^B - 1) / 2 \\
+l_i^{B^W} - l_{n^{B^V}-1}^{B^W} + l_{n^{B^V}-1}^B & \text{ otherwise}
+\end{cases}
+\end{align*}
+\fi
+
+\begin{figure}
+\centering
+\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
+\caption{
+Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
+Distances between the thick black lines constitute diameters $d$,
+the toolpath locations are visualized as dots,
+the widths are visualized as bidirection arrows
+and the middle is highlighted in red.
+}
+\label{beading_interpolation}
+\end{figure}
 
 \subsubsection{Beading conflicts}\label{section_beading_conflicts}
+
+Interpolation distance $t_\text{beading}$
+
 In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.
@@
 The transition length of these transitions to unmarked regions is determined by the fractional difference in bead count between the two beadings:
-if $v.B^* < n$ then $t = t(n) . (R(v) - v.L_n)$
+if $b^*_v < n$ then $t = t(n) . (R(v) - v.L_n)$
 otherwise $t = t(n) . (1 - (R(v) - v.L_n))$,
@@
 
-We modify $v.B^*$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
+We modify $b^*_v$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
 (This propagation is explained in \cref{section_toolpath_extraction}.)
-We assign $v.B^* = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
-For nodes $v_x$ in between $v_0$ and $v$ we interpolate $v_x.B^*$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
+We assign $b^*_v = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
+For nodes $v_x$ in between $v_0$ and $v$ we interpolate $b^*_{v_x}$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
 
-\todo{Compute beading propagation after initial $B^*$ assignment, but before transitioning}
+\todo{Compute beading propagation after initial $b^*$ assignment, but before transitioning}
 \todo{Explain beading propagation before transitioning}

### 2019-08-01 4_method.tex
remove old & outdated heterogeneous_joint_generation image
rewrite toolpath extraction section

@@
 Because there is a plethora ways to cover a distance $d$ with $n$ beads, the placement of junctions depends on the chosen beading strategy.
-The beading strategy is used to generate the radial distances at which the junctions are placed for each node: the \emph{beading}.
+The beading strategy is used to generate the bead widths and radial distances at which the junctions are placed for each node: the \emph{beading}.
 That beading information is then propagated along the unmarked bones of the skeleton, so that we can generate the junctions on each unmarked bone.
@@
 and
-$L(n, d)$, which gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads.
+$L(n, d)$, which gives the sequence of toolpath positions as radial distances from the outline to cover a distance $d$ using $n$ beads.
 \end{definition}
@@
 
-\subsubsection{Beading conflicts}\label{section_beading_conflicts}
-
-Interpolation distance $t_\text{beading}$
-
-In marked regions of the ST we employ the approach of applying the optimal bead counts and employing transitioning, while in unmarked regions the beading is only governed by the beading of locations with locally maximal feature radius.
-Marked bones always form chains and don't branch out because of the angle constraint on $\alpha_\text{max}$. \todo{Not true anymore}
-At the end of such chain $v$ we may need to transition from the former approach to the latter.
-This only happens when the feature radius continues increasing: if $\exists v_n \in v.\text{neighborhood}: R(v) < R(v_n) \land | R(v) - R(v_n) | / |v - v_n| >  \cos(\alpha_\text{max} / 2)$ then the bead count assigned by the marked region doesn't fit with a beading which would follow from a local maximum at $v_n$ or some farther node.
+\subsubsection{Beading propagation}\label{section_beading_conflicts}
+Because the beading information will be propagated outward from the central marked regions, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
 See \cref{beading_conflict_problem}.
-
-\todo{Applying the bead count and determining the beading with the associated widths $W$ and locations $L$ is only handled in the next section, so perhaps we should introduce the beading propagation before the section on transitioning.}
-See \cref{alg_beading_propagation}.
+In such a case we will interpolate between the lower beading and the beading propagated from above,
+starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
+At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
+This interpolation is performed during the beading propagation algorithm.
+\todo{Make a better figure for this.}
 
@@
 
-The transition length of these transitions to unmarked regions is determined by the fractional difference in bead count between the two beadings:
-if $b^*_v < n$ then $t = t(n) . (R(v) - v.L_n)$
-otherwise $t = t(n) . (1 - (R(v) - v.L_n))$,
-where $n = \argmax_i v.L_i < R(v)$.
-At a distance $t$ from $v$ along marked bones we introduce an new node $v_0$ for the end of the transition and again we connect it to the outline as per the ST requirements.
-
-We modify $b^*_v$ such that it coincides with the beading propagated to $v$ from some farther local maximum or another marked region.
-(This propagation is explained in \cref{section_toolpath_extraction}.)
-We assign $b^*_v = n + 1 - \epsilon$, so that the transition switches from the marked beading to the beading of the unmarked approach entirely.
-For nodes $v_x$ in between $v_0$ and $v$ we interpolate $b^*_{v_x}$ again linearly based on the Euclidean distance along the bones in between $v$ and $v_0$.
-
-\todo{Compute beading propagation after initial $b^*$ assignment, but before transitioning}
-\todo{Explain beading propagation before transitioning}
-
-\subsubsection{Junction placement}
-
-Now that we have the skeleton set up, we determine the locations along the bones where the vertices of the toolpath polygons should be: the \emph{junctions}.
-For marked regions we have already inroduced joints around the transitions which serve as those locations.
-For unmarked regions we can simply apply the beading strategy in order to find the toolpath verts.
-
-This needs to be stable against small perturbations in the outline polygon.
-See \cref{heterogeneous_joint_generation}.
-For any sequence on unmarked bones from the outline polygon inward we define the stable end point as the first vertex which is connected to a marked ST segment.
-Based on the feature radius $R$ there we place junctions along the unmarked bones following the beading strategy.
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/heterogeneous_joint_generation.pdf}
-\caption{Toolpaths employing dist rounding vs without.}
-\label{heterogeneous_joint_generation}
-\end{figure}
-
-\subsubsection{Toolpath extraction algorithm}
-After the beading strategy has been applied we have a beading associated with each marked node as well as each node with locally maximal $R$.
-In order to determine the junction locations of trapezoids which don't contain any such node, we propagate the beading information down.
-We therefore sort all trapezoids on their highest $R$-value and process the high $R$ trapezoids first.
-The beading information is then passed down along the bones of the trapezoid to lower $R$ nodes if those nodes don't already have a beading associated.
-
-See \cref{alg_beading_propagation}.
+After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
+The beading propagation is performed in two stages: an upward stage and a downward phases.
+%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
+In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
+In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
+however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
+This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.
 
@@
 \begin{algorithmic}
-\State trapezoids.sortOn(getHighestR())
-\ForAll{$q \in$ trapezoids}
-	\State $v_\text{max} = q$.getHighestR()
-	\State beading = retrieveBeading($v_\text{max}$)
-	\If {$\neg$ retrieveBeading($v_\text{max}$.next())}
-		\State storeBeading($v_\text{max}$.next(), beading)
+\ForAll{$v \in$ nodes}
+	\If {marked($v$)} $\text{map}[v] = (0, B(b^*_v, 2 R(v)))$ \EndIf
+\EndFor
+\ForAll{$e \in$ edges}
+	\If {$R(v_0^e) < R(v_1^e)$}
+		% \State 
+		upwardEdges.add($e$)
 	\EndIf
-	\If {$\neg$ retrieveBeading($v_\text{max}$.prev())}
-		\State storeBeading($v_\text{max}$.prev(), beading)
+\EndFor
+\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
+\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
+	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
+    		\State $(d, B) = \text{map}[v_0^e]$
+    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
+	\EndIf
+\EndFor
+\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
+	\If {$\text{map}[v_1^e]$}
+    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
+    		% d + |v_1^e - v_0^e|
+    		\If {$\text{map}[v_0^e]$}
+    			\State $(d_0, B_0) = \text{map}[v_0^e]$
+    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
+    		\EndIf
+    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
 	\EndIf
@@
 
-We can then process all bones in arbitrary order and generate the junctions along those bones.
-See \cref{alg_junction_generation}.
-
-\begin{algorithm}
-\caption{Junction generation}
-\label{alg_junction_generation}
-\lstset{language=C++}
-\begin{lstlisting}[frame=single]
-Point a = edge->to->p;
-Point b = edge->from->p;
-Point ab = b - a;
-
-int start_R = edge->to->data.distance_to_boundary; // higher R
-int end_R = edge->from->data.distance_to_boundary; // lower R
-assert(end_R <= start_R);
-
-int junction_idx;
-// compute starting junction_idx for this segment
-for (junction_idx = (beading->toolpath_locations.size() - 1) / 2; junction_idx >= 0 && junction_idx < beading->toolpath_locations.size(); junction_idx--)
-{
-  int bead_R = beading->toolpath_locations[junction_idx];
-  if (bead_R <= start_R)
-    break; // junction coinciding with start node is used in this function call
-}
-
-for (; junction_idx >= 0 && junction_idx < coord_t(beading->toolpath_locations.size()); junction_idx--)
-{
-  int bead_R = beading->toolpath_locations[junction_idx];
-  assert(bead_R > 0);
-  if (bead_R < end_R)
-    break; // junction coinciding with a node is handled by the next segment
-
-  Point junction(a + ab * (bead_R - start_R) / (end_R - start_R));
-  junctions.emplace_back(junction, beading->bead_widths[junction_idx], junction_idx);
-}
-\end{lstlisting}
-\end{algorithm}
+\subsubsection{Toolpath extraction algorithm}
+Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
+For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
+\begin{align*}
+J &= \{ v, w, i \} \\ 
+v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
+w &= w_i^B
+% \\ i^J &= i
+\end{align*}
+for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
+We store all junctions of a segment in a mapping from edge to a list of junctions.
 
 We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
-If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one junction unconnected.
+If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
+If a central edge has both nodes with an odd beadcount assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
+We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
 
-\paragraph{Printing order}
-The order in which beads are printed has influence on the quality and dimensional accuracy of a print.
-If the inner beads are printed first then small inaccuracies in the deposition process propagate outward and the final outline of the print layer will be less accurate.
-However, if the second bead is printed before the outer bead then the outer bead has more material to adhere to, which lessens the overhang constraints.
-We therefore choose to print the inner beads first starting from the second bead and at the very end print the outermost bead.
+All segments are then connected together into polylines, which are then closed into polygonal toolpaths.
+The odd center segments remain in polylines, so the final toolpaths contain both polygonal paths and open polyline paths.
 
-\begin{figure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy.jpg}
-\caption{Overview}
-\label{single_bead_strategy_overview}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/single_bead_strategy_order.jpg}
-\caption{Travel order}s
-\end{subfigure}
-\caption{We can do single-bead segments. Blue is travel move.}
-\label{single_bead_strategy}
-\end{figure}
-
-When all extrusion segments are generated, we combine them into semi-continuous polyline toolpaths.
-These polylines generally form closed polygons, but at marked regions of the ST the toolpaths consist of single bead polyline toolpaths.
-See \cref{single_bead_strategy}.
-These single bead polylines can connect to polygonal toolpaths and they can also meet each other at 3-way junctions.
-We determine the printing order for all segments of a given bead index by minimizing the travel distance using a greedy path order optimizer.
-\todo{[implementation needed!]}
-
-In general the toolpath location should be centered on the middle of the bead.
-However, when the bead width is smaller than the nozzle size we might want to offset the toolpath toward a previously printed bead.
-That way the previously printed bead occludes part of the hole in the nozzle such that the unoccluded hole is as wide as the required bead width.
-The printing order and the toolpath positioning of the beading strategy are therefore interrelated.
-
-Around 3-way junctions we need to prevent overextrusion.
-We need to reduce the extrusion amount after the first time we pass an intersection: commonly known as \emph{ghosting}.
-See \cref{ghosting}.
-In order to realize the reduction we remove a section from the extrusion bead up to a distance equal to the feature radius from the junction.
+Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
+Such intersections cause overextrusion because the nozzle passes the location multiple times.
+In order to reduce the amount of overextrusion of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $d_\text{max}^\text{intersection} w^J$, where $d_\text{max}$ is some ration between $0$ and $1$.
+We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.
+See \cref{polyline_reduction}.
 
@@
 \centering
-\includegraphics[width=.99\columnwidth]{sources/method/ghosting.pdf}
-\caption{Ghosting prevents over-extrusion at junctions.}
-\label{ghosting}
+\setlength{\figwidth}{\columnwidth}
+\begin{subfigure}{0.45\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_unreduced.pdf}
+\caption{No reduction}
+\end{subfigure}
+\begin{subfigure}{0.45\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_reduced.pdf}
+\caption{Reduction}
+\end{subfigure}
+\caption{
+Reducing polyline toolpaths away from intersections in order to prevent overextrusion.
+Toolpath locations in black, underextrusion in blue, overextrusion in red and orange and normal extrusion in grey.
+Intersections result in overextrusion, so we remove parts of the polylines at intersections.
+}
+\label{polyline_reduction}
 \end{figure}

### 2019-08-01 4_method.tex
lil

@@
 We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
+\todo{TODO: Image}
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
@@
 Such intersections cause overextrusion because the nozzle passes the location multiple times.
-In order to reduce the amount of overextrusion of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $d_\text{max}^\text{intersection} w^J$, where $d_\text{max}$ is some ration between $0$ and $1$.
+In order to reduce the amount of overextrusion of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
 We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.

### 2019-08-01 6_validation.tex
clearly introduce functions as belonging to the beading strategy
rewrite beading strategy section and write beading interpolation
rewrite toolpath extraction section
remove combined strategy
formalized all tested strategies

@@
 \section{Validation}
+We use the following constants:
+\begin{align}
+d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
+d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
+t_\text{beading} &= \SI{0.4}{\milli\meter} \\
+d_\text{max}^\text{intersection} &= \SI{75}{\percent}
+\end{align}
 
@@
 
+Our beading strategies are based on a prefered width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
+
+We set 
+\begin{align*}
+t(n) &= w_\text{pref} \\
+\alpha_\text{max} &= \SI{135}{\degree} \\
+L(n,d)_i &= 
+\begin{cases}
+-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
+d/2 & \text{ if } i =  \frac12 (n -1) \\
+d - W(n,d)_{n-1-i} & \text{ otherwise }\\
+\end{cases}
+\end{align*}
+
 \subsection{Strategies}
-We can emulate a variety of toolpath generation strategies by applying various beading strategies to our framework.
+We can emulate a variety of toolpath generation methods from related literature by applying various beading strategies to our framework.
 
 \paragraph{Naive Strategy}
+Because the naive strategy never employs single line polyline segments, we disable marking edges using the significance measure by choosing the limit angle.
+\begin{align*}
+\alpha_\text{max} &= \SI{180}{\degree} \\
+b(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+W(n,d)_i &= w_\text{pref} \text{ for all } i 
+%\\
+%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+\end{align*}
 
@@
 
-\paragraph{Deviation at middle}
+\begin{align*}
+b(d) &= C \\
+W(n,d)_i &= d / n \text{ for all } i 
+%\\
+%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+\end{align*}
+
+\paragraph{Deviating toolpath at center}
 Emulates \cite{Jin2017}
+
+$r_\text{min} = 0.8 w_\text{pref}$ and $r_\text{max} = 1.25 w_\text{pref}$
+
+\begin{align*}
+b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+b(d) &= b^-(d) +
+\begin{cases}
+-1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
+1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
+0 & \text{ otherwise}
+\end{cases}
+\\
+W(n,d)_i &= 
+\begin{cases}
+d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
+w_\text{pref} &\text{ otherwise }
+\end{cases}
+%\\
+%L(n,d)_i &= 
+%\begin{cases}
+%d / 2 & \text{ if } i = \frac12 (n-1) \\
+%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
+%\end{cases}
+\end{align*}
 
@@
 Emulates \cite{Moesen2011}
+
+$d_\text{max}^\text{intersection} = \SI{0}{\percent}$
+
+\begin{align*}
+t(n) &= 0 \\
+b(d) &=
+\begin{cases}
+1 & \text{ if } d < w_\text{pref} \\
+2 & \text{ otherwise } \\
+\end{cases}
+ \\
+W(n,d)_i &= 
+\begin{cases}
+d & \text{ if } n = 1 \\
+w_\text{pref} & \text{ otherwise } \\
+\end{cases}
+%\\
+%L(n,d)_i &= 
+%\begin{cases}
+%d / 2 & \text{ if } n = 1 \\
+%w_\text{pref} / 2 & \text{ otherwise } \\
+%\end{cases}
+\end{align*}
 
@@
 
-\paragraph{Combined strategy}
-\Cref{wedge_and_infill} shows a combined toolpath strategy.
-
-\begin{figure}
-\centering
-\includegraphics[width=.99\columnwidth]{sources/method/wedge_and_infill.pdf}
-\caption{Use single and double wall lines in regions where the infill would be too thin.}
-\label{wedge_and_infill}
-\end{figure}
+\begin{align*}
+b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+W(n,d)_i &= d / n \text{ for all } i 
+%\\
+%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
+\end{align*}
 

### 2019-08-01 6_validation.tex
describe inward distributed strategy

@@
 \end{align*}
+
+\paragraph{General distributed strategy}
+Distribute the overfill or underfill which would happen using a naive strategy $E$ over all beads unevenly depending on some weighing function $M(n.d)$, which defines the portion of overfill or underfill which would occur in the naive strategy to distribute to each junction.
+
+\begin{align*}
+b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+E(n,d) &= d - n w_\text{pref} \\
+W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
+%\\
+%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
+\end{align*}
+
+\todo{TODO: check $n$ vs $n-1$ everywhere when comparing indices and the total size! Largest index should be $n-1$, not $n$!}
+
+\paragraph{Inward distributed strategy}
+For example, we can choose 
+$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
+To distribute the hypothetical over-/underfill over the innermost $2N$ beads, and distribute most of it to the inner beads.
+That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
+This helps if print settings for bead widths other than the prefered width aren't calibrated as well as the settings for $w_\text{pref}$.
+Toolpaths with deviating widths might result in less dimensional accuracy on the outline and uncalibrated mechanical properties throughout the volume, so limiting the number of beads width deviating bead width might be beneficial.
+\todo{Emphasize this point more. Put it in the abstract and conclusion.}
 

### 2019-08-02 6_validation.tex
remove outdated proposed optimal beading strategy which uses a max an min width

@@
 
-\subsubsection{Proposed optimal beading strategy}
-@Readers: you can skip reading this section for now.
-\todo{This section is about some optimal strategy which hasn't been fully developed (yet?).}
-\todo{This section still formules the beading strategy in terms of radius instead of diameter, which halves the $n$ values.}
-
-We need a function $W$ from a given radial distance $R(v)$ to a number of beads and their widths.
-These widths depend on the following parameters:
-\begin{description}
-\item[$\wmin$] the minimum possible bead width
-\item[$\wmax$] the maximum possible bead width
-\item[$\wout$] the preferred bead width of the outer inset
-\item[$\win$] the preferred bead width of the other insets
-\end{description}
-
-The function $W$ needs to be able to deal with a range which is considerably shorter than $[\wmin, 2\wmin]$, even so short as to accomodate just $[\win,\win]$ only.
-The function needs to be such that we never overshoot the radial distance $R(v)$, because that would affect the dimensional accuracy.
-Any distance left over which cannot be filled given the range $[\wmin, \wmax]$ should be placed on the inside near the MAT.
-
-We define $W(d)$ as a sequence of bead widths.
-The length of that sequence is $b(d)$.
-For example: with $\win = \SI{0.4}{\milli\meter}$ we could have $b(1.05) = 2.5$ and $W(1.05) = (0.4, 0.4, 0.5)$.
-The last number is the innermost bead width if there is a singleton bead along the medial axis; only half of that bead spans along a radial distance.
-
-The function $b$ should adhere to several criteria:
-\begin{itemize}
-\item $b \left( \frac12 n\win \right) = \frac12 n$ for integer $n$
-%\item $b$ is monotonic
-%the item below follows from the two above
-% \item between a location with radial distance $R(v) \in [\frac12 n\win, \frac12 (n+1)\win]$ (for integer $n$) there is only one transition to a different number of beads
-\item $ 0 \leq b(d) \leq d / w_\text{min} $
-%\item the width $W(c, d)_n$ of each bead $n$ increases monotonically and gradually in regions with constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\end{itemize}
-
-For our application we define a $W$ adhereing to the following aditional constraints in order of priority:
-\begin{itemize}
-\item Minimize unfilled area
-\item Try to get the outer bead width $W_1$ as close as possible to $\wout$
-\item Have the rest of the $W_n$ the same width
-\item at transition regions decide between $n$ and $n+1$ beads using the Loss fuction scheme below
-\item From a $d$ for which $b(d) = 3$ we don't consider fractional $b(d)$ anymore; we don't allow singleton beads along the medial axis.
-\hl{Perhaps we should disallow this because that would require a different transition length}
-\end{itemize}
-
-\iffalse
-\begin{align}
-W(d)_1 = 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   \wout & \text{if } d \geq \wout + \wmin \\
-   w - \wmin  & \text{if } 2\wmin  \leq d < \wout + \wmin
-  \end{cases}
-\end{align}
-\fi
-
-%\subsubsection{Optimal beading strategy}
-%We could decide on a beading strategy based on some loss function $L$ defined on each line width.
-
-\begin{align}
-L(w_1) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \wout) / (\wmax - \wout) & \text{if } w > \wout\\
-   (\wout - w) / (\wout - \wmin)       & \text{otherwise}
-  \end{cases}
-  \\
-L(w_n) &= 
-  \begin{cases} 
-%  \infty & \text{if } w < w_\text{min} \\
-   (w - \win) / (\wmax - \win) & \text{if } w > \win\\
-   (\win - w) / (\win - \wmin)       & \text{otherwise}
-  \end{cases}
-\\
-L(W(d)) &= \left(b(d) - \lfloor b(d) \rfloor \right) L \left( W(d)_{\lceil b(d) \rceil} \right)  +  \sum_{n=1}^{n=\lfloor b(d) \rfloor} L( W(d)_n )
-\end{align}
-
-(Singular beads are counted only half.)
-Together these prioritized constraints uniquely define a single $W$, depending on $\wmin, \wmax, \wout,\win$.
-An example is given in \cref{transition_location}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=.9\textwidth]{sources/method/ticking_v2.pdf}
-\caption{Mapping of different lengths to a ticking.
-Transition location on a line-line segment is to the right of the middle because the preferred line width is to the left of the middle in the range.}
-\label{transition_location}
-\end{figure*}
-
-The prefered width $p$ is given as follows:
-\begin{align}
-p(n) =
-  \begin{cases} 
-   \frac12 \wout & \text{if } n = \frac12 \\
-    \wout + (n - 1) \win       & \text{otherwise}
-  \end{cases}
-\end{align}
-
 \subsection{Computational analysis}

### 2019-08-02 6_validation.tex
make figures showing strategies on gMAT example

@@
 
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.19\textwidth}
+\setlength{\figheight}{0.283\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
+\caption{Naive}\label{TEST_naive_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
+\caption{Single}\label{TEST_SingleBead_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
+\caption{Constant}\label{TEST_Constant_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
+\caption{Center}\label{TEST_Center_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
+\caption{Distributed}\label{TEST_Distributed_accuracy}
+\end{subfigure}
+%\begin{subfigure}{\figwidth}\centering
+%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
+%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
+%\caption{Inward}\label{TEST_InwardDistributed_accuracy}
+%\end{subfigure}
+\begin{subfigure}{.04\columnwidth}\centering
+\vspace{4cm}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
+\end{subfigure}
+\caption{
+Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
+Grey areas are covered by extruded material,
+blue areas in the top images signify underfill regions,
+red areas overfill,
+orange areas triply extruded areas (double overfill).
+The bottom visualized the bead widths at each location by exaggerating their widths.
+Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
+}
+\label{visualized_accuracy}
+\end{figure*}
+
 \subsection{Strategies}
@@
 \begin{align*}
+t(n) &= \frac12 w_\text{pref} \\
 b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\

### 2019-08-05 6_validation.tex
move Moessen method to before Constant
The Moessen method only has a small advantage over the naive method.
emulate related work correctly
describe validation setup

@@
 
-\paragraph{Constant bead count}
-Emulates \cite{Ding2016a}
+\paragraph{Only outer bead}
+Emulates \cite{Moesen2011}. We don't reduce line segments in 3-way intersections.
+
+$d_\text{max}^\text{intersection} = \SI{0}{\percent}$
 
 \begin{align*}
+t(n) &= 0 \\
+b(d) &=
+\begin{cases}
+1 & \text{ if } d < w_\text{pref} \\
+2 & \text{ otherwise } \\
+\end{cases}
+ \\
+W(n,d)_i &= 
+\begin{cases}
+d & \text{ if } n = 1 \\
+w_\text{pref} & \text{ otherwise } \\
+\end{cases}
+%\\
+%L(n,d)_i &= 
+%\begin{cases}
+%d / 2 & \text{ if } n = 1 \\
+%w_\text{pref} / 2 & \text{ otherwise } \\
+%\end{cases}
+\end{align*}
+
+\paragraph{Constant bead count}
+Emulates \cite{Ding2016a}. We unmark all outer segments.
+
+\begin{align*}
+\alpha_\text{max} &= \SI{180}{\degree} \\
 b(d) &= C \\
@@
 %w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
-%\end{cases}
-\end{align*}
-
-\paragraph{Only outer bead}
-Emulates \cite{Moesen2011}
-
-$d_\text{max}^\text{intersection} = \SI{0}{\percent}$
-
-\begin{align*}
-t(n) &= 0 \\
-b(d) &=
-\begin{cases}
-1 & \text{ if } d < w_\text{pref} \\
-2 & \text{ otherwise } \\
-\end{cases}
- \\
-W(n,d)_i &= 
-\begin{cases}
-d & \text{ if } n = 1 \\
-w_\text{pref} & \text{ otherwise } \\
-\end{cases}
-%\\
-%L(n,d)_i &= 
-%\begin{cases}
-%d / 2 & \text{ if } n = 1 \\
-%w_\text{pref} / 2 & \text{ otherwise } \\
 %\end{cases}
@@
 \subsection{Computational analysis}
+Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
+The naive method was implemented using the state-of-the-art polygon offset library called Clipper. \cite{johnson2014clipper}
+
 \paragraph{Accuracy}
-Render toolpaths and calculate amount of overfilling and amount of underfilling.
+In order to estimate the overfill and underfill we need to accurately calculate the area covered by a single extrusion path.
+If we would simply use a isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment we would get strange artifacts at corners in the toolpath.
+We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
+For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
+In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
+See \cref{segment_visualization}.
 
-\paragraph{Printability}
-Define some function to determine printability $0<P<1$, 
-then define a loss function $L = 1/P$.
-Evaluate average loss divided by total toolpath length.
+\begin{figure}
+\centering
+\setlength{\figwidth}{.25\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
+\caption{Blocky}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
+\caption{Rounded}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
+\caption{Excluded}
+\end{subfigure}
+\caption{
+Extruded area of two extrusion toolpath segments.
+Red areas signify doubly extruded areas.
+}
+\label{segment_visualization}
+\end{figure}
 
-\old{Visualize thickness of beads as color.}
+We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then takign the difference from the original outline shape.
+In order to deal with rounding errors we perform a morpholocial close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
 
-Show results for different settings.
+The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
+We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
+Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
+In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
+These tripple extrusion areas count double toward the total amount of overfill.
+The resulting overfill and underfill areas are visualzied for the different toolpath strategies in \cref{visualized_accuracy}.
 
-\old{Also render with nozzle size as minimal width and use middle of toolpaths instead of middle of beads.}
+\todo{Visualize results in tables and/or graphs.}
+
+\paragraph{Manufacturability}
+Depending on the hardware configuration some bead widths are difficult to manufacture.
+A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
+We visualize the bead widths reslting from the different strategies in an exaggerated manner in \cref{visualized_accuracy}.
 

### 2019-08-05 12_conclusions_future_work.tex
rewrite skeletonization section and rename Voronoi Quadrangulation > Skeletal Trapezoidation
mention optimization of beading strategy in future work

@@
 \subsection{Future work}
-Use Voronoi Quadrangulation to generate quad dominant meshings for FEM.
+Define the optimal strategy for a given piece of hardware by finding an accurate objective function which takes into account the manufacturability or dimensional accuracy as a function of bead width and its effect on qualities of top layers, stiffness or the dimensional accuracy of the outline shape.
+
+Use Skeletal Trapezoidation to generate quad dominant meshings for FEM.
 

### 2019-08-05 1_intro.tex
lil goal
lil comments
add a line as goal
zjenja: added goal
lil: update TODOs

@@
 
+\subsection{Problem}
+Too thin lines cannot be fabricated accurately.
+
+\todo{Tim will make pictures of too thin beads and too thick beads.}
+
+Jagged lines cause jerky problems.
+Wears down mechanics.
+Takes long to print.
+
 \subsection{Goal}
 \begin{itemize}
+\item added 1 goal
+\item zjenja added goal
 \item Accurate fabrication of thin walls
@@
 \item ... and/or translucency properties
+\item Without generating paths smaller than \SI{70}{\percent} of the nozzle size
+\item While generating maximally paths of \SI{140}{\percent} of the nozzle size
 \end{itemize}
+
+\subsection{Contributions}
+\begin{itemize}
+\item A framework for generating conentric toolpaths with variable width
+\end{itemize}

### 2019-08-05 6_validation.tex
move example shapes to discussion
lil: update TODOs

@@
 These tripple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualzied for the different toolpath strategies in \cref{visualized_accuracy}.
+The resulting overfill and underfill areas are visualzied for the different toolpath strategies in the top of \cref{visualized_accuracy}.
 
-\todo{Visualize results in tables and/or graphs.}
+\todo{Zjenja should visualize overfill and underfill results in tables and/or graphs.}
 
@@
 A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
-We visualize the bead widths reslting from the different strategies in an exaggerated manner in \cref{visualized_accuracy}.
-
-Example shapes:
-\begin{itemize}
-\item same as Moessen: grids of triangular holes
-\item same as Moessen: circular holes.
-\item same as Jin 
-\item same as Kao
-\item wedge
-\item layer of a typical model: phone case
-\item some of the above shapes, but with some fuzzy randomized outline
-\end{itemize}
+\todo{Tim should put pictures of extremal bead widths in introduction!}
+We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
 
 \subsection{Experimentation}
-Print objects and show qualities:
+\todo{Tim will print objects and show qualities:}
 \begin{itemize}
@@
 \end{itemize}
-
-Print on mississipi?
-
-What material should I print with for the tensile tests?

### 2019-08-05 sources/validation/gMAT_example/resize_all.sh
reduce image quality of accuracy / widths

@@ -1,0 +1,5 @@
+for file in *.png; do
+ convert -resize 50% $file "${file%.png}.png"
+done
+
+

### 2019-08-05 0_main.tex
make properties of significant regions into Lemmas
new figure on transitioning and lil rewording on bead count section
lil
rewrite beading strategy section and write beading interpolation
rewrite toolpath extraction section
lil: abstract: why bead width matters
new title

@@
 
+	\usepackage{amsthm} % \begin{proof}
+	\newtheorem{lemma}{Lemma}[section]
+	\theoremstyle{definition}
+	\newtheorem{definition}{Definition}[section]
+
 	\usepackage[inline]{enumitem} % inline enumerate*
@@
 
-	\usepackage{algpseudocode} % algorithmic
+	\usepackage[noend]{algpseudocode} % algorithmic
 	\usepackage{algorithm} % wrapper for pseudocode to give a caption and label
+
 	\newcommand{\pluseq}{\mathrel{+}=} %pluseq symbol
+	\usepackage{upgreek} % \uplambda
 
@@
 	\renewcommand\floatpagefraction{.8}
+
+	\newlength{\figwidth}
+	\newlength{\figheight}
 
@@
 
-\title{A robust framework for variable extrusion width concentric toolpath generation}
+%\title{A robust framework for variable extrusion width concentric toolpath generation}
+\title{A parametric system for contour parallel variable width toolpath generation}
 
@@
 Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
-However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size.
+However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture.
 We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

### 2019-08-08 10_applications.tex
reference to variable width microstructure paper
application figures

@@
 
-show the effect of the planned toolpath on the performance of varying thickness microstructures
+Show the effect of the planned toolpath on the performance of varying thickness microstructures.
+Compare to \cite{bates2018compressive}.
+
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.1\textwidth}
+\setlength{\figheight}{0.1\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/david.png}
+\caption{Statue}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/gyroid.png}
+\caption{Gyroid}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
+\caption{Hex}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/house.png}
+\caption{House}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
+\caption{Gear}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
+\caption{Case}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
+\caption{Bone}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
+\caption{TUD}%label{applications_}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
+\caption{UM}%label{applications_}
+\end{subfigure}
+\caption{
+Closeups of results for the inward distributed beading strategy for various applications.
+The extrusion widths are visualized exaggeratedly and using a color scheme exaplained in \cref{visualized_accuracy}.
+}
+\label{application_closeups}
+\end{figure*}
+
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{sources/applications/combined_small_dilated_circled.pdf}
+\caption{
+Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
+A legend for the colors can be found in \cref{visualized_accuracy}.
+From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
+}
+\label{applications_overview}
+\end{figure}
 

### 2019-08-08 4_method.tex
fix transition length viability constraint

@@
 From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
+The transitions lengths should be such that they fit between anchor locations of two consecutive transitions even for a bone with high bisector angle:
+$$t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$$
+for each $n \in \mathbb{N}$.
+See \cref{transition_placement}.
+
+\begin{figure}
+\centering
+\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
+\caption{
+Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
+The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
+}
+\label{transition_placement}
+\end{figure}
 
@@
 
-\iffalse
-\begin{figure}
-\centering
-\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
-\caption{
-Transition placement.
-The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
-}
-\label{transition_placement}
-\end{figure}
-\fi
-
 \subsection{Toolpath extraction}
@@
 \item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\item $t$ is viable:  \todo{TODO: verify this.} \\ $t_1(n) + t_0(n+1) < \left( b^{-1}(n + 1) - b^{-1}(n) \right) /{2 \cos \alpha_\text{max}}$
 \end{itemize}

### 2019-08-10 0_main.tex
more outline of introduction section

@@
 \begin{abstract}
-3D printing techniques such as Fused Deposition Modeling (FDM) works by depositing material along paths which lie in horizontal layers.
+Additive manufacturing has enabled the fabrication of complex geometry quickly and cheaply.
+3D printing techniques such as Fused Deposition Modeling (FDM) work by depositing material along paths which lie in horizontal layers.
 The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.
 Filling the outlines with extruded material densely and accurately is important for fabricating parts accurately and stiffly.
-Especially thin parts require an accurate dense filling, such as casings for electronics, blowmolding prototypes, (architectural) models and some tpyes of microstructure.
+An accurate dense filling is aspecially important to thin parts such as casings for electronics, blowmolding prototypes, (architectural) models and microstructures.
 

### 2019-08-10 1_intro.tex
more outline of introduction section

@@
 \section{Introduction}
+Additive manufacturing in general
 
-Compare to simple offsets with constant width
+FDM is
+
+FDM is used for...
+
+FDM works by depositing beads in flat layers
+
+Outer walls are contour following because the resolution determined by the bead width is worse than the spatial accuracy of the XYZ positioning system.
+
+Naive method
+
+mechanical properties of FDM parts and relations with bead width
 
 \subsection{Problem}
+Thin model parts either produce overfill or underfill in the naive method.
+
+3D models may have parts with pieces with a thickness of non-integer multiples of the nominal bead width.
+How can we fill such a shape?
+We must employ varying line width.
+
 Too thin lines cannot be fabricated accurately. 
+See \cref{extremal_bead_widths}.
 
-\todo{Tim will make pictures of too thin beads and too thick beads.}
+\begin{figure}
+\centering
+\setlength{\figwidth}{.4\columnwidth}
+%\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/intro/thin_extrusion.jpg}
+%\caption{Thin}
+%\end{subfigure}
+\caption{
+Extremal bead widths.
+Bead widths from top to bottom: \SI{0.2}{\milli\meter}, \SI{0.3}{\milli\meter}, \SI{0.4}{\milli\meter}, \SI{0.5}{\milli\meter}.
+Too thin lines cannot be manufactured reliably.
+}
+\label{extremal_bead_widths}
+\end{figure}
 
-Jagged lines cause jerky problems.
-Wears down mechanics.
-Takes long to print.
+\subsection{Significance}
+
+There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
+In order to accurately fabricate something with prescribed mechanical properties we need to print while employing roughly homogenous line width.
+
+Line width is influenced by the following factors:
+\begin{itemize}
+\item Larger for filling cravices
+\item Larger or smaller (?) for heat dissipation
+\item Larger for larger contact surface, so better adhesion \cite{N.Turner2014}
+\item Larger fills up an area faster \cite{ahn2002anisotropic}
+\item Smaller for better quality top surfaces \cite{ahn2002anisotropic}
+\item Smaller for overhangs
+\item Smaller to compensate for die swell
+\item Smaller for more detail, less rounded corners \cite{N.Turner2014}
+\end{itemize}
+
+\iffalse
+
+``Small bead width increases build time. Small bead width increases surfacequality.''\cite{ahn2002anisotropic}
+
+``The final width of the road determines the resolution that can be achieved in the print process, as well as the contactarea between neighboring beads.
+The rounded, oblong shape of  the  bead  inevitably  leads  to  small  voids  in  the  part.
+The strength   of   the   bond   between   neighboring   roads,   and ultimately the overall mechanical properties of the part, will depend on the contact area between those beads and the size of the voids.''\cite{N.Turner2014}
+\fi
 
@@
 \begin{itemize}
-\item added 1 goal
-\item zjenja added goal
 \item Accurate fabrication of thin walls
@@
 \end{itemize}
+
+This work is patent pending, but the source code is available open source.

### 2019-08-10 6_validation.tex
omit fig of single bead strategy instead of inward distributed strategy

@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
-\caption{Single}\label{TEST_SingleBead_accuracy}
-\end{subfigure}
+%\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
+%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
+%\caption{Single}\label{TEST_SingleBead_accuracy}
+%\end{subfigure}
 \begin{subfigure}{\figwidth}\centering
@@
 \end{subfigure}
-%\begin{subfigure}{\figwidth}\centering
-%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
-%\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
-%\caption{Inward}\label{TEST_InwardDistributed_accuracy}
-%\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
+\caption{Inward}\label{TEST_InwardDistributed_accuracy}
+\end{subfigure}
 \begin{subfigure}{.04\columnwidth}\centering

### 2019-08-10 8_discussion.tex
move example shapes to discussion
overview of discussion section

@@
 \subsection{Comparison of different beading strategies}
-\todo{Discussion of finding of Validation section}
+\todo{Discussion of finding of Validation section}\
+
+Naive strategy causes a lot of overfills and underfills.
+This overpoweres any positive effect of perfectly homogeneous bead width.
+
+The single bead strategy solves the underfill problem in regions where the model is more thin than the nozzle size.
+However, the strategy doesn't deal with the remaining area.
+In our visualization we print the outline of the remaining area which exposes an overextrusion problem.
+
+The constant beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
+For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
+
+The center beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
+
+The distributed strategy greatly reduces the total underfill and overfill and severely limits the amount of beads with a width which differs greatly from an optimal width, but the toolpaths contain a lot of bends in transitioning areas.
+
+The inward distributed beading strategy shows similar behavior to the distributed strategy, but large regions are less affected by the bends introduced because of transitioning.
+This can be seen in \cref{applications_gear}.

### 2019-08-10 1_intro.tex
remove thin extrusion fig
The intro si going to reer to literature more.
Using only a single image to reason for the motivation is weak
intro wedge toolpaths figure

@@
 
+\begin{figure}\centering
+\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
+\caption{
+Toolpaths for a wedge shape using the naive offsetting approach (top) and our approach (bottom).
+Red signifies overfill and blue underfill.
+}
+\label{intro_wedge}
+\end{figure}
+
 \subsection{Problem}
@@
 We must employ varying line width.
-
-Too thin lines cannot be fabricated accurately. 
-See \cref{extremal_bead_widths}.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.4\columnwidth}
-%\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/intro/thin_extrusion.jpg}
-%\caption{Thin}
-%\end{subfigure}
-\caption{
-Extremal bead widths.
-Bead widths from top to bottom: \SI{0.2}{\milli\meter}, \SI{0.3}{\milli\meter}, \SI{0.4}{\milli\meter}, \SI{0.5}{\milli\meter}.
-Too thin lines cannot be manufactured reliably.
-}
-\label{extremal_bead_widths}
-\end{figure}
 

### 2019-08-11 0_main.tex
write intro

@@
 %\title{A robust framework for variable extrusion width concentric toolpath generation}
-\title{A parametric system for contour parallel variable width toolpath generation}
+\title{A parametric system for adaptive extrusion width contour parallel toolpath generation}
 
@@
 \begin{abstract}
-Additive manufacturing has enabled the fabrication of complex geometry quickly and cheaply.
-3D printing techniques such as Fused Deposition Modeling (FDM) work by depositing material along paths which lie in horizontal layers.
+3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
+FDM works by depositing material along paths which lie in horizontal layers.
 The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.

### 2019-08-11 1_intro.tex
write intro

--- 2019-08-05 1_intro.tex
@@
 \section{Introduction}
+3D printing enables the fabrication of complex geometry under very few design constraints compared to conventional fabrication techniques.
+Recent developments have seen a rapid growth in the use and capabilities of desktop 3D printing systems.
+The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
 
-Compare to simple offsets with constant width
+Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
+It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
+FDM printers are used for example in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures - to name just some.
+Recent research developments have investigated manufacturing complex volumetric structures such as microstructures, topology optimized structures and infill structures.
+Quite some of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
 
-\subsection{Problem}
-Too thin lines cannot be fabricated accurately.
+FDM printers expell molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
+Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
+the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.
 
-\todo{Tim will make pictures of too thin beads and too thick beads.}
+The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the size of the hole in the nozzle from the outline shape.
+However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
+See \cref{intro_wedge}(top).
+Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
+Underfills on the other hand can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
+These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
+In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
+Some such toolpath generation techniques have already been developed.
 
-Jagged lines cause jerky problems.
-Wears down mechanics.
-Takes long to print.
+\begin{figure}\centering
+\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
+\caption{
+Toolpaths for a wedge shape using the naive offsetting approach (top) and our approach (bottom).
+Red signifies overfill and blue underfill.
+}
+\label{intro_wedge}
+\end{figure}
 
-\subsection{Goal}
+There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
+The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads.
+\cite{N.Turner2014,ahn2002anisotropic}
+In order to accurately fabricate a part restricted to prescribed mechanical properties we need to generate toolpaths using the corresponding process parameters as close as possible.
+We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width then existing techniques.
+See \cref{intro_wedge}(bottom).
+
+%\subsection{Contributions}
+A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
+because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
+We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
+Our contributions are as follows:
 \begin{itemize}
-\item added 1 goal
-\item zjenja added goal
-\item Accurate fabrication of thin walls
-\item Prevent underfilling and overfilling
-\item ... for accurately matching stiffness properties
-\item ... and/or translucency properties
-\item Without generating paths smaller than \SI{70}{\percent} of the nozzle size
-\item While generating maximally paths of \SI{140}{\percent} of the nozzle size
+\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
+\item A specific beading strategy function for this framework for:
+\begin{itemize}
+\item Accurately filling a 2D outline with extrusion beads
+\item Reducing the overfill and underfill areas compared to the naive method
+\item Reducing the amount of beads with greatly deviating width compared to existing literature
+\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
+\end{itemize}
 \end{itemize}
 
-\subsection{Contributions}
-\begin{itemize}
-\item A framework for generating conentric toolpaths with variable width
-\end{itemize}
+%This work is patent pending, but the source code is available open source.

### 2019-08-11 10_applications.tex
photo of variable width print
changed gear closeup fig to avoid random thicker bug thing
small remark in fig

@@
 \includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
-\caption{Gear}%label{applications_}
+\caption{Gear}\label{applications_gear}
 \end{subfigure}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=\columnwidth]{sources/applications/wedge_print_v2.png}
+\caption{
+A small wedge shape printed using the variable width scheme prescribed by the ditributed beading strategy.
+Small gaps have been added in between the extrusion paths so that the toolpaths can easily be identified separately.
+}
+\label{wedge_print}
+\end{figure}
+
 \subsection{Widening}

### 2019-08-11 12_conclusions_future_work.tex
more conclusions

@@
 \item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
-\item Our framework is able to emulate several previously proposed methods
+\item Our framework is able to emulate several methods proposed in related literature.
 \item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
 \item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
-\item The computation times are approximately 3 times as fast as the state of the art method for naive toolpath generation employing constant width
-\item (depending on what we do in the validation chapter) The produced parts employing our method are more stiff compared to other methods.
+\item Our framework is stable against slight perturbations of the outline shape or large perturbations of the outline shape in far away regions.
+\item We can define a strategy which distibutes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
+\item Our strategy keep mechanical properties more constant.
+\item The computation times are approximately 3(?) times as fast as the state of the art method for naive toolpath generation employing constant width.
 \end{itemize}

### 2019-08-11 8_discussion.tex
more conclusions

@@
 The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
-\todo{[figure showing wedges, naive toolpaths and gaps]}
+See \cref{naive_overfill_underfill}
 Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
@@
 \subsection{Comparison of different beading strategies}
-\todo{Discussion of finding of Validation section}\
+\todo{Discussion of finding of Validation section}
 
@@
 This can be seen in \cref{applications_gear}.
+
+\subsection{Computation time}
+Algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$.
+The number of elements in the trapezoidation is linear in the number of elements in the VD.
+All of the stages of our framework are also linear in the number of elements in the skeleton.
+
+Experiments.
+The computation time is comparable to the naive method as implemented using Clipper.

### 2019-08-12 10_applications.tex
write applications section

@@
 \section{Applications}
+Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.
+Although the algorithm improves performance for all parts compared to existing techniques, the enhancement is percentually larger for thin parts.
 
-\subsection{Thin parts}
-\begin{itemize}
-\item Casings (e.g. for electronics)
-\item Prototypes for blowmold parts or sheet metal parts etc.
-\item Miniature models, architectural models
-\item Microstructures
-\item Lithophanes
-\end{itemize}
+\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
+\Cref{application_closeups} highlights closeups of the generated toolpaths.
+Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
+Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.
 
-Show the effect of the planned toolpath on the performance of varying thickness microstructures.
-Compare to \cite{bates2018compressive}.
+Architectural models and casings benefit from preventing very thin regions from being filled at all and from the prevention of over- and underfill within thin walls, which makes them stronger.
+Embossed text benefits from the prevention of underfill areas, which would cause various holes in top surfaces, which is detrimental to the visual quality of those top surfaces.
+Gears benefit from the preventio of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout.
 
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.1\textwidth}
-\setlength{\figheight}{0.1\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/david.png}
-\caption{Statue}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/gyroid.png}
-\caption{Gyroid}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
-\caption{Hex}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/house.png}
-\caption{House}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
-\caption{Gear}\label{applications_gear}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
-\caption{Case}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
-\caption{Bone}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
-\caption{TUD}%label{applications_}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
-\caption{UM}%label{applications_}
-\end{subfigure}
-\caption{
-Closeups of results for the inward distributed beading strategy for various applications.
-The extrusion widths are visualized exaggeratedly and using a color scheme exaplained in \cref{visualized_accuracy}.
-}
-\label{application_closeups}
-\end{figure*}
+Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
+For example the result of a topology optimized structure can contain filaments of varying thickness \cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
+Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
+\cref{applications_gyroid} shows how an angled gyroid structure with homogenous thickness results in heterogeneous outline shapes.
+Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
+\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case.
+\cite{bates2018compressive}
 
@@
 \end{figure}
+
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.1\textwidth}
+\setlength{\figheight}{0.1\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/house.png}
+\caption{House}\label{applications_house}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
+\caption{Case}\label{applications_case}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/david.png}
+\caption{Statue}\label{applications_statue}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
+\caption{TUD}\label{applications_tud}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
+\caption{UM}\label{applications_um}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
+\caption{Gear}\label{applications_gear}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
+\caption{Bone}\label{applications_bone}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/gyroid.png}
+\caption{Gyroid}\label{applications_gyroid}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
+\caption{Hex}\label{applications_hex}
+\end{subfigure}
+\caption{
+Closeups of results for the inward distributed beading strategy for various applications.
+The extrusion widths are visualized exaggeratedly and using a color scheme exaplained in \cref{visualized_accuracy}.
+}
+\label{application_closeups}
+\end{figure*}
 

### 2019-08-12 6_validation.tex
write widening section as addendum to strategy

@@
 
+Determining what the optimal distribution scheme would be is left as future work.
+
+\paragraph{Widening}
+Complementary to any of these strategies we can enforce a minimum feature size at no extra cost in our framework.
+Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
+We can simply override
+\begin{align*}
+W'(n,d)_1 &=
+\begin{cases}
+\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
+W(n,d)_1 & \text{ otherwise}
+\end{cases}
+\end{align*}
+
 \subsection{Computational analysis}

### 2019-08-12 4_method.tex
explain segment generation better
follows new algorithm
shows how segments are generated for a single trapezoid

@@
 We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
-\todo{TODO: Image}
+See \cref{segment_generation}.
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
@@
 
-All segments are then connected together into polylines, which are then closed into polygonal toolpaths.
-The odd center segments remain in polylines, so the final toolpaths contain both polygonal paths and open polyline paths.
+Each of the trapezoids is connceting to a single outline polygon.
+By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
+See \cref{segment_generation}.
+In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.
+
+\begin{figure}
+\centering
+\includegraphics[width=.3\columnwidth]{sources/method/segment_generation.pdf}
+\caption{
+Generating toolpaths on a aprt of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
+Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.
+By following the trapezoids along the domain (cyan) of a single outline polygon,
+the segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
+}
+\label{segment_generation}
+\end{figure}
 

### 2019-08-12 4_method.tex
better MAT explanation and better segment generation figures

@@
 \centering
-\includegraphics[width=.3\columnwidth]{sources/method/segment_generation.pdf}
+\includegraphics[width=.4\columnwidth]{sources/method/segment_generation.pdf}
 \caption{
-Generating toolpaths on a aprt of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
+Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
 Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.

### 2019-08-12 12_conclusions_future_work.tex
Tim: spell check

@@
 \item Our framework is stable against slight perturbations of the outline shape or large perturbations of the outline shape in far away regions.
-\item We can define a strategy which distibutes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
+\item We can define a strategy which distributes the bead width deviation over a small region so as to retain smooth toolpaths of nominal width throughout the larger part of big regions.
 \item Our strategy keep mechanical properties more constant.

### 2019-08-12 4_method.tex
Tim: spell check

@@
 Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
-We decide on a bead count at locations which lie in centeral positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the centeral regions outward.
+We decide on a bead count at locations which lie in central positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the central regions outward.
 
@@
 
-Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is disctoninuous,
-or it can be defined as the locations where wavefront propagating from the outline shape make sharp corners. \cite{blum1967transformation}
-This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wavefronts from the outline.
+Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is discontinuous,
+or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
+This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
 The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
@@
 \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
-\caption{Wavefronts}
+\caption{Wave-fronts}
 \end{subfigure}
@@
 The medial axis can be defined in terms of the the number of support points of the inscribed circles,
-as the pinch sites in wavefronts
+as the pinch sites in wave-fronts
 or as ridges in a volume defined by the union of cones.
@@
 (The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
-We repesent such a skeleton in a standard half-edge datastructure.
+We represent such a skeleton in a standard half-edge data-structure.
 See \cref{shape_decomposition_simple}.
@@
 That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical represenatation of the medial axis; see \cref{mat_3d}.
+This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical representation of the medial axis; see \cref{mat_3d}.
 
@@
 \subsubsection{Significance measure}\label{sec:significance_measure}
-Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which arew in some sense \emph{central} to the shape.
+Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which are in some sense \emph{central} to the shape.
 This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
@@
 \caption{
-Overfill and underfill areas in a naive beading using a constant bead witdh $w$ of a wedge area with vertex angle $\beta$.
+Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
 The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
@@
 The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
-Because transitions in bead count only occurs in locations where the prefered bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.
+Because transitions in bead count only occurs in locations where the preferred bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.
 
@@
 
-In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the coresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
+In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
 If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
@@
 \begin{itemize}
-\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
+\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
@@
 Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
-We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry contraints on the upper indices.
+We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
 See \cref{beading_interpolation}.
@@
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
-If a central edge has both nodes with an odd beadcount assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
+If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
 We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
 
-Each of the trapezoids is connceting to a single outline polygon.
+Each of the trapezoids is connecting to a single outline polygon.
 By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.

### 2019-08-12 6_validation.tex
Tim: spell check

@@
 $$t_0(n) =  t(n) \left( b^{-1}(n) / 0.4  - n \right)$$
-This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the prefered bead width for a similar nozzle size.
+This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the preferred bead width for a similar nozzle size.
 
-Our beading strategies are based on a prefered width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
+Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
 
@@
 Distribute the overfill or underfill which would happen using a naive strategy over all beads.
-This maximizes robustness and minimizes narrow beads qhich are difficult to print.
+This maximizes robustness and minimizes narrow beads which are difficult to print.
 
@@
 That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
-This helps if print settings for bead widths other than the prefered width aren't calibrated as well as the settings for $w_\text{pref}$.
+This helps if print settings for bead widths other than the preferred width aren't calibrated as well as the settings for $w_\text{pref}$.
 Toolpaths with deviating widths might result in less dimensional accuracy on the outline and uncalibrated mechanical properties throughout the volume, so limiting the number of beads width deviating bead width might be beneficial.
@@
 
-We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then takign the difference from the original outline shape.
-In order to deal with rounding errors we perform a morpholocial close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
+We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
+In order to deal with rounding errors we perform a morpholocical close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
 
@@
 In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
-These tripple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualzied for the different toolpath strategies in the top of \cref{visualized_accuracy}.
+These triple extrusion areas count double toward the total amount of overfill.
+The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
 

### 2019-08-12 6_validation.tex
motivate inward distributed strategy

@@
 That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
-This helps if print settings for bead widths other than the preferred width aren't calibrated as well as the settings for $w_\text{pref}$.
-Toolpaths with deviating widths might result in less dimensional accuracy on the outline and uncalibrated mechanical properties throughout the volume, so limiting the number of beads width deviating bead width might be beneficial.
-\todo{Emphasize this point more. Put it in the abstract and conclusion.}
+This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
+Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.
 
-Determining what the optimal distribution scheme would be is left as future work.
+Determining what the optimal distribution scheme would be for a particular hardware setup is left as future work.
 

### 2019-08-12 12_conclusions_future_work.tex
write conclusion

--- 2019-08-05 12_conclusions_future_work.tex
@@
 \section{Conclusion and future work}
+In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
+Our framework is shown to be flexible, since we have shown several beading strategies which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
+Our framework is robust and local, meaning that small changes in the toolpath are caused by small local changes in the outline shape.
 
-\begin{itemize}
-\item Accurate filling using few/small overfill and underfill areas
-\item Which allows for accurate reproduction of thin parts and variable thickness microstructures.
-\item Our framework is able to emulate several previously proposed methods
-\item Our framework allows for deposition width control which reduces the amount of extrusion paths with wildly different width compared to previous methods
-\item Our framework allows for limiting the stretch on the outer toolpath in order to reduce any adverse affect of variable extrusion width on dimensional accuracy.
-\item The computation times are approximately 3 times as fast as the state of the art method for naive toolpath generation employing constant width
-\item (depending on what we do in the validation chapter) The produced parts employing our method are more stiff compared to other methods.
-\end{itemize}
+We have introduced the inward distributed beading strategy which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
+and instead distributes the deviation in bead width over several beads near the center of the shape.
+That way the impact of adaptive bead width on mechanical properties of the resulting print are limited.
+Moreover the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realized adaptive bead width.
+
+The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
+On the other hand it leaves most of the toolpaths the same as the naive method in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.
 
 \subsection{Future work}
-Define the optimal strategy for a given piece of hardware by finding an accurate objective function which takes into account the manufacturability or dimensional accuracy as a function of bead width and its effect on qualities of top layers, stiffness or the dimensional accuracy of the outline shape.
+The work presented here is evaluated mostly on a theoretical level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the validation of our techniques.
+Future research might be devoted to optimizing the distribution scheme to a specific hardware setup.
+If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading strategy.
 
-Use Skeletal Trapezoidation to generate quad dominant meshings for FEM.
+In its current form the skeleton has been used to determine toolpaths based on the local feature size.
+One direction of future research could be devoted to incorporating other information.
+We could for example make the bead widths depend on properties on the outline, such as curvature or visibility.
+We could also take into account volumetric considerations such as the toolpathing of the previous layer or some volumetric constraint defined by a functionally graded material.
 
-Generate thicker bead widths near sharp corners in order to mimic limitations in the extrusion process.
-Allow for adjusting the toolpath widths to local part curvature.
-
-Allow for information sharing between the layers.
+Taking a broader perspective we note that the skeletonization decomposes a shape into trapezoids and these trapezoids are decomposed into quads by the toolpath segments which we generate for it.
+It would be interesting to see if similar technique can be used to generate quad dominant meshings for finite element analysis.

### 2019-08-12 2_related_work.tex
some lil related work updates
new ref for zigzag toolpaths
related work in progress - Jun

@@
 
+Toolpath generation is an integral part of process planning for 3D printing.
+For an overview of the processing pipeline, we refer to the survey by Levesu et al.~\cite{Livesu2017CGF} .
+For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
+In this paper, we focus on generating toolpath that seamlessly covers the entire 2D contour.
+This is sometimes called dense infill~\cite{Livesu2017CGF}.
+
+Direction parallel and contour parallel are two basic toolpath strategies.
+Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
+These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
+Contour parallel infill consists of a set of equally spaced offset contours from the slice boundary.
+A strategy to connect the parallel offsets was introduced in [].
+One of the problems with contour parallel infill is that it tends to leave gaps within the slices.
+This is due to the fact that the offset contour meets around the medial axis and the remaining space might not match exactly the (constant) deposition width.
+To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
+Close to the slice boundary there are a few contour parallel curves, while into the interior there is a zig-zag pattern.
+The entire cross-section could also be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014}.
+To reduce the number of sharp turns thereby enable faster motions, Zhao et al proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
+Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD}.
+
+Our method to reduce underfilling is related to the work by Kao and Prinz~\cite{kao1998optimal}.
+Instead of uniformly offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton.
+This approach originally handles simply geometry where there are no branches in the medial axis.
+This was extended by Ding et al to handle complex shape~\cite{}.
+For this purpose, they made use of the medial axis to decompose the slice into different components.
+This approach
+
+Our idea to reduce under- and over-filling is to deposit with varying width which allows the opportunity to locally match the space between adjacent paths.
+Varying width extraction can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
+This width is varying but bounded.
+
 \subsection{Toolpath strategies}
-
-\todo{Find reference on patchwise Zig-Zag toolpathing strategy.}
+Simple Zig-Zag toolpathing strategy. \cite{mcmains2000layered}
+Patchwise Zig-Zag toolpathing strategy. \cite{Ding2014}
 
@@
 
-Defining a continuous extrusion Zig-Zag toolpath. \cite{Jin2017}
+Fractal based toolpaths. \cite{Griffiths1994, mandal2016}
 

### 2019-08-12 2_related_work.tex
revised the related work - Jun

--- 2019-05-19 2_related_work.tex
@@
 \section{Related Work}
-Adjusted MAT structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
-\Cref{moessen}
-Problem: small grey areas which are too small for the second wall lines.
 
-Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017}
-\Cref{jin}
+Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
+The nozzle is then instructed to move along the path while extruding material.
+The deposited material covers the path with a certain width.
+Toolpath generation is an integral part of process planning for 3D printing.
+For an overview of the processing pipeline, we refer to the survey by Levesu et al.~\cite{Livesu2017CGF} .
+For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
+In this paper, we focus on generating toolpath that seamlessly covers the entire 2D contour.
+This is sometimes called dense infill~\cite{Livesu2017CGF}.
 
-Using variable width lines to fit a precise amount of lines using the MAT.
-\cite{Ding2016a} apply the method from \cite{kao1998optimal}.
-\Cref{ding}
+Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
+There are a few desirable properties for the toolpath.
+First, the path shall be as continuous as possible.
+A discontinuous path requires to stop and restart material extrusion.
+For certain material such as TPU, this could lead to material defect~\cite{KUIPERS2019CAD}.
+Furthermore, a smooth path is often preferred.
+A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
+Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling.
+Our method is primarily concerned with this requirement.
 
-\begin{figure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/related_work/moessen.jpg}
-\caption{asfd}
-\label{moessen}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}
-\includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
-\caption{asfd}
-\label{jin}
-\end{subfigure}
-\end{figure}
+Direction parallel and contour parallel are two basic toolpath strategies.
+Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
+These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
+Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
+A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}.
+One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
+This is due to the fact that the offset contour meets around the medial axis and the remaining space might not match exactly the (constant) deposition width.
+To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
+Close to the slice boundary there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
+For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014}.
+To reduce the number of sharp turns thereby enable faster motions, Zhao et al proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
+Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
-\includegraphics[width=.7\columnwidth]{sources/related_work/kao.jpg}
-\caption{Path planning strategies proposed by Kao (bottom) and employed in FDM by Ding et al (top).}
-\label{ding}
-\end{figure}
+Our idea to reduce under- and over-filling is to deposit material with a varying width.
+This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better coverage of the domain.
+Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018}.
+However, we note that the range of possible widths is not unlimited.
+For instance, printing a width that is twice the nozzle radius is challenging.
+Our method to reduce underfilling is related to the work by Kao and Prinz~\cite{kao1998optimal}.
+Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton.
+This approach originally handles simply geometry where there are no branches in the medial axis.
+This was extended by Ding et al to handle complex shapes~\cite{Ding2016a}.
+For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
+This extension, however, inherits a problem in the original method.
+From any point in the geometry skeleton to the boundary, the number of contours is constant.
+Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
+In this paper we propose an adaptive beading strategy to address this problem.
+
+Besides under- and over-filling, there are a few other robustness issues in toolpath generation, especially concerning thin geometric features.
+Moesen et al.
+proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
+Behandish et al.
+presented a method to characterize local topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
+
+% \subsection{Toolpath strategies}
+% Simple Zig-Zag toolpathing strategy. \cite{mcmains2000layered}
+% Patchwise Zig-Zag toolpathing strategy. \cite{Ding2014}
+
+% Combining concentric toolpaths into continuous extrusion spirals. \cite{Held2009}
+
+% Fractal based toolpaths. \cite{Griffiths1994, mandal2016}
+
+% \subsection{Space filling toolpaths}
+% \todo{find other literature which tries to minimize underfilling and overfilling which is not based on a skeletonization.}
+
+% \subsection{Medial axis based toolpaths}
+% Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
+% \Cref{moessen}
+% Problem: small grey areas which are too small for the second wall lines.
+
+% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017}
+% \Cref{jin}
+
+% Using variable width lines to fit a precise amount of lines using the MAT.
+% \cite{Ding2016a} apply the method from \cite{kao1998optimal}.
+% \Cref{ding}
+
+% \begin{figure}
+% \begin{subfigure}{0.45\columnwidth}
+% \includegraphics[width=\columnwidth]{sources/related_work/moessen.jpg}
+% \caption{\citeauthor{Moesen2011}}
+% \label{moessen}
+% \end{subfigure}
+% \begin{subfigure}{0.45\columnwidth}
+% \includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
+% \caption{\citeauthor{Jin2017}}
+% \label{jin}
+% \end{subfigure}
+% \end{figure}
+
+% \begin{figure}
+% \centering
+% \includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
+% \includegraphics[width=.7\columnwidth]{sources/related_work/kao.jpg}
+% \caption{Path planning strategies proposed by Kao (bottom) and employed in FDM by Ding et al (top).}
+% \label{ding}
+% \end{figure}
+
+% \subsection{Variable extrusion width}
+
+% Changing extrusion rate and temperature to match a given velocity. \cite{Ertay2018}
+
+% Changing velocity in order to change extrusion rate.
+% Shortly discussed in \cite{Kuipers2018}.
+% \todo{find another reference}

### 2019-08-13 6_validation.tex
more validation changes

@@
 
-\paragraph{Manufacturability}
-Depending on the hardware configuration some bead widths are difficult to manufacture.
+\paragraph{Uniformity}
+Depending on the hardware configuration some bead widths might be difficult to manufacture.
 A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine.
-\todo{Tim should put pictures of extremal bead widths in introduction!}
+\todo{Include picture of flutter?}
+Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
 We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
@@
 \subsection{Experimentation}
-\todo{Tim will print objects and show qualities:}
+Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle,
+which employs linear advance on a direct drive extruder for accurate deposition width control.
+We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+
+\todo{Maybe test the following qualities:}
 \begin{itemize}
 \item visual consistency of flat top skin surface
-\item visual gradual transparency changes
 \item graphs of tensile tests on thin walled object

### 2019-08-13 2_related_work.tex
Add newline after sentence end.
Tim: citeauthor instead of '[auth] et al'

@@
 Toolpath generation is an integral part of process planning for 3D printing.
-For an overview of the processing pipeline, we refer to the survey by Levesu et al.~\cite{Livesu2017CGF} .
+For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}.~\cite{Livesu2017CGF} .
 For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
@@
 For certain material such as TPU, this could lead to material defect~\cite{KUIPERS2019CAD}.
-Furthermore, a smooth path is often preferred.
-A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
+Furthermore, a smooth path is often preferred. A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
 Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling.
@@
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014}.
-To reduce the number of sharp turns thereby enable faster motions, Zhao et al proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
+To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
 Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.
@@
 Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018}.
-However, we note that the range of possible widths is not unlimited.
-For instance, printing a width that is twice the nozzle radius is challenging.
+However, we note that the range of possible widths is not unlimited. For instance, printing a width that is twice the nozzle radius is challenging.
 Our method to reduce underfilling is related to the work by Kao and Prinz~\cite{kao1998optimal}.
@@
 This approach originally handles simply geometry where there are no branches in the medial axis.
-This was extended by Ding et al to handle complex shapes~\cite{Ding2016a}.
+This was extended by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
 For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
@@
 Besides under- and over-filling, there are a few other robustness issues in toolpath generation, especially concerning thin geometric features.
-Moesen et al.
-proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
-Behandish et al.
-presented a method to characterize local topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
+\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
+\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
 

### 2019-08-13 10_applications.tex
write widening section as addendum to strategy
test print results

@@
 \end{figure*}
-
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{sources/applications/wedge_print_v2.png}
-\caption{
-A small wedge shape printed using the variable width scheme prescribed by the ditributed beading strategy.
-Small gaps have been added in between the extrusion paths so that the toolpaths can easily be identified separately.
-}
-\label{wedge_print}
-\end{figure}
-
-\subsection{Widening}
-Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.

### 2019-08-13 6_validation.tex
test print results

@@
 We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
 
+\begin{figure}
+\centering
+\begin{subfigure}{\columnwidth}\centering
+\setlength{\figwidth}{\columnwidth}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
+\caption{Wedge}\label{print_wedge}
+\end{subfigure}
+\caption{
+A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
+The wedge print can be read like a graph with model diameter on the X-axis and the resulting beads over the Y-axis.
+The naive and center deviation strategy show problems around certain model diameters.
+}
+\label{wedge_print}
+\end{figure}
+
+\begin{figure}
+\centering
+\setlength{\figheight}{.38\columnwidth}
+\setlength{\figwidth}{0.32\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
+\caption{Naive}\label{print_naive}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
+\caption{Center deviation}\label{print_center}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
+\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
+\caption{Inward distributed}\label{print_inward}
+\end{subfigure}
+\caption{
+Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
+The naive method produces distinct underfill areas.
+The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
+The inward distributed strategy produces the least defects.
+}
+\label{wedge_print}
+\end{figure}
+
+\iffalse
 \todo{Maybe test the following qualities:}
@@
 \end{itemize}
+\fi

### 2019-08-14 2_related_work.tex
Tim: some more newlines
Tims edits to Juns related work

@@
 A discontinuous path requires to stop and restart material extrusion. 
-For certain material such as TPU, this could lead to material defect~\cite{KUIPERS2019CAD}.
-Furthermore, a smooth path is often preferred. A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
+For certain material such as TPU, this could lead to material defects~\cite{KUIPERS2019CAD}.
+Furthermore, a smooth path is often preferred.
+A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
 Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling.
@@
 A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}.
+\todo{Tim: connecting the contour parallel lines is also exactly what the Fermat spiral papers are about.}
 One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
@@
 This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better coverage of the domain.
-Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018}.
-However, we note that the range of possible widths is not unlimited. For instance, printing a width that is twice the nozzle radius is challenging.
-Our method to reduce underfilling is related to the work by Kao and Prinz~\cite{kao1998optimal}.
+Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
+However, we note that the range of possible widths is not unlimited.
+For instance, printing a width that is tripple the nozzle diameter is challenging.
+Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
 Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton.
@@
 
+\todo{TODO: Describe the paper by } \citeauthor{Jin2017}
+
 Besides under- and over-filling, there are a few other robustness issues in toolpath generation, especially concerning thin geometric features.
+\todo{Being able to print thin geometrical features can be seen as a a special case of the goal to preventing underfill regions.}
 \citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.

### 2019-08-14 1_intro.tex
Tim: spell check
show jins result in intro

@@
 
-FDM printers expell molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
+FDM printers expel molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
 Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
@@
 \includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_pretty.png}
 \includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
 \caption{
-Toolpaths for a wedge shape using the naive offsetting approach (top) and our approach (bottom).
+Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017}(middle) and our approach (bottom).
 Red signifies overfill and blue underfill.

### 2019-08-14 2_related_work.tex
Zjenjas analysis and some of Juns related work

@@
 Close to the slice boundary there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
-For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014}.
+For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017JCIM}.
 To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.

### 2019-08-14 6_validation.tex
moved accuracy figure down to validation section
Zjenjas analysis and some of Juns related work
lil

@@
 \end{align*}
-
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.19\textwidth}
-\setlength{\figheight}{0.283\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
-\caption{Naive}\label{TEST_naive_accuracy}
-\end{subfigure}
-%\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
-%\caption{Single}\label{TEST_SingleBead_accuracy}
-%\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
-\caption{Constant}\label{TEST_Constant_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
-\caption{Center}\label{TEST_Center_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
-\caption{Distributed}\label{TEST_Distributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
-\caption{Inward}\label{TEST_InwardDistributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{.04\columnwidth}\centering
-\vspace{4cm}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
-\end{subfigure}
-\caption{
-Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
-Grey areas are covered by extruded material,
-blue areas in the top images signify underfill regions,
-red areas overfill,
-orange areas triply extruded areas (double overfill).
-The bottom visualized the bead widths at each location by exaggerating their widths.
-Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
-}
-\label{visualized_accuracy}
-\end{figure*}
 
@@
 
-\paragraph{Distributed strategy}
+\paragraph{Evenly distributed strategy}
 Distribute the overfill or underfill which would happen using a naive strategy over all beads.
@@
 \end{align*}
-
-\todo{TODO: check $n$ vs $n-1$ everywhere when comparing indices and the total size! Largest index should be $n-1$, not $n$!}
 
@@
 \end{align*}
+
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.19\textwidth}
+\setlength{\figheight}{0.283\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
+\caption{Naive}\label{TEST_naive_accuracy}
+\end{subfigure}
+%\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
+%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
+%\caption{Single}\label{TEST_SingleBead_accuracy}
+%\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
+\caption{Constant}\label{TEST_Constant_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
+\caption{Center}\label{TEST_Center_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
+\caption{Distributed}\label{TEST_Distributed_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
+\caption{Inward}\label{TEST_InwardDistributed_accuracy}
+\end{subfigure}
+\begin{subfigure}{.04\columnwidth}\centering
+\vspace{4cm}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
+\end{subfigure}
+\caption{
+Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
+Grey areas are covered by extruded material,
+blue areas in the top images signify underfill regions,
+red areas overfill,
+orange areas triply extruded areas (double overfill).
+The bottom visualized the bead widths at each location by exaggerating their widths.
+Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
+}
+\label{visualized_accuracy}
+\end{figure*}
 
@@
 The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/validation/overunderfill.pdf}
+\caption{total over and underfill for all data}
+\label{over_underfill}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/validation/smoothness.pdf}
+\caption{occurrence of angles between consecutive segments}
+\label{smoothness}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/validation/SD.pdf}
+\caption{variation in extrusion width (standard deviation)}
+\label{sd}
+\end{figure}
 
@@
 }
-\label{wedge_print}
+\label{prints}
 \end{figure}

### 2019-08-14 6_validation.tex
lil rewrite of experimentation

@@
 \subsection{Experimentation}
-Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle,
-which employs linear advance on a direct drive extruder for accurate deposition width control.
+Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
+The firmware of the printer employs linear advance~\cite{linadvance}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
 We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
+
+The resulting prints are viewed in \cref{wedge_print} and \cref{prints}.
+Because of inaccuracies in the depositioning control system some of the prints show defects.
+Such defects are less prevalant for the inward distributed beading strategy than the other strategies.
 

### 2019-08-14 2_related_work.tex
Juns related work edits

@@
 Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
-A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}.
-\todo{Tim: connecting the contour parallel lines is also exactly what the Fermat spiral papers are about.}
+A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
+To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
 One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
@@
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017JCIM}.
-To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}.
 Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.
@@
 Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
-This approach originally handles simply geometry where there are no branches in the medial axis.
-This was extended by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
+Skeleton was also used in~\cite{Jin2017} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
+The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
+An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
 For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
@@
 In this paper we propose an adaptive beading strategy to address this problem.
-
-\todo{TODO: Describe the paper by } \citeauthor{Jin2017}
 

### 2019-08-14 1_intro.tex
update outdated citation keys

@@
 \caption{
-Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017}(middle) and our approach (bottom).
+Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
 Red signifies overfill and blue underfill.

### 2019-08-14 2_related_work.tex
update outdated citation keys

@@
 
+% This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
 Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
@@
 
+% criteria for toolpath generation
 Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
@@
 Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling. 
-Our method is primarily concerned with this requirement.
+An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
+Our method is primarily concerned with minimizing under- and overfill within slices, i.e. horizontal cross-sections.
 
+% basic toolpath strategies and their variations
 Direction parallel and contour parallel are two basic toolpath strategies.
@@
 To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
+Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
 One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
@@
 Close to the slice boundary there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
-For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017JCIM}.
+For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
 Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.
 
+% the idea, and (some of) the most related work
 Our idea to reduce under- and over-filling is to deposit material with a varying width.
@@
 Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
-Skeleton was also used in~\cite{Jin2017} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
+Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
 The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
@@
 
-Besides under- and over-filling, there are a few other robustness issues in toolpath generation, especially concerning thin geometric features.
-\todo{Being able to print thin geometrical features can be seen as a a special case of the goal to preventing underfill regions.}
+% the context where our method can be positioned, and some related problems in that context
+Under- and over-filling are especially problematic for thin geometric features. \citeauthor{Jin2017a} proposed the use of a wavy path pattern for thin-walled parts~\cite{Jin2017a}. 
+This pattern is intended to be sparse. 
+Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
 \citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
@@
 
-% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017}
+% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017JMS}
 % \Cref{jin}
@@
 % \includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
-% \caption{\citeauthor{Jin2017}}
+% \caption{\citeauthor{Jin2017JMS}}
 % \label{jin}

### 2019-08-14 4_method.tex
more improvements to segment generation figure
(re)write eading strategies section

@@
 
-\begin{definition}
+\begin{definition}\label{beading_strategy_definition}
 We define a beading strategy as the following set:
@@
 The following restrictions hold:
-\begin{itemize}
+\begin{enumerate}
 \item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
@@
 \item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\end{itemize}
+\end{enumerate}
 
@@
 \centering
-\includegraphics[width=.4\columnwidth]{sources/method/segment_generation.pdf}
+\includegraphics[width=.5\columnwidth]{sources/method/segment_generation.pdf}
 \caption{

### 2019-08-14 6_validation.tex
update outdated citation keys
(re)write eading strategies section

@@
-\section{Validation}
-We use the following constants:
-\begin{align}
+\section{Beading strategies}
+Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
+We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
+We also introduce new beading strategies which produce toolpaths with less extremal widths then techniques from existing literature.
+
+A beading strategy was defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
+Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
+Most of the beading strategies we introduce share a common ground:
+\begin{align*}
 d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
 d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
-t_\text{beading} &= \SI{0.4}{\milli\meter} \\
-d_\text{max}^\text{intersection} &= \SI{75}{\percent}
-\end{align}
-
-We use a transition anchor position of
+t_\text{beading} &= w_\text{pref} \\
+d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
+%
+%We use a transition anchor position of
 %$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
@@
 %$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
-$$t_0(n) =  t(n) \left( b^{-1}(n) / 0.4  - n \right)$$
-This should ensure that the transitions never overlap with the locations $v$ where $2 R(v) = 0.4n$ for $n \in \mathbb{N}$, since \SI{0.4}{\milli\meter} is the preferred bead width for a similar nozzle size.
-
-Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
-
-We set 
-\begin{align*}
+t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
 t(n) &= w_\text{pref} \\
@@
 
-\subsection{Strategies}
-We can emulate a variety of toolpath generation methods from related literature by applying various beading strategies to our framework.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_\text{pref}$ for $n \in \mathbb{N}$.
+The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
+The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
+The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.
 
 \paragraph{Naive Strategy}
-Because the naive strategy never employs single line polyline segments, we disable marking edges using the significance measure by choosing the limit angle.
+We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
 \begin{align*}
 \alpha_\text{max} &= \SI{180}{\degree} \\
-b(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
 W(n,d)_i &= w_\text{pref} \text{ for all } i 
@@
 \paragraph{Only outer bead}
-Emulates \cite{Moesen2011}. We don't reduce line segments in 3-way intersections.
-
-$d_\text{max}^\text{intersection} = \SI{0}{\percent}$
+We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
+Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
 
 \begin{align*}
+d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
 t(n) &= 0 \\
@@
 \paragraph{Constant bead count}
-Emulates \cite{Ding2016a}. We unmark all outer segments.
+We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
+Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
+Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the skeletal graph is not stable against those.
 
 \begin{align*}
-\alpha_\text{max} &= \SI{180}{\degree} \\
+\alpha_\text{max} &= \SI{0}{\degree} \\
 b(d) &= C \\
@@
 
-\paragraph{Deviating toolpath at center}
-Emulates \cite{Jin2017}
-
-$r_\text{min} = 0.8 w_\text{pref}$ and $r_\text{max} = 1.25 w_\text{pref}$
+\paragraph{Deviating center}
+We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
+We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
+\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
+Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
+We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
 
@@
 
-\paragraph{Evenly distributed strategy}
-Distribute the overfill or underfill which would happen using a naive strategy over all beads.
-This maximizes robustness and minimizes narrow beads which are difficult to print.
+\paragraph{Evenly distributed}
+By taking the advantages of the above two strategies we can define a beading strategy which constitutes a novel toolpathing technique.
+We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
+We determine the local bead count by dividing the diameter by the prefered bead width and rounding to the nearest integer.
+This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.
 
@@
 \paragraph{General distributed strategy}
-Distribute the overfill or underfill which would happen using a naive strategy $E$ over all beads unevenly depending on some weighing function $M(n.d)$, which defines the portion of overfill or underfill which would occur in the naive strategy to distribute to each junction.
+The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total prefered width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
+$w_\text{pref} + E / n$.
+However, depending on the application we might want a different distribution of widths.
+We therefore supply a beading strategy which supports an arbitrary distribution of the discrepancy.
+The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
 
@@
 $$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
-To distribute the hypothetical over-/underfill over the innermost $2N$ beads, and distribute most of it to the inner beads.
-That way we limit the impact of the distributed strategy and have the nominal bead width $w_\text{pref}$ in regions farther away from the middle.
+to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
+That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
+% and it forces most of the beads to have exactly the prefered width.
 Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.
-
-Determining what the optimal distribution scheme would be for a particular hardware setup is left as future work.
 
@@
 \end{align*}
+
+\section{Validation}
 

### 2019-08-14 6_validation.tex
Juns related work & Tims renaming of beading strategies

@@
 
-\paragraph{Naive Strategy}
+\paragraph{Naive Beading Strategy}
 We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
@@
 
-\paragraph{Only outer bead}
+\paragraph{Outer bead}
 We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
@@
 
-\paragraph{Deviating center}
+\paragraph{Centered}
 We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
@@
 
-\paragraph{Inward distributed strategy}
+\paragraph{Inward distributed}
 For example, we can choose 

### 2019-08-14 8_discussion.tex
rewrote computation time

--- 2019-08-10 8_discussion.tex
@@
 
-\subsection{Comparison of different beading strategies}
-\todo{Discussion of finding of Validation section}\
+\subsection{Computation time}
+Algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
+The number of elements in the trapezoidation is linear in the number of elements in the VD
+and all of the stages of our framework are also linear in the number of elements in the skeleton,
+so the total running time of our algorithm is $O(n \log n)$.
 
-Naive strategy causes a lot of overfills and underfills.
+From the experimental results shows in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
+The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
+
+\subsection{Comparison of beading strategies}
+\todo{Discussion of finding of Validation section}
+
+The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
+
+Naive method causes a lot of overfills and underfills.
 This overpoweres any positive effect of perfectly homogeneous bead width.

### 2019-08-14 6_validation.tex
Zjenjas validation
zjenja: added validation figures
zjenja: new validation figures

@@
 \paragraph{General distributed strategy}
-The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total prefered width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
+The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
 $w_\text{pref} + E / n$.
@@
 orange areas triply extruded areas (double overfill).
-The bottom visualized the bead widths at each location by exaggerating their widths.
+The bottom visualizes the bead widths at each location by exaggerating their widths.
 Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
@@
 Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The naive method was implemented using the state-of-the-art polygon offset library called Clipper. \cite{johnson2014clipper}
+The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
 
 \paragraph{Accuracy}
-In order to estimate the overfill and underfill we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use a isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment we would get strange artifacts at corners in the toolpath.
+In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
+If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
 We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{sources/validation/SD.pdf}
-\caption{variation in extrusion width (standard deviation)}
+\includegraphics[width=\columnwidth]{sources/validation/widthHistogram.pdf}
+\caption{Distribution of extrusion width, sampled at 200$\mu$m, visualized data is binned at intervals of 10$\mu$m}
 \label{sd}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{sources/validation/computime2.pdf}
+\caption{Computation time per slice}
+\label{computime}
 \end{figure}

### 2019-08-14 6_validation.tex
zjenja: added some text to validation

@@
 
+\todo{describe dataset of 3d models and random slices...
+X number of 3d files.
+varying in size, topology, features (size).
+random selection of slices.
+300 slices total.
+5 toolpath strategies were applied for each layer.}
+
 \begin{figure*}
@@
 The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
+The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
+\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
 
@@
 If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
-We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
+We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
 For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
@@
 We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
-In order to deal with rounding errors we perform a morpholocical close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
+In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
 
@@
 
+We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
+The overfill and underfill area as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
+The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
+This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to on dataset.
+
 \begin{figure}
 \includegraphics[width=\columnwidth]{sources/validation/overunderfill.pdf}
-\caption{total over and underfill for all data}
+\caption{total over and underfill for entire dataset}
 \label{over_underfill}
@@
 \includegraphics[width=\columnwidth]{sources/validation/widthHistogram.pdf}
-\caption{Distribution of extrusion width, sampled at 200$\mu$m, visualized data is binned at intervals of 10$\mu$m}
-\label{sd}
+\caption{Distribution of extrusion width, sampled at  \SI{200}{\micro\meter}, visualized data is binned at intervals of  \SI{10}{\micro\meter}}
+\label{widthHistogram}
 \end{figure}
@@
 
-\todo{Zjenja should visualize overfill and underfill results in tables and/or graphs.}
-
 \paragraph{Uniformity}
-Depending on the hardware configuration some bead widths might be difficult to manufacture.
+Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
 A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
+Also, large bead widths can cause the extruded material to upwards instead of filling the required width.
 \todo{Include picture of flutter?}
@@
 We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
+
+To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
+at intervals of \SI{200}{\micro\meter} along the toolpath.
+From these sampled values, we calculated the mean bead width, and standard deviation.
+\cref{widthHistogram} shows the distribution of extrusion width for each strategy.
+The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count".
+These values indicate that, while causing less overfill and underfill, our strategy deviates less and less often from the nominal nozzle size.
+
+\paragraph{Smoothness of toolpaths}
+In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
+For each strategy, we measured the angle between consecutive segments.
+The relative frequency of these angles is shown in \cref{smoothness}.
+While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.
 

### 2019-08-15 20_dataset.tex
describe dataset

\section{Dataset}\label{dataset}
The dataset we tested on was a custom selected set of open source 3D models found on the internet which was selected to cover a broad range of different types of application and geometry.
Applications range from prototypes, to fixtures and mechanical end-use parts.
The geometry covers a wide range including thin filaments, smooth surfaces, organic shapes, chamfered shapes, small shapes and large shapes.
The models are described in \cref{dataset_description}.

\begin{table}
\caption{3D models used for validation}\label{dataset_description}
\begin{tabular}{l l l}
Name & Author & License \\
\hline
\href{	https://www.thingiverse.com/thing:26555	}{	AirCasting Air Monitor Casing	} & 	HabitatMap	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3629434	}{	Air hose splitter	} & 	frizinko	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1155772	}{	Al Hamra Tower	} & 	TurnerConstructionCompany	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1498967	}{	canon NP-E3 battery cap	} & 	kosuyoung	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3567409	}{	David	} & 	Thunk3D	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3132621	}{	Deck Assembly Tool, Plank Screwing Tool	} & 	PSomeone	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2920060	}{	Ender 3 Cable Chain	} & 	johnniewhiskey	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2993875	}{	Ergonomic Hacksaw Handle	} & 	mmOne	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2513922	}{	Gap measurement tool	} & 	ravm84	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1673030	}{	G-Clamp fully printable	} & 	johann517	 & 	CC-A	\\
\href{	https://www.youmagine.com/designs/gyroid	}{	Gyroid	} & 	Tim Kuipers	 & 	PD	\\
\href{	https://www.thingiverse.com/thing:1327093	}{	3D Printable Jet Engine	} & 	CATIAV5FTW	 & 	CC-NC	\\
\href{	https://www.thingiverse.com/thing:2752165	}{	Lawn Mower Throttle Replacement	} & 	Spammington	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:2854328	}{	OpenRC F1 Internal gear box mod	} & 	intoxikated	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3592328	}{	PCB Test Fixture	} & 	JMadison	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1078865	}{	Pioneer Radio Holder for Ford Focus	} & 	Perugino	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:34596	}{	Replicator Dual Fan Mount	} & 	aubenc	 & 	PD	\\
\href{	https://www.thingiverse.com/thing:3754728	}{	Atuador vers\~ao 2 * actuator version 2	} & 	Caroline Holanda	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:1595179	}{	TE Pocket Operator Hard case	} & 	Salvation76	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:3682303	}{	Screw sizer	} & 	Pierrolalune63	 & 	CC-NC	\\
\href{	http://homepage.tudelft.nl/z0s1z/projects/2017-bone-infill.html	}{	Bone-like optimized infill	} & 	Jun Wu	 & 	CC-A	\\
\href{	https://www.thingiverse.com/thing:26244	}{	Two-Story Spec House	} & 	pwc-phil	 & 	CC-A	\\
\end{tabular}
\end{table}

### 2019-08-15 6_validation.tex
zjenja: minor edits
describe dataset

@@
 \section{Validation}
+In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
+The dataset is described in detail in the accompanying data in \cref{dataset}.
+We sliced all models in the data set and selected 300 random slices from the total set of slices.
 
@@
 In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-For each strategy, we measured the angle between consecutive segments.
+We measured the angle between consecutive segments generated by each strategy.
 The relative frequency of these angles is shown in \cref{smoothness}.
+All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
 While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.

### 2019-08-15 6_validation.tex
describe dataset

@@
 In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
-The dataset is described in detail in the accompanying data in \cref{dataset}.
-We sliced all models in the data set and selected 300 random slices from the total set of slices.
-
-\todo{describe dataset of 3d models and random slices...
-X number of 3d files.
-varying in size, topology, features (size).
-random selection of slices.
-300 slices total.
-5 toolpath strategies were applied for each layer.}
+The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
+We sliced all models in the dataset and selected 300 random slices from the total set of slices.
 
@@
 \fi
+
+We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2019-08-15 6_validation.tex
redo analysis figures

--- 2019-08-15 6_validation.tex
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/validation/overunderfill.pdf}
-\caption{total over and underfill for entire dataset}
+\begin{figure*}
+\centering
+\setlength{\figheight}{0.2\textwidth}
+\setlength{\figwidth}{0.24\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
+\caption{Computation time and target vertex count for the full dataset}
+\label{computime}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
+\caption{Total over and underfill area}
 \label{over_underfill}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/validation/smoothness.pdf}
-\caption{occurrence of angles between consecutive segments}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
+\caption{Relative frequency of extrusion widths}
+\label{widthHistogram}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
+\caption{Frequency of angles between consecutive segments}
 \label{smoothness}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/validation/widthHistogram.pdf}
-\caption{Distribution of extrusion width, sampled at  \SI{200}{\micro\meter}, visualized data is binned at intervals of  \SI{10}{\micro\meter}}
-\label{widthHistogram}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/validation/computime2.pdf}
-\caption{Computation time per slice}
-\label{computime}
-\end{figure}
+\end{subfigure}
+\caption{Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.}
+\end{figure*}
 
@@
 From these sampled values, we calculated the mean bead width, and standard deviation.
-\cref{widthHistogram} shows the distribution of extrusion width for each strategy.
+\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of  \SI{10}{\micro\meter}.
 The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count".

### 2019-08-15 6_validation.tex
move accuracy figure down
fix reference for linear advance

@@
 
+\subsection{Computational analysis}
+Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
+The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
+The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
+\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
+
+\paragraph{Accuracy}
+In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
+If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
+We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
+For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
+In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
+See \cref{segment_visualization}.
+
+\begin{figure}
+\centering
+\setlength{\figwidth}{.25\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
+\caption{Blocky}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
+\caption{Rounded}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
+\caption{Excluded}
+\end{subfigure}
+\caption{
+Extruded area of two extrusion toolpath segments.
+Red areas signify doubly extruded areas.
+}
+\label{segment_visualization}
+\end{figure}
+
+We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
+In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
+
+The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
+We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
+Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
+In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
+These triple extrusion areas count double toward the total amount of overfill.
+The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
+
 \begin{figure*}
@@
 \end{figure*}
-
-\subsection{Computational analysis}
-Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
-The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
-\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
-
-\paragraph{Accuracy}
-In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
-We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
-For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
-In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
-See \cref{segment_visualization}.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.25\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
-\caption{Blocky}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
-\caption{Rounded}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
-\caption{Excluded}
-\end{subfigure}
-\caption{
-Extruded area of two extrusion toolpath segments.
-Red areas signify doubly extruded areas.
-}
-\label{segment_visualization}
-\end{figure}
-
-We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
-In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
-
-The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
-Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
-In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
-These triple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
 
@@
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance~\cite{linadvance}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
+The firmware of the printer employs linear advance~\cite{tronvoll2019investigating}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
 We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.

### 2019-08-15 6_validation.tex
figure comparison of even and inward distributed strategies

@@
 to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
+See \cref{distributed_comparison}.
 That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
@@
 % and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using hte naive strategy will still hold approximately.
+Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using the naive strategy will still hold approximately.
+
+\begin{figure}
+\centering
+\setlength{\figwidth}{.45\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
+\caption{Evenly distributed}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
+\caption{Inward distributed}
+\end{subfigure}
+\caption{
+Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
+}
+\label{distributed_comparison}
+\end{figure}
 

### 2019-08-15 6_validation.tex
lil edits to validation

@@
 The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
-We sliced all models in the dataset and selected 300 random slices from the total set of slices.
+We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
+We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 \end{subfigure}
-\caption{Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.}
+\caption{
+Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.
+Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
+}
 \end{figure*}
@@
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance~\cite{tronvoll2019investigating}: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.
+The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
 We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.

### 2019-08-15 8_discussion.tex
lil edits to validation

@@
 \subsection{Computation time}
-Algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
+The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
 The number of elements in the trapezoidation is linear in the number of elements in the VD

### 2019-08-15 8_discussion.tex
rewrote dsicussion

@@
 
+% only Moessen reports on computation times, but in a weird manner
+
 \subsection{Comparison of beading strategies}
 \todo{Discussion of finding of Validation section}
-
 The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
 
-Naive method causes a lot of overfills and underfills.
-This overpoweres any positive effect of perfectly homogeneous bead width.
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{10}{\percent} of the total target area is covered by underfill and likewise for overfill.
+These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.
 
-The single bead strategy solves the underfill problem in regions where the model is more thin than the nozzle size.
-However, the strategy doesn't deal with the remaining area.
-In our visualization we print the outline of the remaining area which exposes an overextrusion problem.
+%The single bead strategy solves the underfill problem in regions where the model is more thin than the nozzle size.
+%However, the strategy doesn't deal with the remaining area.
+%In our visualization we print the outline of the remaining area which exposes an overextrusion problem.
 
-The constant beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
+The constant bead count beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
+See \cref{TEST_Constant_accuracy}.
+Note that around regions where the bead width changes a lot we can see some overfill areas, which explains the unusually high overfill statistic in \cref{over_underfill}.
+Because the bead count 
 For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
+Moreover the skeleton marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked skeleton to be very small at that location, which results in tiny bead widths.
 
-The center beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
+If we look at \cref{TEST_Center_accuracy} we can see that
+the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
+According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{2}{\percent}, which is a considerable improvement over the naive method.
 
-The distributed strategy greatly reduces the total underfill and overfill and severely limits the amount of beads with a width which differs greatly from an optimal width, but the toolpaths contain a lot of bends in transitioning areas.
+However, according to \cref{widthHistogram} the centered strategy exhibits a lot wider range of bead widths than the distributed strategies:
+the standard deviation of the bead widths in the centered beading strategy is approximately \SI{38}{\micro\meter}, while the standard deviation resulting from the distributed strategies is approximately \SI{15}{\micro\meter}.
+We can therefore state that the distributed strategies result in bead widths closer to the nominal bead widths than the centered strategy, which means that the distributed strategies realize the mechanical properties associated to a given nominal bead width more closely.
 
-The inward distributed beading strategy shows similar behavior to the distributed strategy, but large regions are less affected by the bends introduced because of transitioning.
-This can be seen in \cref{applications_gear}.
+The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled segments in transitioning regions.
+The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
+Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
+We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.
+However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.
+The errors from such inaccuracies and the errors in mechanical properties due to deviation from the nominal bead width are located near the center of the shape, which means the overal mechanical properties of the part are least affected by the discrepancy between the actual feature size and the preferred feature size when using the inward distributed beading strategy.

### 2019-08-15 8_discussion.tex
lil discussion update

@@
 \subsection{Comparison of beading strategies}
-\todo{Discussion of finding of Validation section}
 The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
 
-We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{10}{\percent} of the total target area is covered by underfill and likewise for overfill.
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
 These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.
@@
 the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
-According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{2}{\percent}, which is a considerable improvement over the naive method.
+According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.
 
@@
 We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.
+
 However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.

### 2019-08-16 4_method.tex
overview figure

@@
 \end{enumerate}
+See \cref{overview_fig}.
 
@@
 \end{figure}
+
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.19\textwidth}
+\begin{subfigure}{\figwidth}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/overview/skeleton.pdf}
+\caption{Skeleton}\label{overview_fig_skeleton}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/overview/marked.pdf}
+\caption{Marked}\label{overview_fig_marked}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/overview/transitions.pdf}
+\caption{Transitions}\label{overview_fig_transitions}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/overview/junctions.png}
+\caption{Junctions}\label{overview_fig_junctions}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\centering
+\includegraphics[width=\columnwidth]{sources/method/overview/toolpaths.png}
+\caption{Toolpaths}\label{overview_fig_toolpaths}
+\end{subfigure}
+\caption{
+Overview of the steps in the method of our framework.
+First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine an initial bead count (numbers) based on the local feature size.
+Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
+We then \subref{overview_fig_junctions} generate a number of junctions (yellow) equal to the bead count along the bones of the skeleton,
+which are \subref{overview_fig_toolpaths} connected together to make the toolpaths.
+}
+\label{overview_fig}
+\end{figure*}
 

### 2019-08-16 4_method.tex
junction placement figure

@@
 for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
+See \cref{junction_placement}.
 We store all junctions of a segment in a mapping from edge to a list of junctions.
+
+\begin{figure}
+\centering
+\setlength{\figheight}{.29\columnwidth}
+\begin{subfigure}{0.14\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
+\caption{Beadings}\label{trapezoid_beading_beading}
+\end{subfigure}
+\begin{subfigure}{0.5\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
+\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
+\end{subfigure}
+\begin{subfigure}{0.34\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
+\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
+\end{subfigure}
+\caption{
+Applying beadings togenerate junctions along trapezoids.
+\subref{trapezoid_beading_beading} shows half of the locations $L(n,d)_i$ and widths $W(n,d)_i$ of two arbitrary different beadings.
+\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
+\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support bones.
+No junctions will be generated along marked bones.
+Wide black lines are outline segments, marked nodes and bones in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = L(n,d)_i$.
+}
+\label{junction_placement}
+\end{figure}
 

### 2019-08-16 4_method.tex
lil: mention example prefered bead count function

@@
 (The feature diameter is twice the radius.)
+For example we might choose to round to the nearest integer multiple of some preferred width $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
 The function $b$ is determined by the beading strategy and is required to increase monotonically with the input feature diameter.

### 2019-08-19 0_main.tex
all authors
first complete version of related work - Jun
describe dataset
gMAT print photos
undor draft option
zjenja: minor changes and corrections

@@
 \usepackage{amsmath}
-\usepackage{hyperref}
+\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
 %\modulolinenumbers[5]
@@
 	\newlength{\figheight}
+	\newlength{\figheightTwo}
 
@@
 \author[um,tud]{Tim Kuipers}
-%\author[tud]{Jun Wu}
-%\author[cuhk]{Charlie Wang{\corref{cor1}}}
-%\ead{cwang@mae.cuhk.edu.hk}
-%\cortext[cor1]{Corresponding author}
+\author[tud]{Eugeni L. Doubrovski}
+\author[tud]{Jun Wu}
+\author[cuhk]{Charlie Wang{\corref{cor1}}}
+\ead{cwang@mae.cuhk.edu.hk}
+\cortext[cor1]{Corresponding author}
 \address[um]{Ultimaker, Utrecht, The Netherlands}
 \address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
-%\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
+\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
 
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
-FDM works by depositing material along paths which lie in horizontal layers.
-The outlines of each layer are filled (partly) using contour-following toolpaths approximately the size of the printing nozzle.
-Filling the outlines with extruded material densely and accurately is important for fabricating parts accurately and stiffly.
-An accurate dense filling is aspecially important to thin parts such as casings for electronics, blowmolding prototypes, (architectural) models and microstructures.
+FDM builds up objects by depositing material along paths which lie in horizontal layers.
+The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
+Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
+An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.
 
@@
 
+\begin{appendices}
+
+\input{20_dataset}
+
+\end{appendices}
 \end{document}

### 2019-08-19 1_intro.tex
zjenja: minor changes and corrections

@@
 It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
-FDM printers are used for example in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures - to name just some.
+FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures.
 Recent research developments have investigated manufacturing complex volumetric structures such as microstructures, topology optimized structures and infill structures.
-Quite some of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
+Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
 
-FDM printers expel molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
-Because the positioning system generally has an order of magnitude better resolution than the width of the nozzle,
+FDM printers deposit molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
+Because the positioning system has an order of magnitude better resolution than the width of the nozzle,
 the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.
 
-The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the size of the hole in the nozzle from the outline shape.
+The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
 However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
@@
 Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
-Underfills on the other hand can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
+Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
 These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
@@
 \cite{N.Turner2014,ahn2002anisotropic}
-In order to accurately fabricate a part restricted to prescribed mechanical properties we need to generate toolpaths using the corresponding process parameters as close as possible.
-We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width then existing techniques.
+In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
+We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
 See \cref{intro_wedge}(bottom).

### 2019-08-19 2_related_work.tex
first complete version of related work - Jun
zjenja: minor changes and corrections

@@
 For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
-In this paper, we focus on generating toolpath that seamlessly covers the entire 2D contour.
+In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
 This is sometimes called dense infill~\cite{Livesu2017CGF}.
@@
 Furthermore, a smooth path is often preferred.
-A path with a lot of sharp turns requires to slow down the movement of the nozzle, and this consequently prolongs the printing process.
-Second, the path, extended with a certain width, ideally shall cover the bounded region no voids or gaps --  underfilling, and no overlap -- overfilling. 
+Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
+Second, the path, extended with a certain width, ideally shall cover the bounded region without voids or gaps --  underfilling, and no overlap -- overfilling. 
 An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
@@
 A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
-To reduce the number of sharp turns thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
+To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
 Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
 One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
-This is due to the fact that the offset contour meets around the medial axis and the remaining space might not match exactly the (constant) deposition width.
+This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
 To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
-Close to the slice boundary there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
+Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
@@
 % the idea, and (some of) the most related work
-Our idea to reduce under- and over-filling is to deposit material with a varying width.
-This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better coverage of the domain.
+Our approach to reduce under- and over-filling is to deposit material with a varying width.
+This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
 Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
 However, we note that the range of possible widths is not unlimited.
-For instance, printing a width that is tripple the nozzle diameter is challenging.
+For instance, printing a width that is triple the nozzle diameter is challenging.
 Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.

### 2019-08-19 4_method.tex
zjenja: minor changes and corrections

@@
 See \cref{beading_conflict_problem}.
-In such a case we will interpolate between the lower beading and the beading propagated from above,
+In such a case we interpolate between the lower beading and the beading propagated from above,
 starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
@@
 After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
-The beading propagation is performed in two stages: an upward stage and a downward phases.
+The beading propagation is performed in two stages: an upward and downward stage.
 %First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.

### 2019-08-19 6_validation.tex
gMAT print photos
zjenja: minor changes and corrections

@@
 We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
-We also introduce new beading strategies which produce toolpaths with less extremal widths then techniques from existing literature.
+We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.
 
-A beading strategy was defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
-Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the size of the hole in the printing nozzle.
+A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
+Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
 Most of the beading strategies we introduce share a common ground:
@@
 \section{Validation}
-In order to test our framework we have assembled a data set of various types of 3D model, ranging over various applications and various types of geometry.
+In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
 The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
 We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
-We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed, and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to on dataset.
+This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the dataset.
 
@@
 A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
-Also, large bead widths can cause the extruded material to upwards instead of filling the required width.
+Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
 \todo{Include picture of flutter?}
@@
 All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
-While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the remaining strategies.
+While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
 
@@
 
-The resulting prints are viewed in \cref{wedge_print} and \cref{prints}.
+The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
 Because of inaccuracies in the depositioning control system some of the prints show defects.
@@
 \setlength{\figheight}{.38\columnwidth}
+\setlength{\figheightTwo}{.47\columnwidth}
 \setlength{\figwidth}{0.32\columnwidth}
 \begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
@@
 \begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
@@
 \begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
@@
 
-We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.
+%We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2019-08-19 1_intro.tex
some small changes in the introduction. will continue tomorrow - Jun

@@
 \section{Introduction}
-3D printing enables the fabrication of complex geometry under very few design constraints compared to conventional fabrication techniques.
-Recent developments have seen a rapid growth in the use and capabilities of desktop 3D printing systems.
-The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
-
+3D printing enables the fabrication of complex geometry under few design constraints compared to conventional fabrication techniques.
+Recent developments have seen a rapid growth in both the use and capabilities of desktop 3D printing systems.
+%The rapid spread of 3D printing through different industries and types of application calls for the possibility to manufacture a wide range of geometries while guaranteeing mechanical properties of the resulting parts.
 Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
@@
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures.
-Recent research developments have investigated manufacturing complex volumetric structures such as microstructures, topology optimized structures and infill structures.
+Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
 Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
 
-FDM printers deposit molten plastic through a nozzle, which extrudes semi-continuous beads of plastic generally in flat horizontal layers.
-Because the positioning system has an order of magnitude better resolution than the width of the nozzle,
+FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
+Because the resolution of the positioning system is order of magnitude smaller than the width of the nozzle (typically from $??$ to $??$),
 the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.
+\jun{I had difficulty to follow the logic behind this sentence}
 

### 2019-08-19 6_validation.tex
some small changes in the introduction. will continue tomorrow - Jun

@@
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
+The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
 We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.

### 2019-08-20 4_method.tex
lil

@@
 \subsection{Bead counts}
-We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
+We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense which will be defined in \cref{sec:significance_measure}.
 Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

### 2019-08-21 4_method.tex
lil

@@
 Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
-We decide on a bead count at locations which lie in central positions of the shape in some sense to be defined below and apply an optimal distribution of widths from the central regions outward.
+We decide on a bead count at locations which lie in central positions of the shape and apply an optimal distribution of widths from the central regions outward.
 

### 2019-08-21 4_method.tex
initial overview in terms of Union of Cones

@@
 \section{Method}
+\subsection{Overview}
+
+The naive method consists of consecutive inward offsets from the outline.
+
+These offsets can be generated from the medial axis transform (MAT).
+The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones with \SI{45}{\degree} touching the input shape.
+The constant width insets are then conceptualized as the intersection between the Union of Cones (UoC) and horizontal planes at regular intervals.
+
+Alternatively: the MAT captures the internal part of the distance field and the constant width insets are the isocontours of the that distance field.
+
+The problem with the constant width insets is that in the center of the shape \todo{it doesn't fit}.
+because the distance to the boundary is not an integer multiple of the nozzle size.
+We therefore change the mesh such that an exact integer beads will be generated.
+
+A simplified version of our framework can be conceptualized as such:
+\begin{itemize}
+\item Compute the mesh representing the Union of Cones (UoC) for the input shape
+\item Round the heights of central nodes to to the nearest slicing height
+\item Smooth out sharp transitions between regions with different integer multiple slice heights
+\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
+\end{itemize}
+See \cref{3d_surface_overview}.
+
+\begin{figure}
+\centering
+\setlength{\figwidth}{.3\columnwidth}
+\begin{subfigure}{\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_mat.png}
+\includegraphics[width=\columnwidth]{sources/method/surface/naive.pdf}
+\caption{Union of Cones}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_no_transitions.png}
+\includegraphics[width=\columnwidth]{sources/method/surface/no_transitions.pdf}
+\caption{Rounded}
+\end{subfigure}
+\begin{subfigure}{\figwidth}
+\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_st.png}
+\includegraphics[width=\columnwidth]{sources/method/surface/distributed.pdf}
+\caption{Smoothed}
+\end{subfigure}
+\caption{
+A simplified geometrical conceptualization of our framework.
+The 3D surface representations (top) are sliced into the toolpaths (bottom) which fill the outline shape.
+We first compute the Union of Cones mesh, then alter it to prevent shallow slopes and then smooth it to prevent instantaneous changes.
+}
+\label{3d_surface_overview}
+\end{figure}
+
+problems
+
+Not all non-outline nodes are central.
+How to determine the height of such nodes?
+
+\Cref{section_toolpath_extraction} shows how we can determine the heights of non-central verts, extends the simplified method to a generalized framework and provides an efficient algorithm to slice the modified UoC.
+
+\todo{OLD: }
 When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.

### 2019-08-21 4_method.tex
big restructure based on new UoC overview

@@
 
-\subsection{Shape decomposition}
+\subsection{Surface construction}
+\todo{TODO: explain section title!}
+
 The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
@@
 
-\subsection{Bead counts}
+\subsection{Center classification}
+\todo{TODO: explain section title!}
+
 We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense which will be defined in \cref{sec:significance_measure}.
@@
 
+\subsection{Central height adjustment}
+\todo{TODO: explain section title!}
+
+\todo{Introduce what's to come in this section.}
+
 \subsubsection{Initial bead count}
@@
 
-\subsection{Toolpath extraction}
+\subsection{Peripheral height adjustment}
 \label{section_toolpath_extraction}
+
+For our purposes we only need to define the height at the locations which will be part of a slice.
+Instead of adjusting the height of peripheral nodes, we determine the locations along the bones where the adjusted height is an integer multiple of half the nozzle size.
+This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.
+
+\todo{TODO:}
+\begin{itemize}
+\item explain section title
+\item Reword and/or introduce concept of Beading 
+\item Check compatibility with surrounding text!
+\end{itemize}
+
 Now that we have decided on the bead counts in the central marked regions, we can apply those bead counts outward along the unmarked bones of the skeleton in order to define the locations of the toolpath junctions.
@@
 
-\begin{definition}\label{beading_strategy_definition}
-We define a beading strategy as the following set:
-$$
-\left\{ \alpha_\text{max}, b(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
-$$
-where
-$\alpha_{\text{max}}$ (the limit bisector angle),
-$b(d)$ (optimal bead count),
-$t(n)$ (transition length)
-and
-$t_0(n)$ (transition anchor position) have already been defined above.
-We introduce here
-$W(n, d)$, which gives the sequence of bead widths to cover a distance $d$ using $n$ beads
-and
-$L(n, d)$, which gives the sequence of toolpath positions as radial distances from the outline to cover a distance $d$ using $n$ beads.
-\end{definition}
-
-The following restrictions hold:
-\begin{enumerate}
-\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
-\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
-\end{enumerate}
-
-\begin{definition}
-By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading $B$, which is defined as the following set:
-$$
-\left\{ d, n, w_i, l_i  \right\}
-$$
-where
-$d = 2 R(v)$ is the diameter associated with $v$,
-$n$ is the bead count,
-$w_i$ is the bead width of the bead with index $0 \leq i < n$ counting from the outline inward
-and
-$l_i$ is the distance of the toolpath location of bead with index $0 \leq i < n$.
-\end{definition}
+\todo{Definition of beading strategy got moved!}
+\todo{Check compatibility with surrounding text!}
 
@@
 
-\subsubsection{Toolpath extraction algorithm}
+\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
 Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.

### 2019-08-21 5_generalization.tex
big restructure based on new UoC overview

--- 2019-08-19 6_validation.tex
@@
-\section{Beading strategies}
+\section{Generalization}
+In this section we will generaize the described method into a parametric system, i.e. a geometric framework.
+
+\todo{TODO:}
+\begin{itemize}
+\item introduce section
+\end{itemize}
+
+\subsection{Beading strategy}
+Depending on the application, the hardware and the materials used we might want to have different strategies for filling a shape with contour parallel toolpaths.
+we therefore..
+
+\begin{definition}\label{beading_strategy_definition}
+We define a beading strategy as the following set:
+$$
+\left\{ \alpha_\text{max}, b(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
+$$
+where
+$\alpha_{\text{max}}$ (the limit bisector angle),
+$b(d)$ (optimal bead count),
+$t(n)$ (transition length)
+and
+$t_0(n)$ (transition anchor position) have already been defined above.
+We introduce here
+$W(n, d)$, which gives the sequence of bead widths to cover a distance $d$ using $n$ beads
+and
+$L(n, d)$, which gives the sequence of toolpath positions as radial distances from the outline to cover a distance $d$ using $n$ beads.
+\end{definition}
+
+The following restrictions hold:
+\begin{enumerate}
+\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
+\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
+\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\end{enumerate}
+
+\begin{definition}
+By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading $B$, which is defined as the following set:
+$$
+\left\{ d, n, w_i, l_i  \right\}
+$$
+where
+$d = 2 R(v)$ is the diameter associated with $v$,
+$n$ is the bead count,
+$w_i$ is the bead width of the bead with index $0 \leq i < n$ counting from the outline inward
+and
+$l_i$ is the distance of the toolpath location of bead with index $0 \leq i < n$.
+\end{definition}
+
+\subsection{Beading strategies}
+\todo{This section was moved. Check compatibility with surrounding text.}
+
 Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
@@
 \end{align*}
-
-\section{Validation}
-In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
-The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
-We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
-We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed, and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
-
-\subsection{Computational analysis}
-Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
-The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
-\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
-
-\paragraph{Accuracy}
-In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
-We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
-For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
-In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
-See \cref{segment_visualization}.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.25\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
-\caption{Blocky}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
-\caption{Rounded}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
-\caption{Excluded}
-\end{subfigure}
-\caption{
-Extruded area of two extrusion toolpath segments.
-Red areas signify doubly extruded areas.
-}
-\label{segment_visualization}
-\end{figure}
-
-We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
-In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
-
-The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
-Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
-In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
-These triple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
-
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.19\textwidth}
-\setlength{\figheight}{0.283\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
-\caption{Naive}\label{TEST_naive_accuracy}
-\end{subfigure}
-%\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
-%\caption{Single}\label{TEST_SingleBead_accuracy}
-%\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
-\caption{Constant}\label{TEST_Constant_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
-\caption{Center}\label{TEST_Center_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
-\caption{Distributed}\label{TEST_Distributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
-\caption{Inward}\label{TEST_InwardDistributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{.04\columnwidth}\centering
-\vspace{4cm}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
-\end{subfigure}
-\caption{
-Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
-Grey areas are covered by extruded material,
-blue areas in the top images signify underfill regions,
-red areas overfill,
-orange areas triply extruded areas (double overfill).
-The bottom visualizes the bead widths at each location by exaggerating their widths.
-Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
-}
-\label{visualized_accuracy}
-\end{figure*}
-
-We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
-The overfill and underfill area as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
-The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the dataset.
-
-\begin{figure*}
-\centering
-\setlength{\figheight}{0.2\textwidth}
-\setlength{\figwidth}{0.24\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
-\caption{Computation time and target vertex count for the full dataset}
-\label{computime}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
-\caption{Total over and underfill area}
-\label{over_underfill}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Relative frequency of extrusion widths}
-\label{widthHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
-\caption{Frequency of angles between consecutive segments}
-\label{smoothness}
-\end{subfigure}
-\caption{
-Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.
-Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
-}
-\end{figure*}
-
-\paragraph{Uniformity}
-Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
-A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
-Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
-\todo{Include picture of flutter?}
-Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
-We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
-
-To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
-at intervals of \SI{200}{\micro\meter} along the toolpath.
-From these sampled values, we calculated the mean bead width, and standard deviation.
-\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of  \SI{10}{\micro\meter}.
-The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count".
-These values indicate that, while causing less overfill and underfill, our strategy deviates less and less often from the nominal nozzle size.
-
-\paragraph{Smoothness of toolpaths}
-In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We measured the angle between consecutive segments generated by each strategy.
-The relative frequency of these angles is shown in \cref{smoothness}.
-All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
-While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
-
-\subsection{Experimentation}
-Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the extruder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
-We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
-
-The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
-Because of inaccuracies in the depositioning control system some of the prints show defects.
-Such defects are less prevalant for the inward distributed beading strategy than the other strategies.
-
-\begin{figure}
-\centering
-\begin{subfigure}{\columnwidth}\centering
-\setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
-\caption{Wedge}\label{print_wedge}
-\end{subfigure}
-\caption{
-A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
-The wedge print can be read like a graph with model diameter on the X-axis and the resulting beads over the Y-axis.
-The naive and center deviation strategy show problems around certain model diameters.
-}
-\label{wedge_print}
-\end{figure}
-
-\begin{figure}
-\centering
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
-\caption{Naive}\label{print_naive}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
-\caption{Center deviation}\label{print_center}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
-\caption{Inward distributed}\label{print_inward}
-\end{subfigure}
-\caption{
-Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
-The naive method produces distinct underfill areas.
-The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
-The inward distributed strategy produces the least defects.
-}
-\label{prints}
-\end{figure}
-
-\iffalse
-\todo{Maybe test the following qualities:}
-\begin{itemize}
-\item visual consistency of flat top skin surface
-\item graphs of tensile tests on thin walled object
-\end{itemize}
-\fi
-
-%We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2019-08-21 6_validation.tex
big restructure based on new UoC overview

@@
-\section{Beading strategies}
-Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
-We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
-We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.
-
-A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
-Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
-Most of the beading strategies we introduce share a common ground:
-\begin{align*}
-d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
-d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
-t_\text{beading} &= w_\text{pref} \\
-d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
-%
-%We use a transition anchor position of
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
-t(n) &= w_\text{pref} \\
-\alpha_\text{max} &= \SI{135}{\degree} \\
-L(n,d)_i &= 
-\begin{cases}
--\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
-d/2 & \text{ if } i =  \frac12 (n -1) \\
-d - W(n,d)_{n-1-i} & \text{ otherwise }\\
-\end{cases}
-\end{align*}
-
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_\text{pref}$ for $n \in \mathbb{N}$.
-The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
-The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
-The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.
-
-\paragraph{Naive Beading Strategy}
-We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
-\begin{align*}
-\alpha_\text{max} &= \SI{180}{\degree} \\
-b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
-W(n,d)_i &= w_\text{pref} \text{ for all } i 
-%\\
-%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{Outer bead}
-We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
-Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
-
-\begin{align*}
-d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
-t(n) &= 0 \\
-b(d) &=
-\begin{cases}
-1 & \text{ if } d < w_\text{pref} \\
-2 & \text{ otherwise } \\
-\end{cases}
- \\
-W(n,d)_i &= 
-\begin{cases}
-d & \text{ if } n = 1 \\
-w_\text{pref} & \text{ otherwise } \\
-\end{cases}
-%\\
-%L(n,d)_i &= 
-%\begin{cases}
-%d / 2 & \text{ if } n = 1 \\
-%w_\text{pref} / 2 & \text{ otherwise } \\
-%\end{cases}
-\end{align*}
-
-\paragraph{Constant bead count}
-We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
-Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
-Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the skeletal graph is not stable against those.
-
-\begin{align*}
-\alpha_\text{max} &= \SI{0}{\degree} \\
-b(d) &= C \\
-W(n,d)_i &= d / n \text{ for all } i 
-%\\
-%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{Centered}
-We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
-We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
-\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
-We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
-
-\begin{align*}
-t(n) &= \frac12 w_\text{pref} \\
-b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
-b(d) &= b^-(d) +
-\begin{cases}
--1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
-1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
-0 & \text{ otherwise}
-\end{cases}
-\\
-W(n,d)_i &= 
-\begin{cases}
-d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
-w_\text{pref} &\text{ otherwise }
-\end{cases}
-%\\
-%L(n,d)_i &= 
-%\begin{cases}
-%d / 2 & \text{ if } i = \frac12 (n-1) \\
-%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
-%\end{cases}
-\end{align*}
-
-\paragraph{Evenly distributed}
-By taking the advantages of the above two strategies we can define a beading strategy which constitutes a novel toolpathing technique.
-We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
-We determine the local bead count by dividing the diameter by the prefered bead width and rounding to the nearest integer.
-This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.
-
-\begin{align*}
-b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
-W(n,d)_i &= d / n \text{ for all } i 
-%\\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{General distributed strategy}
-The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
-$w_\text{pref} + E / n$.
-However, depending on the application we might want a different distribution of widths.
-We therefore supply a beading strategy which supports an arbitrary distribution of the discrepancy.
-The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
-
-\begin{align*}
-b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
-E(n,d) &= d - n w_\text{pref} \\
-W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
-%\\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{Inward distributed}
-For example, we can choose 
-$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
-to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
-See \cref{distributed_comparison}.
-That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
-This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
-% and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using the naive strategy will still hold approximately.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.45\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
-\caption{Evenly distributed}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
-\caption{Inward distributed}
-\end{subfigure}
-\caption{
-Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
-}
-\label{distributed_comparison}
-\end{figure}
-
-\paragraph{Widening}
-Complementary to any of these strategies we can enforce a minimum feature size at no extra cost in our framework.
-Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
-We can simply override
-\begin{align*}
-W'(n,d)_1 &=
-\begin{cases}
-\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
-W(n,d)_1 & \text{ otherwise}
-\end{cases}
-\end{align*}
-
 \section{Validation}

### 2019-08-21 4_method.tex
redo overview

@@
 \subsection{Overview}
+The naive method consists of consecutive inward offsets from the outline using a constant bead width.
+These offsets can be generated from the medial axis transform (MAT).
+The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones of \SI{45}{\degree} which are touching the input shape.
+\cite{blum1967transformation}
+The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
+We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}
 
-The naive method consists of consecutive inward offsets from the outline.
+For the naive method the overfill and underfill problems arise in the center,
+because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
+We therefore change the UoC mesh such that an exact integer beads will be generated in the center.
+More specifically, we round the height to the nearest multiple of \emph{half} the nozzle size.
+That way we allow for an odd number of beads to be placed between the two sides of the outline shape.
 
-These offsets can be generated from the medial axis transform (MAT).
-The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones with \SI{45}{\degree} touching the input shape.
-The constant width insets are then conceptualized as the intersection between the Union of Cones (UoC) and horizontal planes at regular intervals.
-
-Alternatively: the MAT captures the internal part of the distance field and the constant width insets are the isocontours of the that distance field.
-
-The problem with the constant width insets is that in the center of the shape \todo{it doesn't fit}.
-because the distance to the boundary is not an integer multiple of the nozzle size.
-We therefore change the mesh such that an exact integer beads will be generated.
-
-A simplified version of our framework can be conceptualized as such:
+Our technique consists of the folowing steps:
 \begin{itemize}
 \item Compute the mesh representing the Union of Cones (UoC) for the input shape
+\item Identify central regions of the UoC
 \item Round the heights of central nodes to to the nearest slicing height
-\item Smooth out sharp transitions between regions with different integer multiple slice heights
+\item Smooth out sharp transitions between regions with different integer heights
+\item Determine the heights in the periphery (non-central regions)
 \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\setlength{\figwidth}{.3\columnwidth}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_mat.png}
-\includegraphics[width=\columnwidth]{sources/method/surface/naive.pdf}
-\caption{Union of Cones}
+\setlength{\figwidth}{.18\textwidth}
+\setlength{\figwidthTwo}{.17\textwidth}
+\setlength{\figwidthTree}{.22\textwidth}
+\setlength{\tempheight}{-0.3cm}
+\setlength{\tempheightTwo}{-0.5cm}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
+\caption{Union of Cones}\label{3d_surface_overview_uoc}
 \end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_no_transitions.png}
-\includegraphics[width=\columnwidth]{sources/method/surface/no_transitions.pdf}
-\caption{Rounded}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
+\caption{Center}\label{3d_surface_overview_center}
 \end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/surface/simple_surface_st.png}
-\includegraphics[width=\columnwidth]{sources/method/surface/distributed.pdf}
-\caption{Smoothed}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
+\caption{Rounded}\label{3d_surface_overview_rounded}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
+\caption{Smoothed}\label{3d_surface_overview_smoothed}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
+\caption{Sliced}\label{3d_surface_overview_sliced}
 \end{subfigure}
 \caption{
-A simplified geometrical conceptualization of our framework.
-The 3D surface representations (top) are sliced into the toolpaths (bottom) which fill the outline shape.
-We first compute the Union of Cones mesh, then alter it to prevent shallow slopes and then smooth it to prevent instantaneous changes.
+A geometrical conceptualization of our technique.
+3D visualization on top and the corresponding 2D visualization on bottom.
+In the UoC \subref{3d_surface_overview_uoc}
+we mark the central regions blue \subref{3d_surface_overview_center}
+and round the height values to the nearest integer muliple of half the nozzle width \subref{3d_surface_overview_rounded}.
+We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
+and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
 }
 \label{3d_surface_overview}
-\end{figure}
+\end{figure*}
 
-problems
+We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
+explain how to identify central regions in \cref{sec_center_classification}.
+Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
+We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
+and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
+In \cref{sec_generalization} we describe how to generalize our method into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.
 
-Not all non-outline nodes are central.
-How to determine the height of such nodes?
-
-\Cref{section_toolpath_extraction} shows how we can determine the heights of non-central verts, extends the simplified method to a generalized framework and provides an efficient algorithm to slice the modified UoC.
-
-\todo{OLD: }
-When performing the naive method of offsetting the outline inward with constant width paths the overfill and underfill problems arise in the center.
-Constant widths inward steps might not resolve to the arbitrary width of the outline shape.
-Our method therefore decides on the number of beads everywhere first and then determines the widths of the beads.
-We decide on a bead count at locations which lie in central positions of the shape and apply an optimal distribution of widths from the central regions outward.
-
-What constitutes an optimal distribution is governed by a beading strategy.
-Our framework allows for different beading strategies which can optimize for different criteria.
-A beading strategy is defined by several several functions which govern the behavior of our framework.
-
-\begin{enumerate}
-\item Compute a skeleton of the outline shape.
-\item Use a significance measure to mark regions of the skeleton which are central.
-\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
-\item Generate junctions along unmarked bones of the skeleton and connect the junctions together to form the extrusion beads.
-\end{enumerate}
-See \cref{overview_fig}.
+For ease of reference we have included a legend explaining the vocabulary employed in this manuscript in \cref{legend}.
 
@@
 \end{figure}
+
+\iffalse
 
@@
 
-\subsection{Surface construction}
-\todo{TODO: explain section title!}
+\fi
 
+\subsection{Surface construction}\label{sec_surface_construction}
 The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
@@
 
-\subsection{Center classification}
+\subsection{Center classification}\label{sec_center_classification}
 \todo{TODO: explain section title!}
@@
 
-\subsection{Central height adjustment}
+\subsection{Central height adjustment}\label{sec_central_height_adjustment}
 \todo{TODO: explain section title!}
@@
 
-\subsection{Peripheral height adjustment}
-\label{section_toolpath_extraction}
+\subsection{Peripheral height adjustment}\label{sec_peripheral_height_adjustment}
 

### 2019-08-21 sources/method/surface/crop_all.sh

@@ -1,0 +1,5 @@
+for img in *.png; do
+ filename=$(basename "$img")
+ fname="${filename%.*}"
+ convert $img -crop 637x428+253+40 -transparent white "$fname"_cropped.png
+done

### 2019-08-21 4_method.tex
redo surface construction

@@
 \subsection{Surface construction}\label{sec_surface_construction}
-The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
-Starting from the medial axis we further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.
+The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
+By assigning each node in the skeleton a height equal to the radial distance to the outline we obtain the shape of the UoC.
+Starting from the medial axis we further decompose the shape into simple fragments, so that the mesh contains only quads and triangles.
 
@@
 
-Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is discontinuous,
+Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
 or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
-This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
+This last conceptualization is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
 The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
@@
 \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
-\caption{Cones}
+\caption{Union of Cones}
 \end{subfigure}
@@
 
-\begin{figure}
-\begin{subfigure}{0.3\columnwidth}
-\centering
-%\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
-\includegraphics[height=1.5\columnwidth]{sources/method/half_edge_datastructure.pdf}
-\caption{Simple case}
-\label{shape_decomposition_simple}
+\begin{figure}\centering
+\setlength{\figwidth}{0.24\columnwidth}
+\setlength{\figwidthTwo}{0.15\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_mat}
+\caption{MAT}\label{shape_decomposition_mat}
 \end{subfigure}
-\begin{subfigure}{0.65\columnwidth}
-\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
-\caption{Complex case employing discretization}
-\label{shape_decomp_complex}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_vd}
+\caption{VD}\label{shape_decomposition_vd}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_st}
+\caption{ST}\label{shape_decomposition_st}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
+\caption{Datastructure}\label{shape_decomposition_datastructure}
 \end{subfigure}
@@
 
-\begin{figure} \centering
-\includegraphics[width=.75\columnwidth]{sources/method/mat_3d_blender_render.png}
-\caption{
-Visualization of the distance field function as captured by the skeletal trapezoidation.
-}
-\label{mat_3d}
-\end{figure}
-
 \subsubsection{Skeletal trapezoidation}
-We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
+The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
+We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
 Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
@@
 We represent such a skeleton in a standard half-edge data-structure.
-See \cref{shape_decomposition_simple}.
+See \cref{shape_decomposition_datastructure}.
 
@@
 We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
-See \cref{discretization} and \cref{shape_decomp_complex}.
+See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
 That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical representation of the medial axis; see \cref{mat_3d}.
+This makes the skeleton capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
+%; see \cref{mat_3d}.
 

### 2019-08-21 4_method.tex
redo center marking section

@@
 %\begin{subfigure}{0.45\textwidth}
-\includegraphics[width=\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
+\includegraphics[width=.5\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
 %\caption{Transitioning}
@@
 \subsection{Center classification}\label{sec_center_classification}
-\todo{TODO: explain section title!}
-
-We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense which will be defined in \cref{sec:significance_measure}.
-Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.
+The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the skeleton.
+These central regions present themselves as upper ridges in the mountains of the UoC surface.
+This sections covers what parts of the UoC will be marked as being central, rather than peripheral.
 
 We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
+That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
 We also mark whole bones as being central if they are significant according to a common significance measure.
@@
 \subsubsection{Significance measure}\label{sec:significance_measure}
-Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which are in some sense \emph{central} to the shape.
-This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
+Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
 The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
@@
 \centering
-\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
+\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
 \caption{
@@
 
-A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
+A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
 if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
+See \cref{distance_based_angles}.
 This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
-See \cref{distance_based_angles}.
+Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
+
 This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
@@
 and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
-This ensures that the discretization doesn't alter the extent and existence of significant regions.
+This ensures that the discretization doesn't alter the extent and existence of marked central regions.
 See \cref{discretization}.
@@
 
+\fi
+
 \iffalse
@@
 Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
-We then filter out high frequency changes in the marking in order to ensure smooth output toolpaths. 
-We perform filtering on the unmarked regions, so that the properties of significant regions mentioned above remain valid.
-From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}).
-If the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.
+We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
+We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
+From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges;
+if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.
 

### 2019-08-21 4_method.tex
fix some small stuff in overview and mesh generation

@@
 In the UoC \subref{3d_surface_overview_uoc}
-we mark the central regions blue \subref{3d_surface_overview_center}
+we mark the central regions \subref{3d_surface_overview_center}
 and round the height values to the nearest integer muliple of half the nozzle width \subref{3d_surface_overview_rounded}.
@@
 and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
+Blue signifies regions marked as being central.
+The numbers are the integer multiples of half the nozzle width.
 }
@@
 
-\subsection{Surface construction}\label{sec_surface_construction}
+\subsection{Surface generation}\label{sec_surface_construction}
 The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
@@
 This makes the skeleton capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
+The UoC is the ST along with the corresponding feature radius $R$ as the height of each node.
 %; see \cref{mat_3d}.

### 2019-08-21 4_method.tex
redo central height adjustment

@@
 \subsection{Central height adjustment}\label{sec_central_height_adjustment}
-\todo{TODO: explain section title!}
+Now that we have identified and marked the central regions we can round the heights to integer multiples of half the nozzle size.
+We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
+We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
+While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
+we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
 
-\todo{Introduce what's to come in this section.}
+\subsubsection{Initial bead count}\label{sec_initial_bead_count}
+In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
+For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
+In our generalized framewotk the function $b$ is determined by a beading strategy.
 
-\subsubsection{Initial bead count}
-In order to apply a beading strategy to the ST we first assign bead counts to the central regions and then decide on how to apply those bead counts outward.
-In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
-(The feature diameter is twice the radius.)
-For example we might choose to round to the nearest integer multiple of some preferred width $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-The function $b$ is determined by the beading strategy and is required to increase monotonically with the input feature diameter.
-
-We first assign each marked node $v$ of the skeleton an initial bead count $b^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
-See \cref{beading_transitioning_filtering__bead_count}.
-
-We also filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
-From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
+We first assign each marked node $v$ of the skeleton an initial bead count $b^*_v \leftarrow b(2R(v))$.
+We then filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
+From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
 If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
@@
 \centering
-\setlength{\figwidth}{0.15\textwidth}
+\setlength{\figwidth}{0.13\textwidth}
 \begin{subfigure}{\figwidth}
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
-\caption{Transition ends}\label{beading_transitioning_filtering__transition_ends}
+\caption{Transition remp ends}\label{beading_transitioning_filtering__transition_ends}
 \end{subfigure}
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
-\caption{Radial bones}\label{beading_transitioning_filtering__transitions_applied}
+\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
+\end{subfigure}
+\begin{subfigure}{.27\textwidth}
+\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
+\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
 \end{subfigure}
@@
 \subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
-\subref{beading_transitioning_filtering__filtered}We then filter out regions of constant bead count.
+\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
 \subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
@@
 \subsubsection{Transitioning}
-In order to prevent discontinuities in the toolpaths around locations where the bead count changes, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
-See \cref{transitions}.
-The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
-Because transitions in bead count only occurs in locations where the preferred bead count $b$ changes, we introduce $b^{-1}(n) := \argmax_d b(d) = n$.
+For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the preferred bead count $b(2R(v))$ changes.
+We call these locations the \emph{transition anchor positions}.
+Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
 
-For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
-A transition from bead count $n$ to $n+1$ will be placed anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
+We introduce the function $b^{-1}(n) := \argmax_d b(d) = n$.
+%For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
+A transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
 We can compute the location of the anchor simply as
@@
 
-A transition with length $t(n)$ will be placed somewhere covering the anchor position.
-We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
-From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
-The transitions lengths should be such that they fit between anchor locations of two consecutive transitions even for a bone with high bisector angle:
-$$t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$$
-for each $n \in \mathbb{N}$.
-See \cref{transition_placement}.
-
-\begin{figure}
-\centering
-\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
-\caption{
-Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
-The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
-}
-\label{transition_placement}
-\end{figure}
-
 In order to prevent frequent oscillations in the bead count, we filter locally maximal or minimal bead count regions.
@@
 If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
-If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner.
 See \cref{beading_transitioning_filtering__filtered}.
 
-In order to generate the lower and upper end point of the transitions we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
+\subsubsection{Height smoothing}
+In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e.
+where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
+See \cref{transitions}.
+The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
+For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
+
+A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
+We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
+From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
+For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
+
+Before we generate the transition ramps we filter out transition anchors which are positioned too close to the end of a marked region.
+For each edge which contains a transition anchor we walk along the marked regions until until we have traversed a distance more than $t(n)$.
+If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner as described above.
+
+The generation of the transition ramps should be robust against small perturbations in the outline shape;
+compare the top and bottom of \cref{beading_transitioning_filtering}.
+In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
 If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
 See \cref{beading_transitioning_filtering__transition_ends}.
-These fractional bead counts will be used in \cref{section_beading_interpolation}.
+These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support bones for small perturbations and those which are not.
 
-Finally we perform the graph update by introducing nodes at the transition ends and introducing radial bones from these new nodes to the outline as per the trapezoidation requirement.
-See \cref{beading_transitioning_filtering__transitions_applied}.
+Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support bones from these new nodes to the outline as per the trapezoidation requirement.
+We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
+See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.
 
@@
 Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
-We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \frac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
+We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
 See \cref{beading_interpolation}.

### 2019-08-21 5_generalization.tex
redo overview
redo central height adjustment

@@
-\section{Generalization}
+\section{Generalization}\label{sec_generalization}
 In this section we will generaize the described method into a parametric system, i.e. a geometric framework.
@@
 \end{enumerate}
+
+\todo{TODO: Format this in the same way is the list above:}
+The transitions lengths should be such that they fit between anchor locations of two consecutive transitions even for a bone with high bisector angle:
+$$t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$$
+for each $n \in \mathbb{N}$.
+See \cref{transition_placement}.
+
+\begin{figure}
+\centering
+\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
+\caption{
+Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
+The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
+}
+\label{transition_placement}
+\end{figure}
 

### 2019-08-22 4_method.tex
redo peripheral heights section

@@
 \setlength{\figwidth}{\columnwidth}
-\begin{subfigure}{0.9\figwidth}
+\begin{subfigure}{0.9\figwidth}\centering
 \includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated__no_transitions.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{0.9\figwidth}
+\begin{subfigure}{0.9\figwidth}\centering
 \includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated.pdf}
@@
 
-\subsection{Peripheral height adjustment}\label{sec_peripheral_height_adjustment}
+\subsection{Peripheral heights}\label{sec_peripheral_height_adjustment}
+Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e.
+the periphery, and slice the resulting mesh into isocontour toolpaths.
+The peripheral heights could be determined in a plethora of ways according to various beading strategies.
+The ramps from the outline shape to the center might have various curves,
+but for our example we use straight ramps, just like the original UoC.
+See \cref{peripheral_heights}.
+That means we can stretch the $R$ heights of the UoC with a multiplier depending on the height of the center in terms of bead count.
 
-For our purposes we only need to define the height at the locations which will be part of a slice.
-Instead of adjusting the height of peripheral nodes, we determine the locations along the bones where the adjusted height is an integer multiple of half the nozzle size.
+\begin{figure}\centering
+\setlength{\figheight}{.2\columnwidth}
+\begin{subfigure}{.55\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/peripheral_heights_3D.png}
+\caption{Surface mesh}
+\end{subfigure}
+\begin{subfigure}{.4\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/peripheral_heights.pdf}
+\caption{ST}
+\end{subfigure}
+\caption{
+Shallow corners will cause peripheral nodes for which the height should be determined based on the central node above it.
+}
+\label{peripheral_heights}
+\end{figure}
+
+For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
+Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the bones where the adjusted height coincides with a slicing height.
+In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
+how each beading is calculated for a central node
+and how the beadings are propagated outward to peripheral nodes.
 This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.
 
-\todo{TODO:}
-\begin{itemize}
-\item explain section title
-\item Reword and/or introduce concept of Beading 
-\item Check compatibility with surrounding text!
-\end{itemize}
+\begin{definition}
+In order to help generate these toolpath locations we associate each central node with a mapping from radial distances to bead indices, the beading $B$,
+which we define as the following set:
+$$
+B = \left\{ d, n, \left\{ w_0 , \dots , w_{n-1} \right\}, \left\{ l_0 , \dots , l_{n-1} \right\}  \right\}
+$$
+where
+$d = 2 R(v)$ is the diameter associated with $v$,
+$n \in \mathbb{N}$ is the bead count,
+$w_i$ is the bead width of the bead with index $i$ counting from the outline inward
+and
+$l_i$ is the radial distance which maps to the bead with index $i$.
+\end{definition}
 
-Now that we have decided on the bead counts in the central marked regions, we can apply those bead counts outward along the unmarked bones of the skeleton in order to define the locations of the toolpath junctions.
-Because there is a plethora ways to cover a distance $d$ with $n$ beads, the placement of junctions depends on the chosen beading strategy.
-The beading strategy is used to generate the bead widths and radial distances at which the junctions are placed for each node: the \emph{beading}.
-That beading information is then propagated along the unmarked bones of the skeleton, so that we can generate the junctions on each unmarked bone.
-The junctions are then connected together per trapezoid in order to form the final toolpaths.
+For our example we linearly map the $R$ values using a multiplication factor of $d/n$:
+\begin{align*}
+w_i &= d/n  \\
+l_i &= d / n (i + \nicefrac12)
+\end{align*}
+An example beading is visualzied in the top of \cref{beading_interpolation}:
+$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial distances $l$ evenly divided over the length $d$.
 
-\todo{Definition of beading strategy got moved!}
-\todo{Check compatibility with surrounding text!}
+The beading information will be used in the next phase to directly generate the junctions of the toolpaths.
+Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
+the upper half of the beading is therefore unused.
 
 \subsubsection{Beading interpolation}\label{section_beading_interpolation}
-Skeletal nodes which are in the middle of a transition have obtained a fractional bead count, but the functions defined in the beading strategy are only defined on natural numbers.
-The fractional part of the bead count is used to interpolate between two beadings defined on the fractional bead count rounded up and down.
+Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
+In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
 Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
@@
 \subsubsection{Beading propagation}\label{section_beading_conflicts}
-Because the beading information will be propagated outward from the central marked regions, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
+The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
+However, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
 See \cref{beading_conflict_problem}.
@@
 This interpolation is performed during the beading propagation algorithm.
-\todo{Make a better figure for this.}
 
-\begin{figure}
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/transition_to_insignificance_problem.pdf}
+\begin{figure}\centering
+\setlength{\figheight}{.2\columnwidth}
+\begin{subfigure}{.45\columnwidth}\centering
+\includegraphics[width=\columnwidth]{sources/method/beading_conflict_3D.png}
+\includegraphics[height=\figheight]{sources/method/beading_conflict.pdf}
+\caption{Beading conflict}\label{beading_conflict}
+\end{subfigure}
+\begin{subfigure}{.45\columnwidth}\centering
+\includegraphics[width=\columnwidth]{sources/method/beading_conflict_solved_3D.png}
+\includegraphics[height=\figheight]{sources/method/beading_conflict_solved.pdf}
+\caption{Conflict resolution}\label{beading_conflict_solved}
+\end{subfigure}
 \caption{
-Problems at the boundary of marked regions highlighted with red ovals.
-The beading approach from the marked region (blue) results in toolpaths (black) which don't line up with the approach following from the beading which results from the bead count at the local maximum in the bottom center.
+\subref{beading_conflict} The beading propagated from above conflicts with the beading below.
+\subref{beading_conflict_solved} The beading conflict is resolved by gradually interpolating between the two beadings.
+The ramp to the upper ridge doesn't line up with the lower ridge, which means that
+the toolpaths (dashed) resulting from the beading propagated from above doesn't align with the beading from the thin outline feature (highlighted in red).
 }

### 2019-08-22 4_method.tex
redo generalziation section

@@
 and
-$l_i$ is the radial distance which maps to the bead with index $i$.
+$l_i$ is the radial locations which maps to the bead with index $i$.
 \end{definition}
@@
 An example beading is visualzied in the top of \cref{beading_interpolation}:
-$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial distances $l$ evenly divided over the length $d$.
+$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
 
@@
 Applying beadings togenerate junctions along trapezoids.
-\subref{trapezoid_beading_beading} shows half of the locations $L(n,d)_i$ and widths $W(n,d)_i$ of two arbitrary different beadings.
+\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
 \subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
@@
 No junctions will be generated along marked bones.
-Wide black lines are outline segments, marked nodes and bones in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = L(n,d)_i$.
+Wide black lines are outline segments, marked nodes and bones in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
 }

### 2019-08-22 5_generalization.tex
redo generalziation section

@@
 \section{Generalization}\label{sec_generalization}
-In this section we will generaize the described method into a parametric system, i.e. a geometric framework.
-
-\todo{TODO:}
-\begin{itemize}
-\item introduce section
-\end{itemize}
-
-\subsection{Beading strategy}
-Depending on the application, the hardware and the materials used we might want to have different strategies for filling a shape with contour parallel toolpaths.
-we therefore..
+In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
+The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
+Depending on the application, the hardware and the materials used we might need different strategies for determining the bead widths.
+In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
+There are several strategies one can take for determining the distribution of bead widths.
+We will formalize several strategies and describe the set of parameters these strategies require.
 
@@
 We introduce here
-$W(n, d)$, which gives the sequence of bead widths to cover a distance $d$ using $n$ beads
+$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
 and
-$L(n, d)$, which gives the sequence of toolpath positions as radial distances from the outline to cover a distance $d$ using $n$ beads.
+$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
 \end{definition}
@@
 \begin{enumerate}
+\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
 \item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
 \item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
+\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
 \end{enumerate}
-
-\todo{TODO: Format this in the same way is the list above:}
-The transitions lengths should be such that they fit between anchor locations of two consecutive transitions even for a bone with high bisector angle:
-$$t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$$
-for each $n \in \mathbb{N}$.
-See \cref{transition_placement}.
 
@@
 
-\begin{definition}
-By applying the beading strategy to a skeleton location $v$ and a predetermined bead count $n$ we get a beading $B$, which is defined as the following set:
-$$
-\left\{ d, n, w_i, l_i  \right\}
-$$
-where
-$d = 2 R(v)$ is the diameter associated with $v$,
-$n$ is the bead count,
-$w_i$ is the bead width of the bead with index $0 \leq i < n$ counting from the outline inward
-and
-$l_i$ is the distance of the toolpath location of bead with index $0 \leq i < n$.
-\end{definition}
-
 \subsection{Beading strategies}
-\todo{This section was moved. Check compatibility with surrounding text.}
-
-Now that we have described a framework for deciding and applying on bead counts and their widths locally, we can introduce several beading strategies which determine the bead count and their widths in different ways.
+We introduce several beading strategies which determine the bead count and their widths in various ways.
 We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.

### 2019-08-22 0_main.tex
forgot to actually add the new section
redo overview
fix order of chapters
change title

@@
 \usepackage{amsmath}
-\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
+\usepackage[draft]{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
 %\modulolinenumbers[5]
@@
 	\newlength{\figwidth}
+	\newlength{\figwidthTwo}
+	\newlength{\figwidthTree}
 	\newlength{\figheight}
 	\newlength{\figheightTwo}
+	\newlength{\tempheight}
+	\newlength{\tempheightTwo}
 
@@
 %\title{A robust framework for variable extrusion width concentric toolpath generation}
-\title{A parametric system for adaptive extrusion width contour parallel toolpath generation}
+\title{A parametric system for generating contour parallel toolpaths with adaptive extrusion width}
 
@@
 
+\input{5_generalization}
+
 \input{6_validation}

### 2019-08-22 8_discussion.tex
explain robustness better

@@
 Note also that our method is robust against small perturbations in the input shape.
-Although the skeleton might acquire extra bones, the significant portions of the skeleton remain similar and the output toolpaths change infinitesimally.
+Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the ST graph.
+However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the unstability of the skeleton.
+Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
+The toolpaths generated using our framework therefore remain the same when extra bones are added to the ST.
 

### 2019-08-22 6_validation.tex
move computation time to results

@@
 
-\paragraph{Accuracy}
+\paragraph{Computation time}
+The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
+The number of elements in the trapezoidation is linear in the number of elements in the VD
+and all of the stages of our framework are also linear in the number of elements in the skeleton,
+so the total running time of our algorithm is $O(n \log n)$.
+
+From the experimental results shows in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
+The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
+
+% only Moessen reports on computation times, but in a weird manner
+
+\subsubsection{Accuracy}
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
@@
 
-\paragraph{Uniformity}
+\subsubsection{Uniformity}
 Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.

### 2019-08-22 8_discussion.tex
move computation time to results

@@
 and it also allows for some parallelism during the computation of the toolpaths.
-
-\subsection{Computation time}
-The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
-The number of elements in the trapezoidation is linear in the number of elements in the VD
-and all of the stages of our framework are also linear in the number of elements in the skeleton,
-so the total running time of our algorithm is $O(n \log n)$.
-
-From the experimental results shows in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
-The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
-
-% only Moessen reports on computation times, but in a weird manner
 

### 2019-08-22 4_method.tex
new legend
explain that the method is only about the evenly distributed strategy

@@
 
+This section explains how we can generate toolpaths with evenly distributed bead widths.
 We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
@@
 and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
-In \cref{sec_generalization} we describe how to generalize our method into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.
+In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.
 
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{sources/method/terminology.pdf}
-\caption{Explanation of terms.}
+\begin{figure}\centering
+\includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
+\caption{Explanation of terms and common color coding.}
 \label{legend}
@@
 
+\iffalse
+
 \begin{figure}
@@
 \end{figure}
+
+\fi
 
@@
 This ensures that the discretization doesn't alter the extent and existence of marked central regions.
-See \cref{discretization}.
+See \cref{legend}.
 

### 2019-08-22 4_method.tex
explain domains early

@@
 \begin{figure}\centering
-\setlength{\figwidth}{0.24\columnwidth}
-\setlength{\figwidthTwo}{0.15\columnwidth}
+\setlength{\figwidth}{0.19\columnwidth}
+\setlength{\figwidthTwo}{0.3\columnwidth}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_mat}
-\caption{MAT}\label{shape_decomposition_mat}
+\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
+\caption{Medial Axis}\label{shape_decomposition_mat}
 \end{subfigure}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_vd}
-\caption{VD}\label{shape_decomposition_vd}
+\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
+\caption{Voronoi Diagram}\label{shape_decomposition_vd}
 \end{subfigure}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_st}
-\caption{ST}\label{shape_decomposition_st}
+\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
+\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
 \end{subfigure}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
-\caption{Datastructure}\label{shape_decomposition_datastructure}
+\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
+\caption{Data structure}\label{shape_decomposition_datastructure}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
+\caption{Polygon Domains}\label{shape_decomposition_domains}
 \end{subfigure}
@@
 See \cref{shape_decomposition_datastructure}.
+
+The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
+Each polygon in the input shape acquires it's own domain.
+The domains of hole polygons are touching the domains of the outer polygon.
+See \cref{shape_decomposition_domains}.
 

### 2019-08-22 6_validation.tex
redo gMAT toolpath widths an accuracy

@@
 \section{Validation}
-In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
+In order to test our framework, we have assembled a dataset of different types of 3D models, ranging over various applications and various types of geometry.
 The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
-We sliced all models in the dataset and selected 300 random slices from the total set of slices for thorough analysis.
-We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the constant bead count strategy with a bead count of $C=4$, the centered beading strategy, the evenly distributed, and the inward distributed beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We sliced all models in the dataset and selected 300 random slices from the total set of slices for analysis.
+We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 
-\paragraph{Computation time}
 The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
@@
 
-From the experimental results shows in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
+From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
 The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
@@
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get strange artifacts at corners in the toolpath.
-We therefore use a semi-circle with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
-For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position.
-In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
-See \cref{segment_visualization}.
+If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
+We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
+For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position ( \cref{segment_visualization}c).
+
+%In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
+%See \cref{segment_visualization}.
 
@@
 The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a clipper operation which only keeps areas of positive winding order.
-Because the reverse outline shape reduces the winding order of all extruded segments by one, we are left with the overfill areas.
-In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing the clipper operation.
+We then add the original outline shape in reverse and perform a Vatti clipping operation \cite{Vatti2019clipping} which only keeps areas of positive winding number.
+Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
+In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
 These triple extrusion areas count double toward the total amount of overfill.
@@
 \caption{
-Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
-Grey areas are covered by extruded material,
+Visualizing the overfills and underfills and the widths for various beading strategies.
+Extrusion beads in gray tones,
 blue areas in the top images signify underfill regions,
@@
 orange areas triply extruded areas (double overfill).
-The bottom visualizes the bead widths at each location by exaggerating their widths.
-Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
+The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
+Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
 }
@@
 We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
-The overfill and underfill area as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
+The overfill and underfill areas as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
 The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
@@
 \setlength{\figheight}{0.2\textwidth}
-\setlength{\figwidth}{0.24\textwidth}
+\setlength{\figwidth}{0.31\textwidth}
 \begin{subfigure}{\figwidth}\centering
@@
 \label{computime}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
+\caption{Relative frequency of extrusion widths}
+\label{widthHistogram}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/indexedwidths2.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
+\caption{Relative frequency of extrusion widths for 6 outer contours}
+\label{widthIndexedHistogram}
 \end{subfigure}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Relative frequency of extrusion widths}
-\label{widthHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
 \includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
@@
 \end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/smoothnessNoTransition.pdf}
+%\includegraphics[width=\figwidth]{sources/validation/smoothnessNoTransition.pdf}
+\caption{Frequency of angles with and without transitions}
+\label{smoothnessNoTransition}
+\end{subfigure}
+
 \caption{
@@
 \subsubsection{Uniformity}
-Depending on the printer hardware configuration, some bead widths might be difficult or impossible to manufacture.
+Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
 A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
-Also, large bead widths can cause the extruded material to bulge upwards instead of filling the required width.
-\todo{Include picture of flutter?}
+Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
 Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
-We visualize the bead widths resulting from the different strategies in an exaggerated manner in the bottom of \cref{visualized_accuracy}.
+We visualize the bead widths resulting from the different strategies in the bottom of \cref{visualized_accuracy}.
 
 To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
-at intervals of \SI{200}{\micro\meter} along the toolpath.
-From these sampled values, we calculated the mean bead width, and standard deviation.
+at intervals of \SI{1}{\micro\meter} along the toolpath.
+From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
 \cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
-The results show that the mean width of our strategies "Inwards distributed" and "Evenly distributed" is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies "Centered" and "Constant bead count".
-These values indicate that, while causing less overfill and underfill, our strategy deviates less and less often from the nominal nozzle size.
+We found that the mean width of our strategies 'Inwards distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'.
+These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
 
@@
 The relative frequency of these angles is shown in \cref{smoothness}.
-All strategies show a higher number of corners below 45 degrees, with a peak towards 0 degrees.
-While the strategy "constant bead width" has a lower number of corners overall, we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
+All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
+The 'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
+While 
+ we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
 

### 2019-08-23 1_intro.tex
redo all accuracy and width figures

@@
 \begin{figure}\centering
-\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_pretty.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_pretty.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_pretty.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_accuracy.png}
 \caption{

### 2019-08-23 5_generalization.tex
redo all accuracy and width figures

@@
 We introduce several beading strategies which determine the bead count and their widths in various ways.
-We can emulate a variety of toolpath generation methods from related literature by meticulously defining new beading strategies.
+We can emulate a variety of toolpath generation methods from related literature by defining new beading strategies.
 We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.
@@
 \centering
-\setlength{\figwidth}{.45\columnwidth}
+\setlength{\figwidth}{.4\columnwidth}
+\setlength{\figheight}{.25\columnwidth}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
+\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
 \caption{Evenly distributed}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
+\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
 \caption{Inward distributed}
+\end{subfigure}
+\begin{subfigure}{.1\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
 \end{subfigure}
@@
 Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
+Colors represent bead widths.
 }

### 2019-08-23 10_applications.tex
make applciations a subsection of discussion

@@
-\section{Applications}
+\subsection{Applications}
 Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.

### 2019-08-23 4_method.tex
reconceptualize rounding as flattening

@@
 These offsets can be generated from the medial axis transform (MAT).
-The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones of \SI{45}{\degree} which are touching the input shape.
+The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape.
 \cite{blum1967transformation}
@@
 because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
-We therefore change the UoC mesh such that an exact integer beads will be generated in the center.
-More specifically, we round the height to the nearest multiple of \emph{half} the nozzle size.
-That way we allow for an odd number of beads to be placed between the two sides of the outline shape.
+Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
 
-Our technique consists of the folowing steps:
+Our framework can be thought of as following these steps:
 \begin{itemize}
-\item Compute the mesh representing the Union of Cones (UoC) for the input shape
+\item Compute the skeleton of the input shape
+\item Assign each node a height in terms of bead count based on the local feature size
 \item Identify central regions of the UoC
-\item Round the heights of central nodes to to the nearest slicing height
+\item Flatten the central regions at heights equal to the nearest integer bead count
 \item Smooth out sharp transitions between regions with different integer heights
@@
 \includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
-\caption{Rounded}\label{3d_surface_overview_rounded}
+\caption{Flattened}\label{3d_surface_overview_rounded}
 \end{subfigure}
@@
 we mark the central regions \subref{3d_surface_overview_center}
-and round the height values to the nearest integer muliple of half the nozzle width \subref{3d_surface_overview_rounded}.
+and flatten those regions to heights of the nearest integer \subref{3d_surface_overview_rounded}.
 We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
@@
 explain how to identify central regions in \cref{sec_center_classification}.
-Rounding the heights in the central mesh regions and smoothing those heights is handled in \cref{sec_central_height_adjustment}.
+Flattening the central mesh regions and smoothing are handled in \cref{sec_central_height_adjustment}.
 We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
@@
 Overview of the steps in the method of our framework.
-First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine an initial bead count (numbers) based on the local feature size.
+First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine a bead count (numbers) based on the local feature size.
 Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
@@
 
+\subsubsection{Union of cones}
+In order to transform the ST into a 3D surface we add another dimension to the skeleton.
+We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
+We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
+While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
+we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
+
+For each node $v$ we assign an initial bead count based on the feature diameter $2R$ and the nozzle size $w_\text{pref}$: $b^*_v \leftarrow 2 R(v) / w_\text{pref}$.
+The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
+Note that although the overview of the method was described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+
 \subsection{Center classification}\label{sec_center_classification}
@@
 \subsection{Central height adjustment}\label{sec_central_height_adjustment}
-Now that we have identified and marked the central regions we can round the heights to integer multiples of half the nozzle size.
-We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
-We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
-While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
-we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
+Now that we have identified and marked the central regions we flatten those regions to integer heights.
+More specifically we round the heights to integer bead count values.
+When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
+When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
 
-\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-In order to decide on an initial bead count, we require a function mapping a feature diameter to a bead count: $b: \mathbb{R} \to \mathbb{N}$.
-For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $b(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
+%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
+In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
+For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
 In our generalized framewotk the function $b$ is determined by a beading strategy.
 
-We first assign each marked node $v$ of the skeleton an initial bead count $b^*_v \leftarrow b(2R(v))$.
-We then filter unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
+We first assign each marked node $v$ of the skeleton the bead count $b^*_v \leftarrow f(2R(v))$.
+We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
 From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
-\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
+\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
 \end{subfigure}
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
-\caption{Transition remp ends}\label{beading_transitioning_filtering__transition_ends}
+\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
 \end{subfigure}
@@
 
-\subsubsection{Transitioning}
-For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the preferred bead count $b(2R(v))$ changes.
+\subsubsection{Flattening}
+For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
 We call these locations the \emph{transition anchor positions}.
@@
 
-We introduce the function $b^{-1}(n) := \argmax_d b(d) = n$.
+We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
 %For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
-A transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = b^{-1}(n)$.
+A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
 We can compute the location of the anchor simply as
-$$v_x = v_0 + (v_1 - v_0) \frac{ b^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
+$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
 for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
@@
 
-\subsubsection{Height smoothing}
+\subsubsection{Smoothing}
 In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e.

### 2019-08-23 5_generalization.tex
reconceptualize rounding as flattening

@@
 $$
-\left\{ \alpha_\text{max}, b(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
+\left\{ \alpha_\text{max}, f(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
 $$
@@
 $\alpha_{\text{max}}$ (the limit bisector angle),
-$b(d)$ (optimal bead count),
+$f(d)$ (flattening operator),
 $t(n)$ (transition length)
@@
 \begin{enumerate}
-\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ b^{-1}(n + 1) - b^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
+\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ f^{-1}(n + 1) - f^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
 \item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
@@
 %We use a transition anchor position of
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
-%$$t_-(n) =  t(n) \frac{ b^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( b^{-1}(n) / w_\text{pref}  - n \right) \\
+%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
+%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
+%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4}$$
+t_0(n) &=  t(n) \left( f^{-1}(n) / w_\text{pref}  - n \right) \\
 t(n) &= w_\text{pref} \\
@@
 \alpha_\text{max} &= \SI{180}{\degree} \\
-b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
 W(n,d)_i &= w_\text{pref} \text{ for all } i 
@@
 t(n) &= 0 \\
-b(d) &=
+f(d) &=
 \begin{cases}
@@
 \alpha_\text{max} &= \SI{0}{\degree} \\
-b(d) &= C \\
+f(d) &= C \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
-We therefore base the beading strategy on the bead count $b^(d)$ defined by the naive beading strategy.
+We therefore base the beading strategy on the bead count $f^-(d)$ defined by the naive beading strategy.
 \citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
@@
 t(n) &= \frac12 w_\text{pref} \\
-b^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
-b(d) &= b^-(d) +
+f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+f(d) &= f^-(d) +
 \begin{cases}
--1 & \text{ if } b^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
-1  & \text{ if }  b^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
+-1 & \text{ if } f^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
+1  & \text{ if }  f^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
 0 & \text{ otherwise}
@@
 \begin{align*}
-b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 \begin{align*}
-b(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
 E(n,d) &= d - n w_\text{pref} \\

### 2019-08-23 5_generalization.tex
explain how the generalization can be done without extra work

@@
 \end{figure}
+
+Because the peripheral height adjustment was described in terms of a mapping from radial distances to junctions rather than adjusting the heights of peripheral nodes,
+we can introduce non-linear mappings without refining the surface mesh.
+In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
+If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thsu their width becomes larger when going inward.
+In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
+However, our approach bypasses the peripheral height adjustment and directly generates the radial distances at the slicing heights, which means our technique generalized effortlessly.
 

### 2019-08-23 4_method.tex
new transitiong wedge figure

@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated__no_transitions.pdf}
+\includegraphics[width=\columnwidth]{sources/method/wedge_no_transitioning.png}
 \caption{Without transitioning}
@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated.pdf}
+\includegraphics[width=\columnwidth]{sources/method/wedge_transitioning.png}
 \caption{Transitioning}

### 2019-08-23 4_method.tex
lil stuff

@@
 In order to transform the ST into a 3D surface we add another dimension to the skeleton.
-We assign each node a new height value measured in terms of an integer number: it's \emph{bead count}.
+We assign each node a height value measured in terms of an integer number: it's \emph{bead count}.
 We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
@@
 \caption{
-Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomp_complex}.
+Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomposition_domains}.
 Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.

### 2019-08-23 0_main.tex
turn off draft hyperref
lil edits

@@
 \usepackage{amsmath}
-\usepackage[draft]{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
+\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
 %\modulolinenumbers[5]
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
-FDM builds up objects by depositing material along paths which lie in horizontal layers.
+FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
 The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.

### 2019-08-23 1_intro.tex
lil edits

@@
 FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
-Because the resolution of the positioning system is order of magnitude smaller than the width of the nozzle (typically from $??$ to $??$),
-the toolpaths for filling the arbitrary polygonal shape of a layer with extrusion beads are following the contour of that layer.
-\jun{I had difficulty to follow the logic behind this sentence}
+A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
+because the positiong and shape of the toolpath can be controled relatively accurately.
+Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
+Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.
 

### 2019-08-23 4_method.tex
lil edits

@@
 That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
-We also mark whole bones as being central if they are significant according to a common significance measure.
+We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.
 
@@
 Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
+The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
 Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

### 2019-08-23 5_generalization.tex
Zjenja: validation figures and text edits

--- 2019-08-23 5_generalization.tex
@@
 \centering
-\setlength{\figwidth}{.4\columnwidth}
-\setlength{\figheight}{.25\columnwidth}
+\setlength{\figwidth}{.45\columnwidth}
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
+\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_evenly.png}
 \caption{Evenly distributed}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
+\includegraphics[width=.8\columnwidth]{sources/validation/wedge_Distributed_pretty_inward.png}
 \caption{Inward distributed}
-\end{subfigure}
-\begin{subfigure}{.1\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
 \end{subfigure}
@@
 Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
-Colors represent bead widths.
 }

### 2019-08-23 6_validation.tex
redo all accuracy and width figures
Zjenja: validation figures and text edits

@@
 \caption{
-Visualizing the overfills and underfills and the widths for various beading strategies.
-Extrusion beads in gray tones,
+Visualizing the overfills and underfills and the exaggerated widths for various beading strategies.
+Grey areas are covered by extruded material,
 blue areas in the top images signify underfill regions,
@@
 orange areas triply extruded areas (double overfill).
-The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
-Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
+The bottom visualizes the bead widths at each location by exaggerating their widths.
+Cold colors are narrower than the nozzle size and warm colors are wider than the nozzle size.
 }

### 2019-08-23 4_method.tex
remove old overview figure

@@
 \end{figure}
-
-\iffalse
-
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.19\textwidth}
-\begin{subfigure}{\figwidth}
-\centering
-\includegraphics[width=\columnwidth]{sources/method/overview/skeleton.pdf}
-\caption{Skeleton}\label{overview_fig_skeleton}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\centering
-\includegraphics[width=\columnwidth]{sources/method/overview/marked.pdf}
-\caption{Marked}\label{overview_fig_marked}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\centering
-\includegraphics[width=\columnwidth]{sources/method/overview/transitions.pdf}
-\caption{Transitions}\label{overview_fig_transitions}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\centering
-\includegraphics[width=\columnwidth]{sources/method/overview/junctions.png}
-\caption{Junctions}\label{overview_fig_junctions}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\centering
-\includegraphics[width=\columnwidth]{sources/method/overview/toolpaths.png}
-\caption{Toolpaths}\label{overview_fig_toolpaths}
-\end{subfigure}
-\caption{
-Overview of the steps in the method of our framework.
-First we \subref{overview_fig_skeleton} decompose the outline shape into a skeleton (grey), \subref{overview_fig_marked} mark central regions (blue) and determine a bead count (numbers) based on the local feature size.
-Then we \subref{overview_fig_transitions} make alterations to smoothly transition to a different bead count (magenta).
-We then \subref{overview_fig_junctions} generate a number of junctions (yellow) equal to the bead count along the bones of the skeleton,
-which are \subref{overview_fig_toolpaths} connected together to make the toolpaths.
-}
-\label{overview_fig}
-\end{figure*}
-
-\fi
 

### 2019-08-23 4_method.tex
remove old discretization figure

@@
 %; see \cref{mat_3d}.
-
-\iffalse
-
-\begin{figure}
-\centering
-%\begin{subfigure}{0.45\textwidth}
-%\includegraphics[width=\columnwidth]{sources/method/parabola_dip.pdf}
-%\caption{asf}
-%\end{subfigure}
-%\begin{subfigure}{0.45\textwidth}
-\includegraphics[width=.5\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
-%\caption{Transitioning}
-%\end{subfigure}
-\caption{
-Skeletal trapezoidation domain decomposition.
-Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
-Parabolic medial axis segments are discretized and likewise for segments generated by two concave outline vertices, because the feature radius (black text in microns) doesn't increase linearly along those segments.
-The blue segments are significant according to $\alpha_\text{max} = 135\degree$.
-}
-\label{discretization}
-\end{figure}
-
-\fi
 

### 2019-08-23 4_method.tex
lil rewording

@@
 See \cref{MAT_explanation_circles}.
+We therefore represent the skeleton in a standard half-edge data-structure.
+See \cref{shape_decomposition_datastructure}.
 
@@
 Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
+\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
+\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the inout shape polygons.
 }
@@
 We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
-(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
-We represent such a skeleton in a standard half-edge data-structure.
-See \cref{shape_decomposition_datastructure}.
+\footnote{The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984}}
 
@@
 That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-This makes the skeleton capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
-The UoC is the ST along with the corresponding feature radius $R$ as the height of each node.
+This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
 %; see \cref{mat_3d}.
@@
 \subsubsection{Union of cones}
-In order to transform the ST into a 3D surface we add another dimension to the skeleton.
-We assign each node a height value measured in terms of an integer number: it's \emph{bead count}.
+In order to visualize the ST as a 3D surface, we add a third dimension.
+We assign each node a height value measured in terms of beads: it's \emph{bead count}.
 We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.

### 2019-08-23 4_method.tex
'skeleton'/'graph' => 'ST'

@@
 \subsection{Center classification}\label{sec_center_classification}
-The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the skeleton.
+The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the ST.
 These central regions present themselves as upper ridges in the mountains of the UoC surface.
-This sections covers what parts of the UoC will be marked as being central, rather than peripheral.
+This sections covers what parts of the UoC will be marked as being central, as opposed to peripheral.
 
-We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
+We mark a node in the ST as central if its feature radius is larger than that of all of the neighboring nodes.
 That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
@@
 Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
+The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
 Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
@@
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
-We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the skeleton.
+We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the ST.
 Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.
@@
 See \cref{distance_based_angles}.
-This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
+This means we can prevent executing trigonometric functions on \emph{each} of the bones in the ST.
 Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
 
-This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
-For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
+This ratio can readily be applied to simple ST segments to determine whether they are significant.
+For segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
 For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
@@
 Part of outline shape in thick black,
-skeleton in red,
+ST edges in red,
 inscribed circle in gray,
@@
 %\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
-The Euclidean distance between two skeletal vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
+The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
 See \cref{distance_ratio_limit}.
@@
 % This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
-A node in the graph can have at most two significant edges.
+A node in the ST can have at most two significant edges.
 For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
@@
 A saddle point is always marked, i.e.\
-when traversing the skeletal graph from one locally maximal $R$ to another we must pass through a significant region.
+when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
 \end{lemma}
@@
 \begin{lemma}\label{single_upward_edge}
-From any node in the graph which is not a saddle point there is at most a single edge going upward.
+From any node in the ST which is not a saddle point there is at most a single edge going upward.
 \end{lemma}
@@
 Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
-This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
+This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
 \end{proof}
@@
 
-We first assign each marked node $v$ of the skeleton the bead count $b^*_v \leftarrow f(2R(v))$.
+We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
 We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
@@
 \caption{
-Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
+Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
 Outline in black, medial axis edges in red, radial edges in grey.
@@
 A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
-We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the skeleton.
+We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the ST.
 From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
@@
 See \cref{beading_interpolation}.
-The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the skeleton inside of transition regions.
+The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the ST inside of transition regions.
 

### 2019-08-23 5_generalization.tex
'skeleton'/'graph' => 'ST'

--- 2019-08-23 5_generalization.tex
@@
 \caption{
-Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a skeleton segment (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
+Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
 The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
@@
 Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
-Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the skeletal graph is not stable against those.
+Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.
 

### 2019-08-23 6_validation.tex
lil rewording
'skeleton'/'graph' => 'ST'

--- 2019-08-22 6_validation.tex
@@
 The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
-The number of elements in the trapezoidation is linear in the number of elements in the VD
-and all of the stages of our framework are also linear in the number of elements in the skeleton,
+The number of elements in the ST is linear in the number of elements in the VD
+and all of the stages of our framework are also linear in the number of elements in the ST,
 so the total running time of our algorithm is $O(n \log n)$.
@@
 \begin{subfigure}{.04\columnwidth}\centering
-\vspace{4cm}
+\vspace{4.7cm}
 \includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
@@
 A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
-The wedge print can be read like a graph with model diameter on the X-axis and the resulting beads over the Y-axis.
 The naive and center deviation strategy show problems around certain model diameters.

### 2019-08-23 8_discussion.tex
'skeleton'/'graph' => 'ST'

@@
 Note also that our method is robust against small perturbations in the input shape.
-Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the ST graph.
-However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the unstability of the skeleton.
+Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the graph of the ST.
+However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
 Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
@@
 For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
-Moreover the skeleton marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked skeleton to be very small at that location, which results in tiny bead widths.
+Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
 

### 2019-08-23 4_method.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

@@
 We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
-The resulting skeleton consists of straight segments and parabolic segments which form a graph.
+The resulting skeleton consists of straight edges and parabolic edges which form a graph.
 See \cref{MAT_explanation_circles}.
@@
 The medial axis along with the feature radius values along the skeleton combine into a complete shape descriptor, called the medial axis transform (MAT).
-Feature radius and node locations of segments will be used below to analyse the shape locally.
+Feature radius and node locations will be used below to analyse the shape locally.
 
@@
 We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
-Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
+Each of the regions demarcated by the skeleton is further decomposed by adding radial edges from each node $v$ to its support $\text{sup}(v)$.
 The resulting skeleton decomposes the outline shape into trapezoids and triangles.
@@
 
-The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all segments of the VD falling outside of the outline shape and throwing away the bones connected to concave vertices in the outline shape.
+The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all edges of the VD falling outside of the outline shape and throwing away the edges connected to concave vertices in the outline shape.
 \cite{lee1982medial}
-However, the concave vertices are precisely in the support of the nodes to which those bones connect.
-This means we can efficiently compute the ST from the VD by removing all segments which lie outside the outline shape and add radial bones to the nodes from there.
+However, the concave vertices are precisely in the support of the nodes to which those edges connect.
+This means we can efficiently compute the ST from the VD by removing all edges which lie outside the outline shape and add radial edges to the nodes from there.
 See \cref{skeletonization_comparison}.
 
-We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
+We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
 See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
-That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
+That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
 This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
@@
 That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
-We also mark whole bones as being central if they are significant according to a significance measure which is commonly used in shape analysis.
+We also mark whole edges as being central if they are significant according to a significance measure which is commonly used in shape analysis.
 
@@
 Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on a bone of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
-Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
+The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
+Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
 
@@
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
-We mark all significant bones as such and contrary to related literature we keep the unmarked bones of the ST.
+We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
 Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.
@@
 See \cref{distance_based_angles}.
-This means we can prevent executing trigonometric functions on \emph{each} of the bones in the ST.
+This means we can prevent executing trigonometric functions on \emph{each} of the edges in the ST.
 Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
 
-This ratio can readily be applied to simple ST segments to determine whether they are significant.
-For segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
+This ratio can readily be applied to simple ST edges to determine whether they are significant.
+For VD edges generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
 For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
-and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
-This ensures that the discretization doesn't alter the extent and existence of marked central regions.
+and for VD edges with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
+This ensures that the discretization we perform when transforming the VD into the ST doesn't alter the extent and existence of marked central regions.
 See \cref{legend}.
@@
 See \cref{distance_ratio_limit}.
-The condition $|v - p| = \Delta R$ is true exactly for those sekeletal bones between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked bones, so we can perform the trapezoidation after marking.
+The condition $|v - p| = \Delta R$ is true exactly for those ST edges between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked edges, so we can perform the trapezoidation after marking.
 
@@
 \begin{proof}
-You will either go through the marked region of a discretized parabola or of a segment with two polygonal vertices as support.
+You will either go through the marked region of a discretized parabola or of an edge with two polygonal vertices as support.
 This means that the feature radius function in between marked regions is always monotonic.
@@
 %See VoronoiQuadrangulation::filterUnmarkedRegions
-Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
+Edges added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
 This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
@@
 \subsubsection{Marking filtering}
-Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
+Using the significance measure and the local maximum feature radius condition we initialize all marked edges and nodes.
 We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
 We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
-From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges;
-if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.
+From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
+if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
 
@@
 We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
-From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges until we hit another marked node $v_1$.
-If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all bones and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
+From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
+If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
 
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
-\caption{Radial support bones}\label{beading_transitioning_filtering__transitions_applied}
+\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
 \end{subfigure}
@@
 \subsubsection{Flattening}
-For bones which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
+For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
 We call these locations the \emph{transition anchor positions}.
@@
 We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
-%For each marked bone between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
+%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
 A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
@@
 A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
-We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked bones of the ST.
+We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
 From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
@@
 In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
-If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked bone(s).
+If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked edge(s).
 See \cref{beading_transitioning_filtering__transition_ends}.
-These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support bones for small perturbations and those which are not.
+These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
 
-Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support bones from these new nodes to the outline as per the trapezoidation requirement.
+Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support edges from these new nodes to the outline as per the trapezoidation requirement.
 We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
@@
 For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
-Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the bones where the adjusted height coincides with a slicing height.
+Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the edges where the adjusted height coincides with a slicing height.
 In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
@@
 See \cref{beading_interpolation}.
-The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra bones to appear in the ST inside of transition regions.
+The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.
 
@@
 The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
-However, beading conflicts can arise where a marked bone has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
+However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
 See \cref{beading_conflict_problem}.
@@
 See \cref{junction_placement}.
-We store all junctions of a segment in a mapping from edge to a list of junctions.
+We store all junctions of an edge in a mapping from edge to a list of junctions.
 
@@
 \subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
-\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support bones.
-No junctions will be generated along marked bones.
-Wide black lines are outline segments, marked nodes and bones in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
+\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support edges.
+No junctions will be generated along marked edges.
+Wide black lines are outline segments, marked nodes and edges in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
 }
@@
 
-We then generate bead segments for each trapezoid by connecting together the junctions of the same index.
+We then generate extrusion segments for each trapezoid by connecting together the junctions of the same index.
 See \cref{segment_generation}.
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
-If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center segment from both trapezoids.
+If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
 We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
@@
 By following the trapezoids along the domain (cyan) of a single outline polygon,
-the segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
+the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
 }

### 2019-08-23 5_generalization.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

@@
 We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
-Also we turn off the reduction of line segments near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
+Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
 
@@
 We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
-Additionally in order to emulate their definition of branches we mark all segments and in a separate algorithm we unmark the outer bones connected to the outline shape.
+Additionally in order to emulate their definition of branches we mark all ST edges and in a separate algorithm we unmark the outer edges connected to the outline shape.
 Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.

### 2019-08-23 8_discussion.tex
'bone' ==> 'edge' & 'segment' ==> 'edge' or 'extrusion segment'

@@
 See \cref{naive_overfill_underfill}
-Note also that contrary to some literature we don't remove bones from the skeleton, but leave it intact.
+Note also that contrary to some literature we don't remove edges from the skeleton, but leave it intact.
 The final skeleton is still an exact and full feature descriptor.
@@
 Note also that our method is robust against small perturbations in the input shape.
-Geometrically small changes to the outline shape introduce extra bones and therefore change the topology of the graph of the ST.
+Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
 However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
-Moreover, we have developed a method for dealing with bones within transition regions such that the toolpath is the same as if there wasn't any bone in that region.
-The toolpaths generated using our framework therefore remain the same when extra bones are added to the ST.
+Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there wasn't any edge in that region.
+The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
 
@@
 
-The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled segments in transitioning regions.
+The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
 The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.

### 2019-08-23 4_method.tex
clarify implementation of UoC

@@
 We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
-While the feature radii are measured along the support bones, the diameter is not measurable as such because the support bones are generally not collinear;
+While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
 we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
@@
 Note that although the overview of the method was described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+
+We compute the UoC by first generating the VD using the Boost \verb!C++! library, which implements the algorithm proposed by \citeauthor{fortune1986sascg}.\cite{fortune1986sascg}
+We transfer the internal parts of each Voronoi cell to our half-edge data-structure, discretize non-linear VD edges and add the support edges to form the ST.
+We then assign each node the bead count values using the simple formula described above.
 

### 2019-08-23 6_validation.tex
Zjenja: validation edits

@@
 \cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
-We found that the mean width of our strategies 'Inwards distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'.
+We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'.
 These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
+We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed'.
 
@@
 All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
-The 'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
+The Inward  'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
 While 

### 2019-08-23 6_validation.tex
Zjenja: discussion edits

@@
 
-From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $10^{-5} n \log n$ seconds.
+From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
 The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
@@
 These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
-We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed'.
+We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}.
+The outer beads of the 'Inward distributed' strategy clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.
 
@@
 All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
-The Inward  'Evenly distributed' strategy produces an order of magnitude more corners around 30 degrees.
-While 
- we found no significant differences in the smoothness of the toolpaths generated by the other strategies.
+The 'Inward distributed' strategy produces an order of magnitude less corners around 30 degrees, compared to 'Evenly distributed'. 
+We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
+\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around 90 degrees.
 
@@
 The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the prefered width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+We set the preferred width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
@@
 Because of inaccuracies in the depositioning control system some of the prints show defects.
-Such defects are less prevalant for the inward distributed beading strategy than the other strategies.
+Such defects are less prevalent for the inward distributed beading strategy than the other strategies.
 

### 2019-08-23 8_discussion.tex
Zjenja: discussion edits

@@
 \subsection{Comparison of beading strategies}
-The naive strategy and the single bead strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
+The 'Naive' strategy and the 'Outer bead' strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
 
@@
 
-The constant bead count beading strategy effectively deals with all overfills and underfills, but at the cost of wildly differing bead widths.
-See \cref{TEST_Constant_accuracy}.
-Note that around regions where the bead width changes a lot we can see some overfill areas, which explains the unusually high overfill statistic in \cref{over_underfill}.
-Because the bead count 
-For an input outline shape which contains both very small and very large features the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
+The 'Constant bead count' strategy effectively deals with underfills, but generates orders of magnitude more overfills compared to the other strategies. 
+Also, the strategy comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
+Note that most overfill areas occur near regions of alternating bead width.
+
+For an input outline shape which contains both very small and very large features, the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
@@
 If we look at \cref{TEST_Center_accuracy} we can see that
-the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width, which is still quite a bit.
-According to \cref{over_underfill} the overfill and underfill of the over- and underfill for the centered, the evenly distributed and the inward distributed strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.
+the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
+According to \cref{over_underfill} the overfill and underfill for the 'Centered', the 'Evenly distributed' and the 'Inward distributed' strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.
 
-However, according to \cref{widthHistogram} the centered strategy exhibits a lot wider range of bead widths than the distributed strategies:
-the standard deviation of the bead widths in the centered beading strategy is approximately \SI{38}{\micro\meter}, while the standard deviation resulting from the distributed strategies is approximately \SI{15}{\micro\meter}.
-We can therefore state that the distributed strategies result in bead widths closer to the nominal bead widths than the centered strategy, which means that the distributed strategies realize the mechanical properties associated to a given nominal bead width more closely.
+However, according to \cref{widthHistogram} the Centered strategy exhibits a lot wider range of bead widths than the Distributed strategies:
+the standard deviation of the bead widths in the Centered strategy is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed strategies is approximately \SI{14}{\micro\meter}.
+We can therefore state that the Distributed strategies result in bead widths closer to the nominal widths compared to the Centered strategy.
+This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-The inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
+The Inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
 The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
-Also when looking at \cref{smoothness} we cannot conclude any difference in the smoothness between the evenly distributed and the inward distributed beadign strategy.
-We do not provide any statistical evidence that the inward distributed beading strategy is in fact better than the evenly distributed strategy.
 
-However, we can say that by looking at \cref{distributed_comparison} we see that the outer toolpaths have the nominal bead width more often, which means that the inaccuracies of the adaptive bead width deposition system affect the dimensional accuracy of the outline shape less.
-The errors from such inaccuracies and the errors in mechanical properties due to deviation from the nominal bead width are located near the center of the shape, which means the overal mechanical properties of the part are least affected by the discrepancy between the actual feature size and the preferred feature size when using the inward distributed beading strategy.
+However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
+Also, we find that compared to Evenly distributed, the Inward distributed strategy produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
+Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a a low percentage.

### 2019-08-24 6_validation.tex
some more rewording to 'extrusion segment'

@@
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
+If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the extrusion segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
 We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
@@
 \caption{
-Extruded area of two extrusion toolpath segments.
+Extruded area of two extrusion extrusion segments.
 Red areas signify doubly extruded areas.
@@
 In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We measured the angle between consecutive segments generated by each strategy.
+We measured the angle between consecutive extrusion segments generated by each strategy.
 The relative frequency of these angles is shown in \cref{smoothness}.

### 2019-08-24 8_discussion.tex
move theoretical analysis to after comparison of strategies
limitations

@@
 \section{Discussion}
-
-\subsection{Theoretical analysis}
-In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
-The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
-See \cref{naive_overfill_underfill}
-Note also that contrary to some literature we don't remove edges from the skeleton, but leave it intact.
-The final skeleton is still an exact and full feature descriptor.
-In that sense our framework provides an exact solution space.
-
-Note also that our method is robust against small perturbations in the input shape.
-Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
-However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
-Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there wasn't any edge in that region.
-The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
-
-Our framework is also local.
-The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
-This means the toolpathing is stable against large perturbations of the input shape in far away regions
-and it also allows for some parallelism during the computation of the toolpaths.
 
@@
 Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a a low percentage.
+
+\subsection{Theoretical analysis}
+In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
+The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
+See \cref{naive_overfill_underfill}
+Note also that contrary to some literature we don't remove edges from the skeleton, but leave it intact.
+The final skeleton is still an exact and full feature descriptor.
+In that sense our framework provides an exact solution space.
+
+Note also that our method is robust against small perturbations in the input shape.
+Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
+However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
+Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there wasn't any edge in that region.
+The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
+
+Our framework is also local.
+The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
+This means the toolpathing is stable against large perturbations of the input shape in far away regions
+and it also allows for some parallelism during the computation of the toolpaths.
+
+\subsection{Limitations}
+In the beading strategies we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
+That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
+which might be difficult to accurately manufacture on some hardware.
+While ching the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
+Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
+Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
+but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
+Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
+
+Another limiting factor in the adoption of adaptive bead width is that Gcode -- a common file format for storing machine instructions -- doesn't support  moves with varying cross-sectional area.
+A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across the extrusion move.
+This could be mediated by discretizing a variable width extrusion segment into smaller segments, but that approach might still result in some small inaccuracies.
+Ideally the Gcode language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
+
+Taking a broader perspective, we note that our proposed inward distributed strategy is a pragmatic solution.
+Rather than deriving some optimal beading strategy from a clear specification of the objective, we propose some arbitrary inward distributed beading strategy and show that it is better than the other beading strategies.
+An optimal beading strategy can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
+This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading strategy.

### 2019-08-24 8_discussion.tex
lil typo

@@
 Also, we find that compared to Evenly distributed, the Inward distributed strategy produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
-Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a a low percentage.
+Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
 

### 2019-08-24 1_intro.tex
lil rewording
redo accuracy and width figures

@@
 \includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
 \caption{
 Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
-Red signifies overfill and blue underfill.
+Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
+The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
 }

### 2019-08-24 6_validation.tex
redo accuracy and width figures

@@
 Extrusion beads in gray tones,
-blue areas in the top images signify underfill regions,
-red areas overfill,
-orange areas triply extruded areas (double overfill).
-The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
-Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
+overfill in orange,
+underfill in azure,
+narrow beads in blue
+and wide beads in red.
 }

### 2019-08-24 sources/intro/convert_SVGs.sh

@@ -1,0 +1,6 @@
+for file in *.svg; do
+ filename=$(basename "$file")
+ fname="${filename%.*}"
+ echo $file;
+ inkscape -z -e $fname.png $file
+done

### 2019-08-24 0_main.tex
limitations
redo abstract

@@
       breaklines=true,                 % sets automatic line breaking
+      basicstyle=\ttfamily,
+      mathescape
     }
@@
 The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
-Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
+Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
 An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.
@@
 In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
-Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
-However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture.
+Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
+However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
 We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
 
-Our method determines the number of extrusion beads at each location, then it generates the beads from the center of the outline shape outward and finally connects all bead together to form extrusion toolpaths.
-We determine the middle of the shape by applying a significance measure to the skeleton of the outline polygon, use the beading strategy to determine the optimal number of beads in those middle regions and derive the toolpath locations as distances from the middle parts of the skeleton from the beading strategy.
-Because the skeletal structure decomposes the outline domain into simple cells, the toolpaths can be generated by drawing straight line segments along each cell.
+Based on a skeletonization of the 2D outline shape of a single layer we generate a 3D surface mesh, the union of cones.
+By slicing the surface at regular heights we obtain contour parallel toolpaths which cover the 2D area of a single layer.
+The heights of the 3D mesh are first altered:
+the heights at central ridges in the 3D surface are flattened to be parallel with the slicing planes in order to prevent over- and underfill
+and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.
 
@@
 We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
-We show that our implementation exhibits computation times in the same order of magnitude as the naive method.
+We show that our open source implementation exhibits computation times in the same order of magnitude as the naive method.
 \end{abstract}

### 2019-08-24 6_validation.tex
redo analysis figures
use SI instead of writing out

@@
 \centering
-\setlength{\figheight}{0.2\textwidth}
+\setlength{\figheight}{0.22\textwidth}
 \setlength{\figwidth}{0.31\textwidth}
@@
 %\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
-\caption{Computation time and target vertex count for the full dataset}
+\caption{Computation time}
 \label{computime}
@@
 %\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Relative frequency of extrusion widths}
+\caption{Extrusion widths}
 \label{widthHistogram}
@@
 %\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Relative frequency of extrusion widths for 6 outer contours}
+\caption{Extrusion width per index}
 \label{widthIndexedHistogram}
@@
 %\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
-\caption{Total over and underfill area}
+\caption{Over- and underfill}
 \label{over_underfill}
@@
 %\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
-\caption{Frequency of angles between consecutive segments}
+\caption{Junction angles}
 \label{smoothness}
@@
 %\includegraphics[width=\figwidth]{sources/validation/smoothnessNoTransition.pdf}
-\caption{Frequency of angles with and without transitions}
+\caption{Junction angles without smoothing}
 \label{smoothnessNoTransition}
@@
 The relative frequency of these angles is shown in \cref{smoothness}.
-All strategies show a higher number of corners for smaller angles with a peak towards 0 degrees (straight line).
-The 'Inward distributed' strategy produces an order of magnitude less corners around 30 degrees, compared to 'Evenly distributed'. 
+All strategies show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
+The 'Inward distributed' strategy produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
 We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
-\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around 90 degrees.
+\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.
 

### 2019-08-25 0_main.tex
Tim: Spell check

@@
 Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
-An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.
+An accurate dense filling is especially important for thin parts such as casings for electronics, blow molding prototypes, (architectural) models, and microstructures.
 

### 2019-08-25 1_intro.tex
Tim: Spell check

@@
 It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
-FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes blowmold parts, jigs and fixtures.
+FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
 Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
@@
 A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
-because the positiong and shape of the toolpath can be controled relatively accurately.
+because the position and shape of the toolpath can be controlled relatively accurately.
 Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
@@
 The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
-However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfll} areas.
+However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
 See \cref{intro_wedge}(top).

### 2019-08-25 4_method.tex
Tim: Spell check

@@
 \subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
-\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the inout shape polygons.
+\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the input shape polygons.
 }
@@
 A node in the ST can have at most two significant edges.
-For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore nonsignificant.
+For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore not significant.
 % However, because of some filtering operations this property does not neccesarily hold for the markings.
@@
 For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-In our generalized framewotk the function $b$ is determined by a beading strategy.
+In our generalized framework the function $b$ is determined by a beading strategy.
 
@@
 \end{align*}
-An example beading is visualzied in the top of \cref{beading_interpolation}:
+An example beading is visualized in the top of \cref{beading_interpolation}:
 $B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
@@
 the toolpath locations are visualized as dots,
-the widths are visualized as bidirection arrows
+the widths are visualized as bidirectional arrows
 and the middle is highlighted in red.
@@
 \caption{
-Applying beadings togenerate junctions along trapezoids.
+Applying beadings to generate junctions along trapezoids.
 \subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
@@
 Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
-Such intersections cause overextrusion because the nozzle passes the location multiple times.
-In order to reduce the amount of overextrusion of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
+Such intersections cause overfill because the nozzle passes the location multiple times.
+In order to reduce the amount of overfill of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
 We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.
@@
 \caption{
-Reducing polyline toolpaths away from intersections in order to prevent overextrusion.
-Toolpath locations in black, underextrusion in blue, overextrusion in red and orange and normal extrusion in grey.
-Intersections result in overextrusion, so we remove parts of the polylines at intersections.
+Reducing polyline toolpaths away from intersections in order to prevent overfill.
+Toolpath locations in black, underfill in azure and overfill in orange.
+Intersections result in overfill, so we remove parts of the toolpaths at intersections.
 }

### 2019-08-25 5_generalization.tex
Tim: Spell check

@@
 In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
-If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thsu their width becomes larger when going inward.
+If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thus their width becomes larger when going inward.
 In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
@@
 % and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanial properties derived for prints using the naive strategy will still hold approximately.
+Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the naive strategy will still hold approximately.
 

### 2019-08-25 6_validation.tex
Tim: Spell check

@@
 \section{Validation}
-In order to test our framework, we have assembled a dataset of different types of 3D models, ranging over various applications and various types of geometry.
-The dataset is described in detail in the accompanying data in Appendix~\ref{dataset}.
-We sliced all models in the dataset and selected 300 random slices from the total set of slices for analysis.
+In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
+The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
+We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
 We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
@@
 The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
-The computation time of each slice from the dataset was recorded for the "Inward distributed" and "Naive" strategy. 
+The computation time of each slice from the data set was recorded for the "Inward distributed" and "Naive" strategy. 
 \cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
@@
 
-We calculated the total overfill and underfill areas of the different toolpath strategies applied on the dataset. 
-The overfill and underfill areas as a percentage of the total area of the slices from the dataset are illustrated in \cref{over_underfill}.  
+We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
+The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
 The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the dataset.
+This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
 
@@
 \caption{
-Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the dataset.
+Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the data set.
 Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
@@
 The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
-Because of inaccuracies in the depositioning control system some of the prints show defects.
+Because of inaccuracies in the deposition control system some of the prints show defects.
 Such defects are less prevalent for the inward distributed beading strategy than the other strategies.
@@
 \caption{
-A wedge shape printed using the naive strategy, center deivation strategy and the inward distributed strategy.
+A wedge shape printed using the naive strategy, center deviation strategy and the inward distributed strategy.
 The naive and center deviation strategy show problems around certain model diameters.
@@
 \caption{
-Test shapes printed using the naive strategy, center deivation strategy and the inward distributed strategy.
+Test shapes printed using the naive strategy, center deviation strategy and the inward distributed strategy.
 The naive method produces distinct underfill areas.

### 2019-08-25 8_discussion.tex
Tim: Spell check

@@
 which might be difficult to accurately manufacture on some hardware.
-While ching the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
+While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
 Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).

### 2019-08-25 4_method.tex
redo reduction/retreating figure

@@
 \centering
-\setlength{\figwidth}{\columnwidth}
-\begin{subfigure}{0.45\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_unreduced.pdf}
+\setlength{\figwidth}{.35\columnwidth}
+\begin{subfigure}{0.45\columnwidth}\centering
+\includegraphics[width=\figwidth]{sources/method/polyline_reduction_before}
 \caption{No reduction}
 \end{subfigure}
-\begin{subfigure}{0.45\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_reduced.pdf}
+\begin{subfigure}{0.45\columnwidth}\centering
+\includegraphics[width=\figwidth]{sources/method/polyline_reduction_after}
 \caption{Reduction}
@@
 Toolpath locations in black, underfill in azure and overfill in orange.
-Intersections result in overfill, so we remove parts of the toolpaths at intersections.
 }

### 2019-08-25 4_method.tex
describe gready 3-way intersection connection approach and intricacies of algorithm

@@
 Such intersections cause overfill because the nozzle passes the location multiple times.
-In order to reduce the amount of overfill of a polyline ending in a junction $J$ we therefore remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}$ is some ration between $0$ and $1$.
-We do this for all polylines until only two outward toolpath segments remain, which constitute a single pass over the junction.
+We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
+In order to retreat a polyline ending in a junction $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
+This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.
 See \cref{polyline_reduction}.

### 2019-08-25 10_applications.tex
redo applications figure

@@
 \Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
-\Cref{application_closeups} highlights closeups of the generated toolpaths.
 Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\columnwidth]{sources/applications/combined_small_dilated_circled.pdf}
-\caption{
-Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
-A legend for the colors can be found in \cref{visualized_accuracy}.
-From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
-}
-\label{applications_overview}
-\end{figure}
-
 \begin{figure*}
 \centering
-\setlength{\figwidth}{0.1\textwidth}
-\setlength{\figheight}{0.1\textwidth}
+\setlength{\figwidth}{0.099\textwidth}
+\setlength{\figheight}{0.099\textwidth}
+\begin{subfigure}{\textwidth}\centering
+\includegraphics[width=\textwidth]{sources/applications/combined_small_dilated_circled.pdf}
+%\caption{Overview}\label{applications_overview}
+\end{subfigure}
 \begin{subfigure}{\figwidth}\centering
@@
 \caption{
-Closeups of results for the inward distributed beading strategy for various applications.
-The extrusion widths are visualized exaggeratedly and using a color scheme exaplained in \cref{visualized_accuracy}.
+Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
+A legend for the colors can be found in \cref{visualized_accuracy}.
+From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
 }
-\label{application_closeups}
+\label{applications_overview}
 \end{figure*}

### 2019-08-26 0_main.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

@@
 The heights of the 3D mesh are first altered:
-the heights at central ridges in the 3D surface are flattened to be parallel with the slicing planes in order to prevent over- and underfill
+the heights at central ridges in the 3D surface are quantized in order to prevent over- and underfill
 and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.

### 2019-08-26 4_method.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

@@
 \item Identify central regions of the UoC
-\item Flatten the central regions at heights equal to the nearest integer bead count
+\item Quantize the height of central ridges and peaks
 \item Smooth out sharp transitions between regions with different integer heights
@@
 \includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
-\caption{Flattened}\label{3d_surface_overview_rounded}
+\caption{Quantized}\label{3d_surface_overview_rounded}
 \end{subfigure}
@@
 we mark the central regions \subref{3d_surface_overview_center}
-and flatten those regions to heights of the nearest integer \subref{3d_surface_overview_rounded}.
+and quantize the height in those regions \subref{3d_surface_overview_rounded}.
 We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
@@
 explain how to identify central regions in \cref{sec_center_classification}.
-Flattening the central mesh regions and smoothing are handled in \cref{sec_central_height_adjustment}.
+Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
 We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
@@
 \subsection{Central height adjustment}\label{sec_central_height_adjustment}
-Now that we have identified and marked the central regions we flatten those regions to integer heights.
+Now that we have identified and marked the central regions we quantize their heights.
 More specifically we round the heights to integer bead count values.
+Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values coincides with a slicing height.
 When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
@@
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-In order to update the bead count values, we require a flattening operator which maps a feature diameter to a bead count: $f: \mathbb{R} \to \mathbb{N}$.
-For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $f(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-In our generalized framework the function $b$ is determined by a beading strategy.
+In order to update the bead count values, we require a quantization operator which maps a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
+For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
+In our generalized framework the function $q$ is determined by a beading strategy.
 
-We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow f(2R(v))$.
+We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
 We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
@@
 \includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
-\caption{Flattened bead counts}\label{beading_transitioning_filtering__bead_count}
+\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
 \end{subfigure}
@@
 
-\subsubsection{Flattening}
-For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the flattening operator $f(2R(v))$ jump to a different integer.
+\subsubsection{Quantization}
+For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
 We call these locations the \emph{transition anchor positions}.
@@
 
-We introduce the function $f^{-1}(n) := \argmax_d f(d) = n$, which gives the feature diameter at which $f$ jumps from $n$ to $n+1$ beads.
+We introduce the function $q^{-1}(n) := \argmax_d q(d) = n$, which gives the feature diameter at which $q$ jumps from $n$ to $n+1$ beads.
 %For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
-A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = f^{-1}(n)$.
+A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
 We can compute the location of the anchor simply as
-$$v_x = v_0 + (v_1 - v_0) \frac{ f^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
+$$v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
 for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.

### 2019-08-26 5_generalization.tex
'flatten' ==> 'quantize' & f(.) ==> q(.)

@@
 $$
-\left\{ \alpha_\text{max}, f(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
+\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
 $$
@@
 $\alpha_{\text{max}}$ (the limit bisector angle),
-$f(d)$ (flattening operator),
+$q(d)$ (quantization operator),
 $t(n)$ (transition length)
@@
 \begin{enumerate}
-\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ f^{-1}(n + 1) - f^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
+\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
 \item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
@@
 %We use a transition anchor position of
-%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
-%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
-%$$t_-(n) =  t(n) \frac{ f^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( f^{-1}(n) / w_\text{pref}  - n \right) \\
+%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
+%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
+%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
+t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
 t(n) &= w_\text{pref} \\
@@
 \alpha_\text{max} &= \SI{180}{\degree} \\
-f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
 W(n,d)_i &= w_\text{pref} \text{ for all } i 
@@
 t(n) &= 0 \\
-f(d) &=
+q(d) &=
 \begin{cases}
@@
 \alpha_\text{max} &= \SI{0}{\degree} \\
-f(d) &= C \\
+q(d) &= C \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
-We therefore base the beading strategy on the bead count $f^-(d)$ defined by the naive beading strategy.
+We therefore base the beading strategy on the bead count $q^-(d)$ defined by the naive beading strategy.
 \citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
@@
 t(n) &= \frac12 w_\text{pref} \\
-f^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
-f(d) &= f^-(d) +
+q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+q(d) &= q^-(d) +
 \begin{cases}
--1 & \text{ if } f^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
-1  & \text{ if }  f^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
+-1 & \text{ if } q^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
+1  & \text{ if }  q^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
 0 & \text{ otherwise}
@@
 \begin{align*}
-f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 \begin{align*}
-f(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
 E(n,d) &= d - n w_\text{pref} \\

### 2019-08-26 10_applications.tex
anonymization

@@
 \begin{subfigure}{\figwidth}\centering
+\censorbox{
 \includegraphics[height=\figheight]{sources/applications/tud_logo.png}
-\caption{TUD}\label{applications_tud}
+}
+\caption{\censor{TUD}}\label{applications_tud}
 \end{subfigure}
@@
 \includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
-\caption{UM}\label{applications_um}
+\caption{\censor{UM}}\label{applications_um}
 \end{subfigure}
@@
 A legend for the colors can be found in \cref{visualized_accuracy}.
-From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
+From left to right and top to bottom: a house, a case for electronics, a statue, two logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
 }

### 2019-08-26 6_validation.tex
anonymization

@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
+\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
+}
 \caption{Naive}\label{print_naive}
@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
+\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
+}
 \caption{Center deviation}\label{print_center}
@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
+\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
+}
 \caption{Inward distributed}\label{print_inward}

### 2019-08-26 1_intro.tex
title: system => framework

@@
 In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
-We therefore develop a parametric system which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
+We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
 See \cref{intro_wedge}(bottom).

### 2019-08-26 0_main.tex
anonymization
title: system => framework
naive method ==> uniform technique

@@
-\documentclass[5p,twocolumn,10pt,times]{elsarticle}
+\documentclass[preprint,5p,twocolumn,times]{elsarticle}
 \usepackage{amsmath}
@@
 	\makeatother
+
+	\usepackage{censor} % \censor
 
@@
 %\title{A robust framework for variable extrusion width concentric toolpath generation}
-\title{A parametric system for generating contour parallel toolpaths with adaptive extrusion width}
+\title{An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing}
 
 %\author{Paper ID: xxx}
+\author{Anonymized}
 
+\iffalse
 \author[um,tud]{Tim Kuipers}
@@
 \address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
+\fi
 
@@
 
-A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
-In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
+A simple technique for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a uniform width.
+In the center of the outline shapes this simple technique can result in underfill regions and overfill regions as wide as the nozzle size.
 Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
@@
 We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
-We show that our open source implementation exhibits computation times in the same order of magnitude as the naive method.
+We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.
 \end{abstract}
@@
 
- \temp{%Table of contents just for reviewing purposes
- \tableofcontents
- }
+ %\temp{%Table of contents just for reviewing purposes
+ %\tableofcontents
+ %}
 

### 2019-08-26 12_conclusions_future_work.tex
naive method ==> uniform technique

@@
 The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
-On the other hand it leaves most of the toolpaths the same as the naive method in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.
+On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.
 

### 2019-08-26 1_intro.tex
naive method ==> uniform technique

@@
 
-The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
+The simple technique for generating the shape filling toolpaths of a layer consists in performing uniform inward offsets with the radius of the the nozzle from the outline shape.
 However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
@@
 \caption{
-Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
+Toolpaths for a wedge shape using the uniform offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
 Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
@@
 \item Accurately filling a 2D outline with extrusion beads
-\item Reducing the overfill and underfill areas compared to the naive method
+\item Reducing the overfill and underfill areas compared to the uniform width technique
 \item Reducing the amount of beads with greatly deviating width compared to existing literature

### 2019-08-26 4_method.tex
lil fix of ref to non-existent fig
naive method ==> uniform technique

@@
 \subsection{Overview}
-The naive method consists of consecutive inward offsets from the outline using a constant bead width.
+The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
 These offsets can be generated from the medial axis transform (MAT).
@@
 The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
-We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}
+We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}
 
-For the naive method the overfill and underfill problems arise in the center,
+For the uniform offsetting technique the overfill and underfill problems arise in the center,
 because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
@@
 or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
-This last conceptualization is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
+This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
 The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
@@
 We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
-See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
+See the middle of \cref{shape_decomposition_st}.
 That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
@@
 \subsection{Center classification}\label{sec_center_classification}
-The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the ST.
+The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
 These central regions present themselves as upper ridges in the mountains of the UoC surface.
@@
 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w$.
 See \cref{naive_overfill_underfill}.
-The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
+The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
@@
 \caption{
-Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
+Overfill and underfill areas in a simple toolpathing using a uniform bead width $w$ for a wedge area with vertex angle $\beta$.
 The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).

### 2019-08-26 5_generalization.tex
naive method ==> uniform technique

@@
 
-\paragraph{Naive Beading Strategy}
-We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
+\paragraph{Uniform Beading Strategy}
+We can define a beading strategy which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
 \begin{align*}
@@
 \paragraph{Centered}
-We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
-We therefore base the beading strategy on the bead count $q^-(d)$ defined by the naive beading strategy.
-\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
+We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
+We therefore base the beading strategy on the bead count $q^-(d)$ defined by the uniform beading strategy.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
 Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
@@
 % and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the naive strategy will still hold approximately.
+Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform strategy will still hold approximately.
 

### 2019-08-26 6_validation.tex
naive method ==> uniform technique

@@
 We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
-The computation time of each slice from the data set was recorded for the "Inward distributed" and "Naive" strategy. 
+The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
+The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed strategy. 
 \cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
@@
 
-From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
-The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.
+From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
+The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.
 
@@
 \includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
-\caption{Naive}\label{TEST_naive_accuracy}
+\caption{Uniform}\label{TEST_naive_accuracy}
 \end{subfigure}
@@
 The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
-The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
+The inward distributed strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
+This is lower compared to the uniform strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
 
@@
 \caption{
-Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the data set.
+Results of computational analysis of the results from applying the uniform width technique and various beading strategies using our framework to the data set.
 Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
@@
 \caption{
-A wedge shape printed using the naive strategy, center deviation strategy and the inward distributed strategy.
-The naive and center deviation strategy show problems around certain model diameters.
+A wedge shape printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
+The uniform and center deviation strategy show problems around certain model diameters.
 }
@@
 }
-\caption{Naive}\label{print_naive}
+\caption{Uniform}\label{print_naive}
 \end{subfigure}
@@
 \caption{
-Test shapes printed using the naive strategy, center deviation strategy and the inward distributed strategy.
-The naive method produces distinct underfill areas.
+Test shapes printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
+The uniform technique produces distinct underfill areas.
 The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.

### 2019-08-26 8_discussion.tex
naive method ==> uniform technique

@@
 \subsection{Comparison of beading strategies}
-The 'Naive' strategy and the 'Outer bead' strategy are of little use to FDM printers, but they show the flexibility of our parametric system.
+The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
 
-We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the naive method causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
 These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.
@@
 the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
-According to \cref{over_underfill} the overfill and underfill for the 'Centered', the 'Evenly distributed' and the 'Inward distributed' strategy are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the naive method.
+According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
 
@@
 In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
-The significance measure is an exact measure of the relative size of gaps when using the naive toolpathing method.
+The significance measure is an exact measure of the relative size of gaps when using the uniform toolpathing method.
 See \cref{naive_overfill_underfill}

### 2019-08-26 0_main.tex
'beading strategy' ==> 'beading scheme'

@@
 However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
-We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
+We propose a framework which allows to define beading schemes which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
 
@@
 
-Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
-We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
+Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading schemes.
+We show that we can define a scheme which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
 We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.

### 2019-08-26 10_applications.tex
'beading strategy' ==> 'beading scheme'

@@
 
-\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
+\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading scheme.
 Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
@@
 \caption{
-Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
+Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
 A legend for the colors can be found in \cref{visualized_accuracy}.

### 2019-08-26 12_conclusions_future_work.tex
'beading strategy' ==> 'beading scheme'

@@
 In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
-Our framework is shown to be flexible, since we have shown several beading strategies which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
+Our framework is shown to be flexible, since we have shown several beading schemes which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
 Our framework is robust and local, meaning that small changes in the toolpath are caused by small local changes in the outline shape.
 
-We have introduced the inward distributed beading strategy which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
+We have introduced the inward distributed beading scheme which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
 and instead distributes the deviation in bead width over several beads near the center of the shape.
@@
 
-The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
+The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
 On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.
@@
 Future research might be devoted to optimizing the distribution scheme to a specific hardware setup.
-If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading strategy.
+If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.
 

### 2019-08-26 4_method.tex
'beading strategy' ==> 'beading scheme'

@@
 and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
-In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.
+In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.
 
@@
 The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
-Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.
+Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading scheme.
 
@@
 For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-In our generalized framework the function $q$ is determined by a beading strategy.
+In our generalized framework the function $q$ is determined by a beading scheme.
 
@@
 A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
-We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
+We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
 From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
@@
 the periphery, and slice the resulting mesh into isocontour toolpaths.
-The peripheral heights could be determined in a plethora of ways according to various beading strategies.
+The peripheral heights could be determined in a plethora of ways according to various beading schemes.
 The ramps from the outline shape to the center might have various curves,
@@
 
-After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
+After each marked node is assigned a beading by the beading scheme, we propagate the beadings outward to all nodes in the ST.
 The beading propagation is performed in two stages: an upward and downward stage.

### 2019-08-26 5_generalization.tex
'beading strategy' ==> 'beading scheme'

@@
 The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
-Depending on the application, the hardware and the materials used we might need different strategies for determining the bead widths.
+Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
 In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
-There are several strategies one can take for determining the distribution of bead widths.
-We will formalize several strategies and describe the set of parameters these strategies require.
+There are several schemes one can take for determining the distribution of bead widths.
+We will formalize several schemes and describe the set of parameters these schemes require.
 
-\begin{definition}\label{beading_strategy_definition}
-We define a beading strategy as the following set:
+\begin{definition}\label{beading_scheme_definition}
+We define a beading scheme as the following set:
 $$
@@
 
-\subsection{Beading strategies}
-We introduce several beading strategies which determine the bead count and their widths in various ways.
-We can emulate a variety of toolpath generation methods from related literature by defining new beading strategies.
-We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.
+\subsection{Beading schemes}
+We introduce several beading schemes which determine the bead count and their widths in various ways.
+We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
+We also introduce new beading schemes which produce toolpaths with less extremal widths compared to techniques from existing literature.
 
-A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
-Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
-Most of the beading strategies we introduce share a common ground:
+A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
+Our beading schemes are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
+Most of the beading schemes we introduce share a common ground:
 \begin{align*}
@@
 
-\paragraph{Uniform Beading Strategy}
-We can define a beading strategy which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
+\paragraph{Uniform Beading scheme}
+We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
 \begin{align*}
@@
 \paragraph{Outer bead}
-We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
+We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
 Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
@@
 We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
-We therefore base the beading strategy on the bead count $q^-(d)$ defined by the uniform beading strategy.
+We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
 \citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
@@
 \paragraph{Evenly distributed}
-By taking the advantages of the above two strategies we can define a beading strategy which constitutes a novel toolpathing technique.
+By taking the advantages of the above two schemes we can define a beading scheme which constitutes a novel toolpathing technique.
 We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
@@
 
-\paragraph{General distributed strategy}
-The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
+\paragraph{General distributed scheme}
+The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
 $w_\text{pref} + E / n$.
 However, depending on the application we might want a different distribution of widths.
-We therefore supply a beading strategy which supports an arbitrary distribution of the discrepancy.
+We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
 The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
@@
 See \cref{distributed_comparison}.
-That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
+That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
 % and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform strategy will still hold approximately.
+Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
 
@@
 \caption{
-Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
+Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
 Colors represent bead widths.
@@
 \paragraph{Widening}
-Complementary to any of these strategies we can enforce a minimum feature size at no extra cost in our framework.
+Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
 Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.

### 2019-08-26 6_validation.tex
'beading strategy' ==> 'beading scheme'

@@
 We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely 'Constant bead count' scheme with a bead count of $C=4$, the 'Centered' beading scheme, the 'Evenly distributed', and the 'Inward distributed' beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
-The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed strategy. 
+The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
 \cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
@@
 These triple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualized for the different toolpath strategies in the top of \cref{visualized_accuracy}.
+The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.
 
@@
 \caption{
-Visualizing the overfills and underfills and the widths for various beading strategies.
+Visualizing the overfills and underfills and the widths for various beading schemes.
 Extrusion beads in gray tones,
@@
 
-We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
+We calculated the total overfill and underfill areas of the different toolpath schemes applied on the data set. 
 The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
-The inward distributed strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the uniform strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
+The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
+This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
 
@@
 \caption{
-Results of computational analysis of the results from applying the uniform width technique and various beading strategies using our framework to the data set.
+Results of computational analysis of the results from applying the uniform width technique and various beading schemes using our framework to the data set.
 Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
@@
 Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
-We visualize the bead widths resulting from the different strategies in the bottom of \cref{visualized_accuracy}.
+We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
 
@@
 at intervals of \SI{1}{\micro\meter} along the toolpath.
-From these sampled values, we calculated the mean bead width, and standard deviation per strategy.
-\cref{widthHistogram} shows the distribution of extrusion width for each strategy binned at intervals of \SI{10}{\micro\meter}.
-We found that the mean width of our strategies 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for strategies 'Centered' and 'Constant bead count'.
-These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' strategies deviate less and infrequently from the nominal nozzle size compared to the other strategies.
-We compared the width uniformity of the 6 outer beads for the strategies 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}.
-The outer beads of the 'Inward distributed' strategy clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.
+From these sampled values, we calculated the mean bead width, and standard deviation per scheme.
+\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
+We found that the mean width of our schemes 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for schemes 'Centered' and 'Constant bead count'.
+These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' schemes deviate less and infrequently from the nominal nozzle size compared to the other schemes.
+We compared the width uniformity of the 6 outer beads for the schemes 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}.
+The outer beads of the 'Inward distributed' scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.
 
@@
 In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We measured the angle between consecutive extrusion segments generated by each strategy.
+We measured the angle between consecutive extrusion segments generated by each scheme.
 The relative frequency of these angles is shown in \cref{smoothness}.
-All strategies show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
-The 'Inward distributed' strategy produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
+All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
+The 'Inward distributed' scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
 We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
@@
 Because of inaccuracies in the deposition control system some of the prints show defects.
-Such defects are less prevalent for the inward distributed beading strategy than the other strategies.
+Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
 
@@
 \caption{
-A wedge shape printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
-The uniform and center deviation strategy show problems around certain model diameters.
+A wedge shape printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
+The uniform and center deviation scheme show problems around certain model diameters.
 }
@@
 \caption{
-Test shapes printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
+Test shapes printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
 The uniform technique produces distinct underfill areas.
-The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
-The inward distributed strategy produces the least defects.
+The center deviation scheme shows some defects due to inaccurate control of extremal deposition widths.
+The inward distributed scheme produces the least defects.
 }

### 2019-08-26 8_discussion.tex
'beading strategy' ==> 'beading scheme'

@@
 
-\subsection{Comparison of beading strategies}
+\subsection{Comparison of beading schemess}
 The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
@@
 
-%The single bead strategy solves the underfill problem in regions where the model is more thin than the nozzle size.
-%However, the strategy doesn't deal with the remaining area.
+%The single bead scheme solves the underfill problem in regions where the model is more thin than the nozzle size.
+%However, the scheme doesn't deal with the remaining area.
 %In our visualization we print the outline of the remaining area which exposes an overextrusion problem.
 
-The 'Constant bead count' strategy effectively deals with underfills, but generates orders of magnitude more overfills compared to the other strategies. 
-Also, the strategy comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
+The 'Constant bead count' scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemess. 
+Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
 Note that most overfill areas occur near regions of alternating bead width.
@@
 If we look at \cref{TEST_Center_accuracy} we can see that
-the centered beading strategy effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
+the centered beading scheme effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
 
-However, according to \cref{widthHistogram} the Centered strategy exhibits a lot wider range of bead widths than the Distributed strategies:
-the standard deviation of the bead widths in the Centered strategy is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed strategies is approximately \SI{14}{\micro\meter}.
-We can therefore state that the Distributed strategies result in bead widths closer to the nominal widths compared to the Centered strategy.
+However, according to \cref{widthHistogram} the Centered scheme exhibits a lot wider range of bead widths than the Distributed schemess:
+the standard deviation of the bead widths in the Centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed schemess is approximately \SI{14}{\micro\meter}.
+We can therefore state that the Distributed schemess result in bead widths closer to the nominal widths compared to the Centered scheme.
 This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-The Inward distributed beading strategy was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
+The Inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
 The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
@@
 However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
-Also, we find that compared to Evenly distributed, the Inward distributed strategy produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
-Therefore, when using the Inward distributed strategy the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
+Also, we find that compared to Evenly distributed, the Inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
+Therefore, when using the Inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
 
@@
 \subsection{Limitations}
-In the beading strategies we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
+In the beading schemess we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
 That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
@@
 While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
-Our strategies require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
+Our schemess require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
 Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
@@
 
-Taking a broader perspective, we note that our proposed inward distributed strategy is a pragmatic solution.
-Rather than deriving some optimal beading strategy from a clear specification of the objective, we propose some arbitrary inward distributed beading strategy and show that it is better than the other beading strategies.
-An optimal beading strategy can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
-This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading strategy.
+Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
+Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemess.
+An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
+This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.

### 2019-08-26 5_generalization.tex
fix issues with beading scheme naming and referencing

@@
 
-\paragraph{Uniform Beading scheme}
+\paragraph{Uniform beading scheme}
 We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.

### 2019-08-26 6_validation.tex
fix issues with beading scheme naming and referencing

@@
 We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely 'Constant bead count' scheme with a bead count of $C=4$, the 'Centered' beading scheme, the 'Evenly distributed', and the 'Inward distributed' beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
 
@@
 \includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
-\caption{Center}\label{TEST_Center_accuracy}
+\caption{Centered}\label{TEST_Center_accuracy}
 \end{subfigure}
@@
 \cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
-We found that the mean width of our schemes 'Inward distributed' and 'Evenly distributed' is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for schemes 'Centered' and 'Constant bead count'.
-These results indicate that, while causing less overfill and underfill, 'Inwards distributed' and 'Evenly distributed' schemes deviate less and infrequently from the nominal nozzle size compared to the other schemes.
-We compared the width uniformity of the 6 outer beads for the schemes 'Inward distributed' and 'Evenly distributed', the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}.
-The outer beads of the 'Inward distributed' scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the 'Evenly distributed' more often extrudes widths that deviate from the nominal width.
+We found that the mean width of the inward distributed and evenly distributed schemes is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
+These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less and infrequently from the nominal bead width compared to the other schemes.
+We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
+The outer beads of the inward distributed scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the evenly distributed scheme more often extrudes widths that deviate from the nominal width.
 
@@
 All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
-The 'Inward distributed' scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to 'Evenly distributed'. 
+The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
 We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
@@
 \caption{
-A wedge shape printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
-The uniform and center deviation scheme show problems around certain model diameters.
+A wedge shape printed using the uniform scheme, centered scheme and the inward distributed scheme.
+The uniform and centered scheme show problems around certain model diameters.
 }
@@
 }
-\caption{Center deviation}\label{print_center}
+\caption{Centered}\label{print_center}
 \end{subfigure}
@@
 \caption{
-Test shapes printed using the uniform scheme, center deviation scheme and the inward distributed scheme.
+Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
 The uniform technique produces distinct underfill areas.
-The center deviation scheme shows some defects due to inaccurate control of extremal deposition widths.
+The centered scheme shows some defects due to inaccurate control of extremal deposition widths.
 The inward distributed scheme produces the least defects.

### 2019-08-26 8_discussion.tex
fix issues with beading scheme naming and referencing

@@
 
-\subsection{Comparison of beading schemess}
+\subsection{Comparison of beading schemes}
 The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
@@
 
-The 'Constant bead count' scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemess. 
+The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
 Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
@@
 
-However, according to \cref{widthHistogram} the Centered scheme exhibits a lot wider range of bead widths than the Distributed schemess:
-the standard deviation of the bead widths in the Centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the Distributed schemess is approximately \SI{14}{\micro\meter}.
-We can therefore state that the Distributed schemess result in bead widths closer to the nominal widths compared to the Centered scheme.
+However, according to \cref{widthHistogram} the centered scheme exhibits a lot wider range of bead widths than the distributed schemes:
+the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the distributed schemes is approximately \SI{14}{\micro\meter}.
+We can therefore state that the distributed schemes result in bead widths closer to the nominal widths compared to the centered scheme.
 This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-The Inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
+The inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
 The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
@@
 However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
-Also, we find that compared to Evenly distributed, the Inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
+Also, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
 Therefore, when using the Inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
@@
 See \cref{naive_overfill_underfill}
-Note also that contrary to some literature we don't remove edges from the skeleton, but leave it intact.
+Note also that contrary to some literature we do not remove edges from the skeleton, but leave it intact.
 The final skeleton is still an exact and full feature descriptor.
@@
 However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
-Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there wasn't any edge in that region.
+Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there was no such edge in that region.
 The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
@@
 \subsection{Limitations}
-In the beading schemess we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
+In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
 That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
@@
 While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
-Our schemess require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
+Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
 Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
@@
 
-Another limiting factor in the adoption of adaptive bead width is that Gcode -- a common file format for storing machine instructions -- doesn't support  moves with varying cross-sectional area.
+Another limiting factor in the adoption of adaptive bead width is that Gcode -- a common file format for storing machine instructions -- does not support  moves with varying cross-sectional area.
 A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across the extrusion move.
@@
 Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
-Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemess.
+Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemes.
 An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.

### 2019-08-26 6_validation.tex
Revert "anonymization"
This reverts commit 8b839903672f8b3c90553ee94129250609c4d0ec.

@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
-\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
-}
 \caption{Uniform}\label{print_naive}
@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
-\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
-}
 \caption{Centered}\label{print_center}
@@
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
-\censorbox{
 \includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
-}
 \caption{Inward distributed}\label{print_inward}

### 2019-08-26 4_method.tex
new overview figure

@@
 \subsection{Overview}
-The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
-These offsets can be generated from the medial axis transform (MAT).
-The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape.
+
+Given an arbitrarily shaped polygon which represents the intersection of a plane and a 3D shape, our method generates a toolpath with varying width, i.e.
+a set of (mostly) connected line segments, with each node being assigned a width.
+The width along a line segment is linearly interpolated from the widths of its two nodes.
+
+Our method starts with computing the skeleton of the input polygon by medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpath~\cite{eiamsa2003toward}.
+We make use of the union of cones~\cite{blum1967transformation} to visualize the skeleton, by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig.
+2?).
+With the aid of this visualization, contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig.
+2?).
+
+As depicted in Fig.
+2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon.
+The heights at these elements (the distance of the corresponding projected point to the polygon boundary) are then quantized in terms of the number of beads.
+To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights.
+The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width.
+\jun{Do we use regular intervals, but get varying width?}
+
+We note that the union of cones (or UoC) is introduced only for visualization. We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
+explain how to identify central regions in \cref{sec_center_classification}.
+Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
+We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
+and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
+
+This section explains how we can generate toolpaths with evenly distributed bead widths.
+In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.
+
+% The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
+% These offsets can be generated from the medial axis transform (MAT).
+% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape.
 \cite{blum1967transformation}
-The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
-We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}
+% The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
+% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}
 
-For the uniform offsetting technique the overfill and underfill problems arise in the center,
-because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
-Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
+% For the uniform offsetting technique the overfill and underfill problems arise in the center,
+% because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
+% Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
 
-Our framework can be thought of as following these steps:
-\begin{itemize}
-\item Compute the skeleton of the input shape
-\item Assign each node a height in terms of bead count based on the local feature size
-\item Identify central regions of the UoC
-\item Quantize the height of central ridges and peaks
-\item Smooth out sharp transitions between regions with different integer heights
-\item Determine the heights in the periphery (non-central regions)
-\item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
-\end{itemize}
-See \cref{3d_surface_overview}.
+% Our framework can be thought of as following these steps:
+% \begin{itemize}
+% \item Compute the skeleton of the input shape
+% \item Assign each node a height in terms of bead count based on the local feature size
+% \item Identify central regions of the UoC
+% \item Quantize the height of central ridges and peaks
+% \item Smooth out sharp transitions between regions with different integer heights
+% \item Determine the heights in the periphery (non-central regions)
+% \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
+% \end{itemize}
+% See \cref{3d_surface_overview}.
 
@@
 \centering
-\setlength{\figwidth}{.18\textwidth}
+\setlength{\figheight}{.15\textwidth}
+\setlength{\figwidth}{.15\textwidth}
+\setlength{\figwidthTwo}{.22\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
+\caption{Layer outline}\label{}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
+\caption{Skeleton}\label{}
+\end{subfigure}
+\begin{subfigure}{\figwidthTwo}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
+\caption{Union of Cones}\label{}
+\end{subfigure}
+\begin{subfigure}{\figwidthTwo}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
+\caption{Slicing}\label{}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
+\caption{Uniform paths}\label{}
+\end{subfigure}
+
+\setlength{\figwidth}{.22\textwidth}
 \setlength{\figwidthTwo}{.17\textwidth}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}
 
@@
 
-\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
-\caption{Union of Cones}\label{3d_surface_overview_uoc}
+\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
+\caption{Center identification}\label{3d_surface_overview_center}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}
 
@@
 
-\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
-\caption{Center}\label{3d_surface_overview_center}
+\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
+\caption{Quantization}\label{3d_surface_overview_rounded}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}
 
@@
 
-\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
-\caption{Quantized}\label{3d_surface_overview_rounded}
+\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
+\caption{Smoothing}\label{3d_surface_overview_smoothed}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}
 
@@
 
-\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
-\caption{Smoothed}\label{3d_surface_overview_smoothed}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}
-
-\vspace{\tempheight}
-
-\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
-\caption{Sliced}\label{3d_surface_overview_sliced}
+\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
+\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
 \end{subfigure}
@@
 
-This section explains how we can generate toolpaths with evenly distributed bead widths.
-We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
-explain how to identify central regions in \cref{sec_center_classification}.
-Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
-We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
-and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
-In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.
-
-For ease of reference we have included a legend explaining the vocabulary employed in this manuscript in \cref{legend}.
+For ease of reference we have included a legend explaining \jun{this figure itself does not sufficiently "explain".
+How about indicating, highlighting etc?} the terms employed in this manuscript in \cref{legend}.
+These terms will be further explained as they first appear later in the paper.
 
@@
 \subsection{Surface generation}\label{sec_surface_construction}
+\jun{I would like to change the title, don't have a better word.}
+
 The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
@@
 \subsubsection{Medial axis transform}
-One of the most commonly used skeletonizations of a shape is the medial axis.
-The medial axis is defined by the locations where the inscribed circle meets the boundary in at least two locations. \cite{blum1967transformation}
-We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}: $\text{sup}(v) = \argmin_{x\in P} |x - v|$.
+The medial axis is a compact and intrinsic representation of shapes.
+It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation}.
+We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}:
+\begin{equation}
+    \text{sup}(v) = \argmin_{x\in P} |x - v|.
+\end{equation}
 The resulting skeleton consists of straight edges and parabolic edges which form a graph.
 See \cref{MAT_explanation_circles}.
-We therefore represent the skeleton in a standard half-edge data-structure.
-See \cref{shape_decomposition_datastructure}.
+%We therefore represent the skeleton in a standard half-edge data-structure.
+%See \cref{shape_decomposition_datastructure}.
 
-Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
-or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
-This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
-The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
-See \cref{MAT_explanation}.
+%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
+%This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
+%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
+%See \cref{MAT_explanation}.
 
@@
 
-\begin{figure}
-\centering
-\begin{subfigure}{0.3\columnwidth}
-\centering
-\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
-\caption{Circles}
-\label{MAT_explanation_circles}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
-\centering
-\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
-\caption{Wave-fronts}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth}
-\centering
-\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
-\caption{Union of Cones}
-\end{subfigure}
-\caption{
-Medial axis representations.
-The medial axis can be defined in terms of the the number of support points of the inscribed circles,
-as the pinch sites in wave-fronts
-or as ridges in a volume defined by the union of cones.
-}
-\label{MAT_explanation}
-\end{figure}
+% \begin{figure}
+% \centering
+% \begin{subfigure}{0.3\columnwidth}
+% \centering
+% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
+% \caption{Circles}
+% \label{MAT_explanation_circles}
+% \end{subfigure}
+% \begin{subfigure}{0.3\columnwidth}
+% \centering
+% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
+% \caption{Wave-fronts}
+% \end{subfigure}
+% \begin{subfigure}{0.3\columnwidth}
+% \centering
+% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
+% \caption{Union of Cones}
+% \end{subfigure}
+% \caption{
+% Medial axis representations.
+% The medial axis can be defined in terms of the the number of support points of the inscribed circles,
+% as the pinch sites in wave-fronts
+% or as ridges in a volume defined by the union of cones.
+% }
+% \label{MAT_explanation}
+% \end{figure}
 

### 2019-08-26 4_method.tex
Juns new overview section

@@
 \centering
-\setlength{\figheight}{.15\textwidth}
-\setlength{\figwidth}{.15\textwidth}
-\setlength{\figwidthTwo}{.22\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
-\caption{Layer outline}\label{}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
-\caption{Skeleton}\label{}
-\end{subfigure}
-\begin{subfigure}{\figwidthTwo}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
-\caption{Union of Cones}\label{}
-\end{subfigure}
-\begin{subfigure}{\figwidthTwo}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
-\caption{Slicing}\label{}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
-\caption{Uniform paths}\label{}
-\end{subfigure}
-
-\setlength{\figwidth}{.22\textwidth}
+\setlength{\figwidth}{.18\textwidth}
 \setlength{\figwidthTwo}{.17\textwidth}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}
+\includegraphics[width=\figwidthTree]{sources/method/surface/union_of_cones_cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
-\caption{Center identification}\label{3d_surface_overview_center}
+\includegraphics[width=\figwidthTwo]{sources/method/surface/uoc.pdf}
+\caption{Union of Cones}\label{3d_surface_overview_uoc}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}
+\includegraphics[width=\figwidthTree]{sources/method/surface/marking_cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
-\caption{Quantization}\label{3d_surface_overview_rounded}
+\includegraphics[width=\figwidthTwo]{sources/method/surface/marked.pdf}
+\caption{Center}\label{3d_surface_overview_center}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}
+\includegraphics[width=\figwidthTree]{sources/method/surface/rounded_cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
-\caption{Smoothing}\label{3d_surface_overview_smoothed}
+\includegraphics[width=\figwidthTwo]{sources/method/surface/rounded.pdf}
+\caption{Quantized}\label{3d_surface_overview_rounded}
 \end{subfigure}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}
+\includegraphics[width=\figwidthTree]{sources/method/surface/smoothed_cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
-\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
+\includegraphics[width=\figwidthTwo]{sources/method/surface/smoothed.pdf}
+\caption{Smoothed}\label{3d_surface_overview_smoothed}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\hspace*{\tempheightTwo}
+\includegraphics[width=\figwidthTree]{sources/method/surface/sliced_cropped.png}
+
+\vspace{\tempheight}
+
+\includegraphics[width=\figwidthTwo]{sources/method/surface/sliced_2D.png}
+\caption{Sliced}\label{3d_surface_overview_sliced}
 \end{subfigure}

### 2019-08-27 0_main.tex
Revert "anonymization"
This reverts commit 8b839903672f8b3c90553ee94129250609c4d0ec.
sections 3.1 - 3.3

@@
-\documentclass[preprint,5p,twocolumn,times]{elsarticle}
+\documentclass[5p,twocolumn,10pt,times]{elsarticle}
 \usepackage{amsmath}
-\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
+\usepackage[draft]{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
 %\modulolinenumbers[5]
@@
 	\makeatother
-
-	\usepackage{censor} % \censor
 
@@
 %\author{Paper ID: xxx}
-\author{Anonymized}
 
-\iffalse
 \author[um,tud]{Tim Kuipers}
@@
 \address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
-\fi
 
@@
 \begin{keyword} % SPM
-keyword
+Toolpath, 3D printing, adaptive width, underfill
 \end{keyword}
@@
 
- %\temp{%Table of contents just for reviewing purposes
- %\tableofcontents
- %}
+ \temp{%Table of contents just for reviewing purposes
+ \tableofcontents
+ }
 

### 2019-08-27 4_method.tex
sections 3.1 - 3.3

--- 2019-08-26 4_method.tex
@@
 Our method starts with computing the skeleton of the input polygon by medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpath~\cite{eiamsa2003toward}.
-We make use of the union of cones~\cite{blum1967transformation} to visualize the skeleton, by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig.
+We make use of the union of cones to visualize the skeleton (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig.
 2?).
-With the aid of this visualization, contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig.
-2?).
+Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig. 2?).
 
 As depicted in Fig.
-2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon.
-The heights at these elements (the distance of the corresponding projected point to the polygon boundary) are then quantized in terms of the number of beads.
-To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights.
-The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width.
+2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon (\cref{sec_center_classification}).
+The heights at these elements are then quantized in terms of beads.
+To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights (\cref{sec_central_height_adjustment}).
+The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width (\cref{sec_toolpath_extraction}).
 \jun{Do we use regular intervals, but get varying width?}
 
-We note that the union of cones (or UoC) is introduced only for visualization. We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
-explain how to identify central regions in \cref{sec_center_classification}.
-Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
-We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
-and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
+% We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
+% explain how to identify central regions in \cref{sec_center_classification}.
+% Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
+% We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
+% and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
 
@@
 \includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
-\caption{Union of Cones}\label{}
+\caption{Union of cones}\label{}
 \end{subfigure}
@@
 \caption{
-A geometrical conceptualization of our technique.
-3D visualization on top and the corresponding 2D visualization on bottom.
-In the UoC \subref{3d_surface_overview_uoc}
-we mark the central regions \subref{3d_surface_overview_center}
-and quantize the height in those regions \subref{3d_surface_overview_rounded}.
-We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
-and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
-Blue signifies regions marked as being central.
-The numbers are the integer multiples of half the nozzle width.
+The first row illustrates the generation of uniform paths (e) by interpreting the path as the intersection of horizontal planes and the union of cones (c) which is an alternative visualization of the skeleton (b).
+The second row depicts the major steps with both 2D and 3D visualizations for generating paths with adaptive width (i).
+Central elements in the skeleton are first identified (blue in f).
+The heights are then quantized in terms of beads (g, the integer values), and smoothed (h).
+% A geometrical conceptualization of our technique.
+% 3D visualization on top and the corresponding 2D visualization on bottom.
+% In the UoC \subref{3d_surface_overview_uoc}
+% we mark the central regions \subref{3d_surface_overview_center}
+% and quantize the height in those regions \subref{3d_surface_overview_rounded}.
+% We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
+% and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
+% Blue signifies regions marked as being central.
+% The numbers are the integer multiples of half the nozzle width.
 }
@@
 \includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
-\caption{Explanation of terms and common color coding.}
+\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
 \label{legend}
@@
 
-\subsection{Surface generation}\label{sec_surface_construction}
-\jun{I would like to change the title, don't have a better word.}
+%\subsection{Surface generation}\label{sec_surface_construction}
+\subsection{Union of cones}\label{sec_surface_construction}
 
-The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
-By assigning each node in the skeleton a height equal to the radial distance to the outline we obtain the shape of the UoC.
-Starting from the medial axis we further decompose the shape into simple fragments, so that the mesh contains only quads and triangles.
+The union of cones (UoC) is derived from a common skeletonization of the polygonal outline shape: the medial axis.
+By assigning each node in the skeleton a height equal to its shortest distance to the outline we obtain the shape of the UoC.
+Starting from the medial axis we further decompose the shape into simple fragments, so that the domain contains only quads and triangles.
+This decomposition allows to approximate the surface of the UoC as a 3D piecewise linear mesh.
 
-\subsubsection{Medial axis transform}
+%\subsubsection{Medial axis transform}
+\paragraph{Medial axis transform}
 The medial axis is a compact and intrinsic representation of shapes.
-It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation}.
+It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
+The resulting skeleton consists of straight edges and parabolic edges.
+An example is illustrated in \cref{shape_decomposition_mat}.
 We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}:
@@
 \end{equation}
-The resulting skeleton consists of straight edges and parabolic edges which form a graph.
-See \cref{MAT_explanation_circles}.
+Consequently the shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
+%See \cref{MAT_explanation_circles}.
 %We therefore represent the skeleton in a standard half-edge data-structure.
 %See \cref{shape_decomposition_datastructure}.
-
 %Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
@@
 %See \cref{MAT_explanation}.
+%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
+%``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
+The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
+%Feature radius and node locations will be used below to analyse the shape locally.
 
-%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
-``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
-The medial axis along with the feature radius values along the skeleton combine into a complete shape descriptor, called the medial axis transform (MAT).
-Feature radius and node locations will be used below to analyse the shape locally.
+By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a right cone is formed by the inscribed circle as the base and the raised center as the apex.
+The union of cones forms a 3D solid volume. 
+The medial axis can thus also be interpreted as the ridges of the volume defined by the union of cones.
 
@@
 
-\subsubsection{Skeletal trapezoidation}
-The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
-We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
-Each of the regions demarcated by the skeleton is further decomposed by adding radial edges from each node $v$ to its support $\text{sup}(v)$.
+%\subsubsection{Skeletal trapezoidation}
+\paragraph{Skeletal trapezoidation}
+To construct the union of cones, starting from the medial axis we decompose the input polygon into a set of quads and triangles.
+\jun{Tim, what is our initial purpose of skeletal trapezoidation, the purpose before we concept the approach by union of cones?}
+We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
+The basic idea is to add edges connecting each node $v$ on the medial axis to (all of) its supports, $\text{sup}(v)$. 
 The resulting skeleton decomposes the outline shape into trapezoids and triangles.
-We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
-\footnote{The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984}}
+Considering the fact that the concept of trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle~\cite{chazelle1984,fournier1984}, we call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
 
-The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
-Each polygon in the input shape acquires it's own domain.
-The domains of hole polygons are touching the domains of the outer polygon.
-See \cref{shape_decomposition_domains}.
+% The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
+% Each polygon in the input shape acquires it's own domain.
+% The domains of hole polygons are touching the domains of the outer polygon.
+% See \cref{shape_decomposition_domains}.
 
-The medial axis of a polygonal shape can be obtained from the Voronoi Diagram (VD) generated on the line segments and vertices of the shape, by throwing away all edges of the VD falling outside of the outline shape and throwing away the edges connected to concave vertices in the outline shape.
-\cite{lee1982medial}
-However, the concave vertices are precisely in the support of the nodes to which those edges connect.
-This means we can efficiently compute the ST from the VD by removing all edges which lie outside the outline shape and add radial edges to the nodes from there.
-See \cref{skeletonization_comparison}.
+Besides the nodes that are connected by straight or parabolic edges, we insert nodes to discretize a parabolic edge into a polyline (see the middle of \cref{shape_decomposition_st}). 
+The length of edges in the polyline is upper bounded by a prescribed constant $d^\text{discretization}$.
+Additional nodes, with the same upper bound on the resulting edge length, are also added to discretize an edge that is formed by two concave outline vertices (see the vertex-vertex region in \cref{legend}).
+This allows to approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the medial axis by interpolating linearly between $R(v_0)$ and $R(v_1)$.
 
-We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
-See the middle of \cref{shape_decomposition_st}.
-That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
+%We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
+%See the middle of \cref{shape_decomposition_st}.
+%That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
+%This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
 %; see \cref{mat_3d}.
 
-\subsubsection{Union of cones}
-In order to visualize the ST as a 3D surface, we add a third dimension.
-We assign each node a height value measured in terms of beads: it's \emph{bead count}.
-We define the bead count as the number of beads to fit along the \emph{diameter} of the shape, which is twice the feature radius.
-While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
-we introduce the concept of the diameter so that we can deal with an odd number of beads while using integer logic.
+%\subsubsection{Union of cones}
+\paragraph{Approximation of union of cones}
+The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
+%In order to visualize the ST as a 3D surface, we add a third dimension.
+We assign each node in ST a (floating) height value measured in terms of beads, referred to as the \emph{bead count}.
+We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
+\begin{equation}
+    b^*_v = 2 R(v) / w_\text{pref},
+\label{eq:initialBeadCount}
+\end{equation}
+where $w_\text{pref}$ is the nozzle size. 
+%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
+We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
+%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
+Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+\jun{is it only a visualization or will it be used for slicing?}
 
-For each node $v$ we assign an initial bead count based on the feature diameter $2R$ and the nozzle size $w_\text{pref}$: $b^*_v \leftarrow 2 R(v) / w_\text{pref}$.
-The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
-Note that although the overview of the method was described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+\paragraph{Implementation}
+The medial axis of a polygonal shape is a subset of the Voronoi Diagram (VD) generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
+The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
+Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
+From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
+We then assign each node the bead count values using Eq.~\ref{eq:initialBeadCount}.
+We compute the Voronoi diagram using the Boost \verb!C++!
+libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}.
+A half-edge data-structure is used to represent the Voronoi diagram (\cref{shape_decomposition_datastructure}).
 
-We compute the UoC by first generating the VD using the Boost \verb!C++! library, which implements the algorithm proposed by \citeauthor{fortune1986sascg}.\cite{fortune1986sascg}
-We transfer the internal parts of each Voronoi cell to our half-edge data-structure, discretize non-linear VD edges and add the support edges to form the ST.
-We then assign each node the bead count values using the simple formula described above.
+%
+
+\jun{Since VD is not frequently used, I propose to suppress the use of VD. The full consequence needs to be checked.}
 
 \subsection{Center classification}\label{sec_center_classification}
-The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
-These central regions present themselves as upper ridges in the mountains of the UoC surface.
-This sections covers what parts of the UoC will be marked as being central, as opposed to peripheral.
+%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
+%These central regions present themselves as upper ridges in the mountains of the UoC surface.
+%This sections covers what parts of the UoC will be marked as being central.
+\jun{TODO: For what purpose ... }
+we mark parts of the UoC as being central.
+The remaining is called peripheral.
+Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.
 
-We mark a node in the ST as central if its feature radius is larger than that of all of the neighboring nodes.
-That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
-We also mark whole edges as being central if they are significant according to a significance measure which is commonly used in shape analysis.
+We mark a node in the ST as central if its feature radius is larger than that of all its neighboring nodes, i.e. a local maxima.
+%That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
+We also mark an edge as being central if it is significant according to a significance measure.
 
-\subsubsection{Significance measure}\label{sec:significance_measure}
-Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
+%\subsubsection{Significance measure}\label{sec:significance_measure}
+\paragraph{Significance measure}
+We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
+%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
+The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$, formed by two support edges ($vp_0$ and $vp_1$) of node $v$~\cite{attali1996modeling}. 
+\jun{Bisector angle is defined on nodes, but later we classify edges on either of its nodes, or?}
 Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w$.
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ \jun{$w\to w_{pref}$ }when filled using the simple technique of uniform bead width $w$.
 See \cref{naive_overfill_underfill}.
@@
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
-We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
-Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.
+%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
 
@@
 
-A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
-if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
+% The significance evaluation is performed efficiently by checking the ratio between feature radius $R$ and the Euclidean distance:
+% if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
 See \cref{distance_based_angles}.
-This means we can prevent executing trigonometric functions on \emph{each} of the edges in the ST.
-Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
+This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
 
-This ratio can readily be applied to simple ST edges to determine whether they are significant.
+Whether the bisection angle is larger than a threshold $\alpha_\text{max}$ is equivalent to if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$.
+See \cref{distance_based_angles}.
+This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
+%This ratio can readily be applied to simple ST edges to determine whether they are significant.
 For VD edges generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
@@
 See \cref{legend}.
+\jun{This paragraph is not clear to me. Is it related to Fig. 6? what is $x$ and what is $d$?}
 
@@
 
-\subsubsection{Marking filtering}
-Using the significance measure and the local maximum feature radius condition we initialize all marked edges and nodes.
-We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
-We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
+%\subsubsection{Marking filtering}
+\paragraph{Marking filtering}
+After initializing all marked edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
+The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.
 From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
@@
 Now that we have identified and marked the central regions we quantize their heights.
-More specifically we round the heights to integer bead count values.
-Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values coincides with a slicing height.
+More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$).
+Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b_v/2$) coincides with a slicing height.
 When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
@@
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-In order to update the bead count values, we require a quantization operator which maps a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
-For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-In our generalized framework the function $q$ is determined by a beading scheme.
+We define a quantization operator to map a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
+For examples in this section we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
+Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
 

### 2019-08-27 12_conclusions_future_work.tex
Jun: half of changes to section 3.4

@@
 
-Taking a broader perspective we note that the skeletonization decomposes a shape into trapezoids and these trapezoids are decomposed into quads by the toolpath segments which we generate for it.
-It would be interesting to see if similar technique can be used to generate quad dominant meshings for finite element analysis.
+% Taking a broader perspective we note that the skeletonization decomposes a shape into trapezoids and these trapezoids are decomposed into quads by the toolpath segments which we generate for it.
+% It would be interesting to see if similar technique can be used to generate quad dominant meshings for finite element analysis.

### 2019-08-27 4_method.tex
Jun: half of changes to section 3.4

@@
 More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$).
-Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b_v/2$) coincides with a slicing height.
+Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b/2$) coincides with a slicing height.
 When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
@@
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-We define a quantization operator to map a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
-For examples in this section we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
-
-We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
-We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
-From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
-If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
 
@@
 \subsubsection{Quantization}
-For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
+
+We define a quantization operator to map a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
+For examples in this section we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
+Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
+
+We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
+We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
+From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
+If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
+
+For an edge which connects two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
 We call these locations the \emph{transition anchor positions}.
-Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
+% Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
 
@@
 $$v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
-for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
+for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
 See \cref{beading_transitioning_filtering__transition_mids}.

### 2019-08-27 4_method.tex
Tims corrections to 3.1 - 3.3 and Juns corrections to 3.4

--- 2019-08-27 4_method.tex
@@
 
-Given an arbitrarily shaped polygon which represents the intersection of a plane and a 3D shape, our method generates a toolpath with varying width, i.e.
-a set of (mostly) connected line segments, with each node being assigned a width.
-The width along a line segment is linearly interpolated from the widths of its two nodes.
+Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates a toolpath with varying width, i.e.
+a set of (mostly) connected line segments, with each junction being assigned a location and an extrusion width;
+in between the junctions we linearly interpolate the position and extrusion width.
 
-Our method starts with computing the skeleton of the input polygon by medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpath~\cite{eiamsa2003toward}.
-We make use of the union of cones to visualize the skeleton (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (Fig.
-2?).
-Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (Fig. 2?).
+Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpaths~\cite{eiamsa2003toward}.
+We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
+Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
 
-As depicted in Fig.
-2?-?, starting from the medial axis, our method first identifies edges and nodes in the skeleton that are located in the central of the polygon (\cref{sec_center_classification}).
-The heights at these elements are then quantized in terms of beads.
-To ensure a smooth toolpath between regions with quantized integer heights that different more than two, we add new nodes in the skeleton and assign them interpolated integer heights (\cref{sec_central_height_adjustment}).
-The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain a toolpath with varying width (\cref{sec_toolpath_extraction}).
-\jun{Do we use regular intervals, but get varying width?}
+As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
+The heights at these elements are then quantized to an integer number of beads.
+To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights in between (\cref{sec_central_height_adjustment}).
+The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
 
@@
 
-This section explains how we can generate toolpaths with evenly distributed bead widths.
-In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.
+This section explains how we can generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
+In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.
 
@@
 \includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
-\caption{Layer outline}\label{}
+\caption{Layer outline}\label{overview_outline}
 \end{subfigure}
@@
 \includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
-\caption{Skeleton}\label{}
+\caption{Skeleton}\label{overview_skeleton}
 \end{subfigure}
@@
 \includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
-\caption{Union of cones}\label{}
+\caption{Union of cones}\label{overview_uoc}
 \end{subfigure}
@@
 \includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
-\caption{Slicing}\label{}
+\caption{Slicing}\label{overview_uniform_sliced}
 \end{subfigure}
@@
 \includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
-\caption{Uniform paths}\label{}
+\caption{Uniform paths}\label{overview_uniform_paths}
 \end{subfigure}
@@
 \caption{
-The first row illustrates the generation of uniform paths (e) by interpreting the path as the intersection of horizontal planes and the union of cones (c) which is an alternative visualization of the skeleton (b).
-The second row depicts the major steps with both 2D and 3D visualizations for generating paths with adaptive width (i).
-Central elements in the skeleton are first identified (blue in f).
-The heights are then quantized in terms of beads (g, the integer values), and smoothed (h).
-% A geometrical conceptualization of our technique.
-% 3D visualization on top and the corresponding 2D visualization on bottom.
-% In the UoC \subref{3d_surface_overview_uoc}
-% we mark the central regions \subref{3d_surface_overview_center}
-% and quantize the height in those regions \subref{3d_surface_overview_rounded}.
-% We then smooth out the jumps between different integer multiples \subref{3d_surface_overview_smoothed}
-% and finally we slice the structure to get the toolpaths \subref{3d_surface_overview_sliced}.
-% Blue signifies regions marked as being central.
-% The numbers are the integer multiples of half the nozzle width.
+The first row illustrates the generation of uniform paths \subref{overview_uniform_paths}
+by interpreting the path as the intersection between horizontal planes and the union of cones \subref{overview_uoc}, which is an alternative visualization of the skeleton \subref{overview_skeleton}. 
+The second row depicts the stages with both 2D and 3D visualizations for generating paths with adaptive width \subref{3d_surface_overview_sliced}.
+Central elements in the skeleton are first identified (blue in \subref{3d_surface_overview_center}).
+The heights are then quantized in terms of number of beads (the integer values in \subref{3d_surface_overview_rounded}), and smoothed \subref{3d_surface_overview_smoothed}.
 }
@@
 
-For ease of reference we have included a legend explaining \jun{this figure itself does not sufficiently "explain".
-How about indicating, highlighting etc?} the terms employed in this manuscript in \cref{legend}.
-These terms will be further explained as they first appear later in the paper.
+For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
+These terms will be further explained as they first appear later in this paper.
 
@@
 Starting from the medial axis we further decompose the shape into simple fragments, so that the domain contains only quads and triangles.
-This decomposition allows to approximate the surface of the UoC as a 3D piecewise linear mesh.
+This decomposition constitutes an approximation of the UoC.
 
@@
 \paragraph{Medial axis transform}
-The medial axis is a compact and intrinsic representation of shapes.
-It is defined by the locations where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
+The medial axis is a compact and complete representation of a shape.
+It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
 The resulting skeleton consists of straight edges and parabolic edges.
 An example is illustrated in \cref{shape_decomposition_mat}.
-We call the set of closest points on the outline polygon $P$ of a point $v$ on the skeleton its \emph{support}:
+We call the set of points on the outline polygon $P$ closest to a skeletal point $v$ its \emph{support}:
 \begin{equation}
@@
 \end{equation}
-Consequently the shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
+The shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
 %See \cref{MAT_explanation_circles}.
@@
 %Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
-%This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
 %The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
 %See \cref{MAT_explanation}.
-%``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.'' \cite{lee1982medial} 
-%``Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.'' \cite{lee1982medial}
 The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
@@
 
-By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a right cone is formed by the inscribed circle as the base and the raised center as the apex.
-The union of cones forms a 3D solid volume. 
-The medial axis can thus also be interpreted as the ridges of the volume defined by the union of cones.
-
-%\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
-%\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, the feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''
-
-% \begin{figure}
-% \centering
-% \begin{subfigure}{0.3\columnwidth}
-% \centering
-% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
-% \caption{Circles}
-% \label{MAT_explanation_circles}
-% \end{subfigure}
-% \begin{subfigure}{0.3\columnwidth}
-% \centering
-% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
-% \caption{Wave-fronts}
-% \end{subfigure}
-% \begin{subfigure}{0.3\columnwidth}
-% \centering
-% \includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
-% \caption{Union of Cones}
-% \end{subfigure}
-% \caption{
-% Medial axis representations.
-% The medial axis can be defined in terms of the the number of support points of the inscribed circles,
-% as the pinch sites in wave-fronts
-% or as ridges in a volume defined by the union of cones.
-% }
-% \label{MAT_explanation}
-% \end{figure}
+By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a cone is formed. 
+The union of all such cones forms a 3D solid volume. 
+The medial axis can thus also be interpreted as ribs of the surface of the union of cones.~\cite{blum1967transformation}
 
@@
 \paragraph{Skeletal trapezoidation}
-To construct the union of cones, starting from the medial axis we decompose the input polygon into a set of quads and triangles.
-\jun{Tim, what is our initial purpose of skeletal trapezoidation, the purpose before we concept the approach by union of cones?}
+Starting from the medial axis we decompose the input polygon into a set of quads and triangles, so that we can perform the slicing stage on simple shapes.
 We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
@@
 
-Besides the nodes that are connected by straight or parabolic edges, we insert nodes to discretize a parabolic edge into a polyline (see the middle of \cref{shape_decomposition_st}). 
-The length of edges in the polyline is upper bounded by a prescribed constant $d^\text{discretization}$.
-Additional nodes, with the same upper bound on the resulting edge length, are also added to discretize an edge that is formed by two concave outline vertices (see the vertex-vertex region in \cref{legend}).
-This allows to approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the medial axis by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-
-%We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
-%See the middle of \cref{shape_decomposition_st}.
-%That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
-%This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
-%; see \cref{mat_3d}.
+The ST contains all edges from the medial axis which are generated from two line segments in the outline polygons.
+The interaction between an outline vertex and a line segment results in a parabolic region, which is discretized into pieces with a length up to $d^\text{discretization}$ (see the middle of \cref{shape_decomposition_st}).
+Additionally medial axis edges which are generated from two outline vertices are also discretized, so that the feature radius $R$ in between two discretized nodes $v_0$ and $v_1$ can be approximated by linear interpolation between $R(v_0)$ and $R(v_1)$.
+Again we connect the nodes which are introduced by the discretization to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
 
@@
 %In order to visualize the ST as a 3D surface, we add a third dimension.
-We assign each node in ST a (floating) height value measured in terms of beads, referred to as the \emph{bead count}.
+We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count}.
 We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
@@
 %The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
-Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the 2-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
-\jun{is it only a visualization or will it be used for slicing?}
+Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
 
@@
 Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
+These extra edges are a subset of the edges connecting a node to its support, so we can leave them in.
 From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
-We then assign each node the bead count values using Eq.~\ref{eq:initialBeadCount}.
-We compute the Voronoi diagram using the Boost \verb!C++!
-libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}.
+We then assign each node the bead count values using \cref{eq:initialBeadCount}.
+We compute the Voronoi diagram using the Boost \verb!C++! libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}.
 A half-edge data-structure is used to represent the Voronoi diagram (\cref{shape_decomposition_datastructure}).
@@
 
-\jun{Since VD is not frequently used, I propose to suppress the use of VD. The full consequence needs to be checked.}
-
 \subsection{Center classification}\label{sec_center_classification}
@@
 %These central regions present themselves as upper ridges in the mountains of the UoC surface.
+%In order to prevent the over- and underfill we will change the bead counts in the central regions.
 %This sections covers what parts of the UoC will be marked as being central.
+In order to prevent over- and underfill to occur in central
 \jun{TODO: For what purpose ... }
@@
 %Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$, formed by two support edges ($vp_0$ and $vp_1$) of node $v$~\cite{attali1996modeling}. 
-\jun{Bisector angle is defined on nodes, but later we classify edges on either of its nodes, or?}
-Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ \jun{$w\to w_{pref}$ }when filled using the simple technique of uniform bead width $w$.
+The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}.
+Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_\text{pref}^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_\text{pref}$.
 See \cref{naive_overfill_underfill}.
@@
 
-Whether the bisection angle is larger than a threshold $\alpha_\text{max}$ is equivalent to if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$.
-See \cref{distance_based_angles}.
+Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
+\begin{align}\label{simple_significance_measure}
+| R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)
+\end{align}
+(see \cref{distance_based_angles}).
 This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
-%This ratio can readily be applied to simple ST edges to determine whether they are significant.
-For VD edges generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
-For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
-and for VD edges with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
-This ensures that the discretization we perform when transforming the VD into the ST doesn't alter the extent and existence of marked central regions.
-See \cref{legend}.
-\jun{This paragraph is not clear to me. Is it related to Fig. 6? what is $x$ and what is $d$?}
+For line-vertex regions and vertex-vertex regions only a portion of the region may be significant.
+We therefore introduce nodes at the boundaries of the significant portion during the construction of the ST.
+The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.
+
+We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
+For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$.
+We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ x_\text{bound}= 1  / \tan(\alpha_\text{max} / 2)$.
+Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
+The significant portion is given by $ x_\text{bound} = 1  / 2 \tan(\alpha_\text{max} / 2)$
+These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
 
@@
 Now that we have identified and marked the central regions we quantize their heights.
-More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$).
-Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b_v/2$) coincides with a slicing height.
+More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$, also denoted by $b^*$ for short).
+Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^*/2$) coincides with a slicing height.
 When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
 When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
-
+\jun{I like the information in the last few sentences. Shall we make it short here, and describe them in the slicing subsection.}
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-We define a quantization operator to map a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
-For examples in this section we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
-Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
-
-We first assign each marked node $v$ of the ST the bead count $b^*_v \leftarrow q(2R(v))$.
-We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
-From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
-If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
 
@@
 
-\subsubsection{Quantization}
-For edges which connect two nodes $v_0$ and $v_1$ with a different bead count assigned $b^*_{v_0} \neq b^*_{v_1}$ we must figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
-We call these locations the \emph{transition anchor positions}.
-Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
+%\subsubsection{Quantization}
 
-We introduce the function $q^{-1}(n) := \argmax_d q(d) = n$, which gives the feature diameter at which $q$ jumps from $n$ to $n+1$ beads.
+\paragraph{Quantization}
+We define a quantization operator to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
+For examples in this section we first assign $b_\text{initial}$ (Eq.~\ref{eq:initialBeadCount}) to a marked node $v$ and then round it to the nearest integer: $q = \left\lfloor b_\text{initial} + \nicefrac12 \right\rfloor$.
+Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
+Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}.
+Specifically, short unmarked edges (and their nodes) are marked as central if they lie between two nodes with the same integer bead count.
+%We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
+% From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
+% If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
+
+\paragraph{Transition anchors}
+For a marked edge which connects nodes $v_0$ and $v_1$ with $b^*_{v_0}\le n<b^*_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
+% figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
+% We call these locations the \emph{transition anchor positions}.
+% % Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
+To this end, we introduce the function 
+\begin{equation}
+    q^{-1}(n) := \argmax_d q(d) = n,
+\end{equation}
+which gives the feature diameter $d$ at which $q$ the bead count transits from $n$ to $n+1$.
 %For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
-A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
-We can compute the location of the anchor simply as
-$$v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }$$
-for each $n$ such that $b^*_{v_0}<n<b^*_{v_1}$.
-See \cref{beading_transitioning_filtering__transition_mids}.
+The location of the anchor is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. by
+% A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
+% We can compute the location of the anchor simply as
+\begin{equation}
+    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
+\end{equation}
+%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
+An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.
 
-In order to prevent frequent oscillations in the bead count, we filter locally maximal or minimal bead count regions.
-For each edge which contains a transition anchor we walk along the marked regions until we encounter another anchor.
-If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
-See \cref{beading_transitioning_filtering__filtered}.
+We perform a filtering to smooth frequent oscillations in the bead count (which is not visible in the example in \cref{beading_transitioning_filtering}).
+For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
 
-\subsubsection{Smoothing}
-In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e.
+% For each edge which contains a transition anchor we walk along the marked edges until we encounter another anchor.
+% If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
+% See \cref{beading_transitioning_filtering__filtered}.
+
+% \subsubsection{Smooth transition}
+\paragraph{Smooth transition}
+
+A direct transition from $n$ to $n+1$ beads at an anchor creates sharp turns in the toolpath (see \cref{transitions} top).
+A finite transition length ($t(n)$) is designed to ensure a smooth transition (see \cref{transitions} bottom). 
+The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
+%In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e.
 where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
-See \cref{transitions}.
-The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
-For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
+%The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
+%For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
+% A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
+% We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
+% From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
+% For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
+The introduction of transition length requires the edge is longer enough to accommodate it. 
+%Therefore, if the distance from an anchor to its adjacent node is smaller than $t(n)/2$, the anchor is discarded. 
+Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}).
+This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
+compare the top and bottom of \cref{beading_transitioning_filtering}. 
+Finally we update the UoC mesh by adding support edges at transition ends. 
+As shown in \cref{beading_transitioning_filtering__result_uoc}, in the updated UoC mesh, the marked regions become horizontal at integer multiples of $w_{pref}$ for long stretches with ramps in between.
 
-A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
-We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
-From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
-For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
+% These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
 
-Before we generate the transition ramps we filter out transition anchors which are positioned too close to the end of a marked region.
-For each edge which contains a transition anchor we walk along the marked regions until until we have traversed a distance more than $t(n)$.
-If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner as described above.
+% Before we generate the transition ramps we filter out transition anchors which are positioned too close to the end of a marked region.
+% For each edge which contains a transition anchor we walk along the marked regions until until we have traversed a distance more than $t(n)$.
+% If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner as described above.
 
-The generation of the transition ramps should be robust against small perturbations in the outline shape;
-compare the top and bottom of \cref{beading_transitioning_filtering}.
-In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
-If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked edge(s).
-See \cref{beading_transitioning_filtering__transition_ends}.
-These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
+% The generation of the transition ramps should be robust against small perturbations in the outline shape;
+% compare the top and bottom of \cref{beading_transitioning_filtering}.
+% In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
+% If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked edge(s).
+% See \cref{beading_transitioning_filtering__transition_ends}.
+% These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
 
-Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support edges from these new nodes to the outline as per the trapezoidation requirement.
-We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
-See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.
+% Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support edges from these new nodes to the outline as per the trapezoidation requirement.
+% We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
+% See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.
 

### 2019-08-27 4_method.tex
remove commented properteis of significance

@@
 We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
-For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$.
-We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ x_\text{bound}= 1  / \tan(\alpha_\text{max} / 2)$.
+For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$ and $R(x) = y(x)$.
+We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ | x_\text{bound} | = (\tan(\alpha_\text{max} / 2))^{-1}$.
 Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
-The significant portion is given by $ x_\text{bound} = 1  / 2 \tan(\alpha_\text{max} / 2)$
+The boundaries of significance are given by $ | x_\text{bound} | = \nicefrac12 (\tan(\alpha_\text{max} / 2))^{-1}$.
+From these we can derive the locations $l = (\pm x_\text{bound}, y(x_\text{bound}))$.
 These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
@@
 
-\iffalse
-
-\subsubsection{Properties of significant regions}
-%\begin{lemma} \label{min_euclidean_distance} >> this paragraph contains two lemmas and a concluding remark!
-The Euclidean distance between two ST vertices can never be less than the difference in the feature radius $R$ measure between the vertices.
-See \cref{distance_ratio_limit}.
-The condition $|v - p| = \Delta R$ is true exactly for those ST edges between a node $v$ and an outline location $p$ added by the trapezoidation, which means that the trapezoidation never introduces marked edges, so we can perform the trapezoidation after marking.
-
-\iffalse
-% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
-A node in the ST can have at most two significant edges.
-For a node in the VD $v$ with a support of three points on the outline polygon $p_1, p_2, p_3$, the bisector angles $\angle{p_1vp_2} + \angle{p_2vp_3} + \angle{p_3vp_1} = 360\degree$, so if two angles are more than $\alpha_\text{max} > 120\degree$ the third one needs to be smaller than $360\degree - 2\alpha_\text{max} < 120\degree$ and therefore not significant.
-% However, because of some filtering operations this property does not neccesarily hold for the markings.
-The extra edges added to the VD to form the ST can never be significant because their bisector angle is \SI{0}{\degree} by definition,
-so the nodes of the ST also have at most two significant edges.
-\fi
-
-\begin{lemma}\label{saddle_points_are_marked}
-A saddle point is always marked, i.e.\
-when traversing the ST from one locally maximal $R$ to another we must pass through a significant region.
-\end{lemma}
-\begin{proof}
-You will either go through the marked region of a discretized parabola or of an edge with two polygonal vertices as support.
-This means that the feature radius function in between marked regions is always monotonic.
-This means that when propagating beadings downward from marked regions they can never conflict in the middle - they will always conflict at either marked region.
-\end{proof}
-
-\begin{lemma}\label{single_upward_edge}
-From any node in the ST which is not a saddle point there is at most a single edge going upward.
-\end{lemma}
-\begin{proof}
-Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
-If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
-If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
-and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
-Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
-See \cref{branch_upward_edge_property}.
-%See VoronoiQuadrangulation::filterUnmarkedRegions
-Edges added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
-This means that walking up the ST from a marked region to a local maximum follows a single path without branching.
-\end{proof}
-
-\fi
-
-\iffalse
-% This fact is not used anymore, because we change the marking such that it doesn't hold for marked edges any more.
-The two downward edges from a branch point cannot both be significant.
-A branch point which is not a local maximum generated by the support points $p_1, p_2, p_3$ has bisector angles such that $\triangle p_1 p_2 p_3$ has its circumcentre $v$ outside of the triangle, because otherwise the feature radius decreases in all directions.
-This means that all support points lie within a \SI{180}{\degree} range around the node. 
-Suppose the one edge going upward is generated by $p_1$ and $p_3$.
-Then the bisector angle $\angle p_1 v p_3 < 180\degree$ and $\angle p_1 v p_2 + \angle p_2 v p_3 < 180\degree$,
-so if $\angle p_1 v p_2 < 120\degree$ then $\angle p_2 v p_3 < 60\degree$ and is therefore not significant. 
-%so at most either of $\angle p_1 v p_2$ and $\angle p_2 v p_3$ has a significant bisector angle.
-\fi
-
 %\subsubsection{Marking filtering}
 \paragraph{Marking filtering}
-After initializing all marked edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
+After initializing the marking at all edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
 The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.

### 2019-08-27 4_method.tex
Tims edits to 3.3

--- 2019-08-27 4_method.tex
@@
 \paragraph{Marking filtering}
-After initializing all marked edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
+After initializing the marking at all edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
 The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.

### 2019-08-27 4_method.tex
b^* => b~, b- or b^

--- 2019-08-27 4_method.tex
@@
 As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
-The heights at these elements are then quantized to an integer number of beads.
-To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights in between (\cref{sec_central_height_adjustment}).
+The heights $b^\sim$ at these elements are then quantized to an integer number of beads $b^\neg$.
+To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $b^\wedge$ in between (\cref{sec_central_height_adjustment}).
 The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
@@
 %In order to visualize the ST as a 3D surface, we add a third dimension.
-We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count}.
+We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
 We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
 \begin{equation}
-    b^*_v = 2 R(v) / w_\text{pref},
+    b^\sim_v = 2 R(v) / w_\text{pref},
 \label{eq:initialBeadCount}
@@
 Now that we have identified and marked the central regions we quantize their heights.
-More specifically we round the floating heights ($b_\text{initial}$) to integer bead count values ($b_\text{quantized}$, also denoted by $b^*$ for short).
-Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^*/2$) coincides with a slicing height.
+More specifically we round the floating heights ($b^\sim$) to integer bead count values ($b^\neg$).
+Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^\sim/2$) coincides with a slicing height.
 When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
@@
 \paragraph{Transition anchors}
-For a marked edge which connects nodes $v_0$ and $v_1$ with $b^*_{v_0}\le n<b^*_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
+For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0}\le n<b^\neg_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
 % figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
@@
 %Therefore, if the distance from an anchor to its adjacent node is smaller than $t(n)/2$, the anchor is discarded. 
-Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}).
+Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}).
 This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
@@
 \ForAll{$v \in$ nodes}
-	\If {marked($v$)} $\text{map}[v] = (0, B(b^*_v, 2 R(v)))$ \EndIf
+	\If {marked($v$)} $\text{map}[v] = (0, B(b^\wedge_v, 2 R(v)))$ \EndIf
 \EndFor
@@
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
-If a central edge has both nodes with an odd bead count assigned to it $b^* \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
+If a central edge has both nodes with an odd bead count assigned to it $b^\wedge \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
 We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.

### 2019-08-27 4_method.tex
clarify transitioning better in the overview

@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/quantized.png}
 
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_magenta.png}
 
@@
 Now that we have identified and marked the central regions we quantize their heights.
-More specifically we round the floating heights ($b^\sim$) to integer bead count values ($b^\neg$).
-Because the bead count is defined in terms of the feature diameter rather than the radius, only half of the integer bead count values ($b^\sim/2$) coincides with a slicing height.
-When the heights of a ridge are rounded to an \emph{even} bead count, the ridge will be sliced as normal; the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
-When the heights of a ridge are rounded to an \emph{odd} bead count, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
-\jun{I like the information in the last few sentences. Shall we make it short here, and describe them in the slicing subsection.}
+We first quantize the initial bead count $b^\sim$ into an integer bead count $b^\neg$ at the marked nodes using a quantization operator $q$,
+then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
+and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $b^\wedge$ along the smooth transition.
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
@@
 \paragraph{Quantization}
-We define a quantization operator to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
-For examples in this section we first assign $b_\text{initial}$ (Eq.~\ref{eq:initialBeadCount}) to a marked node $v$ and then round it to the nearest integer: $q = \left\lfloor b_\text{initial} + \nicefrac12 \right\rfloor$.
-Alternative realizations of the function $q$ will be discussed in \cref{sec_generalization}.
+We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
+Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
+$q(d) = \left\lfloor d / w_\text{pref} + \nicefrac12 \right\rfloor$.
+Alternative quantization schemes will be discussed in \cref{sec_generalization}.
+By applying $q$ to the heights of central nodes we quantize the bead count:
+$b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor$.
+\iffalse
 Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}.
-Specifically, short unmarked edges (and their nodes) are marked as central if they lie between two nodes with the same integer bead count.
+Specifically, unmarked regions are marked as central if they lie between two nodes with the same integer bead count.
+\fi
 %We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
@@
 \paragraph{Transition anchors}
-For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0}\le n<b^\neg_{v_1}$, we determine \emph{transition anchors} at which the bead count transits from $n$ to $n+1$.
-% figure out the exact location(s $v$ where the quantization operator $q(2R(v))$ jump to a different integer.
-% We call these locations the \emph{transition anchor positions}.
-% % Rather than applying the jumps to the UoC mesh we calculate the transition anchor positions and apply smoothing based on those positions, so that we modify the UoC mesh afterwards.
+For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0} \le n < b^\neg_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
 To this end, we introduce the function 
@@
 \end{equation}
-which gives the feature diameter $d$ at which $q$ the bead count transits from $n$ to $n+1$.
-%For each marked edge between $v_0$ and $v_1$ with $b^*_{v_0} \neq b^*_{v_1}$ we introduce transitions.
-The location of the anchor is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. by
-% A smoothed transition from bead count $n$ to $n+1$ will be anchored on each location $v_x$ where $R(v_x) = q^{-1}(n)$.
-% We can compute the location of the anchor simply as
+which gives the feature diameter $d$ at which the bead count $q$ transitions from $n$ to $n+1$.
+The location of the anchor $v_x$ is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. 
 \begin{equation}
@@
 
-We perform a filtering to smooth frequent oscillations in the bead count (which is not visible in the example in \cref{beading_transitioning_filtering}).
-For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
+We perform a filtering step to prevent frequently changing the bead count back and forth within a short distance.
+For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
 
@@
 % \subsubsection{Smooth transition}
-\paragraph{Smooth transition}
+\paragraph{Smooth transitions}
 
-A direct transition from $n$ to $n+1$ beads at an anchor creates sharp turns in the toolpath (see \cref{transitions} top).
-A finite transition length ($t(n)$) is designed to ensure a smooth transition (see \cref{transitions} bottom). 
+A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
+A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
 The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
-%In order to prevent discontinuities in the toolpaths around locations where the bead count changes i.e.
-where there is a jump in height in the UoC, we need a way to smoothly transition to a different number of beads around locations where the outline shape has a changing bead count.
-%The length along the marked region of a transition from bead count $n$ to $n+1$ is determined by some function $t(n)$.
-%For our example we will use a transition length equal to the nozzle size: $t(n) = w_\text{pref}$.
-% A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
-% We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
-% From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
-% For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.
-The introduction of transition length requires the edge is longer enough to accommodate it. 
-%Therefore, if the distance from an anchor to its adjacent node is smaller than $t(n)/2$, the anchor is discarded. 
-Therefore, we modify nodes that are within $t(n)/2$ by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated from the ratio of the distance over $t(n)$ (see \cref{beading_transitioning_filtering__transitions_applied}).
-This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
-compare the top and bottom of \cref{beading_transitioning_filtering}. 
-Finally we update the UoC mesh by adding support edges at transition ends. 
-As shown in \cref{beading_transitioning_filtering__result_uoc}, in the updated UoC mesh, the marked regions become horizontal at integer multiples of $w_{pref}$ for long stretches with ramps in between.
-
-% These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
-
-% Before we generate the transition ramps we filter out transition anchors which are positioned too close to the end of a marked region.
-% For each edge which contains a transition anchor we walk along the marked regions until until we have traversed a distance more than $t(n)$.
-% If we hit the end of a marked region and the traversed distance from the anchor point is less than the distance $t_{0}(n)$ or $t_{1}(n)$ to the transition end we dissolve the bead count region in the same manner as described above.
-
-% The generation of the transition ramps should be robust against small perturbations in the outline shape;
-% compare the top and bottom of \cref{beading_transitioning_filtering}.
-% In order to generate the lower and upper end point of the transition ramps we walk downward and upward along the marked regions from each anchor position $v$ until we have traversed the corresponding distance of $t_{0}(n)$ or $t_{1}(n)$.
-% If there is any node $v_x$ in between $v$ and $v_0$ or $v_1$ we assign it a fractional bead count by linear interpolation: $b^*_{v_x} = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the cumulative distance measured along the marked edge(s).
-% See \cref{beading_transitioning_filtering__transition_ends}.
-% These fractional bead counts will be used in \cref{section_beading_interpolation} in a way which guarantees a similar toolpath in transitioning regions which are crossed by extra support edges for small perturbations and those which are not.
-
-% Finally we perform the mesh update by introducing nodes at the transition ends and introducing radial support edges from these new nodes to the outline as per the trapezoidation requirement.
-% We end up with a UoC with marked regions altered to be horizontal at integer multiples of half the nozzle width for long stretches with ramps in between.
-% See \cref{beading_transitioning_filtering__transitions_applied} and \subref{beading_transitioning_filtering__result_uoc}.
+We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
+In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes which are in between the two ends of the transition by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}).
+%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
+%compare the top and bottom of \cref{beading_transitioning_filtering}. 
+Finally we update the ST by adding support edges at the transition ends. 
+As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_{pref}$ for long stretches with ramps in between.
 
@@
 If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
-If a central edge has both nodes with an odd bead count assigned to it $b^\wedge \bmod 2 = 1 $ we should prevent the algorithm from generating the center extrusion segment from both trapezoids.
-We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$.
+
+Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $b^\wedge$ in a central region coincide with a slicing height.
+When the bead count $b^\wedge$ is even, the ridge will be sliced as normal;
+the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
+When the bead count $b^\wedge$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
+In that case we should prevent the algorithm from generating the center extrusion segment twice from the trapezoids on either side of that segment.
+We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$: $x_0 < x_1 \lor (x_0 = x_1 \land y_0 < y_1)$.
 

### 2019-08-27 4_method.tex
new transitioning figure
Tims edits to 3.4

@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/quantized.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/rounded_cropped.png}
 
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_magenta.png}
+\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_cropped.png}
 

### 2019-08-27 5_generalization.tex
Tims edits to 3.4

@@
 d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
+d_\text{max}^\text{unmarked} &= w_\text{pref} \\ 
 d^\text{discretization} &= \SI{0.2}{\milli\meter} \\

### 2019-08-27 4_method.tex
w_pref ==> w_*

--- 2019-08-27 4_method.tex
@@
 \begin{equation}
-    b^\sim_v = 2 R(v) / w_\text{pref},
+    b^\sim_v = 2 R(v) / w_*,
 \label{eq:initialBeadCount}
 \end{equation}
-where $w_\text{pref}$ is the nozzle size. 
+where $w_*$ is the nozzle size. 
 %While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
@@
 Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_\text{pref}^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_\text{pref}$.
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_*^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_*$.
 See \cref{naive_overfill_underfill}.
@@
 \begin{subfigure}{.27\textwidth}
-\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.png}
+\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.pdf}
 \caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
@@
 Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
-$q(d) = \left\lfloor d / w_\text{pref} + \nicefrac12 \right\rfloor$.
+$q(d) = \left\lfloor d / w_* + \nicefrac12 \right\rfloor$.
 Alternative quantization schemes will be discussed in \cref{sec_generalization}.
@@
 A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
-The transition is centered at the anchor, and its length is set to $t(n) = w_\text{pref}$.
+The transition is centered at the anchor, and its length is set to $t(n) = w_*$.
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
@@
 Finally we update the ST by adding support edges at the transition ends. 
-As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_{pref}$ for long stretches with ramps in between.
+As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_*$ for long stretches with ramps in between.
 

### 2019-08-27 5_generalization.tex
w_pref ==> w_*

--- 2019-08-26 5_generalization.tex
@@
 A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
-Our beading schemes are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
+Our beading schemes are based on a preferred width $w_* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
 Most of the beading schemes we introduce share a common ground:
@@
 d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
+d_\text{max}^\text{unmarked} &= w_* \\ 
 d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
-t_\text{beading} &= w_\text{pref} \\
+t_\text{beading} &= w_* \\
 d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
@@
 %$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
-t(n) &= w_\text{pref} \\
+t_0(n) &=  t(n) \left( q^{-1}(n) / w_*  - n \right) \\
+t(n) &= w_* \\
 \alpha_\text{max} &= \SI{135}{\degree} \\
@@
 
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_\text{pref}$ for $n \in \mathbb{N}$.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_*$ for $n \in \mathbb{N}$.
 The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
@@
 \alpha_\text{max} &= \SI{180}{\degree} \\
-q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
-W(n,d)_i &= w_\text{pref} \text{ for all } i 
+q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
+W(n,d)_i &= w_* \text{ for all } i 
 %\\
-%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+%L(n,d)_i &= w_* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
 \end{align*}
@@
 \begin{cases}
-1 & \text{ if } d < w_\text{pref} \\
+1 & \text{ if } d < w_* \\
 2 & \text{ otherwise } \\
@@
 d & \text{ if } n = 1 \\
-w_\text{pref} & \text{ otherwise } \\
+w_* & \text{ otherwise } \\
 \end{cases}
@@
 %d / 2 & \text{ if } n = 1 \\
-%w_\text{pref} / 2 & \text{ otherwise } \\
+%w_* / 2 & \text{ otherwise } \\
 %\end{cases}
@@
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_*$.
+Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_*$.\cite{Jin2017JMS}
 We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
@@
 \begin{align*}
-t(n) &= \frac12 w_\text{pref} \\
-q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
+t(n) &= \frac12 w_* \\
+q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
 q(d) &= q^-(d) +
 \begin{cases}
--1 & \text{ if } q^-(d) w_\text{pref} - d > w_\text{pref} - r_\text{max} \\
-1  & \text{ if }  q^-(d) w_\text{pref} - d < w_\text{pref} - r_\text{min} \\
+-1 & \text{ if } q^-(d) w_* - d > w_* - r_\text{max} \\
+1  & \text{ if }  q^-(d) w_* - d < w_* - r_\text{min} \\
 0 & \text{ otherwise}
@@
 \begin{cases}
-d - (n-1) w_\text{pref} &\text{ if } i = \frac12 (n-1) \\
-w_\text{pref} &\text{ otherwise }
+d - (n-1) w_* &\text{ if } i = \frac12 (n-1) \\
+w_* &\text{ otherwise }
 \end{cases}
@@
 %d / 2 & \text{ if } i = \frac12 (n-1) \\
-%w_\text{pref} \left(i + \frac12 \right) & \text{ otherwise }
+%w_* \left(i + \frac12 \right) & \text{ otherwise }
 %\end{cases}
@@
 \begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
+q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 \paragraph{General distributed scheme}
-The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to
-$w_\text{pref} + E / n$.
+The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_*$, dividing the total discrepancy by the number of beads and setting the width of each bead to
+$w_* + E / n$.
 However, depending on the application we might want a different distribution of widths.
@@
 \begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_\text{pref}} + \frac12 \right\rfloor \\
-E(n,d) &= d - n w_\text{pref} \\
-W(n,d)_i &= w_\text{pref} + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
+q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
+E(n,d) &= d - n w_* \\
+W(n,d)_i &= w_* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
 %\\
@@
 See \cref{distributed_comparison}.
-That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
+That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_*$ in regions farther away.
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.

### 2019-08-27 6_validation.tex
w_pref ==> w_*

@@
 We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_*] = \SI{0.4}{\milli\meter}$.
 
@@
 The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the preferred width to $w_\text{pref} = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+We set the preferred width to $w_* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

### 2019-08-27 4_method.tex
junction -> site

@@
 Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates a toolpath with varying width, i.e.
-a set of (mostly) connected line segments, with each junction being assigned a location and an extrusion width;
-in between the junctions we linearly interpolate the position and extrusion width.
+a set of (mostly) connected line segments, with each site being assigned a location and an extrusion width;
+in between the sites we linearly interpolate the position and extrusion width.
 
@@
 
-The beading information will be used in the next phase to directly generate the junctions of the toolpaths.
+The beading information will be used in the next phase to directly generate the sites of the toolpaths.
 Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
@@
 \subsection{Toolpath extraction}\label{sec_toolpath_extraction}
-Now that each node has a beading associated with it we can apply the beading to generate the junctions of the toolpaths.
-For each upward half-edge $e$ we generate each junction $J$ based on the beading $B = B^{v_1^e}$:
+Now that each node has a beading associated with it we can apply the beading to generate the sites of the toolpaths.
+For each upward half-edge $e$ we generate each site $J$ based on the beading $B = B^{v_1^e}$:
 \begin{align*}
@@
 for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
-See \cref{junction_placement}.
-We store all junctions of an edge in a mapping from edge to a list of junctions.
+See \cref{site_placement}.
+We store all sites of an edge in a mapping from edge to a list of sites.
 
@@
 \caption{
-Applying beadings to generate junctions along trapezoids.
+Applying beadings to generate sites along trapezoids.
 \subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
 \subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
-\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective junctions along the support edges.
-No junctions will be generated along marked edges.
-Wide black lines are outline segments, marked nodes and edges in blue, the junctions in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
+\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
+No sites will be generated along marked edges.
+Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
 }
-\label{junction_placement}
+\label{site_placement}
 \end{figure}
 
-We then generate extrusion segments for each trapezoid by connecting together the junctions of the same index.
+We then generate extrusion segments for each trapezoid by connecting together the sites of the same index.
 See \cref{segment_generation}.
-If the amount of junctions on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner junction unconnected.
+If the amount of sites on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner site unconnected.
 
@@
 Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomposition_domains}.
-Each edge is assigned toolpath junctions (yellow) which are connected together as shown in the singled out trapezoid.
+Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
 By following the trapezoids along the domain (cyan) of a single outline polygon,
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline ending in a junction $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
+In order to retreat a polyline ending in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
 This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.

### 2019-08-27 5_generalization.tex
junction -> site

@@
 
-Because the peripheral height adjustment was described in terms of a mapping from radial distances to junctions rather than adjusting the heights of peripheral nodes,
+Because the peripheral height adjustment was described in terms of a mapping from radial distances to sites rather than adjusting the heights of peripheral nodes,
 we can introduce non-linear mappings without refining the surface mesh.

### 2019-08-27 8_discussion.tex
w_pref ==> w_*
junction -> site

@@
 \subsection{Limitations}
-In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w_\text{pref}$.
+In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w_*$.
 That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
 which might be difficult to accurately manufacture on some hardware.
-While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around junctions in the toolpath, so this approach is inherently limited.
+While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around sites in the toolpath, so this approach is inherently limited.
 Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).

### 2019-08-27 4_method.tex
lil rewording

@@
 
-Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates a toolpath with varying width, i.e.
-a set of (mostly) connected line segments, with each site being assigned a location and an extrusion width;
+Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates extrusion toolpaths with varying width, i.e.
+a set polylines where each site consists of a location and an extrusion width;
 in between the sites we linearly interpolate the position and extrusion width.
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline ending in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
+In order to retreat a polyline which ends in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
 This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.

### 2019-08-27 5_generalization.tex
move all beading scheme formulae to a single figure

@@
 
-\paragraph{Uniform beading scheme}
-We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
+%\fboxsep=10mm%padding thickness
+\begin{figure}%\centering
+\setlength{\figwidth}{.2\textwidth}
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
+%\frame{
 \begin{align*}
@@
 \end{align*}
-
-\paragraph{Outer bead}
-We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
-Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
-
+\caption{Uniform scheme}\label{formula_uniform}
+\end{subfigure}
+}
+%
+%
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
 \begin{align*}
-d_\text{max}^\text{intersection} &= \SI{0}{\percent} \\
-t(n) &= 0 \\
 q(d) &=
@@
 \end{align*}
-
-\paragraph{Constant bead count}
-We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
-Additionally in order to emulate their definition of branches we mark all ST edges and in a separate algorithm we unmark the outer edges connected to the outline shape.
-Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.
-
+\caption{Outer bead}\label{formula_outer_bead}
+\end{subfigure}
+}
+%
+%
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
 \begin{align*}
@@
 \end{align*}
-
-\paragraph{Centered}
-We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
-We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_*$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_*$.\cite{Jin2017JMS}
-We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
-
+\caption{Constant bead count}\label{formula_constant_bead_count}
+\end{subfigure}
+}
+%
+%
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
+\begin{align*}
+q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
+W(n,d)_i &= d / n \text{ for all } i 
+%\\
+%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
+\end{align*}
+\caption{Evenly distributed}\label{formula_evenly_distributed}
+\end{subfigure}
+}
+%
+%
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
 \begin{align*}
 t(n) &= \frac12 w_* \\
-q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
+%q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
 q(d) &= q^-(d) +
@@
 \end{align*}
+\caption{Centered}\label{formula_centered}
+\end{subfigure}
+}
+%
+%
+\fbox{
+\begin{subfigure}[b]{\figwidth}\centering
+\begin{align*}
+q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
+E(n,d) &= d - n w_* \\
+W(n,d)_i &= w_* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i \\
+%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
+M(n,d)_i &= \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )
+\end{align*}
+\caption{Inward distributed}\label{formula_inward_distributed}
+\end{subfigure}
+}
+\caption{
+Beading schemes.
+}
+\label{beading_schemes}
+\end{figure}
+
+\paragraph{Uniform beading scheme}
+We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
+See \cref{formula_uniform}.
+
+\paragraph{Outer bead}
+We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
+Also we turn off the reduction of toolpaths near 3-way intersections $d_\text{max}^\text{intersection} = \SI{0}{\percent}$, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
+We don't need transitioning, so we also set $t(n) = 0 $.
+See \cref{formula_outer_bead}.
+
+\paragraph{Constant bead count}
+We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
+Additionally in order to emulate their definition of branches we mark all ST edges and in a separate algorithm we unmark the outer edges connected to the outline shape.
+Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.
+See \cref{formula_constant_bead_count}.
+
+\paragraph{Centered}
+We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
+We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_*$.
+Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_*$.\cite{Jin2017JMS}
+We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
+See \cref{formula_centered}.
 
@@
 This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.
+See \cref{formula_evenly_distributed}.
 
-\begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
-W(n,d)_i &= d / n \text{ for all } i 
-%\\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{General distributed scheme}
+\paragraph{Inward distributed scheme}
+\todo{TODO: merge general distributed with inward distributed decsription.}
 The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_*$, dividing the total discrepancy by the number of beads and setting the width of each bead to
@@
 The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
-
-\begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
-E(n,d) &= d - n w_* \\
-W(n,d)_i &= w_* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i 
-%\\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
-\end{align*}
-
-\paragraph{Inward distributed}
+%\paragraph{Inward distributed}
 For example, we can choose 
@@
 Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
+See \cref{formula_inward_distributed}.
 

### 2019-08-27 4_method.tex
Tims changes to 3.5 and Juns changes to 3.6

@@
 \begin{figure}\centering
-\setlength{\figwidth}{0.19\columnwidth}
+\setlength{\figwidth}{0.24\columnwidth}
 \setlength{\figwidthTwo}{0.3\columnwidth}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
 \caption{Data structure}\label{shape_decomposition_datastructure}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/domains.pdf}
-\caption{Polygon Domains}\label{shape_decomposition_domains}
 \end{subfigure}
@@
 \subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
-\subref{shape_decomposition_domains} The ST divides the shape into primitives which can be classified as belonging to one of the input shape polygons.
 }
@@
 Considering the fact that the concept of trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle~\cite{chazelle1984,fournier1984}, we call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
-
-% The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
-% Each polygon in the input shape acquires it's own domain.
-% The domains of hole polygons are touching the domains of the outer polygon.
-% See \cref{shape_decomposition_domains}.
 
@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central
-\jun{TODO: For what purpose ... }
-we mark parts of the UoC as being central.
+In order to prevent over- and underfill to occur in central, we mark parts of the UoC as being central.
 The remaining is called peripheral.
@@
 We also mark an edge as being central if it is significant according to a significance measure.
+
+\jun{TODO}
 
@@
 These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
+\jun{TODO}
 
@@
 
-\subsection{Peripheral heights}\label{sec_peripheral_height_adjustment}
+\subsection{Peripheral Beading}\label{sec_peripheral_height_adjustment}
+
 Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e.
@@
 See \cref{peripheral_heights}.
-That means we can stretch the $R$ heights of the UoC with a multiplier depending on the height of the center in terms of bead count.
+Mapping an original cone at apex $v$ to a cone with a height equal to the prescribed bead count $b$ of the central region is simply a matter of multiplying the $R$ values by $b / R(v)$.
 
@@
 
-For the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
-Instead of adjusting the height of peripheral mesh nodes, we determine the locations along the edges where the adjusted height coincides with a slicing height.
+However, for the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
+Instead of adjusting the height of peripheral mesh nodes, we determine the radial distances where the adjusted height coincides with a slicing height.
 In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
@@
 
-\begin{definition}
-In order to help generate these toolpath locations we associate each central node with a mapping from radial distances to bead indices, the beading $B$,
-which we define as the following set:
-$$
-B = \left\{ d, n, \left\{ w_0 , \dots , w_{n-1} \right\}, \left\{ l_0 , \dots , l_{n-1} \right\}  \right\}
-$$
+\paragraph{Beading} 
+We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
+For our distributed beading scheme we define the beading for a central node $v$ as:
+\begin{align*}
+    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
+    w_i &= 2R(v) / n  \\
+    l_i &= 2R(v) / n (i + \nicefrac12)
+\end{align*}
 where
-$d = 2 R(v)$ is the diameter associated with $v$,
-$n \in \mathbb{N}$ is the bead count,
-$w_i$ is the bead width of the bead with index $i$ counting from the outline inward
-and
-$l_i$ is the radial locations which maps to the bead with index $i$.
-\end{definition}
-
-For our example we linearly map the $R$ values using a multiplication factor of $d/n$:
-\begin{align*}
-w_i &= d/n  \\
-l_i &= d / n (i + \nicefrac12)
-\end{align*}
+$w_i$ and $l_i$ are the width and location of the $i$th bead,
+respectively, counting from the outline inward.
 An example beading is visualized in the top of \cref{beading_interpolation}:
@@
 
-\subsubsection{Beading interpolation}\label{section_beading_interpolation}
+% \subsubsection{Beading interpolation}\label{section_beading_interpolation}
+\paragraph{Beading interpolation}
 Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
@@
 
-\subsubsection{Beading propagation}\label{section_beading_conflicts}
+% \subsubsection{Beading propagation}\label{section_beading_conflicts}
+\paragraph{Beading propagation}
 The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
@@
 This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.
+
+\jun{It is more logical to first explain the general case (the above paragraph), and then the special treatment -- beading conflict.}
 
@@
 
+\tim{Below is taken from an outdated paragraph in section 3.3 (?)}
+The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
+Each polygon in the input shape acquires it's own domain.
+The domains of hole polygons are touching the domains of the outer polygon.
+See \cref{shape_decomposition_domains}.
+
 Each of the trapezoids is connecting to a single outline polygon.
@@
 \centering
-\includegraphics[width=.5\columnwidth]{sources/method/segment_generation.pdf}
+\setlength{\figheight}{.3\columnwidth}
+\begin{subfigure}{.3\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/domains.pdf}
+\caption{Polygon domains}\label{shape_decomposition_domains}
+\end{subfigure}
+\begin{subfigure}{.6\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/segment_generation.pdf}
+\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
+\end{subfigure}
 \caption{
-Generating toolpaths on a part of the test outline shape which is fully shown in \cref{shape_decomposition_domains}.
+Generating toolpaths on a part of the test outline shape by chaining together extrusion segments along each polygon domain.
 Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.

### 2019-08-27 4_method.tex
w_* => w^*

@@
 \begin{equation}
-    b^\sim_v = 2 R(v) / w_*,
+    b^\sim_v = 2 R(v) / w^*,
 \label{eq:initialBeadCount}
 \end{equation}
-where $w_*$ is the nozzle size. 
+where $w^*$ is the nozzle size. 
 %While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
@@
 Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_*^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_*$.
+For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
 See \cref{naive_overfill_underfill}.
@@
 Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
-$q(d) = \left\lfloor d / w_* + \nicefrac12 \right\rfloor$.
+$q(d) = \left\lfloor d / w^* + \nicefrac12 \right\rfloor$.
 Alternative quantization schemes will be discussed in \cref{sec_generalization}.
@@
 A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
-The transition is centered at the anchor, and its length is set to $t(n) = w_*$.
+The transition is centered at the anchor, and its length is set to $t(n) = w^*$.
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
@@
 Finally we update the ST by adding support edges at the transition ends. 
-As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_*$ for long stretches with ramps in between.
+As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w^*$ for long stretches with ramps in between.
 

### 2019-08-27 5_generalization.tex
w_* => w^*

@@
 A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
-Our beading schemes are based on a preferred width $w_* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
+Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
 Most of the beading schemes we introduce share a common ground:
@@
 d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
-d_\text{max}^\text{unmarked} &= w_* \\ 
+d_\text{max}^\text{unmarked} &= w^* \\ 
 d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
-t_\text{beading} &= w_* \\
+t_\text{beading} &= w^* \\
 d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
@@
 %$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( q^{-1}(n) / w_*  - n \right) \\
-t(n) &= w_* \\
+t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
+t(n) &= w^* \\
 \alpha_\text{max} &= \SI{135}{\degree} \\
@@
 
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w_*$ for $n \in \mathbb{N}$.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
 The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
@@
 \alpha_\text{max} &= \SI{180}{\degree} \\
-q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
-W(n,d)_i &= w_* \text{ for all } i 
+q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
+W(n,d)_i &= w^* \text{ for all } i 
 %\\
-%L(n,d)_i &= w_* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+%L(n,d)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
 \end{align*}
@@
 \begin{cases}
-1 & \text{ if } d < w_* \\
+1 & \text{ if } d < w^* \\
 2 & \text{ otherwise } \\
@@
 d & \text{ if } n = 1 \\
-w_* & \text{ otherwise } \\
+w^* & \text{ otherwise } \\
 \end{cases}
@@
 %d / 2 & \text{ if } n = 1 \\
-%w_* / 2 & \text{ otherwise } \\
+%w^* / 2 & \text{ otherwise } \\
 %\end{cases}
@@
 \begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
+q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
 W(n,d)_i &= d / n \text{ for all } i 
@@
 \begin{align*}
-t(n) &= \frac12 w_* \\
-%q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_*} + \frac12 \right\rfloor \\
+t(n) &= \frac12 w^* \\
+%q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
 q(d) &= q^-(d) +
 \begin{cases}
--1 & \text{ if } q^-(d) w_* - d > w_* - r_\text{max} \\
-1  & \text{ if }  q^-(d) w_* - d < w_* - r_\text{min} \\
+-1 & \text{ if } q^-(d) w^* - d > w^* - r_\text{max} \\
+1  & \text{ if }  q^-(d) w^* - d < w^* - r_\text{min} \\
 0 & \text{ otherwise}
@@
 \begin{cases}
-d - (n-1) w_* &\text{ if } i = \frac12 (n-1) \\
-w_* &\text{ otherwise }
+d - (n-1) w^* &\text{ if } i = \frac12 (n-1) \\
+w^* &\text{ otherwise }
 \end{cases}
@@
 %d / 2 & \text{ if } i = \frac12 (n-1) \\
-%w_* \left(i + \frac12 \right) & \text{ otherwise }
+%w^* \left(i + \frac12 \right) & \text{ otherwise }
 %\end{cases}
@@
 \begin{align*}
-q(d) &= \left\lfloor \frac{d}{ w_*} + \frac12 \right\rfloor \\
-E(n,d) &= d - n w_* \\
-W(n,d)_i &= w_* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i \\
+q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
+E(n,d) &= d - n w^* \\
+W(n,d)_i &= w^* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i \\
 %L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
@@
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_*$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_*$.\cite{Jin2017JMS}
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$.
+Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$.\cite{Jin2017JMS}
 We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
@@
 \todo{TODO: merge general distributed with inward distributed decsription.}
-The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_*$, dividing the total discrepancy by the number of beads and setting the width of each bead to
-$w_* + E / n$.
+The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to
+$w^* + E / n$.
 However, depending on the application we might want a different distribution of widths.
@@
 See \cref{distributed_comparison}.
-That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_*$ in regions farther away.
+That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.

### 2019-08-27 6_validation.tex
junction -> site
w_* => w^*

@@
 We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w_*] = \SI{0.4}{\milli\meter}$.
+We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
 
@@
 %\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
-\caption{Junction angles}
+\caption{Site angles}
 \label{smoothness}
@@
 %\includegraphics[width=\figwidth]{sources/validation/smoothnessNoTransition.pdf}
-\caption{Junction angles without smoothing}
+\caption{Site angles without smoothing}
 \label{smoothnessNoTransition}
@@
 The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the preferred width to $w_* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

### 2019-08-27 4_method.tex
Updates from Overleaf

--- 2019-08-27 4_method.tex
@@
 
-\subsection{Peripheral Beading}\label{sec_peripheral_height_adjustment}
+\subsection{Beading}\label{sec_peripheral_height_adjustment}
 
@@
 \paragraph{Beading} 
-We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
+For toolpath geneWe associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
 For our distributed beading scheme we define the beading for a central node $v$ as:
@@
     B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
-    w_i &= 2R(v) / n  \\
-    l_i &= 2R(v) / n (i + \nicefrac12)
+    w_i &= 2R(v) / n  & \text{for all $i$}\\
+    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i$}
 \end{align*}

### 2019-08-28 4_method.tex
Tims edits to 3.5
some small changes at random places - Jun

--- 2019-08-27 4_method.tex
@@
 Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates extrusion toolpaths with varying width, i.e.
-a set polylines where each site consists of a location and an extrusion width;
+a set of polylines where each site consists of a location and an extrusion width;
 in between the sites we linearly interpolate the position and extrusion width.
@@
 
-This section explains how we can generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
+This section explains how we generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
 In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.
@@
 
-The ST contains all edges from the medial axis which are generated from two line segments in the outline polygons.
-The interaction between an outline vertex and a line segment results in a parabolic region, which is discretized into pieces with a length up to $d^\text{discretization}$ (see the middle of \cref{shape_decomposition_st}).
-Additionally medial axis edges which are generated from two outline vertices are also discretized, so that the feature radius $R$ in between two discretized nodes $v_0$ and $v_1$ can be approximated by linear interpolation between $R(v_0)$ and $R(v_1)$.
-Again we connect the nodes which are introduced by the discretization to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
+The edges generated from MAT can be classified into three types: (a) straight edge generated from two line segments in the outline polygons, (b) parabolic edge resulting from an outline vertex and a line segment in the outline, and (c) straight edge resulting from two outline vertices.
+Type-b and type-c edges are discretized into pieces with a length up to $d^\text{discretization}$.
+This allows to approximate the feature radius in between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 
+Again we connect the newly inserted nodes to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
+
+% The ST contains all edges from the medial axis which are generated from two line segments in the outline polygons.
+% The interaction between an outline vertex and a line segment results in a parabolic edge, which is discretized into pieces with a length up to $d^\text{discretization}$ (see the middle of \cref{shape_decomposition_st}).
+% Additionally medial axis edges which are generated from two outline vertices are also discretized, so that the feature radius $R$ in between two discretized nodes $v_0$ and $v_1$ can be approximated by linear interpolation between $R(v_0)$ and $R(v_1)$.
+% Again we connect the nodes which are introduced by the discretization to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
 
@@
 %The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
-Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+Note that although the overview of the method has been described geometrically in terms of the UoC, the actual toolpath generation relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
 
 \paragraph{Implementation}
-The medial axis of a polygonal shape is a subset of the Voronoi Diagram (VD) generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
+The medial axis of a polygonal shape is a subset of the Voronoi Diagram generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
 The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
 Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
-These extra edges are a subset of the edges connecting a node to its support, so we can leave them in.
+These extra edges are a subset of the edges connecting a node to its support, so we keep them in.
 From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central, we mark parts of the UoC as being central.
+In order to prevent over- and underfill to occur in central, we mark parts of the UoC \jun{ST?} as being central.
 The remaining is called peripheral.
-Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.
+Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).
 
@@
 
-\jun{TODO}
-
 %\subsubsection{Significance measure}\label{sec:significance_measure}
@@
 %Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}.
-Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
-See \cref{naive_overfill_underfill}.
-The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
+The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}.
+An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
+As illustrated in See \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
+This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
+The bisector angle is therefore an exact indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
@@
 
+The significance of the three types of medial axis edges is 
 Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
@@
 We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
-For our distributed beading scheme we define the beading for a central node $v$ as:
+For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads as:
 \begin{align*}
-    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
-    w_i &= 2R(v) / n  \\
-    l_i &= 2R(v) / n (i + \nicefrac12)
+    %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
+    B &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
+    w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
+    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i \leq n$}
 \end{align*}

### 2019-08-28 5_generalization.tex
some small changes at random places - Jun

@@
 \section{Generalization}\label{sec_generalization}
-In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
-The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
-Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
-In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
-There are several schemes one can take for determining the distribution of bead widths.
-We will formalize several schemes and describe the set of parameters these schemes require.
+A critical component in toolpath generation is how to distribute the beads over the feature radius.
+While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3d printer or material.
+
+% In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
+% The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
+% Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
+% In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
+% There are several schemes one can take for determining the distribution of bead widths.
+% We will formalize several schemes and describe the set of parameters these schemes require.
 
 \begin{definition}\label{beading_scheme_definition}
-We define a beading scheme as the following set:
+The beading scheme is configured by the following set of parameters and functions:
 $$
-\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
+\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\},
 $$
-where
-$\alpha_{\text{max}}$ (the limit bisector angle),
-$q(d)$ (quantization operator),
-$t(n)$ (transition length)
+where, as introduced in previous section, $\alpha_{\text{max}}$ is the limit bisector angle,
+$q(d)$ the quantization operator,
+$t(n)$ the transition length
 and
-$t_0(n)$ (transition anchor position) have already been defined above.
-We introduce here
-$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
-and
-$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
+$t_0(n)$ the transition anchor position. \jun{check whether this last one has been defined.}
+$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
 \end{definition}

### 2019-08-28 19_edge_discretization.tex
3.1 - 3.3 Jun

--- 2019-08-27 4_method.tex
@@
-\section{Method}
-\subsection{Overview}
-
-Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates extrusion toolpaths with varying width, i.e.
-a set polylines where each site consists of a location and an extrusion width;
-in between the sites we linearly interpolate the position and extrusion width.
-
-Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpaths~\cite{eiamsa2003toward}.
-We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
-
-As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
-The heights $b^\sim$ at these elements are then quantized to an integer number of beads $b^\neg$.
-To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $b^\wedge$ in between (\cref{sec_central_height_adjustment}).
-The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
-
-% We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
-% explain how to identify central regions in \cref{sec_center_classification}.
-% Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
-% We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
-% and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
-
-This section explains how we can generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
-In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.
-
-% The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
-% These offsets can be generated from the medial axis transform (MAT).
-% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape.
-\cite{blum1967transformation}
-% The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
-% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}
-
-% For the uniform offsetting technique the overfill and underfill problems arise in the center,
-% because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
-% Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
-
-% Our framework can be thought of as following these steps:
-% \begin{itemize}
-% \item Compute the skeleton of the input shape
-% \item Assign each node a height in terms of bead count based on the local feature size
-% \item Identify central regions of the UoC
-% \item Quantize the height of central ridges and peaks
-% \item Smooth out sharp transitions between regions with different integer heights
-% \item Determine the heights in the periphery (non-central regions)
-% \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
-% \end{itemize}
-% See \cref{3d_surface_overview}.
-
-\begin{figure*}
-\centering
-\setlength{\figheight}{.15\textwidth}
-\setlength{\figwidth}{.15\textwidth}
-\setlength{\figwidthTwo}{.22\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
-\caption{Layer outline}\label{overview_outline}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
-\caption{Skeleton}\label{overview_skeleton}
-\end{subfigure}
-\begin{subfigure}{\figwidthTwo}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
-\caption{Union of cones}\label{overview_uoc}
-\end{subfigure}
-\begin{subfigure}{\figwidthTwo}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
-\caption{Slicing}\label{overview_uniform_sliced}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
-\caption{Uniform paths}\label{overview_uniform_paths}
-\end{subfigure}
-
-\setlength{\figwidth}{.22\textwidth}
-\setlength{\figwidthTwo}{.17\textwidth}
-\setlength{\figwidthTree}{.22\textwidth}
-\setlength{\tempheight}{-0.3cm}
-\setlength{\tempheightTwo}{-0.5cm}
-\begin{subfigure}{\figwidth}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}
-
-\vspace{\tempheight}
-
-\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
-\caption{Center identification}\label{3d_surface_overview_center}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/quantized.png}
-
-\vspace{\tempheight}
-
-\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
-\caption{Quantization}\label{3d_surface_overview_rounded}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_magenta.png}
-
-\vspace{\tempheight}
-
-\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
-\caption{Smoothing}\label{3d_surface_overview_smoothed}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}
-
-\vspace{\tempheight}
-
-\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
-\caption{Adaptive width paths}\label{3d_surface_overview_sliced}
-\end{subfigure}
-\caption{
-The first row illustrates the generation of uniform paths \subref{overview_uniform_paths}
-by interpreting the path as the intersection between horizontal planes and the union of cones \subref{overview_uoc}, which is an alternative visualization of the skeleton \subref{overview_skeleton}. 
-The second row depicts the stages with both 2D and 3D visualizations for generating paths with adaptive width \subref{3d_surface_overview_sliced}.
-Central elements in the skeleton are first identified (blue in \subref{3d_surface_overview_center}).
-The heights are then quantized in terms of number of beads (the integer values in \subref{3d_surface_overview_rounded}), and smoothed \subref{3d_surface_overview_smoothed}.
-}
-\label{3d_surface_overview}
-\end{figure*}
-
-For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
-These terms will be further explained as they first appear later in this paper.
-
-\begin{figure}\centering
-\includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
-\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
-\label{legend}
-\end{figure}
-
-%\subsection{Surface generation}\label{sec_surface_construction}
-\subsection{Union of cones}\label{sec_surface_construction}
-
-The union of cones (UoC) is derived from a common skeletonization of the polygonal outline shape: the medial axis.
-By assigning each node in the skeleton a height equal to its shortest distance to the outline we obtain the shape of the UoC.
-Starting from the medial axis we further decompose the shape into simple fragments, so that the domain contains only quads and triangles.
-This decomposition constitutes an approximation of the UoC.
-
-%\subsubsection{Medial axis transform}
-\paragraph{Medial axis transform}
-The medial axis is a compact and complete representation of a shape.
-It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
-The resulting skeleton consists of straight edges and parabolic edges.
-An example is illustrated in \cref{shape_decomposition_mat}.
-We call the set of points on the outline polygon $P$ closest to a skeletal point $v$ its \emph{support}:
-\begin{equation}
-    \text{sup}(v) = \argmin_{x\in P} |x - v|.
-\end{equation}
-The shortest distance for a point on the skeleton is called its feature radius, $R(v)$.
-%See \cref{MAT_explanation_circles}.
-%We therefore represent the skeleton in a standard half-edge data-structure.
-%See \cref{shape_decomposition_datastructure}.
-%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
-%The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
-%See \cref{MAT_explanation}.
-The medial axis along with the feature radius values along the skeleton form a complete shape descriptor, known as the medial axis transform (MAT).
-%Feature radius and node locations will be used below to analyse the shape locally.
-
-By vertically raising the center of an inscribed circle to a height that equals the center's feature radius, a cone is formed. 
-The union of all such cones forms a 3D solid volume. 
-The medial axis can thus also be interpreted as ribs of the surface of the union of cones.~\cite{blum1967transformation}
-
-\begin{figure}\centering
-\setlength{\figwidth}{0.24\columnwidth}
-\setlength{\figwidthTwo}{0.3\columnwidth}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
-\caption{Medial Axis}\label{shape_decomposition_mat}
-\end{subfigure}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
-\caption{Voronoi Diagram}\label{shape_decomposition_vd}
-\end{subfigure}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
-\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
-\end{subfigure}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
-\caption{Data structure}\label{shape_decomposition_datastructure}
-\end{subfigure}
-\caption{
-Skeletonization of an outline shape (black).
-Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
-\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
-}
-\label{skeletonization_comparison}
-\end{figure}
-
-%\subsubsection{Skeletal trapezoidation}
-\paragraph{Skeletal trapezoidation}
-Starting from the medial axis we decompose the input polygon into a set of quads and triangles, so that we can perform the slicing stage on simple shapes.
-We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
-The basic idea is to add edges connecting each node $v$ on the medial axis to (all of) its supports, $\text{sup}(v)$. 
-The resulting skeleton decomposes the outline shape into trapezoids and triangles.
-Considering the fact that the concept of trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle~\cite{chazelle1984,fournier1984}, we call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
-
-The ST contains all edges from the medial axis which are generated from two line segments in the outline polygons.
-The interaction between an outline vertex and a line segment results in a parabolic region, which is discretized into pieces with a length up to $d^\text{discretization}$ (see the middle of \cref{shape_decomposition_st}).
-Additionally medial axis edges which are generated from two outline vertices are also discretized, so that the feature radius $R$ in between two discretized nodes $v_0$ and $v_1$ can be approximated by linear interpolation between $R(v_0)$ and $R(v_1)$.
-Again we connect the nodes which are introduced by the discretization to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
-
-%\subsubsection{Union of cones}
-\paragraph{Approximation of union of cones}
-The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
-%In order to visualize the ST as a 3D surface, we add a third dimension.
-We assign each node in ST a (real number) height value measured in terms of beads, referred to as the \emph{bead count} $b$.
-We define the bead count as the number of beads to fit along the \emph{diameter} of the inscribed circle centered at node $v$, i.e. $2R(v)$, by
-\begin{equation}
-    b^\sim_v = 2 R(v) / w_*,
-\label{eq:initialBeadCount}
-\end{equation}
-where $w_*$ is the nozzle size. 
-%While the feature radii are measured along the support edges, the diameter is not measurable as such because the support edges are generally not collinear;
-We divide the diameter rather than the radius as this allows to deal with an odd number of beads while using integer logic.
-%The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
-Note that although the overview of the method has been described geometrically in terms of the UoC, the actual method relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
-
-\paragraph{Implementation}
-The medial axis of a polygonal shape is a subset of the Voronoi Diagram (VD) generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
-The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
-Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
-These extra edges are a subset of the edges connecting a node to its support, so we can leave them in.
-From the Voronoi diagram we add nodes to discretize parabolic edges and edges formed by two concave outline vertices, and then connect all nodes to their supports, forming a skeletal trapezoidation. 
-We then assign each node the bead count values using \cref{eq:initialBeadCount}.
-We compute the Voronoi diagram using the Boost \verb!C++! libraries~\cite{schaling2011boost}, which implements the algorithm proposed by \citeauthor{fortune1986sascg}~\cite{fortune1986sascg}.
-A half-edge data-structure is used to represent the Voronoi diagram (\cref{shape_decomposition_datastructure}).
-
-%
-
-\subsection{Center classification}\label{sec_center_classification}
-%The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
-%These central regions present themselves as upper ridges in the mountains of the UoC surface.
-%In order to prevent the over- and underfill we will change the bead counts in the central regions.
-%This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central, we mark parts of the UoC as being central.
-The remaining is called peripheral.
-Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes.
-
-We mark a node in the ST as central if its feature radius is larger than that of all its neighboring nodes, i.e. a local maxima.
-%That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
-We also mark an edge as being central if it is significant according to a significance measure.
-
-\jun{TODO}
-
-%\subsubsection{Significance measure}\label{sec:significance_measure}
-\paragraph{Significance measure}
-We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
-%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
-The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting polygon points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}.
-Edges are significant if the bisector angle on any location on the edge exceeds $\alpha_\text{max}$ which is governed by the beading scheme. 
-For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w_*^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w_*$.
-See \cref{naive_overfill_underfill}.
-The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
-%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
-%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
-
-\begin{figure}
-\centering
-\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
-\caption{
-Overfill and underfill areas in a simple toolpathing using a uniform bead width $w$ for a wedge area with vertex angle $\beta$.
-The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
-The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
-}
-\label{naive_overfill_underfill}
-\end{figure}
-
-% The significance evaluation is performed efficiently by checking the ratio between feature radius $R$ and the Euclidean distance:
-% if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
-See \cref{distance_based_angles}.
-This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
-
-Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
-\begin{align}\label{simple_significance_measure}
-| R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)
-\end{align}
-(see \cref{distance_based_angles}).
-This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
-For line-vertex regions and vertex-vertex regions only a portion of the region may be significant.
-We therefore introduce nodes at the boundaries of the significant portion during the construction of the ST.
-The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.
-
+\section{Edge discretization}\label{edge_discretization}
 We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
@@
 These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
-\jun{TODO}
-
-\begin{figure} \centering
-\newlength{\significancePropertiesHeight}
-\setlength{\significancePropertiesHeight}{.25\columnwidth}
-\begin{subfigure}{0.35\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
-\caption{Significance}
-\label{distance_based_angles}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
-\caption{Distance}
-\label{distance_ratio_limit}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
-\caption{Upward edge}
-\label{branch_upward_edge_property}
-\end{subfigure}
-\caption{
-Properties of feature radius $R$.
-Part of outline shape in thick black,
-ST edges in red,
-inscribed circle in gray,
-radii in dashed lines.
-\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
-\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
-\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
-}
-\end{figure}
-
-%\subsubsection{Marking filtering}
-\paragraph{Marking filtering}
-After initializing the marking at all edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
-The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.
-From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
-if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
-
-\subsection{Central height adjustment}\label{sec_central_height_adjustment}
-Now that we have identified and marked the central regions we quantize their heights.
-We first quantize the initial bead count $b^\sim$ into an integer bead count $b^\neg$ at the marked nodes using a quantization operator $q$,
-then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
-and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $b^\wedge$ along the smooth transition.
-%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
-
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.13\textwidth}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
-\caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
-\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
-\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
-\caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
-\end{subfigure}
-\begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
-\caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
-\end{subfigure}
-\begin{subfigure}{.27\textwidth}
-\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.pdf}
-\caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
-\end{subfigure}
-\caption{
-Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
-Outline in black, medial axis edges in red, radial edges in grey.
-\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
-\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
-\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
-\subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
-\subref{beading_transitioning_filtering__transitions_applied} Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
-The symmetry in the result shows that transitioning is robust against small perturbations in the outline shape.
-}
-\label{beading_transitioning_filtering}
-\end{figure*}
-
-%\subsubsection{Quantization}
-
-\paragraph{Quantization}
-We define a quantization operator $q$ to map a feature diameter ($d=2R(v)$) to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
-Because our quantization scheme should round to the nearest integer multiple of the nozzle size, we have
-$q(d) = \left\lfloor d / w_* + \nicefrac12 \right\rfloor$.
-Alternative quantization schemes will be discussed in \cref{sec_generalization}.
-By applying $q$ to the heights of central nodes we quantize the bead count:
-$b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor$.
-\iffalse
-Along with this quantization, an amendment to the marking filtering is performed, in order to alleviate a problem that will be handled in \cref{section_beading_conflicts}.
-Specifically, unmarked regions are marked as central if they lie between two nodes with the same integer bead count.
-\fi
-%We then filter out short unmarked regions where the bead count remains constant in order to limit the extent of a problem handled in \cref{section_beading_conflicts}.
-% From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges until we hit another marked node $v_1$.
-% If the upper node has the same bead count $b^*_{v_1} = b^*_{v_0}$ we mark all edges and nodes $v$ in between, and set the bead count $b^*_v \leftarrow b^*_{v_0}$.
-
-\paragraph{Transition anchors}
-For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0} \le n < b^\neg_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
-To this end, we introduce the function 
-\begin{equation}
-    q^{-1}(n) := \argmax_d q(d) = n,
-\end{equation}
-which gives the feature diameter $d$ at which the bead count $q$ transitions from $n$ to $n+1$.
-The location of the anchor $v_x$ is then computed by inversely interpolating $R(v_x) = q^{-1}(n)$, i.e. 
-\begin{equation}
-    v_x = v_0 + (v_1 - v_0) \frac{ q^{-1}(n) - R(v_0) }{ R(v_1) - R(v_0) }.
-\end{equation}
-%for each $n$ such that $b^*_{v_0}\le n<b^*_{v_1}$.
-An illustration of the anchors is shown in \cref{beading_transitioning_filtering__transition_mids}.
-
-We perform a filtering step to prevent frequently changing the bead count back and forth within a short distance.
-For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
-
-% For each edge which contains a transition anchor we walk along the marked edges until we encounter another anchor.
-% If the other anchor is a transition in the opposite direction and the traversed distance is within some limit $d_\text{max}^\text{transition}$ we remove the transitions and set the bead counts at all nodes in the filtered region to the surrounding bead counts.
-% See \cref{beading_transitioning_filtering__filtered}.
-
-% \subsubsection{Smooth transition}
-\paragraph{Smooth transitions}
-
-A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
-A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
-The transition is centered at the anchor, and its length is set to $t(n) = w_*$.
-We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
-In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes which are in between the two ends of the transition by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}).
-%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
-%compare the top and bottom of \cref{beading_transitioning_filtering}. 
-Finally we update the ST by adding support edges at the transition ends. 
-As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w_*$ for long stretches with ramps in between.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{\columnwidth}
-\begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_no_transitioning.png}
-\caption{Without transitioning}
-\end{subfigure}
-\begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_transitioning.png}
-\caption{Transitioning}
-\end{subfigure}
-\caption{
-Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
-}
-\label{transitions}
-\end{figure}
-
-\subsection{Beading}\label{sec_peripheral_height_adjustment}
-
-Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e.
-the periphery, and slice the resulting mesh into isocontour toolpaths.
-The peripheral heights could be determined in a plethora of ways according to various beading schemes.
-The ramps from the outline shape to the center might have various curves,
-but for our example we use straight ramps, just like the original UoC.
-See \cref{peripheral_heights}.
-Mapping an original cone at apex $v$ to a cone with a height equal to the prescribed bead count $b$ of the central region is simply a matter of multiplying the $R$ values by $b / R(v)$.
-
-\begin{figure}\centering
-\setlength{\figheight}{.2\columnwidth}
-\begin{subfigure}{.55\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/peripheral_heights_3D.png}
-\caption{Surface mesh}
-\end{subfigure}
-\begin{subfigure}{.4\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/peripheral_heights.pdf}
-\caption{ST}
-\end{subfigure}
-\caption{
-Shallow corners will cause peripheral nodes for which the height should be determined based on the central node above it.
-}
-\label{peripheral_heights}
-\end{figure}
-
-However, for the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
-Instead of adjusting the height of peripheral mesh nodes, we determine the radial distances where the adjusted height coincides with a slicing height.
-In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
-how each beading is calculated for a central node
-and how the beadings are propagated outward to peripheral nodes.
-This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.
-
-\paragraph{Beading} 
-For toolpath geneWe associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
-For our distributed beading scheme we define the beading for a central node $v$ as:
-\begin{align*}
-    B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
-    w_i &= 2R(v) / n  & \text{for all $i$}\\
-    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i$}
-\end{align*}
-where
-$w_i$ and $l_i$ are the width and location of the $i$th bead,
-respectively, counting from the outline inward.
-An example beading is visualized in the top of \cref{beading_interpolation}:
-$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
-
-The beading information will be used in the next phase to directly generate the sites of the toolpaths.
-Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
-the upper half of the beading is therefore unused.
-
-% \subsubsection{Beading interpolation}\label{section_beading_interpolation}
-\paragraph{Beading interpolation}
-Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
-In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
-Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
-We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
-See \cref{beading_interpolation}.
-The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.
-
-\iffalse
-In order to create an interpolated beading $B = xB^V + (1-x) B^W$, for some $0<x<1$
-we calculate:
-\begin{align*}
-n^{B} &= n^{B^W} \\
-d^B &= x d^{B^V} + (1-x) d^{B^W} \\
-w_i^{B} &= w_{n^B-i}^{B} = x w_i^{B^V} + (1-x) w_i^{B^W} \text{ for } i < \frac12 n^{B^V} \\
-%  w_{frac{n}{2}^B - frac12}  = something difficult \text{ if } n \mod 2 == 1
-w_i^{B} &= w_i^{B^W} \text{ otherwise}\\
-l_i^{B} &= 
-\begin{cases} 
-x l_i^{B^V} + (1-x) l_i^{B^W} & \text{ for } i < \frac12 (n^{B^V} - 1) \\
-d^B - x l_{i-n^{B^W}+n^{B^V}}^{B^V} + (1-x) l_i^{B^W} & \text{ for } i > n^B - 1 - \frac12 (n^{B^V} - 1) \\
-\frac12 d^B  & \text{ if $n^B$ is odd and } i = (n^B - 1) / 2 \\
-l_i^{B^W} - l_{n^{B^V}-1}^{B^W} + l_{n^{B^V}-1}^B & \text{ otherwise}
-\end{cases}
-\end{align*}
-\fi
-
-\begin{figure}
-\centering
-\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
-\caption{
-Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
-Distances between the thick black lines constitute diameters $d$,
-the toolpath locations are visualized as dots,
-the widths are visualized as bidirectional arrows
-and the middle is highlighted in red.
-}
-\label{beading_interpolation}
-\end{figure}
-
-% \subsubsection{Beading propagation}\label{section_beading_conflicts}
-\paragraph{Beading propagation}
-The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
-However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
-See \cref{beading_conflict_problem}.
-In such a case we interpolate between the lower beading and the beading propagated from above,
-starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
-At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
-This interpolation is performed during the beading propagation algorithm.
-
-\begin{figure}\centering
-\setlength{\figheight}{.2\columnwidth}
-\begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/beading_conflict_3D.png}
-\includegraphics[height=\figheight]{sources/method/beading_conflict.pdf}
-\caption{Beading conflict}\label{beading_conflict}
-\end{subfigure}
-\begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/beading_conflict_solved_3D.png}
-\includegraphics[height=\figheight]{sources/method/beading_conflict_solved.pdf}
-\caption{Conflict resolution}\label{beading_conflict_solved}
-\end{subfigure}
-\caption{
-\subref{beading_conflict} The beading propagated from above conflicts with the beading below.
-\subref{beading_conflict_solved} The beading conflict is resolved by gradually interpolating between the two beadings.
-The ramp to the upper ridge doesn't line up with the lower ridge, which means that
-the toolpaths (dashed) resulting from the beading propagated from above doesn't align with the beading from the thin outline feature (highlighted in red).
-}
-\label{beading_conflict_problem}
-\end{figure}
-
-After each marked node is assigned a beading by the beading scheme, we propagate the beadings outward to all nodes in the ST.
-The beading propagation is performed in two stages: an upward and downward stage.
-%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
-In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
-In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
-however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
-This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.
-
-\jun{It is more logical to first explain the general case (the above paragraph), and then the special treatment -- beading conflict.}
-
-\begin{algorithm}
-\caption{Beading propagation}
-\label{alg_beading_propagation}
-\begin{algorithmic}
-\ForAll{$v \in$ nodes}
-	\If {marked($v$)} $\text{map}[v] = (0, B(b^\wedge_v, 2 R(v)))$ \EndIf
-\EndFor
-\ForAll{$e \in$ edges}
-	\If {$R(v_0^e) < R(v_1^e)$}
-		% \State 
-		upwardEdges.add($e$)
-	\EndIf
-\EndFor
-\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
-\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
-	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
-    		\State $(d, B) = \text{map}[v_0^e]$
-    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
-	\EndIf
-\EndFor
-\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
-	\If {$\text{map}[v_1^e]$}
-    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
-    		% d + |v_1^e - v_0^e|
-    		\If {$\text{map}[v_0^e]$}
-    			\State $(d_0, B_0) = \text{map}[v_0^e]$
-    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
-    		\EndIf
-    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
-	\EndIf
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Toolpath extraction}\label{sec_toolpath_extraction}
-Now that each node has a beading associated with it we can apply the beading to generate the sites of the toolpaths.
-For each upward half-edge $e$ we generate each site $J$ based on the beading $B = B^{v_1^e}$:
-\begin{align*}
-J &= \{ v, w, i \} \\ 
-v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
-w &= w_i^B
-% \\ i^J &= i
-\end{align*}
-for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
-See \cref{site_placement}.
-We store all sites of an edge in a mapping from edge to a list of sites.
-
-\begin{figure}
-\centering
-\setlength{\figheight}{.29\columnwidth}
-\begin{subfigure}{0.14\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
-\caption{Beadings}\label{trapezoid_beading_beading}
-\end{subfigure}
-\begin{subfigure}{0.5\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
-\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
-\end{subfigure}
-\begin{subfigure}{0.34\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
-\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
-\end{subfigure}
-\caption{
-Applying beadings to generate sites along trapezoids.
-\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
-\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
-\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
-No sites will be generated along marked edges.
-Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
-}
-\label{site_placement}
-\end{figure}
-
-We then generate extrusion segments for each trapezoid by connecting together the sites of the same index.
-See \cref{segment_generation}.
-If the amount of sites on both sides of the trapezoid is not the same then this trapezoid is in a transition and we leave one inner site unconnected.
-
-Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $b^\wedge$ in a central region coincide with a slicing height.
-When the bead count $b^\wedge$ is even, the ridge will be sliced as normal;
-the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
-When the bead count $b^\wedge$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
-In that case we should prevent the algorithm from generating the center extrusion segment twice from the trapezoids on either side of that segment.
-We therefore use some arbitrary condition to decide which one of the two to include based on the ordering of the coordinates of $v_0$ and $v_1$: $x_0 < x_1 \lor (x_0 = x_1 \land y_0 < y_1)$.
-
-\tim{Below is taken from an outdated paragraph in section 3.3 (?)}
-The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
-Each polygon in the input shape acquires it's own domain.
-The domains of hole polygons are touching the domains of the outer polygon.
-See \cref{shape_decomposition_domains}.
-
-Each of the trapezoids is connecting to a single outline polygon.
-By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
-See \cref{segment_generation}.
-In a final step we connect the ends of polylines together, so that the final toolpaths contain both polygons and polylines.
-
-\begin{figure}
-\centering
-\setlength{\figheight}{.3\columnwidth}
-\begin{subfigure}{.3\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/domains.pdf}
-\caption{Polygon domains}\label{shape_decomposition_domains}
-\end{subfigure}
-\begin{subfigure}{.6\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/segment_generation.pdf}
-\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
-\end{subfigure}
-\caption{
-Generating toolpaths on a part of the test outline shape by chaining together extrusion segments along each polygon domain.
-Each edge is assigned toolpath sites (yellow) which are connected together as shown in the singled out trapezoid.
-By following the trapezoids along the domain (cyan) of a single outline polygon,
-the extrusion segments can efficiently be connected into existing polyline toolpaths (light and dark gray).
-}
-\label{segment_generation}
-\end{figure}
-
-Around the transition locations and around nodes with odd bead count and more than two marked edges attached there will be intersections in the toolpaths.
-Such intersections cause overfill because the nozzle passes the location multiple times.
-We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline which ends in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
-This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.
-See \cref{polyline_reduction}.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.35\columnwidth}
-\begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth]{sources/method/polyline_reduction_before}
-\caption{No reduction}
-\end{subfigure}
-\begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth]{sources/method/polyline_reduction_after}
-\caption{Reduction}
-\end{subfigure}
-\caption{
-Reducing polyline toolpaths away from intersections in order to prevent overfill.
-Toolpath locations in black, underfill in azure and overfill in orange.
-}
-\label{polyline_reduction}
-\end{figure}

### 2019-08-28 4_method.tex
3.1 - 3.3 Jun

@@
 
-The edges generated from MAT can be classified into three types: (a) straight edge generated from two line segments in the outline polygons, (b) parabolic edge resulting from an outline vertex and a line segment in the outline, and (c) straight edge resulting from two outline vertices.
-Type-b and type-c edges are discretized into pieces with a length up to $d^\text{discretization}$.
+The edges generated from MAT can be classified into three types: (a) line-line edge -- straight edge generated from two line segments in the outline polygons, (b) vertex-line edge -- parabolic edge resulting from an outline vertex and a line segment in the outline, and (c) vertex-vertex edge -- straight edge resulting from two outline vertices.
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to $d^\text{discretization}$.
 This allows to approximate the feature radius in between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 
@@
 
-The significance of the three types of medial axis edges is 
+To avoid evaluating the bisection angle at any location on all edges, we devise an efficient measure which operates only on the two nodes of an edge.
 Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
@@
 This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
-For line-vertex regions and vertex-vertex regions only a portion of the region may be significant.
-We therefore introduce nodes at the boundaries of the significant portion during the construction of the ST.
+For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
+We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \cref{edge_discretization}).
 The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.
-
-We calculate the location $l$ of the boundary between a significant and nonsignificant portion of an edge analytically.
-For example, the parabolic MAT edge generated from the outline vertex $(0,1)$ and an outline segment aligned with the X-axis follows $y(x) = \nicefrac12 x^2$ and $R(x) = y(x)$.
-We can determine the significant portion $[-x_\text{bound}, x_\text{bound}]$ by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$, which is $ | x_\text{bound} | = (\tan(\alpha_\text{max} / 2))^{-1}$.
-Similarly, a MAT edge generated from two vertices at $(0,0)$ and $(0,1)$ follows $y(x) = \nicefrac12$ and $R(x) = \sqrt{\nicefrac14 + x^2}$.
-The boundaries of significance are given by $ | x_\text{bound} | = \nicefrac12 (\tan(\alpha_\text{max} / 2))^{-1}$.
-From these we can derive the locations $l = (\pm x_\text{bound}, y(x_\text{bound}))$.
-These specific cases can easily be transformed into all possible cases using scaling and rotation operations.
-\jun{TODO}
 

### 2019-08-28 4_method.tex
Tim: rewrite 3.5

@@
 We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
-For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads as:
+For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
 \begin{align*}
     %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
-    B &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
+    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
     w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
@@
 
+\paragraph{Beading interpolation}
+The beading is defined in terms of an integer number of beads, while we have assigned a fractional bead count to nodes within a transition region.
+In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead width and location of the first and last $n/2$ lines between a beading $B^V$ based on $n$ and a beading $B^W$ based on $n+1$ (see \cref{beading_interpolation}).
+Such interpolation is also used to deal with beading conflicts (see \cref{beading_conflict_problem}).
+We therefore also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
+and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.
+
+\paragraph{Beading propagation}
+The beading information is then broadcasted throughout the ST from central regions outward,
+so that each unmarked node $v$ knows the beading of the marked node on top of the ramp on which $v$ is placed.
+We first broadcast the beading information upward from all marked nodes,
+so that we can then deal with beading conflicts in a downward phase.
+This the downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
+
+\iffalse
 The beading information will be used in the next phase to directly generate the sites of the toolpaths.
@@
 
+\fi
+
 \begin{figure}\centering
@@
 \end{algorithm}
+
+\fi
 

### 2019-08-28 4_method.tex
merge significance measure and properteis figures

@@
 \centering
-\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
+\setlength{\figheight}{.3\columnwidth}
+\begin{subfigure}{0.45\columnwidth} \centering
+\includegraphics[height=\figheight]{sources/method/naive_overfill_underfill.pdf}
+\caption{Over- and underfill}\label{naive_overfill_underfill}
+\end{subfigure}
+\begin{subfigure}{0.45\columnwidth} \centering
+\includegraphics[height=.8\figheight]{sources/method/significance_properties.pdf}
+\caption{Significance measure}\label{distance_based_angles}
+\end{subfigure}
 \caption{
-Overfill and underfill areas in a simple toolpathing using a uniform bead width $w$ for a wedge area with vertex angle $\beta$.
-The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
-The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
+Properties of the significance measure along a skeletal edge (red) generated from two polygon lines (black) using the properties of inscribed circles (gray) and their radii (dashed).
+\subref{naive_overfill_underfill}
+The size of overfill (orange) and underfill areas (azure) for the uniform toolpathing technique can be calculated from the bisector angle.
+% $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
+\subref{distance_based_angles}
+The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
 }
-\label{naive_overfill_underfill}
 \end{figure}
@@
 The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.
-
-\begin{figure} \centering
-\newlength{\significancePropertiesHeight}
-\setlength{\significancePropertiesHeight}{.25\columnwidth}
-\begin{subfigure}{0.35\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
-\caption{Significance}
-\label{distance_based_angles}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
-\caption{Distance}
-\label{distance_ratio_limit}
-\end{subfigure}
-\begin{subfigure}{0.3\columnwidth} \centering
-\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
-\caption{Upward edge}
-\label{branch_upward_edge_property}
-\end{subfigure}
-\caption{
-Properties of feature radius $R$.
-Part of outline shape in thick black,
-ST edges in red,
-inscribed circle in gray,
-radii in dashed lines.
-\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
-\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
-\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
-}
-\end{figure}
 
@@
 
-\iffalse
 In order to create an interpolated beading $B = xB^V + (1-x) B^W$, for some $0<x<1$
@@
 
+\iffalse
 % \subsubsection{Beading propagation}\label{section_beading_conflicts}
@@
 \subsection{Toolpath extraction}\label{sec_toolpath_extraction}
-Now that each node has a beading associated with it we can apply the beading to generate the sites of the toolpaths.
-For each upward half-edge $e$ we generate each site $J$ based on the beading $B = B^{v_1^e}$:
+Now that each node has been assigned a beading we proceed to generate the sites along its support edge which define the toolpath.
+For each upward half-edge \jun{half-edge?} $\overrightarrow{v_0 v_1}$ we decide the location ($v$), width ($w$) of the $i$-th site $J$ based on the beading $B = B^{v_1}$:
 \begin{align*}
 J &= \{ v, w, i \} \\ 
-v &= v_1^e + (v_0^e - v_1^e) \frac{R(v_1^e) - l_i^B}{R(v_1^e) - R(v_0^e)} \\ 
+v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
 w &= w_i^B
@@
 \end{align*}
-for any $i$ for which $R(v_0^e) < l_i^B \leq R(v_1^e)$.
+for any $i$ for which $R(v_0) < l_i^B \leq R(v_1)$.
 See \cref{site_placement}.

### 2019-08-28 20_dataset.tex
redo dataset: smaller table

@@
 \caption{3D models used for validation}\label{dataset_description}
+\newcommand{\ssize}{\footnotesize}
 \begin{tabular}{l l l}
-Name & Author & License \\
+Model Name & Author \\
 \hline
-\href{	https://www.thingiverse.com/thing:26555	}{	AirCasting Air Monitor Casing	} & 	HabitatMap	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:3629434	}{	Air hose splitter	} & 	frizinko	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:1155772	}{	Al Hamra Tower	} & 	TurnerConstructionCompany	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:1498967	}{	canon NP-E3 battery cap	} & 	kosuyoung	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:3567409	}{	David	} & 	Thunk3D	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:3132621	}{	Deck Assembly Tool, Plank Screwing Tool	} & 	PSomeone	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:2920060	}{	Ender 3 Cable Chain	} & 	johnniewhiskey	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:2993875	}{	Ergonomic Hacksaw Handle	} & 	mmOne	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:2513922	}{	Gap measurement tool	} & 	ravm84	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:1673030	}{	G-Clamp fully printable	} & 	johann517	 & 	CC-A	\\
-\href{	https://www.youmagine.com/designs/gyroid	}{	Gyroid	} & 	Tim Kuipers	 & 	PD	\\
-\href{	https://www.thingiverse.com/thing:1327093	}{	3D Printable Jet Engine	} & 	CATIAV5FTW	 & 	CC-NC	\\
-\href{	https://www.thingiverse.com/thing:2752165	}{	Lawn Mower Throttle Replacement	} & 	Spammington	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:2854328	}{	OpenRC F1 Internal gear box mod	} & 	intoxikated	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:3592328	}{	PCB Test Fixture	} & 	JMadison	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:1078865	}{	Pioneer Radio Holder for Ford Focus	} & 	Perugino	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:34596	}{	Replicator Dual Fan Mount	} & 	aubenc	 & 	PD	\\
-\href{	https://www.thingiverse.com/thing:3754728	}{	Atuador vers\~ao 2 * actuator version 2	} & 	Caroline Holanda	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:1595179	}{	TE Pocket Operator Hard case	} & 	Salvation76	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:3682303	}{	Screw sizer	} & 	Pierrolalune63	 & 	CC-NC	\\
-\href{	http://homepage.tudelft.nl/z0s1z/projects/2017-bone-infill.html	}{	Bone-like optimized infill	} & 	Jun Wu	 & 	CC-A	\\
-\href{	https://www.thingiverse.com/thing:26244	}{	Two-Story Spec House	} & 	pwc-phil	 & 	CC-A	\\
+\href{https://www.thingiverse.com/thing:26555}{\ssize AirCasting Air Monitor Casing} & \ssize HabitatMap\\
+\href{https://www.thingiverse.com/thing:3629434}{\ssize Air hose splitter} & \ssize frizinko\\
+\href{https://www.thingiverse.com/thing:1155772}{\ssize Al Hamra Tower} & \ssize TurnerConstructionCompany\\
+\href{https://www.thingiverse.com/thing:1498967}{\ssize canon NP-E3 battery cap} & \ssize kosuyoung\\
+\href{https://www.thingiverse.com/thing:3567409}{\ssize David} & \ssize Thunk3D\\
+\href{https://www.thingiverse.com/thing:3132621}{\ssize Deck Assembly Tool \comment{, Plank Screwing Tool}} & \ssize PSomeone\\
+\href{https://www.thingiverse.com/thing:2920060}{\ssize Ender 3 Cable Chain} & \ssize johnniewhiskey\\
+\href{https://www.thingiverse.com/thing:2993875}{\ssize Ergonomic Hacksaw Handle} & \ssize mmOne\\
+\href{https://www.thingiverse.com/thing:2513922}{\ssize Gap measurement tool} & \ssize ravm84\\
+\href{https://www.thingiverse.com/thing:1673030}{\ssize G-Clamp fully printable} & \ssize johann517\\
+\href{https://www.youmagine.com/designs/gyroid}{\ssize Gyroid} & \ssize Tim Kuipers\\
+\href{https://www.thingiverse.com/thing:1327093}{\ssize 3D Printable Jet Engine} & \ssize CATIAV5FTW\\
+\href{https://www.thingiverse.com/thing:2752165}{\ssize Lawn Mower Throttle Replacement} & \ssize Spammington\\
+\href{https://www.thingiverse.com/thing:2854328}{\ssize OpenRC F1 Internal gear box mod} & \ssize intoxikated\\
+\href{https://www.thingiverse.com/thing:3592328}{\ssize PCB Test Fixture} & \ssize JMadison\\
+\href{https://www.thingiverse.com/thing:1078865}{\ssize Pioneer Radio Holder for Ford Focus} & \ssize Perugino\\
+\href{https://www.thingiverse.com/thing:34596}{\ssize Replicator Dual Fan Mount} & \ssize aubenc\\
+\href{https://www.thingiverse.com/thing:3754728}{\ssize Atuador versão 2 * actuator version 2} & \ssize Caroline Holanda\\
+\href{https://www.thingiverse.com/thing:1595179}{\ssize TE Pocket Operator Hard case} & \ssize Salvation76\\
+\href{https://www.thingiverse.com/thing:3682303}{\ssize Screw sizer} & \ssize Pierrolalune63\\
+\href{http://homepage.tudelft.nl/z0s1z/projects/2017-bone-infill.html}{\ssize Bone-like optimized infill} & \ssize Jun Wu\\
+\href{https://www.thingiverse.com/thing:26244}{\ssize Two-Story Spec House} & \ssize pwc-phil\\
+
 \end{tabular}

### 2019-08-28 4_method.tex
lil update to appendix reference

--- 2019-08-28 4_method.tex
@@
 For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
-We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \cref{edge_discretization}).
+We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \ref{edge_discretization}).
 The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.

### 2019-08-28 1_intro.tex
'beading strategy' ==> 'beading scheme'
add references in intro

@@
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
-Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{}, topology optimized structures~\cite{} and infill structures~\cite{}.
+Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Liu2019a}, topology optimized structures~\cite{Zong2019,Wu2019a,Cheng2019} and regular honeycomb structures~\cite{Al-Ketan2018,Maskery2018}.
 Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
@@
 \item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
-\item A specific beading strategy function for this framework for:
+\item A specific beading scheme function for this framework for:
 \begin{itemize}

### 2019-08-28 4_method.tex
redo polygon domains figure
Tim: give formula for smoothed bead count and some other small stuff

@@
 \includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
-\caption{Skeletal Trapezoids}\label{shape_decomposition_st}
+\caption{Skeletal Trapezoidation}\label{shape_decomposition_st}
 \end{subfigure}
@@
 
-The edges generated from MAT can be classified into three types: (a) line-line edge -- straight edge generated from two line segments in the outline polygons, (b) vertex-line edge -- parabolic edge resulting from an outline vertex and a line segment in the outline, and (c) vertex-vertex edge -- straight edge resulting from two outline vertices.
+The edges generated by the MAT can be classified into three types:
+\begin{enumerate*}
+\item line-line edge -- straight edge generated from two line segments in the outline polygons,
+\item vertex-line edge -- parabolic edge resulting from an outline vertex and a line segment in the outline, and 
+\item vertex-vertex edge -- straight edge resulting from two outline vertices.
+\end{enumerate*}
 The vertex-line and vertex-vertex edges are discretized into pieces with a length up to $d^\text{discretization}$.
@@
 \begin{equation}
-    b^\sim_v = 2 R(v) / w^*,
+    b^\sim_v = 2 R(v) / w^*
 \label{eq:initialBeadCount}
@@
 
-To avoid evaluating the bisection angle at any location on all edges, we devise an efficient measure which operates only on the two nodes of an edge.
+To avoid evaluating the bisector angle at any location on all edges, we devise an efficient measure which operates only on the two nodes of an edge.
 Because all locations along a line-line edge have the same bisector angle we can evaluate whether the edge is significant by checking whether 
@@
 By applying $q$ to the heights of central nodes we quantize the bead count:
-$b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor$.
+\begin{equation}\label{eq_quantized_bead_count}
+b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor
+\end{equation}
+
 \iffalse
@@
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
-In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes which are in between the two ends of the transition by (re-)assigning them a fractional bead count $b^\wedge$, linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}).
+In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $b^\wedge$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
+\begin{equation}
+b^\wedge_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
+\end{equation}
+where $\Delta$ is the total distance along the edges in between two nodes.
 %This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
@@
 \setlength{\figheight}{.3\columnwidth}
-\begin{subfigure}{.3\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/domains.pdf}
+\begin{subfigure}{.5\columnwidth}\centering
+\includegraphics[width=\figheight,rotate=90]{sources/method/domains.pdf}
 \caption{Polygon domains}\label{shape_decomposition_domains}
 \end{subfigure}
-\begin{subfigure}{.6\columnwidth}\centering
+\begin{subfigure}{.45\columnwidth}\centering
 \includegraphics[height=\figheight]{sources/method/segment_generation.pdf}

### 2019-08-28 4_method.tex
reformalize beading B=(W,L) and site J => S

@@
 \begin{align*}
-    %B &= \left\{ \left( w_0 , l_0 \right), \dots, \left( w_{n-1}, l_{n-1} \right) \right\} \\
-    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
-    w_i &= 2R(v) / n  & \text{for all $i \leq n$}\\
-    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i \leq n$}
+%    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
+    B(n,d) &= \left( W(n,d), L(n,d) \right)\\
+    W(n,d) &= \left\{  w_0 , \dots, w_{n-1} \right\} \\
+    L(n,d) &= \left\{ l_0 , \dots, l_{n-1} \right\} \\
+    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
+    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i <t n$}
 \end{align*}
@@
 \subsection{Toolpath extraction}\label{sec_toolpath_extraction}
-Now that each node has been assigned a beading we proceed to generate the sites along its support edge which define the toolpath.
-For each upward half-edge \jun{half-edge?} $\overrightarrow{v_0 v_1}$ we decide the location ($v$), width ($w$) of the $i$-th site $J$ based on the beading $B = B^{v_1}$:
+Now that each node has been assigned a beading we proceed to generate the toolpath sites along the edges of the ST.
+A site $S$ consists of a location $v$ a width $w$ and an index $i$, which are computed for an edge $v_0v_1$ from the beading $B$ of the upper node $v_1$:
 \begin{align*}
-J &= \{ v, w, i \} \\ 
+S &= \{ v, w, i \} \\ 
 v &= v_1 + (v_0 - v_1) \frac{R(v_1) - l_i^B}{R(v_1) - R(v_0)} \\ 
 w &= w_i^B
-% \\ i^J &= i
+% \\ i^S &= i
 \end{align*}
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline which ends in a site $J$ we remove part of the polyline paths up to the intersection by a distance of $w^J d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
+In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
 This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.

### 2019-08-28 5_generalization.tex
reformalize beading B=(W,L) and site J => S

@@
 $$
-\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\},
+\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), B(n, d) \right\},
 $$
@@
 and
-$t_0(n)$ the transition anchor position. \jun{check whether this last one has been defined.}
-$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
+$t_0(n)$ the transition anchor position \jun{check whether this last one has been defined.}
+and
+$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$.
+%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
 \end{definition}
@@
 \item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
-\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
-\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$
+\item $B$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
+%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
+%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
+\item $W_n$ is positive, monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
 \end{enumerate}
@@
 \begin{align*}
-d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
-d_\text{max}^\text{unmarked} &= w^* \\ 
-d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
-t_\text{beading} &= w^* \\
-d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
-%
-%We use a transition anchor position of
-%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
-%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
-%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
-t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
-t(n) &= w^* \\
-\alpha_\text{max} &= \SI{135}{\degree} \\
-L(n,d)_i &= 
+\begin{array}{rlrl}
+d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}    &    t_\text{beading} &= w^* \\
+d_\text{max}^\text{unmarked} &= w^*    &    t(n) &= w^*  \\ 
+d^\text{discretization} &= \SI{0.2}{\milli\meter}    &    t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
+d_\text{max}^\text{intersection} &= \SI{75}{\percent}     &     \alpha_\text{max} &= \SI{135}{\degree} \\
+\end{array} \\
+%\end{align*}
+%\begin{align*}
+L(n,d)_i = 
 \begin{cases}
@@
 The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
-The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
-The toolpath locations $L$ ensure that beads are extruded from the center of where they end up, that the beads don't overlap and that the symmetry restrictions are met.
+The limit bisector angle $\alpha_\text{max}$ ensures thatwe don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
+The toolpath locations $L$ ensure 
+that the beads don't overlap,
+that beads are extruded from the center of where they end up
+and that the symmetry restrictions are met.
 
@@
 \paragraph{Inward distributed scheme}
-\todo{TODO: merge general distributed with inward distributed decsription.}
 The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to
@@
 %\paragraph{Inward distributed}
-For example, we can choose 
-$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
-to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
+For example, we can choose an $M$ which distributes the discrepancy over the innermost beads, and distribute most of it to the inner beads.
 See \cref{distributed_comparison}.
@@
 % and it forces most of the beads to have exactly the prefered width.
-Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
+%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
 See \cref{formula_inward_distributed}.

### 2019-08-28 6_validation.tex
reformalize beading B=(W,L) and site J => S

@@
 
-From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
+From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2 \times 10^{-5} n \log n$ seconds.
 The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.

### 2019-08-28 4_method.tex
lil: shorten beading definition
Updates from Overleaf
reintroduce t_0

@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central, we mark parts of the UoC \jun{ST?} as being central.
-The remaining is called peripheral.
+In order to prevent over- and underfill to occur in central, we mark parts of the ST as being central.
+The remainder is called peripheral.
 Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).
@@
 A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
-The transition is centered at the anchor, and its length is set to $t(n) = w^*$.
+The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
+$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$, 
+where $\Delta$ is the total distance along the edges in between two nodes.
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
@@
 \end{equation}
-where $\Delta$ is the total distance along the edges in between two nodes.
 %This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
@@
 \begin{align*}
-%    B(n,d) &= \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right)\\
-    B(n,d) &= \left( W(n,d), L(n,d) \right)\\
-    W(n,d) &= \left\{  w_0 , \dots, w_{n-1} \right\} \\
-    L(n,d) &= \left\{ l_0 , \dots, l_{n-1} \right\} \\
+    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
     w_i &= 2R(v) / n  & \text{for all $i < n$}\\
-    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i <t n$}
+    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
 \end{align*}

### 2019-08-28 5_generalization.tex
better width legends
reintroduce t_0

@@
 $q(d)$ the quantization operator,
-$t(n)$ the transition length
-and
-$t_0(n)$ the transition anchor position \jun{check whether this last one has been defined.}
+$t(n)$ the transition length,
+$t_0(n)$ the transition anchor position
 and
@@
 \begin{subfigure}{.1\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
+\includegraphics[height=\figheight]{sources/validation/widths_legend_small.pdf}
 \end{subfigure}

### 2019-08-28 0_main.tex
some small changes at random places - Jun
3.1 - 3.3 Jun
redo dataset: smaller table
Tim: redo abstract and keywords

@@
 
+	\newcommand{\comment}[1]{}
+
     \newcommand{\todo}[1]{\hl{#1}}
@@
 
-% ACM template
-%
-% Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-%
-% DOI
-%\acmDOI{10.475/123_4}
-%
-% ISBN
-%\acmISBN{123-4567-24-567/08/06}
-%
-%Conference
-%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El  Paso, Texas USA}
-%\acmYear{1997}
-%\copyrightyear{2016}
-%
-%\acmPrice{15.00}
-
 \begin{document}
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
-FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
-The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
-Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
-An accurate dense filling is especially important for thin parts such as casings for electronics, blow molding prototypes, (architectural) models, and microstructures.
-
-A simple technique for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a uniform width.
-In the center of the outline shapes this simple technique can result in underfill regions and overfill regions as wide as the nozzle size.
-Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
-However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
-We propose a framework which allows to define beading schemes which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.
-
-Based on a skeletonization of the 2D outline shape of a single layer we generate a 3D surface mesh, the union of cones.
-By slicing the surface at regular heights we obtain contour parallel toolpaths which cover the 2D area of a single layer.
-The heights of the 3D mesh are first altered:
-the heights at central ridges in the 3D surface are quantized in order to prevent over- and underfill
-and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.
-
-Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading schemes.
-We show that we can define a scheme which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
-We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.
+By densely filling consecutive 2D layers with contour-following extrusion toolpaths, FDM can produce parts with high stiffness,
+which is especially important for thin parts such as blow molding prototypes and microstructures.
+%
+Existing approaches using uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape.
+Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center.
+Our framework makes it possible to distribute the workload of the alterations over larger regions farther from the center.
+Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
+By carefully formulating various beading schemes for our framework we can emulate existing approaches and we propose a novel approach which incluences a larger region of toolpaths so that the toolpaths are altered less severely.
+%
+This approach reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
 \end{abstract}
@@
 
-%\keywords{Space-filling Curve, Fractal, Dithering} % ACM
-\begin{keyword} % SPM
-Toolpath, 3D printing, adaptive width, underfill
+\begin{keyword} 
+Adaptive extrusion width, Tool path generation, Additive manufacturing, Geometrical accuracy, Medial axis transform, Polygon offsetting
 \end{keyword}
@@
 
- \temp{%Table of contents just for reviewing purposes
- \tableofcontents
- }
+%  \temp{%Table of contents just for reviewing purposes
+%  \tableofcontents
+%  }
 
@@
 
+\input{19_edge_discretization}
 \input{20_dataset}

### 2019-08-28 5_generalization.tex
better describe boundary conditions in beading scheme

@@
 \begin{enumerate}
-\item $\alpha_\text{max}$ is viable: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
-\item $B$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
+\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
+\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
 %\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$

### 2019-08-28 6_validation.tex
better width legends
remove gMAT print for now

@@
 \vspace{4.7cm}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
+\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.pdf}
 \end{subfigure}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
+%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
+%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
+%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
 \includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}

### 2019-08-28 4_method.tex
change b~ b- b^ to \tilde{b} \bar{b} \hat{b}

@@
 As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
-The heights $b^\sim$ at these elements are then quantized to an integer number of beads $b^\neg$.
-To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $b^\wedge$ in between (\cref{sec_central_height_adjustment}).
+The heights $\tilde{b}$ at these elements are then quantized to an integer number of beads $\bar{b}$.
+To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $\hat{b}$ in between (\cref{sec_central_height_adjustment}).
 The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
@@
 \begin{equation}
-    b^\sim_v = 2 R(v) / w^*
+    \tilde{b}_v = 2 R(v) / w^*
 \label{eq:initialBeadCount}
@@
 Now that we have identified and marked the central regions we quantize their heights.
-We first quantize the initial bead count $b^\sim$ into an integer bead count $b^\neg$ at the marked nodes using a quantization operator $q$,
+We first quantize the initial bead count $\tilde{b}$ into an integer bead count $\bar{b}$ at the marked nodes using a quantization operator $q$,
 then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
-and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $b^\wedge$ along the smooth transition.
+and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $\hat{b}$ along the smooth transition.
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}
@@
 \begin{equation}\label{eq_quantized_bead_count}
-b^\neg_v = q(2R(v)) = \left\lfloor b^\sim_v + \nicefrac12 \right\rfloor
+\bar{b}_v = q(2R(v)) = \left\lfloor \tilde{b}_v + \nicefrac12 \right\rfloor
 \end{equation}
@@
 \paragraph{Transition anchors}
-For a marked edge which connects nodes $v_0$ and $v_1$ with $b^\neg_{v_0} \le n < b^\neg_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
+For a marked edge which connects nodes $v_0$ and $v_1$ with $\bar{b}_{v_0} \le n < \bar{b}_{v_1}$, we determine the \emph{transition anchor locations} at which the bead count transitions from $n$ to $n+1$.
 To this end, we introduce the function 
@@
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
-In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $b^\wedge$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
+In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
 \begin{equation}
-b^\wedge_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
+\hat{b}_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
 \end{equation}
@@
 We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
-For our distributed beading scheme we define the beading for a central node $v$ with $n = b^\wedge_v$ beads and a diameter $d = 2R(v)$  as:
+For our distributed beading scheme we define the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
 \begin{align*}
@@
 \ForAll{$v \in$ nodes}
-	\If {marked($v$)} $\text{map}[v] = (0, B(b^\wedge_v, 2 R(v)))$ \EndIf
+	\If {marked($v$)} $\text{map}[v] = (0, B(\hat{b}_v, 2 R(v)))$ \EndIf
 \EndFor
@@
 
-Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $b^\wedge$ in a central region coincide with a slicing height.
-When the bead count $b^\wedge$ is even, the ridge will be sliced as normal;
+Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $\hat{b}$ in a central region coincide with a slicing height.
+When the bead count $\hat{b}$ is even, the ridge will be sliced as normal;
 the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
-When the bead count $b^\wedge$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
+When the bead count $\hat{b}$ is odd, the ridge will coincide exactly with a slicing height, which results in a single polyline toolpath being generated along the middle of the feature.
 In that case we should prevent the algorithm from generating the center extrusion segment twice from the trapezoids on either side of that segment.

### 2019-08-28 10_applications.tex
place cite before dot

@@
 Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
-For example the result of a topology optimized structure can contain filaments of varying thickness \cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
+For example the result of a topology optimized structure can contain filaments of varying thickness~\cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
 Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
@@
 Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
-\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case.
-\cite{bates2018compressive}
+\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case~\cite{bates2018compressive}.
 

### 2019-08-28 1_intro.tex
place cite before dot

@@
 There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
-The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads.
-\cite{N.Turner2014,ahn2002anisotropic}
+The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
 In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.

### 2019-08-28 2_related_work.tex
'beading strategy' ==> 'beading scheme'
place cite before dot

@@
 Toolpath generation is an integral part of process planning for 3D printing.
-For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}.~\cite{Livesu2017CGF} .
+For an overview of the processing pipeline, we refer to the survey by \citeauthor{Livesu2017CGF}~\cite{Livesu2017CGF}.
 For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
@@
 A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
-To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour ~\cite{Zhao2016}. 
+To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
 Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
@@
 Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
-In this paper we propose an adaptive beading strategy to address this problem.
+In this paper we propose an adaptive beading scheme to address this problem.
 
 % the context where our method can be positioned, and some related problems in that context
-Under- and over-filling are especially problematic for thin geometric features. \citeauthor{Jin2017a} proposed the use of a wavy path pattern for thin-walled parts~\cite{Jin2017a}. 
+Under- and over-filling are especially problematic for thin geometric features.
+\citeauthor{Jin2017a} proposed the use of a wavy path pattern for thin-walled parts~\cite{Jin2017a}. 
 This pattern is intended to be sparse. 
@@
 % \subsection{Toolpath strategies}
-% Simple Zig-Zag toolpathing strategy. \cite{mcmains2000layered}
-% Patchwise Zig-Zag toolpathing strategy. \cite{Ding2014}
+% Simple Zig-Zag toolpathing strategy~\cite{mcmains2000layered}.
+% Patchwise Zig-Zag toolpathing strategy~\cite{Ding2014}.
 
-% Combining concentric toolpaths into continuous extrusion spirals. \cite{Held2009}
+% Combining concentric toolpaths into continuous extrusion spirals~\cite{Held2009}.
 
-% Fractal based toolpaths. \cite{Griffiths1994, mandal2016}
+% Fractal based toolpaths~\cite{Griffiths1994, mandal2016}.
 
@@
 % \subsection{Medial axis based toolpaths}
-% Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
+% Adjusted Medial Axis Transform (MAT) structure for only printing the outer wall, rest area to be filled using normal infill~\cite{Moesen2011}.
 % \Cref{moessen}
@@
 
-% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling. \cite{Jin2017JMS}
+% Figuring out underfilling and overfilling arteas in concentric fill and using single squigly lines to prevent overfilling~\cite{Jin2017JMS}.
 % \Cref{jin}
@@
 % Using variable width lines to fit a precise amount of lines using the MAT.
-% \cite{Ding2016a} apply the method from \cite{kao1998optimal}.
+%~\cite{Ding2016a} apply the method from~\cite{kao1998optimal}.
 % \Cref{ding}
@@
 
-% Changing extrusion rate and temperature to match a given velocity. \cite{Ertay2018}
+% Changing extrusion rate and temperature to match a given velocity~\cite{Ertay2018}.
 
 % Changing velocity in order to change extrusion rate.
-% Shortly discussed in \cite{Kuipers2018}.
+% Shortly discussed in~\cite{Kuipers2018}.
 % \todo{find another reference}

### 2019-08-28 6_validation.tex
place cite before dot

@@
 Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
+The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper~\cite{johnson2014clipper}.
 The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
@@
 The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a Vatti clipping operation \cite{Vatti2019clipping} which only keeps areas of positive winding number.
+We then add the original outline shape in reverse and perform a Vatti clipping operation~\cite{Vatti2019clipping} which only keeps areas of positive winding number.
 Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.

### 2019-08-28 8_discussion.tex
w_* => w^*
place cite before dot

@@
 \subsection{Limitations}
-In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w_*$.
+In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w^*$.
 That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
@@
 Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
-but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms. \cite{tronvoll2019investigating}
+but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms~\cite{tronvoll2019investigating}.
 Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

### 2019-08-28 4_method.tex
place cite before dot
Tim: rewrite Beading intro

@@
 % These offsets can be generated from the medial axis transform (MAT).
-% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape.
-\cite{blum1967transformation}
+% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape~\cite{blum1967transformation}.
 % The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
-% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}
+% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing~\cite{eiamsa2003toward}.
 
@@
 %See \cref{shape_decomposition_datastructure}.
-%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous \cite{blum1967transformation}
+%Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous~\cite{blum1967transformation}
 %The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
@@
 The union of all such cones forms a 3D solid volume. 
-The medial axis can thus also be interpreted as ribs of the surface of the union of cones.~\cite{blum1967transformation}
+The medial axis can thus also be interpreted as ribs of the surface of the union of cones~\cite{blum1967transformation}.
 
@@
 \subsection{Beading}\label{sec_peripheral_height_adjustment}
-
-Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e.
-the periphery, and slice the resulting mesh into isocontour toolpaths.
-The peripheral heights could be determined in a plethora of ways according to various beading schemes.
-The ramps from the outline shape to the center might have various curves,
-but for our example we use straight ramps, just like the original UoC.
-See \cref{peripheral_heights}.
-Mapping an original cone at apex $v$ to a cone with a height equal to the prescribed bead count $b$ of the central region is simply a matter of multiplying the $R$ values by $b / R(v)$.
+Now that we have determined the bead counts in the central regions we will describe how the peripheral regions are handled.
+Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
+while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes (see \cref{peripheral_heights}).
+Instead we determine the radial distance to the boundary at which each bead should occur.
+Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, startign from the outer bead and ending in the center.
+Together with a sequence of bead widths $W$ these form what we call a \emph{beading} $B$.
+For our distributed beading scheme we compute the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
+\begin{align*}
+    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
+    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
+    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
+\end{align*}
+where
+$w_i$ and $l_i$ are the width and location of the $i$th bead,
+respectively, counting from the outline inward.
+An example beading is visualized in the top of \cref{beading_interpolation}:
+$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
 
@@
 \end{figure}
-
-However, for the purpose of generating toolpaths we only need to define the height at the locations which will be part of a slice, rather than at all locations in the periphery.
-Instead of adjusting the height of peripheral mesh nodes, we determine the radial distances where the adjusted height coincides with a slicing height.
-In this section we will show how we can define a mapping from radial distance values to the indices of slicing heights, called a \emph{beading},
-how each beading is calculated for a central node
-and how the beadings are propagated outward to peripheral nodes.
-This helps to define an efficient slicing algorithm in \cref{sec_toolpath_extraction}.
-
-\paragraph{Beading} 
-We associate each central node $v$ with a set of radial distances for each bead along with the width of that bead, which we call the \emph{beading} $B$.
-For our distributed beading scheme we define the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
-\begin{align*}
-    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
-    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
-    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
-\end{align*}
-where
-$w_i$ and $l_i$ are the width and location of the $i$th bead,
-respectively, counting from the outline inward.
-An example beading is visualized in the top of \cref{beading_interpolation}:
-$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
 

### 2019-08-28 5_generalization.tex
simplify beading schemes

@@
 %\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item $W_n$ is positive, monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
+\item For toolpaths to be smooth we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
 \end{enumerate}
@@
 \end{figure}
-
-Because the peripheral height adjustment was described in terms of a mapping from radial distances to sites rather than adjusting the heights of peripheral nodes,
-we can introduce non-linear mappings without refining the surface mesh.
-In the simplified geometrical conceptualization of our technique we can introduce different distributions of bead widths from the center outward, by making the contours of the cones curved.
-If the UoC mesh is generated with cones which are curving inward toward the top, higher slicing planes would intersect more sparsely than lower ones, which means that the inter-bead distance and thus their width becomes larger when going inward.
-In order for the simplified geometrical approach to capture such curved shapes it would have to perform mesh refinement.
-However, our approach bypasses the peripheral height adjustment and directly generates the radial distances at the slicing heights, which means our technique generalized effortlessly.
 

### 2019-08-28 6_validation.tex
some changes in sec. 5

@@
 \section{Validation}
-In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
-The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
-We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
-We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 beading schemes discussed in \cref{sec_generalization}, namely constant bead count scheme with a bead count of $C=4$, the centered beading scheme, the evenly distributed, and the inward distributed beading scheme, using a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
+We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
+The data set is described in Appendix~\ref{dataset}.
+We sliced all models in the data set and selected 300 random slices for analysis.
+Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
+The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
 
 \subsection{Computational analysis}
-Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
-The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper~\cite{johnson2014clipper}.
+
 The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 

### 2019-08-28 4_method.tex
describe beading schemes section not as generalization section

@@
 
-This section explains how we generate toolpaths with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
-In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed beads into a general framework for generating contour parallel toolpaths using an arbitrary beading distribution scheme and we show several such beading schemes.
+This section explains how we generate toolpaths using our framework with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
+In \cref{sec_generalization} we describe how to apply the framework to different beading schemes and we show several such beading schemes.
 

### 2019-08-28 5_generalization.tex
describe beading schemes section not as generalization section

@@
-\section{Generalization}\label{sec_generalization}
+\section{Beading schemes}\label{sec_generalization}
 A critical component in toolpath generation is how to distribute the beads over the feature radius.
 While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3d printer or material.
-
-% In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
-% The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
-% Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
-% In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
-% There are several schemes one can take for determining the distribution of bead widths.
-% We will formalize several schemes and describe the set of parameters these schemes require.
 

### 2019-08-28 5_generalization.tex
make all constants a part of the beading scheme

@@
 \begin{definition}\label{beading_scheme_definition}
-The beading scheme is configured by the following set of parameters and functions:
-$$
-\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), B(n, d) \right\},
-$$
-where, as introduced in previous section, $\alpha_{\text{max}}$ is the limit bisector angle,
+The beading scheme is configured by the following set of functions and constants:
+\begin{align*}
+\{
+&q(d),
+B(n, d),
+t(n),
+t_0(n),
+\\
+&\alpha_\text{max}, 
+t_\text{beading}, 
+d_\text{max}^\text{transition}, 
+d_\text{max}^\text{unmarked}, 
+d_\text{max}^\text{intersection},
+d^\text{discretization}
+ \}
+\end{align*}
+where, as introduced in previous section,
 $q(d)$ the quantization operator,
+$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$,
 $t(n)$ the transition length,
-$t_0(n)$ the transition anchor position
+$t_0(n)$ the transition anchor position,
+$\alpha_{\text{max}}$ is the limit bisector angle,
+$t_\text{beading}$ is the beading conflict transition length,
+$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
+$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
+$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
 and
-$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$.
+$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
 %$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
@@
 %\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item For toolpaths to be smooth we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
+\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
 \end{enumerate}
@@
 \begin{align*}
-\begin{array}{rlrl}
-d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}    &    t_\text{beading} &= w^* \\
-d_\text{max}^\text{unmarked} &= w^*    &    t(n) &= w^*  \\ 
-d^\text{discretization} &= \SI{0.2}{\milli\meter}    &    t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right) \\
-d_\text{max}^\text{intersection} &= \SI{75}{\percent}     &     \alpha_\text{max} &= \SI{135}{\degree} \\
-\end{array} \\
-%\end{align*}
-%\begin{align*}
 L(n,d)_i = 
@@
 \end{cases}
+\\
+\begin{array}{rlrl}
+t_\text{beading} &= w^* 
+&
+d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
+\\
+t(n) &= w^*
+&
+d_\text{max}^\text{unmarked} &= w^*
+\\
+t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
+&
+d^\text{discretization} &= \SI{0.2}{\milli\meter}
+\\
+\alpha_\text{max} &= \SI{135}{\degree} 
+&
+d_\text{max}^\text{intersection} &= \SI{75}{\percent}
+\end{array}
+%\end{align*}
+%\begin{align*}
 \end{align*}
 
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
-The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
-The limit bisector angle $\alpha_\text{max}$ ensures thatwe don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
 The toolpath locations $L$ ensure 
@@
 and that the symmetry restrictions are met.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
+The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
+The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
 

### 2019-08-28 10_applications.tex
sec. 5 and 6. a lot of comments, good luck

--- 2019-08-26 10_applications.tex
@@
 \subsection{Applications}
-Because under- and overfill regions affect narrow parts more than wide parts, the use cases for this algorithm are centered around objects which contain thin parts.
-Although the algorithm improves performance for all parts compared to existing techniques, the enhancement is percentually larger for thin parts.
+Toolpath with varying width is particularly meaningful for narrow parts, since there the negative effect of under- and overfill is more pronounced than in wide parts.
+In extreme cases, thin features might not be filled at all.
+Therefore, our framework, while working for wide parts as well, shows most of its potential for objects which contain thin parts.
 
-\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading scheme.
-Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
-Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.
+\Cref{applications_overview} collectively shows the application of the proposed inward distributed scheme for various types of 3D model, including both thin parts (architectural models, casings, embossed text, gears and microstructures) and wide parts (larger regions (\cref{applications_case}) and organic shapes (\cref{applications_statue})).
 
-Architectural models and casings benefit from preventing very thin regions from being filled at all and from the prevention of over- and underfill within thin walls, which makes them stronger.
-Embossed text benefits from the prevention of underfill areas, which would cause various holes in top surfaces, which is detrimental to the visual quality of those top surfaces.
-Gears benefit from the preventio of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout.
+For architectural models and casings, the prevention of over- and underfill is expected to make them stronger. 
+For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
+Gears benefit from the prevention of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout.
+\jun{I don't follow the benefit for gears}
 
-Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties more closely matching homogenized mechanical properties.
-For example the result of a topology optimized structure can contain filaments of varying thickness \cite{wu2017infill} which follow a varying stress distribution (\cref{applications_bone}).
-Also microstructures with homogenous thickness in the direction perpendicular to the surface of the microstructure can result in horizontal cross-sections with varying thickness;
-\cref{applications_gyroid} shows how an angled gyroid structure with homogenous thickness results in heterogeneous outline shapes.
-Another class of microstructures consists of homogenous patterns which employ varying thickness in order to achieve a functionally graded material.
-\Cref{applications_hex} shows how the toolpathing of a hexagonal grid neatly switches between different bead counts over the volume, which prevents the jagged moves a direction parallel infill pattern would create for such a case.
-\cite{bates2018compressive}
+Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
+Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties closer to expectation.
+For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
+An angled Gyroid structure with uniform thickness results in outline shapes with varying width (\cref{applications_gyroid}).
+Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
+\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.
 

### 2019-08-28 6_validation.tex
sec. 5 and 6. a lot of comments, good luck

@@
 \section{Validation}
+\jun{section title -> Results?}
+
 We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
@@
 
-\subsection{Computational analysis}
-
-The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
-\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
-
-The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
-The number of elements in the ST is linear in the number of elements in the VD
-and all of the stages of our framework are also linear in the number of elements in the ST,
-so the total running time of our algorithm is $O(n \log n)$.
-
-From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2 \times 10^{-5} n \log n$ seconds.
-The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.
-
-% only Moessen reports on computation times, but in a weird manner
+\subsection{Computational results}
 
 \subsubsection{Accuracy}
+We first evaluate the accuracy of different beading schemes in terms of the amount of the overfill and underfill. 
+This is compared on a slice of a \jun{?} model, as shown in \cref{visualized_accuracy} (top).
+\jun{discuss this figure a bit}
+
+We further quantitatively compare the accuracy of the beading schemes on the data set. 
+The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
+The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
+This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
+
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
@@
 
-We calculated the total overfill and underfill areas of the different toolpath schemes applied on the data set. 
-The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
-The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
-
 \begin{figure*}
@@
 
-\paragraph{Smoothness of toolpaths}
+\subsubsection{Smoothness of toolpaths}
 In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
@@
 
-\subsection{Experimentation}
+\subsubsection{Computational performance}
+\cref{computime} plots the computation time for each of the 300 slices against the vertex count of the layer, comparing the uniform technique~\cite{johnson2014clipper} and our framework with the inward distributed scheme.
+For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.
+
+The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
+The other steps in our framework have a complexity of $O(n)$ or $O(m)$, where $m$ is the number of elements in the ST.
+Therefore, the total running time of our algorithm is $O(n \log n)$.
+Results in \cref{computime} conform that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.
+% The computation time of our framework is approximately five times that of the uniform technique, which puts it in the same order of magnitude.
+
+% only Moessen reports on computation times, but in a weird manner
+
+\subsection{Printing results}
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
+The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control~\cite{tronvoll2019investigating}.
+\jun{sentence too long}
+We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
 
-The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
+The prints are shown in \cref{wedge_print} and \cref{prints}.
 Because of inaccuracies in the deposition control system some of the prints show defects.
 Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
+\jun{discuss the positive aspects of the new beading by 2~3 sentences}
 

### 2019-08-28 8_discussion.tex
sec. 5 and 6. a lot of comments, good luck

@@
 \subsection{Comparison of beading schemes}
-The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
+%The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
 
 We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
-These defects surely influence the mechanical properties of the parts beyond a point that process parameters can reliably be correlated to mechanical properties of the part.
+These defects are supposed to negatively influence the mechanical properties of the parts, and exceed the point that process parameters can be reliably correlated to mechanical properties of the part.
+To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.
 
@@
 
-For an input outline shape which contains both very small and very large features, the algorithm produces bead widths which can fall outside of the range of manufacturable bead widths.
+For an input outline shape which contains both very small and very large features, the algorithm \jun{which specific scheme, or our method in general?} produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
 
-If we look at \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with overfill and underfill and produces bead widths which are the optimal bead width in all locations, but in the center the bead widths are within a factor 2 off from the optimal bead width.
+In \cref{TEST_Center_accuracy} we can see that
+the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except in the center the bead widths are within a factor 2 off from the desired bead width.
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
 
-However, according to \cref{widthHistogram} the centered scheme exhibits a lot wider range of bead widths than the distributed schemes:
-the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while the standard deviation resulting from the distributed schemes is approximately \SI{14}{\micro\meter}.
+However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
+the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
 We can therefore state that the distributed schemes result in bead widths closer to the nominal widths compared to the centered scheme.
@@
 
-The inward distributed beading scheme was introduced in order to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
-The effect is difficult to see when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
+The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
+This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
 
 However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
-Also, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
-Therefore, when using the Inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
+Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
+Therefore, when using the inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
 
 \subsection{Theoretical analysis}
+\jun{I suggest to dissolve this subsection. see comments and suggested changes below.}
+
 In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
@@
 See \cref{naive_overfill_underfill}
+\jun{this is in the method, and thus can be removed.}
 Note also that contrary to some literature we do not remove edges from the skeleton, but leave it intact.
@@
 In that sense our framework provides an exact solution space.
+\jun{what is a solution space? what is the benefit of using an exact and full feature descriptor regarding toolpath accuracy, uniformity and smoothness?}
 
@@
 However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
+\jun{this could be mentioned somewhere in the method, shortly.
+The uniform approach can also be thought of using the distance field, is it less robust than ours?}
 Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there was no such edge in that region.
 The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
+\jun{this could be integrated in paragraph Smooth transitions to motivate the fractional bead count}
 
@@
 and it also allows for some parallelism during the computation of the toolpaths.
+\jun{This could mentioned in paragraph Computational performance. This potentially could be parallelized for speeding up.}
 
 \subsection{Limitations}
-In the beading schemes we discussed we set the length of the smoothed transitions to $t(n) = w^*$.
-That might demand changes in cross-sectional area as high as \SI{200}{\percent} over a distance as small as the nozzle size,
-which might be difficult to accurately manufacture on some hardware.
-While changing the cross-sectional area of the bead could be implemented by changing the movement speed, the movement speed is also constrained by acceleration considerations around sites in the toolpath, so this approach is inherently limited.
+\jun{postpone this subsection to Applications}
+We note that printing with varying width is not the current standard in FDM printing.
+It calls for adaptations and developments in printers and the workflow.
+In the beading schemes we set a transition length of $t(n) = w^*$.
+That might demand \jun{can we say, "while it rarely happens, it may demand ..."} changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size.
+This is challenging for some hardware.
+The effect of varying the movement speed to change the cross-sectional area is limited, since the movement speed is constrained by acceleration considerations around sites in the toolpath.
 Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
-Using a filament feeder directly mounted on the print head (a.k.a. direct drive) is certainly a large improvement over Bowden style FDM printers.,
-but still some control system is required in order to accurately change the volumetric flow rate such as advance algorithms~\cite{tronvoll2019investigating}.
-Still inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
+Using a filament feeder directly mounted on the print head (a.k.a.
+direct drive) is certainly a large improvement \jun{in terms of what?
+can we say, "...
+shall improve ...
+significantly"} over Bowden style FDM printers,
+but still requires some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
+Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
+We expect the development in printing hardware will address these challenges in the future.
 
-Another limiting factor in the adoption of adaptive bead width is that Gcode -- a common file format for storing machine instructions -- does not support  moves with varying cross-sectional area.
-A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across the extrusion move.
-This could be mediated by discretizing a variable width extrusion segment into smaller segments, but that approach might still result in some small inaccuracies.
-Ideally the Gcode language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
+Another limiting factor in the adoption of adaptive bead width is G-code which stores machine instructions. G-code does not support moves with varying cross-sectional area.
+A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across \jun{along?} the extrusion move.
+A workaround is to approximate a variable width extrusion segment by smaller segments with constant width. This, nevertheless, introduces errors.
+Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
 
-Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
-Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemes.
-An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
-This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.
+% Taking a broader perspective, we note that our proposed inward distributed scheme is a pragmatic solution.
+% Rather than deriving some optimal beading scheme from a clear specification of the objective, we propose some arbitrary inward distributed beading scheme and show that it is better than the other beading schemes.
+% An optimal beading scheme can be derived if the objective is formalized terms of a unambiguous fitness function, but that would depend on the specific hardware setup and application for which toolpaths are generated.
+% This manuscript is therefore limited to showing the flexibility and versatility of the framework, rather than deriving an optimal beading scheme.

### 2019-08-29 4_method.tex
make all constants a part of the beading scheme
put frame around cropped images

@@
 \begin{subfigure}{0.45\columnwidth} \centering
-\includegraphics[height=\figheight]{sources/method/naive_overfill_underfill.pdf}
+\includegraphics[height=\figheight,frame]{sources/method/naive_overfill_underfill.pdf}
 \caption{Over- and underfill}\label{naive_overfill_underfill}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/beading_conflict_3D.png}
+\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_3D.png}
 \includegraphics[height=\figheight]{sources/method/beading_conflict.pdf}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/beading_conflict_solved_3D.png}
+\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_solved_3D.png}
 \includegraphics[height=\figheight]{sources/method/beading_conflict_solved.pdf}
@@
 \begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth]{sources/method/polyline_reduction_before}
+\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_before}
 \caption{No reduction}
@@
 \begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth]{sources/method/polyline_reduction_after}
+\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_after}
 \caption{Reduction}

### 2019-08-29 5_generalization.tex
put frame around cropped images

@@
 \centering
-\includegraphics[width=.4\columnwidth]{sources/method/transition_length_limit.pdf}
+\includegraphics[width=.4\columnwidth,frame]{sources/method/transition_length_limit.pdf}
 \caption{
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
+\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_evenly.png}
 \caption{Evenly distributed}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
+\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_inward.png}
 \caption{Inward distributed}

### 2019-08-29 4_method.tex
shorten paragraph about polygon domains

@@
 
-\tim{Below is taken from an outdated paragraph in section 3.3 (?)}
-The trapezoids are classified as belonging to a specific domain following \citeauthor{Ding2016a}.
-Each polygon in the input shape acquires it's own domain.
-The domains of hole polygons are touching the domains of the outer polygon.
-See \cref{shape_decomposition_domains}.
-
-Each of the trapezoids is connecting to a single outline polygon.
-By traversing the trapezoids in the domain of each outline polygon in order we can efficiently connect all segments into polylines.
+All trapezoids in the ST can be assigned to separate domains, corresponding to which boundary polygon they are connected to (see \cref{shape_decomposition_domains})~\cite{Ding2016a}.
+By traversing the trapezoids in per domain in order we can efficiently connect all segments into polylines.
 See \cref{segment_generation}.

### 2019-08-29 0_main.tex
new title
restructure results and discussion

@@
 
-%\title{A robust framework for variable extrusion width concentric toolpath generation}
-\title{An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing}
+\title{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}
 
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
-By densely filling consecutive 2D layers with contour-following extrusion toolpaths, FDM can produce parts with high stiffness,
-which is especially important for thin parts such as blow molding prototypes and microstructures.
+By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
 %
-Existing approaches using uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape.
-Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center.
-Our framework makes it possible to distribute the workload of the alterations over larger regions farther from the center.
-Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
-By carefully formulating various beading schemes for our framework we can emulate existing approaches and we propose a novel approach which incluences a larger region of toolpaths so that the toolpaths are altered less severely.
+Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as blow molding prototypes \jun{this seems not discussed in the main text} and microstructures.
+Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center \jun{only widths in the center?}.
+%Our framework makes it possible to distribute the workload of \jun{is the sentence complete if we delete worklaod of} the alterations over larger regions farther from the center. 
+In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
+%Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
+We present various schemes to decide the number of beads and their widths from the center outward.
+%By carefully formulating various beading schemes for our framework we can emulate existing approaches.
+Furthermore, we propose a novel scheme which influences a larger region of toolpaths so that the toolpaths are altered less severely. \jun{I miss a better summary of this inner distribution scheme.}
 %
-This approach reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
+This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
 \end{abstract}
@@
 
-\input{10_applications}
-
 \input{12_conclusions_future_work}

### 2019-08-29 25_accuracy.tex
move accuracy calculation to appendix

--- 2019-08-28 6_validation.tex
@@
-\section{Validation}
-We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
-The data set is described in Appendix~\ref{dataset}.
-We sliced all models in the data set and selected 300 random slices for analysis.
-Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
-The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
+\section{Accuracy calculation}\label{accuracy_calculation}
 
-\subsection{Computational analysis}
-
-The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed scheme. 
-\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.
-
-The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
-The number of elements in the ST is linear in the number of elements in the VD
-and all of the stages of our framework are also linear in the number of elements in the ST,
-so the total running time of our algorithm is $O(n \log n)$.
-
-From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2 \times 10^{-5} n \log n$ seconds.
-The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.
-
-% only Moessen reports on computation times, but in a weird manner
-
-\subsubsection{Accuracy}
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
@@
 \caption{
-Extruded area of two extrusion extrusion segments.
+Extruded area of two extrusion segments.
 Red areas signify doubly extruded areas.
@@
 The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.
-
-\begin{figure*}
-\centering
-\setlength{\figwidth}{0.19\textwidth}
-\setlength{\figheight}{0.283\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
-\caption{Uniform}\label{TEST_naive_accuracy}
-\end{subfigure}
-%\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
-%\caption{Single}\label{TEST_SingleBead_accuracy}
-%\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
-\caption{Constant}\label{TEST_Constant_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
-\caption{Centered}\label{TEST_Center_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
-\caption{Distributed}\label{TEST_Distributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
-\caption{Inward}\label{TEST_InwardDistributed_accuracy}
-\end{subfigure}
-\begin{subfigure}{.04\columnwidth}\centering
-\vspace{4.7cm}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.pdf}
-\end{subfigure}
-\caption{
-Visualizing the overfills and underfills and the widths for various beading schemes.
-Extrusion beads in gray tones,
-overfill in orange,
-underfill in azure,
-narrow beads in blue
-and wide beads in red.
-}
-\label{visualized_accuracy}
-\end{figure*}
-
-We calculated the total overfill and underfill areas of the different toolpath schemes applied on the data set. 
-The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
-The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
-
-\begin{figure*}
-\centering
-\setlength{\figheight}{0.22\textwidth}
-\setlength{\figwidth}{0.31\textwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
-\caption{Computation time}
-\label{computime}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Extrusion widths}
-\label{widthHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/indexedwidths2.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
-\caption{Extrusion width per index}
-\label{widthIndexedHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
-\caption{Over- and underfill}
-\label{over_underfill}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
-\caption{Site angles}
-\label{smoothness}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/smoothnessNoTransition.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/smoothnessNoTransition.pdf}
-\caption{Site angles without smoothing}
-\label{smoothnessNoTransition}
-\end{subfigure}
-
-\caption{
-Results of computational analysis of the results from applying the uniform width technique and various beading schemes using our framework to the data set.
-Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
-}
-\end{figure*}
-
-\subsubsection{Uniformity}
-Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
-A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
-Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
-Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
-We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
-
-To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
-at intervals of \SI{1}{\micro\meter} along the toolpath.
-From these sampled values, we calculated the mean bead width, and standard deviation per scheme.
-\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
-We found that the mean width of the inward distributed and evenly distributed schemes is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
-These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less and infrequently from the nominal bead width compared to the other schemes.
-We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
-The outer beads of the inward distributed scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the evenly distributed scheme more often extrudes widths that deviate from the nominal width.
-
-\paragraph{Smoothness of toolpaths}
-In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We measured the angle between consecutive extrusion segments generated by each scheme.
-The relative frequency of these angles is shown in \cref{smoothness}.
-All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
-The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
-We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
-\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}.
-
-\subsection{Experimentation}
-Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control.\cite{tronvoll2019investigating}
-We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, so that we avoid fluttered printing of lines thinner than the nozzle size.
-We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
-
-The resulting prints are shown in \cref{wedge_print} and \cref{prints}.
-Because of inaccuracies in the deposition control system some of the prints show defects.
-Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
-
-\begin{figure}
-\centering
-\begin{subfigure}{\columnwidth}\centering
-\setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
-\caption{Wedge}\label{print_wedge}
-\end{subfigure}
-\caption{
-A wedge shape printed using the uniform scheme, centered scheme and the inward distributed scheme.
-The uniform and centered scheme show problems around certain model diameters.
-}
-\label{wedge_print}
-\end{figure}
-
-\begin{figure}
-\centering
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
-\caption{Uniform}\label{print_naive}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
-\caption{Centered}\label{print_center}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
-\caption{Inward distributed}\label{print_inward}
-\end{subfigure}
-\caption{
-Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
-The uniform technique produces distinct underfill areas.
-The centered scheme shows some defects due to inaccurate control of extremal deposition widths.
-The inward distributed scheme produces the least defects.
-}
-\label{prints}
-\end{figure}
-
-\iffalse
-\todo{Maybe test the following qualities:}
-\begin{itemize}
-\item visual consistency of flat top skin surface
-\item graphs of tensile tests on thin walled object
-\end{itemize}
-\fi
-
-%We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2019-08-29 6_validation.tex
move accuracy calculation to appendix

@@
 This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
-
-In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the extrusion segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
-We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
-For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position ( \cref{segment_visualization}c).
-
-%In order to print such extrusion paths accurately, we can modulate the amount of material flow per millimeter based on this visualization model.
-%See \cref{segment_visualization}.
-
-\begin{figure}
-\centering
-\setlength{\figwidth}{.25\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
-\caption{Blocky}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
-\caption{Rounded}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
-\caption{Excluded}
-\end{subfigure}
-\caption{
-Extruded area of two extrusion extrusion segments.
-Red areas signify doubly extruded areas.
-}
-\label{segment_visualization}
-\end{figure}
-
-We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
-In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
-
-The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a Vatti clipping operation~\cite{Vatti2019clipping} which only keeps areas of positive winding number.
-Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
-In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
-These triple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.
 

### 2019-08-29 6_validation.tex
redo accuracy section

@@
 \subsubsection{Accuracy}
-We first evaluate the accuracy of different beading schemes in terms of the amount of the overfill and underfill. 
-This is compared on a slice of a \jun{?} model, as shown in \cref{visualized_accuracy} (top).
-\jun{discuss this figure a bit}
+We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
+\begin{wrapfigure}{r}{.3\columnwidth}
+\centering
+\includegraphics[width=.25\columnwidth]{sources/validation/visualization_principle_rounded_excluded_single.pdf}
+\caption{
+Extrusion segments coverage.
+The hole at the end will be filled by the next extrusion segment.
+}
+\label{segment_visualization_simple}
+\end{wrapfigure}
+We construct the over- and underfill area by comparing the shapes covered by each extrusion move (\cref{segment_visualization_simple}) with each other and with the total shape of the boundary polygons.
+(For implementation details see Appendix~\ref{accuracy_calculation}.)
+This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
+there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
 
-We further quantitatively compare the accuracy of the beading schemes on the data set. 
+We compare the total area (in \si{\milli\meter\squared}) of these overfill and underfill shapes to the total area of the boundary for each sample in the data set.
 The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
-The inward distributed scheme has a calculated overfill of 0.24\% and an underfill of 0.17\%.
-This is lower compared to the uniform scheme, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.
+The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
+This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.
 

### 2019-08-29 4_method.tex
lil space to ~

@@
 For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
-We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix \ref{edge_discretization}).
+We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix~\ref{edge_discretization}).
 The significance of all edges can then accurately be evaluated using \cref{simple_significance_measure}.

### 2019-08-29 6_validation.tex
rename validation to results and discussion
Tims edits to computation time and printing results

@@
-\section{Validation}
-\jun{section title -> Results?}
+\section{Results and discussion}
 
@@
 \subsubsection{Computational performance}
-\cref{computime} plots the computation time for each of the 300 slices against the vertex count of the layer, comparing the uniform technique~\cite{johnson2014clipper} and our framework with the inward distributed scheme.
+\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
 For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.
@@
 The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
-The other steps in our framework have a complexity of $O(n)$ or $O(m)$, where $m$ is the number of elements in the ST.
+The other steps in our framework have a complexity of $O(m)$, where $m$ is the number of elements in the ST.
 Therefore, the total running time of our algorithm is $O(n \log n)$.
-Results in \cref{computime} conform that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.
-% The computation time of our framework is approximately five times that of the uniform technique, which puts it in the same order of magnitude.
-
-% only Moessen reports on computation times, but in a weird manner
+Results in \cref{computime} confirm that both our framework and the uniform technique have an expected running time of approximately $5 \times 10^{-6} n \log n$ seconds.
 
@@
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs linear advance: to gain the extra pressure required to change to a wider bead an extra amount of filament is advanced into the physical system between the filament feeder and the nozzle so that we can realize accurate adaptive deposition width control~\cite{tronvoll2019investigating}.
-\jun{sentence too long}
+The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
+gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
 We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
@@
 Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
-\jun{discuss the positive aspects of the new beading by 2~3 sentences}
+The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual performance of the print.
+Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.
+The difference between the centered and the inward distributed schemes is less pronounced.
+We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
+However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extremal bead widths.
+The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
 

### 2019-08-29 12_conclusions_future_work.tex
lil future work sentence
abstract and conclusion - Jun

@@
 In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
-Our framework is shown to be flexible, since we have shown several beading schemes which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
-Our framework is robust and local, meaning that small changes in the toolpath are caused by small local changes in the outline shape.
+Our framework is flexible, demonstrated by the several beading schemes which emulate existing techniques.
+The computation times of our framework are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
+Our framework is robust and local, meaning that small local changes in the outline shape cause only small changes in the toolpath.
 
-We have introduced the inward distributed beading scheme which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
-and instead distributes the deviation in bead width over several beads near the center of the shape.
-That way the impact of adaptive bead width on mechanical properties of the resulting print are limited.
-Moreover the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realized adaptive bead width.
+We have introduced the inward distributed beading scheme.
+It reduces the amount of beads with a width deviating from the nominal bead width by a large amount \jun{by a large amount refers to the deviation or the number of beads which deviate?}, and thus is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
+Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.
 
-The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
-On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.
+The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
+Meanwhile it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
 
 \subsection{Future work}
-The work presented here is evaluated mostly on a theoretical level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the validation of our techniques.
-Future research might be devoted to optimizing the distribution scheme to a specific hardware setup.
-If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.
+The work presented here is evaluated mostly on a computational level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the physical validation of our techniques.
+Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
+An accurate model of manufacturability, print speed, and dimensional accuracy would be valuable to fine tune the beading scheme.
+% If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.
 
-In its current form the skeleton has been used to determine toolpaths based on the local feature size.
-One direction of future research could be devoted to incorporating other information.
-We could for example make the bead widths depend on properties on the outline, such as curvature or visibility.
-We could also take into account volumetric considerations such as the toolpathing of the previous layer or some volumetric constraint defined by a functionally graded material.
+Our framework uses the skeleton to determine toolpaths based on the local feature size.
+Another direction of future research could be devoted to incorporating other information, e.g.
+properties of the outline such as curvature or visibility, toolpaths of the previous layer, and volume constraint (e.g.
+for functionally graded material).
+It might be interesting to incorporate more `horizontal' flow of information between different parts of a shape, rather than `vertically' between an outline location and a local peak or ridge.
+\jun{could this be summarized in a few words and integrated into the previous sentence?
+otherwise we could leave it out}
+% Furthermore we could also take into account volumetric considerations such as the toolpathing of the previous layer or volume constraint defined by a functionally graded material.
 

### 2019-08-29 8_discussion.tex
restructure results and discussion
Tims edits to comparison of schemes

@@
-\section{Discussion}
+%\section{Discussion}
 
 \subsection{Comparison of beading schemes}
-%The uniform beading scheme and the outer bead scheme are of little use to FDM printers, but they show the flexibility of our algorithmic framework.
-
 We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
@@
 
-%The single bead scheme solves the underfill problem in regions where the model is more thin than the nozzle size.
-%However, the scheme doesn't deal with the remaining area.
-%In our visualization we print the outline of the remaining area which exposes an overextrusion problem.
-
 The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
@@
 Note that most overfill areas occur near regions of alternating bead width. 
-
-For an input outline shape which contains both very small and very large features, the algorithm \jun{which specific scheme, or our method in general?} produces bead widths which can fall outside of the range of manufacturable bead widths.
+For an input outline shape which contains both very small and very large features, the the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
@@
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except in the center the bead widths are within a factor 2 off from the desired bead width.
+the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths are within a factor 2 off from the desired bead width.
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
@@
 
+\input{10_applications}
+
 \subsection{Limitations}

### 2019-08-29 10_applications.tex
Tims edits to limitations and applications

@@
 
-\Cref{applications_overview} collectively shows the application of the proposed inward distributed scheme for various types of 3D model, including both thin parts (architectural models, casings, embossed text, gears and microstructures) and wide parts (larger regions (\cref{applications_case}) and organic shapes (\cref{applications_statue})).
+\Cref{applications_overview} collectively shows the application of the proposed inward distributed scheme for various types of 3D model, including both thin parts (architectural models, casings, embossed text, gears and microstructures) and wide parts (\cref{applications_case}) and organic shapes (\cref{applications_statue})).
 
@@
 For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
-Gears benefit from the prevention of under- and overfill regions and the distributed bead width discrepancy in that the mechanical properties of the toolpath are more consistent throughout.
-\jun{I don't follow the benefit for gears}
+Gears benefit from the prevention of under- and overfill regions and the distributed bead widths because the more homogeneous extrusion widths cause the part to more closely match the predicted mechanical properties from some homogenization approach.
+\tim{Hopefully you understand now; could you correct the formulation of this sentence please?}
 

### 2019-08-29 8_discussion.tex
Tims edits to limitations and applications

@@
 \subsection{Limitations}
-\jun{postpone this subsection to Applications}
-We note that printing with varying width is not the current standard in FDM printing.
-It calls for adaptations and developments in printers and the workflow.
+Note that the current industry standard in FDM printing employs little to no bead width variation.
+Properly performing bead width variation calls for adaptations and developments in printers and firmware.
 In the beading schemes we set a transition length of $t(n) = w^*$.
-That might demand \jun{can we say, "while it rarely happens, it may demand ..."} changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size.
-This is challenging for some hardware.
-The effect of varying the movement speed to change the cross-sectional area is limited, since the movement speed is constrained by acceleration considerations around sites in the toolpath.
-Our schemes require a more accurate control of the volumetric flow rate (in \si{\milli\meter\cubed\per\second}).
-Using a filament feeder directly mounted on the print head (a.k.a.
-direct drive) is certainly a large improvement \jun{in terms of what?
-can we say, "...
-shall improve ...
-significantly"} over Bowden style FDM printers,
+That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
+Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath.
+Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
+Using a filament feeder directly mounted on the print head (a.k.a. direct drive) outperforms Bowden style FDM printers in terms of dynamic flow changes,
 but still requires some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
 Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
-We expect the development in printing hardware will address these challenges in the future.
+We expect that developments in printing hardware and firmware will address these challenges in the future.
 
-Another limiting factor in the adoption of adaptive bead width is G-code which stores machine instructions. G-code does not support moves with varying cross-sectional area.
-A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed across \jun{along?} the extrusion move.
-A workaround is to approximate a variable width extrusion segment by smaller segments with constant width. This, nevertheless, introduces errors.
+Another limiting factor in the adoption of adaptive bead width is the format of G-code which stores machine instructions.
+G-code does not support moves with varying cross-sectional area.
+A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
+A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.
+However, this introduces errors nevertheless.
 Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.

### 2019-08-29 0_main.tex
move accuracy calculation to appendix
abstract and conclusion - Jun
Tims edits to abstract

@@
 %
-Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as blow molding prototypes \jun{this seems not discussed in the main text} and microstructures.
-Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center \jun{only widths in the center?}.
+Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
+Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
 %Our framework makes it possible to distribute the workload of \jun{is the sentence complete if we delete worklaod of} the alterations over larger regions farther from the center. 
@@
 %By carefully formulating various beading schemes for our framework we can emulate existing approaches.
-Furthermore, we propose a novel scheme which influences a larger region of toolpaths so that the toolpaths are altered less severely. \jun{I miss a better summary of this inner distribution scheme.}
+Furthermore, we propose a novel scheme which distributes the alterations over an area large enough to avoid extremal bead width values, while limiting the number of altered toolpaths.
 %
@@
 \input{20_dataset}
+\input{25_accuracy}
 

### 2019-08-29 4_method.tex
dissipate theoretical analysis into Significance measure. Smooth transitions, and Computation time sections

@@
 This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
-The bisector angle is therefore an exact indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
+Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},
+we use the bisector angle as an \emph{exact} indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
 %Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
@@
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
-In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
+In order to make the transition ramps robust against small perturbations in the outline shape which cause extra (support) edges in the skeleton,
+we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
 \begin{equation}
@@
 \end{equation}
+Note that although the ST is not stable against noise in the boundary shape, the distance field itself is, so by designing our algorithms such that they are stable against changes in the topology of the skeleton our method is stable against small perturbations in the outline.
 %This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});

### 2019-08-29 6_validation.tex
Tims edits to limitations and applications
dissipate theoretical analysis into Significance measure. Smooth transitions, and Computation time sections

@@
 For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.
+These results could be improved upon by utilizing the locality inherent in our algorithms for parallelization on the GPU.
 
@@
 Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
-The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual performance of the print.
+The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual quality of the print.
 Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.

### 2019-08-29 8_discussion.tex
dissipate theoretical analysis into Significance measure. Smooth transitions, and Computation time sections

@@
 
-\subsection{Theoretical analysis}
-\jun{I suggest to dissolve this subsection. see comments and suggested changes below.}
-
-In this paper the significance measure is not used heuristically, as it is sometimes used in other literature.
-The significance measure is an exact measure of the relative size of gaps when using the uniform toolpathing method.
-See \cref{naive_overfill_underfill}
-\jun{this is in the method, and thus can be removed.}
-Note also that contrary to some literature we do not remove edges from the skeleton, but leave it intact.
-The final skeleton is still an exact and full feature descriptor.
-In that sense our framework provides an exact solution space.
-\jun{what is a solution space? what is the benefit of using an exact and full feature descriptor regarding toolpath accuracy, uniformity and smoothness?}
-
-Note also that our method is robust against small perturbations in the input shape.
-Geometrically small changes to the outline shape introduce extra edges and therefore change the topology of the graph of the ST.
-However, the significance measure and beading are defined in terms of radial distances so the robustness of the distance field against such perturbations means our method bypasses the instability of the skeleton.
-\jun{this could be mentioned somewhere in the method, shortly.
-The uniform approach can also be thought of using the distance field, is it less robust than ours?}
-Moreover, we have developed a method for dealing with edges within transition regions such that the toolpath is the same as if there was no such edge in that region.
-The toolpaths generated using our framework therefore remain the same when extra edges are added to the ST.
-\jun{this could be integrated in paragraph Smooth transitions to motivate the fractional bead count}
-
-Our framework is also local.
-The toolpathing around some section of the input polygons is independent of far away regions of the polygon.
-This means the toolpathing is stable against large perturbations of the input shape in far away regions
-and it also allows for some parallelism during the computation of the toolpaths.
-\jun{This could mentioned in paragraph Computational performance. This potentially could be parallelized for speeding up.}
-
 \input{10_applications}

### 2019-08-29 12_conclusions_future_work.tex
Tims changes to conclusion and future work

@@
 The computation times of our framework are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
-Our framework is robust and local, meaning that small local changes in the outline shape cause only small changes in the toolpath.
+Our framework is stable: small local changes in the outline shape cause only small changes in the toolpath.
 
-We have introduced the inward distributed beading scheme.
-It reduces the amount of beads with a width deviating from the nominal bead width by a large amount \jun{by a large amount refers to the deviation or the number of beads which deviate?}, and thus is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
-Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.
+We presented the inward distributed beading scheme.
+It reduces the amount of beads with a width deviating extremely from the nominal bead width, and thus it is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
+Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.
 
 The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
-Meanwhile it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
+Meanwhile it leaves most of the toolpaths the same as the uniform width technique in case of wide contours, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
 
@@
 Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
-An accurate model of manufacturability, print speed, and dimensional accuracy would be valuable to fine tune the beading scheme.
+An accurate model of manufacturability, print speed, and dimensional accuracy would be valuable to fine-tune the beading scheme.
 % If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.
@@
 Another direction of future research could be devoted to incorporating other information, e.g.
-properties of the outline such as curvature or visibility, toolpaths of the previous layer, and volume constraint (e.g.
-for functionally graded material).
-It might be interesting to incorporate more `horizontal' flow of information between different parts of a shape, rather than `vertically' between an outline location and a local peak or ridge.
-\jun{could this be summarized in a few words and integrated into the previous sentence?
-otherwise we could leave it out}
+properties of the outline such as curvature or visibility, non-local features such as the size of nearby outline features, toolpaths of the previous layer, or voluminal constraints (e.g.
+for functionally graded materials).
 % Furthermore we could also take into account volumetric considerations such as the toolpathing of the previous layer or volume constraint defined by a functionally graded material.

### 2019-08-29 4_method.tex
clean up old commented beading section text

@@
 
-\iffalse
-The beading information will be used in the next phase to directly generate the sites of the toolpaths.
-Note that a beading conceptually covers the whole diameter, while we only apply it along the radii;
-the upper half of the beading is therefore unused.
-
-% \subsubsection{Beading interpolation}\label{section_beading_interpolation}
-\paragraph{Beading interpolation}
-Central nodes which are in the middle of a transition have obtained a fractional bead count, but the definition of a beading presupposed integer numbers.
-In order to generate a beading for a central node with a fractional bead count assigned we use the fractional part of the bead count to interpolate between two beadings defined on the fractional bead count rounded up and down.
-Suppose we want to interpolate between two beadings $B^V$ and $B^W$, for which $n^{B^V} < n^{B^W}$.
-We interpolate the diameter $d$, widths $w_i$ and locations $l_i$ for indices $i < \nicefrac12 n^{B^V}$ linearly and enforce the symmetry constraints on the upper indices.
-See \cref{beading_interpolation}.
-The linear interpolation enforces robustness against small perturbations in the outline shape which cause extra edges to appear in the ST inside of transition regions.
-
-In order to create an interpolated beading $B = xB^V + (1-x) B^W$, for some $0<x<1$
-we calculate:
-\begin{align*}
-n^{B} &= n^{B^W} \\
-d^B &= x d^{B^V} + (1-x) d^{B^W} \\
-w_i^{B} &= w_{n^B-i}^{B} = x w_i^{B^V} + (1-x) w_i^{B^W} \text{ for } i < \frac12 n^{B^V} \\
-%  w_{frac{n}{2}^B - frac12}  = something difficult \text{ if } n \mod 2 == 1
-w_i^{B} &= w_i^{B^W} \text{ otherwise}\\
-l_i^{B} &= 
-\begin{cases} 
-x l_i^{B^V} + (1-x) l_i^{B^W} & \text{ for } i < \frac12 (n^{B^V} - 1) \\
-d^B - x l_{i-n^{B^W}+n^{B^V}}^{B^V} + (1-x) l_i^{B^W} & \text{ for } i > n^B - 1 - \frac12 (n^{B^V} - 1) \\
-\frac12 d^B  & \text{ if $n^B$ is odd and } i = (n^B - 1) / 2 \\
-l_i^{B^W} - l_{n^{B^V}-1}^{B^W} + l_{n^{B^V}-1}^B & \text{ otherwise}
-\end{cases}
-\end{align*}
-\fi
-
 \begin{figure}
@@
 \end{figure}
-
-\iffalse
-% \subsubsection{Beading propagation}\label{section_beading_conflicts}
-\paragraph{Beading propagation}
-The beading information associated with the central nodes is then propagated outward throughout the whole mesh.
-However, beading conflicts can arise where a marked edge has unmarked upward edges attached to them, since beading will also be propagated down from the local maxima or other higher marked regions.
-See \cref{beading_conflict_problem}.
-In such a case we interpolate between the lower beading and the beading propagated from above,
-starting from the lower marked node and ending at a distance $t_\text{beading}$ upward.
-At the nodes in between we will apply the interpolation between the two beadings and propagate the interpolated beading outward from those nodes.
-This interpolation is performed during the beading propagation algorithm.
-
-\fi
 
@@
 \end{figure}
-
-\iffalse
-
-After each marked node is assigned a beading by the beading scheme, we propagate the beadings outward to all nodes in the ST.
-The beading propagation is performed in two stages: an upward and downward stage.
-%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
-In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
-In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
-however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
-This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.
-
-\jun{It is more logical to first explain the general case (the above paragraph), and then the special treatment -- beading conflict.}
-
-\begin{algorithm}
-\caption{Beading propagation}
-\label{alg_beading_propagation}
-\begin{algorithmic}
-\ForAll{$v \in$ nodes}
-	\If {marked($v$)} $\text{map}[v] = (0, B(\hat{b}_v, 2 R(v)))$ \EndIf
-\EndFor
-\ForAll{$e \in$ edges}
-	\If {$R(v_0^e) < R(v_1^e)$}
-		% \State 
-		upwardEdges.add($e$)
-	\EndIf
-\EndFor
-\State upwardEdges.sort($\uplambda e_1 e_2 . R(v_1^{e_1}) < R(v_1^{e_2})$) \Comment {low to high $v_1$}
-\ForAll{$e \in$ upwardEdges} \Comment{upward phase}
-	\If {$\text{map}[v_0^e] \land \neg \text{map}[v_1^e$]}
-    		\State $(d, B) = \text{map}[v_0^e]$
-    		\State $\text{map}[v_1^e] \leftarrow (d + |v_1^e - v_0^e|, B)$
-	\EndIf
-\EndFor
-\ForAll{$e \in$ reverse(upwardEdges)} \Comment{downward phase}
-	\If {$\text{map}[v_1^e]$}
-    		\State $(d, B) \leftarrow \text{map}[v_1^e]$
-    		% d + |v_1^e - v_0^e|
-    		\If {$\text{map}[v_0^e]$}
-    			\State $(d_0, B_0) = \text{map}[v_0^e]$
-    			\State $B \leftarrow \text{interpolate}(\min(1, d_0 /  t_\text{beading}), B_0, B)$
-    		\EndIf
-    		\State $\text{map}[v_1^e] \leftarrow (0, B)$
-	\EndIf
-\EndFor
-\end{algorithmic}
-\end{algorithm}
-
-\fi
 

### 2019-08-29 4_method.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

@@
 Instead we determine the radial distance to the boundary at which each bead should occur.
-Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, startign from the outer bead and ending in the center.
+Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
 Together with a sequence of bead widths $W$ these form what we call a \emph{beading} $B$.
-For our distributed beading scheme we compute the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
+For our distributed beading scheme we compute the beading for a central node $v$ with $n = \lfloor \hat{b}_v \rfloor$ beads and a diameter $r = R(v)$  as:
 \begin{align*}
-    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
-    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
-    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
+    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0 , \dots, w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 , \dots, l_{\lceil n/2 \rceil-1} \right\} \right) \\
+    w_i &= r / n  & \text{for all $i \in \mathbb{N} : i < n / 2 $}\\
+    l_i &= r / n (i + \nicefrac12) & \text{for all $i \in \mathbb{N} : i < n / 2 $}
 \end{align*}
@@
 respectively, counting from the outline inward.
-An example beading is visualized in the top of \cref{beading_interpolation}:
-$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.
+Example beadings for an odd and even bead count with arbitrary widths are visualized in \cref{example_beading}.
 
@@
 The beading is defined in terms of an integer number of beads, while we have assigned a fractional bead count to nodes within a transition region.
-In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead width and location of the first and last $n/2$ lines between a beading $B^V$ based on $n$ and a beading $B^W$ based on $n+1$ (see \cref{beading_interpolation}).
+In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead widths and locations between a beading $B^1$ based on $n$ and a beading $B^2$ based on $n+1$ (see \cref{beading_interpolation}).
 Such interpolation is also used to deal with beading conflicts (see \cref{beading_conflict_problem}).
-We therefore also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
+There we also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
 and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.
@@
 \centering
-\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
+\setlength{\figheight}{.29\columnwidth}
+\begin{subfigure}{0.4\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation_beading.pdf}
+\caption{Example beadings}\label{example_beading}
+\end{subfigure}
+\begin{subfigure}{0.4\columnwidth}\centering
+\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation.pdf}
+\caption{Interpolation}
+\end{subfigure}
 \caption{
-Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
-Distances between the thick black lines constitute diameters $d$,
-the toolpath locations are visualized as dots,
-the widths are visualized as bidirectional arrows
-and the middle is highlighted in red.
+Interpolation between two beadings $B^1$ and $B^2$ with odd and even bead count resulting in a beading $B^x$ at $n+\nicefrac23$.
+Bead indices are counted inward from the outline (thick black).
+Interpolation of locations in dots, interpolation of widths in dashes.
 }
@@
 Applying beadings to generate sites along trapezoids.
-\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
+\subref{trapezoid_beading_beading} shows the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
 \subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.

### 2019-08-29 5_generalization.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

@@
 &q(d),
-B(n, d),
+B(n, r),
 t(n),
@@
 $q(d)$ the quantization operator,
-$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$,
+$B(n,r)$ is the beading function consisting of $\left( W(n,r), L(n,r) \right)$,
 $t(n)$ the transition length,
@@
 $d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
-%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
+%$W(n, r)$ and $L(n, r)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
 \end{definition}
@@
 \item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
-\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
-%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
-%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
-\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
+\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
+\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
 \end{enumerate}
@@
 \begin{align*}
-L(n,d)_i = 
+L(n,r)_i = 
 \begin{cases}
--\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
-d/2 & \text{ if } i =  \frac12 (n -1) \\
-d - W(n,d)_{n-1-i} & \text{ otherwise }\\
+-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
+r & \text{ if } i =  \frac12 (n -1) \\
+%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
 \end{cases}
@@
 and that the symmetry restrictions are met.
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $R(v) = \nicefrac12 n w^*$ for $n \in \mathbb{N}$.
 The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
@@
 q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
-W(n,d)_i &= w^* \text{ for all } i 
+W(n,r)_i &= w^* \text{ for all } i 
 %\\
-%L(n,d)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+%L(n,r)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
 \end{align*}
@@
  \\
-W(n,d)_i &= 
+W(n,r)_i &= 
 \begin{cases}
-d & \text{ if } n = 1 \\
+2r & \text{ if } n = 1 \\
 w^* & \text{ otherwise } \\
@@
 %\\
-%L(n,d)_i &= 
+%L(n,r)_i &= 
 %\begin{cases}
-%d / 2 & \text{ if } n = 1 \\
+%2r / 2 & \text{ if } n = 1 \\
 %w^* / 2 & \text{ otherwise } \\
@@
 q(d) &= C \\
-W(n,d)_i &= d / n \text{ for all } i 
+W(n,r)_i &= 2 r / n \text{ for all } i 
 %\\
-%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
+%L(n,r)_i &= 2r / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
 \end{align*}
@@
 q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
-W(n,d)_i &= d / n \text{ for all } i 
+W(n,r)_i &= 2 r / n \text{ for all } i 
 %\\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
+%L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
 \end{align*}
@@
 \\
-W(n,d)_i &= 
+W(n,r)_i &= 
 \begin{cases}
-d - (n-1) w^* &\text{ if } i = \frac12 (n-1) \\
+2 r - (n-1) w^* &\text{ if } i = \frac12 (n-1) \\
 w^* &\text{ otherwise }
@@
 %\\
-%L(n,d)_i &= 
+%L(n,r)_i &= 
 %\begin{cases}
-%d / 2 & \text{ if } i = \frac12 (n-1) \\
+%2r / 2 & \text{ if } i = \frac12 (n-1) \\
 %w^* \left(i + \frac12 \right) & \text{ otherwise }
@@
 q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
-E(n,d) &= d - n w^* \\
-W(n,d)_i &= w^* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i \\
-%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
-M(n,d)_i &= \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )
+E(n,r) &= 2r - n w^* \\
+W(n,r)_i &= w^* + E(n,r) \frac{\omega(n,r)_i}{\sum_{j=0}^{n-1} \omega(n,r)_j} \text{ for all } i \\
+%L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
+\omega(n,r)_i &= \max(0, 1 - N^{-2} (i - (n-1)/2)^2 )
 \end{align*}
@@
 We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
-The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
+The distribution is determined by some weighing function $\omega(n,r)$, which defines the portion of the discrepancy to distribute to each bead.
 %\paragraph{Inward distributed}
-For example, we can choose an $M$ which distributes the discrepancy over the innermost beads, and distribute most of it to the inner beads.
+See \cref{formula_inward_distributed}.
+For example, we can choose an $\omega$ which distributes the discrepancy over the innermost $N$ beads, and distribute most of it to the inner beads.
 See \cref{distributed_comparison}.
@@
 %Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
-See \cref{formula_inward_distributed}.
 
@@
 \begin{align*}
-W'(n,d)_1 &=
+W'(n,r)_0 &=
 \begin{cases}
-\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
-W(n,d)_1 & \text{ otherwise}
+\max \left( w^*  ,  W(n,r)_0 \right) & \text{ if } n = 1 \\
+W(n,r)_0 & \text{ otherwise}
 \end{cases}

### 2019-08-29 6_validation.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

@@
 Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

### 2019-08-29 5_generalization.tex
lil improvements

@@
 \paragraph{Constant bead count}
-We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature diameter over the widths of a constant number of beads.
-Additionally in order to emulate their definition of branches we mark all ST edges and in a separate algorithm we unmark the outer edges connected to the outline shape.
-Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since the topology of the graph of the ST is not stable against those.
+We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature radius over the widths of a constant number of beads.
+Additionally in order to emulate their definition of ``branches'' we mark all ST edges we unmark the outer edges connected to the outline shape in a separate algorithm.
+Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since this marking depends on the topology of the graph of the ST.
 See \cref{formula_constant_bead_count}.

### 2019-08-30 10_applications.tex
move source files to top level hierarchy

@@
 \begin{subfigure}{\textwidth}\centering
-\includegraphics[width=\textwidth]{sources/applications/combined_small_dilated_circled.pdf}
+\includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
 %\caption{Overview}\label{applications_overview}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/house.png}
+\includegraphics[height=\figheight]{sources-applications-house.png}
 \caption{House}\label{applications_house}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
+\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
 \caption{Case}\label{applications_case}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/david.png}
+\includegraphics[height=\figheight]{sources-applications-david.png}
 \caption{Statue}\label{applications_statue}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
+\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
 \caption{TUD}\label{applications_tud}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
+\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
 \caption{UM}\label{applications_um}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
+\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
 \caption{Gear}\label{applications_gear}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
+\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
 \caption{Bone}\label{applications_bone}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/gyroid.png}
+\includegraphics[height=\figheight]{sources-applications-gyroid.png}
 \caption{Gyroid}\label{applications_gyroid}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
+\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
 \caption{Hex}\label{applications_hex}

### 2019-08-30 1_intro.tex
move source files to top level hierarchy

@@
 FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
-A common strategy to accurately manufacture a given 3D model is to extrude a contour following print path,
+A common strategy to accurately manufacture a given 3D model is to extrude a contour-following print path,
 because the position and shape of the toolpath can be controlled relatively accurately.
@@
 Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
-These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
+These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are relatively large compared to the whole part.
 In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
@@
 \begin{figure}\centering
-\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
-\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
+\includegraphics[width=\columnwidth]{sources-intro-TEST-naive-accuracy.png}
+\includegraphics[width=\columnwidth]{sources-intro-TEST-Center-widths.png}
+\includegraphics[width=\columnwidth]{sources-intro-TEST-InwardDistributed-widths.png}
 \caption{

### 2019-08-30 25_accuracy.tex
move source files to top level hierarchy

@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_blocky.pdf}
+\includegraphics[width=\columnwidth]{sources-validation-visualization-principle-blocky.pdf}
 \caption{Blocky}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded.pdf}
+\includegraphics[width=\columnwidth]{sources-validation-visualization-principle-rounded.pdf}
 \caption{Rounded}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/visualization_principle_rounded_excluded.pdf}
+\includegraphics[width=\columnwidth]{sources-validation-visualization-principle-rounded-excluded.pdf}
 \caption{Excluded}

### 2019-08-30 4_method.tex
lil improvements
move source files to top level hierarchy

@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/input.pdf}
+\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-input.pdf}
 \caption{Layer outline}\label{overview_outline}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/uoc.pdf}
+\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-uoc.pdf}
 \caption{Skeleton}\label{overview_skeleton}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/UoC_with_cones.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-UoC-with-cones.png}
 \caption{Union of cones}\label{overview_uoc}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_naive_cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-naive-cropped.png}
 \caption{Slicing}\label{overview_uniform_sliced}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources/method/overview/2D/naive.png}
+\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-naive.png}
 \caption{Uniform paths}\label{overview_uniform_paths}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/marking_cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-marking-cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/marked.pdf}
+\includegraphics[width=\figheight]{sources-method-overview-2D-marked.pdf}
 \caption{Center identification}\label{3d_surface_overview_center}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/quantized.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-quantized.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/rounded.pdf}
+\includegraphics[width=\figheight]{sources-method-overview-2D-rounded.pdf}
 \caption{Quantization}\label{3d_surface_overview_rounded}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/smoothed_magenta.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-smoothed-magenta.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/smoothed.pdf}
+\includegraphics[width=\figheight]{sources-method-overview-2D-smoothed.pdf}
 \caption{Smoothing}\label{3d_surface_overview_smoothed}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources/method/overview/surface/sliced_cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-cropped.png}
 
@@
 
-\includegraphics[width=\figheight]{sources/method/overview/2D/sliced.png}
+\includegraphics[width=\figheight]{sources-method-overview-2D-sliced.png}
 \caption{Adaptive width paths}\label{3d_surface_overview_sliced}
@@
 For ease of reference we have included a legend showing the terms employed in this manuscript in \cref{legend}.
-These terms will be further explained as they first appear later in this paper.
+These terms will be further explained as they first appear throughout this paper.
 
 \begin{figure}\centering
-\includegraphics[width=.75\columnwidth]{sources/method/legend2.pdf}
+\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
 \caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_mat}
+\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-mat}
 \caption{Medial Axis}\label{shape_decomposition_mat}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_vd}
+\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-vd}
 \caption{Voronoi Diagram}\label{shape_decomposition_vd}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/simple_skeleton_st}
+\includegraphics[height=\figwidthTwo]{sources-method-simple-skeleton-st}
 \caption{Skeletal Trapezoidation}\label{shape_decomposition_st}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
+\includegraphics[height=\figwidthTwo]{sources-method-half-edge-datastructure.pdf}
 \caption{Data structure}\label{shape_decomposition_datastructure}
@@
 \begin{subfigure}{0.45\columnwidth} \centering
-\includegraphics[height=\figheight,frame]{sources/method/naive_overfill_underfill.pdf}
+\includegraphics[height=\figheight,frame]{sources-method-naive-overfill-underfill.pdf}
 \caption{Over- and underfill}\label{naive_overfill_underfill}
@@
 \begin{subfigure}{0.45\columnwidth} \centering
-\includegraphics[height=.8\figheight]{sources/method/significance_properties.pdf}
+\includegraphics[height=.8\figheight]{sources-method-significance-properties.pdf}
 \caption{Significance measure}\label{distance_based_angles}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--bead-count.pdf}
 \caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-mids.pdf}
 \caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--filtered.pdf}
 \caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-ends.pdf}
 \caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transitions-applied.pdf}
 \caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
@@
 \begin{subfigure}{.27\textwidth}
-\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources/method/beading_transitioning_filtering__result_uoc.pdf}
+\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-transitioning-filtering--result-uoc.pdf}
 \caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}
@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_no_transitioning.png}
+\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning.png}
 \caption{Without transitioning}
@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/method/wedge_transitioning.png}
+\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning.png}
 \caption{Transitioning}
@@
 \begin{subfigure}{.55\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/peripheral_heights_3D.png}
+\includegraphics[height=\figheight]{sources-method-peripheral-heights-3D.png}
 \caption{Surface mesh}
@@
 \begin{subfigure}{.4\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/peripheral_heights.pdf}
+\includegraphics[height=\figheight]{sources-method-peripheral-heights.pdf}
 \caption{ST}
@@
 \begin{subfigure}{0.4\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation_beading.pdf}
+\includegraphics[height=\figheight]{sources-method-trapezoid-beading-interpolation-beading.pdf}
 \caption{Example beadings}\label{example_beading}
@@
 \begin{subfigure}{0.4\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation.pdf}
+\includegraphics[height=\figheight]{sources-method-trapezoid-beading-interpolation.pdf}
 \caption{Interpolation}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_3D.png}
-\includegraphics[height=\figheight]{sources/method/beading_conflict.pdf}
+\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-3D.png}
+\includegraphics[height=\figheight]{sources-method-beading-conflict.pdf}
 \caption{Beading conflict}\label{beading_conflict}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=.95\columnwidth,frame]{sources/method/beading_conflict_solved_3D.png}
-\includegraphics[height=\figheight]{sources/method/beading_conflict_solved.pdf}
+\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-solved-3D.png}
+\includegraphics[height=\figheight]{sources-method-beading-conflict-solved.pdf}
 \caption{Conflict resolution}\label{beading_conflict_solved}
@@
 \begin{subfigure}{0.14\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
+\includegraphics[height=\figheight]{sources-method-trapezoid-beading-beading.pdf}
 \caption{Beadings}\label{trapezoid_beading_beading}
@@
 \begin{subfigure}{0.5\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
+\includegraphics[height=\figheight]{sources-method-trapezoid-beading-propagated.pdf}
 \caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
@@
 \begin{subfigure}{0.34\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
+\includegraphics[height=\figheight]{sources-method-trapezoid-beading-separate.pdf}
 \caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
@@
 \begin{subfigure}{.5\columnwidth}\centering
-\includegraphics[width=\figheight,rotate=90]{sources/method/domains.pdf}
+\includegraphics[width=\figheight,rotate=90]{sources-method-domains.pdf}
 \caption{Polygon domains}\label{shape_decomposition_domains}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/method/segment_generation.pdf}
+\includegraphics[height=\figheight]{sources-method-segment-generation.pdf}
 \caption{Extrusion segment chaining}\label{shape_decomposition_domains}
@@
 \begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_before}
+\includegraphics[width=\figwidth,frame]{sources-method-polyline-reduction-before}
 \caption{No reduction}
@@
 \begin{subfigure}{0.45\columnwidth}\centering
-\includegraphics[width=\figwidth,frame]{sources/method/polyline_reduction_after}
+\includegraphics[width=\figwidth,frame]{sources-method-polyline-reduction-after}
 \caption{Reduction}

### 2019-08-30 5_generalization.tex
move source files to top level hierarchy

@@
 \centering
-\includegraphics[width=.4\columnwidth,frame]{sources/method/transition_length_limit.pdf}
+\includegraphics[width=.4\columnwidth,frame]{sources-method-transition-length-limit.pdf}
 \caption{
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_evenly.png}
+\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-evenly.png}
 \caption{Evenly distributed}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight,frame]{sources/validation/wedge_Distributed_pretty_inward.png}
+\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-inward.png}
 \caption{Inward distributed}
@@
 \begin{subfigure}{.1\columnwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/widths_legend_small.pdf}
+\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
 \end{subfigure}

### 2019-08-30 6_validation.tex
move source files to top level hierarchy

@@
 \centering
-\includegraphics[width=.25\columnwidth]{sources/validation/visualization_principle_rounded_excluded_single.pdf}
+\includegraphics[width=.25\columnwidth]{sources-validation-visualization-principle-rounded-excluded-single.pdf}
 \caption{
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
 \caption{Uniform}\label{TEST_naive_accuracy}
@@
 %\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
-%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
 %\caption{Single}\label{TEST_SingleBead_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
 \caption{Constant}\label{TEST_Constant_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
 \caption{Centered}\label{TEST_Center_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
 \caption{Distributed}\label{TEST_Distributed_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
-\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
+\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
+\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
 \caption{Inward}\label{TEST_InwardDistributed_accuracy}
@@
 \vspace{4.7cm}
-\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.pdf}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
 \end{subfigure}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/computime2.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/computime2.pdf}
+\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
 \caption{Computation time}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/widthHistogram.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
+\includegraphics[height=\figheight]{sources-validation-widthHistogram.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
 \caption{Extrusion widths}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/indexedwidths2.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/widthHistogram.pdf}
+\includegraphics[height=\figheight]{sources-validation-indexedwidths2.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
 \caption{Extrusion width per index}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/overunderfill.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/overunderfill.pdf}
+\includegraphics[height=\figheight]{sources-validation-overunderfill.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
 \caption{Over- and underfill}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/smoothness.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/smoothness.pdf}
+\includegraphics[height=\figheight]{sources-validation-smoothness.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
 \caption{Site angles}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources/validation/smoothnessNoTransition.pdf}
-%\includegraphics[width=\figwidth]{sources/validation/smoothnessNoTransition.pdf}
+\includegraphics[height=\figheight]{sources-validation-smoothnessNoTransition.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
 \caption{Site angles without smoothing}
@@
 \setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
 \caption{Wedge}\label{print_wedge}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
-\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
-\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
 \caption{Inward distributed}\label{print_inward}

### 2019-08-30 1_intro.tex
Small changes by Jun and Tim

@@
 \begin{figure}\centering
-\includegraphics[width=\columnwidth]{sources-intro-TEST-naive-accuracy.png}
-\includegraphics[width=\columnwidth]{sources-intro-TEST-Center-widths.png}
-\includegraphics[width=\columnwidth]{sources-intro-TEST-InwardDistributed-widths.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
+\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
 \caption{

### 2019-08-30 0_main.tex
cleanup abstract
Small changes by Jun and Tim
better missing includegraphics file identification

@@
 	\iffalse
-	\newcommand{\noimage}{%
+	\newcommand{\noimage}[1]{%
 	  \setlength{\fboxsep}{-\fboxrule}%
-	  \fbox{\phantom{\rule{10pt}{10pt}}File missing\phantom{\rule{10pt}{10pt}}}% Framed box
+	  \fbox{\phantom{\rule{10pt}{10pt}} Missing file: \path{#1} \phantom{\rule{10pt}{10pt}}}% Framed box
 	}
 	\let\includegraphicsoriginal\includegraphics
-	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage}}
+	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage{#2}}}
+
 	\fi
@@
 By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
-%
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
 Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
-%Our framework makes it possible to distribute the workload of \jun{is the sentence complete if we delete worklaod of} the alterations over larger regions farther from the center. 
 In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
-%Based on the radial distances in the medial axis transform we decide on the number of beads and their widths from the center outward.
 We present various schemes to decide the number of beads and their widths from the center outward.
-%By carefully formulating various beading schemes for our framework we can emulate existing approaches.
 Furthermore, we propose a novel scheme which distributes the alterations over an area large enough to avoid extremal bead width values, while limiting the number of altered toolpaths.
-%
 This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
@@
 \begin{keyword} 
-Adaptive extrusion width, Tool path generation, Additive manufacturing, Geometrical accuracy, Medial axis transform, Polygon offsetting
+Adaptive extrusion width, Toolpath generation, Additive manufacturing, Geometrical accuracy, Medial axis transform
 \end{keyword}

### 2019-08-30 6_validation.tex
Tim: merge print figures

@@
 gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
-We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines thinner than the nozzle size.
+We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
 
-The prints are shown in \cref{wedge_print} and \cref{prints}.
+The prints are shown in \cref{prints}.
 Because of inaccuracies in the deposition control system some of the prints show defects.
 Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
-The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual quality of the print.
-Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.
+The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
+Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
 The difference between the centered and the inward distributed schemes is less pronounced.
@@
 \includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
-\caption{Wedge}\label{print_wedge}
+\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
 \end{subfigure}
-\caption{
-A wedge shape printed using the uniform scheme, centered scheme and the inward distributed scheme.
-The uniform and centered scheme show problems around certain model diameters.
-}
-\label{wedge_print}
-\end{figure}
-
-\begin{figure}
-\centering
 \setlength{\figheight}{.38\columnwidth}

### 2019-08-30 6_validation.tex
Tim: redo accuracy, uniformity and smoothness discussion and figures

@@
 
-We compare the total area (in \si{\milli\meter\squared}) of these overfill and underfill shapes to the total area of the boundary for each sample in the data set.
-The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
+We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
+and report the average percentages in see \cref{over_underfill}.
 The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
@@
 \subsubsection{Uniformity}
-Depending on the printer hardware configuration, some bead widths might be difficult or impossible to produce.
-A bead width far below the nozzle size can result in fluttered extrusion, while a bead width far above the nozzle size can require pressures above the specifications of the machine. 
-Also, large bead widths may cause the extruded material to bulge upwards instead of filling the required width.
-Moreover, bead widths deviating from the nominal bead width by a large amount may impact the mechanical properties of the print.
+Depending on the printer hardware configuration, some bead widths might be difficult to produce;
+too narrow beads might result in fluttered extrusion and too wide beads might require a pressure in the nozzle beyond the specifications of the machine or they might bulge upward on the sides.
+Moreover, bead widths deviating from the preferred bead width by a large amount may be hard to realize and may impact the mechanical properties of the print.
 We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
 
-To evaluate the width uniformity, we sampled the extrusion widths of all generated toolpaths 
-at intervals of \SI{1}{\micro\meter} along the toolpath.
-From these sampled values, we calculated the mean bead width, and standard deviation per scheme.
+To evaluate the uniformity of the width,
+we calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
 \cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
-We found that the mean width of the inward distributed and evenly distributed schemes is close to nominal nozzle size of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
-These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less and infrequently from the nominal bead width compared to the other schemes.
+We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
+These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
 We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
-The outer beads of the inward distributed scheme clearly have more often the nominal width of \SI{400}{\micro\meter}, while the evenly distributed scheme more often extrudes widths that deviate from the nominal width.
+The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
 
@@
 In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We measured the angle between consecutive extrusion segments generated by each scheme.
-The relative frequency of these angles is shown in \cref{smoothness}.
-All schemes show a higher number of corners for smaller angles with a peak towards \SI{0}{\degree} (straight line).
-The inward distributed scheme produces an order of magnitude less corners around \SI{30}{\degree}, compared to evenly distributed. 
+We therefore measured the angle between consecutive extrusion segments generated by each scheme
+and report on the occurence of each angle in \cref{smoothness}.
+All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
+We observe that compared to the naive method our framework produces less acute angles, but more obtuse angles.
+The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
 We also investigated the effect of the transition regions on the smoothness of the toolpaths. 

### 2019-08-30 12_conclusions_future_work.tex
Tim: nominal => preferred
'nominal size' is the size something is supposed to be on paper; that wouldn't work for a sentence like
'The evenly distributed scheme can be conceptualized as calculating the total discrepancy $ between the actual feature diameter $ and the total preferred width  w^*$'

@@
 We presented the inward distributed beading scheme.
-It reduces the amount of beads with a width deviating extremely from the nominal bead width, and thus it is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
+It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
 Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.

### 2019-08-30 1_intro.tex
Tim: nominal => preferred
'nominal size' is the size something is supposed to be on paper; that wouldn't work for a sentence like
'The evenly distributed scheme can be conceptualized as calculating the total discrepancy $ between the actual feature diameter $ and the total preferred width  w^*$'

--- 2019-08-30 1_intro.tex
@@
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
-Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Liu2019a}, topology optimized structures~\cite{Zong2019,Wu2019a,Cheng2019} and regular honeycomb structures~\cite{Al-Ketan2018,Maskery2018}.
-Many of these applications require 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
+Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Liu2019a,Al-Ketan2018,Maskery2018} and topology optimized structures~\cite{Zong2019,Wu2019a,Cheng2019}.
+Many of these applications involve 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
 
 FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
-A common strategy to accurately manufacture a given 3D model is to extrude a contour-following print path,
+A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
 because the position and shape of the toolpath can be controlled relatively accurately.
@@
 
-The simple technique for generating the shape filling toolpaths of a layer consists in performing uniform inward offsets with the radius of the the nozzle from the outline shape.
-However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
+The simple technique for generating the dense contour-parallel toolpaths of a layer consists in performing uniform inward offsets with the radius of the nozzle from the outline shape.
+However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and areas which are not filled at all: \emph{underfill} areas.
 See \cref{intro_wedge}(top).
@@
 These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are relatively large compared to the whole part.
-In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
-Some such toolpath generation techniques have already been developed.
+
+One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
+This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014}, where a wide range of widths could be realized by the hardware. 
+For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$.
+However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
+Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
+On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
+% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
+
+In this paper we propose a framework for planning toolpath with adaptive width for minimizing over- and underfill. 
+We show that this framework supports multiple schemes on deciding the bead locations and extrusion widths. 
+In particular for FDM printing, we propose a novel scheme which reduces the amount of over- and underfill while the extrusion widths deviate less from nozzle size compared to existing approaches (which are mostly designed for wire and arc additive manufacturing).
+% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
+% Some such toolpath generation techniques have already been developed.
 
@@
 
-There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
-The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
-In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
-We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
-See \cref{intro_wedge}(bottom).
+% There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
+% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
+% In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
+% We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the preferred bead width compared to existing techniques.
+% See \cref{intro_wedge}(bottom).
 
 %\subsection{Contributions}
-A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
-because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
-We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
+% A polygonal shape with a width of a fractional multiple of the preferred bead width will always result in the bead widths deviating from the preferred bead width by the fractional part in total,
+% because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
+% We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the preferred width.
 Our contributions are as follows:
 \begin{itemize}
-\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
-\item A specific beading scheme function for this framework for:
-\begin{itemize}
-\item Accurately filling a 2D outline with extrusion beads
-\item Reducing the overfill and underfill areas compared to the uniform width technique
-\item Reducing the amount of beads with greatly deviating width compared to existing literature
-\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
-\end{itemize}
+\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which maps a feature diameter to a number of beads and their widths.
+\item A specific beading scheme for FDM printing which reduces the amount of beads with greatly deviating width, and which promotes smooth toolpaths that are close to the preferred width toward the outline of the shape.
+% \begin{itemize}
+% \item Accurately filling a 2D outline with extrusion beads
+% \item Reducing the overfill and underfill areas compared to the uniform width technique
+% \item Reducing the amount of beads with greatly deviating width compared to existing literature
+% \item Promoting smooth toolpaths which are close to the preferred width toward the outline of the shape.
+% \end{itemize}
 \end{itemize}

### 2019-08-30 8_discussion.tex
Small changes by Jun and Tim
Tim: nominal => preferred
'nominal size' is the size something is supposed to be on paper; that wouldn't work for a sentence like
'The evenly distributed scheme can be conceptualized as calculating the total discrepancy $ between the actual feature diameter $ and the total preferred width  w^*$'

@@
 The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
-Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the nominal bead width.
+Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
 Note that most overfill areas occur near regions of alternating bead width. 
@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-We can therefore state that the distributed schemes result in bead widths closer to the nominal widths compared to the centered scheme.
+We can therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
 This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the nominal bead width and to limit the number of angled extrusion segments in transitioning regions.
+The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the preferred bead width and to limit the number of angled extrusion segments in transitioning regions.
 This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
 
-However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the nominal bead width more often, which means that errors from inaccuracies due to deviation from the nominal bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
+However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
 Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
@@
 
-\subsection{Limitations}
+\subsection{Discussion on implications}
 Note that the current industry standard in FDM printing employs little to no bead width variation.

### 2019-08-30 6_validation.tex
Tim: minor improvements to results and discussion

@@
 Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead widths of $w^* = \SI{0.4}{\milli\meter}$.
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
@@
 All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
-We observe that compared to the naive method our framework produces less acute angles, but more obtuse angles.
+We observe that compared to the naive method our framework produces less acute angles which, but more obtuse angles.
 The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
@@
 \subsubsection{Computational performance}
-\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
+\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique implemented using Clipper~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
 For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.
@@
 
-The algorithmic complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
+The computational complexity is limited by the generation of the Voronoi Diagram, which is $O(n \log n)$, where $n$ is the number of vertices in the input shape.
 The other steps in our framework have a complexity of $O(m)$, where $m$ is the number of elements in the ST.

### 2019-08-30 8_discussion.tex
Tim: minor improvements to results and discussion

@@
 We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
-These defects are supposed to negatively influence the mechanical properties of the parts, and exceed the point that process parameters can be reliably correlated to mechanical properties of the part.
+These defects are presumed to negatively influence the mechanical properties of the parts, and exceed the point that process parameters can be reliably correlated to mechanical properties of the part.
 To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

### 2019-08-30 0_main.tex
introduction, and abstract

@@
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
-Some existing approaches address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
-In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
-We present various schemes to decide the number of beads and their widths from the center outward.
-Furthermore, we propose a novel scheme which distributes the alterations over an area large enough to avoid extremal bead width values, while limiting the number of altered toolpaths.
-This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
+Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
+%address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
+%In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
+In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths from the center outward.
+Furthermore, we propose a novel scheme for FDM printing which avoids extreme bead width deviation from the nozzle size, and limits the number of altered toolpaths.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 slices.
+%This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
 \end{abstract}

### 2019-08-30 1_intro.tex
introduction, and abstract

@@
 For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$.
-However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
+However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (i.e.
+nominal width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
 Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
@@
 % In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
-% We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the preferred bead width compared to existing techniques.
+% We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the nominal bead width compared to existing techniques.
 % See \cref{intro_wedge}(bottom).
@@
 %\subsection{Contributions}
-% A polygonal shape with a width of a fractional multiple of the preferred bead width will always result in the bead widths deviating from the preferred bead width by the fractional part in total,
+% A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
 % because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
-% We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the preferred width.
+% We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
 Our contributions are as follows:
@@
 \item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which maps a feature diameter to a number of beads and their widths.
-\item A specific beading scheme for FDM printing which reduces the amount of beads with greatly deviating width, and which promotes smooth toolpaths that are close to the preferred width toward the outline of the shape.
+\item A specific beading scheme for FDM printing which reduces the amount of beads with greatly deviating width, and which promotes smooth toolpaths that are close to the nominal width toward the outline of the shape.
 % \begin{itemize}
@@
 % \item Reducing the amount of beads with greatly deviating width compared to existing literature
-% \item Promoting smooth toolpaths which are close to the preferred width toward the outline of the shape.
+% \item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
 % \end{itemize}

### 2019-08-30 2_related_work.tex
move source files to top level hierarchy
introduction, and abstract
Updates from Overleaf

@@
 Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
-The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simply geometry where there are no branches in the medial axis.
+The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
 An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
@@
 Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
+Toolpath with varying width for 
 In this paper we propose an adaptive beading scheme to address this problem.
@@
 % \begin{subfigure}{0.45\columnwidth}
-% \includegraphics[width=\columnwidth]{sources/related_work/moessen.jpg}
+% \includegraphics[width=\columnwidth]{sources-related-work-moessen.jpg}
 % \caption{\citeauthor{Moesen2011}}
@@
 % \begin{subfigure}{0.45\columnwidth}
-% \includegraphics[width=\columnwidth]{sources/related_work/jin.jpg}
+% \includegraphics[width=\columnwidth]{sources-related-work-jin.jpg}
 % \caption{\citeauthor{Jin2017JMS}}
@@
 % \centering
-% \includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
-% \includegraphics[width=.7\columnwidth]{sources/related_work/kao.jpg}
+% \includegraphics[width=\columnwidth]{sources-related-work-ding.jpg}
+% \includegraphics[width=.7\columnwidth]{sources-related-work-kao.jpg}
 % \caption{Path planning strategies proposed by Kao (bottom) and employed in FDM by Ding et al (top).}

### 2019-08-30 4_method.tex
Tim: minor improvements to results and discussion
Tim: remove peripheral_heights figure

@@
 Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
-while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes (see \cref{peripheral_heights}).
-Instead we determine the radial distance to the boundary at which each bead should occur.
+while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes.
+Instead we determine the radial distance to the boundary at which each bead should occur from the boundary to the center.
 Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
@@
 \begin{align*}
-    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0 , \dots, w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 , \dots, l_{\lceil n/2 \rceil-1} \right\} \right) \\
+    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0  \dots w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 \dots l_{\lceil n/2 \rceil-1} \right\} \right) \\
     w_i &= r / n  & \text{for all $i \in \mathbb{N} : i < n / 2 $}\\
@@
 Example beadings for an odd and even bead count with arbitrary widths are visualized in \cref{example_beading}.
-
-\begin{figure}\centering
-\setlength{\figheight}{.2\columnwidth}
-\begin{subfigure}{.55\columnwidth}\centering
-\includegraphics[height=\figheight]{sources-method-peripheral-heights-3D.png}
-\caption{Surface mesh}
-\end{subfigure}
-\begin{subfigure}{.4\columnwidth}\centering
-\includegraphics[height=\figheight]{sources-method-peripheral-heights.pdf}
-\caption{ST}
-\end{subfigure}
-\caption{
-Shallow corners will cause peripheral nodes for which the height should be determined based on the central node above it.
-}
-\label{peripheral_heights}
-\end{figure}
 

### 2019-08-30 5_generalization.tex
Tim: nominal => preferred
'nominal size' is the size something is supposed to be on paper; that wouldn't work for a sentence like
'The evenly distributed scheme can be conceptualized as calculating the total discrepancy $ between the actual feature diameter $ and the total preferred width  w^*$'
make transition overlap into wrapfigure to save space

@@
 \begin{enumerate}
-\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
+	\begin{minipage}{\columnwidth}
+	\setlength\intextsep{0pt}
+	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
+	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
+	%\caption{
+	%%Transition ends (magenta and pink) shouldn't cross each other.
+	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
+	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
+	%}
+	\label{transition_placement}
+	\end{wrapfigure}
+	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
+\end{minipage}
 \item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
@@
 \end{enumerate}
-
-\begin{figure}
-\centering
-\includegraphics[width=.4\columnwidth,frame]{sources-method-transition-length-limit.pdf}
-\caption{
-Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
-The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
-}
-\label{transition_placement}
-\end{figure}
 
@@
 See \cref{distributed_comparison}.
-That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
+That way we limit the region of impact of the distributed scheme to a central region and have the preferred bead width $w^*$ in regions farther away.
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
 % and it forces most of the beads to have exactly the prefered width.
-%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
+%Moreover, the bead widths equal the preferred bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
 

### 2019-08-30 25_accuracy.tex
reduce accuracy calculation appendix

@@
 In order to estimate the overfill and underfill, we need to accurately calculate the area covered by a single extrusion path.
-If we would simply use an isosceles trapezoidal area with base lengths equal to the widths of the two end points of the extrusion segment, we would get artifacts at corners in the toolpath (\cref{segment_visualization}a).
-We therefore use a semi-circle (\cref{segment_visualization}b) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
-For polyline extrusion paths which are not closed, we also include the semi-circle corresponding to the extrusion width of the end-position ( \cref{segment_visualization}c).
+If we would simply use an isosceles trapezoidal area, we would get overfill artifacts at corners in the toolpath (\cref{segment_visualization_blocky}).
+We therefore use a semi-circle (\cref{segment_visualization_rounded}) with a diameter equal to the starting width in the one end of each segment, and exclude it at the other end, because it will be included in the next segment.
+For polyline extrusion paths which are not closed, we also include the semi-circle of the destination location (\cref{segment_visualization_excluded}).
 
@@
 \includegraphics[width=\columnwidth]{sources-validation-visualization-principle-blocky.pdf}
-\caption{Blocky}
+\caption{Blocky}\label{segment_visualization_blocky}
 \end{subfigure}
@@
 \includegraphics[width=\columnwidth]{sources-validation-visualization-principle-rounded.pdf}
-\caption{Rounded}
+\caption{Rounded}\label{segment_visualization_rounded}
 \end{subfigure}
@@
 \includegraphics[width=\columnwidth]{sources-validation-visualization-principle-rounded-excluded.pdf}
-\caption{Excluded}
+\caption{Excluded}\label{segment_visualization_excluded}
 \end{subfigure}
@@
 
-We can then estimate the amount of underfill by unioning the rounded visualization of all extrusion segments and then taking the difference from the original outline shape.
-In order to deal with rounding errors, we perform a morphological close of \SI{5}{\micro\meter} before calculating the total area of the underfill regions.
-
-The overfill regions are calculated by adding the polygonal areas of each extrusion segment to a list.
-We then add the original outline shape in reverse and perform a Vatti clipping operation~\cite{Vatti2019clipping} which only keeps areas of positive winding number.
-Because the reverse outline shape reduces the winding number of all extruded segments by one, only the overfill areas are left with a positive winding number.
-In order to estimate the areas which are triply covered by extrusion segments, we repeat the process of adding the outline in reverse and performing Vatti's clipping operation.
-These triple extrusion areas count double toward the total amount of overfill.
-The resulting overfill and underfill areas are visualized for the different toolpath schemes in the top of \cref{visualized_accuracy}.
+Using boolean operations we can obtain the polygonal regions for overfill and those for underfill.
+In order to deal with rounding errors we perform a morphological close of \SI{5}{\micro\meter}, before calculating the total area in \si{\milli\meter\square}.
+We also calculate regions which are covered thrice by different extrusion segments and add twice its area to the total overfill area amount.

### 2019-08-30 6_validation.tex
Tim: redo computational results and comparison

@@
 \subsubsection{Uniformity}
-Depending on the printer hardware configuration, some bead widths might be difficult to produce;
-too narrow beads might result in fluttered extrusion and too wide beads might require a pressure in the nozzle beyond the specifications of the machine or they might bulge upward on the sides.
-Moreover, bead widths deviating from the preferred bead width by a large amount may be hard to realize and may impact the mechanical properties of the print.
 We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
-
-To evaluate the uniformity of the width,
-we calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
+We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
 \cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.

### 2019-08-30 8_discussion.tex
Tim: redo computational results and comparison

@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-We can therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
+We therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
 This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
@@
 This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
-
-However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we can clearly see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
+However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
 Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).

### 2019-08-30 1_intro.tex
probably i did some minior changes without pushing - Jun

--- 2019-08-30 1_intro.tex
@@
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
-Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Liu2019a,Al-Ketan2018,Maskery2018} and topology optimized structures~\cite{Zong2019,Wu2019a,Cheng2019}.
+Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Al-Ketan2018,Maskery2018} and topology optimized structures~\cite{Zegard2016SMO,Wu2019a,Cheng2019}.
 Many of these applications involve 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
-This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014}, where a wide range of widths could be realized by the hardware. 
-For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$.
+This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where a wide range of widths could be realized by the hardware. 
+For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
 However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
@@
 We show that this framework supports multiple schemes on deciding the bead locations and extrusion widths. 
-In particular for FDM printing, we propose a novel scheme which reduces the amount of over- and underfill while the extrusion widths deviate less from nozzle size compared to existing approaches (which are mostly designed for wire and arc additive manufacturing).
+In particular for FDM printing, we propose a novel scheme which reduces the amount of over- and underfill while ensuring a small deviation of extrusion widths from the nozzle size (\cref{intro_wedge} bottom).
 % In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
@@
 \caption{
-Toolpaths for a wedge shape using the uniform offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
-Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
-The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
+Illustration of different toolpath for a wedge shape.
+Top: Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
+Middle: Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
+Bottom: Our approach minimizes over- and underfill with beads close to the nozzle size.
 }

### 2019-08-30 2_related_work.tex
probably i did some minior changes without pushing - Jun

@@
 Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
+\citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
 A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
@@
 Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
-One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices.
+One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
 This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
@@
 From any point in the geometry skeleton to the boundary, the number of contours is constant.
-Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more.
-Toolpath with varying width for 
-In this paper we propose an adaptive beading scheme to address this problem.
+Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
+\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged.
+The variation of width in the central is pronounced (\cref{intro_wedge} middle).
+In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).
 

### 2019-08-30 10_applications.tex
Tim: redo discussio and applciations

@@
 For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
-Gears benefit from the prevention of under- and overfill regions and the distributed bead widths because the more homogeneous extrusion widths cause the part to more closely match the predicted mechanical properties from some homogenization approach.
-\tim{Hopefully you understand now; could you correct the formulation of this sentence please?}
+Gears and similar mechanical parts could benefit from the prevention of under- and overfill regions and the distributed bead widths because the more homogeneous extrusion widths cause the part to more closely
+conform to the presumed homogenized material properties of FDM products.
 
@@
 For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
-An angled Gyroid structure with uniform thickness results in outline shapes with varying width (\cref{applications_gyroid}).
+An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}), which are accurately densely filled using our framework.
+
 Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.

### 2019-08-30 8_discussion.tex
Tim: redo discussio and applciations

@@
 We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
-These defects are presumed to negatively influence the mechanical properties of the parts, and exceed the point that process parameters can be reliably correlated to mechanical properties of the part.
 To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.
@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-We therefore state that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
+We therefore conclude that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
 This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-The inward distributed scheme is introduced with the intention to limit the number of beads deviating from the preferred bead width and to limit the number of angled extrusion segments in transitioning regions.
-This expected effect is difficult to be confirmed when comparing \cref{TEST_Distributed_accuracy} with~\ref{TEST_InwardDistributed_accuracy}, because there are no large solid areas in that specific shape.
-However, when comparing the bead width of the outer toolpaths, \cref{distributed_comparison} and  \cref{widthIndexedHistogram}, we see that the these toolpaths have the preferred bead width more often, which means that errors from inaccuracies due to deviation from the preferred bead width are concentrated near the center of the shape, leaving the dimensional accuracy of the outline shape less affected, if at all.
-Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall (\cref{smoothness}), and with less jaggedness on the contour toolpaths (\cref{smoothness}).
-Therefore, when using the inward distributed scheme the surface of the 3D print is less affected by both width variation and jagged toolpaths, while overfill and underfill are kept at a low percentage.
+It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.
+However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.
+Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
+Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogenous width and affects smaller more centered parts of the print than the other schemes.
 

### 2019-08-30 1_intro.tex
lil abstract change

@@
 because the position and shape of the toolpath can be controlled relatively accurately.
-Filling up a shape using parallel straight lines would expose defects of the size of the nozzle ($\pm 10^2 \mu$), which is generally an order of magnitude larger than the resolution of the positioning system ($\pm 10^1 \mu$).
+Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
 Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

### 2019-08-30 1_intro.tex
Updates from Overleaf

--- 2019-08-30 1_intro.tex
@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
-This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where a wide range of widths could be realized by the hardware. 
+This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where it has been shown that a wide range of widths could be realized by the hardware.
 For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.

### 2019-08-30 2_related_work.tex
Updates from Overleaf

@@
 This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
-Material extraction with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
+Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
 However, we note that the range of possible widths is not unlimited.
@@
 Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
-\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged.
-The variation of width in the central is pronounced (\cref{intro_wedge} middle).
+\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
+The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
 In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).

### 2019-08-30 0_main.tex
Updates from Overleaf
fix article template and corresponding author

@@
 \author[tud]{Eugeni L. Doubrovski}
-\author[tud]{Jun Wu}
-\author[cuhk]{Charlie Wang{\corref{cor1}}}
-\ead{cwang@mae.cuhk.edu.hk}
+\author[tud]{Jun Wu{\corref{cor1}}^*}
+\ead{j.wu-1@tudelft.nl}
+\author[cuhk]{Charlie Wang}
+% \ead{cwang@mae.cuhk.edu.hk}
 \cortext[cor1]{Corresponding author}
@@
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
-Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
-%address this issue by making local alterations to the toolpaths locations and widths in the center of the part.
-%In this paper we present a framework which allows to distribute the alterations from the center to the boundary.
-In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths from the center outward.
+Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
+%Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
+In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
 Furthermore, we propose a novel scheme for FDM printing which avoids extreme bead width deviation from the nozzle size, and limits the number of altered toolpaths.

### 2019-08-30 4_method.tex
Updates from Overleaf

@@
 Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
-\subref{shape_decomposition_datastructure} We can represent a skeleton using a half-edge data-structure.
+\subref{shape_decomposition_datastructure} The skeleton is represented using a half-edge data-structure.
 }
@@
 Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
-Outline in black, medial axis edges in red, radial edges in grey.
+Outline in black, central edges marked in blue, other edges in grey.
 \subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
-\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) of the transitions to a different bead count should be.
+\subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) where the bead count transitions.
 \subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.

### 2019-08-30 0_main.tex
caption and some random changes. - Jun

@@
 \begin{document}
-\baselineskip11pt % SPM template
+\baselineskip11pt
 
-\begin{frontmatter} % SPM template
+\begin{frontmatter}
 
@@
 \author[tud]{Eugeni L. Doubrovski}
-\author[tud]{Jun Wu{\corref{cor1}}^*}
+\author[tud]{Jun Wu\corref{cor1}}
 \ead{j.wu-1@tudelft.nl}
+\cortext[cor1]{Corresponding author}
 \author[cuhk]{Charlie Wang}
 % \ead{cwang@mae.cuhk.edu.hk}
-\cortext[cor1]{Corresponding author}
 \address[um]{Ultimaker, Utrecht, The Netherlands}
@@
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
-Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
+Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities
+%Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
 %Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.

### 2019-08-30 10_applications.tex
caption and some random changes. - Jun

@@
 For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
-Gears and similar mechanical parts could benefit from the prevention of under- and overfill regions and the distributed bead widths because the more homogeneous extrusion widths cause the part to more closely
-conform to the presumed homogenized material properties of FDM products.
+For gears and similar mechanical parts that are designed with finite element analysis, the less variation in extrusion widths is closer to the assumptions under fast analysis (e.g.
+using homogenization~\cite{Liu2016CAD}).
 
 Of particular interest are microstructures that could be uniquely fabricated by 3D printing.
-Microstructures which have layers with varying widths benefit from the prevention of under- and overfill, which will result in structures with mechanical properties closer to expectation.
 For example, topology optimized bone-like structures~\cite{wu2017infill} contain filaments of varying thickness that follow a varying stress direction (\cref{applications_bone}).
-An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}), which are accurately densely filled using our framework.
-
+An angled Gyroid structure with uniform thickness also results in outline shapes with varying width (\cref{applications_gyroid}). 
+These structures are accurately densely filled using our framework.
 Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
@@
 From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
+\jun{is it easy to embed the color lengend here so readers don't have to flip}
 }

### 2019-08-30 4_method.tex
caption and some random changes. - Jun

@@
 Applying bead counts and transitioning on a shape showing the difference between a simple ST (top) and a mirrored version with small perturbations in the outline (bottom).
-Outline in black, central edges marked in blue, other edges in grey.
-\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked regions (blue).
+Outline in black, central edges marked in blue, radial edges in grey.
+\subref{beading_transitioning_filtering__bead_count} First we initialize the bead counts (black) in the marked edges (blue).
 \subref{beading_transitioning_filtering__transition_mids} We then extract the anchor locations (purple) where the bead count transitions.
-\subref{beading_transitioning_filtering__filtered} We then filter out regions of constant bead count.
+\subref{beading_transitioning_filtering__filtered} We then filter out regions which exhibit frequent transition.
 \subref{beading_transitioning_filtering__transition_ends} We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
@@
 \caption{
-Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
+Sharp turns around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
 }

### 2019-08-30 5_generalization.tex
caption and some random changes. - Jun

@@
 
-\subsection{Beading schemes}
+% \subsection{Beading schemes}
 We introduce several beading schemes which determine the bead count and their widths in various ways.
@@
 \citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$.\cite{Jin2017JMS}
+Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}.
 We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

### 2019-08-30 6_validation.tex
caption and some random changes. - Jun

@@
 \caption{
-Visualizing the overfills and underfills and the widths for various beading schemes.
+Visualization of the overfills and underfills (top) and the widths (bottom) for various beading schemes.
 Extrusion beads in gray tones,
@@
 \caption{
-Results of computational analysis of the results from applying the uniform width technique and various beading schemes using our framework to the data set.
+Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
 Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.

### 2019-08-30 12_conclusions_future_work.tex
dash in contour-parallel

@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
 Our framework is flexible, demonstrated by the several beading schemes which emulate existing techniques.

### 2019-08-30 2_related_work.tex
dash in contour-parallel

@@
 % basic toolpath strategies and their variations
-Direction parallel and contour parallel are two basic toolpath strategies.
+Direction parallel and contour-parallel are two basic toolpath strategies.
 Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
 These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
-Contour parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
+Contour-parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
 \citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
@@
 Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
-One of the problems with contour parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
+One of the problems with contour-parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
 This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
-To avoid problems with such gaps, hybrid approaches that combine direction and contour parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
-Close to the slice boundary, there are a few contour parallel curves, while in the interior there is a zig-zag pattern.
+To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
+Close to the slice boundary, there are a few contour-parallel curves, while in the interior there is a zig-zag pattern.
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
@@
 Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
-Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour parallel toolpath. 
+Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour-parallel toolpath. 
 The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.

### 2019-08-30 4_method.tex
dash in contour-parallel

@@
 
-Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
+Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
 

### 2019-08-30 1_intro.tex
dash in contour-parallel
lil edit

@@
 Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
-Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.
+Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.
 
@@
 For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
-However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
+However, for FDM printing, it is challenging to accurately realize varying width by extruding material through a nozzle with a fixed size, either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
 Therefore, a much narrower range of widths is desirable for robust FDM fabrication.

### 2019-08-31 1_intro.tex
Tim redo intro

@@
 Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
-Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.
+Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
 
@@
 However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and areas which are not filled at all: \emph{underfill} areas.
-See \cref{intro_wedge}(top).
+See \cref{intro_wedge_uniform}.
 Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
-This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where it has been shown that a wide range of widths could be realized by the hardware.
-For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
-However, for FDM printing, it is challenging to accurately realize varying width by extruding material through a nozzle with a fixed size, either by varying the movement speed or by dynamically adjusting the volumetric flow rate.
-Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
-On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
-% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
+Wire and arc additive manufacturing supports a wide range of widths~\cite{Ding2014,Xiong2019},
+which led \citeauthor{Ding2016a} to develop a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}.
+However, the limitations on width imposed by the hardware system are far greater for FDM.
+A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
+%Therefore, a limited range of widths is required by the hardware system.
 
-In this paper we propose a framework for planning toolpath with adaptive width for minimizing over- and underfill. 
-We show that this framework supports multiple schemes on deciding the bead locations and extrusion widths. 
-In particular for FDM printing, we propose a novel scheme which reduces the amount of over- and underfill while ensuring a small deviation of extrusion widths from the nozzle size (\cref{intro_wedge} bottom).
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
+See \cref{intro_wedge_centered}.
+Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g.
+linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size, which influences mechanical and surface properties of the part~\cite{N.Turner2014,ahn2002anisotropic}.
+Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
+Therefore, a narrower range of widths is desirable.
+
+In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill. 
+We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
+For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
+See \cref{intro_wedge_distributed}. 
 % In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
@@
 \begin{figure}\centering
-\includegraphics[width=\columnwidth]{sources-intro-TEST-naive-accuracy.png}
-\includegraphics[width=\columnwidth]{sources-intro-TEST-Center-widths.png}
-\includegraphics[width=\columnwidth]{sources-intro-TEST-InwardDistributed-widths.png}
+\setlength{\figwidth}{.9\columnwidth}
+\setlength{\figwidthTwo}{.05\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-InwardDistributed-widths.png}
+\end{subfigure}
 \caption{
 Illustration of different toolpath for a wedge shape.
-Top: Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
-Middle: Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
-Bottom: Our approach minimizes over- and underfill with beads close to the nozzle size.
+\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
+\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with beads close to the nozzle size.
 }
@@
 
-% There is a large body of literature on relating process parameters such as bead width to various mechanical properties of the end part.
-% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
-% In order to accurately fabricate a part restricted to prescribed mechanical properties, we need to generate toolpaths using the corresponding process parameters as close as possible.
-% We therefore develop a framework which can be used to generate toolpaths which not only avoid over- and underfill, but also keep the bead width closer to the preferred bead width compared to existing techniques.
-% See \cref{intro_wedge}(bottom).
-
-%\subsection{Contributions}
-% A polygonal shape with a width of a fractional multiple of the preferred bead width will always result in the bead widths deviating from the preferred bead width by the fractional part in total,
-% because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
-% We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the preferred width.
 Our contributions are as follows:
 \begin{itemize}
-\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which maps a feature diameter to a number of beads and their widths.
-\item A specific beading scheme for FDM printing which reduces the amount of beads with greatly deviating width, and which promotes smooth toolpaths that are close to the preferred width toward the outline of the shape.
-% \begin{itemize}
-% \item Accurately filling a 2D outline with extrusion beads
-% \item Reducing the overfill and underfill areas compared to the uniform width technique
-% \item Reducing the amount of beads with greatly deviating width compared to existing literature
-% \item Promoting smooth toolpaths which are close to the preferred width toward the outline of the shape.
-% \end{itemize}
+\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.
+\item A specific beading scheme for FDM printing which reduces the amount of deviation in the extrusion widths, and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.
 \end{itemize}

### 2019-08-31 1_intro.tex
Tim: redo related work

@@
 Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g.
-linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size, which influences mechanical and surface properties of the part~\cite{N.Turner2014,ahn2002anisotropic}.
+linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size.
 Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.

### 2019-08-31 2_related_work.tex
Tim: redo related work

@@
 % This paragraph explains what toolpath generation is, and the context where toolpath generation is positioned in
-Given a planar contour, representing the intersection of a plane and a 3D solid object, the task is to generate a path in the domain bounded by the contour.
+%Toolpath generation for deposition based additive manufacturing consists in generating geometric paths which the nozzle follow during printing.
+%Extrusion toolpaths are generated within the planar contour of a layer at the intersection of a horizontal plane and a 3D solid object.
+Toolpath generation consists in generating a path in the a planar contour, representing the intersection of a plane and a 3D solid object.
 The nozzle is then instructed to move along the path while extruding material.
-The deposited material covers the path with a certain width.
+Sites along the toolpath are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
 Toolpath generation is an integral part of process planning for 3D printing.
@@
 In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
-This is sometimes called dense infill~\cite{Livesu2017CGF}.
+This is sometimes called `dense infill'~\cite{Livesu2017CGF}.
 
 % criteria for toolpath generation
-Toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object.
-There are a few desirable properties for the toolpath.
-First, the path shall be as continuous as possible.
+The toolpath has a direct influence on the printing time, material cost, and mechanical properties of the printed object~\cite{N.Turner2014,ahn2002anisotropic}.
+FDM calls for toolpaths with several desirable properties.
+First, the extrusion path should be as continuous as possible.
 A discontinuous path requires to stop and restart material extrusion.
-For certain material such as TPU, this could lead to material defects~\cite{KUIPERS2019CAD}.
-Furthermore, a smooth path is often preferred.
+For certain materials such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
+Second, the toolpath is preferred to be smooth.
 Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
-Second, the path, extended with a certain width, ideally shall cover the bounded region without voids or gaps --  underfilling, and no overlap -- overfilling. 
+Third, the extruded path should cover a the region of the contour without gaps.
+Such underfill negatively influences the mechanical performance of the parts.
+Fourth, the extrusion paths should not overlap with one another.
+Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in further paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
 An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
-Our method is primarily concerned with minimizing under- and overfill within slices, i.e. horizontal cross-sections.
+Our method is primarily concerned with minimizing under- and overfill within horizontal cross-sections.
 
 % basic toolpath strategies and their variations
-Direction parallel and contour-parallel are two basic toolpath strategies.
-Direction parallel (or zig-zag) toolpath fills an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
-These parallel segments are linked at one of their extremities, to avoid frequent stop and restart.
-Contour-parallel toolpath typically consists of a set of equally spaced offset contours from the slice boundary.
-\citeauthor{steuben2016implicit} presented implicit slicing and made an interpretation of 2D contour computing as evaluating intersections in 3D~\cite{steuben2016implicit}.
-A strategy to connect the parallel offsets was introduced in~\cite{KUIPERS2019CAD}. This approach however introduces sharp turns.
-To reduce the number of sharp turns, and thereby enable faster motions, \citeauthor{Zhao2016} proposed to use Fermat spiral to cover the contour~\cite{Zhao2016}. 
-Spiral toolpaths have also been applied to machining~\cite{Held2009,Huang2017}.
-One of the problems with contour-parallel toolpath is that it tends to leave gaps within the slices (\cref{intro_wedge} top).
-This is due to the fact that the offset contour meets around the medial axis and the remaining space might not exactly match the (constant) deposition width.
+Two basic strategies for dense toolpath generation are direction-parallel and contour-parallel.
+Direction-parallel (or zig-zag) toolpaths fill an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
+These parallel segments are linked together at one of their extremities, to avoid discontinuous extrusion.
+Contour-parallel toolpaths typically consists of a set of equally spaced offsets from the slice boundary outline polygons.
+\citeauthor{steuben2016implicit} presented a method for generating sparse infill toolpaths based on the isocontours of surface plots of some variable generated on each 2D contour~\cite{steuben2016implicit}.
+In order to increase the continuity of contour-parallel toolpaths, a strategy to connect dense toolpaths into spirals was introduced by \citeauthor{Zhao2016}~\cite{Zhao2016} and later extended to also connect a mixture of dense and sparse toolpaths together~\cite{KUIPERS2019CAD}.
+\citeauthor{Jin2017RCIM} discusses several approaches for connecting direction-parallel and contour-parallel toolpaths into continuous paths~\cite{Jin2017RCIM}.
+Spiral toolpaths have also been applied to (CNC) machining~\cite{Held2009,Huang2017}.
+One of the problems with contour-parallel toolpath is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
+This is due to the fact that the diameter of the part is not exact multiple of the (cosntant) deposition width in those regions.
 To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
-Close to the slice boundary, there are a few contour-parallel curves, while in the interior there is a zig-zag pattern.
+Close to the slice boundary, there are several contour-parallel curves, while in the interior is filled using a zig-zag pattern.
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
@@
 This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
-Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
-However, we note that the range of possible widths is not unlimited.
-For instance, printing a width that is triple the nozzle diameter is challenging.
-Our method to reduce underfilling is related to the work by \citeauthor{kao1998optimal}~\cite{kao1998optimal}.
-Instead of uniform offsetting, they produced adaptive offsetting toolpaths based on the geometry skeleton. 
-Skeleton was also used in~\cite{Jin2017RCIM} to construct a skeleton-based path for alleviating under- and over-filling in contour-parallel toolpath. 
-The adaptive offsetting approach by \citeauthor{kao1998optimal} handles simple geometry where there are no branches in the medial axis.
+%Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
+\citeauthor{kao1998optimal} propose smooth adaptive toolpaths based on the medial axis skeleton of the boundary contour~\cite{kao1998optimal}.
+Their approach handles simple geometry where there are no branches in the medial axis.
 An extension was proposed by \citeauthor{Ding2016a} to handle complex shapes~\cite{Ding2016a}.
-For this purpose, they made use of the medial axis to decompose the slice into a set of simple geometries.
-This extension, however, inherits a problem in the original method.
-From any point in the geometry skeleton to the boundary, the number of contours is constant.
-Since the distance may vary considerably, this strategy leads to a toolpath with widths that may differ by a factor of two or more, which is challenging for FDM prinring.
-\citeauthor{Jin2017JMS} proposed to add a toolpath with varying width along the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
-The resulting variation of width in the central is pronounced (\cref{intro_wedge} middle).
-In this paper we propose a novel scheme to distribute the width variations from center to boundary, and thus limits the width variation (\cref{intro_wedge} bottom).
+However, this extension inherits a problem in the original method:
+from any point in the skeleton to the boundary, the number of toolpaths is constant.
+Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
+\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
+The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
+In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurence of extreme deviations in width (see \cref{intro_wedge_distributed}).
 

### 2019-08-31 8_discussion.tex
Tim: redo related work

@@
 That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
-Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath.
+Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
 Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
-Using a filament feeder directly mounted on the print head (a.k.a. direct drive) outperforms Bowden style FDM printers in terms of dynamic flow changes,
-but still requires some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
+Using a filament feeder directly mounted on the print head (a.k.a.
+direct drive) can control the flow more dynamicaly then FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
+Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
 Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.

### 2019-08-31 2_related_work.tex
move thin geometric features paragraph up in related work
now the section ends in what our paper fixes

@@
 Our method is primarily concerned with minimizing under- and overfill within horizontal cross-sections.
+
+% the context where our method can be positioned, and some related problems in that context
+Under- and over-filling issues have a large proportional impact for thin geometric features.
+\citeauthor{Jin2017a} proposed the use of a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
+Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
+\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
+\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
 
@@
 In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurence of extreme deviations in width (see \cref{intro_wedge_distributed}).
-
-% the context where our method can be positioned, and some related problems in that context
-Under- and over-filling are especially problematic for thin geometric features.
-\citeauthor{Jin2017a} proposed the use of a wavy path pattern for thin-walled parts~\cite{Jin2017a}.
-This pattern is intended to be sparse. 
-Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
-\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
-\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
 

### 2019-08-31 12_conclusions_future_work.tex
Tim: finetune conclusion etc

@@
 We presented the inward distributed beading scheme.
-It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of adaptive bead width on mechanical properties of the resulting print.
-Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realizes adaptive bead width.
+It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
+which in turn can be helpful to efficiently simulate an FDM manufactured part.
+Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
 
 The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for example in architectural models, prototypes for casings or microstructures.
-Meanwhile it leaves most of the toolpaths the same as the uniform width technique in case of wide contours, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
+Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
 

### 2019-08-31 1_intro.tex
Tim: finetune conclusion etc

@@
 See \cref{intro_wedge_centered}.
-Still, controlling the extrusion width through speed changes or through volumetric flow control (e.g.
-linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size.
+Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g.
+linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
+since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
 Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.

### 2019-08-31 20_dataset.tex
spell check

@@
-\section{Dataset}\label{dataset}
-The dataset we tested on was a custom selected set of open source 3D models found on the internet which was selected to cover a broad range of different types of application and geometry.
+\section{Data set}\label{dataset}
+The data set we tested on was a custom selected set of open source 3D models found on the internet which was selected to cover a broad range of different types of application and geometry.
 Applications range from prototypes, to fixtures and mechanical end-use parts.

### 2019-08-31 2_related_work.tex
spell check

@@
 One of the problems with contour-parallel toolpath is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
-This is due to the fact that the diameter of the part is not exact multiple of the (cosntant) deposition width in those regions.
+This is due to the fact that the diameter of the part is not exact multiple of the (constant) deposition width in those regions.
 To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
@@
 The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
-In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurence of extreme deviations in width (see \cref{intro_wedge_distributed}).
+In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme deviations in width (see \cref{intro_wedge_distributed}).
 

### 2019-08-31 4_method.tex
fix small problems
spell check

@@
 \paragraph{Beading propagation}
-The beading information is then broadcasted throughout the ST from central regions outward,
+The beading information is then broadcast throughout the ST from central regions outward,
 so that each unmarked node $v$ knows the beading of the marked node on top of the ramp on which $v$ is placed.
@@
 \includegraphics[height=\figheight]{sources-method-segment-generation.pdf}
-\caption{Extrusion segment chaining}\label{shape_decomposition_domains}
+\caption{Extrusion segment chaining}\label{segment_generation_chaining}
 \end{subfigure}
@@
 Such intersections cause overfill because the nozzle passes the location multiple times.
-We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greadily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
+We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greedily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
 In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.

### 2019-08-31 6_validation.tex
spell check

@@
 We therefore measured the angle between consecutive extrusion segments generated by each scheme
-and report on the occurence of each angle in \cref{smoothness}.
+and report on the occurrence of each angle in \cref{smoothness}.
 All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).

### 2019-08-31 8_discussion.tex
Tim: finetune conclusion etc
spell check

@@
 We therefore conclude that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
-This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
+%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
@@
 Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
-Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogenous width and affects smaller more centered parts of the print than the other schemes.
+Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.
 
@@
 That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
-Varying the movement speed can be utilised to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
+Varying the movement speed can be utilized to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
 Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.

### 2019-08-31 0_main.tex
fix small problems
fix figures and remove comments
syntax fixes all over the paper

@@
 
-    \newcommand{\todo}[1]{\hl{#1}}
-
-	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
-	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
-	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
-
-	\newcommand{\old}[1]{\textcolor{gray}{#1}}
+%    \newcommand{\todo}[1]{\hl{#1}}
+%    
+%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
+%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
+%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
+%	
+%	\newcommand{\old}[1]{\textcolor{gray}{#1}}
 
@@
 \begin{abstract}
-3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
+3D printing techniques such as Fused Deposition Modeling (FDM) have enabled fabricating complex geometry quickly and cheaply. 
 By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.

### 2019-08-31 10_applications.tex
fix figures and remove comments
syntax fixes all over the paper

@@
 Toolpath with varying width is particularly meaningful for narrow parts, since there the negative effect of under- and overfill is more pronounced than in wide parts.
-In extreme cases, thin features might not be filled at all.
+In extreme cases, thin features will not be filled at all.
 Therefore, our framework, while working for wide parts as well, shows most of its potential for objects which contain thin parts.
@@
 
-For architectural models and casings, the prevention of over- and underfill is expected to make them stronger. 
-For embossed text, the prevention of underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
+For architectural models and casings, preventing over- and underfill is expected to make them stronger. 
+For embossed text, preventing underfill reduces the various holes in the top surfaces, which is detrimental to the visual quality of those top surfaces.
 For gears and similar mechanical parts that are designed with finite element analysis, the less variation in extrusion widths is closer to the assumptions under fast analysis (e.g.
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-house.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-david.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-tud-logo.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-gyroid.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight]{sources-applications-hex-grid.png}
@@
 \end{subfigure}
+\begin{subfigure}[t]{.3\figwidth}
+\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
+\end{subfigure}
 \caption{
 Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
-A legend for the colors can be found in \cref{visualized_accuracy}.
 From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
-\jun{is it easy to embed the color lengend here so readers don't have to flip}
 }

### 2019-08-31 12_conclusions_future_work.tex
syntax fixes all over the paper

@@
 It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
-which in turn can be helpful to efficiently simulate an FDM manufactured part.
+which in turn is helpful to efficiently simulate an FDM manufactured part.
 Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.

### 2019-08-31 1_intro.tex
syntax fixes all over the paper

@@
 Fused Deposition Modeling (FDM) is one of the most common 3D printing techniques.
-It is widely used because of the versatility in the types of plastics which can be used and the relatively low running costs.
+It is widely used because of the versatility in the types of plastic which can be used and the relatively low running costs.
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
@@
 because the position and shape of the toolpath can be controlled relatively accurately.
-Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
+Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
 Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
 
-The simple technique for generating the dense contour-parallel toolpaths of a layer consists in performing uniform inward offsets with the radius of the nozzle from the outline shape.
+The simple technique for generating the dense contour-parallel toolpaths of a layer consists in performing uniform inward offsets with the size of the nozzle from the outline shape.
 However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and areas which are not filled at all: \emph{underfill} areas.

### 2019-08-31 2_related_work.tex
syntax fixes all over the paper

@@
 Second, the toolpath is preferred to be smooth.
-Sharp turns require to slow down the movement of the nozzle, and this consequently prolongs the printing process.
+Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
 Third, the extruded path should cover a the region of the contour without gaps.
@@
 Under- and over-filling issues have a large proportional impact for thin geometric features.
-\citeauthor{Jin2017a} proposed the use of a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
+\citeauthor{Jin2017a} proposed a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
 Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
@@
 Close to the slice boundary, there are several contour-parallel curves, while in the interior is filled using a zig-zag pattern.
-For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them, the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
+For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
 Alternative toolpath patterns, seen also in CNC machining, include space-filling curves~\cite{Cox1994CAD,Griffiths1994,Shaikh2016}.

### 2019-08-31 4_method.tex
syntax fixes all over the paper

@@
 
-As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes in the skeleton that are located in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
+As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes of the skeleton in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
 The heights $\tilde{b}$ at these elements are then quantized to an integer number of beads $\bar{b}$.
@@
 We employ a shape decomposition similar to the one proposed by \citeauthor{Ding2016a}~\cite{Ding2016a}. 
-The basic idea is to add edges connecting each node $v$ on the medial axis to (all of) its supports, $\text{sup}(v)$. 
+The basic idea is to add edges connecting each node $v$ on the medial axis to each of its support points $\text{sup}(v)$. 
 The resulting skeleton decomposes the outline shape into trapezoids and triangles.
@@
 
-The edges generated by the MAT can be classified into three types:
+The edges generated by the MAT are classified into three types:
 \begin{enumerate*}
@@
 The vertex-line and vertex-vertex edges are discretized into pieces with a length up to $d^\text{discretization}$.
-This allows to approximate the feature radius in between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 
+This allows to approximate the feature radius between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 
 Again we connect the newly inserted nodes to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
@@
 %The result is a mesh representing the union of cones (UoC) consisting entirely of quads and triangles.
-Note that although the overview of the method has been described geometrically in terms of the UoC, the actual toolpath generation relies on the two-dimensional ST, while the use of the bead count as a height value is only a visualization aid.
+Note that although the overview of the method was described geometrically in terms of the UoC, the actual toolpath generation relies on the two-dimensional ST;
+the use of the bead count as a height value is only a visualization aid.
 
@@
 The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
-Note that the Voronoi diagram contains, in addition to the medial axis, edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
+Note that besides the full medial axis, the Voronoi diagram also contains edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
 These extra edges are a subset of the edges connecting a node to its support, so we keep them in.
@@
 The remainder is called peripheral.
-Our framework will decide on a beading at all of the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).
+Our framework will decide on a beading at all the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).
 
@@
 This ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.
-For vertex-line edges and vertex-vertex edges only a portion of the edge may be significant.
+For vertex-line edges and vertex-vertex edges only a portion of the edge is significant.
 We therefore introduce nodes at the boundaries of the significant portion during the discretization of such edges (see Appendix~\ref{edge_discretization}).
@@
 $q(d) = \left\lfloor d / w^* + \nicefrac12 \right\rfloor$.
-Alternative quantization schemes will be discussed in \cref{sec_generalization}.
+Alternative quantization schemes are discussed in \cref{sec_generalization}.
 By applying $q$ to the heights of central nodes we quantize the bead count:
@@
 A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
-A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
+We introduce a transition length $t(n)$ to ensure a smooth transition (see \cref{transitions}). 
 The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
 $t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,
-where $\Delta$ is the total distance along the edges in between two nodes.
+where $\Delta$ is the total distance along the edges between two nodes.
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
 In order to make the transition ramps robust against small perturbations in the outline shape which cause extra (support) edges in the skeleton,
-we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
+we modify the nodes $v_x$ which are between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
 \begin{equation}
@@
 Because the bead count is defined in terms of the feature diameter rather than the radius, only some of the bead count values $\hat{b}$ in a central region coincide with a slicing height.
-When the bead count $\hat{b}$ is even, the ridge will be sliced as normal;
+When the bead count $\hat{b}$ is even, the ridge is sliced as normal;
 the intersection between a slicing plane and the mesh surface results in a polyline on both sides of the ridge, which are connected together into a polygonal toolpath.
@@
 
-All trapezoids in the ST can be assigned to separate domains, corresponding to which boundary polygon they are connected to (see \cref{shape_decomposition_domains})~\cite{Ding2016a}.
+All trapezoids in the ST are assigned to separate domains, corresponding to which boundary polygon they are connected to (see \cref{shape_decomposition_domains})~\cite{Ding2016a}.
 By traversing the trapezoids in per domain in order we can efficiently connect all segments into polylines.

### 2019-08-31 5_generalization.tex
fix figures and remove comments
spell check
syntax fixes all over the paper

@@
 A critical component in toolpath generation is how to distribute the beads over the feature radius.
-While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3d printer or material.
+While the framework presented in the previous section takes evenly distributed beads as an example, it allows to apply different beading schemes to configure the bead distribution to cater for specific requirements from the application, 3D printer or material.
 
@@
 \item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
-\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
+\item For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
 \end{enumerate}
@@
 We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
-We also introduce new beading schemes which produce toolpaths with less extremal widths compared to techniques from existing literature.
+We also introduce new beading schemes which produce toolpaths with less extreme widths compared to techniques from existing literature.
 
@@
 \paragraph{Outer bead}
-We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
+We can emulate the method from \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
 Also we turn off the reduction of toolpaths near 3-way intersections $d_\text{max}^\text{intersection} = \SI{0}{\percent}$, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.
@@
 \paragraph{Constant bead count}
-We can emulate the method by \citeauthor{Ding2016a}, by dividing the feature radius over the widths of a constant number of beads.
+We can emulate the method from \citeauthor{Ding2016a} by dividing the feature radius over the widths of a constant number of beads.
 Additionally in order to emulate their definition of ``branches'' we mark all ST edges we unmark the outer edges connected to the outline shape in a separate algorithm.
@@
 \paragraph{Centered}
-We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
+We can emulate the method from \citeauthor{Jin2017JMS} by transcribing how they deviate from the uniform width toolpaths.
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
@@
 We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
-We determine the local bead count by dividing the diameter by the prefered bead width and rounding to the nearest integer.
+We determine the local bead count by dividing the diameter by the preferred bead width and rounding to the nearest integer.
 This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.
@@
 This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions.
-% and it forces most of the beads to have exactly the prefered width.
+% and it forces most of the beads to have exactly the preferred width.
 %Moreover, the bead widths equal the preferred bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
@@
 \setlength{\figheight}{.25\columnwidth}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-evenly.png}
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
+\begin{subfigure}[t]{\figwidth}\centering
 \includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-inward.png}
@@
 \end{subfigure}
-\begin{subfigure}{.1\columnwidth}\centering
+\begin{subfigure}[t]{.1\columnwidth}\centering
 \includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}

### 2019-08-31 6_validation.tex
syntax fixes all over the paper

@@
 We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
-These results indicate that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
+These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
 We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
@@
 All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
-We observe that compared to the naive method our framework produces less acute angles which, but more obtuse angles.
+We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
 The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
@@
 We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
-However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extremal bead widths.
+However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
 The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
@@
 The uniform technique produces distinct underfill areas.
-The centered scheme shows some defects due to inaccurate control of extremal deposition widths.
+The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
 The inward distributed scheme produces the least defects.

### 2019-08-31 8_discussion.tex
syntax fixes all over the paper

@@
 Note that most overfill areas occur near regions of alternating bead width. 
-For an input outline shape which contains both very small and very large features, the the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
+For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
@@
 
-Another limiting factor in the adoption of adaptive bead width is the format of G-code which stores machine instructions.
+Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
 G-code does not support moves with varying cross-sectional area.

### 2019-08-31 1_intro.tex
cite cura

@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
-Wire and arc additive manufacturing supports a wide range of widths~\cite{Ding2014,Xiong2019},
-which led \citeauthor{Ding2016a} to develop a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}.
-However, the limitations on width imposed by the hardware system are far greater for FDM.
+\citeauthor{Ding2016a} developed a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}.
+This toolpath strategy was applied to wire and arc additive manufacturing~\cite{Ding2014,Xiong2019},
+However, the allowable width variation for FDM systems is much narrower.
 A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
@@
 
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} is employing a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS},
+which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
 See \cref{intro_wedge_centered}.
@@
 since process parameters such as nozzle temperature are optimized for beads with the nozzle size.
-Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a heterogeneity assumption.
+Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
 Therefore, a narrower range of widths is desirable.

### 2019-08-31 1_intro.tex
some small changes in intro. and related work - Jun

@@
 
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS},
-which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS}.
 See \cref{intro_wedge_centered}.

### 2019-08-31 10_applications.tex
TIm: lil fixes

@@
 Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
-From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
+From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.
 }

### 2019-08-31 2_related_work.tex
some small changes in intro. and related work - Jun
tim: dont focus too much on our method in related work

@@
 
-% the context where our method can be positioned, and some related problems in that context
-Under- and over-filling issues have a large proportional impact for thin geometric features.
-\citeauthor{Jin2017a} proposed a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
-Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
-\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
-\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
-
 % basic toolpath strategies and their variations
@@
 % the idea, and (some of) the most related work
-Our approach to reduce under- and over-filling is to deposit material with a varying width.
-This allows the opportunity to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
+Reducing under- and over-filling can be accurately achieved by making use over adaptive depisition width.
+Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
 %Material extrusion with a varying width can be realized by changing the extrusion rate or the nozzle travel velocity~\cite{Ertay2018,Kuipers2018}.
@@
 In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme deviations in width (see \cref{intro_wedge_distributed}).
+
+% the context where our method can be positioned, and some related problems in that context
+Under- and over-filling issues have a large proportional impact for thin geometric features.
+\citeauthor{Jin2017a} proposed a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
+Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
+\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
+\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.
 

### 2019-08-31 0_cover_letter.tex
latex cover letter

\documentclass[a4paper,12pt]{letter}

% Some of the article customisations are relevant for this class

\name{} % To be used for the return address on the envelope
\signature{
} % Goes after the closing (ie at the end of the letter, with space for a signature)
%\address{Address \\ of \\ Sender}
% Alternatively, these may be set on an individual basis within each letter environment.

\makelabels % this command prints envelope labels on the final page of the document

\begin{document}
\begin{letter}{}

\vspace*{-8\baselineskip}% Correct for vertical displacement

\opening{Dear  Dr. Nelaturi, dear Dr. Tsz-Ho, and dear reviewers,}

We are pleased to submit our manuscript entitled ``A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing'' for consideration for publication in the special issue on Process Planning for Additive/Hybrid Manufacturing of the Computer-Aided Design journal.

3D models with thin parts are difficult to produce using additive manufacturing.
When generating dense contour-parallel toolpaths using uniform-width offsets from the layer outlines,
over- and underfill problems occur in the center of the shape.
Solving this problem by altering the center-most extrusion paths leads to toolpaths with extreme widths, which are difficult to manufacture.
We therefore propose a framework which makes it possible to distribute the alterations over all the toolpaths using an arbitrary width distribution scheme.
In particular, we present one distribution scheme which is shown to produce little over- and underfill, while keeping the bead width closer to the nozzle size than existing methods.

We believe this research is highly relevant to the special issue, since the toolpath generation is a vital part of process planning for additive manufacturing.
Moreover, the accurate manufacturing of thin parts reduces design constraints and enables e.g. the production of microstructures with varying cross-sectional width.

This manuscript describes original work and has not been published and is not under consideration for publication elsewhere.  All authors approved the manuscript and its submission. We have no conflicts of interest to disclose.

It is worth mentioning that we are in the process of filing a patent on the techniques presented in this article. We appreciate your discretion. The implementation will be made open source.

Thank you for your consideration and we are looking forward to your response.

\medskip

Sincerely,

\medskip 
% PhD student at Delft University of Technology, 
Tim Kuipers, Software engineer at Ultimaker \\
Eugeni L. Doubrovski, Assistant professor at  Delft University of Technology \\
Jun Wu, Assistant professor at Delft University of Technology \\
Charlie C. L. Wang, Professor at Chinese University of Hong Kong

%\closing{Sincerely,} % eg Regards,

%\cc{} % people this letter is cc-ed to
%\encl{} % list of anything enclosed
%\ps{} % any post scriptums. ``PS'' labels must be put in manually

\end{letter}
\end{document}

### 2019-08-31 1_intro.tex
Tims lilk edits to intro

--- 2019-08-31 1_intro.tex
@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
-\citeauthor{Ding2016a} developed a toolpath strategy which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a}.
-This toolpath strategy was applied to wire and arc additive manufacturing~\cite{Ding2014,Xiong2019},
-However, the allowable width variation for FDM systems is much narrower.
+\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a,Xiong2019}.
+However, the range of widths manufacturable by FDM systems is limited.
 A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.

### 2019-08-31 0_main.tex
lil changes to abstract

@@
 \begin{abstract}
-3D printing techniques such as Fused Deposition Modeling (FDM) have enabled fabricating complex geometry quickly and cheaply. 
+3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
 By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
-Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities
-%Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which is beyond the capabilities of some hardware systems and difficult to realize accurately for others.
-%Existing approaches for generating toolpath with adaptive width targeted mostly at wire and arc additive manufacturing, and resulted in a large variation in width which is not typically supported by FDM printing.
+Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
@@
 We validate the effectiveness of our framework and this novel scheme on a data set of 300 slices.
-%This scheme reduces the amount of over- and underfill while the extrusion widths deviate less from the nozzle size compared to existing approaches.
 \end{abstract}

### 2019-11-20 5_generalization.tex
make beading schemes figure into table

@@
 
-%\fboxsep=10mm%padding thickness
-\begin{figure}%\centering
-\setlength{\figwidth}{.2\textwidth}
-\setlength{\abovedisplayskip}{0pt}
-\setlength{\belowdisplayskip}{0pt}
-\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-%\frame{
-\begin{align*}
+\begin{table}%\centering
+\caption{
+\revise{Made figure into table}{
+Beading schemes.
+}
+} % revise
+\label{beading_schemes}
+%
+\setlength{\figwidth}{.45\linewidth}
+\captionsetup[subtable]{justification=justified,singlelinecheck=false}
+%
+%
+%
+\begin{tabular}{|l|l|}
+\hline
+%
+%
+\begin{subtable}[b]{\figwidth}
+\smallskip
+\caption{Uniform scheme}\label{formula_uniform}
+$\begin{aligned}
 \alpha_\text{max} &= \SI{180}{\degree} \\
@@
 %L(n,r)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
-\end{align*}
-\caption{Uniform scheme}\label{formula_uniform}
-\end{subfigure}
-}
+\end{aligned}$
+\end{subtable}
 %
 %
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-\begin{align*}
+&
+%
+%
+\begin{subtable}[b]{\figwidth}
+\smallskip
+\caption{Outer bead}\label{formula_outer_bead}
+$\begin{aligned}
 q(d) &=
@@
 %\end{cases}
-\end{align*}
-\caption{Outer bead}\label{formula_outer_bead}
-\end{subfigure}
-}
+\end{aligned}$
+\end{subtable}
 %
 %
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-\begin{align*}
+ \\ \hline
+%
+%
+\begin{subtable}[b]{\figwidth}
+\smallskip
+\caption{Constant bead count}\label{formula_constant_bead_count}
+$\begin{aligned}
 \alpha_\text{max} &= \SI{0}{\degree} \\
@@
 %L(n,r)_i &= 2r / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
-\end{align*}
-\caption{Constant bead count}\label{formula_constant_bead_count}
-\end{subfigure}
-}
+\end{aligned}$
+\end{subtable}
 %
 %
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-\begin{align*}
+&
+%
+%
+\begin{subtable}[b]{\figwidth}
+\smallskip
+\caption{Evenly distributed}\label{formula_evenly_distributed}
+$\begin{aligned}
 q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
@@
 %L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
-\end{align*}
-\caption{Evenly distributed}\label{formula_evenly_distributed}
-\end{subfigure}
-}
+\end{aligned}$
+\end{subtable}
 %
 %
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-\begin{align*}
+ \\ \hline
+%
+%
+\multicolumn{2}{|l|}{
+\begin{subtable}[b]{\linewidth}
+\smallskip
+\caption{Centered}\label{formula_centered}
+$\begin{aligned}
 t(n) &= \frac12 w^* \\
@@
 %\end{cases}
-\end{align*}
-\caption{Centered}\label{formula_centered}
-\end{subfigure}
+\end{aligned}$
+\end{subtable}
 }
@@
 %
-\fbox{
-\begin{subfigure}[b]{\figwidth}\centering
-\begin{align*}
+ \\ \hline
+%
+%
+\multicolumn{2}{|l|}{
+\begin{subtable}[b]{\linewidth}
+\smallskip
+\caption{Inward distributed}\label{formula_inward_distributed}
+$\begin{aligned}
 q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
@@
 \omega(n,r)_i &= \max(0, 1 - N^{-2} (i - (n-1)/2)^2 )
-\end{align*}
-\caption{Inward distributed}\label{formula_inward_distributed}
-\end{subfigure}
+\end{aligned}$
+\end{subtable}
 }
-\caption{
-Beading schemes.
-}
-\label{beading_schemes}
-\end{figure}
+ \\ \hline
+%
+%
+\end{tabular}
+\end{table}
 

### 2019-11-21 1_intro.tex
clarify intro figure shape and use same min feature size

@@
 \begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-InwardDistributed-widths.png}
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
 \end{subfigure}
 \caption{
-Illustration of different toolpath for a wedge shape.
+Illustration of different toolpath for a wedge shape \revise{}{(black)}.
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).

### 2019-11-21 5_generalization.tex
widening figures
extend widening to handle min bead width

@@
 Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
-Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
-We can simply override
+Regions where the model is narrower than some $r_\text{min}$ can be printed with a bead width $w_\text{min}$ larger than the model thickness.
+In order to get results such as in \cref{widening} we can override
 \begin{align*}
+q'(d) &= 
+\begin{cases}
+0 & \text{ if } 0 \leq d < 2 r_\text{min} \\
+1 & \text{ if }  2 r_\text{min} \leq d < w^*  \\
+q(d) & \text{ otherwise}
+\end{cases}
+\\
 W'(n,r)_0 &=
 \begin{cases}
-\max \left( w^*  ,  W(n,r)_0 \right) & \text{ if } n = 1 \\
+\max \left( w_\text{min}  ,  2 r \right) & \text{ if } 2 r < w^* \\
 W(n,r)_0 & \text{ otherwise}
@@
 \end{align*}
+
+\begin{figure}
+\centering
+\setlength{\figwidth}{.45\columnwidth}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
+\caption{$w_\text{min} = 2 r_\text{min} = 0.1$ (Distributed)}
+\end{subfigure}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
+\caption{$w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ (Center)}
+\end{subfigure}
+\caption{
+Widening strategies.
+}
+\label{widening}
+\end{figure}

### 2019-12-04 0_main.tex
revise macro
lil cleanup in main
fix revise command to work with multiple paragraphs
make title FDM specific (reviewer 3.1)
clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)

@@
 
-	\newcommand{\wmin}{w_\text{min}}
-	\newcommand{\wmax}{w_\text{max}}
-	\newcommand{\wout}{w_\text{out}}
-	\newcommand{\win}{w_\text{in}}
-
     % \usepackage[disable]{todonotes} % notes not showed  
@@
 %	\newcommand{\old}[1]{\textcolor{gray}{#1}}
+	\usepackage[normalem]{ulem}
+	\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}
+
+	% Revise macro (usage: \revise{old}{new})
+	% Version a) First arg red and striked out, second argument green
+	\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
+	% Version b) First arg ignored, second argument green
+	%\newcommand{\revise}[2]{\textcolor{blue}{#2}}
+	% Version c) First arg ignored, second argument unchanged (for final draft)
+	%\newcommand{\revise}[2]{#2}
 
@@
 
-\title{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}
+\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}}
 
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
-By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.
+\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
 Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.

### 2019-12-04 0_main.tex
improve language in abstract

@@
 {High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
-Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
+\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
-Furthermore, we propose a novel scheme for FDM printing which avoids extreme bead width deviation from the nozzle size, and limits the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 slices.
+Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
 \end{abstract}

### 2019-12-04 1_intro.tex
fix max bead width deviation in Jin

@@
 
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of $2$~\cite{Jin2017JMS},
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
+% (0.8 * 2) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
 which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.

### 2019-12-04 1_intro.tex
clarify why wedge shape is representative (reviewer 1.6)
clarify contributions (reviewer 1.2)

@@
 \caption{
-Illustration of different toolpath for a wedge shape \revise{}{(black)}.
+Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
@@
 \begin{itemize}
-\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.
-\item A specific beading scheme for FDM printing which reduces the amount of deviation in the extrusion widths, and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.
+\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
+\item A specific beading scheme for FDM printing which \revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to existing literature, and which \revise{promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{produces beads of exactly the preferred width outside of central regions of the outline shape.}
 \end{itemize}

### 2019-12-04 4_method.tex
move method images
fix language mistakes (reviewer 1.7)

@@
-\section{Method}
-\subsection{Overview}
-
-Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates extrusion toolpaths with varying width, i.e.
-a set of polylines where each site consists of a location and an extrusion width;
-in between the sites we linearly interpolate the position and extrusion width.
-
-Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
-We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
-
-As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes of the skeleton in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
-The heights $\tilde{b}$ at these elements are then quantized to an integer number of beads $\bar{b}$.
-To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $\hat{b}$ in between (\cref{sec_central_height_adjustment}).
-The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
-
-% We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
-% explain how to identify central regions in \cref{sec_center_classification}.
-% Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
-% We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
-% and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
-
-This section explains how we generate toolpaths using our framework with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
-In \cref{sec_generalization} we describe how to apply the framework to different beading schemes and we show several such beading schemes.
-
-% The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
-% These offsets can be generated from the medial axis transform (MAT).
-% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape~\cite{blum1967transformation}.
-% The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
-% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing~\cite{eiamsa2003toward}.
-
-% For the uniform offsetting technique the overfill and underfill problems arise in the center,
-% because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
-% Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
-
-% Our framework can be thought of as following these steps:
-% \begin{itemize}
-% \item Compute the skeleton of the input shape
-% \item Assign each node a height in terms of bead count based on the local feature size
-% \item Identify central regions of the UoC
-% \item Quantize the height of central ridges and peaks
-% \item Smooth out sharp transitions between regions with different integer heights
-% \item Determine the heights in the periphery (non-central regions)
-% \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
-% \end{itemize}
-% See \cref{3d_surface_overview}.
-
 \begin{figure*}
@@
 
-\begin{figure}\centering
-\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
-\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
-\label{legend}
-\end{figure}
+\section{Method}
+\subsection{Overview}
+
+Given arbitrarily shaped polygons which represent the 2D outline of a layer of a 3D model, our method generates extrusion toolpaths with varying width, i.e.
+a set of polylines where each site consists of a location and an extrusion width;
+in between the sites we linearly interpolate the position and extrusion width.
+
+Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
+Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
+
+As depicted in \cref{3d_surface_overview_center}, our method first identifies edges and nodes of the skeleton in the center of the polygon, which correspond to ridges and peaks in the UoC  (\cref{sec_center_classification}).
+The heights $\tilde{b}$ at these elements are then quantized to an integer number of beads $\bar{b}$.
+To ensure a smooth toolpath between regions with quantized integer heights that differ, we add new nodes in the skeleton with quantized heights and interpolate the heights $\hat{b}$ in between (\cref{sec_central_height_adjustment}).
+The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
+
+% We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
+% explain how to identify central regions in \cref{sec_center_classification}.
+% Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
+% We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
+% and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
+
+This section explains how we generate toolpaths using our framework with uniform bead widths and evenly distributed locations between the center of the polygon and the outline.
+In \cref{sec_generalization} we describe how to apply the framework to different beading schemes and we show several such beading schemes.
+
+% The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
+% These offsets can be generated from the medial axis transform (MAT).
+% The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape~\cite{blum1967transformation}.
+% The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
+% We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing~\cite{eiamsa2003toward}.
+
+% For the uniform offsetting technique the overfill and underfill problems arise in the center,
+% because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
+% Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.
+
+% Our framework can be thought of as following these steps:
+% \begin{itemize}
+% \item Compute the skeleton of the input shape
+% \item Assign each node a height in terms of bead count based on the local feature size
+% \item Identify central regions of the UoC
+% \item Quantize the height of central ridges and peaks
+% \item Smooth out sharp transitions between regions with different integer heights
+% \item Determine the heights in the periphery (non-central regions)
+% \item Slice the mesh at regular intervals to get the toolpaths to fill the input shape
+% \end{itemize}
+% See \cref{3d_surface_overview}.
 
@@
 Again we connect the newly inserted nodes to their support, which results in vertex-line regions and vertex-vertex regions such as depicted in \cref{legend}.
+
+\begin{figure}\centering
+\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
+\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
+\label{legend}
+\end{figure}
 
@@
 so that we can then deal with beading conflicts in a downward phase.
-This the downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
+\revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
 

### 2019-12-04 4_method.tex
make clear that a skeleton is an undefined term (reviewer 2.1)

@@
 
-Our method starts with computing the skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing \revise{the}{a type of} skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).

### 2019-12-04 4_method.tex
dont say MA is a compact and complete descriptor
lil lang fix

@@
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of planar planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
+Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
 
@@
 \paragraph{Medial axis transform}
-The medial axis is a compact and complete representation of a shape.
+The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
 It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.

### 2019-12-05 1_intro.tex
add patent notice and implementation link

@@
 Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
+\revise{
 Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
+}{
+Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
+This paper focusses on the contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with geometry which is narrower than the typical number of perimeters.
+}
 
@@
 
+\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
+
 %This work is patent pending, but the source code is available open source.

### 2019-12-05 6_2_printing_results.tex
new printing results section

Test prints were performed on an unmodified Ultimaker S5 system,
with a standard  \SI{0.4}{\milli\meter} nozzle
and PLA filament
and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be to varying the speed such that we keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the backpressure that the previous layer exerts on the filament protruding from the nozzle.
We conjecture that the amount of backpressure is monotonically related to the requested line width and compensate for the backpressure using a simple linear model:

\begin{align}
 v(w) &= \frac{f(w)}{h w} \\ 
% f &\sim p \\
% p &= p_\text{in} + p_\text{ext} \\
% p_\text{in} &= C \\
% p_\text{ext} &\sim w \\
% p_\text{ext} &= w / w^* - 1 \\
% f &= f^* - k p_\text{ext} \\
 f(w) &= f_0 - k \left( w / w_0 - 1 \right) \\
 f_0 &= v_0 w_0 h 
% v &= \frac{f^* - k p_\text{ext}}{h w} \\ 
% v &= \frac{v^* w^* h - k (w / w^* - 1)}{h w}
\end{align}
where
$v(w)$ is the movement speed as a function of requested bead width $w$,
$f(w)$ is the filament outflow,
$f_0$ is a constant reference flow
and
$k$ is the amount of backpressure compensation.
Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
$v_0=\SI{30}{\milli\meter\per\second}$, 
$w_0=\SI{0.4}{\milli\meter}$.
See \cref{backpressure}.

\begin{figure}
\centering
\setlength{\figwidth}{0.32\columnwidth}
\setlength{\figheight}{0.5\columnwidth}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation-target.pdf}
\caption{Target widths}\label{backpressure_target}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-zero-backpressure-compensation.png}
\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_backpressure}
\end{subfigure}
\begin{subfigure}[t]{\figwidth}\centering
\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation.png}
\caption{Backpressure compensation}\label{backpressure}
\end{subfigure}
\caption{
Print results of varying width test on top of a dense white raft.
Trying to reproduce \subref{backpressure_target} without backpressure compensation ($k=0$) yields worse results \subref{zero_backpressure} than with backpressure compensation $k=1.1$ \subref{backpressure}.
}
\label{backpressure_compensation}
\end{figure}

### 2019-12-05 6_validation.tex
redo gMAT example images with new pointy wedge bit, and use N=2 for inward distributed
fix analysis figures
colors were weird, figures were swapped and font sizes were unequal
new printing results section

@@
 \includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
-\caption{Inward}\label{TEST_InwardDistributed_accuracy}
+\caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
 \end{subfigure}
@@
 and wide beads in red.
+\revise{New shape contains pointy wedge to see impact on minimal feature size}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
 }
@@
 %\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
-\caption{Site angles without smoothing}
+\caption{Site angles (inward distributed)}
 \label{smoothnessNoTransition}
@@
 \subsection{Printing results}
+\revise{
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
@@
 The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
+}{
+\input{6_2_printing_results}
+}
 

### 2019-12-05 0_reviewer_response.tex
response to reviewers tex

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

\bibliographystyle{elsarticle-num-names}

% ACM template
%
%\documentclass[acmtog,anonymous,timestamp,review]{acmart}
%
%\usepackage{booktabs} % For formal tables
%

% My TK added packages and commands

	% for for using hyperref and elsarticle-num-names together in order to get \citeauthor to work
	\makeatletter
	\providecommand{\doi}[1]{%
	  \begingroup
	    \let\bibinfo\@secondoftwo
	    \urlstyle{rm}%
	    \href{http://dx.doi.org/#1}{%
	      doi:\discretionary{}{}{}%
	      \nolinkurl{#1}%
	    }%
	  \endgroup
	}
	\makeatother

	% have multiline subfigure captions be centered
	\usepackage[labelformat=parens]{subcaption} % subfigures
	\captionsetup[subfigure]{justification=centering}
	\captionsetup{subrefformat=parens} % pure refernce subfigure with parentheses: fig.10a and (b)
	%\renewcommand\thesubfigure{(\alph{subfigure})} % refernce subfigure always with parentheses: fig.10(a) and (b)

	\captionsetup[figure]{labelfont={bf},name={Fig.},labelsep=period} % use `Fig.' for figure subscript instead of `Figure'

	\usepackage[export]{adjustbox} % [right] alignment for includegraphics

	\usepackage{rotating} % turn env for rotating text in figures

	\usepackage{wrapfig} % inline figures

	% tables
	\usepackage{multirow} % multicolumn, multirow
	\usepackage{colortbl} % \cellcolor{<color>}
	\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}   %% centered
	\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}m{#1}}  %% right aligned

	\usepackage[capitalise]{cleveref} % automatically add `Fig.'  etc before a reference.

        \usepackage{ amssymb } % \therefore

	\newcommand{\degree}{^\circ}

	\usepackage[binary-units]{siunitx} % mm and stuff
	\sisetup{per-mode = symbol}
	\DeclareSIUnit\pixel{px}

	\usepackage{units} % \nicefrac{3}{8}

	\DeclareMathOperator*{\argmax}{arg\,max}
	\DeclareMathOperator*{\argmin}{arg\,min}

	\DeclareMathOperator{\abs}{abs} % absolute function

	\usepackage{amsthm} % \begin{proof}
	\newtheorem{lemma}{Lemma}[section]
	\theoremstyle{definition}
	\newtheorem{definition}{Definition}[section]

	\usepackage[inline]{enumitem} % inline enumerate*

	\usepackage[toc,page]{appendix} % appendicces

	\usepackage{pgfplots}
	\usepackage{pgfplotstable} % tikzpicture table plots
	\pgfplotsset{compat=1.15}
	\usetikzlibrary{backgrounds}

	\usepackage[noend]{algpseudocode} % algorithmic
	\usepackage{algorithm} % wrapper for pseudocode to give a caption and label

	\newcommand{\pluseq}{\mathrel{+}=} %pluseq symbol
	\usepackage{upgreek} % \uplambda

	\usepackage{listings} % for listing C++ code instead of pseudocode
	\lstset{ 
      breaklines=true,                 % sets automatic line breaking
      basicstyle=\ttfamily,
      mathescape
    }

    % \usepackage[disable]{todonotes} % notes not showed  
    % \usepackage[draft]{todonotes}   % notes showed
    \usepackage{color,soul} % caps, highlight (\hl)

	\newcommand{\comment}[1]{}

%    \newcommand{\todo}[1]{\hl{#1}}
%    
%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
%	
%	\newcommand{\old}[1]{\textcolor{gray}{#1}}
	\usepackage[normalem]{ulem}
	\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}

	% Revise macro (usage: \revise{old}{new})
	% Version a) First arg red and striked out, second argument green
	\newcommand{\revise}[2]{{\color{red}{{#1}}}{\color{blue}{#2}}}
	% Version b) First arg ignored, second argument green
	%\newcommand{\revise}[2]{\textcolor{blue}{#2}}
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}

	\newcommand{\question}[1]{{\bf#1}}
	\newcommand{\todo}[1]{{\bf \color{orange}#1}}
	\newcommand{\response}[1]{{#1}}

\newcommand\Que[1]{%
   \leavevmode\par
   \stepcounter{question}
   \noindent
   \thequestion. Q --- {\bf#1}\par}

\newcounter{question}
\setcounter{question}{0}

\numberwithin{question}{section}

\usepackage{chngcntr}

\newcommand\subQue[1]{%
   \leavevmode\par
   \stepcounter{subquestion}
   \noindent
   \thesubquestion. Q --- {\bf#1}\par}

\newcounter{subquestion}
\setcounter{subquestion}{0}

\counterwithin{subquestion}{question}

\newcommand\Ans[2][]{%
    \leavevmode\par\noindent
   {%\leftskip37pt
    A --- \textbf{#1}#2\par}}

	\setulcolor{red}

	\usepackage[normalem]{ulem} % squigly underline

	\renewcommand\floatpagefraction{.8}

	\newlength{\figwidth}
	\newlength{\figwidthTwo}
	\newlength{\figwidthTree}
	\newlength{\figheight}
	\newlength{\figheightTwo}
	\newlength{\tempheight}
	\newlength{\tempheightTwo}

	% deal with missing images which are not directly included in the repo
	\iffalse
	\newcommand{\noimage}[1]{%
	  \setlength{\fboxsep}{-\fboxrule}%
	  \fbox{\phantom{\rule{10pt}{10pt}} Missing file: \path{#1} \phantom{\rule{10pt}{10pt}}}% Framed box
	}
	\let\includegraphicsoriginal\includegraphics
	\renewcommand{\includegraphics}[2][width=\textwidth]{\IfFileExists{#2}{\includegraphicsoriginal[#1]{#2}}{\noimage{#2}}}

	\fi
% ENd of TK's added packages and commands

\begin{document}
\baselineskip11pt

\begin{frontmatter}

\title{
Response to reviewers}

%\author{Paper ID: xxx}

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu}
\author[cuhk]{Charlie Wang}
% \ead{cwang@mae.cuhk.edu.hk}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
%\begin{CCSXML}
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

\end{frontmatter}

\section{Reviewer 1}
Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed.

\Que{
Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width? I believe the proposed beading scheme can reduce the underfill/overfill areas somehow. But we still lack a mathematical theory to guide the design.
}

\todo{
Refer to fig 5 and comment about 3-way intersections and 3-way gaps
Try to make a formula which predicts the amount of over- and underfill

Tim: I actually think this question is mostly related to DfAM. I think we should add something like the following to the manuscript:
}

\Ans{
Suppose that under some criterion of manufacturability we have established that we can attain bead widths within the range $[w_min, w_max]$.
We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\cup_i([i w_min,i w_max])$.
If $w_\text{max} > 2 w_\text{min}$ this reduces to $[w_min, \inf]$
If $w_\text{max} = w_\text{min} = w*$ this reduces to $\{w^*, 2w^*, 3w^*, \dots\}$
If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, inf]\}$

However, we propose no such binary criterion of manufacturability; instead we assume that the manufacturability generally goes down as the requested bead width variation goes up. By keeping the bead widths closer to a nominal bead width we guarantee the manufacturability goes up for any system.
}

\stepcounter{question}

\subQue{
The authors should highlight their contributions compared to the existing approaches for generating toolpaths with adaptive width.
}

\subQue{
From Fig. 1(b) and (c), we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
}

Changed image.

\todo{
Tim:
Any beading scheme can easily be modified to change the minimal feature width, simply by supplying that $q(d) = 0$ if $d < w_\text{min}$ and that $q(d) = 1$ if $w_\text{min} < d < w^*$

Tim: changed widening scheme to handle both minimal feature size and minimal bead width
@others: The new widening scheme figure now shows a bug in widening, perhaps we should only control the min feature size and leave out widening.

Note: our tests do compare beading schemes with different $w_\text{min}$.
? Should we redo the tests?
}

\subQue{
If there is no sharp corners exist, then the existing approaches such as Jin et al (2017) do not have to use bead widths of large variations. 
}

that’s not true

\Que{
How do the authors conduct path planning? Could the authors add a simple 2D geometry with multiple holes to explain the path planning process? As the proposed approach adds more disconnected toolpaths to minimize underfill areas, an improper path planning would significantly increase the fabrication time. 
}

Show results on printing time
Mention that the path order is not optimized

\Que{
While the proposed approach can use adaptive bead width to minimize underfill and overfill areas, the generated toolpaths are disconnected compared to the traditional approaches. From my experience, a small overfill area does not have to lead to serious defects. But the disconnected filaments definitely have worse mechanical performances compared to the continuous ones. 
}

We don’t know the effect…

Split overfill and underfill areas and compute the amount of components and make statistics

Tim: get statistics on nuber of areas with a size larger than $0.1 w^*$

Tim: That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.

\Que{
Why the authors state the inward distributed beading scheme as new? Jin et al (2017) has proposed the strategy to add a toolpath with varying width along the center edges of the skeleton, and with unchanging width outside. 1 
}

Tim: we should change the text to stress that we distribute the discrepancy over several beads rather than always over one bead.

\Que{
In Fig.1, how to justify the proposed approach as different geometries are used? I believe if the authors use the same geometries as in Fig 1. (a) and (b), there would be also underfill areas using the proposed approach. 
}

There is now a black outline to show that the shapes used are indeed the same.

Moreover we now use the same minimum feature size for b and c.

\Que{
Please double check the following sentences. ”Third, the extruded path should ...”(at the second paragraph of Section 2) ”This the downward phase...” (at the last paragraph of Section 3.5) 
}

\Que{
In Fig.4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
}

\Que{
What are the differences between the distributed and the inward scheme in Fig. 16(d) and (e)? Are they the same? 
}

\Que{
In Fig. 17(b), where is the curve for the ”uniform” case?
}

\section{Reviewer 2}
The paper is generally well written with clear illustrations. 
\Que{
There are occasional omissions, perhaps unintentional, such as the definition of a skeleton - see section 3.1, second paragraph. 
}

\stepcounter{question}
\subQue{
The authors seem to use linear approximations of the medial axis - see Figure 2 (b), which is understandable given the fact that they compute the MA with the Boost library. If this is so, can the authors comment on the implications of this approximation?
}

Quantify the approximation error depending on discretization size

\subQue{
For example, what happens ifthe obtuse outside angle in Figure 2 goes to 0? 
}
Poor example, because as the degree goes to zero the parts ofo the parabola revealed are more accurately described by the discretization than the highly curved part in the middle.

\Que{
As the authors correctly point out, the MA is not piecewise linear even for polygonal boundaries. In 3.2, second paragraph, the authors state that "the medial axis is a compact and complete representation of the shape". First, the MA + the radius function can be considered a shape representation, which is not true for the MA by itself. Second, the statement that the authors is meant to be generic, but it is not clear what compact means for a medial axis that is not piecewise linear. One can argue that the polygon itself is a rather compact representation of the shapes considered in this manuscript. 
}
Rerword a bit

\Que{
More generally, the technique seems to effectively be a variable offset scheme, but there is little discussion about what is known about variable offsets. 
Find more literature
}

elber1991error,

\Que{
Moreover, the proposed technique seems to rely on rather accurate control of the width w of the deposited material, but it is not clear whether such control is achievable in practice. 
}

Show S5 results. 
The proposed technique relies less on the accuracy of the control than existing techniques – as exemplified by Fig 17b.

\Que{
At the same time, the scheme can potentially result in trajectories with many inflection points - this is slow and demanding for the machine. 
Show print time results
}

\Que{
Finally, the examples provided depict the results obtained by the authors by "emulating" other techniques, but not with the actual results produced by the other techniques. While the reason behind this choice is easy to guess, it weakens the effectiveness of the claims. Adding careful discussions/extensions to support these questions would make the paper stronger.
}
Discuss how much the over-fill / underfill and bead width variation depend on the fact that our reimplementations are only approximations.

\section{Reviewer 3}
Paper is well written. It is mostly easy to follow but overall, I find the the contributions somewhat incremental and the motivation not convincing. The paper mostly feels like a technical report. I am not sure if the methods overall teach enough to the researchers in the field to open up new research possibilities. My specific comments are below:

\Que{
The title is a little misleading that the presented approach may be used for general “Additive Manufacturing”. However, my understanding from the text is that it is designed particularly for FDM. I believe it is important to highlight this in the title. Otherwise, there should be enough evidence to prove that it can be applied to other kinds of printing processes, such as SLS, SLA, DMLS etc. 
}
Material Extrusion additive manufacturing (?)

\Que{
It would be nice to discuss why contour-parallel toolpaths are needed or selected. In what situations, these are required as opposed to zigzag style (or direction-parallel as referred in the text) patterns. Without such a discussion, the motivation seems a little weak. In the second paragraph of introduction, there is a short discussion about this but it sounds like the authors assume that even the perimeters (or outline) are printed with direction-parallel extrusion. However, common approach in FDM is to print the perimeters with contour parallel toolpaths and fill the inner region with direction-parallel paths only (as later acknowledged in the related work 3rd paragraph). I think the motivation for contour parallel toolpaths needs to be justified further. 
}

Add some sentences to make it clear

\Que{
Related work acknowledges the previous work sufficiently. However, the differences between the state of the art and the presented work are not clear. More discussion on where this work stands with respect to the state of the art is required. 
}
Add discussion points?

\Que{
Isn’t it possible to put bounds on the width in the existing methods, such as the approach described in [9]? More discussion on that would be helpful. 
}
Jins method is limited to something like $0.2-1.8 \times$ nozzle\_size
Its not about bounds, its about how often the extremes happen

\Que{
Figure 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
}
Maybe put something like “this figure is for back-reference if you forgot what a thing is for”

\Que{
In Figure 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
}
Fixed.

\Que{
It is unclear how some of the parameters are adjusted, such as $\alpha_{max}, d_\text{max}^\text{unmarked}, d_\text{transition}^\text{max}, t_\text{beading}, d_\text{intersection}^\text{max}$. What are their effects on the end result? Selections seem somewhat arbitrary. 
}
Make my resaons for choosing these more explicit

\Que{
Is this approach generalizable to sparse infill? It is very common in FDM to use a sparse infill and only use dense fill on surface regions.
}
The goal of this paper is to minimize underfill using a low variation in bead width; generalizing it to sparse infill makes no sense because there the ‘underfill’ is intentional.

\Que{
If this is used for outer surface, what are the implications on the surface quality in comparison to other approaches? 
}
This is one of the usecases why this is a good method
Discuss effect of this algorithm on the outline accuracy

\Que{
I think Figure 13 should be replaced with a table. 
}
Done.

\Que{
In text, some references are missing, such as first sentence of “Outer bead” paragraph in Section 4 (Moesen et al [?]), first sentence of “Constant bead count” (Ding et al [?]) paragraph in Section 4 etc. 
}
\Ans{
We cannot reproduce this typesetting bug. Please inform the proofing department to take extra care of these references when preparing this manuscript for publication.
}

\Que{
Evaluation in the results section is overall good but it is not clear what are the implications of the presented approach on the complete 3D result. A discussion on this would be helpful.
}
Perhaps discuss effect of width changes on amount of fusing between layers

\Que{
What are the limitations of the presented algorithm? I do not see any discussions of the limitations of the algorithm.
}
Linear approximations 
a lot of direction changes

\end{document}

### 2019-12-05 0_reviewer_response.tex
lil fixes to reviewers response letter

@@
 
+\todo{
 Show results on printing time
+
 Mention that the path order is not optimized
+}
 
@@
 \subQue{
-For example, what happens ifthe obtuse outside angle in Figure 2 goes to 0? 
+For example, what happens if the obtuse outside angle in Figure 2 goes to 0? 
 }
@@
 }
-Jins method is limited to something like $0.2-1.8 \times$ nozzle\_size
+Jins method is limited to $0.5 - 1.8 \times$ nozzle\_size
 Its not about bounds, its about how often the extremes happen
@@
 \Que{
-It is unclear how some of the parameters are adjusted, such as $\alpha_{max}, d_\text{max}^\text{unmarked}, d_\text{transition}^\text{max}, t_\text{beading}, d_\text{intersection}^\text{max}$.
+It is unclear how some of the parameters are adjusted, such as $\alpha_\text{max}, d_\text{max}^\text{unmarked}, d_\text{transition}^\text{max}, t_\text{beading}, d_\text{intersection}^\text{max}$.
 What are their effects on the end result?

### 2019-12-05 0_reviewer_response.tex
todos to reviewers response from home
cosmetic changes to response to reviewers

@@
    \noindent
-   \thequestion. Q --- {\bf#1}\par}
+   \thequestion. {\it#1}\par}
 
@@
    \noindent
-   \thesubquestion. Q --- {\bf#1}\par}
+   \thesubquestion. {\it#1}\par}
 
@@
    {%\leftskip37pt
-    A --- \textbf{#1}#2\par}}
+    {\bf Response:} \textbf{#1}#2\par}}
 
@@
 \title{
-Response to reviewers}
+Response to reviewers
+\\
+\large{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}
+}
 
@@
 \end{frontmatter}
+
+\Que{Example question by reviewer}
+\Ans{Example response}
+\revise{Old text in manuscript}{New text in manuscript}
 
@@
 
+\todo{redo tests with min feature size}
+
 \Que{
@@
 
+\todo{
 Add some sentences to make it clear
+
+Show LimitedBeadingStrategy or StrategyType::OutlineAccuracy
+
+explain this paper can be used in normal slicing
+}
 
@@
 Maybe put something like “this figure is for back-reference if you forgot what a thing is for”
+
+Are you sure you mean figure 4? Maybe figure 3 or figure 2?
 

### 2019-12-05 0_reviewer_response.tex
give overview of most important changes in response to reviewers

@@
 \address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
+
+\begin{abstract}
+We have more clearly distinguished our work from existing methods.
+We have introduced extensions to the beading schemes:
+\begin{enumerate*}
+\item the widening meta-scheme is extended with a minimal feature size, in order to allow for a fair comparison between the various techniques 
+and
+\item a limiting meta-scheme is introduced which only generates the outer $N$ insets, so that the framework can readily be combined with the direction-parallel strategy in a manner common in FDM.
+\end{enumerate*}
+The results have been recalculated accordingly.
+We have developed a new manufacturing method which doesn't rely on custom machinery and which clearly shows the feasibility of adaptive bead width.
+We have computed fabrication time results.
+We have added a video animation explaining the union of cones approach in an intuitive manner.
+We have made various language fixes and improvements to images to address some of the reviewers' comments.
+\end{abstract}
 

### 2019-12-05 0_reviewer_response.tex
describe DfAM constraints better (in resposne to reviewers)

@@
 
-\Ans{
-Suppose that under some criterion of manufacturability we have established that we can attain bead widths within the range $[w_min, w_max]$.
-We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\cup_i([i w_min,i w_max])$.
-If $w_\text{max} > 2 w_\text{min}$ this reduces to $[w_min, \inf]$
-If $w_\text{max} = w_\text{min} = w*$ this reduces to $\{w^*, 2w^*, 3w^*, \dots\}$
-If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, inf]\}$
+\revise{}{
+Suppose that under some criterion of manufacturability we have established that we can attain bead widths within the range $[w_\text{min}, w_\text{max}]$.
+We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\bigcup_{i\in \mathcal{N}}([i w_\text{min},i w_\text{max}])$.
+If $w_\text{max} > 2 w_\text{min}$ this reduces to $[w_\text{min}, \infty]$
+If $w_\text{max} = w_\text{min} = w^*$ this reduces to $\{w^*, 2w^*, 3w^* \dots\}$
+If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$
 
 However, we propose no such binary criterion of manufacturability; instead we assume that the manufacturability generally goes down as the requested bead width variation goes up.
-By keeping the bead widths closer to a nominal bead width we guarantee the manufacturability goes up for any system.
+By keeping the bead widths closer to a nominal bead width we guarantee the manufacturability goes up for any manufacturability measure.
 }

### 2019-12-05 1_intro.tex
lil lang improvement (reviewer 3.3)
add comment for generalizability of wedge shape (reviewer 1.6)

@@
 Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
+\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
 \subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
-\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with beads close to the nozzle size.
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
 }

### 2019-12-05 0_reviewer_response.tex
describe commits in response to reviewers

@@
 	% Version a) First arg red and striked out, second argument green
-	\newcommand{\revise}[2]{{\color{red}{{#1}}}{\color{blue}{#2}}}
+	\newcommand{\revise}[2]{\noindent{\color{red}{{#1}}}\par\noindent{\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
@@
 
+	\usepackage{alltt}
+
 	\newcommand{\question}[1]{{\bf#1}}
-	\newcommand{\todo}[1]{{\bf \color{orange}#1}}
+	\newcommand{\todo}[1]{\par\noindent{\bf \color{orange}#1}}
+	\newcommand{\commits}[1]{{\bf\begin{alltt} {#1}\end{alltt}}}
 	\newcommand{\response}[1]{{#1}}
@@
 \revise{Old text in manuscript}{New text in manuscript}
+\todo{Comment for us internally (should be removed before this letter is sent).}
+\commits{123commit-hash}
 
@@
 }
+\todo{Actually add this to the manuscript!}
 
@@
 }
+\Ans{
+afs
+}
+\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994}
 
@@
 }
-
-Changed image.
+\Ans{
+We now use the same minimal feature size in all approaches.
+This is now handled by the \emph{widening} meta-scheme.
+We have added a figure to show that functionality.
+See also our response to 1.6.
+}
+\todo{add widening changes; explain how widening is used in generating the results}
+\commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f}
 
@@
 \Que{
+\label{fig1geometry}
 In Fig.1, how to justify the proposed approach as different geometries are used?
@@
 }
+\Ans{
+There are two ways in which we can interpret this question, leading to two responses.
+The question can be interpreted as saying that Fig a has a different geometry than b or c.
+There is now a black outline to show that the shapes in Fig 1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.
 
-There is now a black outline to show that the shapes used are indeed the same.
-
-Moreover we now use the same minimum feature size for b and c.
-
+The question can also be interpreted as saying that one might use a different shape than the geometry in Fig 1.
+We decided on this wedge shape because it shows how the techniques deal with a wide range of feature sizes;
+the wedge shape can be read as a graph where we can read out the resulting beading for any local feature size.
+}
 \todo{redo tests with min feature size}
+\commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1, 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
 
@@
 }
+Okay. Thanks.
+
+\commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}
 
@@
 }
+\Ans{
+Note that the bead count is the number, not the arrow from the number.
+The arrow is now a double thin line.
+}
+\commits{07df258c1fa618808ba9493384550021a03c83e1}
 
@@
 }
+\Ans{
+We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images.
+}
+\commits{735762b1e7daf31ae4465bf288ef867ded7da095}
 
@@
 }
+\Ans{
+Done.
+Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve we now added to the graph is not really informative.
+}
+\commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}
 
@@
 }
+\Ans{
+Indeed we have intentionally not defined the term `skeleton'.
+It seems that there is no generally accepted \emph{intuitive} definition of `skeleton';
+the first occurance of the term was as synonymous with the medial axis and it was only defined \emph{mathematically}.
+However, the term is now used as an umbrella term for the various different types of skeleton.
+We have changes the wording a bit to make clear that `skeleton' refers to an undefined umbrella term.
+}
+\commits{5356492b5a9a690228ffdb6a6a26cf10d099a7d4}
 
@@
 }
-Rerword a bit
+\Ans{
+Indeed the statement was meant generically, but we agree it lacked substance.
+The wording is now changed to better describe the general role of the medial axis in research.
+}
+\commits{d3f19c04e3bb0d80c0b162531dbf576fc705d77c}
 
@@
 }
-
-Show S5 results. 
-The proposed technique relies less on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
+\Ans{
+The photos of our print results already showed that adaptive width control is possible up to some (insufficient) extent.
+We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear backpressure compensation.
+We show the results of linear backpressure compensation in a separate figure which clearly shows the achieved variance in bead width.
+}
+\todo{
+Show S5 prints. 
+The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
+}
+\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b}
 
@@
 }
-Material Extrusion additive manufacturing (?)
+The title has changed.
+\revise{additive manufacturing}{fused deposition modeling}
+\commits{64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0}
 
@@
 }
-
+\Ans{
+The industry standard is to use a combination of contour-parallel and direction-parallel.
+We now clarify why contour-parallel is (partly) used and that in as much as contour-parallel is used, our approach improves on the industry standard.
+}
 \todo{
@@
 
+\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4}
+
 \Que{
@@
 }
+\todo{
 Add discussion points?
+}
+\commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
 
@@
 }
-Jins method is limited to $0.5 - 1.8 \times$ nozzle\_size
+\Ans{
+The bead width in Jin et al.
+is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.2$; this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.2$.
+}
+\todo{
 Its not about bounds, its about how often the extremes happen
+}
+\commits{661d8f6766548c287cb174070432097e396d198f}
 
@@
 }
-Fixed.
+Fixed. Fig 3 c and d now have the same discretization.
+\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
 
@@
 
+\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae}
+
 \Que{
@@
 Done.
+\commits{735762b1e7daf31ae4465bf288ef867ded7da095}
 
@@
 
+\section{Other changes}
+We have fixed some issues with positions and colors being swapped in the statistical analysis subfigures.
+Fig 17f colors are adjusted.
+Fig 17e and 17f are swapped.
+\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
+
+Improvements to abstract.
+\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
+
+Fix double header of References.
+\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}
+
+Added patent notice and url to open source implementation.
+\commits{ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a}
+
+Lil
+\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172}
+
 \end{document}

### 2019-12-06 5_generalization.tex
introduce shell meta-scheme and replace widening figure with widening+shell figure (reviewer 3.2, 1.2.2)

@@
 
-\paragraph{Widening}
+\paragraph{Widening \revise{}{meta-scheme}}
 Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
@@
 
+\revise{}{
+\paragraph{Shell meta-scheme}
+The industry standard of FDM is to generate only a limited contour-parallel perimeters and to fill the remainder using a direction-parallel strategy.
+We therefore provide a meta-scheme to generate adaptive bead width toolpaths only in narrow regions and generate the limited number of perimeters $M$ using the preferred width in regions which are wide enough.
+We also take care not to leave gaps which are too small to be filled using the direction-parallel strategy:
+
+\begin{align*}
+q'(d) &= \min(M, q(d))
+\\
+W'(n,r)_i &= 
+\begin{cases}
+W(n, M w^*)_i & \text{ if } 2 r > q^{-1}(M) \\
+W(n,r)_i & \text{ otherwise}
+\end{cases}
+\end{align*}
+
+These meta-schemes introduce non-linearities in the quantization function.
+Because the beading is only evaluated at nodes in the skeleton, we need to make sure that there are nodes at the locations along the skeleton where the non-linearities happen.
+We therefore insert extra nodes along with their ribs at locations $v$ with a radial distance $R(v) = r_\text{min}$ for widening and at $R(v) \in \left\{ M w^*, q^{-1}(M), q^{-1}(M) + \nicefrac12 w^* \right\} $ for the transition from narrow shell to unconstrained shell.
+Combining all meta-schemes functionality we can generate results such as depicted in \cref{widening_shell}.
+
 \begin{figure}
 \centering
-\setlength{\figwidth}{.45\columnwidth}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
-\caption{$w_\text{min} = 2 r_\text{min} = 0.1$ (Distributed)}
-\end{subfigure}
-\begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
-\caption{$w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ (Center)}
-\end{subfigure}
+\includegraphics[rotate=90,width=.6\columnwidth]{sources-validation-gMat_example_all_combined.png}
 \caption{
-Widening strategies.
+Toolpath generated with the inward distributed strategy ($N=1.5$) in conjunction with the widening meta-scheme ($W_\text{min}=0.5, 2r_\text{min}=0.2$, see top left) and the shell meta-scheme ($M=4$, see middle).
+% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
+Widening and shell require extra edges (green) at key locations in the skeleton.
+The azure area is to be filled using some direction-parallel toolpath generation algorithm.
 }
-\label{widening}
+\label{widening_shell}
 \end{figure}
+}

### 2019-12-06 0_reviewer_response.tex
more reviewers response

@@
 \todo{
-Refer to fig 5 and comment about 3-way intersections and 3-way gaps
-Try to make a formula which predicts the amount of over- and underfill
-
-Tim: I actually think this question is mostly related to DfAM. I think we should add something like the following to the manuscript:
+I actually think this question is mostly related to DfAM. I think we should add something like the following to the manuscript:
 }
@@
 We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\bigcup_{i\in \mathcal{N}}([i w_\text{min},i w_\text{max}])$.
-If $w_\text{max} > 2 w_\text{min}$ this reduces to $[w_\text{min}, \infty]$
-If $w_\text{max} = w_\text{min} = w^*$ this reduces to $\{w^*, 2w^*, 3w^* \dots\}$
-If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$
+If $w_\text{min} = w_\text{max} = w^*$ this reduces to $\{w^*, 2w^*, 3w^* \dots\}$.
+On the other hand we assume that $w_\text{max} > 2 w_\text{min}$ and so a model is manufacturable if the feature size is within $[w_\text{min}, \infty]$ everywhere.
+%If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$
 
-However, we propose no such binary criterion of manufacturability; instead we assume that the manufacturability generally goes down as the requested bead width variation goes up.
-By keeping the bead widths closer to a nominal bead width we guarantee the manufacturability goes up for any manufacturability measure.
+However, we propose no such binary criterion of manufacturability;
+instead we assume that the manufacturability generally diminishes as the requested bead width variation widens.
+By keeping the bead widths closer to the preferred bead width any reasonable measure of manufacturability is higher than for alternative methods.
 }
@@
 \todo{add widening changes; explain how widening is used in generating the results}
-\commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f}
+\commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f, 9281d8ae7350539102be0ead7b2ffc611591d2b4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}
 
@@
 }
+\Ans{
+The wedge shape of Fig. 1 was chosen because it contains a wide range of feature sizes and is therefore representative for a wide range of models.
+Nearly every model induces the full range of $[0.5w^*,1.8w^*]$ using the centered approach by Jin et. al. 2017 JMS,
+because nearly all models have feature sizes which span any range $[iw^*,(i+1)w^*]$ for $i\in\mathcal{N}$.
+See Fig. 17 in the paper of Jin et al for an example shape.
+Only shapes without central regions (a circle) or shapes with central regions with an exact multiple of $w^*$ everywhere (a rectangle) don't require any variation in bead width, but that holds for any of the beading schemes.
 
-that’s not true
+Figure~\ref{no_corners} shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
+}
+\begin{figure} \centering
+\includegraphics[width=.5\linewidth]{response_no_corners}
+\caption{Example shape without sharp corners but with a large variation in feature size.}
+\label{no_corners}
+\end{figure}
 
@@
 }
-
-We don’t know the effect…
-
-Split overfill and underfill areas and compute the amount of components and make statistics
-
-Tim: get statistics on nuber of areas with a size larger than $0.1 w^*$
+\todo{
+Tim: count number of extrusion toolpaths
 
 Tim: That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
+}
 
@@
 Jin et al (2017) has proposed the strategy to add a toolpath with varying width along the center edges of the skeleton, and with unchanging width outside.
-1
 }
-
+\todo{
 Tim: we should change the text to stress that we distribute the discrepancy over several beads rather than always over one bead.
+}
 
@@
 }
+\Ans{
 Okay. Thanks.
-
+}
 \commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}
@@
 \Ans{
-Done.
-Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve we now added to the graph is not really informative.
+We've added it back in.
+Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve is not really informative.
 }
@@
 }
+\Ans{
+We chose for linear approximations because they simplify the process,
+whereas we chose for Boost because it seemed more stable than alternative libraries.
 
-Quantify the approximation error depending on discretization size
+The discretization is handled in section 3.2. Skeletal trapezoidation, second paragraph.
+The discretization simplifies the algorithm, potentially at a slight computational cost.
+Because we used $d^\text{discretization} = \SI{0.2}{\milli\meter}$, we can expect the discretized skeleton to deviate from the real skeleton by approximately \SI{0.013}{\milli\meter}, which is within the range of accuracy of the hardware system used.
+The computation of this value is complicated by the fact that the discretization always introduces a sample point at the apex and at the boundaries of significant portions of the parabola.
+(See section 3.3 Significance measure, last paragraph.)
+See Figure~\ref{response_parabola_discretization}.
+
+We don't feel this type of discretization error is worth extending the manuscript with.
+}
+\begin{figure}\centering
+\includegraphics[width=.3\linewidth]{response_parabola_discretization}
+\caption{Parabola discretization.
+Thick black is part of the outline.
+Red is significant skeleton, violet is non-significant skeleton.
+}\label{response_parabola_discretization}
+\end{figure}
 
@@
 }
-Poor example, because as the degree goes to zero the parts ofo the parabola revealed are more accurately described by the discretization than the highly curved part in the middle.
+\Ans{
+That figure is reproduced here in Fig.~\ref{overview_outline}.
+As the rightmost two points move right the degree of the corner in the middle goes to zero which causes the parts of the parabola revealed are more accurately described by the discretization than the highly curved part in the middle.
+}
+\begin{figure}\centering
+\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_1}
+\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_2}
+\includegraphics[width=.3\linewidth,rotate=-90]{response_simple_example_3}
+\caption{Skeletal trapezoidation}\label{overview_outline}
+\end{figure}
 
@@
 }
-\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b}
+\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b, }
 
@@
 
-\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4}
+\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}
 

### 2019-12-06 5_generalization.tex
redo (inward) distributed comparison fig (reviewer 1.9)

@@
 \centering
-\setlength{\figwidth}{.4\columnwidth}
-\setlength{\figheight}{.25\columnwidth}
+\setlength{\figwidth}{.8\columnwidth}
+\setlength{\figheight}{.3\columnwidth}
+\begin{minipage}[b]{0.8\linewidth}
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-evenly.png}
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly.png}
 \caption{Evenly distributed}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight,frame]{sources-validation-wedge-Distributed-pretty-inward.png}
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward.png}
 \caption{Inward distributed}
 \end{subfigure}
+\end{minipage}
 \begin{subfigure}[t]{.1\columnwidth}\centering
@@
 \caption{
-Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
+Closeup of toolpaths generated with the distributed \revise{}{and inward ($N=1.5$)} beading schemes for a large wedge shape.
 Colors represent bead widths.

### 2019-12-06 1_intro.tex
improve introduction of contour-parallel (reviewer 3.2)

@@
 Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
-This paper focusses on the contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with geometry which is narrower than the typical number of perimeters.
+This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
 }

### 2019-12-06 1_intro.tex
give bounds on width variation (reviewer 3.4)

@@
 \item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme for FDM printing which \revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to existing literature, and which \revise{promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{produces beads of exactly the preferred width outside of central regions of the outline shape.}
+\item A specific beading scheme for FDM printing which
+\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be generally below a factor of 2.}
+\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
 \end{itemize}

### 2019-12-06 8_discussion.tex
give bounds on width variation (reviewer 3.4)

@@
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths are within a factor 2 off from the desired bead width.
+the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the deviation is within a factor of $3.2$.}
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-We therefore conclude that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads the bead widths range from $0.75w^*$ to $1.5w^*$, i.e.
+the deviation is within a factor $2$, which is considerably lower than in the centered scheme.}
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
 %This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

### 2019-12-06 0_reviewer_response.tex
more reviewers responses

@@
 
+We are very grateful for the feedback and contributions of the reviewers.
+We feel that their feedback has provoked a leap forward in quality of the presented manuscript.
+
 \Que{Example question by reviewer}
@@
 
-\Que{
+\stepcounter{question}
+\subQue{
 Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width?
 I believe the proposed beading scheme can reduce the underfill/overfill areas somehow.
-But we still lack a mathematical theory to guide the design.
+}
+\Ans{
+There is not really a relationship between under-/overfill and the allowed variation in bead width,
+aside from the microgaps generated at 3-way intersections which play a minute role.
+The state-of-the-art (Jin et al 2017 JMS) does have a relationship: the ranges $[0,w_\text{min}]$ and $[w_\text{max},2w^*]$ produce underfill and overfill respectively, so making the allowed variation wider reduces the under-/overfill for their method and likewise for the centered beading scheme.
+However, the distributed beading schemes have no such limitation.
+They minimize under-/overfill with the requirement that the allowed variation in bead width is at least a factor of 2 ($[0.75w^*,1.5w^*]$).
+\todo{So...?}
+
+Because the beading scheme decides how to fill the full radial distance using some beading sequence, under-/overfill shouldn't be a problem anymore.
+However, because there are certain interactions in 2D, this doesn't always hold.
+For example a 3-way intersection in a 3D model which is a honeycomb pattern with a feature diameter of $w^*$ causes some over and underfill using \emph{any} possible technique.
+Our proposed beading schemes efectively deal with over- and underfill, and because the current state-of-the-art did not, the proposed beading scheme indeed reduces the undefill/overfill areas.
 }
@@
 \todo{
-I actually think this question is mostly related to DfAM. I think we should add something like the following to the manuscript:
+fix wording
+
+Make changes in paper:
+Clarify in intro, explain when introducing the Centered approach and show in the results section!
+Repeat in the conclusion?
+}
+
+\subQue{
+But we still lack a mathematical theory to guide the design.
+}
+\Ans{
+We now clearly indicate in the conclusion that we expect this paper to contribute to the reduction of Design for Aadditive Manufacturing (DfAM) constraints.
+}
+\todo{
+Maybe we should add something like the following to the manuscript: (but where?)
 }
@@
 %If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$
-
+}
+\todo{
 However, we propose no such binary criterion of manufacturability;
@@
 }
-\todo{Actually add this to the manuscript!}
+
+\commits{2e1c40be93f92a8495c0d7fa379e983dd3ee7b98}
 
@@
 We now use the same minimal feature size in all approaches.
-This is now handled by the \emph{widening} meta-scheme.
-We have added a figure to show that functionality.
-See also our response to 1.6.
+We have added this functionality to the \emph{widening} meta-scheme.
+We have also added a figure to show that functionality.
 }
-\todo{add widening changes; explain how widening is used in generating the results}
+\todo{
+Redo the tests with homogeneous $r_\text{min}$
+
+note value of $r_\text{min}$ in paper
+}
 \commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f, 9281d8ae7350539102be0ead7b2ffc611591d2b4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}
-
-\todo{
-Tim:
-Any beading scheme can easily be modified to change the minimal feature width, simply by supplying that $q(d) = 0$ if $d < w_\text{min}$ and that $q(d) = 1$ if $w_\text{min} < d < w^*$
-
-Tim: changed widening scheme to handle both minimal feature size and minimal bead width
-@others: The new widening scheme figure now shows a bug in widening, perhaps we should only control the min feature size and leave out widening.
-
-Note: our tests do compare beading schemes with different $w_\text{min}$.
-? Should we redo the tests?
-}
 
@@
 }
+\Ans{
+That is a difficult question.
+It might very well be true that discontinuous extrusion lines form a bigger problem than some over- or underfill areas - at least certainly for flexible filaments on a Bowden printer.
+However, it is quite hard to find a mathematical approach to balance discontinuity with the size of over-/underfill areas.
+
+It should be noted that even small underfill areas can be unfillable using an overextrusion approach.
+For example the microgaps at 3-way intersections.
+The viscocity if molten filament is too high to reach into those small crevices.
+}
 \todo{
-Tim: count number of extrusion toolpaths
+Tim: count number of extrusion toolpaths?
+
+mention as future work?
 
@@
 }
-\todo{redo tests with min feature size}
 \commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1, 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
@@
 }
-\commits{735762b1e7daf31ae4465bf288ef867ded7da095}
+\commits{735762b1e7daf31ae4465bf288ef867ded7da095, 93352058a46fb391e323df16f45466adb8cad508}
 
@@
 \Ans{
-The photos of our print results already showed that adaptive width control is possible up to some (insufficient) extent.
+The photos of our print results already showed that adaptive width control is possible up to some (admittedly insufficient) extent.
 We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear backpressure compensation.
@@
 We now clarify why contour-parallel is (partly) used and that in as much as contour-parallel is used, our approach improves on the industry standard.
-}
-\todo{
-Add some sentences to make it clear
-
-Show LimitedBeadingStrategy or StrategyType::OutlineAccuracy
-
-explain this paper can be used in normal slicing
+We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with the industry standard for FDM 3D printing.
 }
 
-\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}
+\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4, a88ccd3309aef1233ed00ce9f22b244fe64668f4, 077c8ee138bb311a8ba9abf303af4b09e973637a}
 
@@
 }
-\todo{
-Add discussion points?
+\Ans{
+We have tried to address this in response to several other reviewers' comments.
+See .
+We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
 }
+\todo{link with other responses}
 \commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
@@
 \Ans{
-The bead width in Jin et al.
-is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.2$; this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.2$.
+The bead width in Jin et al. is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.2$;
+this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.2$.
+We emphasized that our method (generally) results in a bead width deviation of $2$, rather than $3.2$ in the related work section and in the discussion section.
 }
-\todo{
-Its not about bounds, its about how often the extremes happen
-}
-\commits{661d8f6766548c287cb174070432097e396d198f}
+\commits{661d8f6766548c287cb174070432097e396d198f, 92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d}
 

### 2019-12-06 1_intro.tex
stress diff with Jin (reviewer 1.5)
highlight contributions better (reviewer 1.2.1)

@@
 Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
+\revise{
 Therefore, a narrower range of widths is desirable.
+}
+{We therefore reduce the bead width range by distributing the workload from the centermost bead over neighboring beads.}
 
-In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill. 
+In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill. 
 We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 

### 2019-12-06 0_reviewer_response.tex
more reviewers response

@@
 \Ans{
-afs
+See also our response to 1.5.
 }
-\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994}
+\todo{
+Describe changes
+}
+\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994, e806d40e5e6d2bbe450c6792b802f0fcce4df645}
 
@@
 \todo{
-Tim: count number of extrusion toolpaths?
+count number of extrusion toolpaths?
 
@@
 
-Tim: That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
+That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
 }
@@
 }
-\todo{
-Tim: we should change the text to stress that we distribute the discrepancy over several beads rather than always over one bead.
+\Ans{
+The difference between the inward distributed beading scheme and the method by Jin et al 2017 JMS is already shown in Fig 1.b and c. 
+It is also shown in Fig. 16 c and e.
+In order to clearly address the difference early on we mention the difference in the description of Jin in the introduction.
 }
+\commits{b7c4d299a76e9fab6c233d572f3248c1350a2e8c}
 
@@
 
+\todo{
 elber1991error, 
+}
 
@@
 At the same time, the scheme can potentially result in trajectories with many inflection points - this is slow and demanding for the machine. 
-Show print time results
+}
+\Ans{
+We have added statistics on fabrication time and discussed our findings.
+See our response to 1.3.
 }
@@
 }
+\todo{
 Discuss how much the over-fill / underfill and bead width variation depend on the fact that our reimplementations are only approximations.
+}
 
@@
 We have tried to address this in response to several other reviewers' comments.
-See .
+See our response to 1.5, 1.1.1.
 We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
@@
 }
+\todo{
 Maybe put something like “this figure is for back-reference if you forgot what a thing is for”
@@
 Are you sure you mean figure 4? Maybe figure 3 or figure 2?
+}
 
@@
 }
+\Ans{
 Fixed. Fig 3 c and d now have the same discretization.
+}
 \commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
@@
 }
-Make my resaons for choosing these more explicit
+\todo{
+Make my reasons for choosing these more explicit
+}
 
@@
 }
-The goal of this paper is to minimize underfill using a low variation in bead width; generalizing it to sparse infill makes no sense because there the ‘underfill’ is intentional.
-
-\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae}
+\Ans{
+The goal of sparse infill on the otherhand is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
+However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
+See our response to 3.2.
+}
 
@@
 }
+\todo{
 This is one of the usecases why this is a good method
 Discuss effect of this algorithm on the outline accuracy
+}
 
@@
 }
-Done.
+\Ans{
+Indeed. Done.
+}
 \commits{735762b1e7daf31ae4465bf288ef867ded7da095}
@@
 }
+\todo{
 Perhaps discuss effect of width changes on amount of fusing between layers
+}
 
@@
 }
+\todo{
 Linear approximations
-a lot of direction changes
+
+a lot of direction changes (?)
+}
 

### 2019-12-09 0_reviewer_response.tex
reviewer response paper changes

@@
 	% Version a) First arg red and striked out, second argument green
-	\newcommand{\revise}[2]{\noindent{\color{red}{{#1}}}\par\noindent{\color{blue}{#2}}}
+	\newcommand{\revise}[2]{\noindent{\color{red}{{#1}}}\noindent{\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
@@
 	\newcommand{\commits}[1]{{\bf\begin{alltt} {#1}\end{alltt}}}
+	\renewcommand{\commits}[1]{}
 	\newcommand{\response}[1]{{#1}}
+\newcommand\paper[2]{\par changes to \emph{#1} --- ``#2'' }
+\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
 
@@
    \noindent
-   \thequestion. {\it#1}\par}
+   \thequestion. {\bf#1}\par}
 
@@
    \noindent
-   \thesubquestion. {\it#1}\par}
+   \thesubquestion. {\bf#1}\par}
 
@@
    {%\leftskip37pt
-    {\bf Response:} \textbf{#1}#2\par}}
+    {\it Response:} \textbf{#1}#2\par}}
 
@@
 Response to reviewers
-\\
+\
 \large{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}
@@
 \stepcounter{question}
+
 \subQue{
@@
 \commits{2e1c40be93f92a8495c0d7fa379e983dd3ee7b98}
+\paper{Conclusion}{
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards most of the nozzle size considerations.}
+}
 
@@
 }
-\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994, e806d40e5e6d2bbe450c6792b802f0fcce4df645}
+\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 e806d40e5e6d2bbe450c6792b802f0fcce4df645}
+\paper{Intro}{
+ \begin{itemize}
+\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
+\item A specific beading scheme for FDM printing which \revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to existing literature, and which \revise{promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{produces beads of exactly the preferred width outside of central regions of the outline shape.}
+ \end{itemize}}
+ \paper{intro}{In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill.}
 
@@
 }
-\commits{a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13, d3fe6c86ee887da0e33fefdc43a83d014bc6047b, 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f, 9281d8ae7350539102be0ead7b2ffc611591d2b4, a88ccd3309aef1233ed00ce9f22b244fe64668f4}
+\commits{
+%a5ddf3a73e3df20e43f25eafb93e9ce3a1393b13 
+d3fe6c86ee887da0e33fefdc43a83d014bc6047b 
+0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f 
+9281d8ae7350539102be0ead7b2ffc611591d2b4 
+a88ccd3309aef1233ed00ce9f22b244fe64668f4
+}
+\paper{Beading schemes}{
+\paragraph{Widening \revise{}{meta-scheme}}
+Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
+Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
+We can simply override
+\begin{align*}
+q'(d) &= 
+\begin{cases}
+0 & \text{ if } 0 \leq d < 2 r_\text{min} \\
+1 & \text{ if }  2 r_\text{min} \leq d < w^*  \\
+q(d) & \text{ otherwise}
+\end{cases}
+\\
+\revise{}{
+W'(n,r)_0} &=
+\begin{cases}
+\max \left( w_\text{min}  ,  2 r \right) & \text{ if } 2 r < w^* \\
+W(n,r)_0 & \text{ otherwise}
+\end{cases}
+\end{align*}
+
+\revise{}{
+\paragraph{Shell meta-scheme}
+The industry standard of FDM is to generate only a limited contour-parallel perimeters and to fill the remainder using a direction-parallel strategy.
+We therefore provide a meta-scheme to generate adaptive bead width toolpaths only in narrow regions and generate the limited number of perimeters $M$ using the preferred width in regions which are wide enough.
+We also take care not to leave gaps which are too small to be filled using the direction-parallel strategy:
+
+\begin{align*}
+q'(d) &= \min(M, q(d))
+\\
+W'(n,r)_i &= 
+\begin{cases}
+W(n, M w^*)_i & \text{ if } 2 r > q^{-1}(M) \\
+W(n,r)_i & \text{ otherwise}
+\end{cases}
+\end{align*}
+
+These meta-schemes introduce non-linearities in the quantization function.
+Because the beading is only evaluated at nodes in the skeleton, we need to make sure that there are nodes at the locations along the skeleton where the non-linearities happen.
+We therefore insert extra nodes along with their ribs at locations $v$ with a radial distance $R(v) = r_\text{min}$ for widening and at $R(v) \in \left\{ M w^*, q^{-1}(M), q^{-1}(M) + \nicefrac12 w^* \right\} $ for the transition from narrow shell to unconstrained shell.
+Combining all meta-schemes functionality we can generate results such as depicted in \cref{widening_shell}.
+
+\begin{figure}
+\centering
+\includegraphics[rotate=90,width=.6\columnwidth]{sources-validation-gMat_example_all_combined.png}
+\caption{
+Toolpath generated with the inward distributed strategy ($N=1.5$) in conjunction with the widening meta-scheme ($W_\text{min}=0.5, 2r_\text{min}=0.2$, see top left) and the shell meta-scheme ($M=4$, see middle).
+% -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
+Widening and shell require extra edges (green) at key locations in the skeleton.
+The azure area is to be filled using some direction-parallel toolpath generation algorithm.
+}
+\label{widening_shell}
+\end{figure}
+}
+
+}
 
@@
 \commits{b7c4d299a76e9fab6c233d572f3248c1350a2e8c}
+\paper{Intro}{
+\revise{
+ Therefore, a narrower range of widths is desirable.
+}
+{We therefore reduce the bead width range by distributing the workload from the centermost bead over neighboring beads.}
+}
 
@@
 }
-\commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1, 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
+\commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
+\paper{Intro}{
+Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
+}
+\paper{Intro wedge figure}{
+\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
+}
 
@@
 \commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}
+\paper{Related work}{
+Third, the extruded path should cover \revise{a }{}the region of the contour without gaps.
+}
+\paper{Related work}{
+\revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
+}
 
@@
 \commits{07df258c1fa618808ba9493384550021a03c83e1}
+\paper{Fig 4}
+{
+See \cref{legend}.
+\begin{figure}\centering
+\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
+\caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
+\label{legend}
+\end{figure}
+}
 
@@
 }
-\commits{735762b1e7daf31ae4465bf288ef867ded7da095, 93352058a46fb391e323df16f45466adb8cad508}
+\commits{735762b1e7daf31ae4465bf288ef867ded7da095 93352058a46fb391e323df16f45466adb8cad508}
+\paper{Beading schemes}
+{
+See \cref{distributed_comparison}.
+\begin{figure}
+\centering
+\setlength{\figwidth}{.8\columnwidth}
+\setlength{\figheight}{.3\columnwidth}
+\begin{minipage}[b]{0.8\linewidth}
+% -p test_geometry/wedge.svg -o wedge -s nrdi -n 1.5 -a --scale 1.5
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly.png}
+\caption{Evenly distributed}
+\end{subfigure}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward.png}
+\caption{Inward distributed}
+\end{subfigure}
+\end{minipage}
+\begin{subfigure}[t]{.1\columnwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
+\end{subfigure}
+\caption{
+Closeup of toolpaths generated with the distributed \revise{}{and inward ($N=1.5$)} beading schemes for a large wedge shape.
+Colors represent bead widths.
+}
+\label{distributed_comparison}
+\end{figure}
+}
 
@@
 The paper is generally well written with clear illustrations.
+
 \Que{
@@
 \commits{5356492b5a9a690228ffdb6a6a26cf10d099a7d4}
+\paper{Method overview}{
+Our method starts with computing \revise{the}{a type of} skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+}
 
@@
 We don't feel this type of discretization error is worth extending the manuscript with.
-}
+
 \begin{figure}\centering
@@
 \end{figure}
+}
 
@@
 \commits{d3f19c04e3bb0d80c0b162531dbf576fc705d77c}
+\paper{Medial axis transform}{
+The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
+}
 
@@
 }
-\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b, }
+\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b }
+\paper{5.2 Printing results}{
+\revise{}{
+Test prints were performed on an unmodified Ultimaker S5 system,
+with a standard  \SI{0.4}{\milli\meter} nozzle
+and PLA filament
+and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
+In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
+One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly.
+However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
+We conjecture that the filament outflow is related to the total pressure in the system,
+which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
+but also depends on the backpressure that the previous layer exerts on the filament protruding from the nozzle.
+We conjecture that the amount of backpressure is monotonically related to the requested line width and compensate for the backpressure using a simple linear model:
+
+\begin{align}
+ v(w) &= \frac{f(w)}{h w} \\ 
+% f &\sim p \\
+% p &= p_\text{in} + p_\text{ext} \\
+% p_\text{in} &= C \\
+% p_\text{ext} &\sim w \\
+% p_\text{ext} &= w / w^* - 1 \\
+% f &= f^* - k p_\text{ext} \\
+ f(w) &= f_0 - k \left( w / w_0 - 1 \right) \\
+ f_0 &= v_0 w_0 h 
+% v &= \frac{f^* - k p_\text{ext}}{h w} \\ 
+% v &= \frac{v^* w^* h - k (w / w^* - 1)}{h w}
+\end{align}
+where
+$v(w)$ is the movement speed as a function of requested bead width $w$,
+$f(w)$ is the filament outflow,
+$f_0$ is a constant reference flow
+and
+$k$ is the amount of backpressure compensation.
+Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
+$v_0=\SI{30}{\milli\meter\per\second}$, 
+$w_0=\SI{0.4}{\milli\meter}$.
+See \cref{backpressure}.
+
+\begin{figure}
+\centering
+\setlength{\figwidth}{0.32\columnwidth}
+\setlength{\figheight}{0.5\columnwidth}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation-target.pdf}
+\caption{Target widths}\label{backpressure_target}
+\end{subfigure}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[angle=90,height=\figheight]{sources-validation-zero-backpressure-compensation.png}
+\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_backpressure}
+\end{subfigure}
+\begin{subfigure}[t]{\figwidth}\centering
+\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation.png}
+\caption{Backpressure compensation}\label{backpressure}
+\end{subfigure}
+\caption{
+Print results of varying width test on top of a dense white raft.
+Trying to reproduce \subref{backpressure_target} without backpressure compensation ($k=0$) yields worse results \subref{zero_backpressure} than with backpressure compensation $k=1.1$ \subref{backpressure}.
+}
+\label{backpressure_compensation}
+\end{figure}
+
+}
+}
 
@@
 \commits{64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0}
+\paper{Title}{
+A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}
+}
 
@@
 
-\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae, ac800628951417dcb28bd6e3a0ed08801735acf4, a88ccd3309aef1233ed00ce9f22b244fe64668f4, 077c8ee138bb311a8ba9abf303af4b09e973637a}
+\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae ac800628951417dcb28bd6e3a0ed08801735acf4 a88ccd3309aef1233ed00ce9f22b244fe64668f4 077c8ee138bb311a8ba9abf303af4b09e973637a}
+\paper{Intro}{
+\revise{
+Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
+}{
+Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
+This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
+}
+}
+\paper{Abstract}{
+\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
+}
 
@@
 \commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
+\paper{Fig 1}{
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
+}
 
@@
 }
-\commits{661d8f6766548c287cb174070432097e396d198f, 92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d}
+\commits{661d8f6766548c287cb174070432097e396d198f 92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d}
+\paper{Intro}{
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
+}
+\paper{Discussion}{
+In \cref{TEST_Center_accuracy} we can see that
+the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the deviation is within a factor of $3.2$.}
+}
+\paper{Discussion}{
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads the bead widths range from $0.75w^*$ to $1.5w^*$, i.e.
+the deviation is within a factor $2$, which is considerably lower than in the centered scheme.}
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
+}
 
@@
 \commits{735762b1e7daf31ae4465bf288ef867ded7da095}
+% commit only now shows table
 
@@
 \commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
+\paper{Abstract}{
+Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
+\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
+ Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
+ In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
+Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+}
 
@@
 \commits{ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a}
+\paper{Intro}{
+\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
+}
 

### 2019-12-09 5_generalization.tex
lil comment
forgotten \revise

@@
 \begin{minipage}[b]{0.8\linewidth}
+% -p test_geometry/wedge.svg -o wedge -s nrdi -n 1.5 -a --scale 1.5
 \begin{subfigure}[t]{\figwidth}\centering
@@
 Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
-Regions where the model is narrower than some $r_\text{min}$ can be printed with a bead width $w_\text{min}$ larger than the model thickness.
-In order to get results such as in \cref{widening} we can override
+Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
+We can simply override
 \begin{align*}

### 2019-12-09 12_conclusions_future_work.tex
emphasize implication for DfAM in conclusion (reviewer 1.1)
extra changes to conclusion (reviewer 1.2.1)

@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{ and we introduced beading schemes which improve on the state-of-the-art.}
+
 Our framework is flexible, demonstrated by the several beading schemes which emulate existing techniques.
@@
 
-We presented the inward distributed beading scheme.
-It reduces the amount of beads with a width deviating extremely from the preferred bead width, and thus it is expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
+\revise{We presented the}{The} inward distributed beading scheme
+\revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.
+\revise{, and thus it is}{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
 which in turn is helpful to efficiently simulate an FDM manufactured part.
+\revise{
 Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
+}{}
 
@@
 Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards most of the nozzle size considerations.}
 

### 2019-12-09 12_conclusions_future_work.tex
describe implications on full model (reviewer 3.12)

@@
 Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
-\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards most of the nozzle size considerations.}
+\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme improves the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
 

### 2019-12-10 6_2_printing_results.tex
fix lang of backpressure compensation method (reviewer 2.5)
move 5.2 implications to 5.2 printing results (reviewer 2.5)

@@
 In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
-One approach would be to varying the speed such that we keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant.
+One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly.
 However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
@@
 \end{figure}
+
+% adapted from 5.5 Discussion on implications
+\todo{Reword the following paragraph, which is adapted from 5.5 Discussion on implications.}
+
+Note that the current industry standard in FDM printing employs little to no bead width variation.
+\revise{
+Properly performing bead width variation calls for adaptations and developments in printers and firmware.
+In the beading schemes we set a transition length of $t(n) = w^*$.
+That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
+Varying the movement speed can be utilized to change the cross-sectional area, 
+}{While some software packages generate toolpaths similar to the state-of-the-art,
+the naive constant width offset approach is still widely used.
+Our backpressure compensation algorithm effectively changes the speed to realize adaptive width,
+}
+but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
+\revise{
+Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
+}{}
+Using a filament feeder directly mounted on the print head (a.k.a.
+direct drive) can \revise{control the flow more dynamicaly}{provide more dynamic control over the flow} \revise{then}{than} FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
+\revise{
+Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
+Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
+We expect that developments in printing hardware and firmware will address these challenges in the future.
+}{Direct drive printers can benefit from \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating},
+but presumably backpressure would still be a significant factor one might want to compensate for.
+}
+
+\todo{For super small layer heights it might be impossible to reach a bead width range with a factor of $2$.}
+
+Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
+G-code does not support moves with varying cross-sectional area.
+A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
+A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.
+However, this introduces errors nevertheless.
+Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.

### 2019-12-10 6_2_printing_results.tex
overhaul of printing results section (reviewer 2.5)

--- 2019-12-05 6_2_printing_results.tex
@@
-Test prints were performed on an unmodified Ultimaker S5 system,
-with a standard  \SI{0.4}{\milli\meter} nozzle
-and PLA filament
-and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
-In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
-One approach would be to varying the speed such that we keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant.
-However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
+\revise{}{
+\subsection{Printing results}
+In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
+we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
+A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a.
+\emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
+Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.
+
+\paragraph{Back pressure compensation}
+We therefore keep the internal pressure constant, and vary the movement speed instead.
+%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
+One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
+However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
 We conjecture that the filament outflow is related to the total pressure in the system,
 which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
-but also depends on the backpressure that the previous layer exerts on the filament protruding from the nozzle.
-We conjecture that the amount of backpressure is monotonically related to the requested line width and compensate for the backpressure using a simple linear model:
+but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
+We conjecture that the amount of back pressure is monotonically related to the requested line width and compensate for the back pressure using a simple linear model:
 
@@
 and
-$k$ is the amount of backpressure compensation.
+$k$ is the amount of back pressure compensation.
 Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
@@
 $w_0=\SI{0.4}{\milli\meter}$.
-See \cref{backpressure}.
+See \cref{back_pressure}.
+%
+Test prints were performed on an unmodified Ultimaker S5 system,
+with a standard  \SI{0.4}{\milli\meter} nozzle
+and PLA filament
+and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
+Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
+we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
+The results can be viewed in \cref{prints}.
 
@@
 \includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation-target.pdf}
-\caption{Target widths}\label{backpressure_target}
+\caption{Target widths}\label{back_pressure_target}
 \end{subfigure}
@@
 \includegraphics[angle=90,height=\figheight]{sources-validation-zero-backpressure-compensation.png}
-\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_backpressure}
+\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_back_pressure}
 \end{subfigure}
@@
 \includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation.png}
-\caption{Backpressure compensation}\label{backpressure}
+\caption{Back pressure compensation}\label{back_pressure}
 \end{subfigure}
@@
 Print results of varying width test on top of a dense white raft.
-Trying to reproduce \subref{backpressure_target} without backpressure compensation ($k=0$) yields worse results \subref{zero_backpressure} than with backpressure compensation $k=1.1$ \subref{backpressure}.
+Trying to reproduce \subref{back_pressure_target} without back pressure compensation ($k=0$) yields worse results \subref{zero_back_pressure} than with back pressure compensation $k=1.1$ \subref{back_pressure}.
 }
-\label{backpressure_compensation}
+\label{back_pressure_compensation}
 \end{figure}
+
+% discussion of print results
+\todo{TODO: discuss printed results.}
+
+% adapted from 5.5 Discussion on implications
+% limitations of back pressure compensation
+Our back pressure compensation method effectively changes the speed to realize adaptive width,
+but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018}.
+Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
+%
+% direct drive & pressure advance
+Accurate flow control can be further enhanced by using a direct drive hardware system and by employing \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating}.
+Conversely such a setup might benefit from some form of back pressure compensation as well.
+
+\begin{figure}
+\centering
+\begin{subfigure}{\columnwidth}\centering
+\setlength{\figwidth}{\columnwidth}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
+\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
+\end{subfigure}
+\setlength{\figheight}{.38\columnwidth}
+\setlength{\figheightTwo}{.47\columnwidth}
+\setlength{\figwidth}{0.32\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+\caption{Uniform}\label{print_naive}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+\caption{Centered}\label{print_center}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+\caption{Inward distributed}\label{print_inward}
+\end{subfigure}
+\caption{
+Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
+The uniform technique produces distinct underfill areas.
+The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
+The inward distributed scheme produces the least defects.
+}
+\label{prints}
+\end{figure}
+
+}

### 2019-12-10 12_conclusions_future_work.tex
mention back pressure compensation as contribution in intro and conclusion

@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{ and we introduced beading schemes which improve on the state-of-the-art.}
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{
+we introduced beading schemes which improve on the state-of-the-art
+and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
+}
 

### 2019-12-10 1_intro.tex
mention back pressure compensation as contribution in intro and conclusion

@@
 
-In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill. 
+In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
+\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state-of-the-art.} 
 We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
+\revise{
 For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
+}{Furthermore we present an approach to accurately realize adaptive bead width.
+}
 See \cref{intro_wedge_distributed}. 
@@
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
+\revise{}{
+\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
+}
 \end{itemize}

### 2019-12-11 1_intro.tex
fix bounds of width variation in Jin (reviewer 3.4)

@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
-\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is sometimes far greater~\cite{Ding2016a,Xiong2019}.
+\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is \revise{sometimes}{} far greater\revise{}{ for some parts}~\cite{Ding2016a,Xiong2019}.
 However, the range of widths manufacturable by FDM systems is limited.
@@
 
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
-% (0.8 * 2) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
+The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+% (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
 which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
@@
 \item A specific beading scheme for FDM printing which
-\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be generally below a factor of 2.}
+\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be below a factor of 2.}
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}

### 2019-12-11 2_related_work.tex
fix language mistakes (reviewer 1.7)
fix bounds of width variation in Jin (reviewer 3.4)

@@
 Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
-Third, the extruded path should cover a the region of the contour without gaps.
+Third, the extruded path should cover \revise{a }{}the region of the contour without gaps.
 Such underfill negatively influences the mechanical performance of the parts.
@@
 \citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
-The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
-In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme deviations in width (see \cref{intro_wedge_distributed}).
+The resulting variation of width in the center is still up to a factor of \revise{$2$}{$3.6$} (see \cref{intro_wedge_centered}).
+In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme \revise{deviations}{variation} in width (see \cref{intro_wedge_distributed}).
 

### 2019-12-11 5_generalization.tex
fix bounds of width variation in Jin (reviewer 3.4)

@@
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$.
-Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
+Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
 We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

### 2019-12-11 8_discussion.tex
move 5.2 implications to 5.2 printing results (reviewer 2.5)
overhaul of printing results section (reviewer 2.5)
fix bounds of width variation in Jin (reviewer 3.4)

--- 2019-08-31 8_discussion.tex
@@
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths are within a factor 2 off from the desired bead width.
+the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the variation is within a factor of $3.6$.}
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-We therefore conclude that the distributed schemes result in bead widths closer to the preferred widths compared to the centered scheme.
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
+the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
 %This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
@@
 
+\input{6_2_printing_results}
+
 \input{10_applications}
 
+\revise{
 \subsection{Discussion on implications}
@@
 Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
+}{}
 

### 2019-12-11 4_method.tex
give bounds on width variation (reviewer 3.4)
add forgotten \revise
lil language fix

@@
 An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
-As illustrated in See \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
+As illustrated in \revise{See }{}\cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
 This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
@@
 For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
+\revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
 

### 2019-12-11 10_applications.tex
lil clarification of inward bead count in applications fig (reviewer 1.9)

@@
 \caption{
-Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
+Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
 From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.

### 2019-12-11 6_validation.tex
overhaul of printing results section (reviewer 2.5)
describe DfAM implications (reviewer 1.1)

@@
 
+\revise{}
+{
+\subsection{Theoretical considerations}
+Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
+Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
+For the center scheme and for the current state-of-the-art one should only avoid parts for which $(i + 0.8) w^* < d < (i+ 1.25) w^*$ in order to avoid underfill.
+For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
+The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
+where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
+
+\todo{limitations}
+}
+
+\revise{}
+{
+\subsection{Computational results}
+}
 We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
@@
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
-
-\subsection{Computational results}
 
@@
 
-\subsection{Printing results}
 \revise{
@@
 The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
-}{
-\input{6_2_printing_results}
-}
 
@@
 \end{figure}
+}{}
 

### 2019-12-11 0_reviewer_response.tex
lil response fixes
new response to 1.1

@@
 	% Version a) First arg red and striked out, second argument green
-	\newcommand{\revise}[2]{\noindent{\color{red}{{#1}}}\noindent{\color{blue}{#2}}}
+	\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}\noindent{\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
@@
 Response to reviewers
-\
-\large{A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing}
+\\
+\large{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}}
 }
@@
 
-\stepcounter{question}
-
-\subQue{
+%\stepcounter{question}
+\Que{
 Could the authors provide a mathematical foundation for the relationship between the underfill/overfill areas and the allowed variation of bead width?
 I believe the proposed beading scheme can reduce the underfill/overfill areas somehow.
-}
-\Ans{
-There is not really a relationship between under-/overfill and the allowed variation in bead width,
-aside from the microgaps generated at 3-way intersections which play a minute role.
-The state-of-the-art (Jin et al 2017 JMS) does have a relationship: the ranges $[0,w_\text{min}]$ and $[w_\text{max},2w^*]$ produce underfill and overfill respectively, so making the allowed variation wider reduces the under-/overfill for their method and likewise for the centered beading scheme.
-However, the distributed beading schemes have no such limitation.
-They minimize under-/overfill with the requirement that the allowed variation in bead width is at least a factor of 2 ($[0.75w^*,1.5w^*]$).
-\todo{So...?}
-
-Because the beading scheme decides how to fill the full radial distance using some beading sequence, under-/overfill shouldn't be a problem anymore.
-However, because there are certain interactions in 2D, this doesn't always hold.
-For example a 3-way intersection in a 3D model which is a honeycomb pattern with a feature diameter of $w^*$ causes some over and underfill using \emph{any} possible technique.
-Our proposed beading schemes efectively deal with over- and underfill, and because the current state-of-the-art did not, the proposed beading scheme indeed reduces the undefill/overfill areas.
-}
-
-\todo{
-fix wording
-
-Make changes in paper:
-Clarify in intro, explain when introducing the Centered approach and show in the results section!
-Repeat in the conclusion?
-}
-
-\subQue{
 But we still lack a mathematical theory to guide the design.
@@
 \Ans{
-We now clearly indicate in the conclusion that we expect this paper to contribute to the reduction of Design for Aadditive Manufacturing (DfAM) constraints.
-}
-\todo{
-Maybe we should add something like the following to the manuscript: (but where?)
+The relationship between under-/overfill and bead widths can be split into several components:
+\begin{enumerate*}
+\item depending on the feature size
+\item depending on the change in feature size
+\item depending on the topology
+\end{enumerate*}
+.
+In the first case we consider a part with a constant feature size, in the second we consider the rate of change of feature size and in the thirs we consider the influence of 3-way intersections.
+
+1. When considering a part with constant feature diameter $d$ we note that the beading only depends on the feature diameter: $B(n, r) = B(q(2r), r)$.
+From the beading function we can easily derive the under-/overfill by summing over the bead widths $W$.
+We can then derive that the naive scheme produces over-/underfill at all diameters except $d=2i w^*$, the center scheme for $(i + 0.8) w^* < d < (i+ 1.25) w^*$ and the constant and distributed schemes nowhere (except for features smaller than $w^*$).
+We have added a paragraph to the new section 5.1 Theoretical consideration to explain this and the implications for design for additive manufacturing.
+
+2.
+When the feature size changes the amount of over-/underfill is related to a bisector angle $\alpha < \alpha_\text{max}$ according to the formula already given in section 3.3, paragraph `Significance measure':
+``This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$''.
+This formula is also relevant for the other beading schemes because the nonsignificant regions are filled in a similar fashion to the naive technique.
+For small bisector angles these under-/overfill areas are considered to be permittably small.
+We hope that this explanation suffices for the reviewer and the existing text suffices for the general reader.
+
+3.
+The topology also has an influence on underfill.
+For example, a 3-way intersection in a 3D model which is a honeycomb pattern with a feature diameter of $w^*$ causes some over and underfill using \emph{any} possible technique, because 3 printed beads come together in the same point.
+Also a honeycomb of $2w^*$ diameter causes some underfill in the center;
+when 3 beads surround a single point there will always remain a micro-gap because of the high viscosity of the molten filament.
+This is handled in Fig. 12 and the last paragraph of section 3.6.
+
+As for `the allowed variation of bead width': our vision \emph{was} that there should be no binary criterion for manufacturability and instead there should only be a floating number evaluation of manufacturability of a given bead width.
+However, we have now put bounds on the induced bead widths, so that the reader could compare our method to any range of `allowed variation' according to any manufacturability criterion.
+See the answer to question 3.4.
 }
 
-\revise{}{
-Suppose that under some criterion of manufacturability we have established that we can attain bead widths within the range $[w_\text{min}, w_\text{max}]$.
-We can then conclude that in order for a model to be manufacturable its widths should be within the set of ranges $\bigcup_{i\in \mathcal{N}}([i w_\text{min},i w_\text{max}])$.
-If $w_\text{min} = w_\text{max} = w^*$ this reduces to $\{w^*, 2w^*, 3w^* \dots\}$.
-On the other hand we assume that $w_\text{max} > 2 w_\text{min}$ and so a model is manufacturable if the feature size is within $[w_\text{min}, \infty]$ everywhere.
-%If for example $\nicefrac23 w_\text{min} < w_\text{max} < 2 w_\text{min}$, a manufacturable model should have widths in the ranges $\{[w_\text{min},w_\text{max}],[2 w_\text{min}, \infty]\}$
+\commits{2e1c40be93f92a8495c0d7fa379e983dd3ee7b98
+3b13960e15c07f484ab641a2d941f6086eda571c
+5b8c5971d606089754ba118560e51ec6d7dfda0b % new section
 }
-\todo{
-However, we propose no such binary criterion of manufacturability;
-instead we assume that the manufacturability generally diminishes as the requested bead width variation widens.
-By keeping the bead widths closer to the preferred bead width any reasonable measure of manufacturability is higher than for alternative methods.
-}
-
-\commits{2e1c40be93f92a8495c0d7fa379e983dd3ee7b98}
 \paper{Conclusion}{

### 2019-12-12 12_conclusions_future_work.tex
reduce travels as future work (reviewer 1.4)

@@
 Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
-An accurate model of manufacturability, print speed, and dimensional accuracy would be valuable to fine-tune the beading scheme.
+An accurate model of manufacturability, \revise{}{which relates }print speed\revise{, }{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
+\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
 % If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.

### 2019-12-12 6_validation.tex
lil fix to DfAM underfill/overfill bounds (reviewer 1.1)

@@
 Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center scheme and for the current state-of-the-art one should only avoid parts for which $(i + 0.8) w^* < d < (i+ 1.25) w^*$ in order to avoid underfill.
+For the center scheme and for the current state-of-the-art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
 For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.

### 2019-12-12 4_method.tex
lil explanation of 'skeleton' (reviewer 2.1)

@@
 
-Our method starts with computing \revise{the}{a type of} skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing \revise{the}{a type of} skeleton \revise{}{(a graph representing the topology) }of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).

### 2019-12-12 4_method.tex
mention discretization error of 0.013mm (reviewer 2.2.1, omit defaullt value for 3.7)

@@
 \end{enumerate*}
-The vertex-line and vertex-vertex edges are discretized into pieces with a length up to $d^\text{discretization}$.
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
 This allows to approximate the feature radius between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 

### 2019-12-12 5_generalization.tex
expand widening explanation (reviewer 3.2, 1.2.2)

@@
 \paragraph{Widening \revise{}{meta-scheme}}
-Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
+Complementary to any of these schemes we can enforce a minimum feature size \revise{at no extra cost}{and minimum bead width} in our framework.
 Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
+See \cref{min_feature_size} and~\subref{widening}.
 We can simply override
@@
 We therefore insert extra nodes along with their ribs at locations $v$ with a radial distance $R(v) = r_\text{min}$ for widening and at $R(v) \in \left\{ M w^*, q^{-1}(M), q^{-1}(M) + \nicefrac12 w^* \right\} $ for the transition from narrow shell to unconstrained shell.
-Combining all meta-schemes functionality we can generate results such as depicted in \cref{widening_shell}.
+Combining all meta-schemes functionality we can generate results such as depicted in \cref{shell}.
 
@@
 \centering
-\includegraphics[rotate=90,width=.6\columnwidth]{sources-validation-gMat_example_all_combined.png}
+\setlength{\figwidth}{.35\columnwidth}
+\setlength{\figwidthTwo}{.6\columnwidth}
+\begin{minipage}[b]{\figwidthTwo} \centering
+\begin{subfigure}[b]{\figwidthTwo}\centering
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
+\caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
+\\ on top of the Distributed scheme}
+\label{min_feature_size}
+\end{subfigure}
+\begin{subfigure}[b]{\figwidthTwo}\centering
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
+\caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
+\\ on top of the Center scheme}
+\label{widening}
+\end{subfigure}
+\end{minipage}
+\begin{subfigure}[b]{\figwidth}\centering
+\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
+\caption{Shell and widening}
+\label{shell}
+\end{subfigure}
 \caption{
-Toolpath generated with the inward distributed strategy ($N=1.5$) in conjunction with the widening meta-scheme ($W_\text{min}=0.5, 2r_\text{min}=0.2$, see top left) and the shell meta-scheme ($M=4$, see middle).
+Toolpaths using the widening and shel meta-schemes.
+\subref{min_feature_size} and~\subref{widening} show widening.
+\subref{shell}
+show toolpaths generated with the inward distributed strategy ($N=1.5$) in conjunction with the shell meta-scheme ($M=4$) and the same widening as in~\subref{widening}.
 % -p test_geometry/gMAT_example.svg -b 4 -s i -n 1.5 -a --mins 0.2 --minw .5
 Widening and shell require extra edges (green) at key locations in the skeleton.
-The azure area is to be filled using some direction-parallel toolpath generation algorithm.
+The azure area is to be filled using some direction-parallel toolpaths.
 }
@@
 \end{figure}
+
 }

### 2019-12-12 1_intro.tex
deviation > variation (reviewer 3.4)

@@
 \item A specific beading scheme for FDM printing which
-\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be below a factor of 2.}
+\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be below a factor of 2.}
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}

### 2019-12-12 8_discussion.tex
deviation > variation (reviewer 3.4)

@@
 the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
-We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
 %This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

### 2019-12-12 6_2_printing_results.tex
new S5 test prints (reviewer 2.5)

@@
 \centering
-\begin{subfigure}{\columnwidth}\centering
-\setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
-\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
-\end{subfigure}
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
+\setlength{\figwidth}{0.9\columnwidth}
 \begin{subfigure}{\figwidth}\centering
 %\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
 \caption{Uniform}\label{print_naive}
@@
 %\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
 \caption{Centered}\label{print_center}
@@
 %\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
 \caption{Inward distributed}\label{print_inward}

### 2019-12-12 6_2_printing_results.tex
better back pressure tweak figure (reviewer 2.5)

@@
 See \cref{back_pressure}.
+The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
 %
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation-target.pdf}
-\caption{Target widths}\label{back_pressure_target}
+\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure_0_0}
+\caption{$k=0$}\label{zero_back_pressure}
 \end{subfigure}
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[angle=90,height=\figheight]{sources-validation-zero-backpressure-compensation.png}
-\caption{Constant filament inflow (\si{\milli\meter\cubed\per\second})}\label{zero_back_pressure}
+\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure_1_1}
+\caption{$k=1.1$}\label{back_pressure}
 \end{subfigure}
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure-compensation.png}
-\caption{Back pressure compensation}\label{back_pressure}
+\includegraphics[angle=90,height=\figheight]{sources-validation-backpressure_2_0}
+\caption{$k=2.0$}\label{too_much_back_pressure}
 \end{subfigure}
 \caption{
-Print results of varying width test on top of a dense white raft.
-Trying to reproduce \subref{back_pressure_target} without back pressure compensation ($k=0$) yields worse results \subref{zero_back_pressure} than with back pressure compensation $k=1.1$ \subref{back_pressure}.
+Print results (black) of the varying width test on top of a dense white raft.
+Target widths in green.
+\subref{zero_back_pressure} Simple flow equalization without back pressure compensation results in nearly constant bead widths.
+\subref{back_pressure} A value of $k=1.1$ seems to produce good results.
 }

### 2019-12-13 4_method.tex
fix naive over-/underfill area formula (reviewer 1.1)

@@
 As illustrated in \revise{See }{}\cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
-This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
+This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$.
 Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},

### 2019-12-13 4_method.tex
rework beading schemes: remove framework parameters (reviewer 3.7)

@@
 This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$.
+\revise{}{A too large $\alpha_\text{max}$ leaves a lot of under-/overfill, while a too small value will introduce toolpaths to fill in negligibly small underfills.
+We therefore set $\alpha_\text{max} = \SI{135}{\degree}$.}
 Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},
@@
 if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
+\revise{}{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to significance measure.}
 
@@
 For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
+\revise{}{A value of $d_\text{max}^\text{transition} = \SI{1}{\milli\meter}$ seems to produce satisfactory results.}
 \revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
@@
 The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
-$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,
+\revise{$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,}
+{$t_0(n) \equiv \Delta(v_0v_x) =  t(n) \left( q^{-1}(n) / w^*  - n \right)$,}
 where $\Delta$ is the total distance along the edges between two nodes.
+\revise{}{The transition length $t(n)$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and the toolpath smooth.
+The transition anchor position $t_0(n)$ ensures that the transitions never overlap with each other or with locations where all beads have the preferred width $w^*$.}
+
 We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
@@
 There we also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
-and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.
+and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node\revise{.}{, which we set to $t_\text{beading} = w^* $, so that the transition is not too swift.}
 
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greedily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.
+In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$\revise{, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.}{.
+We set $d_\text{max}^\text{intersection} = \SI{75}{\percent}$ in order to slightly favor overfilling over underfilling.}
 This ratio effectively deals with the balance between overfill and underfill generated at that location after the retreat has been applied.

### 2019-12-13 5_generalization.tex
rework beading schemes: remove framework parameters (reviewer 3.7)

@@
 
+\revise{
 \begin{definition}\label{beading_scheme_definition}
@@
 \end{definition}
+}{}
 
+\revise{
 The following restrictions hold:
@@
 \end{enumerate}
+}{}
+
+\revise{}{
+\begin{definition}\label{beading_scheme_definition}
+A beading scheme is defined by the quatization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
+The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
+which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
+\end{definition}
+}
+
+% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section 3.4 Smooth transitions
+
+\revise{}{
+For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$.
+We further ensure
+that beads don't overlap,
+that beads are extruded from the center of where they end up
+and that odd bead counts produce a single polyline toolpath exactly in the center
+by determining the bead locations from the widths:
+}
+\begin{align*}
+L(n,r)_i = 
+\begin{cases}
+-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
+r & \text{ if } i =  \frac12 (n -1) \\
+%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
+\end{cases}
+\end{align*}
 
@@
 
+\revise{
 A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
@@
 \end{align*}
+}{}
 
+\revise{
 The toolpath locations $L$ ensure 
@@
 The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
+}{}
 
@@
 %
-\begin{subtable}[b]{\figwidth}
+\begin{subtable}[t]{\figwidth}
 \smallskip
@@
 $\begin{aligned}
-\alpha_\text{max} &= \SI{180}{\degree} \\
 q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
@@
 $\begin{aligned}
-\alpha_\text{max} &= \SI{0}{\degree} \\
 q(d) &= C \\
@@
 \multicolumn{2}{|l|}{
-\begin{subtable}[b]{\linewidth}
+\begin{subtable}[t]{\linewidth}
 \smallskip
@@
 $\begin{aligned}
-t(n) &= \frac12 w^* \\
 %q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
@@
 q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
+W(n,r)_i &= w^* + E(n,r) \frac{\omega(n,r)_i}{\sum_{j=0}^{n-1} \omega(n,r)_j} \text{ for all } i \\
 E(n,r) &= 2r - n w^* \\
-W(n,r)_i &= w^* + E(n,r) \frac{\omega(n,r)_i}{\sum_{j=0}^{n-1} \omega(n,r)_j} \text{ for all } i \\
 %L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
@@
 We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
-See \cref{formula_uniform}.
+\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simply beading scheme given by} \cref{formula_uniform}.
 
@@
 We can emulate the method from \citeauthor{Ding2016a} by dividing the feature radius over the widths of a constant number of beads.
-Additionally in order to emulate their definition of ``branches'' we mark all ST edges we unmark the outer edges connected to the outline shape in a separate algorithm.
+Additionally in order to emulate their definition of ``branches'' we mark all ST edges \revise{}{($\alpha_\text{max} = \SI{0}{\degree}$) and }we unmark the outer edges connected to the outline shape in a separate algorithm.
 Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since this marking depends on the topology of the graph of the ST.
@@
 Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
-We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.
+We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
 See \cref{formula_centered}.

### 2019-12-13 6_validation.tex
rework beading schemes: remove framework parameters (reviewer 3.7)

@@
 
-\todo{limitations}
+The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
+$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} = \SI{0.4}{\milli\meter}$ long segments.
+
+\todo{
+limitations
+
+mention single bead points here?
+}
+
 }

### 2019-12-13 6_validation.tex
lil typo fix

@@
 We sliced all models in the data set and selected 300 random slices for analysis.
-Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead widths of $w^* = \SI{0.4}{\milli\meter}$.
+Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
+and by our framework using four beading schemes, i.e.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead width\revise{s}{} of $w^* = \SI{0.4}{\milli\meter}$.
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

### 2019-12-13 8_discussion.tex
lil tex fix

@@
 G-code does not support moves with varying cross-sectional area.
-A typical extrusion move \lstinline{G1 X$x$ Y$y$ E$v$} only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
+A typical extrusion move \lstinline!G1 X$x$ Y$y$ E$v$!
+only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
 A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.

### 2019-12-13 12_conclusions_future_work.tex
lil reformulation in conclusion (reviewer 3.12)

@@
 Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
-\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme improves the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
+\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
 \revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}

### 2019-12-13 0_reviewer_response.tex
a lot of reviewers reponse based on feedback Jun & Zjenja

@@
 
-\begin{abstract}
-We have more clearly distinguished our work from existing methods.
-We have introduced extensions to the beading schemes:
-\begin{enumerate*}
-\item the widening meta-scheme is extended with a minimal feature size, in order to allow for a fair comparison between the various techniques 
-and
-\item a limiting meta-scheme is introduced which only generates the outer $N$ insets, so that the framework can readily be combined with the direction-parallel strategy in a manner common in FDM.
-\end{enumerate*}
-The results have been recalculated accordingly.
-We have developed a new manufacturing method which doesn't rely on custom machinery and which clearly shows the feasibility of adaptive bead width.
-We have computed fabrication time results.
-We have added a video animation explaining the union of cones approach in an intuitive manner.
-We have made various language fixes and improvements to images to address some of the reviewers' comments.
-\end{abstract}
-
 %
@@
 We feel that their feedback has provoked a leap forward in quality of the presented manuscript.
+We have addressed the reviewers' feedback and made changes to the text.
+Some of feedback has provoked large and structural changes to the manuscript;
+we list the most important changes here:
+
+\begin{enumerate}
+\item We have more clearly distinguished our work from existing methods.
+\item We have introduced extensions to the beading schemes:
+\begin{enumerate*}
+\item the widening meta-scheme is extended with a minimal feature size, in order to allow for a fair comparison between the various techniques 
+and
+\item a limiting meta-scheme is introduced which only generates the outer $N$ insets, so that the framework can readily be combined with the direction-parallel strategy in a manner common in FDM.
+\end{enumerate*}
+\item The results have been recalculated accordingly.
+\item We have developed a new manufacturing method which doesn't rely on custom machinery and which clearly shows the feasibility of adaptive bead width.
+\item We have computed fabrication time results.
+\item \todo{We have added a video animation explaining the union of cones approach in an intuitive manner.}
+\end{enumerate}
 
@@
 When the feature size changes the amount of over-/underfill is related to a bisector angle $\alpha < \alpha_\text{max}$ according to the formula already given in section 3.3, paragraph `Significance measure':
-``This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$''.
+``This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$}''.
 This formula is also relevant for the other beading schemes because the nonsignificant regions are filled in a similar fashion to the naive technique.
@@
 3b13960e15c07f484ab641a2d941f6086eda571c
-5b8c5971d606089754ba118560e51ec6d7dfda0b % new section
+5b8c5971d606089754ba118560e51ec6d7dfda0b % new section `Theoretical considerations'
+7c2224fc713f5b68436f432a1ade506e9dacf500 % lil edit in above section
+420cf6886a8e248aec4aafc04d13abc693da8dd0 % fix for naive over-/underfill area formula
 }
 \paper{Conclusion}{
-\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards most of the nozzle size considerations.}
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
 }
@@
 \stepcounter{question}
-
 \subQue{
@@
 }
-\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 e806d40e5e6d2bbe450c6792b802f0fcce4df645}
+\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 e806d40e5e6d2bbe450c6792b802f0fcce4df645 86c5aa8fab91e326e658f79a0746462fb99ea2b0}
 \paper{Intro}{
@@
  \paper{intro}{In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill.}
+\paper{Conclusion}{
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{ and we introduced beading schemes which improve on the state-of-the-art.}
+
+[\dots]
+
+\revise{We presented the}{The} inward distributed beading scheme
+\revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.
+\revise{, and thus it is}{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
+which in turn is helpful to efficiently simulate an FDM manufactured part.
+\revise{
+Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
+}{}
+}
 
@@
 \Ans{
-We now use the same minimal feature size in all approaches.
-We have added this functionality to the \emph{widening} meta-scheme.
-We have also added a figure to show that functionality.
+Note that this is not a limitation of the approach, but a consequence of the default parameters which were chosen.
+
+We have introduced a new parameter in the widening meta-scheme which can be used specificly to tune the minimal diameter starting from which we generate a toolpath.
+This minimum feature size is now used in the new computational test results and in Fig. 1.
 }
@@
 a88ccd3309aef1233ed00ce9f22b244fe64668f4
+8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to widening + shell fig
 }
@@
 \begin{figure} \centering
-\includegraphics[width=.5\linewidth]{response_no_corners}
-\caption{Example shape without sharp corners but with a large variation in feature size.}
+\setlength{\figwidth}{.45\columnwidth}
+\begin{subfigure}[b]{\figwidth} \centering
+\includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy.png}
+\caption{Problematic for center, i.e. Jin et al 2017 JMS, exhibiting $4.5w^*$ and $5.8w^*$}
+\end{subfigure}
+\begin{subfigure}[b]{\figwidth} \centering
+\includegraphics[width=\linewidth]{response_no_corners}
+\caption{Problematic for constant, i.e. Ding et al}
+\end{subfigure}
+\caption{Example shapes without sharp corners.}
 \label{no_corners}
@@
 
-Mention that the path order is not optimized
+Describe path order algorithm
 }
@@
 
-It should be noted that even small underfill areas can be unfillable using an overextrusion approach.
-For example the microgaps at 3-way intersections.
-The viscocity if molten filament is too high to reach into those small crevices.
+%It should be noted that even small underfill areas can be unfillable using an overextrusion approach.
+%For example the microgaps at 3-way intersections.
+%The viscocity of molten filament is too high to reach into those small crevices.
 }
@@
 
-mention as future work?
-
 That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
+}
+\commits{
+f2132c1c0cbce6daa29f64890be5f9e20c79c630 % future work notice
 }
@@
 }
-\commits{735762b1e7daf31ae4465bf288ef867ded7da095 93352058a46fb391e323df16f45466adb8cad508}
+\commits{735762b1e7daf31ae4465bf288ef867ded7da095 93352058a46fb391e323df16f45466adb8cad508
+87b1b779b759a9ad115f3ea61243568bfa2e0cb6 % lil change in Fig 20 caption
+}
 \paper{Beading schemes}
@@
 \Ans{
-Indeed we have intentionally not defined the term `skeleton'.
-It seems that there is no generally accepted \emph{intuitive} definition of `skeleton';
-the first occurance of the term was as synonymous with the medial axis and it was only defined \emph{mathematically}.
-However, the term is now used as an umbrella term for the various different types of skeleton.
-We have changes the wording a bit to make clear that `skeleton' refers to an undefined umbrella term.
-}
-\commits{5356492b5a9a690228ffdb6a6a26cf10d099a7d4}
+Early in the overview section we don't have a mathematical definition of the term `skeleton' yet.
+Seeing as there are multiple possible skeletonizations we use the term `skeleton' as an umbrella term and later give a specific definition of skeletons such as the Voronoi Diagram, the Medial axis and the trapezoidal skeletonization.
+We have added a clarification in the overview section for the readers who don't know what the umbrella term would refer to.
+}
+\commits{
+5356492b5a9a690228ffdb6a6a26cf10d099a7d4
+98af7981a67e9d54b3c47db5a2a41035e1278aeb % lil edit to the above
+}
 \paper{Method overview}{
-Our method starts with computing \revise{the}{a type of} skeleton of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing \revise{the}{a type of} skeleton \revise{}{(a graph representing the topology) }of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 }
@@
 See Figure~\ref{response_parabola_discretization}.
-
-We don't feel this type of discretization error is worth extending the manuscript with.
 
@@
 }
+\commits{
+64029a6ef57cf8044c521075ebc70cddfb52156b % mention 0.01mm in paper
+}
 
@@
 More generally, the technique seems to effectively be a variable offset scheme, but there is little discussion about what is known about variable offsets. 
-Find more literature
 }
@@
 elber1991error,
+
+add to related work? Tim doesn't feel this belongs there because the whole related work section is on toolpath generation.
+Adaptive offset techniques are only related to the technical contribution of this paper, so they don't belong in the related work section.
+However, when discussing the union of cones there is no logical place to discuss
 }
@@
 The photos of our print results already showed that adaptive width control is possible up to some (admittedly insufficient) extent.
-We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear backpressure compensation.
-We show the results of linear backpressure compensation in a separate figure which clearly shows the achieved variance in bead width.
+We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear back pressure compensation.
+We show the results of linear back pressure compensation in a separate figure which clearly shows the achieved variance in bead width.
+
+All paragraphs on the physical realization have been put together and moved to after the theoretical analysis:
+we moved the section on limitations of linear advance algorithms (5.5 Discussion on implications) together with the section on Printing results to after the comparison of beading schemes (now 5.2).
 }
 \todo{
-Show S5 prints. 
 The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
 }
-\commits{3d7238e2787f17c4cff63804eb4b84439ff85f1b }
+\commits{
+%3d7238e2787f17c4cff63804eb4b84439ff85f1b  % initial printing results section 5.2
+%b5abdd980240cd4ca964ed0f4751c207baa09b85 % move 5.5 to 5.2
+a0e98d1079b3ab3b262908ea056939813fc49c73 % move 5.2 to 5.3 and overhaul
+6362bb7f1ff11e15efc6667fc7863ca12a29a8a9 % mention in intro and conclusion
+22cb3664ddc722d25e0a73df905100410f8ebf10 444a00a54100e402024335b79265b6900017bc1d % S5 prints
+125162ad9878c0fb5a054f1bab34aa7b1353b86c % better var width test figure
+}
 \paper{5.2 Printing results}{
 \revise{}{
-Test prints were performed on an unmodified Ultimaker S5 system,
-with a standard  \SI{0.4}{\milli\meter} nozzle
-and PLA filament
-and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
-In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
-One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly.
-However, that doesn't result in the intended filament outflow variation - see \cref{zero_backpressure}.
+
+\revise{}{
+\subsection{Printing results}
+In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
+we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
+A different approach might be appropriate depending on whether the filament feeder is mounted directly on the print head (a.k.a.
+\emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
+Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.
+
+\paragraph{Back pressure compensation}
+We therefore keep the internal pressure constant, and vary the movement speed instead.
+%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
+One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
+However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
 We conjecture that the filament outflow is related to the total pressure in the system,
 which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
-but also depends on the backpressure that the previous layer exerts on the filament protruding from the nozzle.
-We conjecture that the amount of backpressure is monotonically related to the requested line width and compensate for the backpressure using a simple linear model:
+but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
+We conjecture that the amount of back pressure is monotonically related to the requested line width and compensate for the back pressure using a simple linear model:
 
@@
 Print results of varying width test on top of a dense white raft.
-Trying to reproduce \subref{backpressure_target} without backpressure compensation ($k=0$) yields worse results \subref{zero_backpressure} than with backpressure compensation $k=1.1$ \subref{backpressure}.
-}
-\label{backpressure_compensation}
+Trying to reproduce \subref{back_pressure_target} without back pressure compensation ($k=0$) yields worse results \subref{zero_back_pressure} than with back pressure compensation $k=1.1$ \subref{back_pressure}.
+}
+\label{back_pressure_compensation}
 \end{figure}
+
+% discussion of print results
+\todo{TODO: discuss printed results.}
+
+% adapted from 5.5 Discussion on implications
+% limitations of back pressure compensation
+Our back pressure compensation method effectively changes the speed to realize adaptive width,
+but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018}.
+Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
+%
+% direct drive & pressure advance
+Accurate flow control can be further enhanced by using a direct drive hardware system and by employing \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating}.
+Conversely such a setup might benefit from some form of back pressure compensation as well.
+
+\begin{figure}
+\centering
+\begin{subfigure}{\columnwidth}\centering
+\setlength{\figwidth}{\columnwidth}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
+\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
+\end{subfigure}
+\setlength{\figheight}{.38\columnwidth}
+\setlength{\figheightTwo}{.47\columnwidth}
+\setlength{\figwidth}{0.32\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+\caption{Uniform}\label{print_naive}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+\caption{Centered}\label{print_center}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+\caption{Inward distributed}\label{print_inward}
+\end{subfigure}
+\caption{
+Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
+The uniform technique produces distinct underfill areas.
+The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
+The inward distributed scheme produces the least defects.
+}
+\label{prints}
+\end{figure}
+
+}
 
@@
 
-\commits{6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae ac800628951417dcb28bd6e3a0ed08801735acf4 a88ccd3309aef1233ed00ce9f22b244fe64668f4 077c8ee138bb311a8ba9abf303af4b09e973637a}
+\commits{
+6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae % clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)
+ac800628951417dcb28bd6e3a0ed08801735acf4 % emphasize importance of contour-parallel toolpaths (reviewer 3.2)
+a88ccd3309aef1233ed00ce9f22b244fe64668f4 % introduce shell meta-scheme and replace widening figure with widening+shell figure 
+077c8ee138bb311a8ba9abf303af4b09e973637a % improve introduction of contour-parallel (reviewer 3.2)
+8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to shell + widening fig
+}
 \paper{Intro}{
@@
 }
-\commits{661d8f6766548c287cb174070432097e396d198f 92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d}
+\commits{
+661d8f6766548c287cb174070432097e396d198f 
+92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d
+2f230ea9f26f9870027e80db89eae8774f19d339
+acf8bbed0e530a3038d6fea064c33e7df6f0f933 % deviation > variation
+}
 \paper{Intro}{
@@
 }
-\todo{
-Maybe put something like “this figure is for back-reference if you forgot what a thing is for”
-
-Are you sure you mean figure 4? Maybe figure 3 or figure 2?
+\Ans{
+Fig. 4 shows a legend of terms and color coding scheme used throughout the paper;
+it doesn't show a decomposition.
+It is unclear to us what this review comment is asking for.
 }
@@
 }
-\todo{
-Make my reasons for choosing these more explicit
+\Ans{
+We feel that some of the confusion was due to the fact that the chosen values for these variables is stated in a location in the paper far away from where they were introduced.
+We now mention their value where they are introduced and explain their value further where needed.
+Making these framework parameters independent of the beading schemes simplifies the definition of a beading scheme and greatly simplifies section 4. Beading schemes.
+}
+\commits{
+64029a6ef57cf8044c521075ebc70cddfb52156b % d^discretization
+1ea800d0b4f68963befff90e535d5c82748df5e2 % big rework
 }
@@
 \Ans{
-The goal of sparse infill on the otherhand is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
+The goal of sparse infill is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
 However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
@@
 \todo{
-This is one of the usecases why this is a good method
-Discuss effect of this algorithm on the outline accuracy
+discuss visual quality of S5 prints in the paper.
 }
@@
 }
+\Ans{
+
+}
+\commits{
+3b13960e15c07f484ab641a2d941f6086eda571c dd293c060baae147ad1a217cf6ab68d8c4cb00c8
+}
+\paper{Conclusion}{
+\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
+}
+
+\Que{
+What are the limitations of the presented algorithm? I do not see any discussions of the limitations of the algorithm.
+}
 \todo{
-Perhaps discuss effect of width changes on amount of fusing between layers
-}
-
-\Que{
-What are the limitations of the presented algorithm? I do not see any discussions of the limitations of the algorithm.
-}
-\todo{
-Linear approximations
-
-a lot of direction changes (?)
+disconnected toolpaths
+
+single point tool paths
+
+still under-/overfill in non-significant regions
 }
@@
 Lil
-\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172}
+\commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172
+1662d3c4c3aa977bddd730ac59f1bc874b9eb574 % -''See ``
+b108d7de4f1e1e9676d45cf24eea263af6b8b9c7 % width => widths
+}
 

### 2019-12-17 6_2_printing_results.tex
better print results fig (reviewer 2.5)
spatially reorder prints and add target shapes (reviewer 2.5)
discuss print results, path order algorithm and restructure print results section (reviewer 2.5, 1.3)

@@
 
-\paragraph{Back pressure compensation}
+\subsubsection{Back pressure compensation}
 We therefore keep the internal pressure constant, and vary the movement speed instead.
@@
 % f &= f^* - k p_\text{ext} \\
- f(w) &= f_0 - k \left( w / w_0 - 1 \right) \\
- f_0 &= v_0 w_0 h 
+ f(w) &= f_0 - k \left( w / w_0 - 1 \right)
+ % f_0 &= v_0 w_0 h 
 % v &= \frac{f^* - k p_\text{ext}}{h w} \\ 
@@
 $k$ is the amount of back pressure compensation.
-Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
+
+% adapted from 5.5 Discussion on implications
+% limitations of back pressure compensation
+Our back pressure compensation method effectively changes the speed to realize adaptive width,
+but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018}.
+Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
+%
+% direct drive & pressure advance
+Accurate flow control can be further enhanced by using a direct drive hardware system and by employing \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating}.
+Conversely such a setup might benefit from some form of back pressure compensation as well.
+
+\subsubsection{Prints}
+Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
+$f_0 = v_0 w_0 h $
+with
 $v_0=\SI{30}{\milli\meter\per\second}$, 
-$w_0=\SI{0.4}{\milli\meter}$.
+$w_0=\SI{0.4}{\milli\meter}$
+and
+$h=\SI{0.1}{\milli\meter}$.
 See \cref{back_pressure}.
@@
 with a standard  \SI{0.4}{\milli\meter} nozzle
-and PLA filament
-and a layer thickness of $h=\SI{0.1}{\milli\meter}$.
+and PLA filament.
+The printing order is determined greadily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
 Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,
@@
 % discussion of print results
-\todo{TODO: discuss printed results.}
-
-% adapted from 5.5 Discussion on implications
-% limitations of back pressure compensation
-Our back pressure compensation method effectively changes the speed to realize adaptive width,
-but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018}.
-Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
-%
-% direct drive & pressure advance
-Accurate flow control can be further enhanced by using a direct drive hardware system and by employing \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating}.
-Conversely such a setup might benefit from some form of back pressure compensation as well.
+In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for the Ultimaker word mark, which negatively impacts the visual quality and the stiffness of the part.
+Moreover, in the case of the spatially graded honeycomb there are several fully disconnected hexagons, which means the object falls apart when picked up.
+The honeycomb print is also missing all parts which are slightly more thin than the preferred bead width $w^*$.
+\Cref{print_center} still shows some underfill, but considerably less than the uniform approach.
+These prints also exhibit dark regions where the translucency of the layer is less because the bead is higher.
+This can be explained by inaccuracies in the back pressure compensation method, which arise for bead widths which deviate from the preferred width by a large amount.
+\Cref{print_inward} diminishes the underfill nearly completely and the visual quality of these prints is more homogenous than those of the other methods.
+Moreover, the absence of dark regions signifies that our proposed method is more robust against inaccuracies in the deposition system.
+However, both the centered and inward distributed approach introduce transitions to a different bead count in the word `Delft', which reduces the dimensional accuracy on the outline around those locations.
 
@@
 \centering
-\setlength{\figwidth}{0.9\columnwidth}
+\setlength{\figwidth}{\columnwidth}
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-target}
+\caption{Outlines}\label{print_outlines}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
 \includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
 \includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
 \includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}

### 2019-12-17 6_validation.tex
move Theoretical considerations to 5.3 and discuss limitations (reviewer 3.13)

--- 2019-12-12 6_validation.tex
@@
 {
-\subsection{Theoretical considerations}
-Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
-Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center scheme and for the current state-of-the-art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
-For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
-The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
-where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
-
-\todo{limitations}
-}
-
-\revise{}
-{
-\subsection{Computational results}
+\subsection{Computational results}\label{sec_computational_results}
 }

### 2019-12-17 8_discussion.tex
move Theoretical considerations to 5.3 and discuss limitations (reviewer 3.13)

@@
 Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.
+
+\revise{}
+{
+\subsection{Limitations}
+Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
+Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
+For the center scheme and for the current state-of-the-art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
+The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
+where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
+
+The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
+$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} \approx \SI{0.4}{\milli\meter}$ long segments
+and under-/overfill areas of $\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right) \approx \SI{0.05}{\milli\meter\squared}$.
+However, future work might be aimed at reducing under-/overfill in regions with a low bisector angle without the introduction of short single polyline extrusion segments.
+If the over-/underfill problem is also solved for non-significant regions we might be able to increase $\alpha_\text{max}$ and reduce the discontinuity introduced by short extrusion segments.
+
+Another limitation of our method is that in a location $v$ with locally maximal $R(v) \approx (i + \nicefrac12) w^*$ the odd bead count will result in a single polyline extrusion segment consisting of only a single point.
+This can be viewed in the bottom right of \cref{TEST_InwardDistributed_accuracy} for example.
+In order to print such a dot, we make it into a \SI{10}{\micro\meter} long extrusion segment, with an altered width such that the total volume remains correct.
+A more principled way of dealing with such a situation remains future work.
+}
 

### 2019-12-17 8_discussion.tex
discuss emulation limitation (reviewer 2.7)

@@
 A more principled way of dealing with such a situation remains future work.
+
+Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
+The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
+Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
+However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
 }

### 2019-12-17 6_2_printing_results.tex
lil change in print section titles

@@
 \revise{}{
-\subsection{Printing results}
+\subsection{Fabrication}
 In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
@@
 
-\subsubsection{Prints}
+\subsubsection{Print results}
 Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use

### 2019-12-17 0_reviewer_response.tex
more reviewers response; before new statistics

@@
    \leavevmode\par
-   \stepcounter{question}
+   \refstepcounter{question}
    \noindent
@@
    \leavevmode\par
-   \stepcounter{subquestion}
+   \refstepcounter{subquestion}
    \noindent
@@
 The authors should highlight their contributions compared to the existing approaches for generating toolpaths with adaptive width.
-}
-\Ans{
-See also our response to 1.5.
-}
-\todo{
-Describe changes
-}
-\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 e806d40e5e6d2bbe450c6792b802f0fcce4df645 86c5aa8fab91e326e658f79a0746462fb99ea2b0}
+}\label{contributions}
+\Ans{
+The contributions were already listed at the end of the introduction, but now we highlight them in comparison to existing techniques.
+The focus on the comparison to existing techniques has also been applied to the conclusion.
+See also our response to question~\ref{difference_to_jin}.
+}
+\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 
+e806d40e5e6d2bbe450c6792b802f0fcce4df645 % hightlight contributions
+86c5aa8fab91e326e658f79a0746462fb99ea2b0 % changes to conclusion
+}
 \paper{Intro}{
@@
 }
-
+\Ans{
+We now included a description of the path order algorithm, which is naive and greedy.
+Because this algorithm is suboptimal, we separate the printing time into extrusion time and travel time.
+These (new) results shed light on how much more travel time is required relatively.
+Although an optimal path order algorithm might influence the travel time, such an algorithm is slow and not generally used in the industry.
+The software package Cura currently employs a similarly greedy algorithm.
+}
+\commits{
+d375878a8a6d01c53436aeb9c473dbedd8f3edcf % path order algorithm
+}
 \todo{
 Show results on printing time
-
-Describe path order algorithm
 }
@@
 Jin et al (2017) has proposed the strategy to add a toolpath with varying width along the center edges of the skeleton, and with unchanging width outside.
-}
+}\label{difference_to_jin}
 \Ans{
@@
 \Que{
-\label{fig1geometry}
 In Fig.1, how to justify the proposed approach as different geometries are used?
@@
 (a) and (b), there would be also underfill areas using the proposed approach.
-}
+}\label{fig1geometry}
 \Ans{
@@
 Moreover, the proposed technique seems to rely on rather accurate control of the width w of the deposited material, but it is not clear whether such control is achievable in practice. 
-}
-\Ans{
-The photos of our print results already showed that adaptive width control is possible up to some (admittedly insufficient) extent.
-We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: linear back pressure compensation.
-We show the results of linear back pressure compensation in a separate figure which clearly shows the achieved variance in bead width.
+}\label{s5_prints}
+\Ans{
+The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
+
+The photos of our print results already showed that adaptive width control is possible up to an admittedly insufficient extent.
+We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: \emph{back pressure compensation}.
+We show the results of back pressure compensation in a separate figure which clearly shows the achieved variance in bead width.
 
@@
 we moved the section on limitations of linear advance algorithms (5.5 Discussion on implications) together with the section on Printing results to after the comparison of beading schemes (now 5.2).
-}
-\todo{
-The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
 }
@@
 6362bb7f1ff11e15efc6667fc7863ca12a29a8a9 % mention in intro and conclusion
-22cb3664ddc722d25e0a73df905100410f8ebf10 444a00a54100e402024335b79265b6900017bc1d % S5 prints
+22cb3664ddc722d25e0a73df905100410f8ebf10 444a00a54100e402024335b79265b6900017bc1d ab38e07c84b6e62dc028d224b7a57bba9239552f cb3325a9cf00457fab5f1bdc5d29f1d178de4e35% S5 prints
+d375878a8a6d01c53436aeb9c473dbedd8f3edcf % prints discussion
 125162ad9878c0fb5a054f1bab34aa7b1353b86c % better var width test figure
@@
 }
-\todo{
-Discuss how much the over-fill / underfill and bead width variation depend on the fact that our reimplementations are only approximations.
+\Ans{
+We've added a paragraph to section 5.3. Limitations, which discusses these emulation limitations.
+}
+\commits{
+639dccad8e97fa1f0bdbb28e16b64f587572792d % paragraph in limitations
 }
@@
 We have tried to address this in response to several other reviewers' comments.
-See our response to 1.5, 1.1.1.
+See our response to question~\ref{difference_to_jin} and question~\ref{contributions}.
 We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
 }
-\todo{link with other responses}
 \commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
@@
 }
-\todo{
-discuss visual quality of S5 prints in the paper.
+\Ans{
+The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
+See our response to question ~\ref{s5_prints}.
 }
@@
 \Ans{
-
+We have discussed several implications of our method and in a sense they are all implications on the complete 3D result.
+In our revision we address several new implications;
+we address the influence of layers in each other and the implications of underfill on stiffness.
+We hope that these suffice.
 }
@@
 3b13960e15c07f484ab641a2d941f6086eda571c dd293c060baae147ad1a217cf6ab68d8c4cb00c8
+2f83d078036e267195431a7b077201eef0352e19 % influence of layers on back pressure
 }
@@
 }
-\todo{
-disconnected toolpaths
-
-single point tool paths
-
-still under-/overfill in non-significant regions
+\Ans{
+The limitations are now handled in section 5.3 Theoretical considerations, together with an analysis of the relation between feature size and bead width range.
+Some more general limitations are discussed in the Conclusions section.
+}
+\commits{
+5b8c5971d606089754ba118560e51ec6d7dfda0b % extrusion width range considerations
+ecf99f47dadf9973f527c1d471d662d87f6a5f51 % Limitations
 }

### 2019-12-18 12_conclusions_future_work.tex
lil change in conclusion
lil typo fixes

@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{
-we introduced beading schemes which improve on the state-of-the-art
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{,
+we introduced beading schemes which improve on the state of the art
 and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
@@
 
-\revise{We presented the}{The} inward distributed beading scheme
+\revise{We presented}{Compared to the state of the art,} the inward distributed beading scheme
 \revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.

### 2019-12-18 1_intro.tex
lil typo fixes

--- 2019-12-11 1_intro.tex
@@
 
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
 % (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
@@
 In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
-\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state-of-the-art.} 
+\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
 We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
@@
 \item A specific beading scheme for FDM printing which
-\revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to \revise{existing literature, }{the state-of-the-art to be below a factor of 2.}
+\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}

### 2019-12-18 4_method.tex
lil typo fixes

@@
 \paragraph{Approximation of union of cones}
-The skeleton trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
+The skeletal trapezoidation (ST) provides a means to visualize the union of cones (UoC) approximated by a 3D surface mesh composed of quadrilateral and triangular patches.
 %In order to visualize the ST as a 3D surface, we add a third dimension.

### 2019-12-18 8_discussion.tex
lil typo fixes

@@
 Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center scheme and for the current state-of-the-art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
 For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.

### 2019-12-18 0_reviewer_response.tex
add all changes to response and change some responses

@@
 	% Version a) First arg red and striked out, second argument green
-	\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}\noindent{\color{blue}{#2}}}
+	%\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}\noindent{\color{blue}{#2}}}
+	%\newcommand{\revise}[2]{{\textcolor{red}{#1}}{\textcolor{blue}{#2}}}
+	\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
@@
 \newcommand\paper[2]{\par changes to \emph{#1} --- ``#2'' }
-\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
+%\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
 
@@
 
-\Que{Example question by reviewer}
-\Ans{Example response}
-\revise{Old text in manuscript}{New text in manuscript}
+\Que{Example question by reviewer?}
+\Ans{Example response.}
+\paper{Section name}{
+Remaining text, followed by 
+\revise{outdated text in manuscript}{new text in manuscript}
+}
 \todo{Comment for us internally (should be removed before this letter is sent).}
@@
 
-\commits{2e1c40be93f92a8495c0d7fa379e983dd3ee7b98
-3b13960e15c07f484ab641a2d941f6086eda571c
+\commits{
+2e1c40be93f92a8495c0d7fa379e983dd3ee7b98 % emphasize implication for DfAM in conclusion
 5b8c5971d606089754ba118560e51ec6d7dfda0b % new section `Theoretical considerations'
@@
 }
-\paper{Conclusion}{
+\paper{6. Conclusion, last paragraph}{
 \revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
+}
+\paper{5.3 Limitations, first paragraph}{
+\revise{}{
+Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
+Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
+For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
+The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
+where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
+}
+}
+\paper{3.3 Method, Significance measure}{
+This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
 }
@@
 }
-\commits{66d006d91d406c0064ee1f4f1e4df85fc0821994 
-e806d40e5e6d2bbe450c6792b802f0fcce4df645 % hightlight contributions
+\commits{
+66d006d91d406c0064ee1f4f1e4df85fc0821994 % new contributions enumeration
+e806d40e5e6d2bbe450c6792b802f0fcce4df645 % lil typo
 86c5aa8fab91e326e658f79a0746462fb99ea2b0 % changes to conclusion
@@
 \paper{Intro}{
+In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
+\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
+We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
+\revise{
+For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
+}{Furthermore we present an approach to accurately realize adaptive bead width.
+}
+See \cref{intro_wedge_distributed}. 
+% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
+% Some such toolpath generation techniques have already been developed.
+
+Our contributions are as follows:
 \begin{itemize}
 \item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme for FDM printing which \revise{}{furthermore} reduces the amount of deviation in the extrusion widths compared to existing literature, and which \revise{promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{produces beads of exactly the preferred width outside of central regions of the outline shape.}
- \end{itemize}}
- \paper{intro}{In this paper we propose a framework for planning toolpaths with control over the adaptive width \revise{for}{while} minimizing over- and underfill.}
+\item A specific beading scheme for FDM printing which
+\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
+\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
+\revise{}{
+\item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
+}
+\end{itemize}
+}
 \paper{Conclusion}{
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{ and we introduced beading schemes which improve on the state-of-the-art.}
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{,
+we introduced beading schemes which improve on the state of the art
+and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
+}
 
@@
 From Fig. 1(b) and (c), we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
-}
+}\label{widening_question}
 \Ans{
@@
 0ac1c930a7cd2d1d305da730c9d5db20f4a8ea3f 
-9281d8ae7350539102be0ead7b2ffc611591d2b4 
-a88ccd3309aef1233ed00ce9f22b244fe64668f4
+9281d8ae7350539102be0ead7b2ffc611591d2b4 % fix widening figure
+a88ccd3309aef1233ed00ce9f22b244fe64668f4 %  introduce shell meta-scheme and replace widening figure with widening+shell figure
 8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to widening + shell fig
 }
-\paper{Beading schemes}{
+\paper{1. Introduction}
+{
+\begin{figure}\centering
+\setlength{\figwidth}{.9\columnwidth}
+\setlength{\figwidthTwo}{.05\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
+\end{subfigure}
+\caption{
+Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
+\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
+\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
+\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
+}
+\label{intro_wedge}
+\end{figure}
+\todo{See \cref{intro_wedge}.}
+}
+\paper{4. Beading schemes, end of section}{
 \paragraph{Widening \revise{}{meta-scheme}}
-Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
+Complementary to any of these schemes we can enforce a minimum feature size \revise{at no extra cost}{and minimum bead width} in our framework.
 Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
+See \cref{min_feature_size} and~\subref{widening}.
 We can simply override
@@
 \\
-\revise{}{
-W'(n,r)_0} &=
+W'(n,r)_0 &=
 \begin{cases}
@@
 }
-
 }
@@
 \paper{Intro}{
-Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
-}
-\paper{Intro wedge figure}{
-\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
+\todo{See caption of \cref{intro_wedge}.}
 }
@@
 {
-See \cref{legend}.
+\todo{See \cref{legend}.}
 \begin{figure}\centering
@@
 {
-See \cref{distributed_comparison}.
+\todo{See \cref{distributed_comparison}.}
 \begin{figure}
@@
 }
+\paper{Fig. 16}
+{
+\todo{New shape contains pointy wedge to see impact on minimal feature size.}
+}
+\paper{Caption of Fig. 16}
+{
+\revise{}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
+}
+\paper{Caption of Fig. 20}
+{
+Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
+}
 
@@
 \commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}
+\paper{Fig. 17b}{
+\todo{Figure now has the uniform curve}
+}
 
@@
 \commits{
-5356492b5a9a690228ffdb6a6a26cf10d099a7d4
-98af7981a67e9d54b3c47db5a2a41035e1278aeb % lil edit to the above
-}
-\paper{Method overview}{
+98af7981a67e9d54b3c47db5a2a41035e1278aeb % lil explanation of 'skeleton' (reviewer 2.1)
+5356492b5a9a690228ffdb6a6a26cf10d099a7d4 % make clear that a skeleton is an undefined term (reviewer 2.1)
+}
+\paper{3.1 Method overview}{
 Our method starts with computing \revise{the}{a type of} skeleton \revise{}{(a graph representing the topology) }of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
@@
 \Ans{
-We chose for linear approximations because they simplify the process,
+We chose for linear approximations because they simplify the algorithms,
 whereas we chose for Boost because it seemed more stable than alternative libraries.
@@
 }
+\paper{3.2 Union of cones, Skeletal trapezoidation}
+{
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
+}
 
@@
 That figure is reproduced here in Fig.~\ref{overview_outline}.
-As the rightmost two points move right the degree of the corner in the middle goes to zero which causes the parts of the parabola revealed are more accurately described by the discretization than the highly curved part in the middle.
+As the rightmost two points move right, the degree of the corner in the middle goes to zero, which causes the parts of the parabola revealed to be more accurately described by the discretization than the highly curved part in the middle.
 }
@@
 }
-
+\Ans{
+Indeed the locations of the junctions in the toolpaths are at variable offsets from the outline, but that doesn't make our framework a variable offset scheme, because the junction locations are determined both by the radius in the central regions and the location of the outline.
+Computing the same toolpaths using some variable offset scheme would still require the computation of the radial distances in central regions and relate those to outline locations, which means that we would still need to use the skeleton.
+Therefore a variable offset scheme is not an alternative to our framework.
+
+We have not found any variable offset scheme literature which is specifically on toolpath generation, so it wouldn't fit in the related work section.
+The method section, however, doesn't go into variable offset schemes because offset schemes apply offset values given at the outline, while our framework principally relates the outline and the skeleton.
+}
 \todo{
-elber1991error,
-
-add to related work? Tim doesn't feel this belongs there because the whole related work section is on toolpath generation.
-Adaptive offset techniques are only related to the technical contribution of this paper, so they don't belong in the related work section.
-However, when discussing the union of cones there is no logical place to discuss
+elber1991error
 }
@@
 \paper{5.2 Printing results}{
-\revise{}{
-
-\revise{}{
-\subsection{Printing results}
+
+\revise{
+Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
+The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
+gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
+We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
+We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
+
+The prints are shown in \cref{prints_old}.
+Because of inaccuracies in the deposition control system some of the prints show defects.
+Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
+The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
+Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
+The difference between the centered and the inward distributed schemes is less pronounced.
+We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
+However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
+The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
+
+\begin{figure}
+\centering
+\begin{subfigure}{\columnwidth}\centering
+\setlength{\figwidth}{\columnwidth}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
+\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
+\end{subfigure}
+\setlength{\figheight}{.38\columnwidth}
+\setlength{\figheightTwo}{.47\columnwidth}
+\setlength{\figwidth}{0.32\columnwidth}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+\caption{Uniform}\label{print_naive}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+\caption{Centered}\label{print_center}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+\caption{Inward distributed}\label{print_inward}
+\end{subfigure}
+\caption{
+Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
+The uniform technique produces distinct underfill areas.
+The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
+The inward distributed scheme produces the least defects.
+}
+\label{prints_old}
+\end{figure}
+}{
+\subsection{Fabrication}
 In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
@@
 $k$ is the amount of back pressure compensation.
-Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where
+
+% adapted from 5.5 Discussion on implications
+% limitations of back pressure compensation
+Our back pressure compensation method effectively changes the speed to realize adaptive width,
+but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018}.
+Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
+Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.
+%
+% direct drive & pressure advance
+Accurate flow control can be further enhanced by using a direct drive hardware system and by employing \emph{pressure advance algorithms} which dynamically change the internal pressure \cite{tronvoll2019investigating}.
+Conversely such a setup might benefit from some form of back pressure compensation as well.
+
+\subsubsection{Print results}
+Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use
+$f_0 = v_0 w_0 h $
+with
 $v_0=\SI{30}{\milli\meter\per\second}$, 
-$w_0=\SI{0.4}{\milli\meter}$.
+$w_0=\SI{0.4}{\milli\meter}$
+and
+$h=\SI{0.1}{\milli\meter}$.
 See \cref{back_pressure}.
+The fact that the printed lines are wider than intended is compensated for using a flow reduction to \SI{90}{\percent}.
 %
@@
 \centering
-\begin{subfigure}{\columnwidth}\centering
 \setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
-\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
-\end{subfigure}
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-target}
+\caption{Outlines}\label{print_outlines}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
 \caption{Inward distributed}\label{print_inward}
@@
 \end{figure}
-
-}
-
-}
+}
+\revise{
+\subsection{Discussion on implications}
+Note that the current industry standard in FDM printing employs little to no bead width variation.
+Properly performing bead width variation calls for adaptations and developments in printers and firmware.
+In the beading schemes we set a transition length of $t(n) = w^*$.
+That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
+Varying the movement speed can be utilized to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
+Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
+Using a filament feeder directly mounted on the print head (a.k.a.
+direct drive) can control the flow more dynamicaly then FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
+Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
+Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
+We expect that developments in printing hardware and firmware will address these challenges in the future.
+
+Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
+G-code does not support moves with varying cross-sectional area.
+A typical extrusion move \lstinline!G1 X$x$ Y$y$ E$v$!
+only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
+A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.
+However, this introduces errors nevertheless.
+Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
+}{}
 }
@@
 639dccad8e97fa1f0bdbb28e16b64f587572792d % paragraph in limitations
+}
+\paper{5.3 Limitations}
+{
+\revise{}{
+Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
+The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
+Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
+However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
+}
 }
@@
 }
+\Ans{
 The title has changed.
-\revise{additive manufacturing}{fused deposition modeling}
-\commits{64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0}
+}
+\commits{
+64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0
+}
 \paper{Title}{
@@
 We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with the industry standard for FDM 3D printing.
+See also the changes to the paper presented under question~\ref{widening_question}.
 }
@@
 }
+\paper{Abstract}{
+\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
+}
+
 \paper{Intro}{
@@
 }
+
+\Que{
+Related work acknowledges the previous work sufficiently.
+However, the differences between the state of the art and the presented work are not clear.
+More discussion on where this work stands with respect to the state of the art is required.
+}
+\Ans{
+We have tried to address this in response to several other reviewers' comments.
+See our response to question~\ref{difference_to_jin} and question~\ref{contributions}.
+We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
+See also our response to question~\ref{widening_question} for clarification in the difference between Fig 1b and 1c.
+}
+\commits{
+004894210fbc961f82b792fc702d1b67a1a8e8e8 lil lang improvement (reviewer 3.3)
+9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in fig 1 (reviewer 1.6, 3.3)
+}
+\paper{Fig 1}{
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
+}
+
+\Que{
+Isn’t it possible to put bounds on the width in the existing methods, such as the approach described in [9]? More discussion on that would be helpful. 
+}
+\Ans{
+The bead width in Jin et al. is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.6$;
+this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.6$.
+We emphasized that our method results in a bead width variation of $2$, rather than $3.6$ in the related work section and in the discussion section.
+This factor comes from the transition from a single bead to two beads.
+(The transition from zero beads to one is disregarded; it is controlled separately by the Widening meta-scheme.)
+}
+\commits{
+661d8f6766548c287cb174070432097e396d198f 
+92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d give bounds on width variation (reviewer 3.4)
+2f230ea9f26f9870027e80db89eae8774f19d339 fix bounds of width variation in Jin (reviewer 3.4)
+acf8bbed0e530a3038d6fea064c33e7df6f0f933 % deviation > variation
+}
+\paper{Intro}{
+The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+}
+\paper{3.4. Central height adjustment, Transition anchors, filtering paragraph}
+{
+\revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
+}
+\paper{5.2 Comparison of beading schemes, paragraph 3, 4}{
+In \cref{TEST_Center_accuracy} we can see that
+the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the variation is within a factor of $3.6$.}
+
+[\dots]
+
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
+the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
+}
+
+\Que{
+Figure 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
+}
+\Ans{
+Fig. 4 shows a legend of terms and color coding scheme used throughout the paper;
+it doesn't show a decomposition.
+It is unclear to us what this review comment is asking for.
+}
+
+\Que{
+In Figure 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
+}
+\Ans{
+Fixed. Fig 3 c and d now have the same discretization.
+}
+\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
+
+\Que{
+It is unclear how some of the parameters are adjusted, such as $\alpha_\text{max}, d_\text{max}^\text{unmarked}, d_\text{transition}^\text{max}, t_\text{beading}, d_\text{intersection}^\text{max}$.
+What are their effects on the end result?
+Selections seem somewhat arbitrary.
+}
+\Ans{
+We feel that some of the confusion was due to the fact that the chosen values for these variables is stated in a location in the paper far away from where they were introduced.
+We now mention their value where they are introduced and explain their value further where needed.
+Making these framework parameters independent of the beading schemes simplifies the definition of a beading scheme and greatly simplifies section 4. Beading schemes.
+}
+\commits{
+64029a6ef57cf8044c521075ebc70cddfb52156b % d^discretization
+1ea800d0b4f68963befff90e535d5c82748df5e2 % big rework
+}
+\paper{3.2 Union of cones, Skeletal trapezoidation}
+{
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
+}
+\paper{3.3 Center classification, Significance measure}
+{
+\revise{}{A too large $\alpha_\text{max}$ leaves a lot of under-/overfill, while a too small value will introduce toolpaths to fill in negligibly small underfills.
+We therefore set $\alpha_\text{max} = \SI{135}{\degree}$.}
+}
+\paper{3.3 Center classification, Marking filtering}
+{
+\revise{}{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to significance measure.}
+}
+\paper{3.4 Central height adjustment, Transition anchors}
+{
+\revise{}{A value of $d_\text{max}^\text{transition} = \SI{1}{\milli\meter}$ seems to produce satisfactory results.}
+}
+\paper{3.4 Central height adjustment, Smooth transitions}
+{
+ The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
+\revise{$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,}
+{$t_0(n) \equiv \Delta(v_0v_x) =  t(n) \left( q^{-1}(n) / w^*  - n \right)$,}
+ where $\Delta$ is the total distance along the edges between two nodes.
+\revise{}{The transition length $t(n)$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and the toolpath smooth.
+The transition anchor position $t_0(n)$ ensures that the transitions never overlap with each other or with locations where all beads have the preferred width $w^*$.}
+}
+\paper{3.5 Beading, Beading interpolation}{
+There we also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
+and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node\revise{.}{, which we set to $t_\text{beading} = w^* $, so that the transition is not too swift.}
+ }
+\paper{3.6 Toolpath extraction, last paragraph}{
+In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$\revise{, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.}{.
+We set $d_\text{max}^\text{intersection} = \SI{75}{\percent}$ in order to slightly favor overfilling over underfilling.}
+}
+\paper{4. Beading schemes}
+{
+\revise{
+\begin{definition}\label{beading_scheme_definition}
+The beading scheme is configured by the following set of functions and constants:
+\begin{align*}
+\{
+&q(d),
+B(n, r),
+t(n),
+t_0(n),
+\\
+&\alpha_\text{max}, 
+t_\text{beading}, 
+d_\text{max}^\text{transition}, 
+d_\text{max}^\text{unmarked}, 
+d_\text{max}^\text{intersection},
+d^\text{discretization}
+ \}
+\end{align*}
+where, as introduced in previous section,
+$q(d)$ the quantization operator,
+$B(n,r)$ is the beading function consisting of $\left( W(n,r), L(n,r) \right)$,
+$t(n)$ the transition length,
+$t_0(n)$ the transition anchor position,
+$\alpha_{\text{max}}$ is the limit bisector angle,
+$t_\text{beading}$ is the beading conflict transition length,
+$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
+$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
+$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
+and
+$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
+%$W(n, r)$ and $L(n, r)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
+\end{definition}
+}{}
+
+\revise{
+The following restrictions hold:
+\begin{enumerate}
+	\begin{minipage}{\columnwidth}
+	\setlength\intextsep{0pt}
+	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
+	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
+	%\caption{
+	%%Transition ends (magenta and pink) shouldn't cross each other.
+	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
+	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
+	%}
+	\label{transition_placement}
+	\end{wrapfigure}
+	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
+\end{minipage}
+\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
+\item For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
+\end{enumerate}
+}{}
+
+\revise{}{
+\begin{definition}\label{beading_scheme_definition}
+A beading scheme is defined by the quatization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
+The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
+which provides sequences of $n$ bead widths and of $n$ distances from the outline to fill up a radial distance $r$.
+\end{definition}
+}
+% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section 3.4 Smooth transitions
+
+\revise{}{
+For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$.
+We further ensure
+that beads don't overlap,
+that beads are extruded from the center of where they end up
+and that odd bead counts produce a single polyline toolpath exactly in the center
+by determining the bead locations from the widths:
+}
+\begin{align*}
+L(n,r)_i = 
+\begin{cases}
+-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
+r & \text{ if } i =  \frac12 (n -1) \\
+%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
+\end{cases}
+\end{align*}
+
+% \subsection{Beading schemes}
+We introduce several beading schemes which determine the bead count and their widths in various ways.
+We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
+We also introduce new beading schemes which produce toolpaths with less extreme widths compared to techniques from existing literature.
+
+\revise{
+A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
+Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
+Most of the beading schemes we introduce share a common ground:
+\begin{align*}
+L(n,r)_i = 
+\begin{cases}
+-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
+r & \text{ if } i =  \frac12 (n -1) \\
+%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
+\end{cases}
+\\
+\begin{array}{rlrl}
+t_\text{beading} &= w^* 
+&
+d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
+\\
+t(n) &= w^*
+&
+d_\text{max}^\text{unmarked} &= w^*
+\\
+t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
+&
+d^\text{discretization} &= \SI{0.2}{\milli\meter}
+\\
+\alpha_\text{max} &= \SI{135}{\degree} 
+&
+d_\text{max}^\text{intersection} &= \SI{75}{\percent}
+\end{array}
+%\end{align*}
+%\begin{align*}
+\end{align*}
+}{}
+
+\revise{
+The toolpath locations $L$ ensure 
+that the beads don't overlap,
+that beads are extruded from the center of where they end up
+and that the symmetry restrictions are met.
+The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $R(v) = \nicefrac12 n w^*$ for $n \in \mathbb{N}$.
+The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
+The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
+}{}
+
+\paragraph{Uniform beading scheme}
+[\dots]
+\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.
+
+[\dots]
+
+\paragraph{Constant bead count}
+[\dots]
+Additionally in order to emulate their definition of ``branches'' we mark all ST edges \revise{}{($\alpha_\text{max} = \SI{0}{\degree}$) and }we unmark the outer edges connected to the outline shape in a separate algorithm.
+[\dots]
+
+\paragraph{Centered}
+[\dots]
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
+Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
+We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
+}
+\paper{5.3 Limitations, second paragraph}
+{
+\revise{}{
+The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
+$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} \approx \SI{0.4}{\milli\meter}$ long segments
+and under-/overfill areas of $\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right) \approx \SI{0.05}{\milli\meter\squared}$.
+However, future work might be aimed at reducing under-/overfill in regions with a low bisector angle without the introduction of short single polyline extrusion segments.
+If the over-/underfill problem is also solved for non-significant regions we might be able to increase $\alpha_\text{max}$ and reduce the discontinuity introduced by short extrusion segments.
+}
+}
+
+\Que{
+Is this approach generalizable to sparse infill? It is very common in FDM to use a sparse infill and only use dense fill on surface regions.
+}
+\Ans{
+The goal of sparse infill is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
+However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
+See our response to 3.2.
+}
+
+\Que{
+If this is used for outer surface, what are the implications on the surface quality in comparison to other approaches? 
+}
+\Ans{
+The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
+See our response to question ~\ref{s5_prints}.
+}
+\commits{
+6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)
+}
 \paper{Abstract}{
@@
 {High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
-}
-
-\Que{
-Related work acknowledges the previous work sufficiently.
-However, the differences between the state of the art and the presented work are not clear.
-More discussion on where this work stands with respect to the state of the art is required.
-}
-\Ans{
-We have tried to address this in response to several other reviewers' comments.
-See our response to question~\ref{difference_to_jin} and question~\ref{contributions}.
-We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
-}
-\commits{004894210fbc961f82b792fc702d1b67a1a8e8e8}
-\paper{Fig 1}{
-\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
-}
-
-\Que{
-Isn’t it possible to put bounds on the width in the existing methods, such as the approach described in [9]? More discussion on that would be helpful. 
-}
-\Ans{
-The bead width in Jin et al. is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.2$;
-this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.2$.
-We emphasized that our method (generally) results in a bead width deviation of $2$, rather than $3.2$ in the related work section and in the discussion section.
-}
-\commits{
-661d8f6766548c287cb174070432097e396d198f 
-92217c04e118dcf6f65b16a1ffcdfa40b4d50c0d
-2f230ea9f26f9870027e80db89eae8774f19d339
-acf8bbed0e530a3038d6fea064c33e7df6f0f933 % deviation > variation
-}
-\paper{Intro}{
-The current state-of-the-art for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads at most by a factor of \revise{$2$}{$3.2$}~\cite{Jin2017JMS},
-}
-\paper{Discussion}{
-In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
-the deviation is within a factor of $3.2$.}
-}
-\paper{Discussion}{
-\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads the bead widths range from $0.75w^*$ to $1.5w^*$, i.e.
-the deviation is within a factor $2$, which is considerably lower than in the centered scheme.}
-We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width deviation} compared to the centered scheme.
-}
-
-\Que{
-Figure 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
-}
-\Ans{
-Fig. 4 shows a legend of terms and color coding scheme used throughout the paper;
-it doesn't show a decomposition.
-It is unclear to us what this review comment is asking for.
-}
-
-\Que{
-In Figure 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
-}
-\Ans{
-Fixed. Fig 3 c and d now have the same discretization.
-}
-\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
-
-\Que{
-It is unclear how some of the parameters are adjusted, such as $\alpha_\text{max}, d_\text{max}^\text{unmarked}, d_\text{transition}^\text{max}, t_\text{beading}, d_\text{intersection}^\text{max}$.
-What are their effects on the end result?
-Selections seem somewhat arbitrary.
-}
-\Ans{
-We feel that some of the confusion was due to the fact that the chosen values for these variables is stated in a location in the paper far away from where they were introduced.
-We now mention their value where they are introduced and explain their value further where needed.
-Making these framework parameters independent of the beading schemes simplifies the definition of a beading scheme and greatly simplifies section 4. Beading schemes.
-}
-\commits{
-64029a6ef57cf8044c521075ebc70cddfb52156b % d^discretization
-1ea800d0b4f68963befff90e535d5c82748df5e2 % big rework
-}
-
-\Que{
-Is this approach generalizable to sparse infill? It is very common in FDM to use a sparse infill and only use dense fill on surface regions.
-}
-\Ans{
-The goal of sparse infill is to generate intentional spacing between lines; this is not reconcilable with the goal of preventing underfill.
-However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
-See our response to 3.2.
-}
-
-\Que{
-If this is used for outer surface, what are the implications on the surface quality in comparison to other approaches? 
-}
-\Ans{
-The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
-See our response to question ~\ref{s5_prints}.
 }
@@
 We hope that these suffice.
-}
-\commits{
-3b13960e15c07f484ab641a2d941f6086eda571c dd293c060baae147ad1a217cf6ab68d8c4cb00c8
+% See answers to question~\ref{contributions}
+}
+\commits{
+3b13960e15c07f484ab641a2d941f6086eda571c describe implications on full model (reviewer 3.12)
+dd293c060baae147ad1a217cf6ab68d8c4cb00c8 lil reformulation in conclusion (reviewer 3.12)
 2f83d078036e267195431a7b077201eef0352e19 % influence of layers on back pressure
 }
-\paper{Conclusion}{
+\paper{6. Conclusion and future work, last paragraph}{
 \revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
+}
+\paper{5.4.1 Back pressure compensation}
+{
+\revise{}{Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.}
 }
@@
 \Ans{
-The limitations are now handled in section 5.3 Theoretical considerations, together with an analysis of the relation between feature size and bead width range.
-Some more general limitations are discussed in the Conclusions section.
+The limitations are now handled in a new section, together with an analysis of the relation between feature size and bead width range.
+%Some more general limitations are discussed in the Conclusions section.
 }
@@
 5b8c5971d606089754ba118560e51ec6d7dfda0b % extrusion width range considerations
-ecf99f47dadf9973f527c1d471d662d87f6a5f51 % Limitations
+ecf99f47dadf9973f527c1d471d662d87f6a5f51 move Theoretical considerations to 5.3 and discuss limitations (reviewer 3.13)
+}
+\paper{5.3 Limitations}
+{
+\revise{}{
+Another limitation of our method is that in a location $v$ with locally maximal $R(v) \approx (i + \nicefrac12) w^*$ the odd bead count will result in a single polyline extrusion segment consisting of only a single point.
+This can be viewed in the bottom right of \cref{TEST_InwardDistributed_accuracy} for example.
+In order to print such a dot, we make it into a \SI{10}{\micro\meter} long extrusion segment, with an altered width such that the total volume remains correct.
+A more principled way of dealing with such a situation remains future work.
+
+Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.
+The transitions resulting from out framework introduce sharper corners and there is more width variation in those corners.
+Whereas the width of the connecting segment in the approach by \citeauthor{Jin2017JMS} is the preferred width $w^*$, the bead widths closer to the center resulting from our framework will be twice the local radius, which is larger than $w^*$.
+However, this inflated bead width variation is expected to have an insignificant impact on the measured bead width variation.
+}
 }
@@
 b108d7de4f1e1e9676d45cf24eea263af6b8b9c7 % width => widths
+9d9f02edc43689c0970a74118e44a196cc11c729 % typos
+}
+
+Our department has changed its name:
+\commits{
+442a5df5a4f27f1ce94a5ef298a1f7bcc3df934d
+}
+
+Removed confusing red parts from beading figure:
+\commits{
+1196bad1c2bf4fb41e7d28985938cfe678384e5a
 }

### 2020-01-16 0_reviewer_response.tex
lil edits to response to reviewers

@@
 %\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
+
+\newcommand\Summary[1]{
+   \noindent\emph{Summary.} {\bf#1}\par}
 
@@
 
-\Que{Example question by reviewer?}
+\Que{Example text by reviewer.}
 \Ans{Example response.}
@@
 \section{Reviewer 1}
+\Summary{
 Overall, the paper proposes some novel frameworks which are meaningful to additive manufacturing. Therefore, I suggest it for publication once the following major comments are addressed. 
+}
+\Ans{
+We agree with this summary, although it does not stress the contribution of a novel beading scheme in the framework which improves on the state of the art.
+We have made various changes to highlight those as separate contributions.
+}
 
@@
 \section{Reviewer 2}
+\Summary{
 The paper is generally well written with clear illustrations. 
+}
+\Ans{
+Thank you.
+}
 
@@
 \section{Reviewer 3}
+\Summary{
 Paper is well written.
@@
 My specific comments are below:
+}
+\Ans{
+Thank you for your feedback.
+
+}
 
@@
 
+\bibliography{99_mybib}
+
 \end{document}

### 2020-01-16 4_method.tex
reclarify 'skeleton' (reviewer 2.1)

@@
 
-Our method starts with computing \revise{the}{a type of} skeleton \revise{}{(a graph representing the topology) }of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
+Our skeleton is} based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).

### 2020-01-16 4_method.tex
remove concept of peripheral, because it's not really used

@@
 In order to prevent over- and underfill to occur in central, we mark parts of the ST as being central.
-The remainder is called peripheral.
+\revise{The remainder is called peripheral.}{}
 Our framework will decide on a beading at all the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).

### 2020-01-16 4_method.tex
lil rephrase (reviewer 3.7)

@@
 This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$.
-\revise{}{A too large $\alpha_\text{max}$ leaves a lot of under-/overfill, while a too small value will introduce toolpaths to fill in negligibly small underfills.
+\revise{}{A too large $\alpha_\text{max}$ may leave a lot of under-/overfill, while a too small value may introduce toolpaths to fill in negligibly small underfills.
 We therefore set $\alpha_\text{max} = \SI{135}{\degree}$.}

### 2020-01-16 4_method.tex
remove 'periphery' (lil extra changes)

@@
 \subsection{Beading}\label{sec_peripheral_height_adjustment}
-Now that we have determined the bead counts in the central regions we will describe how the peripheral regions are handled.
+Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
 Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;

### 2020-01-16 6_2_printing_results.tex
influence of layers on back pressure (reviewer(3.12)
lil interpnuction (reviewer 2.5)

@@
 \subsection{Fabrication}
-In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system.
+In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system,
 we need a model which relates the required width to process parameters such as movement speed and filament extrusion speed.
@@
 \emph{direct drive}) or the filament fed from the back of the printer to the print head via a \emph{Bowden tube}.
-Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.
+Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle, changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.
 
@@
 Moreover, as the layer height is decreased the back pressure becomes larger compared to the internal pressure, which might cause the back pressure compensation method to demand prohibitively slow movement speeds.
+Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.
 %

### 2020-01-16 8_discussion.tex
lil typo (reviewer 1.1)

@@
 The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
-where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
+where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.
 

### 2020-01-16 6_2_printing_results.tex
explain unexplained math symbol (reviewer 2.5)

@@
 $f(w)$ is the filament outflow,
-$f_0$ is a constant reference flow
+$f_0$ is a constant reference flow,
+$w_0$ is a constant reference bead width
 and

### 2020-01-20 0_main.tex
fix double References header
new revise macros
new revision command
reenable temp commands in main
fix pdfedlink bug (from hyperref package)
change department name
add censoring (for reproduction in apendix of INRIA paper)

@@
 % My TK added packages and commands
+
+    \usepackage{censor}
+	\def\censorcolor{black}
+	\let\svcensorrule\censorrule
+	\renewcommand\censorrule[1]{%
+	\textcolor{\censorcolor}{\svcensorrule{#1}}}
+
+	\newcommand{\censoromit}[1]{}
+	%\newcommand{\censoromit}[1]{#1}
+    % \StopCensoring
 
@@
 
-%    \newcommand{\todo}[1]{\hl{#1}}
-%    
-%	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
-%	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
-%	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
-%	
-%	\newcommand{\old}[1]{\textcolor{gray}{#1}}
+    \newcommand{\todo}[1]{\hl{#1}}
+
+	\newcommand{\temp}[1]{\textcolor[rgb]{0, 0, 0.2}{#1}}
+	\newcommand{\tim}[1]{\temp{\todo{[Tim: #1]}}}
+	\newcommand{\jun}[1]{\temp{\todo{[Jun: #1]}}}
+
+	\newcommand{\old}[1]{\textcolor{gray}{#1}}
 	\usepackage[normalem]{ulem}
@@
 	% Version a) First arg red and striked out, second argument green
-	\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
+	%\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
+	%\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
-	%\newcommand{\revise}[2]{\textcolor{blue}{#2}}
+	\newcommand{\revise}[2]{{\color{blue}{#2}}}
 	% Version c) First arg ignored, second argument unchanged (for final draft)
 	%\newcommand{\revise}[2]{#2}
+	%\newcommand{\revise}[2]{#1}
 
@@
 
-\author[um,tud]{Tim Kuipers}
-\author[tud]{Eugeni L. Doubrovski}
-\author[tud]{Jun Wu\corref{cor1}}
-\ead{j.wu-1@tudelft.nl}
+\author[um,tud]{\censor{Tim Kuipers}}
+\author[tud]{\censor{Eugeni L. Doubrovski}}
+\author[tud]{\censor{Jun Wu}\corref{cor1}}
+\censoromit{\ead{j.wu-1@tudelft.nl}}
 \cortext[cor1]{Corresponding author}
-\author[cuhk]{Charlie Wang}
+\author[cuhk]{\censor{Charlie Wang}}
 % \ead{cwang@mae.cuhk.edu.hk}
-\address[um]{Ultimaker, Utrecht, The Netherlands}
-\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
-\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
+\address[um]{\censor{Ultimaker, Utrecht, The Netherlands}}
+\address[tud]{\censor{Department of Sustainable Design Engineering, Delft University of Technology, The Netherlands}}
+\address[cuhk]{\censor{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}}
 
@@
 
-\section*{References}
+%\section*{References}
+\interlinepenalty=100000 % prevents pdfendlink ended up accross pages error. see https://tex.stackexchange.com/a/449633/129190
 \bibliography{99_mybib}

### 2020-01-20 10_applications.tex
add censoring (for reproduction in apendix of INRIA paper)

@@
 \begin{subfigure}{\textwidth}\centering
+\censorbox{
 \includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
+}
 %\caption{Overview}\label{applications_overview}
@@
 \begin{subfigure}[t]{\figwidth}\centering
+\censorbox{
 \includegraphics[height=\figheight]{sources-applications-tud-logo.png}
-\caption{TUD}\label{applications_tud}
+}
+\caption{\censor{TUD}}\label{applications_tud}
 \end{subfigure}
 \begin{subfigure}[t]{\figwidth}\centering
+\censorbox{
 \includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
-\caption{UM}\label{applications_um}
+}
+\caption{\censor{UM}}\label{applications_um}
 \end{subfigure}

### 2020-01-20 1_intro.tex
lil edit because the paper in total is now only for FDM (reviewer 3.1)
add censoring (for reproduction in apendix of INRIA paper)

@@
 \item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme for FDM printing which
+\item A specific beading scheme \revise{for FDM printing}{} which
 \revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
@@
 
-\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
+\revise{}{\xblackout{The presented framework is patented by Ultimaker and open source available at} \censor{\url{github.com/Ultimaker/libArachne}}.}
 

### 2020-01-20 6_2_printing_results.tex
add censoring (for reproduction in apendix of INRIA paper)

@@
 % discussion of print results
-In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for the Ultimaker word mark, which negatively impacts the visual quality and the stiffness of the part.
+In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for \xblackout{the Ultimaker word mark}, which negatively impacts the visual quality and the stiffness of the part.
 Moreover, in the case of the spatially graded honeycomb there are several fully disconnected hexagons, which means the object falls apart when picked up.
@@
 Moreover, the absence of dark regions signifies that our proposed method is more robust against inaccuracies in the deposition system.
-However, both the centered and inward distributed approach introduce transitions to a different bead count in the word `Delft', which reduces the dimensional accuracy on the outline around those locations.
+However, both the centered and inward distributed approach introduce transitions to a different bead count in \xblackout{the word `Delft'}, which reduces the dimensional accuracy on the outline around those locations.
 
@@
 \begin{subfigure}{\figwidth}\centering
+\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-target}
+}
 \caption{Outlines}\label{print_outlines}
@@
 \begin{subfigure}{\figwidth}\centering
+\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
+}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
+\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
+}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
+\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
+}
 \caption{Inward distributed}\label{print_inward}

### 2020-01-21 6_validation.tex
remove old comment
new statistics, new figures, new colors

@@
 \centering
-\setlength{\figheight}{0.22\textwidth}
-\setlength{\figwidth}{0.31\textwidth}
+\setlength{\figheight}{0.25\textwidth}
+\setlength{\figwidth}{0.32\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-over-underfill.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
+\caption{\revise{}{Over- and underfill}}
+\label{over_underfill}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-print-time.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
+\caption{\revise{}{Print time}}
+\label{printtime}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-path-counts.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
+\caption{\revise{}{Path counts}}
+\label{pathcounts}
+\end{subfigure}
+
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-widths.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
+\caption{\revise{}{Extrusion widths}}
+\label{widthHistogram}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-angles.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
+\caption{\revise{}{Site angles}}
+\label{smoothness}
+\end{subfigure}
 \begin{subfigure}{\figwidth}\centering
@@
 \end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-widthHistogram.pdf}
-%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
-\caption{Extrusion widths}
-\label{widthHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-indexedwidths2.pdf}
-%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
-\caption{Extrusion width per index}
-\label{widthIndexedHistogram}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-overunderfill.pdf}
-%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
-\caption{Over- and underfill}
-\label{over_underfill}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-smoothness.pdf}
-%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
-\caption{Site angles}
-\label{smoothness}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-smoothnessNoTransition.pdf}
-%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
-\caption{Site angles (inward distributed)}
-\label{smoothnessNoTransition}
-\end{subfigure}
 
@@
 Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
-Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
+Note the use of a logarithmic scale \revise{}{in the bottom graphs }on the Y-axes and \revise{on some of}{for \subref{computime} on} the X-axes as well.
 }
+\label{statisticsfig}
 \end{figure*}
@@
 
-\iffalse
-\todo{Maybe test the following qualities:}
-\begin{itemize}
-\item visual consistency of flat top skin surface
-\item graphs of tensile tests on thin walled object
-\end{itemize}
-\fi
-
 %We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2020-01-22 0_main.tex
censoring options

@@
 
+	\newif\ifcensor
+	\newif\ifcolorrevise
+
+	\censortrue
+	\colorrevisefalse
+
     \usepackage{censor}
@@
     \newcommand{\censoromit}[1]{}
-	%\newcommand{\censoromit}[1]{#1}
-    % \StopCensoring
+	\newcommand{\censornotice}{}
+	\ifcensor
+		\renewcommand{\censornotice}{\\Anonymized 2020 (under revision)}
+	\else
+		\renewcommand{\censoromit}[1]{#1}
+		\StopCensoring
+    \fi
 
@@
 	% Revise macro (usage: \revise{old}{new})
+	\newcommand{\revise}[2]{#2}
 	% Version a) First arg red and striked out, second argument green
@@
 	% Version b) First arg ignored, second argument green
-	\newcommand{\revise}[2]{{\color{blue}{#2}}}
+	\ifcolorrevise
+	\renewcommand{\revise}[2]{{\color{blue}{#2}}}
+	\fi
 	% Version c) First arg ignored, second argument unchanged (for final draft)
@@
 
-\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}}
+\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice}
 

### 2020-01-22 6_validation.tex
use smae rmin and N=2 in statistics (reviewer 1.9, 1.2.2)

@@
 \subsection{Computational results}\label{sec_computational_results}
-}
+} % tew
 We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
@@
 and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a preferred bead width\revise{s}{} of $w^* = \SI{0.4}{\milli\meter}$.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

### 2020-01-22 6_validation.tex
explain statistics (extra change)
remove wrapfigure because that is already explained in the appendix (extra change)

@@
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
+\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
 
@@
 We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
-\begin{wrapfigure}{r}{.3\columnwidth}
-\centering
-\includegraphics[width=.25\columnwidth]{sources-validation-visualization-principle-rounded-excluded-single.pdf}
-\caption{
-Extrusion segments coverage.
-The hole at the end will be filled by the next extrusion segment.
-}
-\label{segment_visualization_simple}
-\end{wrapfigure}
-We construct the over- and underfill area by comparing the shapes covered by each extrusion move (\cref{segment_visualization_simple}) with each other and with the total shape of the boundary polygons.
+We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons.
 (For implementation details see Appendix~\ref{accuracy_calculation}.)
@@
 there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
-
+%
+%
 We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set

### 2020-01-22 6_validation.tex
don't compute graph for widths of outer bead (reviewer 1.9)

@@
 We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
+\revise{
 We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
 \cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
+}{
+We binned the tool paths into width bins at \SI{0.01}{\milli\meter} increments and determine the total tool path length pertaining to each bin.
+From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
+}
 We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
 These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
+\revise{
 We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
 The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
+}{}
 

### 2020-01-22 6_validation.tex
print time, path count statistics (reviewer 1.3)

@@
 
+\revise{
 \subsubsection{Smoothness of toolpaths}
@@
 \cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
+}{
+\subsubsection{Print time}
+The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the tool paths.
+In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
+We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
+While the idealized print time is predominantly determined by the total tool path length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
+Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
+We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
+Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
+Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
+For closed polygonal tool paths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
+We therefore report both on the open and closed path count in \cref{pathcounts}.
+}
 

### 2020-01-22 6_2_printing_results.tex
lil typo in revised text

@@
 and PLA filament.
-The printing order is determined greadily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
+The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.
 Because the machine instructions file format \emph{G-code} doesn't natively support adaptive width beads,

### 2020-01-22 6_validation.tex
new beading schemes comparison (reviewer 1.3, 2.6)

@@
 We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
-and report the average percentages in see \cref{over_underfill}.
-The inward distributed scheme has a calculated overfill of \SI{0.24}{\percent} and an underfill of \SI{0.17}{\percent}.
-This is lower compared to the uniform scheme, which results in \SI{1.2}{\percent} overfill and \SI{1.7}{\percent} underfill in the data set.
+and report the average percentages in \revise{see }{}\cref{over_underfill}.
+The inward distributed scheme has a calculated overfill of \revise{\SI{0.24}{\percent}}{\SI{0.30}{\percent}} and an underfill of \revise{\SI{0.17}{\percent}}{\SI{0.24}{\percent}}.
+This is lower compared to the uniform scheme, which results in \revise{\SI{1.2}{\percent}}{\SI{1.63}{\percent}} overfill and \revise{\SI{1.7}{\percent}}{\SI{1.62}{\percent}} underfill in the data set.
+\iffalse
+names ['naive', 'Constant', 'Center', 'Distributed', 'InwardDistributed']
+overfill [  1.63223926  22.21073295   0.37059604   0.45119725   0.30226112]
+outer_underfill [ 0.04664107  0.03232884  0.04357603  0.03494708  0.03475748]
+underfill [ 1.62009421  0.0712721   0.76886316  0.2440984   0.24461937]
+\fi
 

### 2020-01-22 8_discussion.tex
new beading schemes comparison (reviewer 1.3, 2.6)

@@
 \subsection{Comparison of beading schemes}
-We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average \revise{approximately}{} \revise{\SI{1}{\percent}}{\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
 To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.
@@
 Note that most overfill areas occur near regions of alternating bead width. 
+\revise{}{While the scheme results in short tool paths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
+See \cref{statisticsfig}.}
 For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
+\revise{}{See top right of \cref{TEST_Constant_accuracy}.}
 
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
 the variation is within a factor of $3.6$.}
+\revise{}{However, it does produce some narrow underfill regions.}
+\revise{
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
+}{
+Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of tool path angles below \SI{45}{\degree}.
+See \cref{statisticsfig}.
+}
 
 However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
-the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
+the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
+\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+\SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
 \revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
 the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
-We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
 %This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.
-However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.
-Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
-Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.
+\revise{It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.}
+{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline acuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
+%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
+%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
+\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{} % _
+Furthermore, \revise{from \cref{smoothness} }{}we find that compared to evenly distributed, the inward distributed scheme produces \revise{smoother toolpaths overall}{less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
+Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes\revise{}{, while incurring little to no extra print time}.
 

### 2020-01-22 6_2_printing_results.tex
move print results to before statistics (reviewer 1.3)

@@
 
-\subsubsection{Print results}
+\subsubsection{Print results}\label{print_results_section}
 Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use

### 2020-01-22 0_reviewer_response.tex
more reviewers response

@@
-\documentclass[5p,twocolumn,10pt,times]{elsarticle}
+\documentclass[5p,10pt,times]{elsarticle}
 \usepackage{amsmath}
@@
 420cf6886a8e248aec4aafc04d13abc693da8dd0 % fix for naive over-/underfill area formula
+86cd8dd7f2112696f650736a81b24b63af739639 % lil typo
 }
@@
 The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
-where $w_\text{min}$ is a configarable parameter when using the widening meta-scheme.
+where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.
 }
@@
 \paper{3.3 Method, Significance measure}{
-This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
+This corresponds to overfill areas and underfill areas the size of \\ \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
 }
@@
 }
-\todo{
-Redo the tests with homogeneous $r_\text{min}$
-
-note value of $r_\text{min}$ in paper
-}
 \commits{
@@
 8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to widening + shell fig
+ca322806c80ddc82c6f0c01d9ea5096b37ffcf8e % use smae rmin and N=2 in statistics
 }
@@
 }
+\paper{5.2 Computational results}
+{
+Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
+and by our framework using four beading schemes, i.e.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
+}
 
@@
 We now included a description of the path order algorithm, which is naive and greedy.
-Because this algorithm is suboptimal, we separate the printing time into extrusion time and travel time.
-These (new) results shed light on how much more travel time is required relatively.
 Although an optimal path order algorithm might influence the travel time, such an algorithm is slow and not generally used in the industry.
 The software package Cura currently employs a similarly greedy algorithm.
+%Some preliminary (unpublished) tests have indicated that Cura's path planning deviates from the optimal paths by only \SI{1}{\percent} of the total print time on average.
+
+We also include statistics on print time and path counts.
+These new statistics are now reflected upon in the comparison of the beading schemes.
+
+Because the print time depends on the actual printing setup we have moved the section on print results to before the statistics section.
 }
@@
 d375878a8a6d01c53436aeb9c473dbedd8f3edcf % path order algorithm
-}
-\todo{
-Show results on printing time
+e2c940f2362556ae8d017cff63c81b4bbcb77286 % print time, path count statistics
+7f567012b409445fc120968e995f861cab56e776 % new beading schemes comparison
+bf403fe797193e40b004c2cae806935f699271e5 % move print results to before statistics 
+}
+\paper{5.1.2 Print results}{\revise{}{The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.}}
+\paper{5.2.3 Print time}
+{
+\revise{
+\subsubsection{Smoothness of toolpaths}
+In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
+We therefore measured the angle between consecutive extrusion segments generated by each scheme
+and report on the occurrence of each angle in \cref{smoothness}.
+All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
+We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
+The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
+We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
+\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
+}{
+\subsubsection{Print time}
+The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the tool paths.
+In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
+We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
+While the idealized print time is predominantly determined by the total tool path length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
+Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
+We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
+Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
+Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
+For closed polygonal tool paths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
+We therefore report both on the open and closed path count in \cref{pathcounts}.
+}
+}
+\paper{5.3 Comparison of beading schemes}
+{
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average \revise{approximately}{} \revise{\SI{1}{\percent}}{\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
+To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.
+
+The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
+Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
+Note that most overfill areas occur near regions of alternating bead width. 
+\revise{}{While the scheme results in short tool paths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
+See \cref{statisticsfig}.}
+For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
+Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
+\revise{}{See top right of \cref{TEST_Constant_accuracy}.}
+
+In \cref{TEST_Center_accuracy} we can see that
+the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the variation is within a factor of $3.6$.}
+\revise{}{However, it does produce some narrow underfill regions.}
+\revise{
+According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
+}{
+Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of tool path angles below \SI{45}{\degree}.
+See \cref{statisticsfig}.
+}
+
+However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
+the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
+\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+\SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
+the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
+%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
+
+\revise{It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.}
+{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline acuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
+%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
+%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
+\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{} % _
+Furthermore, \revise{from \cref{smoothness} }{}we find that compared to evenly distributed, the inward distributed scheme produces \revise{smoother toolpaths overall}{less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
+Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes\revise{}{, while incurring little to no extra print time}.
 }
@@
 The difference between the inward distributed beading scheme and the method by Jin et al 2017 JMS is already shown in Fig 1.b and c. 
-It is also shown in Fig. 16 c and e.
+It is also shown in Fig. 18 c and e.
 In order to clearly address the difference early on we mention the difference in the description of Jin in the introduction.
@@
 \Ans{
-We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images.
+We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig 18d and 18e).
+The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths along the outer paths can be omitted.
 }
@@
 87b1b779b759a9ad115f3ea61243568bfa2e0cb6 % lil change in Fig 20 caption
+ca322806c80ddc82c6f0c01d9ea5096b37ffcf8e % use smae rmin and N=2 in statistics
+b4d03f0d8ea92ac9800794e154dc5b53e4448cab % don't compute graph for widths of outer bead
 }
@@
 }
-\paper{Fig. 16}
+\paper{Fig. 18}
 {
@@
 }
-\paper{Caption of Fig. 16}
+\paper{Caption of Fig. 18}
 {
@@
 Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
+}
+\todo{redo all experiments with N=2}
+\paper{5.2 Computational results}
+{
+Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
+and by our framework using four beading schemes, i.e.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
+}
+\paper{5.2.2 Uniformity}
+{
+\revise{
+We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
+The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
+}{}
 }
@@
 \commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}
-\paper{Fig. 17b}{
+\paper{Fig. 19b}{
 \todo{Figure now has the uniform curve}
@@
 5356492b5a9a690228ffdb6a6a26cf10d099a7d4 % make clear that a skeleton is an undefined term (reviewer 2.1)
+74227189eba03d13e18249f3235680691c6ebea9 % clarify skeleton more
 }
 \paper{3.1 Method overview}{
-Our method starts with computing \revise{the}{a type of} skeleton \revise{}{(a graph representing the topology) }of the input polygon based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
+Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
+Our skeleton is} based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}
 }
@@
 \Ans{
-The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 17b.
+The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 19d.
 
@@
 125162ad9878c0fb5a054f1bab34aa7b1353b86c % better var width test figure
+34e923fbf4c2ad45bf2dd0a03ef70d4a714b4b0b % lil comma (x2)
+1b7bb61648b97b8084ca8817aa457bde2c91e1b3 % lil: explain unexplained math symbol 
 }
@@
 64eb2f2c1cbb28258a984b5f84ea6e3a039ee1f0
+1935689874235a6c1d5b8f0fed725afa53804935 % don't introduce only one strategy for FDM only
 }
@@
 A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}
+}
+\paper{Introduction, bulletlist}{
+A specific beading scheme \revise{for FDM printing}{} which [\dots]
 }
@@
 1ea800d0b4f68963befff90e535d5c82748df5e2 % big rework
+1c1159c482047f9aaa110e9086f800977adde268 % lil rephrase
 }
@@
 {
-\revise{}{A too large $\alpha_\text{max}$ leaves a lot of under-/overfill, while a too small value will introduce toolpaths to fill in negligibly small underfills.
-We therefore set $\alpha_\text{max} = \SI{135}{\degree}$.}
+\revise{}{A too large $\alpha_\text{max}$ may leave a lot of under-/overfill, while a too small value may introduce toolpaths to fill in negligibly small underfills.}
 }
@@
 Added patent notice and url to open source implementation.
-\commits{ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a}
+\commits{
+ff3c09037f05eba5028cb51bf8cd6c0bb77a0b0a
+}
 \paper{Intro}{
 \revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
+}
+
+Remove reference to the concept of `periphery' seeing as it was not really used.
+\commits{
+74227189eba03d13e18249f3235680691c6ebea9 % dont introduce
+10bc58dc50f314e2d86f28ae6d8532fee3d20893 % don't use
+a5c0d134c106876ae0edcb201eb270b66c11462f % typo near these^ commits
+}
+\paper{3.3 Center classification}{
+\revise{The remainder is called peripheral.}{}
+}
+\paper{3.5 Beading}{
+Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
 }
@@
 9d9f02edc43689c0970a74118e44a196cc11c729 % typos
+87bed1e663ea831d8f52b0ccf4ef5eebaab32ade % typo
 }
@@
 
+We fixed a mistake when performing the statistical analysis.
+In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme.
+The extrusion width statistics figure (19d) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
+
+Explain why and how statistics are gathered over the whole data set:
+\commits{17135b010f5ac51fda77357136a19f67a80dbc33}
+\paper{5.2 Computational results}
+{
+\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
+}
+
+Remove wrapfigure explaining the area covered by a single extrusion move (in section 5.2.1 `Accuracy'), since that is already explained in the appendix.
+\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
+
+Change width histogram calculation so that we use accurate statistics instead of sampling the width along the path:
+\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
+\paper{5.2.2 Uniformity}
+{
+\revise{
+We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
+\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
+}{
+We binned the tool paths into width bins at \SI{0.01}{\milli\meter} increments and determine the total tool path length pertaining to each bin.
+From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
+}
+}
+
 \bibliography{99_mybib}

### 2020-01-23 0_reviewer_response.tex
change formatting of response letter
fix figures in response letter

@@
-\documentclass[5p,10pt,times]{elsarticle}
+\documentclass[3p,10pt,times]{elsarticle}
 \usepackage{amsmath}
@@
 	\newcommand{\response}[1]{{#1}}
-\newcommand\paper[2]{\par changes to \emph{#1} --- ``#2'' }
+
+\newcommand\paper[2]{
+\par
+changes to \emph{#1} --- ``#2'' 
+}
 %\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
@@
 \newcommand\Summary[1]{
-   \noindent\emph{Summary.} {\bf#1}\par}
+   \noindent\emph{\qq{Summary}{#1}}\par}
+
+\usepackage{tcolorbox}
+
+\newcommand\qq[2]{
+\begin{tcolorbox}[]
+  #1 \indent {\bf #2}
+\end{tcolorbox}
+}
 
@@
    \noindent
-   \thequestion. {\bf#1}\par}
+   {\qq{\thequestion.}{#1}}\par}
 
@@
    \noindent
-   \thesubquestion. {\bf#1}\par}
+   {\qq{\thesubquestion.}{#1}}\par}
 
@@
 \newcommand\Ans[2][]{%
+	\begin{tcolorbox}[colback=white, arc=0mm]
     \leavevmode\par\noindent
    {%\leftskip37pt
-    {\it Response:} \textbf{#1}#2\par}}
+    %{\it Response:} 
+    \textbf{#1}#2\medskip\par}
+    \end{tcolorbox}
+    }
 
@@
 	\renewcommand\floatpagefraction{.8}
+
+	\newlength{\mycolumnwidth}
+\setlength{\mycolumnwidth}{.5\columnwidth}
 
@@
 \begin{figure}\centering
-\setlength{\figwidth}{.9\columnwidth}
-\setlength{\figwidthTwo}{.05\columnwidth}
+\setlength{\figwidth}{.9\mycolumnwidth}
+\setlength{\figwidthTwo}{.05\mycolumnwidth}
 \begin{subfigure}{\figwidth}\centering
@@
 \centering
-\setlength{\figwidth}{.35\columnwidth}
-\setlength{\figwidthTwo}{.6\columnwidth}
+\setlength{\figwidth}{.35\mycolumnwidth}
+\setlength{\figwidthTwo}{.6\mycolumnwidth}
 \begin{minipage}[b]{\figwidthTwo} \centering
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
+\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Distributed-feature-size.png}
 \caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
@@
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
+\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Center-widening.png}
 \caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
@@
 \begin{figure} \centering
-\setlength{\figwidth}{.45\columnwidth}
+\setlength{\figwidth}{.45\mycolumnwidth}
 \begin{subfigure}[b]{\figwidth} \centering
@@
 \begin{figure}\centering
-\includegraphics[width=.75\columnwidth]{sources-method-legend2.pdf}
+\includegraphics[width=.75\mycolumnwidth]{sources-method-legend2.pdf}
 \caption{Illustrative explanation of terms and color coding that are consistently used in this paper.}
@@
 \centering
-\setlength{\figwidth}{.8\columnwidth}
-\setlength{\figheight}{.3\columnwidth}
+\setlength{\figwidth}{.8\mycolumnwidth}
+\setlength{\figheight}{.3\mycolumnwidth}
 \begin{minipage}[b]{0.8\linewidth}
@@
 \end{minipage}
-\begin{subfigure}[t]{.1\columnwidth}\centering
+\begin{subfigure}[t]{.1\mycolumnwidth}\centering
 \includegraphics[height=\figheight]{sources-validation-widths-legend-small.pdf}
@@
 See Figure~\ref{response_parabola_discretization}.
+}
+\commits{
+64029a6ef57cf8044c521075ebc70cddfb52156b % mention 0.01mm in paper
+}
+\paper{3.2 Union of cones, Skeletal trapezoidation}
+{
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
+}
 
 \begin{figure}\centering
-\includegraphics[width=.3\linewidth]{response_parabola_discretization}
+\includegraphics[width=.3\mycolumnwidth]{response_parabola_discretization}
 \caption{Parabola discretization.
@@
 \end{figure}
-}
-\commits{
-64029a6ef57cf8044c521075ebc70cddfb52156b % mention 0.01mm in paper
-}
-\paper{3.2 Union of cones, Skeletal trapezoidation}
-{
-The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
-}
 
@@
 \centering
-\begin{subfigure}{\columnwidth}\centering
-\setlength{\figwidth}{\columnwidth}
+\begin{subfigure}{\mycolumnwidth}\centering
+\setlength{\figwidth}{\mycolumnwidth}
 \includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
@@
 \end{subfigure}
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
+\setlength{\figheight}{.38\mycolumnwidth}
+\setlength{\figheightTwo}{.47\mycolumnwidth}
+\setlength{\figwidth}{0.32\mycolumnwidth}
 \begin{subfigure}{\figwidth}\centering
@@
 \centering
-\setlength{\figwidth}{0.32\columnwidth}
-\setlength{\figheight}{0.5\columnwidth}
+\setlength{\figwidth}{0.32\mycolumnwidth}
+\setlength{\figheight}{0.5\mycolumnwidth}
 \begin{subfigure}[t]{\figwidth}\centering
@@
 \centering
-\setlength{\figwidth}{\columnwidth}
+\setlength{\figwidth}{\mycolumnwidth}
 \begin{subfigure}{\figwidth}\centering
@@
 \begin{enumerate}
-	\begin{minipage}{\columnwidth}
+	\begin{minipage}{\mycolumnwidth}
 	\setlength\intextsep{0pt}
-	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
-	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
+	\begin{wrapfigure}[4]{o}{.4\mycolumnwidth} %\centering
+	\includegraphics[width=.3\mycolumnwidth,frame]{sources-method-transition-length-limit.pdf}
 	%\caption{

### 2020-01-23 6_validation.tex
move print results to before statistics (reviewer 1.3)
fix figures in response letter

@@
 \section{Results and discussion}
+
+\input{6_2_printing_results}
 
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
-\includegraphics[width=\columnwidth]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
 \caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}

### 2020-01-23 0_reviewer_response.tex
add results figures to resposne letter

@@
 }
+
+\begin{figure*}
+\centering
+\setlength{\figwidth}{0.19\textwidth}
+\setlength{\figheight}{0.283\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
+\caption{Uniform}\label{TEST_naive_accuracy}
+\end{subfigure}
+%\begin{subfigure}{\figwidth}\centering
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
+%\caption{Single}\label{TEST_SingleBead_accuracy}
+%\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
+\caption{Constant}\label{TEST_Constant_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
+\caption{Centered}\label{TEST_Center_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
+\caption{Distributed}\label{TEST_Distributed_accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
+\caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
+\end{subfigure}
+\begin{subfigure}{.04\mycolumnwidth}\centering
+\vspace{4.7cm}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
+\end{subfigure}
+\caption{
+Visualization of the overfills and underfills (top) and the widths (bottom) for various beading schemes.
+Extrusion beads in gray tones,
+overfill in orange,
+underfill in azure,
+narrow beads in blue
+and wide beads in red.
+\revise{New shape contains pointy wedge to see impact on minimal feature size}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
+}
+\label{visualized_accuracy}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\setlength{\figheight}{0.25\textwidth}
+\setlength{\figwidth}{0.32\textwidth}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-over-underfill.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
+\caption{\revise{}{Over- and underfill}}
+\label{over_underfill}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-print-time.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
+\caption{\revise{}{Print time}}
+\label{printtime}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-path-counts.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
+\caption{\revise{}{Path counts}}
+\label{pathcounts}
+\end{subfigure}
+
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-widths.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
+\caption{\revise{}{Extrusion widths}}
+\label{widthHistogram}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-angles.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
+\caption{\revise{}{Site angles}}
+\label{smoothness}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
+%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
+\caption{Computation time}
+\label{computime}
+\end{subfigure}
+
+\caption{
+Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
+Note the use of a logarithmic scale \revise{}{in the bottom graphs }on the Y-axes and \revise{on some of}{for \subref{computime} on} the X-axes as well.
+}
+\label{statisticsfig}
+\end{figure*}
 

### 2020-01-23 0_reviewer_response.tex
explain travel time response letter

@@
 The software package Cura currently employs a similarly greedy algorithm.
-%Some preliminary (unpublished) tests have indicated that Cura's path planning deviates from the optimal paths by only \SI{1}{\percent} of the total print time on average.
-
-We also include statistics on print time and path counts.
-These new statistics are now reflected upon in the comparison of the beading schemes.
-
-Because the print time depends on the actual printing setup we have moved the section on print results to before the statistics section.
+Travel times are approximately \SI{2}{\percent} of the total print time in our current setup, so the effect of improper path planning is negligible compared to the differences in extrusion time.
+
+We now include statistics on extrusion time, travel time and path counts.
+These new statistics are now also reflected upon in the comparison of the beading schemes.
+
+Because the extrusion time depends on the actual printing setup we have moved the section on print results to before the statistics section.
 }
@@
 bf403fe797193e40b004c2cae806935f699271e5 % move print results to before statistics 
+b106dd1e0067114756bf96a7dc10458202380f2e % new print time pdf graph
 }

### 2020-01-25 0_reviewer_response.tex
strikethrough revised text

@@
 	\usepackage[normalem]{ulem}
-	\newcommand{\stkout}[1]{\ifmmode\text{\sout{\ensuremath{#1}}}\else\sout{#1}\fi}
+	\newcommand{\stkout}[1]{\ifmmode\text{\st{\ensuremath{#1}}}\else\sout{#1}\fi}
+
+ \usetikzlibrary{patterns}
+\usepackage[framemethod=tikz]{mdframed}
+\mdfdefinestyle{strikeoutbox}{%
+  linecolor=red,%
+  apptotikzsetting={\tikzset{mdfbackground/.append style={%
+        draw=red!10,pattern=horizontal lines,pattern color=red}
+        % ,color=red!20  >makes whole box red
+      }},%
+  innertopmargin=\topskip,
+}
+
+\renewcommand\SI[2]{\ensuremath{#1#2}}
+\newcommand\percent{\%}
+\newcommand\milli{\text{m}}
+\newcommand\meter{\text{m}}
+\newcommand\micro{\mu}
+\newcommand\second{\text{s}}
+\newcommand\per{/}
+\newcommand\squared{^2}
+\newcommand\cubed{^3}
+\renewcommand\si[1]{\ensuremath{#1}}
+
+\let\oldCref\Cref
+\renewcommand{\Cref}[1]{\mbox{\oldCref{#1}}}
+
+\let\oldcref\cref
+\renewcommand{\cref}[1]{\mbox{\oldcref{#1}}}
 
@@
 	% Version a) First arg red and striked out, second argument green
-	%\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}\noindent{\color{blue}{#2}}}
+	\newcommand{\revise}[2]{\noindent{\color{red}{\stkout{#1}}}{\color{blue}{#2}}}
+	\newcommand{\revisepar}[2]{
+	\if\relax\detokenize{#1}\relax
+	  {\color{blue}{#2}} % no paragraph to be left out
+	\else
+	{
+	  \noindent{\begin{mdframed}[style=strikeoutbox]
+	  %\color{red}{#1}
+	  #1
+	  \end{mdframed}
+	  }{\color{blue}{#2}}}
+	\fi}
+
 	%\newcommand{\revise}[2]{{\textcolor{red}{#1}}{\textcolor{blue}{#2}}}
-	\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
+	%\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
 	% Version b) First arg ignored, second argument green
@@
 }
-\paper{Intro}{
+\paper{Intro}
+{
 In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
@@
 We also take care not to leave gaps which are too small to be filled using the direction-parallel strategy:
-
+}
+
+\revise{}{
 \begin{align*}
@@
 \end{align*}
-
+}
+
+\revise{}{
 These meta-schemes introduce non-linearities in the quantization function.
@@
 Combining all meta-schemes functionality we can generate results such as depicted in \cref{shell}.
-
+}
 \begin{figure}
@@
 }
-}
 \paper{5.2 Computational results}
@@
 {
-\revise{
+\revisepar{
 \subsubsection{Smoothness of toolpaths}
@@
 }
-\paper{5.2 Printing results}{
-
-\revise{
+\paper{5.2 Printing results}
+{
+\revisepar{
 Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
@@
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
-
+}{}
+
+\revisepar{
 The prints are shown in \cref{prints_old}.
@@
 The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
+}{}
 
@@
 \end{figure}
-}{
+
+\revisepar{}{
 \subsection{Fabrication}
@@
 Because Bowden style 3D printing systems have the filament feeder relatively far away from the nozzle, changing the internal pressure in the system requires a large amount of filament movement, which requires a prohibitive amount of time.
-
+}
+
+\revisepar{}{
 \subsubsection{Back pressure compensation}
@@
 We conjecture that the amount of back pressure is monotonically related to the requested line width and compensate for the back pressure using a simple linear model:
-
+}
+
+\revisepar{}{
 \begin{align}
@@
 $k$ is the amount of back pressure compensation.
-
+}
+
+\revisepar{}{
 % adapted from 5.5 Discussion on implications
@@
 Conversely such a setup might benefit from some form of back pressure compensation as well.
-
+}
+
+\revisepar{}{
 \subsubsection{Print results}
@@
 The results can be viewed in \cref{prints}.
+}
 
@@
 
+\revisepar{}{
 % discussion of print results
@@
 However, both the centered and inward distributed approach introduce transitions to a different bead count in the word `Delft', which reduces the dimensional accuracy on the outline around those locations.
-
+}
+
+\revisepar{}{
 \begin{figure}
@@
 }
-\revise{
+
+\revisepar{
 \subsection{Discussion on implications}
@@
 We expect that developments in printing hardware and firmware will address these challenges in the future.
-
+}{}
+
+\revisepar{
 Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
@@
 {
-\revise{
+\revisepar{
 \begin{definition}\label{beading_scheme_definition}
@@
 
-\revise{
+\revisepar{
 The following restrictions hold:
@@
 
-\revise{}{
+\revisepar{}{
 For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$.
@@
 
-\revise{
+\revisepar{
 A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
@@
 
-\revise{
+\revisepar{
 The toolpath locations $L$ ensure 
@@
 {
-\revise{}{
+\revisepar{}{
 The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;

### 2020-01-25 0_reviewer_response.tex
make response figures more like paper figures
mention gMAT shape change in reviewer 1.2.2 instead of 1.9
mention figure changes differently (without \todo)

@@
 	\newlength{\mycolumnwidth}
-\setlength{\mycolumnwidth}{.5\columnwidth}
+\setlength{\mycolumnwidth}{.73\columnwidth}
+%\captionsetup{width=\mycolumnwidth}
 
@@
 This minimum feature size is now used in the new computational test results and in Fig. 1.
+
+We have also changed the example shape of Fig. 16 (Now Fig. 17, reproduced here \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig. 1.
 }
@@
 {
+[See \cref{intro_wedge}.]
+}
 \begin{figure}\centering
@@
 \end{figure}
-\todo{See \cref{intro_wedge}.}
-}
+
 \paper{4. Beading schemes, end of section}{
@@
 \paper{Intro}{
-\todo{See caption of \cref{intro_wedge}.}
+[See caption of \cref{intro_wedge}.]
 }
@@
 {
-\todo{See \cref{legend}.}
+[See \cref{legend}.]
+}
 \begin{figure}\centering
@@
 \end{figure}
-}
 
@@
 {
-\todo{See \cref{distributed_comparison}.}
+[See \cref{distributed_comparison}.]
+}
 \begin{figure}
@@
 \end{figure}
-}
-\paper{Fig. 18}
-{
-\todo{New shape contains pointy wedge to see impact on minimal feature size.}
-}
 \paper{Caption of Fig. 18}
@@
 }
-\todo{redo all experiments with N=2}
 \paper{5.2 Computational results}
@@
 \commits{e5f3649455c73c8146e8d07cce13bc1e89d84cbb}
-\paper{Fig. 19b}{
-\todo{Figure now has the uniform curve}
-}
 

### 2020-01-25 0_reviewer_response.tex
Don't mention elber1991
add example revised paragraph

@@
 \revise{outdated text in manuscript}{new text in manuscript}
+\revisepar{
+Old paragraph which might contain various i.e. multiple lines, which makes the LaTeX macro for strikout text fail, because the soul package doesn't work well enough for our purposes.
+}
+{Revised paragraph is better.}
 }
@@
 The method section, however, doesn't go into variable offset schemes because offset schemes apply offset values given at the outline, while our framework principally relates the outline and the skeleton.
-}
-\todo{
-elber1991error
 }

### 2020-01-25 1_intro.tex
Updates from Overleaf

--- 2019-12-18 1_intro.tex
@@
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
-\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
+\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicated in red and blue, respectively.
 \subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.

### 2020-01-25 0_reviewer_response.tex
spell check

@@
 \paper{Conclusion}{
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{,
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
 we introduced beading schemes which improve on the state of the art
@@
 \caption{
-Toolpaths using the widening and shel meta-schemes.
+Toolpaths using the widening and shell meta-schemes.
 \subref{min_feature_size} and~\subref{widening} show widening.
@@
 \subsubsection{Print time}
-The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the tool paths.
+The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
 In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
 We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
-While the idealized print time is predominantly determined by the total tool path length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
+While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
 Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
@@
 Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
-For closed polygonal tool paths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
+For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
 We therefore report both on the open and closed path count in \cref{pathcounts}.
@@
 Note that most overfill areas occur near regions of alternating bead width. 
-\revise{}{While the scheme results in short tool paths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
+\revise{}{While the scheme results in short toolpaths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
 See \cref{statisticsfig}.}
@@
 }{
-Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of tool path angles below \SI{45}{\degree}.
+Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of toolpath angles below \SI{45}{\degree}.
 See \cref{statisticsfig}.
@@
 \begin{definition}\label{beading_scheme_definition}
-A beading scheme is defined by the quatization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
+A beading scheme is defined by the quantization operator $q$ and the beading operator $B$: $\{q(d), B(n ,r)\}$.
 The beading function $B(n,r)$ consists of $\left( W(n,r), L(n,r) \right)$,
@@
 }{
-We binned the tool paths into width bins at \SI{0.01}{\milli\meter} increments and determine the total tool path length pertaining to each bin.
+We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
 From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.

### 2020-01-25 12_conclusions_future_work.tex
spell check

@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{,
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{,
 we introduced beading schemes which improve on the state of the art
-and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
+and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
 }

### 2020-01-25 1_intro.tex
spell check

--- 2020-01-20 1_intro.tex
@@
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
-\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicatd in red and blue, respectively.
+\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
 \subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.

### 2020-01-25 4_method.tex
fix typo
spell check

@@
 \paragraph{Medial axis transform}
-The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
+The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyze} a shape.
 It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central, we mark parts of the ST as being central.
+In order to prevent over- and underfill \revise{to occur}{from occurring} in central\revise{}{ regions}, we mark parts of the ST as being central.
 \revise{The remainder is called peripheral.}{}

### 2020-01-25 5_generalization.tex
lil typo fixes
spell check

@@
 We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
-\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simply beading scheme given by} \cref{formula_uniform}.
+\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.
 

### 2020-01-25 8_discussion.tex
move print results to before statistics (reviewer 1.3)
spell check

@@
 \revise{It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.}
-{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline acuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
+{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline accuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
 %{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
@@
 
-\input{6_2_printing_results}
-
 \input{10_applications}

### 2020-01-25 0_reviewer_response.tex
lil respponse commit

@@
 87bed1e663ea831d8f52b0ccf4ef5eebaab32ade % typo
+2e21687731d95a9a1315206531f0474fb924c6eb % spell check
 }

### 2020-01-25 0_main.tex
undo censoring in master
remove \revise macro everywhere

@@
 
-	\censortrue
-	\colorrevisefalse
+	\censorfalse
+	\colorrevisetrue
 
@@
 
+\iffalse
+
 	% Revise macro (usage: \revise{old}{new})
@@
 	%\newcommand{\revise}[2]{#1}
+
+\fi
 
@@
 
-\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice}
+\title{A framework for adaptive width control of dense contour-parallel toolpaths in {fused deposition modeling}\censornotice}
 
@@
 3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply.
-\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
+
 {High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
-\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
+{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially {detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
-Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+Furthermore, we propose a novel scheme for FDM printing which {reduces} extreme bead width deviation, {while limiting} the number of altered toolpaths.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 {layer outlines}.
+We {statistically }validate the effectiveness of our framework and this novel scheme on a data set of {representative 3D models, }%sgd
+{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
 \end{abstract}
@@
 
-%\section*{References}
+\section*{References}
 \interlinepenalty=100000 % prevents pdfendlink ended up accross pages error. see https://tex.stackexchange.com/a/449633/129190

### 2020-01-25 10_applications.tex
remove \revise macro everywhere

@@
 \caption{
-Visualization of the widths for the output toolpaths of the inward distributed beading scheme \revise{}{($N=3$) }applied to various example application objects.
+Visualization of the widths for the output toolpaths of the inward distributed beading scheme {($N=3$) }applied to various example application objects.
 From left to right and top to bottom: a house, a case for electronics, a statue, two common logos, a gear, a topologically optimized bone structure, a tilted homogeneous gyroid structure and a heterogeneous thickness hexagonal grid.

### 2020-01-25 12_conclusions_future_work.tex
remove \revise macro everywhere

--- 2019-12-13 12_conclusions_future_work.tex
@@
 \section{Conclusion and future work}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfilland overfill areas\revise{.}{
-we introduced beading schemes which improve on the state-of-the-art
-and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas{,
+we introduced beading schemes which improve on the state of the art
+and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
 }
@@
 
-\revise{We presented the}{The} inward distributed beading scheme
-\revise{It}{} reduces the amount of beads with a width deviating extremely from the preferred bead width \revise{}{by changing the width of several beads near the center instead of only the center-most bead}.
-\revise{, and thus it is}{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
+{Compared to the state of the art,} the inward distributed beading scheme
+reduces the amount of beads with a width deviating extremely from the preferred bead width {by changing the width of several beads near the center instead of only the center-most bead}.
+{It is therefore} expected to limit the impact of varying the bead width in terms of production accuracy and homogeneity of material properties,
 which in turn is helpful to efficiently simulate an FDM manufactured part.
-\revise{
-Furthermore, by distributing the deviation in bead width over several beads near the center of the shape, the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy of the shape of the outline contour is affected less by inaccuracies in the mechanical control system which realizes adaptive bead width.
-}{}
 
@@
 Meanwhile it leaves most of the toolpaths the same as the uniform width technique in large features, meaning that existing studies which relate process parameters with mechanical properties of the print are still applicable.
-\revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
-\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
+{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
+{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
+
+\medskip
+{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
 
@@
 Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
-An accurate model of manufacturability, \revise{}{which relates }print speed\revise{, }{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
-\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
+An accurate model of manufacturability, {which relates }print speed, {layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
+{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
 % If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.

### 2020-01-25 1_intro.tex
remove \revise macro everywhere

--- 2020-01-25 1_intro.tex
@@
 Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
-\revise{
-Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
-}{
+{
 Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
@@
 One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
-\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is \revise{sometimes}{} far greater\revise{}{ for some parts}~\cite{Ding2016a,Xiong2019}.
+\citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is  far greater{ for some parts}~\cite{Ding2016a,Xiong2019}.
 However, the range of widths manufacturable by FDM systems is limited.
@@
 
-The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+The current {state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads {within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
 % (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
@@
 Moreover, reducing the variation in width is beneficial for limiting the variation in mechanical properties of the resulting product, meaning it conforms better to a simulation which employs a homogeneity assumption.
-\revise{
-Therefore, a narrower range of widths is desirable.
-}
+
 {We therefore reduce the bead width range by distributing the workload from the centermost bead over neighboring beads.}
@@
 In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
-\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
+{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
 We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
-\revise{
-For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
-}{Furthermore we present an approach to accurately realize adaptive bead width.
+{Furthermore we present an approach to accurately realize adaptive bead width.
 }
@@
 \caption{
-Illustration of different toolpath\revise{}{s} for a \revise{wedge }{}shape \revise{}{showcasing a range of shape radii }\revise{}{(black)}.
-\revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
+Illustration of different toolpath{s} for a shape {showcasing a range of shape radii }{(black)}.
+{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
 \subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
-\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are indicated in red and blue, respectively.
-\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
+\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are {indicated} in red and blue, respectively.
+\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with {less extreme widths}.
 }
@@
 \begin{itemize}
-\item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme for FDM printing which
-\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
-\revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
-\revise{}{
+\item A geometric framework {allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
+\item A specific beading scheme  which
+{furthermore} reduces the amount of {variation} in the extrusion widths compared to {the state of the art to be below a factor of 2.}
+
+{
 \item A back pressure compensation approach to accurately realize adaptive bead width on Bowden style hardware systems.
@@
 
-\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
-
 %This work is patent pending, but the source code is available open source.

### 2020-01-25 2_related_work.tex
lil typo
remove \revise macro everywhere

--- 2019-08-31 2_related_work.tex
@@
 Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
-Third, the extruded path should cover a the region of the contour without gaps.
+Third, the extruded path should cover the region of the contour without gaps.
 Such underfill negatively influences the mechanical performance of the parts.
@@
 % the idea, and (some of) the most related work
-Reducing under- and over-filling can be accurately achieved by making use over adaptive depisition width.
+Reducing under- and over-filling can be accurately achieved by making use over adaptive {deposition} width.
 Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.
@@
 \citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
-The resulting variation of width in the center is still up to a factor of $2$ (see \cref{intro_wedge_centered}).
-In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme deviations in width (see \cref{intro_wedge_distributed}).
+The resulting variation of width in the center is still up to a factor of {$3.6$} (see \cref{intro_wedge_centered}).
+In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme {variation} in width (see \cref{intro_wedge_distributed}).
 

### 2020-01-25 4_method.tex
remove \revise macro everywhere

--- 2020-01-16 4_method.tex
@@
 
-Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
+Our method starts with computing {a graph which represents the topology of the input polygon: its \emph{skeleton}. 
 Our skeleton is} based on the medial axis transform (MAT), a strategy that has been commonly used for generating contour-parallel toolpaths~\cite{eiamsa2003toward}.
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
+Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of {horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).
 
@@
 The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
+{%afs
+The video in the supplementary material provides an example animation of this approach.
+}
 
@@
 \paragraph{Medial axis transform}
-The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
+The medial axis is a {representation commonly used to analyze} a shape.
 It is defined as the set of positions where the inscribed circle meets the boundary in at least two locations~\cite{blum1967transformation,lee1982medial}.
@@
 \end{enumerate*}
-The vertex-line and vertex-vertex edges are discretized into pieces with a length up to \revise{$d^\text{discretization}$}{\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
+The vertex-line and vertex-vertex edges are discretized into pieces with a length up to {\SI{0.2}{\milli\meter}, which gives an approximation error of only $\pm$\SI{0.01}{\milli\meter}}.
 This allows to approximate the feature radius between two discretized nodes $v_0$ and $v_1$ by linear interpolation. 
@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill to occur in central, we mark parts of the ST as being central.
-\revise{The remainder is called peripheral.}{}
+In order to prevent over- and underfill {from occurring} in central{ regions}, we mark parts of the ST as being central.
+
 Our framework will decide on a beading at all the marked nodes in `the center' and apply the beading outward to the unmarked nodes (\cref{sec_peripheral_height_adjustment}).
@@
 An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
-As illustrated in \revise{See }{}\cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
-This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$.
-\revise{}{A too large $\alpha_\text{max}$ may leave a lot of under-/overfill, while a too small value may introduce toolpaths to fill in negligibly small underfills.
+As illustrated in \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
+This corresponds to overfill areas and underfill areas the size of {$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$.
+{A too large $\alpha_\text{max}$ may leave a lot of under-/overfill, while a too small value may introduce toolpaths to fill in negligibly small underfills.
 We therefore set $\alpha_\text{max} = \SI{135}{\degree}$.}
@@
 if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
-\revise{}{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to significance measure.}
+{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to significance measure.}
 
@@
 For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
-\revise{}{A value of $d_\text{max}^\text{transition} = \SI{1}{\milli\meter}$ seems to produce satisfactory results.}
-\revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
+{A value of $d_\text{max}^\text{transition} = \SI{1}{\milli\meter}$ seems to produce satisfactory results.}
+{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
 
@@
 The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
-\revise{$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,}
+
 {$t_0(n) \equiv \Delta(v_0v_x) =  t(n) \left( q^{-1}(n) / w^*  - n \right)$,}
 where $\Delta$ is the total distance along the edges between two nodes.
-\revise{}{The transition length $t(n)$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and the toolpath smooth.
+{The transition length $t(n)$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and the toolpath smooth.
 The transition anchor position $t_0(n)$ ensures that the transitions never overlap with each other or with locations where all beads have the preferred width $w^*$.}
@@
 \subsection{Beading}\label{sec_peripheral_height_adjustment}
-Now that we have determined the bead counts in the central regions we will describe how the peripheral regions are handled.
+Now that we have determined the bead counts in the {marked }central regions we will describe how the {unmarked} regions are handled.
 Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
@@
 There we also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
-and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node\revise{.}{, which we set to $t_\text{beading} = w^* $, so that the transition is not too swift.}
+and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node{, which we set to $t_\text{beading} = w^* $, so that the transition is not too swift.}
 
@@
 so that we can then deal with beading conflicts in a downward phase.
-\revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
+{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
 
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greedily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$\revise{, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.}{.
+In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}${.
 We set $d_\text{max}^\text{intersection} = \SI{75}{\percent}$ in order to slightly favor overfilling over underfilling.}

### 2020-01-25 5_generalization.tex
remove \revise macro everywhere

@@
 
-\revise{
-\begin{definition}\label{beading_scheme_definition}
-The beading scheme is configured by the following set of functions and constants:
-\begin{align*}
-\{
-&q(d),
-B(n, r),
-t(n),
-t_0(n),
-\\
-&\alpha_\text{max}, 
-t_\text{beading}, 
-d_\text{max}^\text{transition}, 
-d_\text{max}^\text{unmarked}, 
-d_\text{max}^\text{intersection},
-d^\text{discretization}
- \}
-\end{align*}
-where, as introduced in previous section,
-$q(d)$ the quantization operator,
-$B(n,r)$ is the beading function consisting of $\left( W(n,r), L(n,r) \right)$,
-$t(n)$ the transition length,
-$t_0(n)$ the transition anchor position,
-$\alpha_{\text{max}}$ is the limit bisector angle,
-$t_\text{beading}$ is the beading conflict transition length,
-$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
-$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
-$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
-and
-$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
-%$W(n, r)$ and $L(n, r)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
-\end{definition}
-}{}
-
-\revise{
-The following restrictions hold:
-\begin{enumerate}
-	\begin{minipage}{\columnwidth}
-	\setlength\intextsep{0pt}
-	\begin{wrapfigure}[4]{o}{.4\columnwidth} %\centering
-	\includegraphics[width=.3\columnwidth,frame]{sources-method-transition-length-limit.pdf}
-	%\caption{
-	%%Transition ends (magenta and pink) shouldn't cross each other.
-	%Placement of transition ends (magenta and pink) with respect to the anchor positions of the transitions (purple) on a ST edge (blue) with bisector angle $\alpha \approx \SI{135}{\degree}$.
-	%The distance between the anchor position and the upper end ($t_1$) and the distance between the anchor position and the lower end of the transition ($t_0$) should add up to less than the total distance between the anchor positions, which is limited by $\alpha_\text{max}$.
-	%}
-	\label{transition_placement}
-	\end{wrapfigure}
-	\item Transitions shouldn't overlap each other: \\ $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ \\ for each $n \in \mathbb{N}$ \\ (see \cref{transition_placement})
-\end{minipage}
-\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
-\item For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
-\end{enumerate}
-}{}
-
-\revise{}{
+{
 \begin{definition}\label{beading_scheme_definition}
@@
 
-\revise{}{
+{
 For the smoothness and continuity of toolpaths we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$.
@@
 
-\revise{
-A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
-Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
-Most of the beading schemes we introduce share a common ground:
-\begin{align*}
-L(n,r)_i = 
-\begin{cases}
--\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
-r & \text{ if } i =  \frac12 (n -1) \\
-%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
-\end{cases}
-\\
-\begin{array}{rlrl}
-t_\text{beading} &= w^* 
-&
-d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
-\\
-t(n) &= w^*
-&
-d_\text{max}^\text{unmarked} &= w^*
-\\
-t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
-&
-d^\text{discretization} &= \SI{0.2}{\milli\meter}
-\\
-\alpha_\text{max} &= \SI{135}{\degree} 
-&
-d_\text{max}^\text{intersection} &= \SI{75}{\percent}
-\end{array}
-%\end{align*}
-%\begin{align*}
-\end{align*}
-}{}
-
-\revise{
-The toolpath locations $L$ ensure 
-that the beads don't overlap,
-that beads are extruded from the center of where they end up
-and that the symmetry restrictions are met.
-The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $R(v) = \nicefrac12 n w^*$ for $n \in \mathbb{N}$.
-The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
-The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.
-}{}
-
 \begin{table}%\centering
 \caption{
-\revise{Made figure into table}{
+{
 Beading schemes.
@@
 We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
-\revise{See}{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.
+{We can simply set $\alpha_\text{max} = \SI{180}{\degree}$ and supply a simple beading scheme given by} \cref{formula_uniform}.
 
@@
 We can emulate the method from \citeauthor{Ding2016a} by dividing the feature radius over the widths of a constant number of beads.
-Additionally in order to emulate their definition of ``branches'' we mark all ST edges \revise{}{($\alpha_\text{max} = \SI{0}{\degree}$) and }we unmark the outer edges connected to the outline shape in a separate algorithm.
+Additionally in order to emulate their definition of ``branches'' we mark all ST edges {($\alpha_\text{max} = \SI{0}{\degree}$) and }we unmark the outer edges connected to the outline shape in a separate algorithm.
 Note that this deviation from the proposed framework violates the robustness against small perturbations in the outline polygon, since this marking depends on the topology of the graph of the ST.
@@
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
-Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
-We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*${, which gives us $w_\text{max}=1.8 w^*$}.
+Conversely, they place an extra bead when the radius exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}{, which gives us $w_\text{min}=0.5 w^*$}.
+We emulate the rounded polygonal path rerouting they define by supplying a transition length {$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
 See \cref{formula_centered}.
@@
 \caption{
-Closeup of toolpaths generated with the distributed \revise{}{and inward ($N=1.5$)} beading schemes for a large wedge shape.
+Closeup of toolpaths generated with the distributed {and inward ($N=1.5$)} beading schemes for a large wedge shape.
 Colors represent bead widths.
@@
 
-\paragraph{Widening \revise{}{meta-scheme}}
-Complementary to any of these schemes we can enforce a minimum feature size \revise{at no extra cost}{and minimum bead width} in our framework.
-Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
-See \cref{min_feature_size} and~\subref{widening}.
+\paragraph{Widening {meta-scheme}}
+Complementary to any of these schemes we can enforce a minimum feature size {and minimum bead width} in our framework.
+Regions where the model is narrower than {some $r_\text{min}$} can be printed with a bead width {$w_\text{min}$} larger than the model thickness.
+See \cref{min_feature_size,widening}.
 We can simply override
@@
 
-\revise{}{
+{
 \paragraph{Shell meta-scheme}

### 2020-01-25 6_validation.tex
remove \revise macro everywhere

@@
 
-\revise{}
 {
@@
 and by our framework using four beading schemes, i.e.
-the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
+the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using {$N=2$}, all with a preferred bead width{} of {$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
 The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
-\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
+{We report on the total statistics summed over the whole data set, because averaging would be biased.}
 
@@
 We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
-We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons.
+We construct the over- and underfill area by comparing the shapes covered by each extrusion move  with each other and with the total shape of the boundary polygons.
 (For implementation details see Appendix~\ref{accuracy_calculation}.)
@@
 We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
-and report the average percentages in \revise{see }{}\cref{over_underfill}.
-The inward distributed scheme has a calculated overfill of \revise{\SI{0.24}{\percent}}{\SI{0.30}{\percent}} and an underfill of \revise{\SI{0.17}{\percent}}{\SI{0.24}{\percent}}.
-This is lower compared to the uniform scheme, which results in \revise{\SI{1.2}{\percent}}{\SI{1.63}{\percent}} overfill and \revise{\SI{1.7}{\percent}}{\SI{1.62}{\percent}} underfill in the data set.
+and report the average percentages in \cref{over_underfill}.
+The inward distributed scheme has a calculated overfill of {\SI{0.30}{\percent}} and an underfill of {\SI{0.24}{\percent}}.
+This is lower compared to the uniform scheme, which results in {\SI{1.63}{\percent}} overfill and {\SI{1.62}{\percent}} underfill in the data set.
 \iffalse
@@
 \includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
-\caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
+\caption{Inward {($N=2$)}}\label{TEST_InwardDistributed_accuracy}
 \end{subfigure}
@@
 and wide beads in red.
-\revise{New shape contains pointy wedge to see impact on minimal feature size}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
+{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
 }
@@
 %\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
-\caption{\revise{}{Over- and underfill}}
+\caption{{Over- and underfill}}
 \label{over_underfill}
@@
 %\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
-\caption{\revise{}{Print time}}
+\caption{{Print time}}
 \label{printtime}
@@
 %\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
-\caption{\revise{}{Path counts}}
+\caption{{Path counts}}
 \label{pathcounts}
@@
 %\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
-\caption{\revise{}{Extrusion widths}}
+\caption{{Extrusion widths}}
 \label{widthHistogram}
@@
 %\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
-\caption{\revise{}{Site angles}}
+\caption{{Site angles}}
 \label{smoothness}
@@
 Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
-Note the use of a logarithmic scale \revise{}{in the bottom graphs }on the Y-axes and \revise{on some of}{for \subref{computime} on} the X-axes as well.
+Note the use of a logarithmic scale {in the bottom graphs }on the Y-axes and {for \subref{computime} on} the X-axes as well.
 }
@@
 We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
-\revise{
-We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
-\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
-}{
+{
 We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
@@
 These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
-\revise{
-We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
-The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
-}{}
 
-\revise{
-\subsubsection{Smoothness of toolpaths}
-In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
-We therefore measured the angle between consecutive extrusion segments generated by each scheme
-and report on the occurrence of each angle in \cref{smoothness}.
-All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
-We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
-The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
-We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
-\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
-}{
+{
 \subsubsection{Print time}
@@
 Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
-Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
+Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which may introduce defects and incurs extra print time.
 For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
@@
 
-\revise{
-Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
-The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
-gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
-We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
-We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
-
-The prints are shown in \cref{prints}.
-Because of inaccuracies in the deposition control system some of the prints show defects.
-Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
-The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
-Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
-The difference between the centered and the inward distributed schemes is less pronounced.
-We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
-However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
-The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
-
-\begin{figure}
-\centering
-\begin{subfigure}{\columnwidth}\centering
-\setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
-\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
-\end{subfigure}
-\setlength{\figheight}{.38\columnwidth}
-\setlength{\figheightTwo}{.47\columnwidth}
-\setlength{\figwidth}{0.32\columnwidth}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
-\caption{Uniform}\label{print_naive}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
-\caption{Centered}\label{print_center}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
-\caption{Inward distributed}\label{print_inward}
-\end{subfigure}
-\caption{
-Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
-The uniform technique produces distinct underfill areas.
-The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
-The inward distributed scheme produces the least defects.
-}
-\label{prints}
-\end{figure}
-}{}
-
 %We therefore visualize include a semi-circle with a diameter equal to the starting width in the one end, and exclude it at the other end, because it will be included in the next extrusion segment.

### 2020-01-25 8_discussion.tex
remove \revise macro everywhere

--- 2020-01-16 8_discussion.tex
@@
 \subsection{Comparison of beading schemes}
-We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
+We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average  {\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
 To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.
@@
 Note that most overfill areas occur near regions of alternating bead width. 
+{While the scheme results in short toolpaths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
+See \cref{statisticsfig}.}
 For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
 Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
+{See top right of \cref{TEST_Constant_accuracy}.}
 
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
+the centered beading scheme effectively deals with overfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths {range between $0.5 w^*$ and $1.8w^*$, i.e.
 the variation is within a factor of $3.6$.}
-According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
+{However, it does produce some narrow underfill regions.}
+{
+Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of toolpath angles below \SI{45}{\degree}.
+See \cref{statisticsfig}.
+}
 
 However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
-the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
-\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
+the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
+{\footnote{{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+\SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
+{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
 the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
-We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
+We therefore conclude that the distributed schemes {exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
 %This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.
 
-It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.
-However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.
-Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
-Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.
+{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline accuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
+%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
+%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
+ % _
+Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces {less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
+Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes{, while incurring little to no extra print time}.
 
-\revise{}
 {
@@
 
-\input{6_2_printing_results}
-
 \input{10_applications}
-
-\revise{
-\subsection{Discussion on implications}
-Note that the current industry standard in FDM printing employs little to no bead width variation.
-Properly performing bead width variation calls for adaptations and developments in printers and firmware.
-In the beading schemes we set a transition length of $t(n) = w^*$.
-That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
-Varying the movement speed can be utilized to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
-Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
-Using a filament feeder directly mounted on the print head (a.k.a.
-direct drive) can control the flow more dynamicaly then FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
-Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
-Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
-We expect that developments in printing hardware and firmware will address these challenges in the future.
-
-Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
-G-code does not support moves with varying cross-sectional area.
-A typical extrusion move \lstinline!G1 X$x$ Y$y$ E$v$!
-only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
-A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.
-However, this introduces errors nevertheless.
-Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
-}{}
 

### 2020-01-26 0_reviewer_response.tex
fix Fig refs in paper and mostly response letter

@@
 }
-See \cref{intro_wedge_distributed}. 
+See \cref{intro_wedge_distributed} here. 
 % In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
@@
 \subQue{
-From Fig. 1(b) and (c), we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
+From Figs. 1b and 1c, we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
 }\label{widening_question}
@@
 
-We have also changed the example shape of Fig. 16 (Now Fig. 17, reproduced here \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig. 1.
+We have also changed the example shape of Fig. 16 (Now Fig. 17, reproduced here in \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig. 1.
 }
@@
 {
-[See \cref{intro_wedge}.]
+[See \cref{intro_wedge} here.]
 }
@@
 Regions where the model is narrower than \revise{the nozzle size}{some $r_\text{min}$} can be printed with a bead width \revise{}{$w_\text{min}$} larger than the model thickness.
-See \cref{min_feature_size} and~\subref{widening}.
+See \cref{min_feature_size,widening}.
 We can simply override
@@
 
-Figure~\ref{no_corners} shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
+\Cref{no_corners} (of this document) shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
 }
@@
 \Ans{
-The difference between the inward distributed beading scheme and the method by Jin et al 2017 JMS is already shown in Fig 1.b and c. 
-It is also shown in Fig. 18 c and e.
+The difference between the inward distributed beading scheme and the method by Jin et al 2017 JMS is already shown in Figs. 1c and 1b respectively. 
+It is also shown in Figs. 17c and 17e (old Figs. 16c and 16e).
 In order to clearly address the difference early on we mention the difference in the description of Jin in the introduction.
@@
 \Que{
-In Fig.1, how to justify the proposed approach as different geometries are used?
-I believe if the authors use the same geometries as in Fig 1.
-(a) and (b), there would be also underfill areas using the proposed approach.
+In Fig.
+1, how to justify the proposed approach as different geometries are used?
+I believe if the authors use the same geometries as in Figs.
+1a and 1b, there would be also underfill areas using the proposed approach.
 }\label{fig1geometry}
@@
 There are two ways in which we can interpret this question, leading to two responses.
-The question can be interpreted as saying that Fig a has a different geometry than b or c.
-There is now a black outline to show that the shapes in Fig 1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.
-
-The question can also be interpreted as saying that one might use a different shape than the geometry in Fig 1.
+The question can be interpreted as saying that Fig. 1a has a different geometry than Figs. 1b and/or 1c.
+There is now a black outline to show that the shapes in Figs. 1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.
+
+The question can also be interpreted as saying that one might use a different shape than the geometry in Fig. 1.
 We decided on this wedge shape because it shows how the techniques deal with a wide range of feature sizes;
@@
 \paper{Intro}{
-[See caption of \cref{intro_wedge}.]
+[See caption of \cref{intro_wedge} here.]
 }
@@
 \Que{
-In Fig.4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
+In Fig. 4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
 }
@@
 \commits{07df258c1fa618808ba9493384550021a03c83e1}
-\paper{Fig 4}
-{
-[See \cref{legend}.]
+\paper{Fig. 4}
+{
+[See \cref{legend} here.]
 }
@@
 \Que{
-What are the differences between the distributed and the inward scheme in Fig. 16(d) and (e)? Are they the same? 
-}
-\Ans{
-We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig 18d and 18e).
+What are the differences between the distributed and the inward scheme in Fig. 16d and 16e? Are they the same? 
+}
+\Ans{
+We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig. 17d and 17e).
 The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths along the outer paths can be omitted.
@@
 {
-[See \cref{distributed_comparison}.]
+[See \cref{distributed_comparison} here.]
 }
@@
 \end{figure}
-\paper{Caption of Fig. 18}
+\paper{Caption of Fig. 17}
 {
@@
 }
-\paper{Caption of Fig. 20}
+\paper{Caption of Fig. 19}
 {
@@
 \Que{
-In Fig. 17(b), where is the curve for the ”uniform” case?
+In Fig. 17b, where is the curve for the ”uniform” case?
 }
@@
 We've added it back in.
+The graph is now displayed in Fig. 18d.
 Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve is not really informative.
@@
 \subQue{
-The authors seem to use linear approximations of the medial axis - see Figure 2 (b), which is understandable given the fact that they compute the MA with the Boost library.
+The authors seem to use linear approximations of the medial axis - see Fig.
+2b, which is understandable given the fact that they compute the MA with the Boost library.
 If this is so, can the authors comment on the implications of this approximation?
@@
 (See section 3.3 Significance measure, last paragraph.)
-See Figure~\ref{response_parabola_discretization}.
+See \cref{response_parabola_discretization} here.
 }
@@
 \subQue{
-For example, what happens if the obtuse outside angle in Figure 2 goes to 0? 
-}
-\Ans{
-That figure is reproduced here in Fig.~\ref{overview_outline}.
+For example, what happens if the obtuse outside angle in Fig. 2 goes to 0? 
+}
+\Ans{
+That figure is reproduced here in \cref{overview_outline}.
 As the rightmost two points move right, the degree of the corner in the middle goes to zero, which causes the parts of the parabola revealed to be more accurately described by the discretization than the highly curved part in the middle.
@@
 \Ans{
-The proposed technique relies \emph{less} on the accuracy of the control than existing techniques – as exemplified by Fig 19d.
+The proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evely distributed schemes exhibit less variation than the state-of-the-art centered technique.
+See Fig. 18d (old Fig. 17b).
 
@@
 We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
-See also our response to question~\ref{widening_question} for clarification in the difference between Fig 1b and 1c.
+See also our response to question~\ref{widening_question} for clarification in the difference between Figs. 1b and 1c.
 }
@@
 004894210fbc961f82b792fc702d1b67a1a8e8e8 lil lang improvement (reviewer 3.3)
-9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in fig 1 (reviewer 1.6, 3.3)
-}
-\paper{Fig 1}{
+9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in Fig. 1 (reviewer 1.6, 3.3)
+}
+\paper{Fig. 1}{
 \subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
@@
 \Que{
-Figure 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
+Fig. 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
 }
@@
 \Que{
-In Figure 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
-}
-\Ans{
-Fixed. Fig 3 c and d now have the same discretization.
+In Fig. 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
+}
+\Ans{
+Fixed. Fig. 3c and 3d now have the same discretization.
 }
@@
 The visual quality in terms of a homogenous surface are discussed in the section on the new printing results.
-See our response to question ~\ref{s5_prints}.
+See our response to question~\ref{s5_prints}.
 }
@@
 \Que{
-I think Figure 13 should be replaced with a table. 
+I think Fig. 13 should be replaced with a table. 
 }
@@
 We have fixed some issues with positions and colors being swapped in the statistical analysis subfigures.
-Fig 17f colors are adjusted.
-Fig 17e and 17f are swapped.
+Fig. 17 colors are adjusted.
 \commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
@@
 In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme.
-The extrusion width statistics figure (19d) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
+The extrusion width statistics figure (now Fig.
+18d, old Fig.
+17b) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
 

### 2020-01-26 4_method.tex
fix Fig refs in paper and mostly response letter

--- 2020-01-25 4_method.tex
@@
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{3d_surface_overview}\subref{overview_outline}-\subref{overview_uniform_paths}).
+Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).
 

### 2020-01-26 0_reviewer_response.tex
fix formatting of removed paragraphs

@@
 We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
-}{}
-
-\revisepar{
+%}{}
+\par
+%\revisepar{
 The prints are shown in \cref{prints_old}.
@@
 We expect that developments in printing hardware and firmware will address these challenges in the future.
-}{}
-
-\revisepar{
+%}{}
+\par
+%\revisepar{
 Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
@@
 \end{definition}
-}{}
-
-\revisepar{
+%}{}
+\par
+%\revisepar{
 The following restrictions hold:
@@
 \end{align*}
-}{}
-
-\revisepar{
+%}{}
+\par
+%\revisepar{
 The toolpath locations $L$ ensure 

### 2020-01-26 12_conclusions_future_work.tex
more emphasis on defects introduced by discontinuities (reviewer 1.4)"

--- 2020-01-25 12_conclusions_future_work.tex
@@
 Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
-An accurate model of manufacturability, \revise{}{which relates }print speed\revise{, }{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
+An accurate model of manufacturability, \revise{}{which relates }print speed, \revise{}{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
 \revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}

### 2020-01-26 0_reviewer_response.tex
reformulate response to 1.4

@@
 \Ans{
-That is a difficult question.
-It might very well be true that discontinuous extrusion lines form a bigger problem than some over- or underfill areas - at least certainly for flexible filaments on a Bowden printer.
-However, it is quite hard to find a mathematical approach to balance discontinuity with the size of over-/underfill areas.
-
-%It should be noted that even small underfill areas can be unfillable using an overextrusion approach.
-%For example the microgaps at 3-way intersections.
-%The viscocity of molten filament is too high to reach into those small crevices.
-}
-\todo{
-count number of extrusion toolpaths?
-
-That might be true, but the microgaps near 3-way intersections are not fillable using overfilling; the plastic cannot creap into those cravices.
-}
-\commits{
+Indeed the discontinuities are both relevant to print time and introduce defects.
+We now address these facts in text and show statistics on the number of discontinuities in Fig. 18c.
+The evenly and inward distributed schemes cause approximately \SI{20}{\percent} more discontinuities compared to the uniform method, but the print time is not significantly increased.
+
+We have not performed a physical tests which informs on the influence of discontinuities or of overfill on the mechanical performance of any 3D printer.
+Disconnected filaments will have worse mechanical performance compared to continuous ones, but we don't know how they compare against overfilling ones.
+Altering the beading strategy locally depending on the size of the overfill area is in interesting idea for future research.
+
+Without such a method we can only compare the total impact of our method compared to existing methods.
+While the evenly and inward distributed schemes cost \SI{20}{\percent} more discontinuities than the uniform method, the uniform method costs approx. \SI{400}{\percent} more over- and underfill.
+The cost of the discontinuities is negligible compared to the benefit of reduced over- and underfill.
+
+Compared against the state-of-the-art centered method, our schemes only reduce the number of discontinuities.
+}
+\commits{
+272fbca357c379ebe291735e3084cf86db4bdee1 % more emphasis on defects introduced by discontinuities
 f2132c1c0cbce6daa29f64890be5f9e20c79c630 % future work notice
+}
+\paper{5.2.3 Print time}
+{
+\revise{}{
+Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which may introduce defects and incurs extra print time.
+}
+}
+\paper{6.1 Future work}
+{
+An accurate model of manufacturability, \revise{}{which relates }print speed, \revise{}{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
+\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
 }

### 2020-01-26 0_reviewer_response.tex
comment on leaving out two statistics graphs in the response

@@
 We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig. 17d and 17e).
-The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths along the outer paths can be omitted.
+The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths of the outer paths can be omitted;
+Fig. 17c of the first submission is omitted from the revised manuscript.
 }
@@
 
+Remove Fig. 17e.
+The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.
+
 Fix double header of References.

### 2020-01-26 0_reviewer_response.tex
fix response change section numbers and names

@@
 }
-\paper{Intro}
+\paper{1. Introduction}
 {
@@
 }
-\paper{Conclusion}{
+\paper{6. Conclusion and future work}{
 In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
@@
 \commits{b7c4d299a76e9fab6c233d572f3248c1350a2e8c}
-\paper{Intro}{
+\paper{1. Introduction}{
 \revise{
@@
 \commits{45853e8b30d93f60e9465cbb649e347f9cfc23b1 53224c04ceff6c1b18a9eea6de8e7e33957b7797}
-\paper{Intro}{
+\paper{1. Introduction}{
 [See caption of \cref{intro_wedge} here.]
@@
 \commits{eb2a5207c83dfe069d3ab3fc37bf2149b8a51964}
-\paper{Related work}{
+\paper{2. Related work}{
 Third, the extruded path should cover \revise{a }{}the region of the contour without gaps.
 }
-\paper{Related work}{
+\paper{3.5 Beading, Beading propagation}{
 \revise{This the}{The} downward phase makes sure that all nodes have a beading associated with it, so that the slicing algorithm can efficiently slice the edges leading up to a marked or unmarked node.
@@
 }
-\paper{Beading schemes}
+\paper{4. Beading schemes}
 {
@@
 }
-\paper{3.1 Method overview}{
+\paper{3.1 Overview}{
 Our method starts with computing \revise{the skeleton of the input polygon}{a graph which represents the topology of the input polygon: its \emph{skeleton}. 
@@
 \commits{d3f19c04e3bb0d80c0b162531dbf576fc705d77c}
-\paper{Medial axis transform}{
+\paper{3.2 Union of cones, Medial axis transform}{
 The medial axis is a \revise{compact and complete representation of}{representation commonly used to analyse} a shape.
@@
 }
-\paper{5.2 Printing results}
+\paper{5.1.2 Printing results}
 {
@@
 }
-\paper{5.3 Limitations}
+\paper{5.4 Limitations}
 {
@@
 }
-\paper{Introduction, bulletlist}{
+\paper{1. Introduction, bulletlist}{
 A specific beading scheme \revise{for FDM printing}{} which [\dots]
@@
 
-\paper{Intro}{
+\paper{1. Introduction}{
 \revise{
@@
 }
-\paper{Intro}{
+\paper{1. Introduction}{
 The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
@@
 }
-\paper{5.2 Comparison of beading schemes, paragraph 3, 4}{
+\paper{5.3 Comparison of beading schemes, paragraph 3, 4}{
 In \cref{TEST_Center_accuracy} we can see that
@@
 }
-\paper{5.3 Limitations, second paragraph}
+\paper{5.4 Limitations, second paragraph}
 {
@@
 }
-\paper{5.4.1 Back pressure compensation}
+\paper{5.1.1 Back pressure compensation}
 {
@@
 }
-\paper{Intro}{
+\paper{1. Introduction}{
 \revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}

### 2020-01-26 0_reviewer_response.tex
fix response changes ordering
add References section title
enhance formatting of response
explain formatting of response better

@@
 \bibliographystyle{elsarticle-num-names}
+
+\newif\ifIncludeTextChanges
+
+\IncludeTextChangesfalse
 
@@
 }
-%\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
+\ifIncludeTextChanges\else
+\renewcommand\paper[2]{\par changes to \emph{#1} --- ``\dots'' }
+\fi
 
@@
 
-\newcommand\Ans[2][]{%
-	\begin{tcolorbox}[colback=white, arc=0mm]
-    \leavevmode\par\noindent
-   {%\leftskip37pt
-    %{\it Response:} 
-    \textbf{#1}#2\medskip\par}
+\newlength\oldparindent
+
+\newcommand\Ans[1]{%
+	\begin{tcolorbox}[colback=white, arc=0mm,before upper={\parindent15pt\noindent}]
+   #1
     \end{tcolorbox}
+    \medskip\par
     }
@@
 
+\section*{Formatting of this document}
+This document contains the reviewer feedback on the first submission, our response to that feedback and the changes we made to arrive at the current submission.
+When referring to figure numbers we clearly indicate whether we are referring to a figure in this document (`here'), in the first submission (`old') or in the current submission (`now').
+References numbers in the textual changes reproduced here do not correspond with the reference numbers in the actual manuscript.
+
+The following explains the formatting using in this response to reviewers:
+
 \Que{Example text by reviewer.}
@@
 }
-\paper{6. Conclusion, last paragraph}{
-\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
+\paper{3.3 Method, Significance measure}{
+This corresponds to overfill areas and underfill areas the size of \\ \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
 }
@@
 }
-\paper{3.3 Method, Significance measure}{
-This corresponds to overfill areas and underfill areas the size of \\ \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$} when filled using the simple technique of uniform bead width $w^*$
+\paper{6. Conclusion, last paragraph}{
+\revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
 }
@@
 }
+\paper{5.1.1 Back pressure compensation}
+{
+\revise{}{Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.}
+}
+
 \paper{6. Conclusion and future work, last paragraph}{
@@
 \revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
-}
-\paper{5.1.1 Back pressure compensation}
-{
-\revise{}{Furthermore, the shape and filling of the previous layer might influence the amount of back pressure.}
 }
@@
 
+\section*{References}
 \bibliography{99_mybib}

### 2020-01-26 0_reviewer_response.tex
fix figure references and citations in response

@@
 
-\IncludeTextChangesfalse
+\IncludeTextChangestrue
 
@@
 \Ans{Example response.}
-\paper{Section name}{
+\paper{New section name}{
 Remaining text, followed by 
@@
 We can then derive that the naive scheme produces over-/underfill at all diameters except $d=2i w^*$, the center scheme for $(i + 0.8) w^* < d < (i+ 1.25) w^*$ and the constant and distributed schemes nowhere (except for features smaller than $w^*$).
-We have added a paragraph to the new section 5.1 Theoretical consideration to explain this and the implications for design for additive manufacturing.
+We have added a paragraph to the new section~5.1~Theoretical consideration to explain this and the implications for design for additive manufacturing.
 
 2.
-When the feature size changes the amount of over-/underfill is related to a bisector angle $\alpha < \alpha_\text{max}$ according to the formula already given in section 3.3, paragraph `Significance measure':
+When the feature size changes the amount of over-/underfill is related to a bisector angle $\alpha < \alpha_\text{max}$ according to the formula already given in section~3.3, paragraph `Significance measure':
 ``This corresponds to overfill areas and underfill areas the size of \revise{$\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$}{$\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right)$}''.
@@
 when 3 beads surround a single point there will always remain a micro-gap because of the high viscosity of the molten filament.
-This is handled in Fig. 12 and the last paragraph of section 3.6.
+This is handled in Fig.~12 and the last paragraph of section~3.6.
 
@@
 2e1c40be93f92a8495c0d7fa379e983dd3ee7b98 % emphasize implication for DfAM in conclusion
-5b8c5971d606089754ba118560e51ec6d7dfda0b % new section `Theoretical considerations'
+5b8c5971d606089754ba118560e51ec6d7dfda0b % new section~`Theoretical considerations'
 7c2224fc713f5b68436f432a1ade506e9dacf500 % lil edit in above section
@@
 \subQue{
-From Figs. 1b and 1c, we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
+From Figs.~1b and 1c, we can see that the approach in Jin et al (2017) can fill the sharp right end, but the proposed approach can not. 
 }\label{widening_question}
 \Ans{
-Note that this is not a limitation of the approach, but a consequence of the default parameters which were chosen.
-
-We have introduced a new parameter in the widening meta-scheme which can be used specificly to tune the minimal diameter starting from which we generate a toolpath.
-This minimum feature size is now used in the new computational test results and in Fig. 1.
-
-We have also changed the example shape of Fig. 16 (Now Fig. 17, reproduced here in \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig. 1.
+Note that this is not a limitation of the approach, but a consequence of the default parameters which had been chosen.
+
+We have now introduced a new parameter in the widening meta-scheme which can be used specificly to tune the minimal diameter starting from which we generate a toolpath.
+This minimum feature size is now used in the new computational test results and in Fig.~1.
+
+We have also changed the example shape of Fig.~17 (old Fig.~16, reproduced here in \cref{visualized_accuracy}) to include a pointy wedge shape similar to Fig.~1.
 }
@@
 \Ans{
-The wedge shape of Fig. 1 was chosen because it contains a wide range of feature sizes and is therefore representative for a wide range of models.
-Nearly every model induces the full range of $[0.5w^*,1.8w^*]$ using the centered approach by Jin et. al. 2017 JMS,
+The wedge shape of Fig.~1 was chosen because it contains a wide range of feature sizes and is therefore representative for a wide range of models.
+Nearly every model induces the full range of $[0.5w^*,1.8w^*]$ using the centered approach by \citeauthor{Jin2017JMS},
 because nearly all models have feature sizes which span any range $[iw^*,(i+1)w^*]$ for $i\in\mathcal{N}$.
-See Fig. 17 in the paper of Jin et al for an example shape.
+The shape of Fig.~17 from the paper of \citeauthor{Jin2017JMS} itself already shows this.
 Only shapes without central regions (a circle) or shapes with central regions with an exact multiple of $w^*$ everywhere (a rectangle) don't require any variation in bead width, but that holds for any of the beading schemes.
 
-\Cref{no_corners} (of this document) shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by Ding et al.
+\Cref{no_corners} (of this document) shows an example of a shape without sharp corners, and which also requires a large bead width variation when using the constant bead count approach by \citeauthor{Ding2016a}.
 }
@@
 \includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy.png}
-\caption{Problematic for center, i.e. Jin et al 2017 JMS, exhibiting $4.5w^*$ and $5.8w^*$}
+\caption{Problematic for center, i.e. \citeauthor{Jin2017JMS}, exhibiting $4.5w^*$ and $5.8w^*$}
 \end{subfigure}
@@
 \includegraphics[width=\linewidth]{response_no_corners}
-\caption{Problematic for constant, i.e. Ding et al}
+\caption{Problematic for constant, i.e. \citeauthor{Ding2016a}}
 \end{subfigure}
@@
 Indeed the discontinuities are both relevant to print time and introduce defects.
-We now address these facts in text and show statistics on the number of discontinuities in Fig. 18c.
+We now address these facts in text and show statistics on the number of discontinuities in Fig.~18c (\cref{printtime} here).
 The evenly and inward distributed schemes cause approximately \SI{20}{\percent} more discontinuities compared to the uniform method, but the print time is not significantly increased.
@@
 \Ans{
-The difference between the inward distributed beading scheme and the method by Jin et al 2017 JMS is already shown in Figs. 1c and 1b respectively. 
-It is also shown in Figs. 17c and 17e (old Figs. 16c and 16e).
-In order to clearly address the difference early on we mention the difference in the description of Jin in the introduction.
+The difference between the inward distributed beading scheme and the method by \citeauthor{Jin2017JMS} is already shown in Figs.~1c and 1b respectively. 
+It is also shown in Figs.~17c and 17e (old Figs.~16c and 16e, \cref{TEST_Center_accuracy,TEST_InwardDistributed_accuracy} here).
+In order to clearly address the difference early on we mention the difference in the description of \citeauthor{Jin2017JMS} in the introduction.
 }
@@
 \Que{
-In Fig.
-1, how to justify the proposed approach as different geometries are used?
-I believe if the authors use the same geometries as in Figs.
-1a and 1b, there would be also underfill areas using the proposed approach.
+In Fig.~1, how to justify the proposed approach as different geometries are used?
+I believe if the authors use the same geometries as in Figs.~1a and 1b, there would be also underfill areas using the proposed approach.
 }\label{fig1geometry}
@@
 There are two ways in which we can interpret this question, leading to two responses.
-The question can be interpreted as saying that Fig. 1a has a different geometry than Figs. 1b and/or 1c.
-There is now a black outline to show that the shapes in Figs. 1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.
-
-The question can also be interpreted as saying that one might use a different shape than the geometry in Fig. 1.
+The question can be interpreted as saying that Fig.~1a has a different geometry than Figs.~1b and/or 1c.
+There is now a black outline to show that the shapes in Figs.~1a, b and c are actually the same geometry, and the output is less confusing because we now use the same minimum feature size for b and c.
+
+The question can also be interpreted as saying that one might use a different shape than the geometry in Fig.~1.
 We decided on this wedge shape because it shows how the techniques deal with a wide range of feature sizes;
@@
 \Que{
-Please double check the following sentences. ”Third, the extruded path should ...”(at the second paragraph of Section 2) ”This the downward phase...” (at the last paragraph of Section 3.5) 
+Please double check the following sentences. ”Third, the extruded path should ...”(at the second paragraph of Section~2) ”This the downward phase...” (at the last paragraph of Section~3.5) 
 }
@@
 \Que{
-In Fig. 4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
+In Fig.~4, the bead count should marked in another way. The ultra thick solid line conflicts with that for ”outline”. 
 }
@@
 \commits{07df258c1fa618808ba9493384550021a03c83e1}
-\paper{Fig. 4}
+\paper{Fig.~4}
 {
@@
 \Que{
-What are the differences between the distributed and the inward scheme in Fig. 16d and 16e? Are they the same? 
-}
-\Ans{
-We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig. 17d and 17e).
+What are the differences between the distributed and the inward scheme in Fig.~16d and 16e? Are they the same? 
+}
+\Ans{
+We have adjusted the range of the inward distributed scheme to $N=2$ in order to generate a bigger difference between these images (Now Fig.~17d and 17e, here \cref{TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy}).
 The difference between inward and evenly distributed is now deemed to be so clear that the statistics graphs on the widths of the outer paths can be omitted;
-Fig. 17c of the first submission is omitted from the revised manuscript.
+Fig.~17c of the first submission is omitted from the revised manuscript.
 }
@@
 \end{figure}
-\paper{Caption of Fig. 17}
+\paper{Caption of now Fig.~17}
 {
@@
 }
-\paper{Caption of Fig. 19}
+\paper{Caption of now Fig.~19}
 {
@@
 \Que{
-In Fig. 17b, where is the curve for the ”uniform” case?
+In Fig.~17b, where is the curve for the ”uniform” case?
 }
@@
 We've added it back in.
-The graph is now displayed in Fig. 18d.
+The graph is now displayed in Fig.~18d (\cref{widthHistogram} here).
 Note that the width of the uniform case is \SI{0.4}{\milli\meter} \emph{everywhere}, so the curve is not really informative.
@@
 \Que{
-There are occasional omissions, perhaps unintentional, such as the definition of a skeleton - see section 3.1, second paragraph. 
+There are occasional omissions, perhaps unintentional, such as the definition of a skeleton - see section~3.1, second paragraph. 
 }
@@
 \subQue{
-The authors seem to use linear approximations of the medial axis - see Fig.
-2b, which is understandable given the fact that they compute the MA with the Boost library.
+The authors seem to use linear approximations of the medial axis - see Fig.~2b, which is understandable given the fact that they compute the MA with the Boost library.
 If this is so, can the authors comment on the implications of this approximation?
@@
 
-The discretization is handled in section 3.2. Skeletal trapezoidation, second paragraph.
+The discretization is handled in section~3.2~Skeletal trapezoidation, second paragraph.
 The discretization simplifies the algorithm, potentially at a slight computational cost.
@@
 The computation of this value is complicated by the fact that the discretization always introduces a sample point at the apex and at the boundaries of significant portions of the parabola.
-(See section 3.3 Significance measure, last paragraph.)
+(See section~3.3~Significance measure, last paragraph.)
 See \cref{response_parabola_discretization} here.
@@
 \subQue{
-For example, what happens if the obtuse outside angle in Fig. 2 goes to 0? 
+For example, what happens if the obtuse outside angle in Fig.~2 goes to 0? 
 }
@@
 The proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evely distributed schemes exhibit less variation than the state-of-the-art centered technique.
-See Fig. 18d (old Fig. 17b).
+See Fig.~18d (old Fig.~17b, \cref{widthHistogram} here).
 
@@
 We have added statistics on fabrication time and discussed our findings.
-See our response to 1.3.
+See our response to question~\ref{printtime_question}.
 }
@@
 \Ans{
-We've added a paragraph to section 5.3. Limitations, which discusses these emulation limitations.
+We've added a paragraph to section~5.4~Limitations, which discusses these emulation limitations.
 }
@@
 We now clearly claim that our method produces a lower range of bead widths than the state-of-the-art.
-See also our response to question~\ref{widening_question} for clarification in the difference between Figs. 1b and 1c.
+See also our response to question~\ref{widening_question} for clarification in the difference between Figs.~1b and 1c.
 }
@@
 004894210fbc961f82b792fc702d1b67a1a8e8e8 lil lang improvement (reviewer 3.3)
-9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in Fig. 1 (reviewer 1.6, 3.3)
-}
-\paper{Fig. 1}{
+9ac2c005c2eb1c0696e2582963353b038fa71072 use limited distributed strategy in Fig.~1 (reviewer 1.6, 3.3)
+}
+\paper{Fig.~1}{
 \subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
@@
 \Ans{
-The bead width in Jin et al. is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.6$;
+The bead width in \citeauthor{Jin2017JMS} is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.6$;
 this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.6$.
@@
 \Que{
-Fig. 4 and corresponding explanation in Section 3.2 are confusing. Why such decomposition is needed is not clear to me. 
-}
-\Ans{
-Fig. 4 shows a legend of terms and color coding scheme used throughout the paper;
+Fig.~4 and corresponding explanation in Section~3.2 are confusing. Why such decomposition is needed is not clear to me. 
+}
+\Ans{
+Fig.~4 shows a legend of terms and color coding scheme used throughout the paper;
 it doesn't show a decomposition.
@@
 \Que{
-In Fig. 3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
-}
-\Ans{
-Fixed. Fig. 3c and 3d now have the same discretization.
+In Fig.~3, why some of the edges in (c) (the ones in the center area) disappear in (d)?
+}
+\Ans{
+Fixed. Fig.~3c and 3d now have the same discretization.
 }
@@
 We now mention their value where they are introduced and explain their value further where needed.
-Making these framework parameters independent of the beading schemes simplifies the definition of a beading scheme and greatly simplifies section 4. Beading schemes.
+Making these framework parameters independent of the beading schemes simplifies the definition of a beading scheme and greatly simplifies section~4~Beading schemes.
 }
@@
 }
-% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section 3.4 Smooth transitions
+% the condition that transitions don't overlap is already caught by the way in which we defined $t_0$ in section~3.4~Smooth transitions
 
@@
 However, we did show that the contour-parallel toolpaths can be combined with sparse infill.
-See our response to 3.2.
+See our response to question~\ref{outline_question}.
 }
@@
 \Que{
-I think Fig. 13 should be replaced with a table. 
+I think Fig.~13 should be replaced with a table. 
 }
@@
 \Que{
-In text, some references are missing, such as first sentence of “Outer bead” paragraph in Section 4 (Moesen et al [?]), first sentence of “Constant bead count” (Ding et al [?]) paragraph in Section 4 etc.
+In text, some references are missing, such as first sentence of “Outer bead” paragraph in Section~4 (Moesen et al [?]), first sentence of “Constant bead count” (Ding et al [?]) paragraph in Section~4 etc.
 }
@@
 We have fixed some issues with positions and colors being swapped in the statistical analysis subfigures.
-Fig. 17 colors are adjusted.
+Fig.~18 colors are adjusted.
 \commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
@@
 
-Remove Fig. 17e.
+Remove Fig.~17e.
 The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.
@@
 In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme.
-The extrusion width statistics figure (now Fig.
-18d, old Fig.
-17b) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
+The extrusion width statistics figure (now Fig.~18d, old Fig.~17b, \cref{widthHistogram} here) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
 

### 2020-01-26 0_reviewer_response.tex
lil fixes to response
improve most of reviewer 2 and 3's response

@@
 }
-See \cref{intro_wedge_distributed} here. 
+See \cref{intro_wedge_distributed}. 
 % In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
@@
 As the proposed approach adds more disconnected toolpaths to minimize underfill areas, an improper path planning would significantly increase the fabrication time.
-}
-\Ans{
-We now included a description of the path order algorithm, which is naive and greedy.
-Although an optimal path order algorithm might influence the travel time, such an algorithm is slow and not generally used in the industry.
-The software package Cura currently employs a similarly greedy algorithm.
-Travel times are approximately \SI{2}{\percent} of the total print time in our current setup, so the effect of improper path planning is negligible compared to the differences in extrusion time.
+}\label{printtime_question}
+\Ans{
+We now included a description of the path order algorithm, which is naive and greedy -- similar to the one employed by the software package Ultimaker Cura.
+A suboptimal path planning is preferred because of a reduced computation time.
+Travel times are only \SI{2}{\percent} of the total print time in our current setup, so the effect of improper path planning is negligible compared to the differences in extrusion time.
 
@@
 \Ans{
+Evidently it is not the case that the method we introduce is the same as the current state-of-the-art.
+In order to clearly mention the output of our method as a novel technique we now adjusted the contributions and made several changes throughout the introduction, results and conclusion.
+See also our response to question~\ref{contributions}.
+
 The difference between the inward distributed beading scheme and the method by \citeauthor{Jin2017JMS} is already shown in Figs.~1c and 1b respectively. 
@@
 That figure is reproduced here in \cref{overview_outline}.
-As the rightmost two points move right, the degree of the corner in the middle goes to zero, which causes the parts of the parabola revealed to be more accurately described by the discretization than the highly curved part in the middle.
+As the rightmost two points move right, the degree of the corner in the middle goes to zero, which reveals parts of the parabola which are more accurately described by the discretization than the highly curved part in the middle.
+The discretization error for this specific example is even smaller than the discretization error in the middle of the parabola.
 }
@@
 \Ans{
-The proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evely distributed schemes exhibit less variation than the state-of-the-art centered technique.
+On the contrary,
+the proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evely distributed schemes exhibit less variation than the state-of-the-art centered technique.
 See Fig.~18d (old Fig.~17b, \cref{widthHistogram} here).
 
-The photos of our print results already showed that adaptive width control is possible up to an admittedly insufficient extent.
-We have developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: \emph{back pressure compensation}.
-We show the results of back pressure compensation in a separate figure which clearly shows the achieved variance in bead width.
-
-All paragraphs on the physical realization have been put together and moved to after the theoretical analysis:
-we moved the section on limitations of linear advance algorithms (5.5 Discussion on implications) together with the section on Printing results to after the comparison of beading schemes (now 5.2).
-}
+The old photos (old Fig. 18, here \cref{prints_old}) of our print results already showed that adaptive width control is possible up to an admittedly insufficient extent.
+
+Because it was insufficient, we have now developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: \emph{back pressure compensation}.
+We show the results of back pressure compensation in a new figure (Fig. 15, reproduced here in \cref{back_pressure_compensation}) which clearly shows the achieved variance in bead width.
+
+All paragraphs on the physical realization, i.e. on linear advance and its limitations and on gcode limitations, have been assembled together and moved to 5.1. Fabrication.
+Because the print time statistics use our back pressure compensation approach we moved the fabrication results to before the statistical analysis.
+}
+
 \commits{
-%3d7238e2787f17c4cff63804eb4b84439ff85f1b  % initial printing results section 5.2
+%3d7238e2787f17c4cff63804eb4b84439ff85f1b  % initial printing results section~5.2
 %b5abdd980240cd4ca964ed0f4751c207baa09b85 % move 5.5 to 5.2
@@
 I think the motivation for contour parallel toolpaths needs to be justified further.
-}
+}\label{outline_question}
 \Ans{
 The industry standard is to use a combination of contour-parallel and direction-parallel.
-We now clarify why contour-parallel is (partly) used and that in as much as contour-parallel is used, our approach improves on the industry standard.
-We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with the industry standard for FDM 3D printing.
+Our approach was developed to improve on the former part while keeping the latter intact -- not to replace the latter by the former.
+
+We now clarify why contour-parallel is (partly) used and that \emph{in as much as contour-parallel is used}, our approach improves on the industry standard.
+We have also developed and presented a new meta-scheme for generating only a limited number of perimeters, which shows that our technique is compatible with generating direction-parallel toolpaths for internal areas.
 See also the changes to the paper presented under question~\ref{widening_question}.
@@
 }
-\paper{Fig.~1}{
-\subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.
-}
 
@@
 \Ans{
-The bead width in \citeauthor{Jin2017JMS} is limited to $0.5 w^*$ to $1.8 w^*$ , which means the variation is a factor of $3.6$;
-this was already described in the related work section, but the factor was wrongly said to be $2$ instead of $3.6$.
-We emphasized that our method results in a bead width variation of $2$, rather than $3.6$ in the related work section and in the discussion section.
+The bead width in \citeauthor{Jin2017JMS} is limited to the interval $[0.5 w^*,1.8 w^*]$ , which means the variation is a factor of $\text{max} / \text{min} = 1.8 / 0.5 = 3.6$. 
+\footnote{
+This new statistic replaces the old statistic of deviation from the preferred nozzle size: $\text{max} / w^*$.
+This old statistic is odd because it cannot take the min into account.
+Also the old statistic of $2.0$ had been computed using the hypothetical max of $2.0 w^*$ rather than the actually used $1.8w^*$.
+}
+
+We now emphasize that our method results in a bead width variation of $2$ (which is less than $3.6$) in the related work section and in the discussion section.
 This factor comes from the transition from a single bead to two beads.
-(The transition from zero beads to one is disregarded; it is controlled separately by the Widening meta-scheme.)
+It is not possible to generate toolpaths with a lower interval of bead widths if you consider geometry with arbitrary feature radius.
+%(The transition from zero beads to one is disregarded; it is controlled separately by the Widening meta-scheme.)
 }
@@
 \Ans{
-Fig.~4 shows a legend of terms and color coding scheme used throughout the paper;
-it doesn't show a decomposition.
-It is unclear to us what this review comment is asking for.
+Fig.~4 shows a legend of terms and color coding scheme used throughout the paper.
+It does also exhibit the skeletal trapezoidation decomposition, which is the starting point of our method.
+We have tried to explain our method clearly.
+We are unsure how we should further improve the method section in order to address this question.
 }
@@
 }
-\commits{
-6b0f8c78d31bd0c6946885da96f73f1cfc1a21ae clarify widespread use of concentric toolpaths in abstract (reviewer 3.9)
-}
-\paper{Abstract}{
-\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
-{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
-}
 
@@
 In our revision we address several new implications;
-we address the influence of layers in each other and the implications of underfill on stiffness.
+we address the influence of layers on each other and the implications of underfill on stiffness.
 We hope that these suffice.
@@
 \section{Other changes}
-We have fixed some issues with positions and colors being swapped in the statistical analysis subfigures.
-Fig.~18 colors are adjusted.
-\commits{43cadb352a6a276bbaaab53f9b5b217bec4b3a2e}
-
-Improvements to abstract.
+Several other issues have caught our attention during the revision process and were addressed in the current manuscript.
+
+We removed the angles graph of old Fig.~17e.
+The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.
+
+We fixed a mistake when performing the statistical analysis.
+In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme.
+The extrusion width statistics figure (now Fig.~18d, old Fig.~17b, \cref{widthHistogram} here) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
+
+We changed the width histogram calculation so that we use accurate statistics instead of sampling the width along the path.
+\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
+\paper{5.2.2 Uniformity}
+{
+\revise{
+We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
+\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
+}{
+We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
+From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
+}
+}
+
+We have made some improvements on the abstract.
 \commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
@@
 
-Remove Fig.~17e.
-The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.
-
-Fix double header of References.
-\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}
-
-Added patent notice and url to open source implementation.
+We added a patent notice and an url to the open source implementation.
 \commits{
@@
 
-Lil
+Explain why and how statistics are gathered over the whole data set.
+\commits{17135b010f5ac51fda77357136a19f67a80dbc33}
+\paper{5.2 Computational results}
+{
+\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
+}
+
+Furthermore:
+\begin{itemize*}
+\item Remove wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.
+\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
+\item Fig.~10 and Fig.~18 colors are adjusted.
+\commits{
+1196bad1c2bf4fb41e7d28985938cfe678384e5a % fig 10
+43cadb352a6a276bbaaab53f9b5b217bec4b3a2e
+}
+\item Fix double header of References.
+\commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}
+\item Fixed some typos.
 \commits{5f5c4c640d94010816e6d6d5934a2dc016b4d172
@@
 }
-
-Our department has changed its name:
+\item Our department has changed its name to \emph{Sustainable} Design Engineering.
 \commits{
@@
 }
-
-Removed confusing red parts from beading figure:
-\commits{
-1196bad1c2bf4fb41e7d28985938cfe678384e5a
-}
-
-We fixed a mistake when performing the statistical analysis.
-In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme.
-The extrusion width statistics figure (now Fig.~18d, old Fig.~17b, \cref{widthHistogram} here) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.
-
-Explain why and how statistics are gathered over the whole data set:
-\commits{17135b010f5ac51fda77357136a19f67a80dbc33}
-\paper{5.2 Computational results}
-{
-\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
-}
-
-Remove wrapfigure explaining the area covered by a single extrusion move (in section 5.2.1 `Accuracy'), since that is already explained in the appendix.
-\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
-
-Change width histogram calculation so that we use accurate statistics instead of sampling the width along the path:
-\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
-\paper{5.2.2 Uniformity}
-{
-\revise{
-We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
-\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
-}{
-We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
-From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
-}
-}
+\end{itemize*}
 

### 2020-01-26 0_reviewer_response.tex
spell check of response

@@
 .
-In the first case we consider a part with a constant feature size, in the second we consider the rate of change of feature size and in the thirs we consider the influence of 3-way intersections.
+In the first case we consider a part with a constant feature size, in the second we consider the rate of change of feature size and in the third we consider the influence of 3-way intersections.
 
@@
 
-We have now introduced a new parameter in the widening meta-scheme which can be used specificly to tune the minimal diameter starting from which we generate a toolpath.
+We have now introduced a new parameter in the widening meta-scheme which can be used specifically to tune the minimal diameter starting from which we generate a toolpath.
 This minimum feature size is now used in the new computational test results and in Fig.~1.
@@
 On the contrary,
-the proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evely distributed schemes exhibit less variation than the state-of-the-art centered technique.
+the proposed technique relies \emph{less} on the accuracy of the control than existing techniques, seeing as the extrusion widths of the inward and evenly distributed schemes exhibit less variation than the state-of-the-art centered technique.
 See Fig.~18d (old Fig.~17b, \cref{widthHistogram} here).
@@
 }
-\paper{1. Introduction, bulletlist}{
+\paper{1. Introduction, bullet list}{
 A specific beading scheme \revise{for FDM printing}{} which [\dots]

### 2020-01-28 0_reviewer_response.tex
Juns reponse suggestions

@@
 \Ans{
-We agree with this summary, although it does not stress the contribution of a novel beading scheme in the framework which improves on the state of the art.
-We have made various changes to highlight those as separate contributions.
+Thank you.
+We have addressed the comments, and have clarified our contributions.
 }
@@
 \Ans{
-Okay. Thanks.
+Thanks.
+The following changes have been made.
 }
@@
 \Ans{
-We cannot reproduce this typesetting bug. Please inform the proofing department to take extra care of these references when preparing this manuscript for publication.
+We cannot reproduce this typesetting bug, and will pay attention to this in future proofreading.
 }

### 2020-01-28 0_reviewer_response.tex
remove patent notice and move code url to conclusion

@@
 
-We added a patent notice and an url to the open source implementation.
+We added an url to the open source implementation.
 \commits{
@@
 }
-\paper{1. Introduction}{
-\revise{}{The presented framework is patented by Ultimaker and open source available at \url{github.com/Ultimaker/libArachne}.}
+\paper{6. Conclusion}{
+\revise{}{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
 }

### 2020-01-28 0_reviewer_response.tex
mention back pressure compensation in abstract

@@
 1b7bb61648b97b8084ca8817aa457bde2c91e1b3 % lil: explain unexplained math symbol 
+}
+\paper{Abstract}
+{
+We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd
+\revise{}{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
 }
@@
 Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd
+\revise{}{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
 }

### 2020-01-28 0_main.tex
add References section title
mention back pressure compensation in abstract

--- 2020-01-22 0_main.tex
@@
 We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd
+\revise{}{and physically validate it by developing a technique, called \emph{back pressure compensation}, for off-the-shelf FDM systems to effectively realize adaptive width.}
 \end{abstract}

### 2020-01-28 0_reviewer_response.tex
mention back pressure compensation in abstract

--- 2020-01-28 0_reviewer_response.tex
@@
 1b7bb61648b97b8084ca8817aa457bde2c91e1b3 % lil: explain unexplained math symbol 
+}
+\paper{Abstract}
+{
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
+\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
 }
@@
 Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
+\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
 }

### 2020-01-28 0_main.tex
mention back pressure compensation in abstract

--- 2020-01-22 0_main.tex
@@
 Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
+We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
+\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
 \end{abstract}

### 2020-01-28 0_reviewer_response.tex
reference to video in paper (extra change)

--- 2020-01-28 0_reviewer_response.tex
@@
 \item We have computed fabrication time results.
-\item \todo{We have added a video animation explaining the union of cones approach in an intuitive manner.}
+\item We have added a video animation explaining the union of cones approach in an intuitive manner.
 \end{enumerate}
@@
 
+We have added a 3D animation showing the union of cones slicing technique.
+\paper{3.1 Overview, third paragraph}
+{
+\revise{}{%afs
+The video in the supplementary material provides an example animation of this approach.
+}
+}
+
 We removed the angles graph of old Fig.~17e.

### 2020-01-29 0_reviewer_response.tex
remove TODO notice in response letter
remove preprint notice from response letter
fix various aspects of abstract

@@
 \IncludeTextChangestrue
+
+    \makeatletter
+    \def\ps@pprintTitle{%
+       \let\@oddhead\@empty
+       \let\@evenhead\@empty
+       \def\@oddfoot{\reset@font\hfil\thepage\hfil}
+       \let\@evenfoot\@oddfoot
+    }
+    \makeatother
 
@@
 	\newcommand{\question}[1]{{\bf#1}}
-	\newcommand{\todo}[1]{\par\noindent{\bf \color{orange}#1}}
+	%\newcommand{\todo}[1]{\par\noindent{\bf \color{orange}#1}}
 	\newcommand{\commits}[1]{{\bf\begin{alltt} {#1}\end{alltt}}}
@@
 }
-\todo{Comment for us internally (should be removed before this letter is sent).}
+%\todo{Comment for us internally (should be removed before this letter is sent).}
 \commits{123commit-hash}
@@
 \revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
-{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers with contour-parallel extrusion toolpaths.}
 }
@@
 \paper{Abstract}{
-Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
-\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
- Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
- In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
+3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
+\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers with contour-parallel extrusion toolpaths.}
+\revise{Toolpath with uniform }{Uniform width toolpaths consisting of} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts\revise{ such as casings and microstructures}{}.
+\revise{}{In order to fill shapes with arbitrary diameter densely the toolpaths require adaptive width.}
+Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately\revise{, if not beyond their capabilities.}{.}
+In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
 Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.

### 2020-01-29 0_main.tex
fix Charlie Wangs name!
fix various aspects of abstract

--- 2020-01-28 0_main.tex
@@
 \cortext[cor1]{Corresponding author}
-\author[cuhk]{\censor{Charlie Wang}}
+\author[cuhk]{\censor{Charlie C. L. Wang}}
 % \ead{cwang@mae.cuhk.edu.hk}
@@
 \revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
-{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
-\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
-Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
-In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
+{High stiffness parts are produced by filling the 2D polygons of consecutive layers with contour-parallel extrusion toolpaths.}
+\revise{Toolpath with uniform }{Uniform width toolpaths consisting of} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts\revise{ such as casings and microstructures}{}.
+\revise{}{In order to fill shapes with arbitrary diameter densely the toolpaths require adaptive width.}
+Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately\revise{, if not beyond their capabilities.}{.}
+In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
 Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
-We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
 We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd

### 2020-01-29 0_reviewer_response.tex
explain contour vs direction parallel better

@@
 \paper{1. Introduction}{
+FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
 \revise{
+A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
+because the position and shape of the toolpath can be controlled relatively accurately.
+Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
 Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
-}{
-Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
-This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
+}{%sgd
+A common strategy is to extrude along a number of parallel toolpaths which follow the shape of the contour of the layer and fill up the remaining area using parallel straight toolpaths.
+Contour-parallel toolpaths fit to the layer outlines more accurately, because the resolution of the positioning system is an order of magnitude smaller than the size of the hole in the nozzle.
+This paper is concerned with the generation of such contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
+%Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
+%This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
 }

### 2020-01-29 1_intro.tex
remove patent notice and move code url to conclusion
explain contour vs direction parallel better

--- 2020-01-25 1_intro.tex
@@
 FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
+\revise{
 A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
@@
 Filling up a shape using parallel straight lines would expose defects of the size of the hole in the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
-\revise{
 Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction-parallel extrusion does.
-}{
-Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
-This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
+}{%sgd
+A common strategy is to extrude along a number of parallel toolpaths which follow the shape of the contour of the layer and fill up the remaining area using parallel straight toolpaths.
+Contour-parallel toolpaths fit to the layer outlines more accurately, because the resolution of the positioning system is an order of magnitude smaller than the size of the hole in the nozzle.
+This paper is concerned with the generation of such contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
+%Because contour-parallel extrusion leads to a more accurate outline shape it is common practice to print either the whole layer or only a limited number of outer perimeters that way.
+%This paper improves on those contour-parallel toolpaths and addresses several issues which commonly occur in 3D models with narrow geometry.
 }
@@
 
-\revise{}{\xblackout{The presented framework is patented by Ultimaker and open source available at} \censor{\url{github.com/Ultimaker/libArachne}}.}
-
 %This work is patent pending, but the source code is available open source.

### 2020-01-29 0_reviewer_response.tex
some lil changes to response extra changes

@@
 8a11aa0105d1c7f1f5690c8e1f932be85a90bcae % more changes to shell + widening fig
+fc6e05c79340dafd15a9f95de175de696c427513 % explain contour vs direction parallel better
 }
@@
 \begin{itemize*}
-\item Remove wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.
+\item Removed wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.
 \commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
@@
 }
-\item Fix double header of References.
+\item Fixed double header of References.
 \commits{7597b176f6a88ae98c8c7a4c791475af356b3da6}
+\item Fixed various issues in References.
+\commits{c524eae1a78dd1ca54293522139c44a68a911e80}
 \item Fixed some typos.

### 2020-01-29 0_main.tex
remove 'for FDM' (reviewer 3.1)

@@
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
-Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+Furthermore, we propose a novel scheme\revise{ for FDM printing} which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
 We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd

### 2020-01-29 10_applications.tex
small textual changes suggested by Zjenja

--- 2020-01-20 10_applications.tex
@@
 \subsection{Applications}
-Toolpath with varying width is particularly meaningful for narrow parts, since there the negative effect of under- and overfill is more pronounced than in wide parts.
+Toolpath\revise{}{s} with varying width is particularly meaningful for narrow parts, since there the negative effect of under- and overfill is more pronounced than in wide parts.
 In extreme cases, thin features will not be filled at all.

### 2020-01-29 1_intro.tex
small textual changes suggested by Zjenja

@@
 FDM printers are used, for example, in showcasing scale models of buildings, casings for electronics, prototypes for blow molded parts, jigs and fixtures.
-Recent research developments have investigated manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Al-Ketan2018,Maskery2018} and topology optimized structures~\cite{Zegard2016SMO,Wu2019a,Cheng2019}.
-Many of these applications involve 3D models with detailed features within the order of magnitude of the printing resolution, which restrains the field of the process planning algorithms.
+Recent research \revise{developments have investigated}{adressed} manufacturing complex volumetric structures such as microstructures~\cite{bates2018compressive,Al-Ketan2018,Maskery2018} and topology optimized structures~\cite{Zegard2016SMO,Wu2019a,Cheng2019}.
+Many of these applications involve 3D models with detailed features within the order of magnitude of the \revise{printing resolution}{nozzle size}, which restrains the field of the process planning algorithms.
 
@@
 
-The simple technique for generating the dense contour-parallel toolpaths of a layer consists in performing uniform inward offsets with the size of the nozzle from the outline shape.
+The simple technique for generating the dense contour-parallel toolpaths of a layer consists \revise{in}{of} performing uniform inward offsets with the size of the nozzle from the outline shape.
 However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and areas which are not filled at all: \emph{underfill} areas.
@@
 Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
-Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
-These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are relatively large compared to the whole part.
+Underfills\revise{}{,} on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
+These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are relatively large compared to the \revise{whole part}{those features}.
 
-One promising direction to avoid over- and underfills is to employ toolpath with adaptive width.
+One promising direction to avoid over- and underfills is to employ toolpath\revise{}{s} with adaptive width.
 \citeauthor{Ding2016a} developed a toolpath strategy for wire and arc additive manufacturing which produces a width variation typically lower than a factor of $3$, but is \revise{sometimes}{} far greater\revise{}{ for some parts}~\cite{Ding2016a,Xiong2019}.
-However, the range of widths manufacturable by FDM systems is limited.
+However, the range of \revise{}{bead }widths manufacturable by FDM systems is limited.
 A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
@@
 
-The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+The current \revise{state-of-the-art}{state of the art of contour-parallel toolpath generation} \revise{for FDM printing }{}developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
 % (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
@@
 Still, controlling the extrusion width through movement speed changes or through volumetric flow control (e.g.
-linear advance) yields diminishing accuracy for deposition widths farther away from the nozzle size,
+linear advance) yields diminishing accuracy for deposition widths \revise{farther away}{deviating more} from the nozzle size,
 since process parameters such as nozzle temperature are optimized for beads with the nozzle size.

### 2020-01-29 2_related_work.tex
small textual changes suggested by Zjenja

--- 2019-12-11 2_related_work.tex
@@
 A discontinuous path requires to stop and restart material extrusion.
-For certain materials such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
+For certain materials\revise{}{,} such as TPU, this could lead to printing defects or even print failure~\cite{KUIPERS2019CAD}.
 Second, the toolpath is preferred to be smooth.
 Sharp turns require to reduce the movement speed of the nozzle, and so this prolongs the printing process.
-Third, the extruded path should cover \revise{a }{}the region of the contour without gaps.
+Third, the extruded path should cover \revise{a }{}the region of the contour without \revise{gaps}{underfilling}.
 Such underfill negatively influences the mechanical performance of the parts.
 Fourth, the extrusion paths should not overlap with one another.
-Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in further paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
+Such overfill causes a pressure build up in the mechanical system, which leads to overextrusion in \revise{further}{later} paths and in extreme cases cause print failure~\cite{KUIPERS2019CAD}.
 An analysis of under- and overfill from a vertical cross-section was presented in~\cite{Han2002JMSE}. 
@@
 % basic toolpath strategies and their variations
-Two basic strategies for dense toolpath generation are direction-parallel and contour-parallel.
+Two basic strategies for dense toolpath generation are \revise{}{the }direction-parallel\revise{}{ strategy} and \revise{}{the }contour-parallel\revise{}{ strategy}.
 Direction-parallel (or zig-zag) toolpaths fill an arbitrarily shaped contour with a set of parallel, equally spaced line segments.
@@
 To avoid problems with such gaps, hybrid approaches that combine direction and contour-parallel are often used~\cite{Mcmains2000DETC,Jin2013adaptive}.
-Close to the slice boundary, there are several contour-parallel curves, while in the interior is filled using a zig-zag pattern.
+Close to the slice boundary, there are several contour-parallel curves, while \revise{in }{}the interior is filled using a zig-zag pattern.
 For complex shapes, the entire cross-section could be decomposed into a set of patches, and for each of them the basic strategies can be applied~\cite{Ding2014,Jin2017RCIM}.
@@
 % the idea, and (some of) the most related work
-Reducing under- and over-filling can be accurately achieved by making use over adaptive depisition width.
+Reducing under- and over-filling can be accurately achieved by making use \revise{over}{of} adaptive \revise{depisition}{deposition} width.
 Adaptive width can be used to locally match the nonuniform space between adjacent paths, and thus to ensure a better filling of the area.

### 2020-01-29 4_method.tex
reference to video in paper (extra change)
small textual changes suggested by Zjenja

@@
 The union of cones corresponding to the smoothed skeleton is then sliced at regular intervals to obtain toolpaths with varying spacing, which translates into varying width (\cref{sec_toolpath_extraction}).
+\revise{}{%afs
+The video in the supplementary material provides an example animation of this approach.
+}
 
@@
 The medial axis of a polygonal shape is a subset of the Voronoi Diagram generated from the line segments and vertices of the shape~\cite{lee1982medial}. 
-The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and thus discarded.
+The edges of the Voronoi diagram that fall outside of the outline shape are irrelevant for our purpose and \revise{}{are }thus discarded.
 Note that besides the full medial axis, the Voronoi diagram also contains edges connecting to concave vertices in the outline shape (see \cref{shape_decomposition_vd}). 
@@
 After initializing the marking at all edges and nodes, we filter out high frequency changes in the marking in order to ensure that the generated toolpath is smooth. 
-The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce large over- and underfill areas.
+The filtering is performed by additionally marking some unmarked elements, rather than the opposite since unmarking central regions reintroduce\revise{}{s} large over- and underfill areas.
 From each marked node $v_0$ with an upward unmarked edge attached we walk along the upward edges;
 if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all edges encountered as being central.
-\revise{}{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to significance measure.}
+\revise{}{We use $d_\text{max}^\text{unmarked} = w^*$ in order to filter out high frequency oscillations in the order of magnitude of the nozzle size, while keeping close to the significance measure.}
 
 \subsection{Central height adjustment}\label{sec_central_height_adjustment}
-Now that we have identified and marked the central regions we quantize their heights.
+Now that we have identified and marked the central regions\revise{}{,} we quantize their heights.
 We first quantize the initial bead count $\tilde{b}$ into an integer bead count $\bar{b}$ at the marked nodes using a quantization operator $q$,
@@
 Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
-Together with a sequence of bead widths $W$ these form what we call a \emph{beading} $B$.
+Together with a sequence of bead widths $W$\revise{}{,} these form what we call a \emph{beading} $B$.
 For our distributed beading scheme we compute the beading for a central node $v$ with $n = \lfloor \hat{b}_v \rfloor$ beads and a diameter $r = R(v)$  as:
@@
 All trapezoids in the ST are assigned to separate domains, corresponding to which boundary polygon they are connected to (see \cref{shape_decomposition_domains})~\cite{Ding2016a}.
-By traversing the trapezoids in per domain in order we can efficiently connect all segments into polylines.
+By traversing the trapezoids \revise{in }{}per domain in order we can efficiently connect all segments into polylines.
 See \cref{segment_generation}.
@@
 We deal with this special case by forcing a new polyline when traversing the trapezoids, and in the final polyline connection step we greedily connect the first two polylines ending in the same location and retreat all other polylines ending in that same location in order to prevent the overfill.
-In order to retreat a polyline which ends in a site $S$ we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$\revise{, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.}{.
+In order to retreat a polyline which ends in a site $S$\revise{}{,} we remove part of the polyline paths up to the intersection by a distance of $w^S d_\text{max}^\text{intersection}$\revise{, where $d_\text{max}^\text{intersection}$ is some ration between $0$ and $1$.}{.
 We set $d_\text{max}^\text{intersection} = \SI{75}{\percent}$ in order to slightly favor overfilling over underfilling.}

### 2020-01-29 6_2_printing_results.tex
remove \revise macro everywhere
small textual changes suggested by Zjenja

@@
 %In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
-One approach would be keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
+One approach would be\revise{}{ to} keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
 However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
@@
 but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
-We conjecture that the amount of back pressure is monotonically related to the requested line width and compensate for the back pressure using a simple linear model:
+The amount of back pressure is most likely monotonically related to the requested line width.
+We compensate for the back pressure using a simple linear model:
 
@@
 we discretize adaptive width extrusions into \SI{0.2}{\milli\meter} long segments of the average width.
-The results can be viewed in \cref{prints}.
+The print results can be viewed in \cref{prints}.
 
@@
 In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for \xblackout{the Ultimaker word mark}, which negatively impacts the visual quality and the stiffness of the part.
-Moreover, in the case of the spatially graded honeycomb there are several fully disconnected hexagons, which means the object falls apart when picked up.
+Moreover, in the case of the spatially graded honeycomb\revise{}{,} there are several fully disconnected hexagons, which means the object falls apart when picked up.
 The honeycomb print is also missing all parts which are slightly more thin than the preferred bead width $w^*$.

### 2020-01-29 0_reviewer_response.tex
remove 'for FDM' (reviewer 3.1)
focus on dense shell of 3D model (reviewer 3.2)

@@
 }
+\paper{Abstract}
+{
+Furthermore, we propose a novel scheme\revise{ for FDM printing} which [\dots]
+}
 \paper{1. Introduction, bullet list}{
@@
 }
+}
+\paper{2. Related Work}
+{
+In this paper, we focus on \revise{generating toolpath that seamlessly fills the entire 2D contour.}{the generation of toolpaths for dense regions, such as the boundary shell of 3D shapes.}
 }

### 2020-01-29 2_related_work.tex
focus on dense shell of 3D model (reviewer 3.2)

@@
 For reducing printing time and material cost, sparse infill structures such as triangular and hexagonal patterns have been used to approximate the interior of 3D shapes.
-In this paper, we focus on generating toolpath that seamlessly fills the entire 2D contour.
+In this paper, we focus on \revise{generating toolpath that seamlessly fills the entire 2D contour.}{the generation of toolpaths for dense regions, such as the boundary shell of 3D shapes.}
 This is sometimes called `dense infill'~\cite{Livesu2017CGF}.

### 2020-01-29 2_related_work.tex
some more textual changes

@@
 Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
-\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
+\citeauthor{Moesen2011} proposed a method to \revise{make beam compensation more reliable for}{reliably manufacture} thin geometric features\revise{}{ using laser-based additive manufacturing techniques}~\cite{Moesen2011}.
+>> achange!!
 \citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.

### 2020-01-29 6_2_printing_results.tex
some more textual changes

@@
 \subsubsection{Back pressure compensation}
-We therefore keep the internal pressure constant, and vary the movement speed instead.
+Because changing the internal pressure is difficult in our setup,
+we keep the internal pressure constant, and vary the movement speed instead.
 %In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.

### 2020-01-29 0_reviewer_response.tex
commit tags in response

@@
 1935689874235a6c1d5b8f0fed725afa53804935 % don't introduce only one strategy for FDM only
+56bbbaf0b6de98f6e6d4b4fa849ee17cf98e4b3a % remove `for FDM'
 }
@@
 fc6e05c79340dafd15a9f95de175de696c427513 % explain contour vs direction parallel better
+7a2b37513a940ea71a54be05075e46157084b40b % in related work
 }

### 2020-01-29 6_validation.tex
commit tags in response

@@
 }
-We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme.
+We found that the mean width of the inward and evenly distributed schemes is close to \revise{}{the }preferred bead width of \revise{\SI{400}{\micro\meter}}{\SI{0.5}{\milli\meter}}, while their standard deviation is lower than for the centered and constant bead count scheme.
 These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.

### 2020-01-29 0_main.tex
remove all censoring stuff (fixes layout issue)

@@
 
-	\newif\ifcensor
 	\newif\ifcolorrevise
 
-	\censorfalse
 	\colorrevisetrue
-
-    \usepackage{censor}
-	\def\censorcolor{black}
-	\let\svcensorrule\censorrule
-	\renewcommand\censorrule[1]{%
-	\textcolor{\censorcolor}{\svcensorrule{#1}}}
-
-    \newcommand{\censoromit}[1]{}
-	\newcommand{\censornotice}{}
-	\ifcensor
-		\renewcommand{\censornotice}{\\Anonymized 2020 (under revision)}
-	\else
-		\renewcommand{\censoromit}[1]{#1}
-		\StopCensoring
-    \fi
 
@@
 
-\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice}
+\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}}
 
@@
 
-\author[um,tud]{\censor{Tim Kuipers}}
-\author[tud]{\censor{Eugeni L. Doubrovski}}
-\author[tud]{\censor{Jun Wu}\corref{cor1}}
-\censoromit{\ead{j.wu-1@tudelft.nl}}
+\author[um,tud]{Tim Kuipers}
+\author[tud]{Eugeni L. Doubrovski}
+\author[tud]{Jun Wu\corref{cor1}}
+\ead{j.wu-1@tudelft.nl}
 \cortext[cor1]{Corresponding author}
-\author[cuhk]{\censor{Charlie C. L. Wang}}
+\author[cuhk]{Charlie C. L. Wang}
 % \ead{cwang@mae.cuhk.edu.hk}
-\address[um]{\censor{Ultimaker, Utrecht, The Netherlands}}
-\address[tud]{\censor{Department of Sustainable Design Engineering, Delft University of Technology, The Netherlands}}
-\address[cuhk]{\censor{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}}
+\address[um]{Ultimaker, Utrecht, The Netherlands}
+\address[tud]{Department of Sustainable Design Engineering, Delft University of Technology, The Netherlands}
+\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
 

### 2020-01-29 10_applications.tex
remove all censoring stuff (fixes layout issue)

@@
 \begin{subfigure}{\textwidth}\centering
-\censorbox{
 \includegraphics[width=\textwidth]{sources-applications-combined-small-dilated-circled.pdf}
-}
 %\caption{Overview}\label{applications_overview}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\censorbox{
 \includegraphics[height=\figheight]{sources-applications-tud-logo.png}
-}
-\caption{\censor{TUD}}\label{applications_tud}
+\caption{TUD}\label{applications_tud}
 \end{subfigure}
 \begin{subfigure}[t]{\figwidth}\centering
-\censorbox{
 \includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
-}
-\caption{\censor{UM}}\label{applications_um}
+\caption{UM}\label{applications_um}
 \end{subfigure}

### 2020-01-29 6_2_printing_results.tex
remove all censoring stuff (fixes layout issue)

@@
 % discussion of print results
-In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for \xblackout{the Ultimaker word mark}, which negatively impacts the visual quality and the stiffness of the part.
+In \cref{print_naive} the underfill problem of the naive uniform offset approach is most prevalent for the Ultimaker word mark, which negatively impacts the visual quality and the stiffness of the part.
 Moreover, in the case of the spatially graded honeycomb\revise{}{,} there are several fully disconnected hexagons, which means the object falls apart when picked up.
@@
 Moreover, the absence of dark regions signifies that our proposed method is more robust against inaccuracies in the deposition system.
-However, both the centered and inward distributed approach introduce transitions to a different bead count in \xblackout{the word `Delft'}, which reduces the dimensional accuracy on the outline around those locations.
+However, both the centered and inward distributed approach introduce transitions to a different bead count in the word `Delft', which reduces the dimensional accuracy on the outline around those locations.
 
@@
 \begin{subfigure}{\figwidth}\centering
-\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-target}
-}
 \caption{Outlines}\label{print_outlines}
@@
 \begin{subfigure}{\figwidth}\centering
-\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
-}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
-\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
-}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
-\censorbox{
 \includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
-}
 \caption{Inward distributed}\label{print_inward}

### 2020-01-29 0_main.tex
lil language fix in abstract

@@
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
-Furthermore, we propose a novel scheme\revise{ for FDM printing} which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+Furthermore, we propose a novel scheme\revise{ for FDM printing} which \revise{avoids}{reduces} extreme bead width\revise{ deviation from the nozzle size}{s}, \revise{and limits}{while limiting} the number of altered toolpaths.
 We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd

### 2020-01-29 0_reviewer_response.tex
lil fix of revise command in abstract

@@
 {
-Furthermore, we propose a novel scheme\revise{ for FDM printing} which [\dots]
+Furthermore, we propose a novel scheme\revise{ for FDM printing}{} which [\dots]
 }
@@
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
-Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+Furthermore, we propose a novel scheme\revise{ for FDM printing}{} which \revise{avoids}{reduces} extreme bead width\revise{ deviation from the nozzle size}{s}, \revise{and limits}{while limiting} the number of altered toolpaths.
 We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd

### 2020-01-29 0_main.tex
lil fix of revise command in abstract

--- 2020-01-29 0_main.tex
@@
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by \revise{using}{employing} a function to decide the number of beads and their widths\revise{ which are applied from the center outward.}{.}
-Furthermore, we propose a novel scheme\revise{ for FDM printing} which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
+Furthermore, we propose a novel scheme\revise{ for FDM printing}{} which \revise{avoids}{reduces} extreme bead width\revise{ deviation from the nozzle size}{s}, \revise{and limits}{while limiting} the number of altered toolpaths.
 We \revise{}{statistically }validate the effectiveness of our framework and this novel scheme on a data set of \revise{300 slices.}{representative 3D models, }%sgd

### 2020-01-29 0_reviewer_response.tex
center scheme => centered scheme

@@
 From the beading function we can easily derive the under-/overfill by summing over the bead widths $W$.
-We can then derive that the naive scheme produces over-/underfill at all diameters except $d=2i w^*$, the center scheme for $(i + 0.8) w^* < d < (i+ 1.25) w^*$ and the constant and distributed schemes nowhere (except for features smaller than $w^*$).
+We can then derive that the naive scheme produces over-/underfill at all diameters except $d=2i w^*$, the centered scheme for $(i + 0.8) w^* < d < (i+ 1.25) w^*$ and the constant and distributed schemes nowhere (except for features smaller than $w^*$).
 We have added a paragraph to the new section~5.1~Theoretical consideration to explain this and the implications for design for additive manufacturing.
@@
 Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
 For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.

### 2020-01-29 8_discussion.tex
center scheme => centered scheme

--- 2020-01-25 8_discussion.tex
@@
 Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.25) w^*$ in order to avoid underfill.
 For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.

### 2020-01-29 0_reviewer_response.tex
don't describe factor, but range, and fix range of Jin (reviewer 3.4)

@@
 Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
-For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
+For the center\revise{ed} scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.25) w^*$ in order to avoid underfill.
 For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
@@
 \item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme for FDM printing which
-\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
+\item A specific beading scheme\revise{ for FDM printing}{,} which
+reduces the \revise{amount of deviation}{variation} in the extrusion widths \revise{compared to existing literature, }{to within $[0.75w,1.5w]$.}
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}
@@
 The wedge shape of Fig.~1 was chosen because it contains a wide range of feature sizes and is therefore representative for a wide range of models.
-Nearly every model induces the full range of $[0.5w^*,1.8w^*]$ using the centered approach by \citeauthor{Jin2017JMS},
+Nearly every model induces the full range of $[0.25w^*,1.8w^*]$ using the centered approach by \citeauthor{Jin2017JMS},
 because nearly all models have feature sizes which span any range $[iw^*,(i+1)w^*]$ for $i\in\mathcal{N}$.
@@
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
-the variation is within a factor of $3.6$.}
+the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.25 w^*$ and $1.8w^*$.}
 \revise{}{However, it does produce some narrow underfill regions.}
@@
 the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
-\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+\revise{}{{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
 \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
-\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
-the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, which is a considerably smaller range than in the centered scheme.}
 We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
@@
 \Ans{
-The bead width in \citeauthor{Jin2017JMS} is limited to the interval $[0.5 w^*,1.8 w^*]$ , which means the variation is a factor of $\text{max} / \text{min} = 1.8 / 0.5 = 3.6$. 
-\footnote{
-This new statistic replaces the old statistic of deviation from the preferred nozzle size: $\text{max} / w^*$.
-This old statistic is odd because it cannot take the min into account.
-Also the old statistic of $2.0$ had been computed using the hypothetical max of $2.0 w^*$ rather than the actually used $1.8w^*$.
-}
-
-We now emphasize that our method results in a bead width variation of $2$ (which is less than $3.6$) in the related work section and in the discussion section.
-This factor comes from the transition from a single bead to two beads.
-It is not possible to generate toolpaths with a lower interval of bead widths if you consider geometry with arbitrary feature radius.
-%(The transition from zero beads to one is disregarded; it is controlled separately by the Widening meta-scheme.)
+The bead width in \citeauthor{Jin2017JMS} is limited to the interval $[0.25 w^*,1.8 w^*]$, whereas ours is limited to $[0.75 w^*, 1.5 w^*]$.
+
+In the old manuscript we referred to the `deviation' from the preferred width as $1.8w^*/w^*=1.8$, wich was a confusing statistic.
+Moreover, instead of the actual $1.8$ used by \citeauthor{Jin2017JMS} we used the theoretically maximum value of $2.0$ to arrive at a `deviation factor' of $2$.
+We now don't refer to any such confusing statistic and instead just mention the range of widths itself.
 }
@@
 \paper{1. Introduction}{
-The current \revise{state-of-the-art}{state of the art} for FDM printing developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
+The current \revise{state-of-the-art}{state of the art of contour-parallel toolpath generation} \revise{for FDM printing }{}developed by \citeauthor{Jin2017JMS}
+employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths $[0.25w,1.8w]$}~\cite{Jin2017JMS},
 }
@@
 In \cref{TEST_Center_accuracy} we can see that
-the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e.
-the variation is within a factor of $3.6$.}
+the centered beading scheme effectively deals with \revise{both }{}overfill \revise{and underfill }{}and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.25 w^*$ and $1.8w^*$.}
 
@@
 
-\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
-the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, which is a considerably smaller range than in the centered scheme.}
 We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
@@
 [\dots]
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
-Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the \revise{radius}{distance} between the center \revise{and either }{}of those beads falls short of \revise{$r_\text{min} = 0.8 w^*$}{$d_\text{min} = 0.8 w^*$}\revise{}{, which gives us $w_\text{max}=d_\text{min} + 2 \cdot \frac12 w^* = 1.8 w^*$}.
+Conversely, they place an extra bead when the \revise{radius between the center and either of the innermost beads}{distance} exceeds \revise{$r_\text{max} = 1.25 w^*$}{$d_\text{max} = 1.25 w^*$}~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}= d_\text{max} - 2 \cdot \frac12 w^* = 0.25 w^*$}~\cite[p.~72]{Jin2017JMS}.
 We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.

### 2020-01-29 1_intro.tex
don't describe factor, but range, and fix range of Jin (reviewer 3.4)

@@
 However, the range of \revise{}{bead }widths manufacturable by FDM systems is limited.
-A nozzle of \SI{0.4}{\milli\meter} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
+A nozzle of \revise{\SI{0.4}{\milli\meter}}{$w=\SI{0.4}{\milli\meter}$} will typically start to cause fluttered extrusion around lines narrower than \SI{0.3}{\milli\meter} and lines will start to bulge upward if they are wider than the flat part of the nozzle, which is typically \SI{1.0}{\milli\meter}.
 %Therefore, a limited range of widths is required by the hardware system.
 
-The current \revise{state-of-the-art}{state of the art of contour-parallel toolpath generation} \revise{for FDM printing }{}developed by \citeauthor{Jin2017JMS} employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths with a factor of $3.6$}~\cite{Jin2017JMS},
-% (0.8 + 1) / (2* (1.25 - 1)), see rmin, rmax, Table 1e, Centered strategy
+The current \revise{state-of-the-art}{state of the art of contour-parallel toolpath generation} \revise{for FDM printing }{}developed by \citeauthor{Jin2017JMS}
+employs a strategy which alters the widths of the centermost beads \revise{at most by a factor of $2$}{within a range of widths $[0.25w,1.8w]$}~\cite{Jin2017JMS},
 which is similar to the strategy employed by the open source industry standard software package Ultimaker Cura~\cite{cura}.
@@
 \item A geometric framework \revise{for generating densely filling contour-parallel toolpaths employing adaptive width, according to any beading scheme which decides on the bead spacing and widths.}{allowing various adaptive bead width control schemes used to generate contour-parallel toolpaths which minimize under- and overfill.}
-\item A specific beading scheme \revise{for FDM printing}{} which
-\revise{}{furthermore} reduces the amount of \revise{deviation}{variation} in the extrusion widths compared to \revise{existing literature, }{the state of the art to be below a factor of 2.}
+\item A specific beading scheme\revise{ for FDM printing}{,} which
+reduces the \revise{amount of deviation}{variation} in the extrusion widths \revise{compared to existing literature, }{to within $[0.75w,1.5w]$.}
 \revise{and which promotes smooth toolpaths that are equal to the preferred width toward the outline of the shape.}{}

### 2020-01-29 2_related_work.tex
don't describe factor, but range, and fix range of Jin (reviewer 3.4)

@@
 from any point in the skeleton to the boundary, the number of toolpaths is constant.
+\revise{%sdg
 Since the distance may vary considerably for shapes with both large and small features, this strategy leads to a toolpath with widths that may differ by a factor beyond $3$, which is impossible for some FDM systems.
+}{%f
+Depending on the size of small and large features in the layer outlines, this strategy can require a range of bead widths beyond the capabilities of the manufacturing system.
+}%sagd
 \citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
-The resulting variation of width in the center is still up to a factor of \revise{$2$}{$3.6$} (see \cref{intro_wedge_centered}).
+The resulting \revise{variation of width in the center is still up to a factor of $2$}{beads have widths within the wide range of $[0.25w,1.8w]$} (see \cref{intro_wedge_centered}).
 In this paper we propose a novel scheme to distribute the width alterations throughout a region around the center, and thus limit the occurrence of extreme \revise{deviations}{variation} in width (see \cref{intro_wedge_distributed}).

### 2020-01-29 5_generalization.tex
fix Fig refs in paper and mostly response letter
center scheme => centered scheme
don't describe factor, but range, and fix range of Jin (reviewer 3.4)

--- 2020-01-25 5_generalization.tex
@@
 \begin{cases}
--1 & \text{ if } q^-(d) w^* - d > w^* - r_\text{max} \\
-1  & \text{ if }  q^-(d) w^* - d < w^* - r_\text{min} \\
+-1 & \text{ if } q^-(d) w^* - d > w^* - \revise{r}{d}_\text{max} \\
+1  & \text{ if }  q^-(d) w^* - d < w^* - \revise{r}{d}_\text{min} \\
 0 & \text{ otherwise}
@@
 We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
-\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w^*$\revise{}{, which gives us $w_\text{max}=1.8 w^*$}.
-Conversely, they place an extra bead when the radius \revise{between the center and either of the innermost beads }{}exceeds $r_\text{max} = 1.25 w^*$~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}=0.5 w^*$}.
+\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the \revise{radius}{distance} between the center \revise{and either }{}of those beads falls short of \revise{$r_\text{min} = 0.8 w^*$}{$d_\text{min} = 0.8 w^*$}\revise{}{, which gives us $w_\text{max}=d_\text{min} + 2 \cdot \frac12 w^* = 1.8 w^*$}.
+Conversely, they place an extra bead when the \revise{radius between the center and either of the innermost beads}{distance} exceeds \revise{$r_\text{max} = 1.25 w^*$}{$d_\text{max} = 1.25 w^*$}~\cite{Jin2017JMS}\revise{}{, which gives us $w_\text{min}= d_\text{max} - 2 \cdot \frac12 w^* = 0.25 w^*$}~\cite[p.~72]{Jin2017JMS}.
 We emulate the rounded polygonal path rerouting they define by supplying a transition length \revise{}{$t(n) = \frac12 w^*$} which results in a discretized version of their rounded polygon segment.
@@
 \caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
-\\ on top of the Center scheme}
+\\ on top of the Centered scheme}
 \label{widening}

### 2020-01-29 8_discussion.tex
don't describe factor, but range, and fix range of Jin (reviewer 3.4)

@@
 \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
-\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e.
-the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
+\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, which is a considerably smaller range than in the centered scheme.}
 We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.

### 2020-01-29 8_discussion.tex
lil: fix some revise typesetting issues

@@
 \revise{}{However, it does produce some narrow underfill regions.}
-\revise{
+\revise{%gs
 According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.
-}{
+}{%sg
 Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of toolpath angles below \SI{45}{\degree}.
-See \cref{statisticsfig}.
-}
+See \cref{statisticsfig}.%afs
+}%zgds
 
@@
 %While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
-\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{} % _
+\revise{However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.}{}% _
 Furthermore, \revise{from \cref{smoothness} }{}we find that compared to evenly distributed, the inward distributed scheme produces \revise{smoother toolpaths overall}{less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.

### 2020-01-29 0_reviewer_response.tex
fix comparison of beading schemes to accomodate new center statistics

@@
 However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
-the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
-\revise{}{{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+the standard deviation of the bead widths in the centered scheme is approximately \revise{\SI{39}{\micro\meter}}{\SI{53}{\micro\meter}}, while that of the distributed schemes is approximately \revise{\SI{14}{\micro\meter}}{\SI{23}{\micro\meter}}.%_
+\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher than that of the evenly distributed scheme, the mean absolute deviation is lower (i.e.
 \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}

### 2020-01-29 8_discussion.tex
fix comparison of beading schemes to accomodate new center statistics

@@
 However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
-the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
-\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e.
+the standard deviation of the bead widths in the centered scheme is approximately \revise{\SI{39}{\micro\meter}}{\SI{53}{\micro\meter}}, while that of the distributed schemes is approximately \revise{\SI{14}{\micro\meter}}{\SI{23}{\micro\meter}}.%_
+\revise{}{\footnote{\revise{}{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher than that of the evenly distributed scheme, the mean absolute deviation is lower (i.e.
 \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}

### 2020-01-29 0_reviewer_response.tex
remove contributions paragraph in favor of bullet list

@@
 {
-In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
-\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
-We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
-\revise{
-For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
-}{Furthermore we present an approach to accurately realize adaptive bead width.
-}
-See \cref{intro_wedge_distributed}. 
-% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
-% Some such toolpath generation techniques have already been developed.
-
 Our contributions are as follows:
@@
 \begin{itemize*}
+\item Removed paragraph before bullet list of contributions, because it contained the same information as the bullet list.
+\commit{}
 \item Removed wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.

### 2020-01-29 1_intro.tex
remove contributions paragraph in favor of bullet list

@@
 
+\revise{
 In this paper we propose a framework for planning toolpaths with control over the adaptive width for minimizing over- and underfill
-\revise{}{and introduce a beading scheme which reduces the bead width variation compared to the state of the art.} 
 We show that this framework supports various control schemes for determining the bead spacing and extrusion widths. 
-\revise{
 For FDM printing in particular we propose a novel scheme which reduces the amount of over- and underfill while ensuring the extrusion beads deviate little from the nozzle size.
-}{Furthermore we present an approach to accurately realize adaptive bead width.
-}
 See \cref{intro_wedge_distributed}. 
-% In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
-% Some such toolpath generation techniques have already been developed.
+}{}
 

### 2020-01-29 0_reviewer_response.tex
change fabrication into its own main section

@@
 }
-\paper{5.3 Limitations, first paragraph}{
+\paper{6.3 Limitations, first paragraph}{
 \revise{}{
@@
 }
-\paper{6. Conclusion, last paragraph}{
+\paper{7. Conclusion, last paragraph}{
 \revise{}{It is expected that as distributed beading schemes are implemented in commercial software packages and bead width variation control become commonplace, the practice of design for additive manufacturing can disregards some of the nozzle size considerations.}
@@
 }
-\paper{6. Conclusion and future work}{
+\paper{7. Conclusion and future work}{
 In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
@@
 }
-\paper{5.2 Computational results}
+\paper{6 Results and discussion}
 {
@@
 }
-\paper{5.1.2 Print results}{\revise{}{The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.}}
-\paper{5.2.3 Print time}
+\paper{5.2 Print results}{\revise{}{The printing order is determined greedily by choosing the closest point of a polygonal extrusion path, or the closest of either end point in case of an open polyline extrusion path.}}
+\paper{6.1.3 Print time}
 {
@@
 }
-\paper{5.3 Comparison of beading schemes}
+\paper{6.2 Comparison of beading schemes}
 {
@@
 }
-\paper{5.2.3 Print time}
+\paper{6.1.3 Print time}
 {
@@
 }
-\paper{6.1 Future work}
+\paper{7.1 Future work}
 {
@@
 }
-\paper{5.2.2 Uniformity}
+\paper{6.1.2 Uniformity}
 {
@@
 }
-\paper{5.1.2 Printing results}
+\paper{5.2 Printing results}
 {
@@
 }
-\paper{5.4 Limitations}
+\paper{6.3 Limitations}
 {
@@
 }
-\paper{5.3 Comparison of beading schemes, paragraph 3, 4}{
+\paper{6.2 Comparison of beading schemes, paragraph 3, 4}{
 In \cref{TEST_Center_accuracy} we can see that
@@
 }
-\paper{5.4 Limitations, second paragraph}
+\paper{6.3 Limitations, second paragraph}
 {
@@
 }
-\paper{5.1.1 Back pressure compensation}
+\paper{5.1 Back pressure compensation}
 {
@@
 
-\paper{6. Conclusion and future work, last paragraph}{
+\paper{7. Conclusion and future work, last paragraph}{
 \revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
@@
 \commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
-\paper{5.2.2 Uniformity}
+\paper{6.1.2 Uniformity}
 {
@@
 }
-\paper{6. Conclusion}{
+\paper{7. Conclusion}{
 \revise{}{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
@@
 \commits{17135b010f5ac51fda77357136a19f67a80dbc33}
-\paper{5.2 Computational results}
+\paper{6 Results and discussion}
 {

### 2020-01-29 6_2_printing_results.tex
change fabrication into its own main section

@@
 \revise{}{
-\subsection{Fabrication}
+\section{Fabrication}
 In order to accurately manufacture adaptive width toolpaths using an off-the-shelf 3D printing system,
@@
 
-\subsubsection{Back pressure compensation}
+\subsection{Back pressure compensation}
 Because changing the internal pressure is difficult in our setup,
@@
 
-\subsubsection{Print results}\label{print_results_section}
+\subsection{Print results}\label{print_results_section}
 Using increments of $0.1$ we established that using a factor of $k=1.1$ yields satisfactory bead width variation for our setup where we use

### 2020-01-29 6_validation.tex
change fabrication into its own main section

@@
 
-\input{6_2_printing_results}
-
-\revise{}
-{
-\subsection{Computational results}\label{sec_computational_results}
-} % tew
 We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
@@
 \revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}
+
+\subsection{Computational results}\label{sec_computational_results}
 

### 2020-01-29 10_applications.tex
make toolpaths plural when separate extrusion paths are considered

@@
 Another class of microstructures consists of parameterized patterns with varying thickness to achieve functional gradation.
-\Cref{applications_hex} shows the contour-parallel toolpath with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath would create for such a case~\cite{bates2018compressive}.
+\Cref{applications_hex} shows the contour-parallel toolpath\revise{}{s} with varying width of a hexagonal grid neatly switches between different bead counts over the volume, preventing the jagged moves a direction-parallel toolpath\revise{}{s} would create for such a case~\cite{bates2018compressive}.
 

### 2020-01-29 1_intro.tex
make toolpaths plural when separate extrusion paths are considered

@@
 \revise{}{These results can be read as a graph with feature size on the horizontal axis and its corresponding beading along the vertical axis.}
-\subref{intro_wedge_uniform} Toolpath using uniform offsetting results in large overfill (orange) and underfill (azure).
-\subref{intro_wedge_centered} Toolpath with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
+\subref{intro_wedge_uniform} Toolpath\revise{}{s} using uniform offsetting results in large overfill (orange) and underfill (azure).
+\subref{intro_wedge_centered} Toolpath\revise{}{s} with adaptive width~\cite{Jin2017JMS} where beads that are wider or narrower than the nozzle size are \revise{indicatd}{indicated} in red and blue, respectively.
 \subref{intro_wedge_distributed} Our approach minimizes over- and underfill with \revise{beads close to the nozzle size}{less extreme widths}.

### 2020-01-29 2_related_work.tex
make toolpaths plural when separate extrusion paths are considered

@@
 The nozzle is then instructed to move along the path while extruding material.
-Sites along the toolpath are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
+Sites along the toolpath\revise{}{s} are assigned several properties such as movement speed, but for this paper we will focus on the assigned width of the extruded bead.
 Toolpath generation is an integral part of process planning for 3D printing.
@@
 Spiral toolpaths have also been applied to (CNC) machining~\cite{Held2009,Huang2017}.
-One of the problems with contour-parallel toolpath is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
+One of the problems with contour-parallel toolpath\revise{}{s} is that it tends to leave gaps between the toolpaths (see \cref{intro_wedge_uniform}).
 This is due to the fact that the diameter of the part is not exact multiple of the (constant) deposition width in those regions.
@@
 }%sagd
-\citeauthor{Jin2017JMS} proposed a strategy of adding a toolpath with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
+\citeauthor{Jin2017JMS} proposed a strategy of adding \revise{a }{}toolpath\revise{}{s} with varying width along the center edges of the skeleton, while leaving other paths unchanged~\cite{Jin2017JMS}.
 The resulting \revise{variation of width in the center is still up to a factor of $2$}{beads have widths within the wide range of $[0.25w,1.8w]$} (see \cref{intro_wedge_centered}).

### 2020-01-29 4_method.tex
make toolpaths plural when separate extrusion paths are considered

@@
 We visualize the skeleton as the union of cones (UoC) (\cref{sec_surface_construction}), by raising each point in the domain to a height that equals the shortest distance from the point to the polygon boundary (\cref{overview_uoc}).
-Contour-parallel toolpath with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).
+Contour-parallel toolpath\revise{}{s} with uniform width can be interpreted as the intersection of the union of cones with a set of \revise{planar}{horizontal} planes at equally spaced heights (\cref{overview_outline,overview_skeleton,overview_uoc,overview_uniform_sliced,overview_uniform_paths}).
 

### 2020-01-29 0_reviewer_response.tex
remove future work in favor of limitations

@@
 }
-\paper{7. Conclusion and future work}{
+\paper{7. Conclusion}{
 In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
@@
 }
-\paper{7.1 Future work}
-{
-An accurate model of manufacturability, \revise{}{which relates }print speed, \revise{}{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
-\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
+\paper{6.3 Limitations}
+{
+\revise{}{
+The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
+$\alpha_\text{max} = \SI{135}{\degree}$ corresponds to $w^* / \cos \nicefrac12 \alpha_\text{max} \approx \SI{0.4}{\milli\meter}$ long segments
+and under-/overfill areas of $\nicefrac14 (w^*)^2 \left( \tan ( \alpha / 2) - \alpha / 2 \right) \approx \SI{0.05}{\milli\meter\squared}$.
+However, future work might be aimed at reducing under-/overfill in regions with a low bisector angle without the introduction of short single polyline extrusion segments.
+If the over-/underfill problem is also solved for non-significant regions we might be able to increase $\alpha_\text{max}$ and reduce the discontinuity introduced by short extrusion segments.
+}
 }
@@
 
-\paper{7. Conclusion and future work, last paragraph}{
+\paper{7. Conclusion, last paragraph}{
 \revise{}{Compared to the naive approach of constant width toolpaths our beading scheme is expected to improve the stiffness, dimensional accuracy and visual qualities of the manufactured model.}
@@
 \item Removed paragraph before bullet list of contributions, because it contained the same information as the bullet list.
-\commit{}
+\commits{0ed48668c93047be8423be054d98a81dfabce305}
+\item Removed Future work section because the limitations are now handled in 6.3 Limitations.
+\commits{}
 \item Removed wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.

### 2020-01-29 12_conclusions_future_work.tex
remove patent notice and move code url to conclusion
remove future work in favor of limitations

@@
-\section{Conclusion and future work}
+\section{Conclusion}
 In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{,
@@
 
+\medskip
+\revise{}{The presented framework is open source available at \\ \url{github.com/Ultimaker/libArachne}}
+
+\revise{
 \subsection{Future work}
@@
 Future research could be devoted to optimizing the distribution scheme to a specific hardware setup.
-An accurate model of manufacturability, \revise{}{which relates }print speed, \revise{}{ layer thickness }and dimensional accuracy would be valuable to fine-tune the beading scheme.
-\revise{}{The work could also be extended in a way which reduces the number of starts and stops of extrusion.}
+An accurate model of manufacturability, print speed and dimensional accuracy would be valuable to fine-tune the beading scheme.
 % If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.
+}{}
 
+\revise{
 Our framework uses the skeleton to determine toolpaths based on the local feature size.
@@
 % Furthermore we could also take into account volumetric considerations such as the toolpathing of the previous layer or volume constraint defined by a functionally graded material.
-
+}{}
 % Taking a broader perspective we note that the skeletonization decomposes a shape into trapezoids and these trapezoids are decomposed into quads by the toolpath segments which we generate for it.

### 2020-01-29 8_discussion.tex
remove future work in favor of limitations

@@
 \subsection{Limitations}
+% design considerations
 Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
@@
 
+% single line segments & continuity
 The default limit bisector angle $\alpha_\text{max} = \SI{135}{\degree}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths;
@@
 
+% single beads
 Another limitation of our method is that in a location $v$ with locally maximal $R(v) \approx (i + \nicefrac12) w^*$ the odd bead count will result in a single polyline extrusion segment consisting of only a single point.
@@
 
+% emulation troubles
 Finally it should be noted that although our framework can accurately emulate the constant bead count approach by \citeauthor{Ding2016a}, its emulation of the centered approach by \citeauthor{Jin2017JMS} is imperfect.

### 2020-01-29 0_reviewer_response.tex
lil breakup of long sentence

@@
 \paper{7. Conclusion}{
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize \revise{underfilland}{underfill and} overfill areas\revise{.}{,
-we introduced beading schemes which improve on the state of the art
-and we have introduced a backpressure compensation method for accurate fabrication of adaptive width.
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
+\revise{}{%af
+We introduced beading schemes which improve on the state of the art,
+and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.
 }

### 2020-01-29 12_conclusions_future_work.tex
lil breakup of long sentence

@@
 \section{Conclusion}
-In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas\revise{.}{,
-we introduced beading schemes which improve on the state of the art
+In this paper we have introduced a framework for computing contour-parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
+\revise{}{%af
+We introduced beading schemes which improve on the state of the art,
 and we have introduced a back pressure compensation method for accurate fabrication of adaptive width.

### 2020-01-29 4_method.tex
prevent overuse of 'We' in section 3

@@
 %This sections covers what parts of the UoC will be marked as being central.
-In order to prevent over- and underfill \revise{to occur}{from occurring} in central\revise{}{ regions}, we mark parts of the ST as being central.
+In order to prevent over- and underfill \revise{to occur}{from occurring} in central\revise{}{ regions}, \revise{we mark }{}parts of the ST \revise{}{are marked }as being central.
 \revise{The remainder is called peripheral.}{}
@@
 
-We mark a node in the ST as central if its feature radius is larger than that of all its neighboring nodes, i.e. a local maxima.
+\revise{We mark a}{A} node in the ST \revise{}{is marked as }as central if its feature radius is larger than that of all its neighboring nodes, i.e. a local maxima.
 %That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
-We also mark an edge as being central if it is significant according to a significance measure.
+\revise{We also mark an}{An} edge \revise{}{and its two nodes are also marked }as being central if it is significant according to a significance measure.
 
@@
 \subsection{Central height adjustment}\label{sec_central_height_adjustment}
-Now that we have identified and marked the central regions\revise{}{,} we quantize their heights.
-We first quantize the initial bead count $\tilde{b}$ into an integer bead count $\bar{b}$ at the marked nodes using a quantization operator $q$,
-then find the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$
-and then introduce ramps to smoothly transition from $n$ to $n+1$ using fractional bead counts $\hat{b}$ along the smooth transition.
+\revise{Now that we have identified and marked}{After }the central regions\revise{}{ have been identified,} \revise{we quantize }{}their heights\revise{}{ are quantized}.
+\revise{We first quantize}{First,} the initial bead count $\tilde{b}$ \revise{}{is quantized }into an integer bead count $\bar{b}$ at the marked nodes using a quantization operator $q$,
+then \revise{find }{}the locations along the edges where $q$ makes a jump from one bead count $n$ to another $n+1$\revise{}{ are identified}
+and then \revise{introduce }{}ramps \revise{}{are introduced }to smoothly transition from $n$ to $n+1$ using fractional bead counts $\hat{b}$ along the smooth transition.
 %\subsubsection{Initial bead count}\label{sec_initial_bead_count}

### 2020-01-29 4_method.tex
reduce overuse of 'Now that' in section 3

@@
 \subsection{Beading}\label{sec_peripheral_height_adjustment}
-Now that we have determined the bead counts in the \revise{}{marked }central regions we will describe how the \revise{peripheral}{unmarked} regions are handled.
+Now that we \revise{have determined}{know how to determine} the bead counts in the \revise{}{marked }central regions \revise{we will describe}{the question is} how the \revise{peripheral}{unmarked} regions are handled.
 Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
@@
 \subsection{Toolpath extraction}\label{sec_toolpath_extraction}
-Now that each node has been assigned a beading we proceed to generate the toolpath sites along the edges of the ST.
+\revise{Now that}{Once} each node has been assigned a beading\revise{}{,} we proceed to generate the toolpath sites along the edges of the ST.
 A site $S$ consists of a location $v$ a width $w$ and an index $i$, which are computed for an edge $v_0v_1$ from the beading $B$ of the upper node $v_1$:

### 2020-02-03 4_method.tex
rename files to meet file name character limit

@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--bead-count.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-filtering--bead-count.pdf}
 \caption{Quantized bead counts}\label{beading_transitioning_filtering__bead_count}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-mids.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-filtering--transition-mids.pdf}
 \caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--filtered.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-filtering--filtered.pdf}
 \caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transition-ends.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-filtering--transition-ends.pdf}
 \caption{Transition ramp ends}\label{beading_transitioning_filtering__transition_ends}
@@
 \begin{subfigure}{\figwidth}
-\includegraphics[width=\columnwidth]{sources-method-beading-transitioning-filtering--transitions-applied.pdf}
+\includegraphics[width=\columnwidth]{sources-method-beading-filtering--transitions-applied.pdf}
 \caption{Radial support edges}\label{beading_transitioning_filtering__transitions_applied}
@@
 \begin{subfigure}{.27\textwidth}
-\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-transitioning-filtering--result-uoc.pdf}
+\hspace*{-.5cm}\includegraphics[width=1.2\columnwidth]{sources-method-beading-filtering--result-uoc.pdf}
 \caption{Result UoC}\label{beading_transitioning_filtering__result_uoc}

### 2020-02-03 6_validation.tex
rename files to meet file name character limit

@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-naive-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-naive-widths.png}
 \caption{Uniform}\label{TEST_naive_accuracy}
@@
 %\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-SingleBead-accuracy.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-SingleBead-widths.png}
 %\caption{Single}\label{TEST_SingleBead_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Constant-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Constant-widths.png}
 \caption{Constant}\label{TEST_Constant_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Center-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Center-widths.png}
 \caption{Centered}\label{TEST_Center_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Distributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-Distributed-widths.png}
 \caption{Distributed}\label{TEST_Distributed_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-InwardDistributed-accuracy.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-InwardDistributed-widths.png}
 \caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}

### 2020-04-28 0_reviewer_response.tex
prevent overuse of 'We' in section 3
lil commit hashes
convert png to jpg

@@
 \begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
-\end{subfigure}
-\begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths}
+\end{subfigure}
+\begin{subfigure}{\figwidth}\centering
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths}
 \end{subfigure}
@@
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Distributed-feature-size.png}
+\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Distributed-feature-size}
 \caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
@@
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Center-widening.png}
+\includegraphics[width=\figwidthTwo]{sources-validation-wedge-TEST-Center-widening}
 \caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 
@@
 \begin{subfigure}[b]{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined.png}
+\includegraphics[width=\figwidth]{sources-validation-gMat_example_all_combined}
 \caption{Shell and widening}
@@
 \begin{subfigure}[b]{\figwidth} \centering
-\includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy.png}
+\includegraphics[rotate=-90,width=\linewidth]{response_rects_Center_accuracy}
 \caption{Problematic for center, i.e. \citeauthor{Jin2017JMS}, exhibiting $4.5w^*$ and $5.8w^*$}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths}
 \caption{Uniform}\label{TEST_naive_accuracy}
@@
 %\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths}
 %\caption{Single}\label{TEST_SingleBead_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths}
 \caption{Constant}\label{TEST_Constant_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths}
 \caption{Centered}\label{TEST_Center_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths}
 \caption{Distributed}\label{TEST_Distributed_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths}
 \caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly.png}
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-evenly}
 \caption{Evenly distributed}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward.png}
+\includegraphics[width=\figwidth]{sources-validation-wedge-Distributed-pretty-inward}
 \caption{Inward distributed}
@@
 \setlength{\figwidth}{\mycolumnwidth}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited}
 \caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
-\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
+%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward}
+\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited}
 \caption{Inward distributed}\label{print_inward}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-naive-bw}
 \caption{Uniform}\label{print_naive}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-center-bw}
 \caption{Centered}\label{print_center}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw.png}
+\includegraphics[width=\figwidth]{sources-applications-result-prints-inward-bw}
 \caption{Inward distributed}\label{print_inward}
@@
 \item Removed Future work section because the limitations are now handled in 6.3 Limitations.
-\commits{}
+\commits{e86c7b879a580f9fdcd599fcd9ff12a669f35190}
 \item Removed wrapfigure explaining the area covered by a single extrusion move (in section~5.2.1~Accuracy), since that is already explained in the appendix.
@@
 \commits{c524eae1a78dd1ca54293522139c44a68a911e80}
+\item Reduced superfluous use of the term `we'.
+\commits{a8f434957a577944ed16597de353349844a16462}
+\item Improved syntac and flow of the text.
+% numerous commits
 \item Fixed some typos.

### 2020-04-28 10_applications.tex
convert png to jpg

@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-house.png}
+\includegraphics[height=\figheight]{sources-applications-house}
 \caption{House}\label{applications_house}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-pocket-operator-case.png}
+\includegraphics[height=\figheight]{sources-applications-pocket-operator-case}
 \caption{Case}\label{applications_case}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-david.png}
+\includegraphics[height=\figheight]{sources-applications-david}
 \caption{Statue}\label{applications_statue}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-tud-logo.png}
+\includegraphics[height=\figheight]{sources-applications-tud-logo}
 \caption{TUD}\label{applications_tud}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-ultimaker-logo.png}
+\includegraphics[height=\figheight]{sources-applications-ultimaker-logo}
 \caption{UM}\label{applications_um}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor.png}
+\includegraphics[height=\figheight]{sources-applications-pinion-gear-motor}
 \caption{Gear}\label{applications_gear}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-topopt-bone.png}
+\includegraphics[height=\figheight]{sources-applications-topopt-bone}
 \caption{Bone}\label{applications_bone}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-gyroid.png}
+\includegraphics[height=\figheight]{sources-applications-gyroid}
 \caption{Gyroid}\label{applications_gyroid}
@@
 \begin{subfigure}[t]{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-applications-hex-grid.png}
+\includegraphics[height=\figheight]{sources-applications-hex-grid}
 \caption{Hex}\label{applications_hex}

### 2020-04-28 1_intro.tex
convert png to jpg

@@
 \begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy.png}
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_uniform}}\includegraphics[width=\figwidth]{sources-intro-TEST-naive-accuracy}
 \end{subfigure}
 \begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths.png}
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_centered}}\includegraphics[width=\figwidth]{sources-intro-TEST-Center-widths}
 \end{subfigure}
 \begin{subfigure}{\figwidth}\centering
-\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths.png}
+\parbox[b]{\figwidthTwo}{\subcaption{}\label{intro_wedge_distributed}}\includegraphics[width=\figwidth]{sources-intro-TEST-Distributed-widths}
 \end{subfigure}

### 2020-04-28 4_method.tex
convert png to jpg

--- 2020-01-29 4_method.tex
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-UoC-with-cones.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-UoC-with-cones}
 \caption{Union of cones}\label{overview_uoc}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-naive-cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-naive-cropped}
 \caption{Slicing}\label{overview_uniform_sliced}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-naive.png}
+\includegraphics[width=\figheight,rotate=-90]{sources-method-overview-2D-naive}
 \caption{Uniform paths}\label{overview_uniform_paths}
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-marking-cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-marking-cropped}
 
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-quantized.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-quantized}
 
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-smoothed-magenta.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-smoothed-magenta}
 
@@
 \hspace*{\tempheightTwo}
-\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-cropped.png}
+\includegraphics[height=\figheight]{sources-method-overview-surface-sliced-cropped}
 
@@
 
-\includegraphics[width=\figheight]{sources-method-overview-2D-sliced.png}
+\includegraphics[width=\figheight]{sources-method-overview-2D-sliced}
 \caption{Adaptive width paths}\label{3d_surface_overview_sliced}
@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning.png}
+\includegraphics[width=\columnwidth]{sources-method-wedge-no-transitioning}
 \caption{Without transitioning}
@@
 \begin{subfigure}{0.9\figwidth}\centering
-\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning.png}
+\includegraphics[width=\columnwidth]{sources-method-wedge-transitioning}
 \caption{Transitioning}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-3D.png}
+\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-3D}
 \includegraphics[height=\figheight]{sources-method-beading-conflict.pdf}
@@
 \begin{subfigure}{.45\columnwidth}\centering
-\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-solved-3D.png}
+\includegraphics[width=.95\columnwidth,frame]{sources-method-beading-conflict-solved-3D}
 \includegraphics[height=\figheight]{sources-method-beading-conflict-solved.pdf}

### 2020-04-28 5_generalization.tex
convert png to jpg

@@
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size.png}
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Distributed-feature-size}
 \caption{Widening meta-scheme using $w_\text{min} = 2 r_\text{min} = 0.1$
@@
 \begin{subfigure}[b]{\figwidthTwo}\centering
-\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening.png}
+\includegraphics[width=\columnwidth]{sources-validation-wedge-TEST-Center-widening}
 \caption{Widening meta-scheme using $w_\text{min} = 0.5$, $2 r_\text{min} = 0.2$ 

### 2020-04-28 6_validation.tex
convert png to jpg

@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-naive-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-naive-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths}
 \caption{Uniform}\label{TEST_naive_accuracy}
@@
 %\begin{subfigure}{\figwidth}\centering
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-SingleBead-accuracy.png}
-%\includegraphics[height=\figheight]{sources-validation-gMAT-example-SingleBead-widths.png}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy}
+%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths}
 %\caption{Single}\label{TEST_SingleBead_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Constant-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Constant-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths}
 \caption{Constant}\label{TEST_Constant_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Center-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Center-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths}
 \caption{Centered}\label{TEST_Center_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Distributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-Distributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths}
 \caption{Distributed}\label{TEST_Distributed_accuracy}
@@
 \begin{subfigure}{\figwidth}\centering
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-InwardDistributed-accuracy.png}
-\includegraphics[height=\figheight]{sources-validation-gMAT-example-InwardDistributed-widths.png}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy}
+\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths}
 \caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
@@
 \setlength{\figwidth}{\columnwidth}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
-\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited}
+\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited}
 \caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
